### 2019-04-17 Plan/pages/work_plan.tex
Changes; - Added plan - Organised papers

\chapter{Work Plan}

\section{Literature review}
\label{litReview}
\textbf{Duration}: ? 
\\\\
This stage will involve reviewing the research into producing near collisions with SHA1. This may also extend into producing a review around full collisions of SHA1.
\par
SHA1 has been selected due to its vulnerability. Methods for producing collisions have been known for a long time and it seems the algorithm is on its way out of mainstream use.

\section{Formulation specific research questions}
\textbf{Duration}: ?
\\\\
Questions may currently involve:

\begin{itemize}
    \item What is the probability of producing near-collisions with SHA1?
    \item What would be the complexity in storage and computation?
    \item Can such near-collisions be generated e.g. using the university’s high-performance computing facilities? 
\end{itemize}

Further questions may be added using information gained from already performed research.

\section{Implementing near-collision code}
\label{code}
\textbf{Duration}: ?
\\\\
This section will involve the actual implementation of code using knowledge gained through the literature review. This may be pre-existing code manipulated to work on the university’s HPC cluster.

\section{Determining metrics for measuring experiments}

Ways to measure the progress of a project

\section{Experimentation stage}

\textbf{Duration}: ?
\\\\
This stage will involve running experiments to gain complexity data. This may involve working on further research and validating results.

\section{Thesis/Paper writing}

\textbf{Duration}: ?
\\\\
This will involve the creation of a \textasciitilde70 page dissertation alongside a condensed paper for submission to a journal

### 2019-04-17 Plan/plan.tex
Changes; - Added plan - Organised papers

\documentclass[a4paper,smallheadings,11pt,oneside,bibliography=totoc]{scrreprt}

%Used to change the margin
\newcommand{\margin}{0.75in}
\usepackage[a4paper, left=\margin, right=\margin, top=\margin, bottom=\margin]{geometry}

% Packages
\usepackage[numbers]{natbib} 		% Package for IEE Referencing
\usepackage{graphicx} 				% Package for images
\usepackage{hyperref} 				% Package for URLS and Content links
\usepackage[titletoc]{appendix} 	% Package added for the appendix
\usepackage{mathtools}				% Package for mathmatical notation
\usepackage{wrapfig}				% Wrapping figures on a page
\usepackage{tcolorbox}				% For code listings
\usepackage{titlesec}				% Package for reducing space after headers

%Paragraph settings
\setlength{\parindent}{0em}
\setlength{\parskip}{0.75em}

\begin{document}

	\input{pages/work_plan}
	\input{pages/delivery_plan}

\end{document}

### 2019-05-18 Code/GreenOnion/util/conversion.cpp
Changes; - Began cleaning the #includes

@@ -1,7 +1,6 @@
-#include <string>
-#include <sstream>
-#include <bitset>
-
+#include <bitset>       // for bitset
+#include <sstream>      // for hex, ostringstream, stringstream, basic_ostream
+#include <string>       // for string, operator+, operator<<, basic_string
 
 /*
     UInt32 --> Hex

### 2019-05-18 Code/GreenOnion/util/functions.cpp

@@ -1,15 +1,15 @@
-#include <string.h>
-#include <iostream>
-#include <sstream>
-#include <bitset>
-#include <vector>
-#include <chrono>
-#include <thread>
-#include <math.h>
-
-#include "../cppcodec/cppcodec/base64_rfc4648.hpp"
-#include "../cppcodec/cppcodec/hex_upper.hpp"
-#include "conversion.hpp"
+#include <math.h>                                   // for ceil
+#include <string.h>                                 // for size_t
+#include <sys/types.h>                              // for uint
+#include <chrono>                                   // for milliseconds
+#include <iostream>                                 // for basic_istream, cout
+#include <string>                                   // for string, operator+
+#include <thread>                                   // for sleep_for
+#include <vector>                                   // for vector
+#include <sstream>                                  // for sstream
+#include "../cppcodec/cppcodec/base64_rfc4648.hpp"  // for base64_rfc4648
+#include "../cppcodec/cppcodec/hex_upper.hpp"       // for hex_upper
+#include "conversion.hpp"                           // for hex_to_integer
 
 using base64 = cppcodec::base64_rfc4648;
 using hex = cppcodec::hex_upper;

### 2019-05-18 Code/GreenOnion/bloom/BloomFilter.cpp
Changes; - Fixed all unused imports and provided comments on what included imports provide access to

@@ -1,8 +1,6 @@
-#include <array>
-#include <math.h> 
-
+#include <math.h>         // for log, abs
+#include "MurmurHash3.h"  // for MurmurHash3_x86_32
 #include "BloomFilter.hpp"
-#include "MurmurHash3.h"
 
 BloomFilter::BloomFilter(unsigned long size, short numHashes): m_numHashes(numHashes) 
 {

### 2019-05-18 Code/GreenOnion/bloom/BloomFilter.hpp

@@ -1,5 +1,4 @@
-#include <vector>
-#include <cstdint> 
+#include <cstdint>  // for uint8_t
 
 #ifndef BloomFilter_H
 #define BloomFilter_H

### 2019-05-18 Code/GreenOnion/crypto/hash_util.cpp

@@ -1,7 +1,10 @@
-#include <sstream>
-#include <vector>
+#include <stddef.h>  // for size_t
+#include <stdint.h>  // for uint32_t
+#include <sstream>   // for stringstream, hex, basic_ostream, basic_ostream<...
+#include <string>    // for string, operator+, operator<<
+#include <vector>    // for vector
+#include "sha1.hpp"  // for transform
 
-#include "sha1.hpp"
 
 /*
     Adds SHA-1 padding to a hex string

### 2019-05-18 Code/GreenOnion/crypto/hash_util.hpp

@@ -1,5 +1,6 @@
-#include <sstream>
-#include <vector>
+#include <stdint.h>  // for uint32_t
+#include <string>    // for string
+#include <vector>    // for vector
 
 std::string pad_hex_string_for_sha1(std::string hexString);
 std::vector<std::string> split_hex_to_blocks(std::string hexString, int blockSizeInBytes);

### 2019-05-18 Code/GreenOnion/crypto/sha1.cpp

@@ -14,9 +14,9 @@
         -- Eugene Hopkinson <slowriot at voxelstorm dot com>
 */
 
-#include <sstream>
-#include <vector>
-#include <iostream>
+#include <stddef.h>  // for size_t
+#include <stdint.h>  // for uint32_t, uint64_t
+#include <string>    // for string
 
 
 void reset(uint32_t digest[], std::string &buffer, uint64_t &transforms)

### 2019-05-18 Code/GreenOnion/crypto/sha1.hpp

@@ -1,4 +1,6 @@
-#include <string>
+#include <stddef.h>  // for size_t
+#include <stdint.h>  // for uint32_t, uint64_t
+#include <string>    // for string
 
 #ifndef SHA1_H
 #define SHA1_H

### 2019-05-18 Code/GreenOnion/util/OpenCLHelper.cpp

@@ -1,6 +1,12 @@
-#include <CL/cl.hpp>
-#include <iostream>
-#include <fstream>
+#include <CL/cl.h>    // for CL_DEVICE_NAME, CL_DEVICE_TYPE_ALL, CL_DEVICE_V...
+#include <stdlib.h>   // for exit
+#include <CL/cl.hpp>  // for Device, Platform, Program, Context, Program::So...
+#include <iostream>   // for operator<<, basic_ostream, endl, cout, ostream
+#include <iterator>   // for istreambuf_iterator, operator!=
+#include <string>     // for operator<<, string
+#include <utility>    // for make_pair
+#include <vector>     // for vector
+#include <fstream>    // for ifstream
 
 const char *getErrorString(int error)
 {
@@ -142,4 +148,3 @@ cl::Program BuildProgram(const std::string& fileName, cl::Context context)
 
     return program;
 }
-

### 2019-05-18 Code/GreenOnion/util/OpenCLHelper.hpp

@@ -1,5 +1,6 @@
-#include <CL/cl.hpp>
-#include <vector>
+#include <CL/cl.hpp>  // for Context (ptr only), Device (ptr only), Platform
+#include <string>     // for string
+#include <vector>     // for vector
 
 const char *getErrorString(int error); 
 void opencl_handle_error(int error, std::string name="");

### 2019-05-18 Code/GreenOnion/util/conversion.hpp

@@ -1,4 +1,5 @@
-#include <string>
+#include <sys/types.h>  // for uint
+#include <string>       // for string
 
 // Hex
 std::string unsigned_integer_to_hex(uint integer);

### 2019-05-18 Code/GreenOnion/util/functions.hpp

@@ -1,5 +1,6 @@
-#include <string>
-#include <vector>
+#include <sys/types.h>  // for uint
+#include <string>       // for string
+#include <vector>       // for vector
 
 void pad(std::string &inputString, int minimumLength, char paddingChar);
 void sleep(int milliseconds);

### 2019-05-18 Code/GreenOnion/util/kernel_work.cpp

@@ -1,5 +1,3 @@
-#include <iostream>
-
 #include "kernel_work.hpp"
 
 KernelWork::KernelWork (

### 2019-05-18 Code/GreenOnion/util/kernel_work.hpp

@@ -1,4 +1,5 @@
-#include <iostream>
+#include <sys/types.h>  // for uint
+#include <string>       // for string
 
 #ifndef KernelWork_H
 #define KernelWork_H

### 2019-05-18 Code/GreenOnion/util/pgp.cpp

@@ -1,21 +1,19 @@
-#include <string>
-#include <utility>
-#include <exception>
-#include <tuple>
-#include <bitset>
-#include <math.h>
+#include <openssl/ossl_typ.h>                       // for BIGNUM, BN_CTX, RSA
+#include <openssl/rsa.h>                            // for RSA_generate_key
+#include <openssl/bn.h>                             // for BN_bn2hex, BN_CTX...
+#include <sys/types.h>                              // for uint
+#include <iostream>                                 // for endl, operator<<
+#include <cstdlib>                                  // for system, NULL
+#include <bitset>                                   // for bitset
+#include <string>                                   // for string, allocator
+#include <vector>                                   // for vector
 
-#include <openssl/rsa.h>
-#include <openssl/rand.h>
-#include <openssl/pem.h>
-
-#include "conversion.hpp"
-#include "functions.hpp"
-#include "kernel_work.hpp"
-#include "../crypto/hash_util.hpp"
-
-#include "../cppcodec/cppcodec/base64_rfc4648.hpp"
-#include "../cppcodec/cppcodec/hex_upper.hpp"
+#include "../cppcodec/cppcodec/base64_rfc4648.hpp"  // for base64_rfc4648
+#include "../cppcodec/cppcodec/hex_upper.hpp"       // for hex_upper
+#include "../crypto/hash_util.hpp"                  // for hash_blocks, hex_...
+#include "kernel_work.hpp"                          // for KernelWork
+#include "conversion.hpp"                           // for hex_string_to_mpi
+#include "functions.hpp"                            // for pad, split_string...
 
 using base64 = cppcodec::base64_rfc4648;
 using hex = cppcodec::hex_upper;

### 2019-05-18 Code/GreenOnion/util/pgp.hpp

@@ -1,6 +1,6 @@
-#include <string>
-
-#include "kernel_work.hpp"
+#include <sys/types.h>     // for uint
+#include <string>          // for string
+#include "kernel_work.hpp" // for KernelWork
 
 void generate_rsa_key(
                         std::string &str_n,

### 2019-05-18 Code/GreenOnion/util/timer.cpp

@@ -1,6 +1,4 @@
-#include <iostream>
-#include <chrono>
-
+#include <chrono>  // for duration_cast, operator-, duration, system_clock::...
 #include "timer.hpp"
 
 Timer::Timer() : beg_(clock_::now()) \

### 2019-05-18 Code/GreenOnion/util/timer.hpp

@@ -1,5 +1,5 @@
-#include <iostream>
-#include <chrono>
+#include <chrono>  // for duration, high_resolution_clock, time_point
+#include <ratio>   // for ratio
 
 // https://gist.github.com/gongzhitaao/7062087
 

### 2019-05-18 Plan/pages/work_plan.tex
Changes; - Updated the main README.md for the project - Added some more papers
Changes; - Added archive folder - Added metaphone similar technique to C++ project - Small project re-structuring

@@
 \chapter{Work Plan}
+
+\section{Project title/goal}
+
+{
+    \small
+    "Investigating the feasibility of generating near-collisions for pEp TrustWords and its affect on security"
+
+    \textbf{Points: } \\
+    Use-case for TrustWords:
+    \begin{itemize}
+        \item Users are often deterred by difficulty in key authentication (e.g. PGP web-of-trust).
+    \end{itemize}
+}
+
+\subsection{RFC drafts}
+{
+\small
+\verb|draft-marques-pep-handshake-02|
+\\
+\textit{"Short Trustword Mapping (S-TWM) requires a number of Trustwords that MUST retain \textbf{at least 64 bits} of entropy.
+Thus, S-TWM results into at least \textbf{four Trustwords} to be compared by the user."}
+
+Showing that 4 words is too low in certain cases could be very useful?
+
+\verb|draft-birk-pep-trustwords-00|
+\\
+In another draft document it also states:
+
+\textit{"It is for further study, what minimal number of words (or entropy) should be required."}
+
+This shows there is some sort of research gap.
+}
 
@@
 \label{litReview}
-\textbf{Duration}: ? 
-\\\\
-This stage will involve reviewing the research into producing near collisions with SHA1. This may also extend into producing a review around full collisions of SHA1.
-\par
-SHA1 has been selected due to its vulnerability. Methods for producing collisions have been known for a long time and it seems the algorithm is on its way out of mainstream use.
+
+{
+\small
+\textbf{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}\\
+Paper shows the usability of current schemes. The can be useful to show the need for trustwords and how they would fit in. Maybe even that the security needs improving for word based auth schemes?
+
+\textbf{Can Unicorns Help Users Compare Crypto Key Fingerprints?}\\
+Another paper talking about the usability of user authentication schemes.
+
+\textbf{An Empirical Study of Textual Key-Fingerprint Representations}\\
+Another study on the usability of methods of comparing key-fingerprints. This one highlights on the high usability of words.
+
+}
 
 \section{Formulation specific research questions}
-\textbf{Duration}: ?
-\\\\
-Questions may currently involve:
+What is the purpose of this project and how could it be useful?
 
+\newpage
+\section{Methods for creating similarities in words}
+
+Visual: 
 \begin{itemize}
-    \item What is the probability of producing near-collisions with SHA1?
-    \item What would be the complexity in storage and computation?
-    \item Can such near-collisions be generated e.g. using the university’s high-performance computing facilities? 
+    \item Levenshtein 
 \end{itemize}
 
-Further questions may be added using information gained from already performed research.
+Auditory:
+\begin{itemize}
+    \item Soundex
+    \item Metaphone (successor to Soundex)
+\end{itemize}
 
-\section{Implementing near-collision code}
-\label{code}
-\textbf{Duration}: ?
-\\\\
-This section will involve the actual implementation of code using knowledge gained through the literature review. This may be pre-existing code manipulated to work on the university’s HPC cluster.
+Combined:
+\begin{itemize}
+    \item Metaphone + Levenshtein
+\end{itemize}
 
-\section{Determining metrics for measuring experiments}
-
-Ways to measure the progress of a project
-
-\section{Experimentation stage}
-
-\textbf{Duration}: ?
-\\\\
-This stage will involve running experiments to gain complexity data. This may involve working on further research and validating results.
-
-\section{Thesis/Paper writing}
-
-\textbf{Duration}: ?
-\\\\
-This will involve the creation of a \textasciitilde70 page dissertation alongside a condensed paper for submission to a journal
+\section{Experimentation}
+What do we want to look at?

### 2019-05-18 Code/GreenOnion/build.sh

@@ -6,8 +6,7 @@ g++ hash.cpp \
     -lOpenCL \
     -lcrypto \
     -lssl \
-    -o \
-    GreenOnion.out \
+    -o GreenOnion.out \
 
 rc=$?; 
 if [[ $rc != 0 ]]; 

### 2019-05-18 Code/TrustWords/SimilarWords/build.sh

@@ -1,0 +1,1 @@
+g++ similar_words.cpp ./modes/*.cpp -o SimilarWords.out

### 2019-05-18 Code/TrustWords/SimilarWords/modes/double_metaphone.cpp

@@ -1,0 +1,1105 @@
+#include <vector>
+#include <string>
+#include <string.h>
+#include <stdio.h>
+#include <ctype.h>
+#include <stdlib.h>
+#include <string.h>
+#include <stdarg.h>
+#include <assert.h>
+#include "double_metaphone.hpp"
+
+const unsigned int max_length = 32;
+
+void MakeUpper(std::string &s)
+{
+  for (unsigned int i = 0; i < s.length(); i++)
+  {
+    s[i] = toupper(s[i]);
+  }
+}
+
+int IsVowel(std::string &s, unsigned int pos)
+{
+  char c;
+
+  if ((pos < 0) || (pos >= s.length()))
+    return 0;
+
+  c = s[pos];
+  if ((c == 'A') || (c == 'E') || (c == 'I') || (c == 'O') ||
+      (c == 'U') || (c == 'Y'))
+  {
+    return 1;
+  }
+
+  return 0;
+}
+
+int SlavoGermanic(std::string &s)
+{
+  if ((char *)strstr(s.c_str(), "W"))
+    return 1;
+  else if ((char *)strstr(s.c_str(), "K"))
+    return 1;
+  else if ((char *)strstr(s.c_str(), "CZ"))
+    return 1;
+  else if ((char *)strstr(s.c_str(), "WITZ"))
+    return 1;
+  else
+    return 0;
+}
+
+char GetAt(std::string &s, unsigned int pos)
+{
+  if ((pos < 0) || (pos >= s.length()))
+  {
+    return '\0';
+  }
+
+  return s[pos];
+}
+
+void SetAt(std::string &s, unsigned int pos, char c)
+{
+  if ((pos < 0) || (pos >= s.length()))
+  {
+    return;
+  }
+
+  s[pos] = c;
+}
+
+/*
+  Caveats: the START value is 0 based
+*/
+int StringAt(std::string &s, unsigned int start, unsigned int length, ...)
+{
+  char *test;
+  const char *pos;
+  va_list ap;
+
+  if ((start < 0) || (start >= s.length()))
+  {
+    return 0;
+  }
+
+  pos = (s.c_str() + start);
+  va_start(ap, length);
+
+  do
+  {
+    test = va_arg(ap, char *);
+    if (*test && (strncmp(pos, test, length) == 0))
+    {
+      return 1;
+    }
+  } while (strcmp(test, ""));
+
+  va_end(ap);
+
+  return 0;
+}
+
[…]

### 2019-05-18 Code/TrustWords/SimilarWords/modes/double_metaphone.hpp

@@ -1,0 +1,18 @@
+#include <string>
+#include <vector>
+
+#ifndef DOUBLE_METAPHONE__H
+#define DOUBLE_METAPHONE__H
+
+void MakeUpper(std::string &s);
+int IsVowel(std::string &s, unsigned int pos);
+int SlavoGermanic(std::string &s);
+char GetAt(std::string &s, unsigned int pos);
+void SetAt(std::string &s, unsigned int pos, char c);
+int StringAt(std::string &s, unsigned int start, unsigned int length, ...);
+
+std::string DoubleMetaphone(const std::string &str);
+
+bool metaphone_similar(std::string word1, std::string word2);
+
+#endif /* DOUBLE_METAPHONE__H */

### 2019-05-18 Code/TrustWords/SimilarWords/modes/soundex.cpp

@@ -63,3 +63,9 @@ string soundex(const string &s)
 
     return result;
 }
+
+bool soundex_similar(std::string word1_soundex, std::string word2)
+{
+    std::string word2_soundex = soundex(word2);
+    return  word1_soundex == word2_soundex;
+}

### 2019-05-18 Code/TrustWords/SimilarWords/similar_words.cpp

@@ -5,23 +5,25 @@
 #include <sstream>
 #include <fstream>
 
-#include "soundex.cpp"
-
-int DIFFERENCE_TOLERANCE = 1;
+#include "./modes/soundex.hpp"
+#include "./modes/levenshtien.hpp"
+#include "./modes/double_metaphone.hpp"
 
 std::string inputFileName = "";
 std::string outputFileName = "";
 
 static bool LEV_DISTANCE = false;
 static bool SOUNDEX = false;
+static bool METAPHONE = false;
 
 std::string SOUNDEX_CLI_TAG = "-s";
 std::string LEV_CLI_TAG = "-l";
+std::string METAPHONE_CLI_TAG = "-m";
 
 /*
     Saves the similar words to a specified file
 */
-void save_similar_words_to_file(ofstream &outFile, std::vector<std::string> sim_words)
+void save__CSV(ofstream &outFile, std::vector<std::string> sim_words)
 {
     for (std::string word : sim_words)
     {
@@ -51,46 +53,6 @@ std::vector<std::string> load_CSV(std::string filePath)
 }
 
 /*
-    Calculates the levistien distance of two words
-*/
-int lev_distance(std::string word1, std::string word2)
-{
-    int diff = 0;
-
-    int len_diff = word1.length() - word2.length();
-    len_diff = std::abs(len_diff);
-
-    //Deals with different length strings
-    int min_len = 0;
-    std::string min_word, max_word;
-    if (word1.length() > word2.length())
-    {
-        min_len = word2.length();
-        min_word = word1;
-        max_word = word2;
-    }
-    else
-    {
-        min_len = word1.length();
-        min_word = word2;
-        max_word = word1;
-    }
-        
-    for (size_t i = 0; i < min_len; i++)
-    {
-        if (min_word[i] != max_word[i])
-        {
-            diff += 1;
-        }
-    }
-
-    // Adds on the remaining letters
-    diff += len_diff;
-    return diff;
-        
-}
-
-/*
     Compares each word using it's levistien distance
 */
 void find_similar_words(std::vector<std::string> words)
@@ -103,15 +65,21 @@ void find_similar_words(std::vector<std::string> words)
     std::vector<std::string> sim_words;
     std::ofstream outFile (outputFileName);
 
+
     int loop = 0;
     for (std::string word_y : words)
     {
-        // Recreates the vector for this word_y
+        // Refreshes the vector for each word_y
         sim_words.clear();
[…]

### 2019-05-18 Code/GreenOnion/build.sh
Changes; Added makefile for C++ projects

@@ -1,17 +1,0 @@
-g++ hash.cpp \
-    ./crypto/*.cpp \
-    ./util/*.cpp \
-    ./bloom/*.cpp \
-    -pthread \
-    -lOpenCL \
-    -lcrypto \
-    -lssl \
-    -o GreenOnion.out \
-
-rc=$?; 
-if [[ $rc != 0 ]]; 
-then 
-    echo "[*] Error in complilation!"
-    exit $rc;
-fi
-./GreenOnion.out

### 2019-05-18 Code/TrustWords/SimilarWords/build.sh

@@ -1,1 +1,0 @@
-g++ similar_words.cpp ./modes/*.cpp -o SimilarWords.out

### 2019-05-19 Code/GreenOnion/bloom/BloomFilter.cpp
Changes; - Some refactoring - Added pretty colours to the printing - Fixed some issues flagged by gcc - OpenCL script no recives number of bloom filter hashes as a parameter

@@ -27,7 +27,7 @@ long calculate_bloom_size(long num_of_elements)
 {
     //TODO : this can be altered
     // Currently: 1 in a trillion
-    double probability = 1e-6;
+    double probability = 1e-20;
 
     auto top = abs((num_of_elements * log(probability)));
     auto bottom = (log(2) * log(2));

### 2019-05-19 Code/GreenOnion/crypto/hash_util.cpp

@@ -91,7 +91,7 @@ void hash_blocks(std::vector<std::string> hex_blocks, uint32_t* digest, int num_
     digest[3] = 0x10325476;
     digest[4] = 0xC3D2E1F0;
     // Full hash
-    for(size_t i = 0; i < num_of_blocks; ++i)
+    for(int i = 0; i < num_of_blocks; ++i)
     {
         uint32_t W[16];
         hex_block_to_words(W, hex_blocks[i]);

### 2019-05-19 Code/GreenOnion/hash.cpp

@@ -1,66 +1,73 @@
-#include <CL/cl.hpp>              // for Buffer, Kernel, CommandQueue, Context
-#include <CL/cl.h>                // for CL_MEM_COPY_HOST_PTR, CL_MEM_READ_ONLY
+#include <CL/cl.hpp>                    // for Buffer, Kernel, CommandQueue, Context
+#include <CL/cl.h>                      // for CL_MEM_COPY_HOST_PTR, CL_MEM_READ_ONLY
 
-#include <openssl/sha.h>          // for SHA1
-#include <sys/types.h>            // for uint
-#include <string.h>               // for strlen
-#include <iostream>               // for operator<<, basic_ostream, cout
-#include <stdio.h>                // for printf
-#include <fstream>                // for ifstream
-#include <csignal>                // for signal, SIGINT
-#include <cstdlib>                // for exit, size_t
-#include <chrono>                 // for milliseconds
-#include <string>                 // for string, getline, operator<<, to_string
-#include <thread>                 // for thread, sleep_for
-#include <vector>                 // for vector
-#include <ctime>                  // for time
-#include <mutex>                  // for mutex, lock_guard
-#include <queue>                  // for queue
-#include <map>                    // for map
+#include <openssl/sha.h>                // for SHA1
+#include <sys/types.h>                  // for uint
+#include <string.h>                     // for strlen
+#include <iostream>                     // for operator<<, basic_ostream, cout
+#include <stdio.h>                      // for printf
+#include <fstream>                      // for ifstream
+#include <csignal>                      // for signal, SIGINT
+#include <cstdlib>                      // for exit, size_t
+#include <chrono>                       // for milliseconds
+#include <string>                       // for string, getline, operator<<, to_string
+#include <thread>                       // for thread, sleep_for
+#include <vector>                       // for vector
+#include <ctime>                        // for time
+#include <mutex>                        // for mutex, lock_guard
+#include <queue>                        // for queue
+#include <map>                          // for map
 
[…]

### 2019-05-19 Code/GreenOnion/util/OpenCLHelper.cpp

@@ -1,12 +1,14 @@
-#include <CL/cl.h>    // for CL_DEVICE_NAME, CL_DEVICE_TYPE_ALL, CL_DEVICE_V...
-#include <stdlib.h>   // for exit
-#include <CL/cl.hpp>  // for Device, Platform, Program, Context, Program::So...
-#include <iostream>   // for operator<<, basic_ostream, endl, cout, ostream
-#include <iterator>   // for istreambuf_iterator, operator!=
-#include <string>     // for operator<<, string
-#include <utility>    // for make_pair
-#include <vector>     // for vector
-#include <fstream>    // for ifstream
+#include <CL/cl.h>              // for CL_DEVICE_NAME, CL_DEVICE_TYPE_ALL, CL_DEVICE_V...
+#include <stdlib.h>             // for exit
+#include <CL/cl.hpp>            // for Device, Platform, Program, Context, Program::So...
+#include <iostream>             // for operator<<, basic_ostream, endl, cout, ostream
+#include <iterator>             // for istreambuf_iterator, operator!=
+#include <string>               // for operator<<, string
+#include <utility>              // for make_pair
+#include <vector>               // for vector
+#include <fstream>              // for ifstream
+
+#include "terminal_colors.hpp"  // for INFO, WARNING, OUTPUT
 
 const char *getErrorString(int error)
 {
@@ -87,7 +89,7 @@ const char *getErrorString(int error)
 
 void opencl_handle_error(int error, std::string name="")
 {
-    std::cout << "[!] " << getErrorString(error) << ": " << name << std::endl;
+    std::cout << WARNING << " " << getErrorString(error) << ": " << name << std::endl;
     exit(error);
 }
 
@@ -98,7 +100,7 @@ std::vector<cl::Device> GetAllDevices(cl::Platform platform, bool printInfo)
 
     if (devices.size() == 0)
     {
-        std::cout << "[!] No avaliable devices!" << std::endl;
+        std::cout << WARNING << " No avaliable devices!" << std::endl;
         exit(0);
     }
 
@@ -107,8 +109,8 @@ std::vector<cl::Device> GetAllDevices(cl::Platform platform, bool printInfo)
 
     if (printInfo)
     {
-        std::cout << "[!] Device:  " << device.getInfo<CL_DEVICE_NAME>() << std::endl;
-        std::cout << "[!] Version: " << device.getInfo<CL_DEVICE_VERSION>() << std::endl;
[…]

### 2019-05-19 Code/GreenOnion/util/conversion.cpp

@@ -139,7 +139,7 @@ std::string hex_string_to_mpi(std::string hexString)
 std::string sha_digest_to_string(uint *digest, int len)
 {
     std::string result;
-    for (size_t i = 0; i < len; i++)
+    for (int i = 0; i < len; i++)
     {
         result += unsigned_integer_to_hex(digest[i]);
     }

### 2019-05-19 Code/GreenOnion/util/functions.cpp

@@ -17,7 +17,7 @@ using hex = cppcodec::hex_upper;
 /*
     Pads a string to a certain length
 */
-void pad(std::string &inputString, int minimumLength, char paddingChar)
+void pad(std::string &inputString, size_t minimumLength, char paddingChar)
 {
     while (inputString.length() < minimumLength)
     {

### 2019-05-19 Code/GreenOnion/util/functions.hpp

@@ -2,7 +2,7 @@
 #include <string>       // for string
 #include <vector>       // for vector
 
-void pad(std::string &inputString, int minimumLength, char paddingChar);
+void pad(std::string &inputString, size_t minimumLength, char paddingChar);
 void sleep(int milliseconds);
 void split(std::vector<std::string> &result, std::string str, char delim);
 std::string key_from_exponent_and_base_packet(std::string basePacket, std::string exponent);

### 2019-05-19 Code/GreenOnion/util/terminal_colors.hpp

@@ -1,0 +1,10 @@
+#include <string>
+
+#ifndef COLOUR_H
+#define COLOUR_H
+
+static std::string INFO    = "\033[1;32m[+]\033[0m";
+static std::string WARNING = "\033[1;31m[!]\033[0m";
+static std::string OUTPUT  = "\033[1;33m[*]\033[0m";
+
+#endif

### 2019-05-19 Code/Misc/fingerprint.py

@@ -1,39 +1,0 @@
-import base64
-from Crypto.Hash import SHA1
-import sys
-import re
-
-if len(sys.argv) != 2:
-    print("[!] Usage: python signature.py <KEY_FILE>")
-    exit()
-
-path = sys.argv[1]
-
-key = None
-with open(path, "r") as file:
-    key = file.read()
-
-public_key_parts = key.split("\n")
-middle = "".join(public_key_parts[2:-3])
-middleBytes = base64.b64decode(middle)
-middleHex = middleBytes.hex()
-
-# Format from RFC 4880
-public_key_len = int(middleHex[2:6], 16)
-
-# Grabs the header and all of the key information
-pgp_key_information = middleHex[0:(public_key_len * 2) + 6]
-
-print(pgp_key_information)
-
-pgp_key_information_bytes = bytes.fromhex(pgp_key_information)
-
-sha1 = SHA1.new()
-sha1.update(pgp_key_information_bytes)
-
-fingerprint = sha1.hexdigest().upper()
-
-fingerprint_formatted = " ".join(re.findall(r"....", fingerprint))
-
-print("KEY FINGERPRINT:\n\n\t", fingerprint_formatted)
-print()

### 2019-05-19 Papers/Notes_TeX/pages/paper_notes.tex
Changes; - Restructuring of the archive folder - Added TeX version of paper notes - Added new papers for relevancy review - Included a script to generate fabricated target_key lists for benchmarking

\textbf{TODO:} Need to find papers on study of words are a comparative measure.

\section{Can Unicorns Help Users Compare Crypto Key Fingerprints}

This paper tested 8 different fingerprint representations with 661 different participants. All of these representations are testing using compare-and-confirm (basic comparison process for fingerprints) and compare-and-select (select from a list)

\begin{itemize}
    \item Hexadecimal
    \item TODO
\end{itemize}

The paper also emphasises the attention that has been taken to realism in the experimentation stage.

Talks about long term usability issues with public-key crypto and states fingerprints are a main source of the problem. ([28])

There seems to be mixed findings with compare-and-select and compare-and-confirm ([14, 17])

\subsection{Findings}

\begin{itemize}
    \item Graphical representations have mixed success rates (with quick comparison times)
    \item Recommendations not to use \textbf{compare-and-select}
\end{itemize}

### 2019-05-19 Plan_TeX/pages/work_plan.tex
Changes; - Restructuring of the archive folder - Added TeX version of paper notes - Added new papers for relevancy review - Included a script to generate fabricated target_key lists for benchmarking

--- 2019-05-18 Plan/pages/work_plan.tex
@@
-\chapter{Work Plan}
+\section{Work Plan}
 
-\section{Project title/goal}
+\subsection{Project title/goal}
 
-{
-    \small
 "Investigating the feasibility of generating near-collisions for pEp TrustWords and its affect on security"
 
-    \textbf{Points: } \\
-    Use-case for TrustWords:
 \begin{itemize}
-        \item Users are often deterred by difficulty in key authentication (e.g. PGP web-of-trust).
+    \item Use-case for TrustWords: Users are often deterred by difficulty in key authentication (e.g. PGP web-of-trust).
 \end{itemize}
-}
 
 \subsection{RFC drafts}
-{
-\small
-\verb|draft-marques-pep-handshake-02|
-\\
-\textit{"Short Trustword Mapping (S-TWM) requires a number of Trustwords that MUST retain \textbf{at least 64 bits} of entropy.
-Thus, S-TWM results into at least \textbf{four Trustwords} to be compared by the user."}
+\subsubsection{draft-marques-pep-handshake-02}
+``Short Trustword Mapping (S-TWM) requires a number of Trustwords that MUST retain \textbf{at least 64 bits} of entropy.
+Thus, S-TWM results into at least \textbf{four Trustwords} to be compared by the user."
 
@@
 
-\verb|draft-birk-pep-trustwords-00|
-\\
+\subsubsection{draft-birk-pep-trustwords-00}
 In another draft document it also states:
 
-\textit{"It is for further study, what minimal number of words (or entropy) should be required."}
+``It is for further study, what minimal number of words (or entropy) should be required."
 
 This shows there is some sort of research gap.
-}
 
@@
 
-{
-\small
 \textbf{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}\\
@@
 
-}
-
 \section{Formulation specific research questions}
@@
 
-\newpage
 \section{Methods for creating similarities in words}

### 2019-05-19 Archive/Code/FPGA/hash.c

@@ -1,0 +1,23 @@
+#include "sha1.c"
+
+int main()
+{
+     // Test message
+     char *buff = "hello";
+
+     // Needs to be 20 long
+     char *results[20];
+
+     SHA1Hash(&results, buff);
+
+     printHash(&results);
+}
+
+void printHash(unsigned char *buffer)
+{
+     for (int n = 0; n < 20; n++)
+     {
+          printf("%02x", buffer[n]);
+     }
+     putchar('\n');
+}

### 2019-05-19 Archive/Code/FPGA/sha1.c

@@ -1,0 +1,230 @@
+/*
+SHA-1 in C
+By Steve Reid <steve@edmweb.com>
+*/
+
+#include <stdio.h>
+#include <string.h>
+#include <stdint.h> /* for uint32_t */
+#include <time.h>
+
+#define rol(value, bits) (((value) << (bits)) | ((value) >> (32 - (bits))))
+
+/* blk0() and blk() perform the initial expand. */
+/* I got the idea of expanding during the round function from SSLeay */
+#if BYTE_ORDER == LITTLE_ENDIAN
+#define blk0(i) (block->l[i] = (rol(block->l[i],24)&0xFF00FF00) \
+    |(rol(block->l[i],8)&0x00FF00FF))
+#elif BYTE_ORDER == BIG_ENDIAN
+#define blk0(i) block->l[i]
+#else
+#error "Endianness not defined!"
+#endif
+#define blk(i) (block->l[i&15] = rol(block->l[(i+13)&15]^block->l[(i+8)&15] \
+    ^block->l[(i+2)&15]^block->l[i&15],1))
+
+/* (R0+R1), R2, R3, R4 are the different operations used in SHA1 */
+#define R0(v,w,x,y,z,i) z+=((w&(x^y))^y)+blk0(i)+0x5A827999+rol(v,5);w=rol(w,30);
+#define R1(v,w,x,y,z,i) z+=((w&(x^y))^y)+blk(i)+0x5A827999+rol(v,5);w=rol(w,30);
+#define R2(v,w,x,y,z,i) z+=(w^x^y)+blk(i)+0x6ED9EBA1+rol(v,5);w=rol(w,30);
+#define R3(v,w,x,y,z,i) z+=(((w|x)&y)|(w&x))+blk(i)+0x8F1BBCDC+rol(v,5);w=rol(w,30);
+#define R4(v,w,x,y,z,i) z+=(w^x^y)+blk(i)+0xCA62C1D6+rol(v,5);w=rol(w,30);
+
+typedef struct
+{
+    uint32_t state[5];
+    uint32_t count[2];
+    unsigned char buffer[64];
+} SHA1_CTX;
+
+/* SHA1Init - Initialize new context */
+void SHA1Init(SHA1_CTX * context)
+{
+    /* SHA1 initialization constants */
+    context->state[0] = 0x67452301;
+    context->state[1] = 0xEFCDAB89;
+    context->state[2] = 0x98BADCFE;
[…]

### 2019-05-19 Archive/Code/SHA1/SHA1.py

@@ -1,0 +1,148 @@
+import sys ; sys.path += ['.', '../..']
+from bitstring import BitArray
+import base64
+import re
+
+class SHA1():
+    
+    @staticmethod
+    def createDigest(message, ml=None, h0=0x67452301, h1=0xEFCDAB89, h2=0x98BADCFE, h3=0x10325476, h4=0xC3D2E1F0, padding=True):
+        """
+        Creates a message digests for a bytes message.
+        Output is in Base64
+        """
+
+        # Converts to binary
+        messageBinary = BitArray(bytes=message).bin
+
+        if ml is None:
+            ml = len(messageBinary)
+
+        # Adds padding to the value
+        if padding: 
+            messageBinary = SHA1.addPadding(messageBinary, ml)
+
+        # Creates 512 bit chunks
+        messageChunks = SHA1.splitStringIntoChunks(messageBinary, size=512)
+
+        for chunk in messageChunks:
+
+            # Split chunck into 32bit words
+            # Should expect 16 chunks
+            words = SHA1.splitStringIntoChunks(chunk, size=32)
+            words += [0] * 64
+
+            # Extends sixteen 32 bit values into eighty
+            for i in range(16, 80):
+
+                xor = int(words[i-3], 2) ^ int(words[i-8], 2) ^ \
+                      int(words[i-14], 2) ^ int(words[i-16], 2)
+
+                xor = SHA1.left_rotate(xor, shift=1)
+                words[i] = format(xor, "032b")
+
+           # Initialize hash value for this chunk:
+            a = h0
+            b = h1
+            c = h2
+            d = h3
+            e = h4
+
+            # Main loop
+            for i in range(0, 80):
+                if 0 <= i <= 19:
+                    f = d ^ (b & (c ^ d))  
+                    k = 0x5A827999
+
+                elif 20 <= i <= 39:
+                    f = b ^ c ^ d
+                    k = 0x6ED9EBA1
+                    
+                elif 40 <= i <= 59:
+                    f = (b & c) | (d & (b | c))
+                    k = 0x8F1BBCDC
+
+                else:
+                    f = b ^ c ^ d
+                    k = 0xCA62C1D6
+
+                temp = SHA1.left_rotate(a, shift=5) + f + e + k + int(words[i], 2) & 0xffffffff
+                e = d
+                d = c
+                c = SHA1.left_rotate(b, shift=30)
+                b = a
[…]

### 2019-05-19 Code/GreenOnion/create_target_keys.py

@@ -1,0 +1,26 @@
+import sys
+
+"""
+A script to create a dud target_keys file.
+This is used to calculate speed required
+"""
+
+def usage():
+    print("[!] python create_target_keys.py <NUMBER_OF_KEYS>")
+    exit()
+
+if len(sys.argv) != 2:
+    usage()
+
+number_of_keys = int(sys.argv[1])
+
+# Starts off at 0 and just increments up
+data = 0
+
+with open("target_keys.txt", "w") as file:
+    for x in range(number_of_keys):
+        data_str = str(hex(data)[2:]).zfill(16)
+        file.write(data_str + "\n")
+        data += 1
+
+print("[+] Save complete!")

### 2019-05-19 Code/GreenOnion/hash.cpp

@@ -41,6 +41,8 @@
 //       number to create a predicted time
 //
 // TODO: Saving found keys to file
+//
+// TODO: Benchmark mode
 //########################################################//
 static std::queue<KernelWork> kernel_work;
 static std::mutex kernel_work_lock;
@@ -54,8 +56,8 @@ int KEY_LENGTH = 2048;
 int EXPONENT = 0x01000001;
 
 // Bloom filter params
-uint BLOOM_NUMBER_OF_HASHES = 2;
-long BLOOM_SIZE_STATIC = 17000000;  //Set to 0 for dynamic size
+uint BLOOM_NUMBER_OF_HASHES = 5;
+long BLOOM_SIZE_STATIC = 0;  //Set to 0 for dynamic size
 
 // Threading params
 bool running = true;

### 2019-05-19 Code/GreenOnion/hash.cpp
Changes; - Small code changes - Updated TODOs

@@ -43,6 +43,9 @@
 // TODO: Saving found keys to file
 //
 // TODO: Benchmark mode
+//
+// TODO: Program is having an error where when the first FP
+//       is introduced the number starts rapidly climbing??
 //########################################################//
 static std::queue<KernelWork> kernel_work;
 static std::mutex kernel_work_lock;
@@ -56,8 +59,8 @@ int KEY_LENGTH = 2048;
 int EXPONENT = 0x01000001;
 
 // Bloom filter params
-uint BLOOM_NUMBER_OF_HASHES = 5;
-long BLOOM_SIZE_STATIC = 0;  //Set to 0 for dynamic size
+uint BLOOM_NUMBER_OF_HASHES = 4;
+long BLOOM_SIZE_STATIC = 500000;  //Set to 0 for dynamic size
 
 // Threading params
 bool running = true;
@@ -162,35 +165,6 @@ uint get_and_check_target_key_length(std::string filePath)
     return number_of_lines;
 }
 
-/*
-    TODO
-*/
-bool check_for_real_key(uint* outResult, KernelWork work, std::map<std::string, bool> target_keys_hash_table)
-{
-    //TODO: Encapsulate all here into a single method
-
-    std::string exponent = integer_to_hex(outResult[1]);
-    pad(exponent, 8, '0');
-
-    //Recreates the key
-    auto pgp_key = key_from_exponent_and_base_packet(work.m_fingerprintPacket, exponent);
-    
-    //Obtains the hash of the key
-    uint digest[5];
-    hash_string(pgp_key, digest);
-
-    // Only takes the 2 left most 32-bit blocks
-    auto hex_digest = sha_digest_to_string(digest, 2);
-
-    // If true an actual key is found
-    if(target_keys_hash_table.count(hex_digest))
-    {
-        print_found_key(work, exponent);
-        return true;
-    }
-
-    return false;
-}
 
 /*
     Communicates with OpenCL and proccess results
@@ -306,17 +280,31 @@ void compute()
 
             //Looks for the positive result value
             if (outResult[0] == (uint)0x12345678)
-            {   
-                if (check_for_real_key(outResult, work, target_keys_hash_table))
+            {
+                std::string exponent = integer_to_hex(outResult[1]);
+                pad(exponent, 8, '0');
+
+                //Recreates the key
+                auto pgp_key = key_from_exponent_and_base_packet(work.m_fingerprintPacket, exponent);
+                
+                //Obtains the hash of the key
[…]

### 2019-05-19 Code/TrustWords/create_perms.py

@@ -15,13 +15,13 @@ import base64
 file_path = "."
 
 # The fingerprint of the target
-# UNCONTROLLED_FINGERPRINT    = "7E6C 4BF0 5CF3 F379"
-UNCONTROLLED_FINGERPRINT    = "7E6C 4BF0 5CF3 F379 1191"
+UNCONTROLLED_FINGERPRINT    = "7E6C 4BF0 5CF3 F379"
+# UNCONTROLLED_FINGERPRINT    = "7E6C 4BF0 5CF3 F379 1191"
 
 
 # The fingerprint we can change via MITM
-# CONTROLLABLE_FINGERPRINT    = "2F88 CE86 1A1B 19D3"
-CONTROLLABLE_FINGERPRINT    = "2F88 CE86 1A1B 19D3 5F80"
+CONTROLLABLE_FINGERPRINT    = "2F88 CE86 1A1B 19D3"
+# CONTROLLABLE_FINGERPRINT    = "2F88 CE86 1A1B 19D3 5F80"
 
 
 # Stops the program from generating permutations that fill the RAM

### 2019-05-19 Code/GreenOnion/bloom/BloomFilter.cpp
Changes; - Added calc for the number of hashes need for the bloom filter

@@ -1,6 +1,10 @@
-#include <math.h>         // for log, abs
-#include "MurmurHash3.h"  // for MurmurHash3_x86_32
+#include <math.h>           // for log, abs, round
+#include "MurmurHash3.h"    // for MurmurHash3_x86_32
 #include "BloomFilter.hpp"
+
+// The odds of occurrence that a match will appear
+// static double p = 5.88e-10;
+static double p = 1e-5;
 
 BloomFilter::BloomFilter(unsigned long size, short numHashes): m_numHashes(numHashes) 
 {
@@ -23,16 +27,14 @@ void BloomFilter::add(unsigned long value)
     }
 }
 
-long calculate_bloom_size(long num_of_elements)
+long calculate_bloom_size(long n)
 {
-    //TODO : this can be altered
-    // Currently: 1 in a trillion
-    double probability = 1e-20;
+    return ceil((n * log(p)) / log(1 / pow(2, log(2))));
+}
 
-    auto top = abs((num_of_elements * log(probability)));
-    auto bottom = (log(2) * log(2));
-
-    auto m =  (long)(top / bottom);
-
-    return m;
+uint calculate_number_of_hashes(long n, long m)
+{
+    // Division by 2 dues to the split nature of
+    // the way the hash is added to the bloom filter
+    return round((m / n) * log(2)) / 2;  
 }

### 2019-05-19 Code/GreenOnion/bloom/BloomFilter.hpp

@@ -19,3 +19,4 @@ public:
 #endif
 
 long calculate_bloom_size(long num_of_elements);
+uint calculate_number_of_hashes(long n, long m);

### 2019-05-19 Code/GreenOnion/hash.cpp

@@ -59,8 +59,8 @@ int KEY_LENGTH = 2048;
 int EXPONENT = 0x01000001;
 
 // Bloom filter params
-uint BLOOM_NUMBER_OF_HASHES = 4;
-long BLOOM_SIZE_STATIC = 500000;  //Set to 0 for dynamic size
+uint BLOOM_NUMBER_OF_HASHES_STATIC  = 0;  //Set to 0 for dynamic size
+long BLOOM_SIZE_STATIC              = 0;  //Set to 0 for dynamic size
 
 // Threading params
 bool running = true;
@@ -188,9 +188,25 @@ void compute()
     // ### FILTER INIT ###
     auto number_of_target_keys = get_and_check_target_key_length(target_keys_file_path);
 
-    long BLOOM_SIZE;
-    if (BLOOM_SIZE_STATIC != 0) BLOOM_SIZE = BLOOM_SIZE_STATIC;
-    else                        BLOOM_SIZE = calculate_bloom_size(number_of_target_keys);
+    long BLOOM_SIZE = 0;
+    if (BLOOM_SIZE_STATIC != 0) 
+    {
+        BLOOM_SIZE = BLOOM_SIZE_STATIC;
+    }
+    else
+    {
+        BLOOM_SIZE = calculate_bloom_size(number_of_target_keys);
+    }
+
+    uint BLOOM_NUMBER_OF_HASHES = 0;
+    if (BLOOM_NUMBER_OF_HASHES_STATIC != 0) 
+    {
+        BLOOM_NUMBER_OF_HASHES = BLOOM_NUMBER_OF_HASHES_STATIC;
+    }
+    else 
+    {
+        BLOOM_NUMBER_OF_HASHES = calculate_number_of_hashes(number_of_target_keys, BLOOM_SIZE);
+    }
 
     std::cout << INFO << " Bloom filter size: " << BLOOM_SIZE << std::endl;
     std::cout << INFO << " Number of bloom filter hash cycles: " << BLOOM_NUMBER_OF_HASHES << std::endl;
@@ -302,6 +318,7 @@ void compute()
                 }
                 else
                 {
+                    //Resets
                     false_positives++;
                     outResult[0] = 0xffffffff;
                 }

### 2019-05-19 Code/GreenOnion/bloom/BloomFilter.cpp
Changes; - Added run-time to the output - Included calculation for k

@@ -3,8 +3,8 @@
 #include "BloomFilter.hpp"
 
 // The odds of occurrence that a match will appear
-// static double p = 5.88e-10;
-static double p = 1e-5;
+// this is to keep to to about one FP per 100 loops
+static double p = 1e-10;
 
 BloomFilter::BloomFilter(unsigned long size, short numHashes): m_numHashes(numHashes) 
 {
@@ -36,5 +36,5 @@ uint calculate_number_of_hashes(long n, long m)
 {
     // Division by 2 dues to the split nature of
     // the way the hash is added to the bloom filter
-    return round((m / n) * log(2)) / 2;  
+    return round((m / n) * log(2));  
 }

### 2019-05-19 Code/GreenOnion/hash.cpp

@@ -9,10 +9,12 @@
 #include <fstream>                      // for ifstream
 #include <csignal>                      // for signal, SIGINT
 #include <cstdlib>                      // for exit, size_t
+#include <iomanip>                      // for setprecision
 #include <chrono>                       // for milliseconds
 #include <string>                       // for string, getline, operator<<, to_string
 #include <thread>                       // for thread, sleep_for
 #include <vector>                       // for vector
+#include <math.h>                       // for pow, round
 #include <ctime>                        // for time
 #include <mutex>                        // for mutex, lock_guard
 #include <queue>                        // for queue
@@ -31,21 +33,21 @@
 //########################################################//
 //                     ISSUES                             //
 //########################################################//
+// BUG: Program is having an error where when the first FP
+//       is introduced the number starts rapidly climbing??
+//
+//########################################################//
 // TODO: Dynamically sized bloom filter functionality
 //
 // TODO: pass in 'target_keys.txt' as a parameter to the
 //       script
 //
-// TODO: Create output that includes a dynamic time. This
-//       can use the speed, number of words and target_key
-//       number to create a predicted time
-//
 // TODO: Saving found keys to file
 //
 // TODO: Benchmark mode
 //
-// TODO: Program is having an error where when the first FP
-//       is introduced the number starts rapidly climbing??
+// TODO: Have the script only print when a key is pressed
+//       this is similar to the way HashCat works
 //########################################################//
 static std::queue<KernelWork> kernel_work;
 static std::mutex kernel_work_lock;
@@ -59,16 +61,16 @@ int KEY_LENGTH = 2048;
 int EXPONENT = 0x01000001;
 
 // Bloom filter params
-uint BLOOM_NUMBER_OF_HASHES_STATIC  = 0;  //Set to 0 for dynamic size
-long BLOOM_SIZE_STATIC              = 0;  //Set to 0 for dynamic size
+uint BLOOM_NUMBER_OF_HASHES_STATIC  = 5;    //Set to 0 for dynamic size
+long BLOOM_SIZE_STATIC              = 0;    //Set to 0 for dynamic size
 
 // Threading params
 bool running = true;
 size_t numberOfThreads = 1;
 std::vector<std::thread> workThreads;
 
[…]

### 2019-05-19 Code/Misc/time_calc.py

@@ -15,8 +15,10 @@ length_in_chars = float(sys.argv[1])
 hashspeed = int(sys.argv[2]) * 1000000
 permutations = float(sys.argv[3])
 
-time_seconds = (2**(4 * length_in_chars)) / hashspeed / permutations
+top = (2**(4 * length_in_chars))
 
+print(top)
+time_seconds = top / hashspeed / permutations
 time_days = time_seconds / 3600 / 24
 
 print(f"[*] It will take:")

### 2019-05-20 Code/TrustWords/create_perms.py
Changes; - Added similar keys - Updated the plan

@@ -342,28 +342,34 @@ def generate_words_for_PGP_keys(key_path_1, key_path_2):
     #     key_data_1 = key1.readlines()
     
     # TEMP
-    key_finger_print_2 = "7E6C 4BF0 5CE3 F379".replace(" ", "")
+    key_finger_print_1 = "7E6C 4BF0 5CE3 F379".replace(" ", "")
 
     key_data_2 = []
     with open(key_path_2) as key2:
         key_data_2 = key2.readlines()
 
-
-    key_base64_1= ""
+    key_base64_2 = ""
 
     # Skips headers and formatting lines
     for l in key_data_2[1:-2]:
-        key_base64_1 += l.strip()
+        key_base64_2 += l.strip()
 
-    key_bytes_1 = base64.b64decode(key_base64_1)
+    # All the bytes from the key
+    bytes_2 = base64.b64decode(key_base64_2)
+
+    # Takes the PGP packey length from the header
+    key_length = int.from_bytes(bytes_2[1:3], byteorder="big")
+
+    # Takes the header and length
+    key_bytes_2 = bytes_2[:key_length + 3]
 
     sha1 = SHA1.new()
-    sha1.update(key_bytes_1)
+    sha1.update(key_bytes_2)
 
-    key_finger_print_1 = sha1.hexdigest()[:16].upper()
+    # Takes the left 64-bit
+    key_finger_print_2 = sha1.hexdigest()[:16].upper()
 
     combined_key = XOR_fingerprints(key_finger_print_1, key_finger_print_2)
-
     finger_print_to_words(combined_key)
 
 def args():

### 2019-05-20 Papers/Notes_TeX/pages/paper_notes.tex
Changes; - Added similar keys - Updated the plan
Changes; - Added more papers - Added more notes on papers

@@
 \textbf{TODO:} Need to find papers on study of words are a comparative measure.
+
+\textbf{OVERVIEW} 
+\begin{itemize}
+    \item Lots of research performed on E2E applications (Telegram, WhatsApp etc)
+    \item Lots of study into overall representations of fingerprints
+\end{itemize}
 
@@
     \item Hexadecimal
-    \item TODO
+    \item Alternating vowel/consonant
+    \item Words
+    \item Numbers
+    \item Sentences
+    \item OpenSSH visual host key
+    \item Vash
+    \item Unicorns
 \end{itemize}
@@
 
+There has been research into OpenSSH fingerprints and how users interact ([19, 24])
+
+Paper chose to target a security level of 160-bits
+
+Papers attack strengths were $2^{40}$, $2^{60}$ and $2^{80}$
+
+Paper states that MTurk users have been shown to be younger and better educated than the general US population ([15])
+
 \subsection{Findings}
@@
     \item Recommendations not to use \textbf{compare-and-select}
+    \item \textbf{No method} really provided enough security for high risk situations, they recommend removing users from the loop by using smart phone cameras etc
 \end{itemize}
+
+\section{An Empirical Study of Textual Key-Fingerprint Representations}
+
+Study involved 1047 participants evaluating 6 different textual representations on MTurk. The study also includes an evaluation into usability.
+
+The study has an attacker power of around 80 of 112 bits.
+
+\begin{itemize}
+    \item X
+\end{itemize}
+
+More mention to decentralised method finding it hard to find adoption such as Web of Trust and Namecoin ([7, 13, 30])
+
+References as system called CONIKS and others ([24, 39, 27]) that aim to provided a directory of keys
+
+States that many systems still rely on fingerprint comparison ([17])
+
+States that the \textbf{hexadecimal} encoding is used in most systems.
+
+States again that fingerprint comparison is seldom done in practice ([17, 37])
+
+Studies have shown that users find it difficult to compare long and "meaningless" strings ([19])
+
+References to other word lists used. PGP Word list [22] and english word list compiled by K.C. Ogden [31]. The Peerio word list is generated from the most common words in english subtitles.
+
+Interesting recommendation into the use of \textit{scrypt} [34] and \textit{Argon 2} [3] can be used to shorten the fingerprint length. These work slowly and a prevent easy computation of pre-images.
+
+When generating partial-collision fixing the bits at the start and end has been shown a best practice ([17, 37])
+
+\subsection{Findings}
+\begin{itemize}
+    \item Overall recommendation is to replace \textbf{hexadecimal} with \textbf{sentence} based encoding
+    \item Findings show that \textbf{hexadecimal} and \textbf{Base32} perform worse than the other alternatives in realistic threat models.
+With over \textbf{10\%} of users failing to detect attacks with these schemes.
+\end{itemize}

### 2019-05-20 Code/GreenOnion/hash.cpp
Changes; - Added functionality to pass a target_keys file to the GreenOnion script - Added some computed similar word lists

@@ -33,14 +33,7 @@
 //########################################################//
 //                     ISSUES                             //
 //########################################################//
-// BUG: Program is having an error where when the first FP
-//       is introduced the number starts rapidly climbing??
-//
-//########################################################//
 // TODO: Dynamically sized bloom filter functionality
-//
-// TODO: pass in 'target_keys.txt' as a parameter to the
-//       script
 //
 // TODO: Saving found keys to file
 //
@@ -78,7 +71,7 @@ size_t MAX_WORK_SIZE = 1000;                //Set to 0 for no cap
 // std::string target_keys_file_path = "/home/main_user/GitHub/Cyber-Security-Individual-Project/Code/GreenOnion/target_keys.txt";
 // std::string kernel_file_path = "/home/main_user/GitHub/Cyber-Security-Individual-Project/Code/GreenOnion/opencl/SHA1.cl";
 
-std::string target_keys_file_path = "./target_keys.txt";
+std::string target_keys_file_path = "";
 std::string kernel_file_path = "./opencl/SHA1.cl";
 
 /*
@@ -161,7 +154,7 @@ uint get_and_check_target_key_length(std::string filePath)
 
     if (number_of_lines == 0)
     {
-        std::cout << WARNING <<" Error: No target keys have been loaded. Please check the target_keys.txt file" << std::endl;
+        std::cout << WARNING <<" Error: No target keys have been loaded. Please check the target_keys file path" << std::endl;
         exit(0);
     }
     std::cout << INFO <<" Number of target keys loaded: " << number_of_lines << std::endl;
@@ -424,8 +417,17 @@ void signalHandler(int signum)
     exit(signum);
 }
 
-int main()
+void usage()
 {
+    std::cout << "./GreenOnion <TARGET_KEYS_FILE_PATH>" << std::endl;
+    exit(0);
+}
+
+int main(int argc, char* argv[])
+{
+    // Argument handling
+    if (argc != 2) usage();
+    target_keys_file_path = argv[1];
 
     signal(SIGINT, signalHandler);  
 

### 2019-05-20 Code/Misc/time_calc.py

@@ -16,8 +16,6 @@ hashspeed = int(sys.argv[2]) * 1000000
 permutations = float(sys.argv[3])
 
 top = (2**(4 * length_in_chars))
-
-print(top)
 time_seconds = top / hashspeed / permutations
 time_days = time_seconds / 3600 / 24
 

### 2019-05-20 Code/GreenOnion/hash.cpp
Changes; - Changes made for CUDA

@@ -91,7 +91,7 @@ void sha1_test()
     // 160 bit digest
     uint openclHash[5];
 
-    cl::Buffer valueBuf(context, CL_MEM_READ_WRITE | CL_MEM_HOST_READ_ONLY, sizeof(openclHash));
+    cl::Buffer valueBuf(context, CL_MEM_READ_WRITE | CL_MEM_ALLOC_HOST_PTR, sizeof(openclHash));
 
     cl::Kernel kernel(program, "shaTest");
     kernel.setArg(0, valueBuf);
@@ -203,7 +203,11 @@ std::string calculate_run_time(long hashRate, long numberOfKeys)
         }
     }
 
-    return std::to_string((uint)time_value) + " " + current_unit;
+    std::stringstream stream;
+
+    stream << std::fixed << std::setprecision(2) << time_value << " " << current_unit;
+
+    return stream.str();
 }
 
 /*
@@ -294,7 +298,7 @@ void compute()
             cl::Buffer buf_numberOfHashes(context, CL_MEM_READ_ONLY | CL_MEM_COPY_HOST_PTR, sizeof(uint), bloom_number_of_hashes, &err);
             if (err != 0) opencl_handle_error(err, "number_of_hashes");
             
-            cl::Buffer buf_out_result(context, CL_MEM_WRITE_ONLY | CL_MEM_HOST_READ_ONLY, resultSize);
+            cl::Buffer buf_out_result(context, CL_MEM_WRITE_ONLY | CL_MEM_ALLOC_HOST_PTR, resultSize);
 
             kernel.setArg(0, buf_finalBlock);
             kernel.setArg(1, buf_currentHash);
@@ -349,7 +353,7 @@ void compute()
                 if(target_keys_hash_table.count(hex_digest))
                 {
                     print_found_key(work, exponent);
-                    // if (END_ON_KEY_FOUND) break;
+                    if (END_ON_KEY_FOUND) break;
                 }
                 else
                 {

### 2019-05-20 Code/GreenOnion/hash.cpp
Removed some debug values

@@ -56,7 +56,7 @@ int EXPONENT = 0x01000001;
 // Bloom filter params
 uint BLOOM_NUMBER_OF_HASHES_STATIC  = 2;    //Set to 0 for dynamic size
 // long BLOOM_SIZE_STATIC              = 1700000;    //Set to 0 for dynamic size
-long BLOOM_SIZE_STATIC              = 0;    //Set to 0 for dynamic size
+long BLOOM_SIZE_STATIC              = 1500000;    //Set to 0 for dynamic size
 
 
 // Threading params
@@ -240,11 +240,6 @@ void compute()
 
     if (BLOOM_NUMBER_OF_HASHES_STATIC != 0)     BLOOM_NUMBER_OF_HASHES = BLOOM_NUMBER_OF_HASHES_STATIC;
     else                                        BLOOM_NUMBER_OF_HASHES = calculate_number_of_hashes(number_of_target_keys, BLOOM_SIZE);
-
-
-    //DEBUG
-    BLOOM_SIZE = 1800000;
-    BLOOM_NUMBER_OF_HASHES = 2;
 
     std::cout << INFO << " Bloom filter size: " << BLOOM_SIZE << std::endl;
     std::cout << INFO << " Number of bloom filter hash cycles: " << BLOOM_NUMBER_OF_HASHES << std::endl;

### 2019-05-21 Papers/Notes_TeX/pages/paper_notes.tex
Changes; - More paper notes addded

@@
 \begin{itemize}
-    \item X
+    \item Alphanumerical
+    \item Numerical
+    \item Words
+    \item Sentences
 \end{itemize}
@@
 With over \textbf{10\%} of users failing to detect attacks with these schemes.
+    \item According to their study, \textbf{words} and \textbf{sentences} we some of the best methods for avoiding attack
+    \item Words has the second highest usability ratings second to only sentences
 \end{itemize}
+
+\section{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}
+
+Paper looks into the positives of secondary channels used to authenticate device pairing. Such as device fingerprint comparison.
+
+"People are the weakest link in the security chain" [26]
+
+Mentions a normal channel as a "Dolev-Yao" channel [5]. This is where an attacker can overhead, delete and modify messages.
+
+\subsection{Findings}
+\begin{itemize}
+    \item Showed for \textbf{usability} methods ranked:
+    \begin{itemize}
+        \item Comparing-confirm
+        \item Typing strings
+        \item Comparing-select
+        \item Barcode
+    \end{itemize}
+
+    \item Showed for \textbf{combined security} and \textbf{usability} methods ranked:
+    \begin{itemize}
+        \item Typing strings
+        \item Barcodes
+        \item Comparing-confirm
+        \item Comparing-select
+    \end{itemize}
+\end{itemize}

### 2019-05-22 Literature_Review/pages/review_content.tex
Changes; - Organised papers into relevant categories using a review matrix - Added some more potentially relevant papers - Start creating the literature review

\section{Research questions}

Overall the research will aim to investigate the strength of pEp's Trustword fingerprint mappings, and the ease in which partial collisions can be obtained for keys and how this will ultimately affect the end user(s).

Key areas that will be looked into:
\begin{itemize}
    \item Is the recommended minimum number of Trustwords enough to provide a basic level of security.
    \item What attributes make a strong general wordlist for fingerprint mapping and does the Trustword implementation exhibit these features.
    \item How easy is it to generate similar keys that attack a targeted key pair?
    \item How can similarity be quantified in terms of words? Does this include pronunciation or visual aspects?
    \item As usability is the main justification for the use of Trustwords are there alternatives that provide the same usability but with more security?
\end{itemize}

\section{Review}

\subsection{Fingerprint representation and comparison}

Current research in ways to represent and validate fingerprints has almost exclusively focused on the usability of such schemes. The following section will discuss available research findings alongside a overall comparison of the research recommendations.

Work by Dechand Sergej, \textit{et al.}\cite{dechand2016empirical} empirically investigated the usability of 4 distinct textual representations evaluated with a experiments involving a total of 1047 participant. The textual representations were: Alphanumeric, Numeric, Words and Sentences. They assessed the number of attacks missed with each scheme alongside results from a questionnaire on the participants preferred scheme and perceived usability.

The paper touches upon issues with decentralised methods of identification such a PGP's Web of Trust and the problems these solutions have with user adoption. These points are made in an attempt to validate the requirement for manual comparison of key based fingerprints. This is a common theme that appears in the majority of the reviewed papers.

Other references made within the paper touch upon the vulnerabilities and usability issues present with the way humans interact with the security systems. Example of these are studies showing humans find it difficult to comprehend long and "meaningless" strings and the lack of actual comparison performed by actual users in live scenario's. These are, however, acknowledged as limitations in the later stages of the paper.

The paper has defined the upper and lower bound costs of the attacker's resources and strength as \$610K to \$16B, with an ability to control 80-bits of the fingerprint. This in comparison to other papers is high and is almost encroaching into the realm of a highly sophisticated attacker. Therefore, the lack of consideration for the lower-end of the attack resource spectrum can be considered a limitation of this study.

Overall, findings from the paper state that conventional encodings such as Hexadecimal and Base32 perform worse than all other alternatives in a realistic threat model with over 10\% of users failing to detect an attack on these encoding schemes. The recommendations of the authors is to to replace these encoding schemes with Words or Sentences due to their very high success rate and high usability scores.

### 2019-05-22 Papers/Notes_TeX/pages/paper_notes.tex
Changes; - Organised papers into relevant categories using a review matrix - Added some more potentially relevant papers - Start creating the literature review

@@
 
-Paper looks into the positives of secondary channels used to authenticate device pairing. Such as device fingerprint comparison.
+Paper looks into the positives of secondary channels used to authenticate device pairing.
+Such as device fingerprint comparison.
+It also aims to look into the fact that many studies performed do not take into consideration the aspect of human interaction.
+
+Total of 30 paid participants were recruited where the experiment simulated a P2P payment system.
+
+They collected:
+\begin{itemize}
+    \item Time to completed the associated process
+    \item Number of security or non-security related errors
+\end{itemize}
+
+And quantified using questionnaires:
+\begin{itemize}
+    \item Ease of use with the representation
+    \item Satisfaction with time spent with a method/representation
+    \item Participant's confidence with the scheme
+\end{itemize}
+
+The paper also tested methods:
+\begin{itemize}
+    \item Compare and Confirm
+    \item Compare and Select
+    \item Compare and Enter
+    \item Barcode scanning
+\end{itemize}
+
+Representations:
+\begin{itemize}
+    \item Numerical
+    \item Alphanumerical
+    \item Words
+    \begin{itemize}
+        \item Dictionary of 1024 words each mapped to 10-bits
+    \end{itemize}
+    \item Sentences
+    \item Images
+    \item Melodies
+    \item Sound (Numerical/Alphanumerical)
+\end{itemize}
 
@@
 Mentions a normal channel as a "Dolev-Yao" channel [5]. This is where an attacker can overhead, delete and modify messages.
+
+Talks about systems that were secure on paper that ended up in practice being miss-handled to reduce security. One example is with the Russian army in WWI [1]
+
+Bruce Schneier [27] also argues that systems and involves humans therefore often systems are broken due to improper use.
 
@@
     \end{itemize}
+
+    Showed that the best methods in terms of the SUM score [24] ranked the top 3 as:
+    \begin{itemize}
+        \item Numeric(C\&C)          [73.7]
+        \item Alphanumerical(C\&C)   [72.5]
+        \item Words (C\&C)           [70.6]
     \end{itemize}
+
+    Numerical had 0\% security failures, Word 3.3\% and Alphanumerical had a high 13.3\%
+
+    NOTE: This is a very small sample size.
+\end{itemize}
+
+\newpage
+
+\section{SafeSlinger: An Easy-to-use and Secure Approach for
+Human Trust Establishment}
+
+The aim of SafeSlinger is to solve the issue of key exchange.
+They aim to leverage the initial personal contact of people to facilitate trust.
+To solve the issue of people that would never meet they implement a system of "shared acquaintance"
+
+Talks about issues with decentralised (PGP [42]) and centralised (SSL CA [27, 34]) key exchange.
+
+"Tim Berners-Lee has called upon security researchers and professionals to design a public key encryption system for the people [11]"
+
+Only uses \textbf{24-bits} of a SHA-1 hash of all the exchanged information, \textbf{could this be exploited?}

### 2019-05-23 Literature_Review/pages/review_content.tex
Changes; - Added more references papers - More content added to the lit' review

@@
 Current research in ways to represent and validate fingerprints has almost exclusively focused on the usability of such schemes.
-The following section will discuss available research findings alongside a overall comparison of the research recommendations.
+The following will individually discuss available research findings alongside a overall comparison of the research recommendations.
 
+The first work in this area was performed by Hsu-Chun Hsiao, \textit{et. al.} in their paper: \textit{A Study of User-Friendly Hash Comparison Schemes}\cite{hsiao2009study} around 2009.
+
+The aim of the study was to provide the first insight into the best encoding scheme used to represent a hash fingerprint.
+The schemes used were Base32, English words, Random Art\footnote{A scheme proposed by A.
+Perrig \textit{et al.}\cite{perrig1999hash}}, Flag\footnote{Encoding scheme proposed by C Ellison \textit{et al.}\cite{ellison2003public}}, T-Flag\footnote{Yue-Hsun Lin \textit{et al.}\cite{lin2010spate} improvement on Flag}, Flag Ext\footnote{The author's own improvment on Flag} and finally Chinese, Korean and Japanese symbol encoding.
+
+\textbf{TODO: Finish review of paper}
+
+% DEBUG
+\newpage
 Work by Dechand Sergej, \textit{et al.}\cite{dechand2016empirical} empirically investigated the usability of 4 distinct textual representations evaluated with a experiments involving a total of 1047 participant.

### 2019-05-23 Papers/Notes_TeX/pages/paper_notes.tex
Changes; - Added more references papers - More content added to the lit' review

@@
 \textbf{TODO:} Need to find papers on study of words are a comparative measure.
+
+Lots of research has been done into the secure pairing of devices with minimal human involvement:
+
+\begin{itemize}
+    \item Using Camera Phones for Human-Verifiable Authentication
+    \item Loud and Clear: Human-Verifiable Authentication Based on Audio
+    \item A human-verifiable authentication protocol using visible laser light
+    \item Secure Device Pairing based on a Visual Channel
+    \item NFC
+    \item Physical contact
+\end{itemize}
 
@@
 
+\newpage
 \section{An Empirical Study of Textual Key-Fingerprint Representations}
@@
 
+\newpage
 \section{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}
@@
 \newpage
-
 \section{SafeSlinger: An Easy-to-use and Secure Approach for
@@
 Only uses \textbf{24-bits} of a SHA-1 hash of all the exchanged information, \textbf{could this be exploited?}
+
+\newpage
+\section{A Study of User-Friendly Hash Comparison Schemes}
+
+The aim of this study is to provide a study on what hash comparison scheme provides the best accuracy and shortest comparison time.
+
+The paper also proposes new schemes: An extension to Flag and three asian character representations.
+
+An interesting aspect is the effort put into the study to link characteristics about the participants, i.e.
+gender or age to how well they perform or rate the usability of the scheme.
+In total they had 436 participants.
+
+Overall they compare:
+\begin{itemize}
+    \item Base32
+    \item English words
+    \item Random Art
+    \item Flag
+    \item T-Flag
+    \item Flag ext
+    \item Chinese, Korean, Japanese characters
+\end{itemize}
+
+Key phrase: "We did not use hexadecimal digits because they're similar to Base32 and known to be error prone" [NO REFERENCE].
+This is shown in \textit{``An Empirical Study of Textual Key-Fingerprint Representations''} that this isn't true - ``However, our work shows that numeric representations actually perform significantly better than Base32 and is less error prone.''
+
+They study also considers the comparison of "easy" and "hard" pairs of hashes.
+Hard is where the hashes are designed to be very similar.
+This is designed to provide a base-line (easy) and a worst-case (hard).
+
+The paper deals with ranges of entropy of 22-28bits.
+
+Another system that uses word is the Unmanaged Internet Architecture [4]
+
+States that users make errors when comparing long strings [11]
+
+Dicussions are also made into the pre-requirements needed for some of these schemes.
+Random-Art needs a colour display and requires a relativly high computational cost to generate a representation.
+Asian characters require unicode or codec support.
+
+Paper also touches on ``Additional Benefits'' - the paper talks about the ability to verbally describe the scheme, this is so the encoding scheme can be verified using a channel that does not involve a visual feed such as a telephone conversation
+
+Overall the paper provides a table of requirements for the schemes with the graphical representations requiring a large number of pre-requirements.
+
+\subsection{Findings}
+\begin{itemize}
+    \item Source, age and gender have no significant impact on the accuracy across the schemes. But younger participants were significantly faster
+    \item In general, Base32, Random Art, T-Flag and Flag Ext provide fast and accurate comparisons
+    \item Comprehension of a language when used as a encoding scheme affects the ability to distinguish hard pairs by a significant amount
+\end{itemize}
+
+\newpage
+\section{Usability Analysis of Secure Pairing Methods}
+
+Paper is aiming to perform a comparative usability evaluation of \textbf{selection methods} of hash comparisons
+
+This paper is doing this study in the context of secure device pairing in a diffie-hellman type key exchange.
+However, the results of the study could directly apply to that of hash comparison, however, it must be considered that the comparisons here are for \textbf{very} short strings.
+Around 4-digits
+
+Comparison methods compared:
+\begin{itemize}
+    \item Compare-and-Confirm
+    \item Select-and-Confirm
+    \item Copy-and-Confirm
+\end{itemize}
+
+The paper also compared to methods of passphrase comparison that weren't relevant.
+
+Paper also included demographical information in the study, with two round of 40 participants in the usability studies.
+
+Findings:
+
+Round 1:
+\begin{itemize}
+    \item Copy-and-confirm was percieved as hard to use
+    \item Copy-and-confirm has the lowest fatal error rate but the longest comparison time and lowest percieved usability
+    \item The schemes reduced fatal error rate as their comparison times rose
+    \item Copy-and-confirm had issues with user confusion in terms of use
+\end{itemize}
+
+In the second round they only decided to continue with
+
+\begin{itemize}
+    \item Compare-and-Confirm
+    \item Select-and-Confirm
+\end{itemize}
+
+They dropped Copy-and-confirm due to its high similarity to the other scheme "Copy" that was being used for passphrase sharing
+
+The second round included some UI changes that were backed up by external research.
+
+This round the changes performed on the schemes resulted in much lower fatal error rates.
+However, Select-and-confirm had an unacceptable 5\% error rate.
+Compare-and-confirm had 0\% fatal error rate.
+The was an improvment from 20\% to 0\%.
+
+Both schemes were again percieved as easy to use
+
+Overall it was shown that compare-and-confirm was the superior choice.

### 2019-05-24 Literature_Review/pages/review_content.tex
Changes; - More content added to the literature review - Updated review matrix

@@
 Current research in ways to represent and validate fingerprints has almost exclusively focused on the usability of such schemes.
-The following will individually discuss available research findings alongside a overall comparison of the research recommendations.
+The following section will individually discuss available research findings alongside a overall comparison of the research recommendations.
 
-The first work in this area was performed by Hsu-Chun Hsiao, \textit{et. al.} in their paper: \textit{A Study of User-Friendly Hash Comparison Schemes}\cite{hsiao2009study} around 2009.
+The first work in this area was performed by Hsu-Chun Hsiao, \textit{et. al.} in their paper: \textit{A Study of User-Friendly Hash Comparison Schemes}\cite{hsiao2009study} in around 2009.
 
@@
 Perrig \textit{et al.}\cite{perrig1999hash}}, Flag\footnote{Encoding scheme proposed by C Ellison \textit{et al.}\cite{ellison2003public}}, T-Flag\footnote{Yue-Hsun Lin \textit{et al.}\cite{lin2010spate} improvement on Flag}, Flag Ext\footnote{The author's own improvment on Flag} and finally Chinese, Korean and Japanese symbol encoding.
+436 participants were assessed in the study.
 
-\textbf{TODO: Finish review of paper}
+Alongside the main aim of the paper, the authors wanted to provide empirical links between participant attributes such as age or gender to performance with the encoding scheme.
+This is something rarely seen in the related research.
+Hsu-Chun Hsiao \textit{et al.} also provided two categories of similarities; ``hard'' and ``easy''.
+These were designed to be worst and best case respectively.
+As a final aim and the reason for the inclusion of Chinese, Korean and Japanese characters was to research if being a native speaker assists the user in distinguishing subtle differences between encodings in the respective language.
 
-% DEBUG
-\newpage
+The entropy of encodings ranged from 22-bits to 28-bits.
+This is extremely low in comparison to similar research.
+However, this can be attributed to the age of the paper due to its 10 year age and the time of writing.
+
+The authors decision to exclude hexadecimal (one of the most widespread encoding schemes) was due to its similarity to Base32 and its well known deficiencies.
+This is not consistent with available research (such as \textit{``Empirical Study of Textual Key-Fingerprint Representations''}) and in some cases hexadecimal has been show to exceeded the performance on some of the more advanced schemes in usability and security.
+
+Overall, findings from the paper showed that age and gender does not affect the accuracy of the scheme, however younger participants were significantly faster. \\
+The paper recommends Base32, Random Art, T-Flag or their own improvement; Flag Ext.
+These encoding recommendations were also supplemented with a review of requirements required by these schemes.
+The recommendation of graphical encoding schemes is inconsistent with alternative literature, where most other papers have found graphical encodings hard to use and insecure.
+In terms of language comprehension; being able to speak the language assists in the ability to discern the different between hard pairs.
+Knowledge of the language subsequently did not help with easy pairs.
+
+In conclusion, the paper provided a very strong foundation for further research due to the wide variety of topics touched upon.
+However, its age means that results cannot be applicable to modern day scenarios, and oversights in the development of the study such as the exclusion of hexadecimal encoding and the lack of information gained on the perceived usability of the scheme from users results in an incomplete study of these encoding schemes.
+
+Further research bu Kainda \textit{et al.}\cite{kainda2009usability} in 2009 investigated fingerprint representations and comparison methods in the context of using humans as the Out-Of-Band (OOB) channel for secure device pairing.
+This study was comprehensive and assessed a wide variety of concepts.
+This is one of the few papers in the literature that assessed the way to compare representations alongside the representations themselves.
+
+For comparison methods that paper looked into Compare-and-Confirm, Compare-and-Select, Compare-and-Enter and Barcode scanning.
+This set includes the most common ways of comparison acording to available research.
+Alongside this, the paper reviews Numerical, Alphanumerical, Word, Sentences, Images, Melodies and Sound (Numerical/Alphanumerical).
+Again, this in comparison to similar literature is highly comprehensive.
+
+In terms of empirical data gathered by the paper, they reviewed time completed to review the representation and the number of security and non-security related errors.
+Further more, the authors also collected user opinion on ease-of-use, satisfaction and confidence of the reviewed schemes.
+The overall schemes were then quantified using a single metric known as the Single Usability Metric (SUM)\cite{sauro2005method}.
+This provides a quick way to rank and compare the schemes, thus improving the usability of the results.
+However, the one apparent downside to the experimental side of the study is 40 participants enrolled.
+This in comparison to other studies is one of the smallest size of enrolment and thus, puts a possible limit on the accuracy and applicability of the obtained results.
+
+Overall, if usability is the only consideration the paper ranked the comparison methods like so: Compare-and-Confirm, Compare-and-Enter, Compare-and-Select and Barcode.
+If, however, the consideration of security alongside usability is required the best is Compare-and-enter, Barcode, Compare-and-Confirm and Compare-and-Select.
+Research has been limited in this area of modes of comparison, however, the results from this paper are consistent with the alternative literature.
+\\
+In terms of encoding schemes the paper ranked Numerical, Alphanumerical and Words as the top three encoding schemes (These were all with Compare-and-Confirm).
+This took into consideration the usability and security of the scheme.
+This is relatively consistent with other literature where numerical and written encoding schemes seem to be the most effective overall.
+
+In conclusion, this paper provided a highly comprehensive review of all the aspects of human fingerprint verification, where it reviewed all the elements involved in the human fingerprint verification.
+The only limitation of the paper is the size of the participants enrolled.
+
+A paper by Ersin Uzun \textit{et al.} exclusively reviewed comparison methods.
+This is performed in the context of ``Secure device pairing'' and thus some comparison schemes are tested that are not relevant in a fingerprint comparison context, for example:  ``Choose-and-Enter'' (A participant chooses a passphrase from an available list and enters it into to the other device).
+Thus, only relevant comparison scheme and their results have been extracted and compared.
+
+The relevant comparison methods tested were, Compare-and-Confirm, Compare-and-Select and Compare-and-Enter.
+These are almost exactly the same encoding schemes assesed in the relevant research literature.
+The paper also had two rounds of experiments including 40 participants each where changes were made to UX and format between these studies.
+
+Due to the ``Secure device pairing'' context the paper was written under, consideration needs to be made into the strings encoded.
+Due to secure device pairing commonly utilising Short Authentication Strings (SAS) the paper only reviewed encodings of 4 digit long strings.
+This, therefore, limits the applicability of the results to fingerprint encoding.
+This will be considered later when comparing the results to alternative literature.
+
+Between the two rounds the authors dropped Confirm-and-Enter due to it low usability and over similarity to a similar scheme "Copy" used for passphrase verification.
+The low rating for Confirm-and-Enter is in contrast with research performed by Kainda \textit{et al.}\cite{kainda2009usability} They ranked Confirm-and-Enter as the 2nd most usable system.
+
+With changes to the UX of Confirm-and-Confirm backed up by external research \cite{palmer1990attentional}\cite{hammer2009category} the second round of research was performed with a new set of participants.
+
+Overall, the changes took Confirm-and-Confirm from 20\% to 0\% fatal error rate (FER).
+The same trend for Confirm-and-Select with it reducing its FER from 12.5\% to 5\%.
+With the changes the participants perceived the systems as easy to use.
+The authors therefore recommended Confirm-and-Confirm as the overall best choice for comparison methods.
+Again, comparing this word to the most similar work done by Kainda \textit{et al.}\cite{kainda2009usability} this is consistent with their findings where they ranked Compare-and-Confirm as more secure compared to that of Compare-and-Select.
+
+Overall, the paper provides a sizeable insight into suitable methods of comparison, this is due to the cross over fingerprint comparison and secure device pairing have.
+This paper is limited in terms of the short strings compared, the different overall research aim and the size of the number of participants used in the studies.
+In terms of security of the schemes the results were constant with that of alternative research but clashed when usability was considered.
+This, however, may be due to the differing use-cases of the comparison methods and the sizes of strings being compared.
+
 Work by Dechand Sergej, \textit{et al.}\cite{dechand2016empirical} empirically investigated the usability of 4 distinct textual representations evaluated with a experiments involving a total of 1047 participant.
@@
 The recommendations of the authors is to to replace these encoding schemes with Words or Sentences due to their very high success rate and high usability scores.
+The performance of the Alphanumerical encoding schemes is relatively consistent with the literature, however, it is hard to say conclusively due to the small number and lack of visual encoding schemes reviewed making it hard to place alphanumerical encodings in an overall rating.

### 2019-05-24 Literature_Review/pages/review_content.tex
Changes; - Added more content to the literature review. - Finished adding the inital notes for all of the fingerprint representation review papers

@@
 
-The authors decision to exclude hexadecimal (one of the most widespread encoding schemes) was due to its similarity to Base32 and its well known deficiencies.
-This is not consistent with available research (such as \textit{``Empirical Study of Textual Key-Fingerprint Representations''}) and in some cases hexadecimal has been show to exceeded the performance on some of the more advanced schemes in usability and security.
+The authors decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes) was due to their similarity to Base32 and their well known deficiencies.
+This is not consistent with available research where, for example in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}) it was shown numerical representations performed better than that of Base32.
 
@@
 The performance of the Alphanumerical encoding schemes is relatively consistent with the literature, however, it is hard to say conclusively due to the small number and lack of visual encoding schemes reviewed making it hard to place alphanumerical encodings in an overall rating.
+
+J Tan \textit{et al.} work is very similar to that of the research already discussed.
+8 distinct fingerprint representations were tested with over 661 participants.
+Each representation was tested using Compare-and-Confirm and Compare-and-Select.
+The small difference with this paper is the inclusion of two novel graphical encodings Vash\footnote{https://github.com/thevash/vash} and Unicorns\footnote{https://unicornify.pictures/}.
+The compared schemes were: Hexadecimal, Alternating vowel/consonants, Words, Numbers, Sentences, OpenSSH visual host key, Vash and Unicorns.
+
+The target security level chosen was an entropy of 160-bits.
+This is very high level of security and allows for the papers results to be effectively ``future-proofed''.
+Alongside this, the paper defined attack strengths of an average $2^{60}$ with other specific use-cases for lower and higher attacker strength.
+Users were recruited via MTurk and assigned an experiment attempting to emulate a real-life condition (Comparison of a fingerprint on a business card).
+The real-world accuracy was one unique element that this paper concentrated on, this was portrayed through the author's attention to detail when designing the experiment.
+
+Overall, results from the experiments emulated previously discussed literature.
+Textual representations faired effectively well with Words and Sentences again being some of the best options overall.
+Performance of graphical representation was mixed with OpenSSH having performance matching that of a strong textual mapping while Unicorns having the worst performance overall.
+This performance with graphical representations is consistent with the available literature apart from the positive performance of OpenSSH.
+The results of different modes of comparison was highly consistent with other studies where again the recommendation was to not use compare-and-select as its performance across the board was below even simple levels of security.

### 2019-05-24 Papers/Notes_TeX/pages/paper_notes.tex
Changes; - Added more content to the literature review. - Finished adding the inital notes for all of the fingerprint representation review papers

--- 2019-05-21 Papers/Notes_TeX/pages/paper_notes.tex
@@
 
-\section{An Empirical Study of Textual Key-Fingerprint Representations}
+\newpage
+% \section{An Empirical Study of Textual Key-Fingerprint Representations}
 
-Study involved 1047 participants evaluating 6 different textual representations on MTurk. The study also includes an evaluation into usability.
+% Study involved 1047 participants evaluating 6 different textual representations on MTurk. The study also includes an evaluation into usability.
 
-The study has an attacker power of around 80 of 112 bits.
+% The study has an attacker power of around 80 of 112 bits.
 
+% \begin{itemize}
+%     \item Alphanumerical
+%     \item Numerical
+%     \item Words
+%     \item Sentences
+% \end{itemize}
+
+% More mention to decentralised method finding it hard to find adoption such as Web of Trust and Namecoin ([7, 13, 30])
+
+% References as system called CONIKS and others ([24, 39, 27]) that aim to provided a directory of keys
+
+% States that many systems still rely on fingerprint comparison ([17])
+
+% States that the \textbf{hexadecimal} encoding is used in most systems.
+
+% States again that fingerprint comparison is seldom done in practice ([17, 37])
+
+% Studies have shown that users find it difficult to compare long and "meaningless" strings ([19])
+
+% References to other word lists used. PGP Word list [22] and english word list compiled by K.C. Ogden [31]. The Peerio word list is generated from the most common words in english subtitles.
+
+% Interesting recommendation into the use of \textit{scrypt} [34] and \textit{Argon 2} [3] can be used to shorten the fingerprint length.
+These work slowly and a prevent easy computation of pre-images.
+
+% When generating partial-collision fixing the bits at the start and end has been shown a best practice ([17, 37])
+
+% \subsection{Findings}
+% \begin{itemize}
+%     \item Overall recommendation is to replace \textbf{hexadecimal} with \textbf{sentence} based encoding
+%     \item Findings show that \textbf{hexadecimal} and \textbf{Base32} perform worse than the other alternatives in realistic threat models.
+With over \textbf{10\%} of users failing to detect attacks with these schemes.
+%     \item According to their study, \textbf{words} and \textbf{sentences} we some of the best methods for avoiding attack
+%     \item Words has the second highest usability ratings second to only sentences
+% \end{itemize}
+
+% \newpage
+% \section{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}
+
+% Paper looks into the positives of secondary channels used to authenticate device pairing.
+Such as device fingerprint comparison.
+It also aims to look into the fact that many studies performed do not take into consideration the aspect of human interaction.
+
+% Total of 30 paid participants were recruited where the experiment simulated a P2P payment system.
+
+% They collected:
+% \begin{itemize}
+%     \item Time to completed the associated process
+%     \item Number of security or non-security related errors
+% \end{itemize}
+
+% And quantified using questionnaires:
+% \begin{itemize}
+%     \item Ease of use with the representation
+%     \item Satisfaction with time spent with a method/representation
+%     \item Participant's confidence with the scheme
+% \end{itemize}
+
+% The paper also tested methods:
+% \begin{itemize}
+%     \item Compare and Confirm
+%     \item Compare and Select
+%     \item Compare and Enter
+%     \item Barcode scanning
+% \end{itemize}
+
+% Representations:
+% \begin{itemize}
+%     \item Numerical
+%     \item Alphanumerical
+%     \item Words
+%     \begin{itemize}
+%         \item Dictionary of 1024 words each mapped to 10-bits
+%     \end{itemize}
+%     \item Sentences
+%     \item Images
+%     \item Melodies
+%     \item Sound (Numerical/Alphanumerical)
+% \end{itemize}
+
+% "People are the weakest link in the security chain" [26]
+
+% Mentions a normal channel as a "Dolev-Yao" channel [5]. This is where an attacker can overhead, delete and modify messages.
+
+% Talks about systems that were secure on paper that ended up in practice being miss-handled to reduce security. One example is with the Russian army in WWI [1]
+
+% Bruce Schneier [27] also argues that systems and involves humans therefore often systems are broken due to improper use.
+
+% \subsection{Findings}
+% \begin{itemize}
+%     \item Showed for \textbf{usability} methods ranked:
+%     \begin{itemize}
+%         \item Comparing-confirm
+%         \item Typing strings
+%         \item Comparing-select
+%         \item Barcode
+%     \end{itemize}
+
+%     \item Showed for \textbf{combined security} and \textbf{usability} methods ranked:
+%     \begin{itemize}
+%         \item Typing strings
+%         \item Barcodes
+%         \item Comparing-confirm
+%         \item Comparing-select
+%     \end{itemize}
+
+%     Showed that the best methods in terms of the SUM score [24] ranked the top 3 as:
+%     \begin{itemize}
+%         \item Numeric(C\&C)          [73.7]
+%         \item Alphanumerical(C\&C)   [72.5]
+%         \item Words (C\&C)           [70.6]
+%     \end{itemize}
+
+%     Numerical had 0\% security failures, Word 3.3\% and Alphanumerical had a high 13.3\%
+
+%     NOTE: This is a very small sample size.
+% \end{itemize}
+
+% \newpage
+% \section{SafeSlinger: An Easy-to-use and Secure Approach for
+% Human Trust Establishment}
+
+% The aim of SafeSlinger is to solve the issue of key exchange.
+They aim to leverage the initial personal contact of people to facilitate trust.
+To solve the issue of people that would never meet they implement a system of "shared acquaintance"
+
+% Talks about issues with decentralised (PGP [42]) and centralised (SSL CA [27, 34]) key exchange.
+
+% "Tim Berners-Lee has called upon security researchers and professionals to design a public key encryption system for the people [11]"
+
+% Only uses \textbf{24-bits} of a SHA-1 hash of all the exchanged information, \textbf{could this be exploited?}
+
+% \newpage
+% \section{A Study of User-Friendly Hash Comparison Schemes}
+
+% The aim of this study is to provide a study on what hash comparison scheme provides the best accuracy and shortest comparison time.
+
+% The paper also proposes new schemes: An extension to Flag and three asian character representations.
+
+% An interesting aspect is the effort put into the study to link characteristics about the participants, i.e.
+gender or age to how well they perform or rate the usability of the scheme.
+In total they had 436 participants.
+
+% Overall they compare:
+% \begin{itemize}
+%     \item Base32
+%     \item English words
+%     \item Random Art
+%     \item Flag
+%     \item T-Flag
+%     \item Flag ext
+%     \item Chinese, Korean, Japanese characters
+% \end{itemize}
+
+% Key phrase: "We did not use hexadecimal digits because they're similar to Base32 and known to be error prone" [NO REFERENCE].
+This is shown in \textit{``An Empirical Study of Textual Key-Fingerprint Representations''} that this isn't true - ``However, our work shows that numeric representations actually perform significantly better than Base32 and is less error prone.''
+
+% They study also considers the comparison of "easy" and "hard" pairs of hashes.
+Hard is where the hashes are designed to be very similar.
+This is designed to provide a base-line (easy) and a worst-case (hard).
+
+% The paper deals with ranges of entropy of 22-28bits.
+
+% Another system that uses word is the Unmanaged Internet Architecture [4]
+
+% States that users make errors when comparing long strings [11]
+
+% Dicussions are also made into the pre-requirements needed for some of these schemes.
+Random-Art needs a colour display and requires a relativly high computational cost to generate a representation.
+Asian characters require unicode or codec support.
+
+% Paper also touches on ``Additional Benefits'' - the paper talks about the ability to verbally describe the scheme, this is so the encoding scheme can be verified using a channel that does not involve a visual feed such as a telephone conversation
+
+% Overall the paper provides a table of requirements for the schemes with the graphical representations requiring a large number of pre-requirements.
+
+% \subsection{Findings}
+% \begin{itemize}
+%     \item Source, age and gender have no significant impact on the accuracy across the schemes. But younger participants were significantly faster
+%     \item In general, Base32, Random Art, T-Flag and Flag Ext provide fast and accurate comparisons
+%     \item Comprehension of a language when used as a encoding scheme affects the ability to distinguish hard pairs by a significant amount
+% \end{itemize}
+
+% \newpage
+% \section{Usability Analysis of Secure Pairing Methods}
+
+% Paper is aiming to perform a comparative usability evaluation of \textbf{selection methods} of hash comparisons
+
+% This paper is doing this study in the context of secure device pairing in a diffie-hellman type key exchange.
+However, the results of the study could directly apply to that of hash comparison, however, it must be considered that the comparisons here are for \textbf{very} short strings.
+Around 4-digits
+
+% Comparison methods compared:
+% \begin{itemize}
+%     \item Compare-and-Confirm
+%     \item Select-and-Confirm
+%     \item Copy-and-Confirm
+% \end{itemize}
+
+% The paper also compared to methods of passphrase comparison that weren't relevant.
+
+% Paper also included demographical information in the study, with two round of 40 participants in the usability studies.
+
+% Findings:
+
+% Round 1:
+% \begin{itemize}
+%     \item Copy-and-confirm was percieved as hard to use
+%     \item Copy-and-confirm has the lowest fatal error rate but the longest comparison time and lowest percieved usability
+%     \item The schemes reduced fatal error rate as their comparison times rose
+%     \item Copy-and-confirm had issues with user confusion in terms of use
+% \end{itemize}
+
+% In the second round they only decided to continue with
+
+% \begin{itemize}
+%     \item Compare-and-Confirm
+%     \item Select-and-Confirm
+% \end{itemize}
+
+% They dropped Copy-and-confirm due to its high similarity to the other scheme "Copy" that was being used for passphrase sharing
+
+% The second round included some UI changes that were backed up by external research.
+
+% This round the changes performed on the schemes resulted in much lower fatal error rates.
+However, Select-and-confirm had an unacceptable 5\% error rate.
+Compare-and-confirm had 0\% fatal error rate.
+The was an improvment from 20\% to 0\%.
+
+% Both schemes were again percieved as easy to use
+
+% Overall it was shown that compare-and-confirm was the superior choice.
+
+\newpage
+\section{On the Pitfalls of End-to-End Encrypted Communications: A Study of Remote Key-Fingerprint Verification}
+
+Paper compares the fingerprint verification task in the context of Instant messaging E2E The paper is also choosing to focus on the remote vs proximity ways of comparing fingerprints.
+They aim to study the security and usability of human-centred E2E key verification.
+The study ran with 25 participants.
+
+Seems to be the first study of remote code verification study
+
+Study compares Numerical, Image and verbally spoken codes and QR just for proximity alongside all the other alternatives.
+
+The studies main aim to compare remote to proximity, not compare the various methods
+
+The research is split into two sub-goals: Robustness - looks at the FAR and FRR. User experience and perception - System usability, Comfort, Satisfaction and Adaptability
+
+States that numerical is the one of the most common representations, but out of the chosen methods 50\% use numerical and the rest hexadecimal?
+
+They included 3 level of incorrect codes. One char change, one block and the entire fingerprint
+
+Overall Audio was one of the most secure and easiest to use.
+However results for image based comparisons were not controlled in any way due to the author being unable to access the telegram image generation, this means while the other schemes had controlled restraints the image did not.
+Images was rated the worst.
+
+Findings:
 \begin{itemize}
-    \item Alphanumerical
-    \item Numerical
-    \item Words
-    \item Sentences
+    \item High False Acceptance Rate (False Negative) for all code verification methods 
+    \item Results point to low usability in remote code verification settings, aside from audio based verification ever scheme has above 20\% False Rejection Rate (False Positive)
+    \item In proximity settings users were able to detect attacks with minimal error rates
 \end{itemize}
-
-More mention to decentralised method finding it hard to find adoption such as Web of Trust and Namecoin ([7, 13, 30])
-
-References as system called CONIKS and others ([24, 39, 27]) that aim to provided a directory of keys
-
-States that many systems still rely on fingerprint comparison ([17])
-
-States that the \textbf{hexadecimal} encoding is used in most systems.
-
-States again that fingerprint comparison is seldom done in practice ([17, 37])
-
-Studies have shown that users find it difficult to compare long and "meaningless" strings ([19])
-
-References to other word lists used. PGP Word list [22] and english word list compiled by K.C. Ogden [31]. The Peerio word list is generated from the most common words in english subtitles.
-
-Interesting recommendation into the use of \textit{scrypt} [34] and \textit{Argon 2} [3] can be used to shorten the fingerprint length. These work slowly and a prevent easy computation of pre-images.
-
-When generating partial-collision fixing the bits at the start and end has been shown a best practice ([17, 37])
-
-\subsection{Findings}
-\begin{itemize}
-    \item Overall recommendation is to replace \textbf{hexadecimal} with \textbf{sentence} based encoding
-    \item Findings show that \textbf{hexadecimal} and \textbf{Base32} perform worse than the other alternatives in realistic threat models.
-With over \textbf{10\%} of users failing to detect attacks with these schemes.
-    \item According to their study, \textbf{words} and \textbf{sentences} we some of the best methods for avoiding attack
-    \item Words has the second highest usability ratings second to only sentences
-\end{itemize}
-
-\section{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}
-
-Paper looks into the positives of secondary channels used to authenticate device pairing. Such as device fingerprint comparison.
-
-"People are the weakest link in the security chain" [26]
-
-Mentions a normal channel as a "Dolev-Yao" channel [5]. This is where an attacker can overhead, delete and modify messages.
-
-\subsection{Findings}
-\begin{itemize}
-    \item Showed for \textbf{usability} methods ranked:
-    \begin{itemize}
-        \item Comparing-confirm
-        \item Typing strings
-        \item Comparing-select
-        \item Barcode
-    \end{itemize}
-
-    \item Showed for \textbf{combined security} and \textbf{usability} methods ranked:
-    \begin{itemize}
-        \item Typing strings
-        \item Barcodes
-        \item Comparing-confirm
-        \item Comparing-select
-    \end{itemize}
-\end{itemize}

### 2019-05-25 Literature_Review/pages/review_content.tex
Changes; - Added more content to the literature review

@@
 The authors decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes) was due to their similarity to Base32 and their well known deficiencies.
-This is not consistent with available research where, for example in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}) it was shown numerical representations performed better than that of Base32.
+This is not consistent with available research.
+For example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''} it was shown numerical representations performed better than that of Base32.
 
@@
 These encoding recommendations were also supplemented with a review of requirements required by these schemes.
-The recommendation of graphical encoding schemes is inconsistent with alternative literature, where most other papers have found graphical encodings hard to use and insecure.
-In terms of language comprehension; being able to speak the language assists in the ability to discern the different between hard pairs.
+The recommendation of graphical encoding schemes is inconsistent with alternative literature, where most other papers have found graphical encodings easy to use but insecure.
+In terms of language comprehension; being able to speak the language assists in the ability to discern the differences between hard pairs.
 Knowledge of the language subsequently did not help with easy pairs.
@@
 In conclusion, the paper provided a very strong foundation for further research due to the wide variety of topics touched upon.
-However, its age means that results cannot be applicable to modern day scenarios, and oversights in the development of the study such as the exclusion of hexadecimal encoding and the lack of information gained on the perceived usability of the scheme from users results in an incomplete study of these encoding schemes.
+However, its age means that results cannot be applicable to modern day scenarios, and oversights in the development of the study such as the exclusion of hexadecimal encoding and the lack of information gained on the perceived usability of the scheme from users results in an ultimately incomplete study.
 
@@
 Overall, if usability is the only consideration the paper ranked the comparison methods like so: Compare-and-Confirm, Compare-and-Enter, Compare-and-Select and Barcode.
-If, however, the consideration of security alongside usability is required the best is Compare-and-enter, Barcode, Compare-and-Confirm and Compare-and-Select.
+If, however, the consideration of security alongside usability is required the best is Compare-and-Enter, Barcode, Compare-and-Confirm and Compare-and-Select.
 Research has been limited in this area of modes of comparison, however, the results from this paper are consistent with the alternative literature.
@@
 With changes to the UX of Confirm-and-Confirm backed up by external research \cite{palmer1990attentional}\cite{hammer2009category} the second round of research was performed with a new set of participants.
-
-Overall, the changes took Confirm-and-Confirm from 20\% to 0\% fatal error rate (FER).
+The alterations took Compare-and-Confirm from 20\% to 0\% fatal error rate (FER).
 The same trend for Confirm-and-Select with it reducing its FER from 12.5\% to 5\%.
 With the changes the participants perceived the systems as easy to use.
-The authors therefore recommended Confirm-and-Confirm as the overall best choice for comparison methods.
-Again, comparing this word to the most similar work done by Kainda \textit{et al.}\cite{kainda2009usability} this is consistent with their findings where they ranked Compare-and-Confirm as more secure compared to that of Compare-and-Select.
+The authors therefore recommended Compare-and-Confirm as the overall best choice for comparison methods.
+Again, comparing this word to the most similar work done by Kainda \textit{et al.}\cite{kainda2009usability} this is consistent with their findings where they ranked Compare-and-Confirm as the most secure comparison method.
 
-Overall, the paper provides a sizeable insight into suitable methods of comparison, this is due to the cross over fingerprint comparison and secure device pairing have.
+Overall, the paper provides a sizeable insight into suitable methods of comparison, this is due to the cross over between fingerprint comparison and secure device pairing.
 This paper is limited in terms of the short strings compared, the different overall research aim and the size of the number of participants used in the studies.
@@
 Other references made within the paper touch upon the vulnerabilities and usability issues present with the way humans interact with the security systems.
-Example of these are studies showing humans find it difficult to comprehend long and "meaningless" strings and the lack of actual comparison performed by actual users in live scenario's.
+Example of these are studies showing humans find it difficult to comprehend long and "meaningless" strings and the lack of actual comparison performed by users in live scenarios.
 These are, however, acknowledged as limitations in the later stages of the paper.
@@
 This performance with graphical representations is consistent with the available literature apart from the positive performance of OpenSSH.
-The results of different modes of comparison was highly consistent with other studies where again the recommendation was to not use compare-and-select as its performance across the board was below even simple levels of security.
+The results of different modes of comparison was highly consistent with other studies where again the recommendation was to not use Compare-and-Select as its performance across the board was below even basic levels of security.
+
+\textbf{TODO: } Summarise research section
+
+\section{Fingerprint encoding schemes}
+Another area of research is investigation into the actual physical encodings of the hash digest.
+This section will briefly discuss the current research available on the creation and security of actual encoding schemes.
+The actual details of operation of the schemes are outside the scope of this literature review, therefore, minimal attention will be allocated to these details.
+
+Some of the oldest preliminary work into visual encoding schemes was performed by Adrian Perrig \textit{et al}\cite{perrig1999hash}.
+in the creation of their scheme ``Random Art" in 1999.
+The motivation for creating such a scheme was the perceived flaws in the ways humans verify information and compare written information.
+As mentioned in previous sections visual encoding schemes have been shown to have mixed success, with low security being one of their most alarming flaws.
+This research laid the foundation for further work in analysing the security of visual encoding schemes (as discussed in the previous section) to the creation of new schemes.
+
+Further research into creation of unique visual hash schemes have been performed by C Ellison \textit{et al.} \cite{ellison2003public} (Flag), Yue-Hsun Lin \textit{et al.}\cite{lin2010spate} (T-Flag) and work by MM Olembo \textit{et al.}\cite{olembo2013developing}.
+Each publication has provided a new way to visually represent a key fingerprint.
+This list is by no means exhaustive but is used to depict amount of research into this topic.
+
+One paper of note is the preliminary work performed by D Loss \textit{et al.}\cite{loss2009drunken} in their \textit{``An analysis of the OpenSSH fingerprint visualization algorithm''} where their aim was to spur on further research with their initial findings into the security of the OpenSSH scheme.
+The authors claim that the use of the algorithm in OpenSSH is only heuristically defined and there is a need for a formal proof of its security.
+
+The paper proposed a number of ways to generate similar fingerprints.
+The methods proposed were: Naive brute force, graph theory methods, and brute force of a full visual set.
+They were able to produce only very basic results and have proposed a large amount of potential further work.
+Since the papers publication in 2009, there seems to have been no publications building on the work of the authors.
+This highlights a current gap in the available literature.
+
+Minimal research has also focused on textual fingerprint representations and their respective security.
+Work by A.
+Karole and N.
+Saxena\cite{karole2009improving} is the only relevant research looking into ways to improve the security of a textual representation.
+This research aim is to improve the secure device pairing process of comparing two numerical values.
+The devices used (Nokia 6030b - Mid range devices at the time of publication) and short SAS compared results in findings that only slightly applicable in a fingerprint comparison context.
+
+Aside from this research there has been no other publications exploring the security textual representations. This clearly shows the presence of a sizeable research gap in the available literature.
+
+{\small \textbf{TODO: } \textit{Need to double check this, I think there might have been some work into sentences}}
+
+In conclusion to this topic, the current research has primarily focused on the research and creation of visual representations.
+This leaves a previously mentioned research gap for anything focusing primarily on the security and usability of encoding schemes such as words, or sentences.

### 2019-05-25 Papers/Notes_TeX/pages/paper_notes.tex
Changes; - Added more content to the literature review

@@
 \end{itemize}
+
+\newpage
+
+\section{The drunken bishop: An analysis of the OpenSSH
+fingerprint visualization algorithm}
+
+The aim of this research is to study the OpenSSH Visual Host Key.
+The authors claim that the scheme was heuristically designed and has very little backing in terms of formal research, this paper aims to create a foundation for this research.
+
+OpenSSH uses MD5 to generate a 128-bit fingerprint of the Server's key, this is then split into 64 2-bit pairs.
+These are then traversed byte wise in a right to left over the bit pairs.
+Each pair defines the direction of travel.
+If the snake reaches a position multiple times a pre define character is added depending on the number of visits (for example, 6 times == "B")
+
+The paper also discusses ways to create collisions:
+
+In conclusive results and more of an inital PoC
+
+\begin{itemize}
+    \item Brute force
+    \item Graph theory
+    \item Brute forcing a visual set
+\end{itemize}
+
+\newpage
+
+\section{Improving the Robustness of Wireless Device
+Pairing Using Hyphen-Delimited Numeric
+Comparison}
+
+In the context of secure device pairing the paper aims to improve the human interaction with number pairing.
+
+Lots of research has gone into Short Authentication String (SAS) numbers ([14], [10], [4])
+
+The research was peformed on very old devices. Nokia 6030b, very out of date and not reflective of anything around at this time.
+
+Usability study looked into Efficiency, Robustness, General Usability
+
+Strange format of keeping the numbers exactly the same but just placing hyphens in the middle. The authors attempted to remedy this by spacing the experiments with a days gap
+
+Study was performed with 40 participants
+
+Very small number of values tested only 5 overall???
+
+Initial results show promising results for hypen delimitations etc alongside improved user impressions

### 2019-05-25 Literature_Review/pages/review_content.tex
Changes; - More content to the literature review

@@
 Each publication has provided a new way to visually represent a key fingerprint.
-This list is by no means exhaustive but is used to depict amount of research into this topic.
+Alongside the accademic literature there are more informally presented methods of visual fingerprints such as Unicorns\footnote{https://unicornify.pictures/} and Robots\footnote{https://github.com/e1ven/Robohash} This list is by no means exhaustive but is used to depict amount of research and work invested into this topic.
 
@@
 
-Minimal research has also focused on textual fingerprint representations and their respective security.
+Minimal research has also focused on basic textual fingerprint representations and their respective security.
 Work by A.
 Karole and N.
-Saxena\cite{karole2009improving} is the only relevant research looking into ways to improve the security of a textual representation.
+Saxena\cite{karole2009improving} looked into ways to improve the security of a textual representation.
 This research aim is to improve the secure device pairing process of comparing two numerical values.
@@
 
-Aside from this research there has been no other publications exploring the security textual representations. This clearly shows the presence of a sizeable research gap in the available literature.
+A more specific subsection of textual fingerprints is the use of words and sentences to encode hash digests. Some of the first work in this area was produced by Patrick Juola and Philip Zimmermann 
+\cite{juola1996whole} and their work in generating a word list where phonetic distinctiveness was prioritised. 
+The inital sampling of words was taken from the Grady Ward's Moby Pronunciator that contains a huge list of word/pronunciation pairs.
+Each word is mapped to one byte where the unique aspect of the word list is the separation of ``even'' and ``odd'' words where even byte positions sample from the even list and odd from the odd list.
+The effectively creates two sub-word lists.
+The pairing of these word lists were determined through the use of a Genetic algorithm.
+The paper also includes a study on effective measures of linguistic distances of words and provided an in-depth discussion into these areas.
 
-{\small \textbf{TODO: } \textit{Need to double check this, I think there might have been some work into sentences}}
+Overall the paper provides a foundation for formalising the creation of an effective wordlists.
+A limitation, however, is the lack of empirical data gathered on the effectiveness of the word list.
+This was evaluated later by the work of Dechand \textit{et al.}
+\cite{dechand2016empirical} and shown to be an effective encoding scheme.
+
+\textbf{TODO: } Add Loud and Clear: Human-Verifiable Authentication Based on Audio
+
+Aside from this research there has been more informal implementations.
+The first being by Michael Rogers\footnote{https://github.com/akwizgran/basic-english}.
+Rogers' implementation is a program designed to map fingerprints to pseudo-random poems.
+This implementation was empirically evaluated in work by Dechand \textit{et al.} that was discussed in the previous section and in their paper was considered a sentence generator.
 
@@
 This leaves a previously mentioned research gap for anything focusing primarily on the security and usability of encoding schemes such as words, or sentences.
+
+\textbf{TODO: } Need to include a statement expressing the overall gaps in the literature

### 2019-05-25 Papers/Notes_TeX/pages/paper_notes.tex
Changes; - More content to the literature review

@@
 Initial results show promising results for hypen delimitations etc alongside improved user impressions
+
+\newpage
+
+\section{Loud and Clear: Human-Verifiable Authentication Based on Audio}
+
+Paper is in the context of secure device pairing. The paper proposes the use of Loud-and-Clear which uses text to speech to vocalise a robust english like sentence derived from a public key
+
+"Stajano and Anderson proposed a method
+for establishing keys by means of a link created through physical contact [9]."
+
+``A number of efforts have been made to involve a human user in the secondary channel in order to manually verify/compare
+keys (or hashes thereof) including [24, 11, 12] and [21].''
+
+CHECK: Manual authentication for wireless devices.
+
+``system represents a cryptographic hash as a series of six short (up to four-
+letter) words'' - N. Haller. Rfc1760: The s/key one-time password system, 1995.
+
+System truncates the hash and encodes into 10-bit sections.
+
+The system is based of MadLib sentences that are used mainly as amusment for children where gaps in text are filled with nouns
+
+The effort placed into making an order for the wordlist is similar to that of PGPfone. They effectively want to make sure that one bit change, results in a completely distinct word
+
+The paper is not backed up by any empirical data and is just a technical description on the system. It included just a performance analysis.
+
+\newpage
+
+\section{Whole-Word Phonetic Distances and the PGPfone Alphabet}
+
+PGPfones designed solution was the development of a wordless based of military NATO codes.
+
+The authors used Moby Pronunciator database of nearly 200,000 word/pronunciation pairs.
+
+Use-case for these findings are when verification needs to occur over a auditory line.
+
+Mentions on potential further work in the emprical evaluation of these points
+
+TODO: An analysis of perceptual confusions among some English consonants

### 2019-05-26 Literature_Review/pages/review_content.tex
Changes; - Spelling and grammer mistakes checked and corrected

@@
 Current research in ways to represent and validate fingerprints has almost exclusively focused on the usability of such schemes.
-The following section will individually discuss available research findings alongside a overall comparison of the research recommendations.
+The following section will individually discuss available research findings alongside an overall comparison of the research recommendations.
 
-The first work in this area was performed by Hsu-Chun Hsiao, \textit{et. al.} in their paper: \textit{A Study of User-Friendly Hash Comparison Schemes}\cite{hsiao2009study} in around 2009.
-
+The first work in this area was performed by Hsu-Chun Hsiao, \textit{et. al.} in their paper: \textit{A Study of User-Friendly Hash Comparison Schemes}\cite{hsiao2009study} in around 2009. \\
 The aim of the study was to provide the first insight into the best encoding scheme used to represent a hash fingerprint.
@@
 Hsu-Chun Hsiao \textit{et al.} also provided two categories of similarities; ``hard'' and ``easy''.
-These were designed to be worst and best case respectively.
+These were designed to be the worst and best case respectively.
 As a final aim and the reason for the inclusion of Chinese, Korean and Japanese characters was to research if being a native speaker assists the user in distinguishing subtle differences between encodings in the respective language.
@@
 This is extremely low in comparison to similar research.
-However, this can be attributed to the age of the paper due to its 10 year age and the time of writing.
+However, this can be attributed to the age of the paper due to its 10 year age at the time of writing.
 
-The authors decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes) was due to their similarity to Base32 and their well known deficiencies.
+The authors' decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes) was due to their similarity to Base32 and their well-known deficiencies.
 This is not consistent with available research.
@@
 
-Overall, findings from the paper showed that age and gender does not affect the accuracy of the scheme, however younger participants were significantly faster. \\
+Overall, findings from the paper showed that age and gender do not affect the accuracy of the scheme, however, younger participants were significantly faster. \\
 The paper recommends Base32, Random Art, T-Flag or their own improvement; Flag Ext.
-These encoding recommendations were also supplemented with a review of requirements required by these schemes.
+These encoding recommendations were also supplemented with a review of the requirements required by these schemes.
 The recommendation of graphical encoding schemes is inconsistent with alternative literature, where most other papers have found graphical encodings easy to use but insecure.
@@
 For comparison methods that paper looked into Compare-and-Confirm, Compare-and-Select, Compare-and-Enter and Barcode scanning.
-This set includes the most common ways of comparison acording to available research.
+This set includes the most common ways of comparison according to available research.
 Alongside this, the paper reviews Numerical, Alphanumerical, Word, Sentences, Images, Melodies and Sound (Numerical/Alphanumerical).
@@
 
-In terms of empirical data gathered by the paper, they reviewed time completed to review the representation and the number of security and non-security related errors.
-Further more, the authors also collected user opinion on ease-of-use, satisfaction and confidence of the reviewed schemes.
+In terms of empirical data gathered by the paper, they reviewed the time completed to asses the representation and the number of security and non-security related errors.
+Furthermore, the authors also collected user opinion on ease-of-use, satisfaction and confidence of the reviewed schemes.
 The overall schemes were then quantified using a single metric known as the Single Usability Metric (SUM)\cite{sauro2005method}.
 This provides a quick way to rank and compare the schemes, thus improving the usability of the results.
-However, the one apparent downside to the experimental side of the study is 40 participants enrolled.
-This in comparison to other studies is one of the smallest size of enrolment and thus, puts a possible limit on the accuracy and applicability of the obtained results.
+However, the one apparent downside to the experimental side of the study is the 40 participants enrolled.
+This in comparison to other studies is one of the smallest sizes of enrolment and thus, puts a possible limit on the accuracy and applicability of the obtained results.
 
@@
 \\
-In terms of encoding schemes the paper ranked Numerical, Alphanumerical and Words as the top three encoding schemes (These were all with Compare-and-Confirm).
+In terms of encoding schemes, the paper ranked Numerical, Alphanumerical and Words as the top three encoding schemes (These were all with Compare-and-Confirm).
 This took into consideration the usability and security of the scheme.
@@
 
-In conclusion, this paper provided a highly comprehensive review of all the aspects of human fingerprint verification, where it reviewed all the elements involved in the human fingerprint verification.
-The only limitation of the paper is the size of the participants enrolled.
+In conclusion, this paper provided a highly comprehensive review of all the aspects of human fingerprint verification, where it reviewed all the elements involved in the process.
+The only limitation of the paper is the size of the participants enrolled for the study.
 
-A paper by Ersin Uzun \textit{et al.} exclusively reviewed comparison methods.
-This is performed in the context of ``Secure device pairing'' and thus some comparison schemes are tested that are not relevant in a fingerprint comparison context, for example:  ``Choose-and-Enter'' (A participant chooses a passphrase from an available list and enters it into to the other device).
-Thus, only relevant comparison scheme and their results have been extracted and compared.
+A paper by Ersin Uzun \textit{et al.}\cite{uzun2007usability} exclusively reviewed comparison methods.
+This is performed in the context of ``Secure device pairing'' and thus some comparison schemes are tested that are not relevant in a fingerprint comparison context, for example  ``Choose-and-Enter'' (A participant chooses a passphrase from an available list and enters it into the other device).
+Thus, the only relevant comparison scheme and their results have been extracted and compared.
 
 The relevant comparison methods tested were, Compare-and-Confirm, Compare-and-Select and Compare-and-Enter.
-These are almost exactly the same encoding schemes assesed in the relevant research literature.
+These are almost exactly the same encoding schemes assessed in the relevant research literature.
 The paper also had two rounds of experiments including 40 participants each where changes were made to UX and format between these studies.
 
-Due to the ``Secure device pairing'' context the paper was written under, consideration needs to be made into the strings encoded.
+Due to the ``Secure device pairing'' context, the paper was written under, consideration needs to be made into the strings encoded.
 Due to secure device pairing commonly utilising Short Authentication Strings (SAS) the paper only reviewed encodings of 4 digit long strings.
@@
 
-Between the two rounds the authors dropped Confirm-and-Enter due to it low usability and over similarity to a similar scheme "Copy" used for passphrase verification.
+Between the two rounds, the authors dropped Confirm-and-Enter due to its low usability and over similarity to a similar scheme "Copy" used for passphrase verification.
 The low rating for Confirm-and-Enter is in contrast with research performed by Kainda \textit{et al.}\cite{kainda2009usability} They ranked Confirm-and-Enter as the 2nd most usable system.
@@
 The same trend for Confirm-and-Select with it reducing its FER from 12.5\% to 5\%.
-With the changes the participants perceived the systems as easy to use.
-The authors therefore recommended Compare-and-Confirm as the overall best choice for comparison methods.
+With the changes, the participants perceived the systems as easy to use.
+The authors, therefore, recommended Compare-and-Confirm as the overall best choice for comparison methods.
 Again, comparing this word to the most similar work done by Kainda \textit{et al.}\cite{kainda2009usability} this is consistent with their findings where they ranked Compare-and-Confirm as the most secure comparison method.
@@
 This paper is limited in terms of the short strings compared, the different overall research aim and the size of the number of participants used in the studies.
-In terms of security of the schemes the results were constant with that of alternative research but clashed when usability was considered.
+In terms of security of the schemes, the results were consistent with that of alternative research but clashed when usability was considered.
 This, however, may be due to the differing use-cases of the comparison methods and the sizes of strings being compared.
 
-Work by Dechand Sergej, \textit{et al.}\cite{dechand2016empirical} empirically investigated the usability of 4 distinct textual representations evaluated with a experiments involving a total of 1047 participant.
+Work by Dechand Sergej, \textit{et al.}\cite{dechand2016empirical} empirically investigated the usability of 4 distinct textual representations evaluated with an experiment involving a total of 1047 participants.
 The textual representations were: Alphanumeric, Numeric, Words and Sentences.
@@
 Other references made within the paper touch upon the vulnerabilities and usability issues present with the way humans interact with the security systems.
-Example of these are studies showing humans find it difficult to comprehend long and "meaningless" strings and the lack of actual comparison performed by users in live scenarios.
+Example of these are studies showing humans find it difficult to comprehend long and ``meaningless" strings and the lack of actual comparison performed by users in live scenarios.
 These are, however, acknowledged as limitations in the later stages of the paper.
@@
 Overall, findings from the paper state that conventional encodings such as Hexadecimal and Base32 perform worse than all other alternatives in a realistic threat model with over 10\% of users failing to detect an attack on these encoding schemes.
-The recommendations of the authors is to to replace these encoding schemes with Words or Sentences due to their very high success rate and high usability scores.
-The performance of the Alphanumerical encoding schemes is relatively consistent with the literature, however, it is hard to say conclusively due to the small number and lack of visual encoding schemes reviewed making it hard to place alphanumerical encodings in an overall rating.
+The recommendations of the authors are to replace these encoding schemes with Words or Sentences due to their very high success rate and high usability scores.
+The performance of the Alphanumerical encoding schemes is relatively consistent with the literature, however, it is hard to say conclusively due to the small number of total schemes assessed and lack of visual encoding schemes making it hard to place alphanumerical encodings in an overall rating.
 
-J Tan \textit{et al.} work is very similar to that of the research already discussed.
+J Tan \textit{et al.}\cite{tan2017can} work is very similar to that of the research already discussed.
 8 distinct fingerprint representations were tested with over 661 participants.
@@
 The target security level chosen was an entropy of 160-bits.
-This is very high level of security and allows for the papers results to be effectively ``future-proofed''.
+This is a very high level of security in comparison to alternative literature.
 Alongside this, the paper defined attack strengths of an average $2^{60}$ with other specific use-cases for lower and higher attacker strength.
@@
 This performance with graphical representations is consistent with the available literature apart from the positive performance of OpenSSH.
-The results of different modes of comparison was highly consistent with other studies where again the recommendation was to not use Compare-and-Select as its performance across the board was below even basic levels of security.
+The results of different modes of comparison were highly consistent with other studies where again the recommendation was to not use Compare-and-Select as its performance across the board was below even basic levels of security.
 
-\textbf{TODO: } Summarise research section
+\subsection{Topic conclusion}
 
-\section{Fingerprint encoding schemes}
-Another area of research is investigation into the actual physical encodings of the hash digest.
+In conclusion for this section, there has been extensive work in the investigation of the usability of textual and visual encoding schemes alongside methods of comparison.
+There are mixed opinions about visual representations, however, the majority defines them as easy to use but severely lacking in security.
+Research on textual representations, however, is in agreement; natural language based encodings such as words or sentences provide some of the highest usability and security over the baseline performance of alphanumerical encodings.
+The literature also concurs on the use of Compare-and-Confirm as the best method of comparing fingerprints overall, with Compare-and-Select being highlighted for its poor security and usability.\\
+The starkest limitations of the literature are the range of participant and encoding entropy, where at its worst only 22-bits of entropy were tested.
+Another limitation is the scant amount of research solely investigating modes of comparison, where the literature only contains two papers with this research exclusive research aim.
+Even these limitations, as a whole the literature on this topic has provided a relatively comprehensive and coherent view on the usability of textual and visual hash encoding schemes.
+
+\section{Fingerprint representation schemes}
+Another area of research is investigations into the actual physical encodings of the hash digest.
 This section will briefly discuss the current research available on the creation and security of actual encoding schemes.
-The actual details of operation of the schemes are outside the scope of this literature review, therefore, minimal attention will be allocated to these details.
+The actual details of the operation of the schemes are outside the scope of this literature review, therefore, minimal attention will be allocated to these details.
 
@@
 in the creation of their scheme ``Random Art" in 1999.
-The motivation for creating such a scheme was the perceived flaws in the ways humans verify information and compare written information.
+The motivation for creating such a scheme was the perceived flaws in the ways humans verify and compare written information.
 As mentioned in previous sections visual encoding schemes have been shown to have mixed success, with low security being one of their most alarming flaws.
-This research laid the foundation for further work in analysing the security of visual encoding schemes (as discussed in the previous section) to the creation of new schemes.
+This research laid the foundation for further work in analysing the security of visual encoding schemes (as discussed in the previous section).
 
-Further research into creation of unique visual hash schemes have been performed by C Ellison \textit{et al.} \cite{ellison2003public} (Flag), Yue-Hsun Lin \textit{et al.}\cite{lin2010spate} (T-Flag) and work by MM Olembo \textit{et al.}\cite{olembo2013developing}.
+Further research into the creation of unique visual hash schemes have been performed by C Ellison \textit{et al.} \cite{ellison2003public} (Flag), Yue-Hsun Lin \textit{et al.}\cite{lin2010spate} (T-Flag) and work by MM Olembo \textit{et al.}\cite{olembo2013developing}.
 Each publication has provided a new way to visually represent a key fingerprint.
-Alongside the accademic literature there are more informally presented methods of visual fingerprints such as Unicorns\footnote{https://unicornify.pictures/} and Robots\footnote{https://github.com/e1ven/Robohash} This list is by no means exhaustive but is used to depict amount of research and work invested into this topic.
+Alongside the academic literature, there are more informally presented methods of visual fingerprints such as Unicorns\footnote{https://unicornify.pictures/} and Robots\footnote{https://github.com/e1ven/Robohash}.
+This list is by no means exhaustive but is used to depict the amount of research and work invested into graphical hash representations.
 
@@
 The authors claim that the use of the algorithm in OpenSSH is only heuristically defined and there is a need for a formal proof of its security.
-
+\\
 The paper proposed a number of ways to generate similar fingerprints.
-The methods proposed were: Naive brute force, graph theory methods, and brute force of a full visual set.
-They were able to produce only very basic results and have proposed a large amount of potential further work.
-Since the papers publication in 2009, there seems to have been no publications building on the work of the authors.
-This highlights a current gap in the available literature.
+The methods proposed were: Naive brute force, Graph Theory, and brute force of a full visual set.
+They were only able to produce only very basic results and have proposed a large amount of potential further work.
+Since the paper's publication in 2009, there seems to have been no research building on the work of the authors.
+This highlights the current gap in the available literature.
 
@@
 This research aim is to improve the secure device pairing process of comparing two numerical values.
-The devices used (Nokia 6030b - Mid range devices at the time of publication) and short SAS compared results in findings that only slightly applicable in a fingerprint comparison context.
+The devices used (Nokia 6030b; Mid-range devices at the time of publication) and short SAS compared results in findings that are not directly applicable in a fingerprint comparison context.
 
@@
 \cite{juola1996whole} and their work in generating a word list where phonetic distinctiveness was prioritised.
-The inital sampling of words was taken from the Grady Ward's Moby Pronunciator that contains a huge list of word/pronunciation pairs.
 Each word is mapped to one byte where the unique aspect of the word list is the separation of ``even'' and ``odd'' words where even byte positions sample from the even list and odd from the odd list.
@@
 
-Overall the paper provides a foundation for formalising the creation of an effective wordlists.
-A limitation, however, is the lack of empirical data gathered on the effectiveness of the word list.
-This was evaluated later by the work of Dechand \textit{et al.}
+Overall the paper provides a foundation for formalising the creation of effective wordlists.
+A limitation is the lack of empirical data gathered on the effectiveness of the word list.
+However, this was later evaluated in work by Dechand \textit{et al.}
 \cite{dechand2016empirical} and shown to be an effective encoding scheme.
 
-\textbf{TODO: } Add Loud and Clear: Human-Verifiable Authentication Based on Audio
+Other research of note is work by M.
+Goodrich \textit{et al.}\cite{goodrich2006loud} called \textit{Loud and Clear: Human-Verifiable Authentication Based on Audio}.
+As the name suggests the authors were researching ways to improve current methods of secure device pairing.
+The unique aspect of this work is the use of a Text-to-Speech system reading out syntactically correct English sentences.
+The sentences are based on a MadLibs\footnote{https://en.wikipedia.org/wiki/Mad\_Libs} where static placeholders were replaced with potential words.\\
+The work into a potential wordlist can be seen as an extension to the work performed by Juola and Zimmermann\cite{juola1996whole} as they aimed to emulate the techniques used in PGPfone.
+The paper's finding are limited by the lack of empirical data backing up claims made by the author as the systems performance and security are only theoretically assessed.
 
-Aside from this research there has been more informal implementations.
+Aside from this research, there have been further implementations.
 The first being by Michael Rogers\footnote{https://github.com/akwizgran/basic-english}.
 Rogers' implementation is a program designed to map fingerprints to pseudo-random poems.
-This implementation was empirically evaluated in work by Dechand \textit{et al.} that was discussed in the previous section and in their paper was considered a sentence generator.
+This implementation was again, empirically evaluated by Dechand \textit{et al.}\cite{dechand2016empirical}.
+Older work by N.
+Haller with the S/KEY\cite{haller1995s} shows the implementation of a system designed to represent a hash as a series of six short words.
+However, this system is designed for a one-time-password purpose and only provides word mappings for basic human usability of the password and not within a fingerprint verification context.
+Therefore, the wordlist has not been designed with pronounceability in mind.
+\\
+A very recent implementation of a word list can be found in Pretty Easy Privacy (pEp) implementation of TrustWords\footnote{https://tools.ietf.org/html/draft-birk-pep-trustwords-03}.
+The unique aspect of TrustWords is its mapping of words to 16-bits.
+In comparison to other literature, this is the highest number of bits-per-word seen.
+Full mappings (no duplication of words) would, therefore, require $2^{16}$ words.
+This is arguably higher than most users vocabulary.
+This deviation from the norm has not been currently backed up by research.
+This, therefore, highlights a gap in the current literature.
+
+\section{Topic conclusion}
 
 In conclusion to this topic, the current research has primarily focused on the research and creation of visual representations.
-This leaves a previously mentioned research gap for anything focusing primarily on the security and usability of encoding schemes such as words, or sentences.
-
-\textbf{TODO: } Need to include a statement expressing the overall gaps in the literature
+Research for textual fingerprints is fragmented and incomplete with work Juola and Zimmermann
+\cite{juola1996whole} and M.
+Goodrich \textit{et al.}\cite{goodrich2006loud} providing meaningful research to build upon in terms of word a sentence based encodings.
+The fragmentation of this research leaves room for further work into this topic area.
+Alongside this, findings from the previous sections research shows that human language based encodings provided the best usability and, therefore, should be a target for further research looking to improve upon security and usability.

### 2019-05-27 Literature_Review/pages/review_content.tex
Changes; - Added more Literature review information - Moved papers - Added papers

@@
-\section{Research questions}
+\section{Possible research questions}
 
@@
 
-\subsection{Topic conclusion}
+\subsubsection{Topic conclusion}
 
@@
 
-\section{Fingerprint representation schemes}
+\subsection{Fingerprint representation schemes}
 Another area of research is investigations into the actual physical encodings of the hash digest.
@@
 
-\section{Topic conclusion}
+\subsubsection{Topic conclusion}
 
@@
 Alongside this, findings from the previous sections research shows that human language based encodings provided the best usability and, therefore, should be a target for further research looking to improve upon security and usability.
+
+\section{Attacks on fingerprint verification}
+This area of research studies ways to physically execute attacks on fingerprint encoding schemes.
+This differs from previously examined work due to papers discussing the performance and fallibility of encoding schemes simulated the attack without consideration for how the attack would be performed.
+
+Research in this area is scant, with lots of research attention being directed towards the security of Man-in-the-Middle (MITM) attacks and not the encoding schemes themselves.
+
+Research in 2002 by Konrad Rieck\cite{rieck2002fuzzy} is the first formalisation of attacks on fingerprint representations.
+The paper titled \textit{``Fuzzy Fingerprints Attacking Vulnerabilities in the Human Brain''}
+aimed to look into ways users check hexadecimal encoded OpenSSH fingerprint representations.
+The author created an elegant way to `weight' more important chunks of the digest.
+The bytes furthest to the right and left of the digests provided the highest weight.
+The weight was the smallest in the centre of the digest.
+This provides a way to score digests and determine the best partial collisions found.
+For example with the target fingerprint: \verb|9F23| a partial match \verb|9313| is given a score of 45\% even though only two characters were matching.
+This is due to the weightings.
+
+The paper contains an implementation with a ``1.2GHz CPU'' being able to obtain 130,000 H/s (With MD5).
+In comparison to this, a mid-range Intel i5-3320M CPU can today obtain 111,700,000 MD5 H/s shows that the results obtained from the paper are not applicable today.
+However, even with the low hash rate, the author was able to obtain some promising results.
+Figure~\ref{ref:fuzz} contains the best example used.
+
+\begin{figure}[!h]
+    \begin{center}
+        \verb|TARGET: d6:b7:df:31:aa:55:d2:56:9b:32:71:61:24:08:44:87|
+        \verb|MATCH:  d6:b7:8f:a6:fa:21:0c:0d:7d:0a:fb:9d:30:90:4a:87|
+    \end{center}
+    \caption{Best match obtained after a few minutes of hashing}
+    \label{ref:fuzz}
+\end{figure}
+
+Overall the paper shows an interesting way to create partial fingerprint matches but is not quantified by any empirical evidence gathered on real world users.
+This, therefore, leaves gaps in the coverage of this literature.
+
+The only other relevant research on this topic is the work by M 
+Shirvanian \textit{et al.}\cite{shirvanian2014wiretapping} 
+and their paper \textit{``Wiretapping via Mimicry: Short 
+Voice Imitation Man-in-the-Middle Attacks on Crypto 
+Phones''}. In this paper, the authors develop a way to 
+impersonate users when authenticating 
+Short-authentication-Strings (SAS) in pairing of 
+Crypto-phones. To achieve this impersonating they propose 
+two methods: ``Short voice reordering attack'' where an 
+arbitrary SAS string is recreated by re-ordering snipped 
+obtains from eavesdropping a previous connection
+and ``Short voice morphing attacks'' whereby the use of 
+previously eavesdropped audio snippets the attacker can
+morph their own voice to match that of the victim. With 
+these methods, they aimed to attack encodings of Numbers, 
+PGP word list (previously discussed work by Juola and 
+Zimmermann \cite{juola1996whole}) and MadLib (M. Goodrich 
+\textit{et al.}\cite{goodrich2006loud} work also 
+previously discussed). The effectiveness of these attacks 
+were evaluated with a study involving 30 participants.
+
+Results from the paper show the effectiveness of these 
+methods. Compared to the baseline of the attacker's voice 
+replacing the victim where this performed with a 
+\textasciitilde18\% success rate. Morphing gained an 
+overall success rate of 50.58\% and Reordering a very 
+impressive 78.23\% success rate. Showing that these 
+attacks provide an improvement on top of the naive implementation.
+
+One of the biggest limitations addressed by the authors 
+was the reduction in success rates as the size of the 
+authentication string grew. The morphing and reordering 
+attacks become increasingly ineffective as the user has 
+longer to detect imperfections. This is not quantified by 
+the author and the extent of this degradation is never 
+empirically discussed. Therefore, the results from this 
+study are only effective and applicable in a SAS context.
+
+\subsubsection{Topic Conclusion}
+Overall the literature for this subtopic remains sparse and incomplete.
+Further suggested work could look into the feasibility of generating partial collisions for all textual representations alongside quantified effectiveness on users.
+With the possibility to concentrate on a few selected implementations.
+The work would aim to focus on the various physical methods used and their feasibility.
+This is one area the previous literature has failed to cover and has only theoretically quantified attacker strength without consideration for the actual real-world cost of these attacks.
+
+\section{Overall Summary}
+
+\textbf{TODO: } Create an overall summary of all the gaps identified

### 2019-05-27 Papers/Notes_TeX/pages/paper_notes.tex
Changes; - Added more Literature review information - Moved papers - Added papers

@@
 TODO: An analysis of perceptual confusions among some English consonants
+
+\newpage
+
+\section{Wiretapping via Mimicry: Short Voice Imitation
+Man-in-the-Middle Attacks on Crypto Phones}
+
+The aim of the paper is to simulate a MITM attack on SAS and the voice channel used to authenticate
+
+``Short voice reordering attack'' builds arbitrary SAS
+strings in a victim’s voice by reordering previously eavesdropped SAS strings spoken by the victim.
+
+called the ``short voice morphing attack;;, builds arbitrary SAS strings in a victim’s voice from a few previously eavesdropped sentences (less
+than 3 minutes) spoken by the victim.
+
+Is attempting to prove the assumption that "Mallory" being in control of the channel can controls Communications but cannot impersonate alice or bob.
+
+Paper showed, that it is very possible to successfully attack SAS strings. Authors do comment on their difficulty in generating longer strings i.e. longer hash digests
+
+Findings:
+\begin{itemize}
+    \item Success is more likely with shorter strings
+    \item Showed that with 80\% success participants can distinguish a different voice from a familiar voice
+    \item Their morphed attack was overall just above 50\% however, their reordering attack had almost 80\% success rate
+    \item Both attacks were above the baseline of a different voice. I.e. the case of Mallory just replacing the audio with their voice.
+\end{itemize}

### 2019-05-27 Literature_Review/pages/review_content.tex
Changes; - Organised paper notes - Added more context to lit' review - Corrections made to lit' review

@@
 As a final aim and the reason for the inclusion of Chinese, Korean and Japanese characters was to research if being a native speaker assists the user in distinguishing subtle differences between encodings in the respective language.
-
 The entropy of encodings ranged from 22-bits to 28-bits.
 This is extremely low in comparison to similar research.
-However, this can be attributed to the age of the paper due to its 10 year age at the time of writing.
-
+However, this can be attributed to the age of the paper.
+\\
 The authors' decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes) was due to their similarity to Base32 and their well-known deficiencies.
 This is not consistent with available research.
-For example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''} it was shown numerical representations performed better than that of Base32.
+For example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}\cite{dechand2016empirical} it was shown numerical representations performed significantly better than that of Base32.
 
-Overall, findings from the paper showed that age and gender do not affect the accuracy of the scheme, however, younger participants were significantly faster. \\
+Findings from the paper showed that age and gender do not affect the accuracy of the scheme, however, younger participants were significantly faster. \\
 The paper recommends Base32, Random Art, T-Flag or their own improvement; Flag Ext.
@@
 In terms of language comprehension; being able to speak the language assists in the ability to discern the differences between hard pairs.
-Knowledge of the language subsequently did not help with easy pairs.
+Subsequently, knowledge of the language did not help with easy pairs.
 
@@
 This study was comprehensive and assessed a wide variety of concepts.
-This is one of the few papers in the literature that assessed the way to compare representations alongside the representations themselves.
-
-For comparison methods that paper looked into Compare-and-Confirm, Compare-and-Select, Compare-and-Enter and Barcode scanning.
+This is one of the few papers in the literature that assessed the way to compare encodings alongside the representations themselves.
+For comparison methods the paper looked into ``Compare-and-Confirm'', ``Compare-and-Select'', ``Compare-and-Enter'' and ``Barcode'' scanning.
 This set includes the most common ways of comparison according to available research.
-Alongside this, the paper reviews Numerical, Alphanumerical, Word, Sentences, Images, Melodies and Sound (Numerical/Alphanumerical).
+Alongside this, the paper reviews Numerical, Alphanumerical, Words, Sentences, Images, Melodies and Sound (Numerical/Alphanumerical).
 Again, this in comparison to similar literature is highly comprehensive.
@@
 However, the one apparent downside to the experimental side of the study is the 40 participants enrolled.
-This in comparison to other studies is one of the smallest sizes of enrolment and thus, puts a possible limit on the accuracy and applicability of the obtained results.
+This is one of the smallest sizes of enrolment in the literature and thus, puts a possible limit on the accuracy and applicability of the obtained results.
 
-Overall, if usability is the only consideration the paper ranked the comparison methods like so: Compare-and-Confirm, Compare-and-Enter, Compare-and-Select and Barcode.
-If, however, the consideration of security alongside usability is required the best is Compare-and-Enter, Barcode, Compare-and-Confirm and Compare-and-Select.
+Overall, if usability is the only consideration the paper ranked the comparison methods: Compare-and-Confirm, Compare-and-Enter, Compare-and-Select and Barcode.
+If, however, the consideration of security alongside usability is required the best is: Compare-and-Enter, Barcode, Compare-and-Confirm and Compare-and-Select.
 Research has been limited in this area of modes of comparison, however, the results from this paper are consistent with the alternative literature.
@@
 This is performed in the context of ``Secure device pairing'' and thus some comparison schemes are tested that are not relevant in a fingerprint comparison context, for example  ``Choose-and-Enter'' (A participant chooses a passphrase from an available list and enters it into the other device).
-Thus, the only relevant comparison scheme and their results have been extracted and compared.
+Thus, only relevant comparison scheme and their results have been extracted and compared.
 
-The relevant comparison methods tested were, Compare-and-Confirm, Compare-and-Select and Compare-and-Enter.
+The relevant comparison methods tested were, Compare-and-Confirm, 
+Compare-and-Select and Compare-and-Enter.
 These are almost exactly the same encoding schemes assessed in the relevant research literature.
 The paper also had two rounds of experiments including 40 participants each where changes were made to UX and format between these studies.
+Due to the ``Secure device pairing'' context, consideration needs to be made into the actual strings being encoded.
+Due to secure device pairing commonly utilising Short Authentication Strings (SAS) the
+paper only reviewed encodings of 4 digit long strings. This, therefore,limits the applicability of the results in comparison to other fingerprint encoding literature.
 
-Due to the ``Secure device pairing'' context, the paper was written under, consideration needs to be made into the strings encoded.
-Due to secure device pairing commonly utilising Short Authentication Strings (SAS) the paper only reviewed encodings of 4 digit long strings.
-This, therefore, limits the applicability of the results to fingerprint encoding.
-This will be considered later when comparing the results to alternative literature.
-
-Between the two rounds, the authors dropped Confirm-and-Enter due to its low usability and over similarity to a similar scheme "Copy" used for passphrase verification.
+Between the two rounds, the authors dropped ``Confirm-and-Enter'' due to its low usability and over similarity to a similar scheme called ``Copy'' (used for passphrase verification).
 The low rating for Confirm-and-Enter is in contrast with research performed by Kainda \textit{et al.}\cite{kainda2009usability} They ranked Confirm-and-Enter as the 2nd most usable system.
@@
 The same trend for Confirm-and-Select with it reducing its FER from 12.5\% to 5\%.
-With the changes, the participants perceived the systems as easy to use.
-The authors, therefore, recommended Compare-and-Confirm as the overall best choice for comparison methods.
-Again, comparing this word to the most similar work done by Kainda \textit{et al.}\cite{kainda2009usability} this is consistent with their findings where they ranked Compare-and-Confirm as the most secure comparison method.
+The authors, therefore, recommended ``Compare-and-Confirm'' as the overall best choice for comparison methods.
+Again, comparing this word to the most similar work done by Kainda \textit{et al.}\cite{kainda2009usability} this is consistent with their findings where they ranked ``Compare-and-Confirm'' as the most secure comparison method.
 
@@
 In terms of security of the schemes, the results were consistent with that of alternative research but clashed when usability was considered.
-This, however, may be due to the differing use-cases of the comparison methods and the sizes of strings being compared.
+This, however, may be due to the differing use-cases of the comparison methods.
 
-Work by Dechand Sergej, \textit{et al.}\cite{dechand2016empirical} empirically investigated the usability of 4 distinct textual representations evaluated with an experiment involving a total of 1047 participants.
+Work by Dechand \textit{et al.}\cite{dechand2016empirical} empirically investigated the usability of 4 distinct textual representations evaluated with an experiment involving a total of 1047 participants.
 The textual representations were: Alphanumeric, Numeric, Words and Sentences.
@@
 This is a common theme that appears in the majority of the reviewed papers.
-
 Other references made within the paper touch upon the vulnerabilities and usability issues present with the way humans interact with the security systems.
-Example of these are studies showing humans find it difficult to comprehend long and ``meaningless" strings and the lack of actual comparison performed by users in live scenarios.
+Examples of these are studies showing humans find it difficult to comprehend long and ``meaningless" strings and the lack of actual comparison performed by users in live scenarios.
 These are, however, acknowledged as limitations in the later stages of the paper.
@@
 This in comparison to other papers is high and is almost encroaching into the realm of a highly sophisticated attacker.
-Therefore, the lack of consideration for the lower-end of the attack resource spectrum can be considered a limitation of this study.
+Therefore, the lack of consideration for the lower-end of the attack resource spectrum can be considered another limitation.
 
-Overall, findings from the paper state that conventional encodings such as Hexadecimal and Base32 perform worse than all other alternatives in a realistic threat model with over 10\% of users failing to detect an attack on these encoding schemes.
+Summarised findings from the paper state that conventional encodings such as Hexadecimal and Base32 perform worse than all other alternatives in a realistic threat model with over 10\% of users failing to detect an attack on these encoding schemes.
 The recommendations of the authors are to replace these encoding schemes with Words or Sentences due to their very high success rate and high usability scores.
-The performance of the Alphanumerical encoding schemes is relatively consistent with the literature, however, it is hard to say conclusively due to the small number of total schemes assessed and lack of visual encoding schemes making it hard to place alphanumerical encodings in an overall rating.
+The performance of the Alphanumerical encoding schemes is relatively consistent with the literature, however, it is hard to say conclusively due to the small number of total schemes assessed making it hard to place alphanumerical encodings in an overall rating.
 
 J Tan \textit{et al.}\cite{tan2017can} work is very similar to that of the research already discussed.
-8 distinct fingerprint representations were tested with over 661 participants.
-Each representation was tested using Compare-and-Confirm and Compare-and-Select.
+Eight distinct fingerprint representations were tested with over 661 participants.
+Each representation was tested using ``Compare-and-Confirm'' and ``Compare-and-Select''.
 The small difference with this paper is the inclusion of two novel graphical encodings Vash\footnote{https://github.com/thevash/vash} and Unicorns\footnote{https://unicornify.pictures/}.
@@
 Users were recruited via MTurk and assigned an experiment attempting to emulate a real-life condition (Comparison of a fingerprint on a business card).
-The real-world accuracy was one unique element that this paper concentrated on, this was portrayed through the author's attention to detail when designing the experiment.
+The real-world accuracy was one unique element that this paper concentrated on, this was portrayed through the authors' attention to detail when designing the experiment.
 
@@
 This performance with graphical representations is consistent with the available literature apart from the positive performance of OpenSSH.
-The results of different modes of comparison were highly consistent with other studies where again the recommendation was to not use Compare-and-Select as its performance across the board was below even basic levels of security.
+The results of different modes of comparison were highly consistent with other studies where again the recommendation was to not use ``Compare-and-Select'' as its performance across the board was below even basic levels of security.
+
+Further work in the context of secure messaging pairing was produced by M.
+Shirvanian \textit{et al.}\cite{shirvanian2017pitfalls} in 2017.
+This paper was unique for a number of reasons.
+First was to consideration for ``remote-vs-proximity'' pairing where, this is the first consideration of this aspect found in the literature.
+Second, was their studies aim into investigating fingerprint security and usability in a end-to-end encryption context.
+The study compared Numerical, Visual and Auditory representations.
+This is a standard setup for similar studies in the literature.
+QR code verification was also added to the proximity tests.
+They split the variance of attack severity into three levels; one character change, one block change and changes to the entire fingerprint.
+
+The findings from the paper showed a high false negative rate for all the schemes, this is an aspect also missing from the literature.
+Alongside this, results for usability were lower in a remote setting for all the schemes where the author comments on the expected nature of this result.\\
+The paper measured the number of successful attacks in the False Accept Rate (FAR).
+With this in mind images were the most secure method of authentication in the remote setting, but voted as the method with the worst usability.
+This is highly inconsistent with previous work in this area.
+However, this could be due to the unique setting of remote verification resulting in distinct results from user studies.
+Without further work in this area it is difficult to conclusively validate these results.
+In the proximity setting the results were negligible where at most 2.67\% of attacks were successful.
+In summary, this paper provides a unique look into the real-world aspects of fingerprint verification in a end-to-end context providing a unique viewpoint on the usability and possible security of the main fingerprint encoding schemes.
 
@@
 Research on textual representations, however, is in agreement; natural language based encodings such as words or sentences provide some of the highest usability and security over the baseline performance of alphanumerical encodings.
-The literature also concurs on the use of Compare-and-Confirm as the best method of comparing fingerprints overall, with Compare-and-Select being highlighted for its poor security and usability.\\
+The literature also concurs on the use of ``Compare-and-Confirm'' as the best method of comparing fingerprints overall, with Compare-and-Select being highlighted for its poor security and usability.\\
 The starkest limitations of the literature are the range of participant and encoding entropy, where at its worst only 22-bits of entropy were tested.
-Another limitation is the scant amount of research solely investigating modes of comparison, where the literature only contains two papers with this research exclusive research aim.
+Another limitation is the scant amount of research solely investigating modes of comparison, where the literature only contains two papers with this aim.
 Even these limitations, as a whole the literature on this topic has provided a relatively comprehensive and coherent view on the usability of textual and visual hash encoding schemes.
@@
 \cite{juola1996whole} and their work in generating a word list where phonetic distinctiveness was prioritised.
-Each word is mapped to one byte where the unique aspect of the word list is the separation of ``even'' and ``odd'' words where even byte positions sample from the even list and odd from the odd list.
-The effectively creates two sub-word lists.
-The pairing of these word lists were determined through the use of a Genetic algorithm.
-The paper also includes a study on effective measures of linguistic distances of words and provided an in-depth discussion into these areas.
+Each word is mapped to one byte where the unique aspect of the word list is the separation of ``even'' and ``odd'' words where ``even'' byte positions are sample from the even-list and ``odd'' from the odd-list.
+This effectively creates two sub-word lists.
+The pairing of these word lists were determined through the use of a Genetic algorithm with phonetic distance as the metric.
+The paper also includes a study on effective measures of ``linguistic distances'' of words and provided an in-depth discussion into these areas.
 
 Overall the paper provides a foundation for formalising the creation of effective wordlists.
-A limitation is the lack of empirical data gathered on the effectiveness of the word list.
-However, this was later evaluated in work by Dechand \textit{et al.}
-\cite{dechand2016empirical} and shown to be an effective encoding scheme.
+A limitation is the lack of empirical data gathered on the performance.
+However, this was later evaluated in work by Dechand \textit{et al.} \cite{dechand2016empirical} and shown to be an effective encoding scheme.
 
@@
 
-Aside from this research, there have been further implementations.
+Aside from this research, there have been further informal implementations of fingerprint encodings.
 The first being by Michael Rogers\footnote{https://github.com/akwizgran/basic-english}.
@@
 A very recent implementation of a word list can be found in Pretty Easy Privacy (pEp) implementation of TrustWords\footnote{https://tools.ietf.org/html/draft-birk-pep-trustwords-03}.
-The unique aspect of TrustWords is its mapping of words to 16-bits.
+The unique aspect of TrustWords is its mapping of a single word to 16-bits.
 In comparison to other literature, this is the highest number of bits-per-word seen.
-Full mappings (no duplication of words) would, therefore, require $2^{16}$ words.
-This is arguably higher than most users vocabulary.
+Full mappings (no duplication of words) would, therefore, require $2^{16}$ words in the dictionary and arguably is higher than most users vocabulary.
 This deviation from the norm has not been currently backed up by research.
-This, therefore, highlights a gap in the current literature.
+Therefore, highlighting on a gap in the current literature.
 
@@
 The paper contains an implementation with a ``1.2GHz CPU'' being able to obtain 130,000 H/s (With MD5).
-In comparison to this, a mid-range Intel i5-3320M CPU can today obtain 111,700,000 MD5 H/s shows that the results obtained from the paper are not applicable today.
+In comparison to this, a mid-range Intel i5-3320M CPU can today obtain 111,700,000 MD5 H/s shows that the results obtained from the paper are outdated.
 However, even with the low hash rate, the author was able to obtain some promising results.
@@
 arbitrary SAS string is recreated by re-ordering snipped 
-obtains from eavesdropping a previous connection
+obtained from eavesdropping a previous connection
 and ``Short voice morphing attacks'' whereby the use of 
@@
 attacks become increasingly ineffective as the user has 
-longer to detect imperfections. This is not quantified by 
+more time to detect imperfections. This is not quantified by 
 the author and the extent of this degradation is never 
@@
 \section{Overall Summary}
-
 \textbf{TODO: } Create an overall summary of all the gaps identified

### 2019-05-27 Papers/Notes_TeX/pages/can_unicorns.tex
Changes; - Organised paper notes - Added more context to lit' review - Corrections made to lit' review

--- 2019-05-25 Papers/Notes_TeX/pages/paper_notes.tex
@@
-\textbf{TODO:} Need to find papers on study of words are a comparative measure.
-
-Lots of research has been done into the secure pairing of devices with minimal human involvement:
-
-\begin{itemize}
-    \item Using Camera Phones for Human-Verifiable Authentication
-    \item Loud and Clear: Human-Verifiable Authentication Based on Audio
-    \item A human-verifiable authentication protocol using visible laser light
-    \item Secure Device Pairing based on a Visual Channel
-    \item NFC
-    \item Physical contact
-\end{itemize}
-
-\textbf{OVERVIEW} 
-\begin{itemize}
-    \item Lots of research performed on E2E applications (Telegram, WhatsApp etc)
-    \item Lots of study into overall representations of fingerprints
-\end{itemize}
-
 \section{Can Unicorns Help Users Compare Crypto Key Fingerprints}
@@
 \end{itemize}
-
-\newpage
-% \section{An Empirical Study of Textual Key-Fingerprint Representations}
-
-% Study involved 1047 participants evaluating 6 different textual representations on MTurk. The study also includes an evaluation into usability.
-
-% The study has an attacker power of around 80 of 112 bits.
-
-% \begin{itemize}
-%     \item Alphanumerical
-%     \item Numerical
-%     \item Words
-%     \item Sentences
-% \end{itemize}
-
-% More mention to decentralised method finding it hard to find adoption such as Web of Trust and Namecoin ([7, 13, 30])
-
-% References as system called CONIKS and others ([24, 39, 27]) that aim to provided a directory of keys
-
-% States that many systems still rely on fingerprint comparison ([17])
-
-% States that the \textbf{hexadecimal} encoding is used in most systems.
-
-% States again that fingerprint comparison is seldom done in practice ([17, 37])
-
-% Studies have shown that users find it difficult to compare long and "meaningless" strings ([19])
-
-% References to other word lists used. PGP Word list [22] and english word list compiled by K.C. Ogden [31]. The Peerio word list is generated from the most common words in english subtitles.
-
-% Interesting recommendation into the use of \textit{scrypt} [34] and \textit{Argon 2} [3] can be used to shorten the fingerprint length.
-These work slowly and a prevent easy computation of pre-images.
-
-% When generating partial-collision fixing the bits at the start and end has been shown a best practice ([17, 37])
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Overall recommendation is to replace \textbf{hexadecimal} with \textbf{sentence} based encoding
-%     \item Findings show that \textbf{hexadecimal} and \textbf{Base32} perform worse than the other alternatives in realistic threat models.
-With over \textbf{10\%} of users failing to detect attacks with these schemes.
-%     \item According to their study, \textbf{words} and \textbf{sentences} we some of the best methods for avoiding attack
-%     \item Words has the second highest usability ratings second to only sentences
-% \end{itemize}
-
-% \newpage
-% \section{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}
-
-% Paper looks into the positives of secondary channels used to authenticate device pairing.
-Such as device fingerprint comparison.
-It also aims to look into the fact that many studies performed do not take into consideration the aspect of human interaction.
-
-% Total of 30 paid participants were recruited where the experiment simulated a P2P payment system.
-
-% They collected:
-% \begin{itemize}
-%     \item Time to completed the associated process
-%     \item Number of security or non-security related errors
-% \end{itemize}
-
-% And quantified using questionnaires:
-% \begin{itemize}
-%     \item Ease of use with the representation
-%     \item Satisfaction with time spent with a method/representation
-%     \item Participant's confidence with the scheme
-% \end{itemize}
-
-% The paper also tested methods:
-% \begin{itemize}
-%     \item Compare and Confirm
-%     \item Compare and Select
-%     \item Compare and Enter
-%     \item Barcode scanning
-% \end{itemize}
-
-% Representations:
-% \begin{itemize}
-%     \item Numerical
-%     \item Alphanumerical
-%     \item Words
-%     \begin{itemize}
-%         \item Dictionary of 1024 words each mapped to 10-bits
-%     \end{itemize}
-%     \item Sentences
-%     \item Images
-%     \item Melodies
-%     \item Sound (Numerical/Alphanumerical)
-% \end{itemize}
-
-% "People are the weakest link in the security chain" [26]
-
-% Mentions a normal channel as a "Dolev-Yao" channel [5]. This is where an attacker can overhead, delete and modify messages.
-
-% Talks about systems that were secure on paper that ended up in practice being miss-handled to reduce security. One example is with the Russian army in WWI [1]
-
-% Bruce Schneier [27] also argues that systems and involves humans therefore often systems are broken due to improper use.
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Showed for \textbf{usability} methods ranked:
-%     \begin{itemize}
-%         \item Comparing-confirm
-%         \item Typing strings
-%         \item Comparing-select
-%         \item Barcode
-%     \end{itemize}
-
-%     \item Showed for \textbf{combined security} and \textbf{usability} methods ranked:
-%     \begin{itemize}
-%         \item Typing strings
-%         \item Barcodes
-%         \item Comparing-confirm
-%         \item Comparing-select
-%     \end{itemize}
-
-%     Showed that the best methods in terms of the SUM score [24] ranked the top 3 as:
-%     \begin{itemize}
-%         \item Numeric(C\&C)          [73.7]
-%         \item Alphanumerical(C\&C)   [72.5]
-%         \item Words (C\&C)           [70.6]
-%     \end{itemize}
-
-%     Numerical had 0\% security failures, Word 3.3\% and Alphanumerical had a high 13.3\%
-
-%     NOTE: This is a very small sample size.
-% \end{itemize}
-
-% \newpage
-% \section{SafeSlinger: An Easy-to-use and Secure Approach for
-% Human Trust Establishment}
-
-% The aim of SafeSlinger is to solve the issue of key exchange.
-They aim to leverage the initial personal contact of people to facilitate trust.
-To solve the issue of people that would never meet they implement a system of "shared acquaintance"
-
-% Talks about issues with decentralised (PGP [42]) and centralised (SSL CA [27, 34]) key exchange.
-
-% "Tim Berners-Lee has called upon security researchers and professionals to design a public key encryption system for the people [11]"
-
-% Only uses \textbf{24-bits} of a SHA-1 hash of all the exchanged information, \textbf{could this be exploited?}
-
-% \newpage
-% \section{A Study of User-Friendly Hash Comparison Schemes}
-
-% The aim of this study is to provide a study on what hash comparison scheme provides the best accuracy and shortest comparison time.
-
-% The paper also proposes new schemes: An extension to Flag and three asian character representations.
-
-% An interesting aspect is the effort put into the study to link characteristics about the participants, i.e.
-gender or age to how well they perform or rate the usability of the scheme.
-In total they had 436 participants.
-
-% Overall they compare:
-% \begin{itemize}
-%     \item Base32
-%     \item English words
-%     \item Random Art
-%     \item Flag
-%     \item T-Flag
-%     \item Flag ext
-%     \item Chinese, Korean, Japanese characters
-% \end{itemize}
-
-% Key phrase: "We did not use hexadecimal digits because they're similar to Base32 and known to be error prone" [NO REFERENCE].
-This is shown in \textit{``An Empirical Study of Textual Key-Fingerprint Representations''} that this isn't true - ``However, our work shows that numeric representations actually perform significantly better than Base32 and is less error prone.''
-
-% They study also considers the comparison of "easy" and "hard" pairs of hashes.
-Hard is where the hashes are designed to be very similar.
-This is designed to provide a base-line (easy) and a worst-case (hard).
-
-% The paper deals with ranges of entropy of 22-28bits.
-
-% Another system that uses word is the Unmanaged Internet Architecture [4]
-
-% States that users make errors when comparing long strings [11]
-
-% Dicussions are also made into the pre-requirements needed for some of these schemes.
-Random-Art needs a colour display and requires a relativly high computational cost to generate a representation.
-Asian characters require unicode or codec support.
-
-% Paper also touches on ``Additional Benefits'' - the paper talks about the ability to verbally describe the scheme, this is so the encoding scheme can be verified using a channel that does not involve a visual feed such as a telephone conversation
-
-% Overall the paper provides a table of requirements for the schemes with the graphical representations requiring a large number of pre-requirements.
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Source, age and gender have no significant impact on the accuracy across the schemes. But younger participants were significantly faster
-%     \item In general, Base32, Random Art, T-Flag and Flag Ext provide fast and accurate comparisons
-%     \item Comprehension of a language when used as a encoding scheme affects the ability to distinguish hard pairs by a significant amount
-% \end{itemize}
-
-% \newpage
-% \section{Usability Analysis of Secure Pairing Methods}
-
-% Paper is aiming to perform a comparative usability evaluation of \textbf{selection methods} of hash comparisons
-
-% This paper is doing this study in the context of secure device pairing in a diffie-hellman type key exchange.
-However, the results of the study could directly apply to that of hash comparison, however, it must be considered that the comparisons here are for \textbf{very} short strings.
-Around 4-digits
-
-% Comparison methods compared:
-% \begin{itemize}
-%     \item Compare-and-Confirm
-%     \item Select-and-Confirm
-%     \item Copy-and-Confirm
-% \end{itemize}
-
-% The paper also compared to methods of passphrase comparison that weren't relevant.
-
-% Paper also included demographical information in the study, with two round of 40 participants in the usability studies.
-
-% Findings:
-
-% Round 1:
-% \begin{itemize}
-%     \item Copy-and-confirm was percieved as hard to use
-%     \item Copy-and-confirm has the lowest fatal error rate but the longest comparison time and lowest percieved usability
-%     \item The schemes reduced fatal error rate as their comparison times rose
-%     \item Copy-and-confirm had issues with user confusion in terms of use
-% \end{itemize}
-
-% In the second round they only decided to continue with
-
-% \begin{itemize}
-%     \item Compare-and-Confirm
-%     \item Select-and-Confirm
-% \end{itemize}
-
-% They dropped Copy-and-confirm due to its high similarity to the other scheme "Copy" that was being used for passphrase sharing
-
-% The second round included some UI changes that were backed up by external research.
-
-% This round the changes performed on the schemes resulted in much lower fatal error rates.
-However, Select-and-confirm had an unacceptable 5\% error rate.
-Compare-and-confirm had 0\% fatal error rate.
-The was an improvment from 20\% to 0\%.
-
-% Both schemes were again percieved as easy to use
-
-% Overall it was shown that compare-and-confirm was the superior choice.
-
-\newpage
-\section{On the Pitfalls of End-to-End Encrypted Communications: A Study of Remote Key-Fingerprint Verification}
-
-Paper compares the fingerprint verification task in the context of Instant messaging E2E The paper is also choosing to focus on the remote vs proximity ways of comparing fingerprints.
-They aim to study the security and usability of human-centred E2E key verification.
-The study ran with 25 participants.
-
-Seems to be the first study of remote code verification study
-
-Study compares Numerical, Image and verbally spoken codes and QR just for proximity alongside all the other alternatives.
-
-The studies main aim to compare remote to proximity, not compare the various methods
-
-The research is split into two sub-goals: Robustness - looks at the FAR and FRR. User experience and perception - System usability, Comfort, Satisfaction and Adaptability
-
-States that numerical is the one of the most common representations, but out of the chosen methods 50\% use numerical and the rest hexadecimal?
-
-They included 3 level of incorrect codes. One char change, one block and the entire fingerprint
-
-Overall Audio was one of the most secure and easiest to use.
-However results for image based comparisons were not controlled in any way due to the author being unable to access the telegram image generation, this means while the other schemes had controlled restraints the image did not.
-Images was rated the worst.
-
-Findings:
-\begin{itemize}
-    \item High False Acceptance Rate (False Negative) for all code verification methods 
-    \item Results point to low usability in remote code verification settings, aside from audio based verification ever scheme has above 20\% False Rejection Rate (False Positive)
-    \item In proximity settings users were able to detect attacks with minimal error rates
-\end{itemize}
-
-\newpage
-
-\section{The drunken bishop: An analysis of the OpenSSH
-fingerprint visualization algorithm}
-
-The aim of this research is to study the OpenSSH Visual Host Key.
-The authors claim that the scheme was heuristically designed and has very little backing in terms of formal research, this paper aims to create a foundation for this research.
-
-OpenSSH uses MD5 to generate a 128-bit fingerprint of the Server's key, this is then split into 64 2-bit pairs.
-These are then traversed byte wise in a right to left over the bit pairs.
-Each pair defines the direction of travel.
-If the snake reaches a position multiple times a pre define character is added depending on the number of visits (for example, 6 times == "B")
-
-The paper also discusses ways to create collisions:
-
-In conclusive results and more of an inital PoC
-
-\begin{itemize}
-    \item Brute force
-    \item Graph theory
-    \item Brute forcing a visual set
-\end{itemize}
-
-\newpage
-
-\section{Improving the Robustness of Wireless Device
-Pairing Using Hyphen-Delimited Numeric
-Comparison}
-
-In the context of secure device pairing the paper aims to improve the human interaction with number pairing.
-
-Lots of research has gone into Short Authentication String (SAS) numbers ([14], [10], [4])
-
-The research was peformed on very old devices. Nokia 6030b, very out of date and not reflective of anything around at this time.
-
-Usability study looked into Efficiency, Robustness, General Usability
-
-Strange format of keeping the numbers exactly the same but just placing hyphens in the middle. The authors attempted to remedy this by spacing the experiments with a days gap
-
-Study was performed with 40 participants
-
-Very small number of values tested only 5 overall???
-
-Initial results show promising results for hypen delimitations etc alongside improved user impressions

### 2019-05-27 Papers/Notes_TeX/pages/hash_comparisons.tex
Changes; - Organised paper notes - Added more context to lit' review - Corrections made to lit' review

\section{A Study of User-Friendly Hash Comparison Schemes}

The aim of this study is to provide a study on what hash comparison scheme provides the best accuracy and shortest comparison time.

The paper also proposes new schemes: An extension to Flag and three asian character representations.

An interesting aspect is the effort put into the study to link characteristics about the participants, i.e. gender or age to how well they perform or rate the usability of the scheme. In total they had 436 participants.

Overall they compare:
\begin{itemize}
    \item Base32
    \item English words
    \item Random Art
    \item Flag
    \item T-Flag
    \item Flag ext
    \item Chinese, Korean, Japanese characters
\end{itemize}

Key phrase: "We did not use hexadecimal digits because they're similar to Base32 and known to be error prone" [NO REFERENCE]. This is shown in \textit{``An Empirical Study of Textual Key-Fingerprint Representations''} that this isn't true - ``However, our work shows that numeric representations actually perform significantly better than Base32 and is less error prone.''

They study also considers the comparison of "easy" and "hard" pairs of hashes. Hard is where the hashes are designed to be very similar. This is designed to provide a base-line (easy) and a worst-case (hard).

The paper deals with ranges of entropy of 22-28bits.

Another system that uses word is the Unmanaged Internet Architecture [4]

States that users make errors when comparing long strings [11]

Dicussions are also made into the pre-requirements needed for some of these schemes. Random-Art needs a colour display and requires a relativly high computational cost to generate a representation. Asian characters require unicode or codec support.

Paper also touches on ``Additional Benefits'' - the paper talks about the ability to verbally describe the scheme, this is so the encoding scheme can be verified using a channel that does not involve a visual feed such as a telephone conversation

Overall the paper provides a table of requirements for the schemes with the graphical representations requiring a large number of pre-requirements.

\subsection{Findings}
\begin{itemize}
    \item Source, age and gender have no significant impact on the accuracy across the schemes. But younger participants were significantly faster
    \item In general, Base32, Random Art, T-Flag and Flag Ext provide fast and accurate comparisons
    \item Comprehension of a language when used as a encoding scheme affects the ability to distinguish hard pairs by a significant amount
\end{itemize}

### 2019-05-27 Papers/Notes_TeX/pages/improving_robustness.tex
Changes; - Organised paper notes - Added more context to lit' review - Corrections made to lit' review

--- 2019-05-25 Papers/Notes_TeX/pages/paper_notes.tex
@@
-\textbf{TODO:} Need to find papers on study of words are a comparative measure.
-
-Lots of research has been done into the secure pairing of devices with minimal human involvement:
-
-\begin{itemize}
-    \item Using Camera Phones for Human-Verifiable Authentication
-    \item Loud and Clear: Human-Verifiable Authentication Based on Audio
-    \item A human-verifiable authentication protocol using visible laser light
-    \item Secure Device Pairing based on a Visual Channel
-    \item NFC
-    \item Physical contact
-\end{itemize}
-
-\textbf{OVERVIEW} 
-\begin{itemize}
-    \item Lots of research performed on E2E applications (Telegram, WhatsApp etc)
-    \item Lots of study into overall representations of fingerprints
-\end{itemize}
-
-\section{Can Unicorns Help Users Compare Crypto Key Fingerprints}
-
-This paper tested 8 different fingerprint representations with 661 different participants.
-All of these representations are testing using compare-and-confirm (basic comparison process for fingerprints) and compare-and-select (select from a list)
-
-\begin{itemize}
-    \item Hexadecimal
-    \item Alternating vowel/consonant
-    \item Words
-    \item Numbers
-    \item Sentences
-    \item OpenSSH visual host key
-    \item Vash
-    \item Unicorns
-\end{itemize}
-
-The paper also emphasises the attention that has been taken to realism in the experimentation stage.
-
-Talks about long term usability issues with public-key crypto and states fingerprints are a main source of the problem. ([28])
-
-There seems to be mixed findings with compare-and-select and compare-and-confirm ([14, 17])
-
-There has been research into OpenSSH fingerprints and how users interact ([19, 24])
-
-Paper chose to target a security level of 160-bits
-
-Papers attack strengths were $2^{40}$, $2^{60}$ and $2^{80}$
-
-Paper states that MTurk users have been shown to be younger and better educated than the general US population ([15])
-
-\subsection{Findings}
-
-\begin{itemize}
-    \item Graphical representations have mixed success rates (with quick comparison times)
-    \item Recommendations not to use \textbf{compare-and-select}
-    \item \textbf{No method} really provided enough security for high risk situations, they recommend removing users from the loop by using smart phone cameras etc
-\end{itemize}
-
-\newpage
-% \section{An Empirical Study of Textual Key-Fingerprint Representations}
-
-% Study involved 1047 participants evaluating 6 different textual representations on MTurk. The study also includes an evaluation into usability.
-
-% The study has an attacker power of around 80 of 112 bits.
-
-% \begin{itemize}
-%     \item Alphanumerical
-%     \item Numerical
-%     \item Words
-%     \item Sentences
-% \end{itemize}
-
-% More mention to decentralised method finding it hard to find adoption such as Web of Trust and Namecoin ([7, 13, 30])
-
-% References as system called CONIKS and others ([24, 39, 27]) that aim to provided a directory of keys
-
-% States that many systems still rely on fingerprint comparison ([17])
-
-% States that the \textbf{hexadecimal} encoding is used in most systems.
-
-% States again that fingerprint comparison is seldom done in practice ([17, 37])
-
-% Studies have shown that users find it difficult to compare long and "meaningless" strings ([19])
-
-% References to other word lists used. PGP Word list [22] and english word list compiled by K.C. Ogden [31]. The Peerio word list is generated from the most common words in english subtitles.
-
-% Interesting recommendation into the use of \textit{scrypt} [34] and \textit{Argon 2} [3] can be used to shorten the fingerprint length.
-These work slowly and a prevent easy computation of pre-images.
-
-% When generating partial-collision fixing the bits at the start and end has been shown a best practice ([17, 37])
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Overall recommendation is to replace \textbf{hexadecimal} with \textbf{sentence} based encoding
-%     \item Findings show that \textbf{hexadecimal} and \textbf{Base32} perform worse than the other alternatives in realistic threat models.
-With over \textbf{10\%} of users failing to detect attacks with these schemes.
-%     \item According to their study, \textbf{words} and \textbf{sentences} we some of the best methods for avoiding attack
-%     \item Words has the second highest usability ratings second to only sentences
-% \end{itemize}
-
-% \newpage
-% \section{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}
-
-% Paper looks into the positives of secondary channels used to authenticate device pairing.
-Such as device fingerprint comparison.
-It also aims to look into the fact that many studies performed do not take into consideration the aspect of human interaction.
-
-% Total of 30 paid participants were recruited where the experiment simulated a P2P payment system.
-
-% They collected:
-% \begin{itemize}
-%     \item Time to completed the associated process
-%     \item Number of security or non-security related errors
-% \end{itemize}
-
-% And quantified using questionnaires:
-% \begin{itemize}
-%     \item Ease of use with the representation
-%     \item Satisfaction with time spent with a method/representation
-%     \item Participant's confidence with the scheme
-% \end{itemize}
-
-% The paper also tested methods:
-% \begin{itemize}
-%     \item Compare and Confirm
-%     \item Compare and Select
-%     \item Compare and Enter
-%     \item Barcode scanning
-% \end{itemize}
-
-% Representations:
-% \begin{itemize}
-%     \item Numerical
-%     \item Alphanumerical
-%     \item Words
-%     \begin{itemize}
-%         \item Dictionary of 1024 words each mapped to 10-bits
-%     \end{itemize}
-%     \item Sentences
-%     \item Images
-%     \item Melodies
-%     \item Sound (Numerical/Alphanumerical)
-% \end{itemize}
-
-% "People are the weakest link in the security chain" [26]
-
-% Mentions a normal channel as a "Dolev-Yao" channel [5]. This is where an attacker can overhead, delete and modify messages.
-
-% Talks about systems that were secure on paper that ended up in practice being miss-handled to reduce security. One example is with the Russian army in WWI [1]
-
-% Bruce Schneier [27] also argues that systems and involves humans therefore often systems are broken due to improper use.
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Showed for \textbf{usability} methods ranked:
-%     \begin{itemize}
-%         \item Comparing-confirm
-%         \item Typing strings
-%         \item Comparing-select
-%         \item Barcode
-%     \end{itemize}
-
-%     \item Showed for \textbf{combined security} and \textbf{usability} methods ranked:
-%     \begin{itemize}
-%         \item Typing strings
-%         \item Barcodes
-%         \item Comparing-confirm
-%         \item Comparing-select
-%     \end{itemize}
-
-%     Showed that the best methods in terms of the SUM score [24] ranked the top 3 as:
-%     \begin{itemize}
-%         \item Numeric(C\&C)          [73.7]
-%         \item Alphanumerical(C\&C)   [72.5]
-%         \item Words (C\&C)           [70.6]
-%     \end{itemize}
-
-%     Numerical had 0\% security failures, Word 3.3\% and Alphanumerical had a high 13.3\%
-
-%     NOTE: This is a very small sample size.
-% \end{itemize}
-
-% \newpage
-% \section{SafeSlinger: An Easy-to-use and Secure Approach for
-% Human Trust Establishment}
-
-% The aim of SafeSlinger is to solve the issue of key exchange.
-They aim to leverage the initial personal contact of people to facilitate trust.
-To solve the issue of people that would never meet they implement a system of "shared acquaintance"
-
-% Talks about issues with decentralised (PGP [42]) and centralised (SSL CA [27, 34]) key exchange.
-
-% "Tim Berners-Lee has called upon security researchers and professionals to design a public key encryption system for the people [11]"
-
-% Only uses \textbf{24-bits} of a SHA-1 hash of all the exchanged information, \textbf{could this be exploited?}
-
-% \newpage
-% \section{A Study of User-Friendly Hash Comparison Schemes}
-
-% The aim of this study is to provide a study on what hash comparison scheme provides the best accuracy and shortest comparison time.
-
-% The paper also proposes new schemes: An extension to Flag and three asian character representations.
-
-% An interesting aspect is the effort put into the study to link characteristics about the participants, i.e.
-gender or age to how well they perform or rate the usability of the scheme.
-In total they had 436 participants.
-
-% Overall they compare:
-% \begin{itemize}
-%     \item Base32
-%     \item English words
-%     \item Random Art
-%     \item Flag
-%     \item T-Flag
-%     \item Flag ext
-%     \item Chinese, Korean, Japanese characters
-% \end{itemize}
-
-% Key phrase: "We did not use hexadecimal digits because they're similar to Base32 and known to be error prone" [NO REFERENCE].
-This is shown in \textit{``An Empirical Study of Textual Key-Fingerprint Representations''} that this isn't true - ``However, our work shows that numeric representations actually perform significantly better than Base32 and is less error prone.''
-
-% They study also considers the comparison of "easy" and "hard" pairs of hashes.
-Hard is where the hashes are designed to be very similar.
-This is designed to provide a base-line (easy) and a worst-case (hard).
-
-% The paper deals with ranges of entropy of 22-28bits.
-
-% Another system that uses word is the Unmanaged Internet Architecture [4]
-
-% States that users make errors when comparing long strings [11]
-
-% Dicussions are also made into the pre-requirements needed for some of these schemes.
-Random-Art needs a colour display and requires a relativly high computational cost to generate a representation.
-Asian characters require unicode or codec support.
-
-% Paper also touches on ``Additional Benefits'' - the paper talks about the ability to verbally describe the scheme, this is so the encoding scheme can be verified using a channel that does not involve a visual feed such as a telephone conversation
-
-% Overall the paper provides a table of requirements for the schemes with the graphical representations requiring a large number of pre-requirements.
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Source, age and gender have no significant impact on the accuracy across the schemes. But younger participants were significantly faster
-%     \item In general, Base32, Random Art, T-Flag and Flag Ext provide fast and accurate comparisons
-%     \item Comprehension of a language when used as a encoding scheme affects the ability to distinguish hard pairs by a significant amount
-% \end{itemize}
-
-% \newpage
-% \section{Usability Analysis of Secure Pairing Methods}
-
-% Paper is aiming to perform a comparative usability evaluation of \textbf{selection methods} of hash comparisons
-
-% This paper is doing this study in the context of secure device pairing in a diffie-hellman type key exchange.
-However, the results of the study could directly apply to that of hash comparison, however, it must be considered that the comparisons here are for \textbf{very} short strings.
-Around 4-digits
-
-% Comparison methods compared:
-% \begin{itemize}
-%     \item Compare-and-Confirm
-%     \item Select-and-Confirm
-%     \item Copy-and-Confirm
-% \end{itemize}
-
-% The paper also compared to methods of passphrase comparison that weren't relevant.
-
-% Paper also included demographical information in the study, with two round of 40 participants in the usability studies.
-
-% Findings:
-
-% Round 1:
-% \begin{itemize}
-%     \item Copy-and-confirm was percieved as hard to use
-%     \item Copy-and-confirm has the lowest fatal error rate but the longest comparison time and lowest percieved usability
-%     \item The schemes reduced fatal error rate as their comparison times rose
-%     \item Copy-and-confirm had issues with user confusion in terms of use
-% \end{itemize}
-
-% In the second round they only decided to continue with
-
-% \begin{itemize}
-%     \item Compare-and-Confirm
-%     \item Select-and-Confirm
-% \end{itemize}
-
-% They dropped Copy-and-confirm due to its high similarity to the other scheme "Copy" that was being used for passphrase sharing
-
-% The second round included some UI changes that were backed up by external research.
-
-% This round the changes performed on the schemes resulted in much lower fatal error rates.
-However, Select-and-confirm had an unacceptable 5\% error rate.
-Compare-and-confirm had 0\% fatal error rate.
-The was an improvment from 20\% to 0\%.
-
-% Both schemes were again percieved as easy to use
-
-% Overall it was shown that compare-and-confirm was the superior choice.
-
-\newpage
-\section{On the Pitfalls of End-to-End Encrypted Communications: A Study of Remote Key-Fingerprint Verification}
-
-Paper compares the fingerprint verification task in the context of Instant messaging E2E The paper is also choosing to focus on the remote vs proximity ways of comparing fingerprints.
-They aim to study the security and usability of human-centred E2E key verification.
-The study ran with 25 participants.
-
-Seems to be the first study of remote code verification study
-
-Study compares Numerical, Image and verbally spoken codes and QR just for proximity alongside all the other alternatives.
-
-The studies main aim to compare remote to proximity, not compare the various methods
-
-The research is split into two sub-goals: Robustness - looks at the FAR and FRR. User experience and perception - System usability, Comfort, Satisfaction and Adaptability
-
-States that numerical is the one of the most common representations, but out of the chosen methods 50\% use numerical and the rest hexadecimal?
-
-They included 3 level of incorrect codes. One char change, one block and the entire fingerprint
-
-Overall Audio was one of the most secure and easiest to use.
-However results for image based comparisons were not controlled in any way due to the author being unable to access the telegram image generation, this means while the other schemes had controlled restraints the image did not.
-Images was rated the worst.
-
-Findings:
-\begin{itemize}
-    \item High False Acceptance Rate (False Negative) for all code verification methods 
-    \item Results point to low usability in remote code verification settings, aside from audio based verification ever scheme has above 20\% False Rejection Rate (False Positive)
-    \item In proximity settings users were able to detect attacks with minimal error rates
-\end{itemize}
-
-\newpage
-
-\section{The drunken bishop: An analysis of the OpenSSH
-fingerprint visualization algorithm}
-
-The aim of this research is to study the OpenSSH Visual Host Key.
-The authors claim that the scheme was heuristically designed and has very little backing in terms of formal research, this paper aims to create a foundation for this research.
-
-OpenSSH uses MD5 to generate a 128-bit fingerprint of the Server's key, this is then split into 64 2-bit pairs.
-These are then traversed byte wise in a right to left over the bit pairs.
-Each pair defines the direction of travel.
-If the snake reaches a position multiple times a pre define character is added depending on the number of visits (for example, 6 times == "B")
-
-The paper also discusses ways to create collisions:
-
-In conclusive results and more of an inital PoC
-
-\begin{itemize}
-    \item Brute force
-    \item Graph theory
-    \item Brute forcing a visual set
-\end{itemize}
-
-\newpage
-
 \section{Improving the Robustness of Wireless Device

### 2019-05-28 Literature_Review/pages/review_content.tex
Changes; - Added a few more references - Adjusted structure of lit' review

@@
-\section{Possible research questions}
+% \section{Possible research questions}
 
-Overall the research will aim to investigate the strength of pEp's Trustword fingerprint mappings, and the ease in which partial collisions can be obtained for keys and how this will ultimately affect the end user(s).
+% Overall the research will aim to investigate the strength of pEp's Trustword fingerprint mappings, and the ease in which partial collisions can be obtained for keys and how this will ultimately affect the end user(s).
 
-Key areas that will be looked into:
-\begin{itemize}
-    \item Is the recommended minimum number of Trustwords enough to provide a basic level of security.
-    \item What attributes make a strong general wordlist for fingerprint mapping and does the Trustword implementation exhibit these features.
-    \item How easy is it to generate similar keys that attack a targeted key pair?
-    \item How can similarity be quantified in terms of words? Does this include pronunciation or visual aspects?
-    \item As usability is the main justification for the use of Trustwords are there alternatives that provide the same usability but with more security?
-\end{itemize}
+% Key areas that will be looked into:
+% \begin{itemize}
+%     \item Is the recommended minimum number of Trustwords enough to provide a basic level of security.
+%     \item What attributes make a strong general wordlist for fingerprint mapping and does the Trustword implementation exhibit these features.
+%     \item How easy is it to generate similar keys that attack a targeted key pair?
+%     \item How can similarity be quantified in terms of words? Does this include pronunciation or visual aspects?
+%     \item As usability is the main justification for the use of Trustwords are there alternatives that provide the same usability but with more security?
+% \end{itemize}
 
-\section{Review}
+\section{Review - Fingerprint representations}
 
-\subsection{Fingerprint representation and comparison}
+\subsection{Fingerprint representation comparison}
 
@@
 
-The first work in this area was performed by Hsu-Chun Hsiao, \textit{et. al.} in their paper: \textit{A Study of User-Friendly Hash Comparison Schemes}\cite{hsiao2009study} in around 2009. \\
+\textbf{Hsu-Chun Hsiao, \textit{et.
+al.}} produced the first work in this area in their paper: \textit{A Study of User-Friendly Hash Comparison Schemes}\cite{hsiao2009study} in around 2009.
 The aim of the study was to provide the first insight into the best encoding scheme used to represent a hash fingerprint.
-The schemes used were Base32, English words, Random Art\footnote{A scheme proposed by A.
-Perrig \textit{et al.}\cite{perrig1999hash}}, Flag\footnote{Encoding scheme proposed by C Ellison \textit{et al.}\cite{ellison2003public}}, T-Flag\footnote{Yue-Hsun Lin \textit{et al.}\cite{lin2010spate} improvement on Flag}, Flag Ext\footnote{The author's own improvment on Flag} and finally Chinese, Korean and Japanese symbol encoding.
-436 participants were assessed in the study.
+The schemes used were Base32, English words, Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Flag Ext\footnote{The author's own improvement on Flag} and finally Chinese, Korean and Japanese symbol encoding.
+A total of 436 participants were assessed in the study.
 
-Alongside the main aim of the paper, the authors wanted to provide empirical links between participant attributes such as age or gender to performance with the encoding scheme.
+Alongside the main aim of the paper, the authors wanted to provide empirical links between participant attributes (such as age or gender) and performance with the encoding scheme.
 This is something rarely seen in the related research.
@@
 In terms of language comprehension; being able to speak the language assists in the ability to discern the differences between hard pairs.
-Subsequently, knowledge of the language did not help with easy pairs.
+Subsequently, knowledge of the language did not assist in differentiating easy pairs as these had high accuracy regardless of the spoken language.
 
@@
 
-Further research bu Kainda \textit{et al.}\cite{kainda2009usability} in 2009 investigated fingerprint representations and comparison methods in the context of using humans as the Out-Of-Band (OOB) channel for secure device pairing.
+\textbf{Kainda \textit{et al.}}\cite{kainda2009usability} in 2009 investigated fingerprint representations and comparison methods in the context of using humans as the Out-Of-Band (OOB) channel for secure device pairing.
 This study was comprehensive and assessed a wide variety of concepts.
@@
 Furthermore, the authors also collected user opinion on ease-of-use, satisfaction and confidence of the reviewed schemes.
-The overall schemes were then quantified using a single metric known as the Single Usability Metric (SUM)\cite{sauro2005method}.
-This provides a quick way to rank and compare the schemes, thus improving the usability of the results.
+The overall schemes were then quantified using a metric known as the Single Usability Metric (SUM)\cite{sauro2005method}.
+This provides an elementary way to rank and compare the schemes, thus improving the usability of the results.
 However, the one apparent downside to the experimental side of the study is the 40 participants enrolled.
@@
 If, however, the consideration of security alongside usability is required the best is: Compare-and-Enter, Barcode, Compare-and-Confirm and Compare-and-Select.
-Research has been limited in this area of modes of comparison, however, the results from this paper are consistent with the alternative literature.
-\\
+Research has been limited in this area of modes of comparison, however, the results from this paper are consistent with the limited alternative literature.
 In terms of encoding schemes, the paper ranked Numerical, Alphanumerical and Words as the top three encoding schemes (These were all with Compare-and-Confirm).
@@
 
-A paper by Ersin Uzun \textit{et al.}\cite{uzun2007usability} exclusively reviewed comparison methods.
+\textbf{Ersin Uzun \textit{et al.}}\cite{uzun2007usability} exclusively reviewed comparison methods.
 This is performed in the context of ``Secure device pairing'' and thus some comparison schemes are tested that are not relevant in a fingerprint comparison context, for example  ``Choose-and-Enter'' (A participant chooses a passphrase from an available list and enters it into the other device).
@@
 
-The relevant comparison methods tested were, Compare-and-Confirm, 
-Compare-and-Select and Compare-and-Enter.
+The relevant comparison methods tested were,Compare-and-Confirm, Compare-and-Select and Compare-and-Enter.
 These are almost exactly the same encoding schemes assessed in the relevant research literature.
@@
 Due to secure device pairing commonly utilising Short Authentication Strings (SAS) the
-paper only reviewed encodings of 4 digit long strings. This, therefore,limits the applicability of the results in comparison to other fingerprint encoding literature.
-
+paper only reviewed encodings of 4 digit long strings.
+This, therefore,limits the applicability of the results in comparison to other fingerprint encoding literature.
 Between the two rounds, the authors dropped ``Confirm-and-Enter'' due to its low usability and over similarity to a similar scheme called ``Copy'' (used for passphrase verification).
 The low rating for Confirm-and-Enter is in contrast with research performed by Kainda \textit{et al.}\cite{kainda2009usability} They ranked Confirm-and-Enter as the 2nd most usable system.
-
 With changes to the UX of Confirm-and-Confirm backed up by external research \cite{palmer1990attentional}\cite{hammer2009category} the second round of research was performed with a new set of participants.
@@
 
-Work by Dechand \textit{et al.}\cite{dechand2016empirical} empirically investigated the usability of 4 distinct textual representations evaluated with an experiment involving a total of 1047 participants.
+\textbf{Dechand \textit{et al.}}\cite{dechand2016empirical} empirically investigated the usability of 4 distinct textual representations evaluated with an experiment involving a total of 1047 participants.
 The textual representations were: Alphanumeric, Numeric, Words and Sentences.
@@
 These are, however, acknowledged as limitations in the later stages of the paper.
-
 The paper has defined the upper and lower bound costs of the attacker's resources and strength as \$610K to \$16B, with an ability to control 80-bits of the fingerprint.
@@
 
-J Tan \textit{et al.}\cite{tan2017can} work is very similar to that of the research already discussed.
+\textbf{J Tan \textit{et al.}}\cite{tan2017can} work is very similar to that of the research already discussed.
 Eight distinct fingerprint representations were tested with over 661 participants.
@@
 
-Further work in the context of secure messaging pairing was produced by M.
-Shirvanian \textit{et al.}\cite{shirvanian2017pitfalls} in 2017.
+\textbf{M.
+Shirvanian \textit{et al.}}\cite{shirvanian2017pitfalls} produced further work in the context of secure messaging pairing.
 This paper was unique for a number of reasons.
@@
 Research on textual representations, however, is in agreement; natural language based encodings such as words or sentences provide some of the highest usability and security over the baseline performance of alphanumerical encodings.
-The literature also concurs on the use of ``Compare-and-Confirm'' as the best method of comparing fingerprints overall, with Compare-and-Select being highlighted for its poor security and usability.\\
+The literature also concurs on the use of Compare-and-Confirm as the best method of comparing fingerprints overall, with Compare-and-Select being highlighted for its poor security and usability.\\
 The starkest limitations of the literature are the range of participant and encoding entropy, where at its worst only 22-bits of entropy were tested.
@@
 
-Some of the oldest preliminary work into visual encoding schemes was performed by Adrian Perrig \textit{et al}\cite{perrig1999hash}.
+Some of the oldest preliminary work into visual encoding schemes was performed by \textbf{Adrian Perrig \textit{et al}}\cite{perrig1999hash}.
 in the creation of their scheme ``Random Art" in 1999.
@@
 
-Further research into the creation of unique visual hash schemes have been performed by C Ellison \textit{et al.} \cite{ellison2003public} (Flag), Yue-Hsun Lin \textit{et al.}\cite{lin2010spate} (T-Flag) and work by MM Olembo \textit{et al.}\cite{olembo2013developing}.
+Further research into the creation of unique visual hash schemes have been performed by \textbf{C Ellison \textit{et al.}} \cite{ellison2003public} (Flag), \textbf{Yue-Hsun Lin \textit{et al.}}\cite{lin2010spate} (T-Flag) and work by \textbf{M.
+Olembo \textit{et al.}}\cite{olembo2013developing}.
 Each publication has provided a new way to visually represent a key fingerprint.
@@
 
-One paper of note is the preliminary work performed by D Loss \textit{et al.}\cite{loss2009drunken} in their \textit{``An analysis of the OpenSSH fingerprint visualization algorithm''} where their aim was to spur on further research with their initial findings into the security of the OpenSSH scheme.
+One paper of note is the preliminary work performed by \textbf{D Loss \textit{et al.}}\cite{loss2009drunken} in their \textit{``An analysis of the OpenSSH fingerprint visualization algorithm''} where their aim was to spur on further research with their initial findings into the security of the OpenSSH scheme.
 The authors claim that the use of the algorithm in OpenSSH is only heuristically defined and there is a need for a formal proof of its security.
@@
 Minimal research has also focused on basic textual fingerprint representations and their respective security.
-Work by A.
-Karole and N.
-Saxena\cite{karole2009improving} looked into ways to improve the security of a textual representation.
+Work by \textbf{A.
+Karole} and \textbf{N.
+Saxena}\cite{karole2009improving} looked into ways to improve the security of a textual representation.
 This research aim is to improve the secure device pairing process of comparing two numerical values.
@@
 
-A more specific subsection of textual fingerprints is the use of words and sentences to encode hash digests. Some of the first work in this area was produced by Patrick Juola and Philip Zimmermann 
+A more specific subsection of textual fingerprints is the use of words and sentences to encode hash digests. Some of the first work in this area was produced by \textbf{Juola} and \textbf{Zimmermann}
 \cite{juola1996whole} and their work in generating a word list where phonetic distinctiveness was prioritised.
@@
 
-Other research of note is work by M.
-Goodrich \textit{et al.}\cite{goodrich2006loud} called \textit{Loud and Clear: Human-Verifiable Authentication Based on Audio}.
+Other research of note is work by \textbf{M.
+Goodrich \textit{et al.}}\cite{goodrich2006loud} called \textit{Loud and Clear: Human-Verifiable Authentication Based on Audio}.
 As the name suggests the authors were researching ways to improve current methods of secure device pairing.
@@
 Aside from this research, there have been further informal implementations of fingerprint encodings.
-The first being by Michael Rogers\footnote{https://github.com/akwizgran/basic-english}.
+The first being by \textbf{Michael Rogers}\footnote{https://github.com/akwizgran/basic-english}.
 Rogers' implementation is a program designed to map fingerprints to pseudo-random poems.
@@
 
-\section{Attacks on fingerprint verification}
+\subsection{Fingerprint representation attacks}
 This area of research studies ways to physically execute attacks on fingerprint encoding schemes.
@@
 
-Research in 2002 by Konrad Rieck\cite{rieck2002fuzzy} is the first formalisation of attacks on fingerprint representations.
+Research in 2002 by \textbf{Konrad Rieck}\cite{rieck2002fuzzy} is the first formalisation of attacks on fingerprint representations.
 The paper titled \textit{``Fuzzy Fingerprints Attacking Vulnerabilities in the Human Brain''}
@@
 
-The only other relevant research on this topic is the work by M 
-Shirvanian \textit{et al.}\cite{shirvanian2014wiretapping} 
+The only other relevant research on this topic is the work by \textbf{M Shirvanian \textit{et al.}}\cite{shirvanian2014wiretapping} 
 and their paper \textit{``Wiretapping via Mimicry: Short 
 Voice Imitation Man-in-the-Middle Attacks on Crypto 
-Phones''}. In this paper, the authors develop a way to 
+Phones''}.
+Further research in the area of ``human voice impersonation'' has received lots of attention \cite{mukhopadhyay2015all}\cite{chen2017you}\cite{wu2015spoofing}.
+This paper was chosen over other alternatives due to is specific use of encoding schemes in its evaluation.
+
+In this paper, the authors develop a way to 
 impersonate users when authenticating 

### 2019-05-29 Documents/paper_notes/pages/loud_and_clear.tex
Changes; - Started formalising the plan for the project - Added elements to the archive - Re-ordered LaTeX documents in the directory

--- 2019-05-25 Papers/Notes_TeX/pages/paper_notes.tex
@@
-\textbf{TODO:} Need to find papers on study of words are a comparative measure.
-
-Lots of research has been done into the secure pairing of devices with minimal human involvement:
-
-\begin{itemize}
-    \item Using Camera Phones for Human-Verifiable Authentication
-    \item Loud and Clear: Human-Verifiable Authentication Based on Audio
-    \item A human-verifiable authentication protocol using visible laser light
-    \item Secure Device Pairing based on a Visual Channel
-    \item NFC
-    \item Physical contact
-\end{itemize}
-
-\textbf{OVERVIEW} 
-\begin{itemize}
-    \item Lots of research performed on E2E applications (Telegram, WhatsApp etc)
-    \item Lots of study into overall representations of fingerprints
-\end{itemize}
-
-\section{Can Unicorns Help Users Compare Crypto Key Fingerprints}
-
-This paper tested 8 different fingerprint representations with 661 different participants.
-All of these representations are testing using compare-and-confirm (basic comparison process for fingerprints) and compare-and-select (select from a list)
-
-\begin{itemize}
-    \item Hexadecimal
-    \item Alternating vowel/consonant
-    \item Words
-    \item Numbers
-    \item Sentences
-    \item OpenSSH visual host key
-    \item Vash
-    \item Unicorns
-\end{itemize}
-
-The paper also emphasises the attention that has been taken to realism in the experimentation stage.
-
-Talks about long term usability issues with public-key crypto and states fingerprints are a main source of the problem. ([28])
-
-There seems to be mixed findings with compare-and-select and compare-and-confirm ([14, 17])
-
-There has been research into OpenSSH fingerprints and how users interact ([19, 24])
-
-Paper chose to target a security level of 160-bits
-
-Papers attack strengths were $2^{40}$, $2^{60}$ and $2^{80}$
-
-Paper states that MTurk users have been shown to be younger and better educated than the general US population ([15])
-
-\subsection{Findings}
-
-\begin{itemize}
-    \item Graphical representations have mixed success rates (with quick comparison times)
-    \item Recommendations not to use \textbf{compare-and-select}
-    \item \textbf{No method} really provided enough security for high risk situations, they recommend removing users from the loop by using smart phone cameras etc
-\end{itemize}
-
-\newpage
-% \section{An Empirical Study of Textual Key-Fingerprint Representations}
-
-% Study involved 1047 participants evaluating 6 different textual representations on MTurk. The study also includes an evaluation into usability.
-
-% The study has an attacker power of around 80 of 112 bits.
-
-% \begin{itemize}
-%     \item Alphanumerical
-%     \item Numerical
-%     \item Words
-%     \item Sentences
-% \end{itemize}
-
-% More mention to decentralised method finding it hard to find adoption such as Web of Trust and Namecoin ([7, 13, 30])
-
-% References as system called CONIKS and others ([24, 39, 27]) that aim to provided a directory of keys
-
-% States that many systems still rely on fingerprint comparison ([17])
-
-% States that the \textbf{hexadecimal} encoding is used in most systems.
-
-% States again that fingerprint comparison is seldom done in practice ([17, 37])
-
-% Studies have shown that users find it difficult to compare long and "meaningless" strings ([19])
-
-% References to other word lists used. PGP Word list [22] and english word list compiled by K.C. Ogden [31]. The Peerio word list is generated from the most common words in english subtitles.
-
-% Interesting recommendation into the use of \textit{scrypt} [34] and \textit{Argon 2} [3] can be used to shorten the fingerprint length.
-These work slowly and a prevent easy computation of pre-images.
-
-% When generating partial-collision fixing the bits at the start and end has been shown a best practice ([17, 37])
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Overall recommendation is to replace \textbf{hexadecimal} with \textbf{sentence} based encoding
-%     \item Findings show that \textbf{hexadecimal} and \textbf{Base32} perform worse than the other alternatives in realistic threat models.
-With over \textbf{10\%} of users failing to detect attacks with these schemes.
-%     \item According to their study, \textbf{words} and \textbf{sentences} we some of the best methods for avoiding attack
-%     \item Words has the second highest usability ratings second to only sentences
-% \end{itemize}
-
-% \newpage
-% \section{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}
-
-% Paper looks into the positives of secondary channels used to authenticate device pairing.
-Such as device fingerprint comparison.
-It also aims to look into the fact that many studies performed do not take into consideration the aspect of human interaction.
-
-% Total of 30 paid participants were recruited where the experiment simulated a P2P payment system.
-
-% They collected:
-% \begin{itemize}
-%     \item Time to completed the associated process
-%     \item Number of security or non-security related errors
-% \end{itemize}
-
-% And quantified using questionnaires:
-% \begin{itemize}
-%     \item Ease of use with the representation
-%     \item Satisfaction with time spent with a method/representation
-%     \item Participant's confidence with the scheme
-% \end{itemize}
-
-% The paper also tested methods:
-% \begin{itemize}
-%     \item Compare and Confirm
-%     \item Compare and Select
-%     \item Compare and Enter
-%     \item Barcode scanning
-% \end{itemize}
-
-% Representations:
-% \begin{itemize}
-%     \item Numerical
-%     \item Alphanumerical
-%     \item Words
-%     \begin{itemize}
-%         \item Dictionary of 1024 words each mapped to 10-bits
-%     \end{itemize}
-%     \item Sentences
-%     \item Images
-%     \item Melodies
-%     \item Sound (Numerical/Alphanumerical)
-% \end{itemize}
-
-% "People are the weakest link in the security chain" [26]
-
-% Mentions a normal channel as a "Dolev-Yao" channel [5]. This is where an attacker can overhead, delete and modify messages.
-
-% Talks about systems that were secure on paper that ended up in practice being miss-handled to reduce security. One example is with the Russian army in WWI [1]
-
-% Bruce Schneier [27] also argues that systems and involves humans therefore often systems are broken due to improper use.
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Showed for \textbf{usability} methods ranked:
-%     \begin{itemize}
-%         \item Comparing-confirm
-%         \item Typing strings
-%         \item Comparing-select
-%         \item Barcode
-%     \end{itemize}
-
-%     \item Showed for \textbf{combined security} and \textbf{usability} methods ranked:
-%     \begin{itemize}
-%         \item Typing strings
-%         \item Barcodes
-%         \item Comparing-confirm
-%         \item Comparing-select
-%     \end{itemize}
-
-%     Showed that the best methods in terms of the SUM score [24] ranked the top 3 as:
-%     \begin{itemize}
-%         \item Numeric(C\&C)          [73.7]
-%         \item Alphanumerical(C\&C)   [72.5]
-%         \item Words (C\&C)           [70.6]
-%     \end{itemize}
-
-%     Numerical had 0\% security failures, Word 3.3\% and Alphanumerical had a high 13.3\%
-
-%     NOTE: This is a very small sample size.
-% \end{itemize}
-
-% \newpage
-% \section{SafeSlinger: An Easy-to-use and Secure Approach for
-% Human Trust Establishment}
-
-% The aim of SafeSlinger is to solve the issue of key exchange.
-They aim to leverage the initial personal contact of people to facilitate trust.
-To solve the issue of people that would never meet they implement a system of "shared acquaintance"
-
-% Talks about issues with decentralised (PGP [42]) and centralised (SSL CA [27, 34]) key exchange.
-
-% "Tim Berners-Lee has called upon security researchers and professionals to design a public key encryption system for the people [11]"
-
-% Only uses \textbf{24-bits} of a SHA-1 hash of all the exchanged information, \textbf{could this be exploited?}
-
-% \newpage
-% \section{A Study of User-Friendly Hash Comparison Schemes}
-
-% The aim of this study is to provide a study on what hash comparison scheme provides the best accuracy and shortest comparison time.
-
-% The paper also proposes new schemes: An extension to Flag and three asian character representations.
-
-% An interesting aspect is the effort put into the study to link characteristics about the participants, i.e.
-gender or age to how well they perform or rate the usability of the scheme.
-In total they had 436 participants.
-
-% Overall they compare:
-% \begin{itemize}
-%     \item Base32
-%     \item English words
-%     \item Random Art
-%     \item Flag
-%     \item T-Flag
-%     \item Flag ext
-%     \item Chinese, Korean, Japanese characters
-% \end{itemize}
-
-% Key phrase: "We did not use hexadecimal digits because they're similar to Base32 and known to be error prone" [NO REFERENCE].
-This is shown in \textit{``An Empirical Study of Textual Key-Fingerprint Representations''} that this isn't true - ``However, our work shows that numeric representations actually perform significantly better than Base32 and is less error prone.''
-
-% They study also considers the comparison of "easy" and "hard" pairs of hashes.
-Hard is where the hashes are designed to be very similar.
-This is designed to provide a base-line (easy) and a worst-case (hard).
-
-% The paper deals with ranges of entropy of 22-28bits.
-
-% Another system that uses word is the Unmanaged Internet Architecture [4]
-
-% States that users make errors when comparing long strings [11]
-
-% Dicussions are also made into the pre-requirements needed for some of these schemes.
-Random-Art needs a colour display and requires a relativly high computational cost to generate a representation.
-Asian characters require unicode or codec support.
-
-% Paper also touches on ``Additional Benefits'' - the paper talks about the ability to verbally describe the scheme, this is so the encoding scheme can be verified using a channel that does not involve a visual feed such as a telephone conversation
-
-% Overall the paper provides a table of requirements for the schemes with the graphical representations requiring a large number of pre-requirements.
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Source, age and gender have no significant impact on the accuracy across the schemes. But younger participants were significantly faster
-%     \item In general, Base32, Random Art, T-Flag and Flag Ext provide fast and accurate comparisons
-%     \item Comprehension of a language when used as a encoding scheme affects the ability to distinguish hard pairs by a significant amount
-% \end{itemize}
-
-% \newpage
-% \section{Usability Analysis of Secure Pairing Methods}
-
-% Paper is aiming to perform a comparative usability evaluation of \textbf{selection methods} of hash comparisons
-
-% This paper is doing this study in the context of secure device pairing in a diffie-hellman type key exchange.
-However, the results of the study could directly apply to that of hash comparison, however, it must be considered that the comparisons here are for \textbf{very} short strings.
-Around 4-digits
-
-% Comparison methods compared:
-% \begin{itemize}
-%     \item Compare-and-Confirm
-%     \item Select-and-Confirm
-%     \item Copy-and-Confirm
-% \end{itemize}
-
-% The paper also compared to methods of passphrase comparison that weren't relevant.
-
-% Paper also included demographical information in the study, with two round of 40 participants in the usability studies.
-
-% Findings:
-
-% Round 1:
-% \begin{itemize}
-%     \item Copy-and-confirm was percieved as hard to use
-%     \item Copy-and-confirm has the lowest fatal error rate but the longest comparison time and lowest percieved usability
-%     \item The schemes reduced fatal error rate as their comparison times rose
-%     \item Copy-and-confirm had issues with user confusion in terms of use
-% \end{itemize}
-
-% In the second round they only decided to continue with
-
-% \begin{itemize}
-%     \item Compare-and-Confirm
-%     \item Select-and-Confirm
-% \end{itemize}
-
-% They dropped Copy-and-confirm due to its high similarity to the other scheme "Copy" that was being used for passphrase sharing
-
-% The second round included some UI changes that were backed up by external research.
-
-% This round the changes performed on the schemes resulted in much lower fatal error rates.
-However, Select-and-confirm had an unacceptable 5\% error rate.
-Compare-and-confirm had 0\% fatal error rate.
-The was an improvment from 20\% to 0\%.
-
-% Both schemes were again percieved as easy to use
-
-% Overall it was shown that compare-and-confirm was the superior choice.
-
-\newpage
-\section{On the Pitfalls of End-to-End Encrypted Communications: A Study of Remote Key-Fingerprint Verification}
-
-Paper compares the fingerprint verification task in the context of Instant messaging E2E The paper is also choosing to focus on the remote vs proximity ways of comparing fingerprints.
-They aim to study the security and usability of human-centred E2E key verification.
-The study ran with 25 participants.
-
-Seems to be the first study of remote code verification study
-
-Study compares Numerical, Image and verbally spoken codes and QR just for proximity alongside all the other alternatives.
-
-The studies main aim to compare remote to proximity, not compare the various methods
-
-The research is split into two sub-goals: Robustness - looks at the FAR and FRR. User experience and perception - System usability, Comfort, Satisfaction and Adaptability
-
-States that numerical is the one of the most common representations, but out of the chosen methods 50\% use numerical and the rest hexadecimal?
-
-They included 3 level of incorrect codes. One char change, one block and the entire fingerprint
-
-Overall Audio was one of the most secure and easiest to use.
-However results for image based comparisons were not controlled in any way due to the author being unable to access the telegram image generation, this means while the other schemes had controlled restraints the image did not.
-Images was rated the worst.
-
-Findings:
-\begin{itemize}
-    \item High False Acceptance Rate (False Negative) for all code verification methods 
-    \item Results point to low usability in remote code verification settings, aside from audio based verification ever scheme has above 20\% False Rejection Rate (False Positive)
-    \item In proximity settings users were able to detect attacks with minimal error rates
-\end{itemize}
-
-\newpage
-
-\section{The drunken bishop: An analysis of the OpenSSH
-fingerprint visualization algorithm}
-
-The aim of this research is to study the OpenSSH Visual Host Key.
-The authors claim that the scheme was heuristically designed and has very little backing in terms of formal research, this paper aims to create a foundation for this research.
-
-OpenSSH uses MD5 to generate a 128-bit fingerprint of the Server's key, this is then split into 64 2-bit pairs.
-These are then traversed byte wise in a right to left over the bit pairs.
-Each pair defines the direction of travel.
-If the snake reaches a position multiple times a pre define character is added depending on the number of visits (for example, 6 times == "B")
-
-The paper also discusses ways to create collisions:
-
-In conclusive results and more of an inital PoC
-
-\begin{itemize}
-    \item Brute force
-    \item Graph theory
-    \item Brute forcing a visual set
-\end{itemize}
-
-\newpage
-
-\section{Improving the Robustness of Wireless Device
-Pairing Using Hyphen-Delimited Numeric
-Comparison}
-
-In the context of secure device pairing the paper aims to improve the human interaction with number pairing.
-
-Lots of research has gone into Short Authentication String (SAS) numbers ([14], [10], [4])
-
-The research was peformed on very old devices. Nokia 6030b, very out of date and not reflective of anything around at this time.
-
-Usability study looked into Efficiency, Robustness, General Usability
-
-Strange format of keeping the numbers exactly the same but just placing hyphens in the middle. The authors attempted to remedy this by spacing the experiments with a days gap
-
-Study was performed with 40 participants
-
-Very small number of values tested only 5 overall???
-
-Initial results show promising results for hypen delimitations etc alongside improved user impressions
-
-\newpage
-
 \section{Loud and Clear: Human-Verifiable Authentication Based on Audio}
@@
 The paper is not backed up by any empirical data and is just a technical description on the system. It included just a performance analysis.
-
-\newpage
-
-\section{Whole-Word Phonetic Distances and the PGPfone Alphabet}
-
-PGPfones designed solution was the development of a wordless based of military NATO codes.
-
-The authors used Moby Pronunciator database of nearly 200,000 word/pronunciation pairs.
-
-Use-case for these findings are when verification needs to occur over a auditory line.
-
-Mentions on potential further work in the emprical evaluation of these points
-
-TODO: An analysis of perceptual confusions among some English consonants

### 2019-05-29 Documents/paper_notes/pages/usability_and_security.tex
Changes; - Started formalising the plan for the project - Added elements to the archive - Re-ordered LaTeX documents in the directory

\section{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}

Paper looks into the positives of secondary channels used to authenticate device pairing. Such as device fingerprint comparison. It also aims to look into the fact that many studies performed do not take into consideration the aspect of human interaction.

Total of 30 paid participants were recruited where the experiment simulated a P2P payment system.

They collected:
\begin{itemize}
    \item Time to completed the associated process
    \item Number of security or non-security related errors
\end{itemize}

And quantified using questionnaires:
\begin{itemize}
    \item Ease of use with the representation
    \item Satisfaction with time spent with a method/representation
    \item Participant's confidence with the scheme
\end{itemize}

The paper also tested methods:
\begin{itemize}
    \item Compare and Confirm
    \item Compare and Select
    \item Compare and Enter
    \item Barcode scanning
\end{itemize}

Representations:
\begin{itemize}
    \item Numerical
    \item Alphanumerical
    \item Words
    \begin{itemize}
        \item Dictionary of 1024 words each mapped to 10-bits
    \end{itemize}
    \item Sentences
    \item Images
    \item Melodies
    \item Sound (Numerical/Alphanumerical)
\end{itemize}

"People are the weakest link in the security chain" [26]

Mentions a normal channel as a "Dolev-Yao" channel [5]. This is where an attacker can overhead, delete and modify messages.

Talks about systems that were secure on paper that ended up in practice being miss-handled to reduce security. One example is with the Russian army in WWI [1]

Bruce Schneier [27] also argues that systems and involves humans therefore often systems are broken due to improper use.

\subsection{Findings}
\begin{itemize}
    \item Showed for \textbf{usability} methods ranked:
    \begin{itemize}
        \item Comparing-confirm
        \item Typing strings
        \item Comparing-select
        \item Barcode
    \end{itemize}

    \item Showed for \textbf{combined security} and \textbf{usability} methods ranked:
    \begin{itemize}
        \item Typing strings
        \item Barcodes
        \item Comparing-confirm
        \item Comparing-select
    \end{itemize}

    Showed that the best methods in terms of the SUM score [24] ranked the top 3 as:
    \begin{itemize}
        \item Numeric(C\&C)          [73.7]
        \item Alphanumerical(C\&C)   [72.5]
        \item Words (C\&C)           [70.6]
    \end{itemize}

    Numerical had 0\% security failures, Word 3.3\% and Alphanumerical had a high 13.3\%

    NOTE: This is a very small sample size.
\end{itemize}

### 2019-05-29 Documents/paper_notes/pages/usability_secure_pairing.tex
Changes; - Started formalising the plan for the project - Added elements to the archive - Re-ordered LaTeX documents in the directory

\section{Usability Analysis of Secure Pairing Methods}

Paper is aiming to perform a comparative usability evaluation of \textbf{selection methods} of hash comparisons

This paper is doing this study in the context of secure device pairing in a diffie-hellman type key exchange. However, the results of the study could directly apply to that of hash comparison, however, it must be considered that the comparisons here are for \textbf{very} short strings. Around 4-digits

Comparison methods compared:
\begin{itemize}
    \item Compare-and-Confirm
    \item Select-and-Confirm
    \item Copy-and-Confirm
\end{itemize}

The paper also compared to methods of passphrase comparison that weren't relevant.

Paper also included demographical information in the study, with two round of 40 participants in the usability studies.

Findings:

Round 1:
\begin{itemize}
    \item Copy-and-confirm was percieved as hard to use
    \item Copy-and-confirm has the lowest fatal error rate but the longest comparison time and lowest percieved usability
    \item The schemes reduced fatal error rate as their comparison times rose
    \item Copy-and-confirm had issues with user confusion in terms of use
\end{itemize}

In the second round they only decided to continue with

\begin{itemize}
    \item Compare-and-Confirm
    \item Select-and-Confirm
\end{itemize}

They dropped Copy-and-confirm due to its high similarity to the other scheme "Copy" that was being used for passphrase sharing

The second round included some UI changes that were backed up by external research.

This round the changes performed on the schemes resulted in much lower fatal error rates. However, Select-and-confirm had an unacceptable 5\% error rate. Compare-and-confirm had 0\% fatal error rate. The was an improvment from 20\% to 0\%.

Both schemes were again percieved as easy to use

Overall it was shown that compare-and-confirm was the superior choice.

### 2019-05-29 Documents/paper_notes/pages/use_your_words.tex
Changes; - Started formalising the plan for the project - Added elements to the archive - Re-ordered LaTeX documents in the directory

\section{Use Your Words: Designing One-time Pairing Codes toImprove User Experience}

The use of works instead of numerical codes. This is in the context of device pairing in IoT. Something that is new in the literature

Search space required was 500,000,000

Numeric:        9 digits
Alphanumeric:   5 chars
Words:          3 words

Paper contains references to lots of research into words distributions etc

Paper claimed that 800 works would need to be used but in the experiment only utilised 242 words???

Words provided a faster entry time with no reduction in accuracy

``It is known that typing familiar words is faster than typing random strings [22]''

Paper did not consider malicious aspect of their methods, no discussion was made into how a dictionary of 800 words could be easily impersonated

However, promising results for the usability of word based encodings on displays with low fidelity

### 2019-05-29 Documents/project_plan/pages/work_plan.tex
Changes; - Started formalising the plan for the project - Added elements to the archive - Re-ordered LaTeX documents in the directory

\section{Title}

\begin{center}
    \textit{\large ``Security evaluation of pEp's TrustWord implementation"}
\end{center}

\section{Motivation}
\begin{itemize}
    \item Use-case for TrustWords: Users are often deterred by difficulty in key authentication and end-to-end encryption (e.g. PGP web-of-trust).

    \item Other word lists result in a higher number of words to compare. Trustwords mapping of a word to 2 bytes results in a lower number of words. Meaning the possibility of increased usability

    \item However, the mapping of words to 16-bits is yet to be proved as secure as this is the highest number of bits per word seen in the literature.

\end{itemize}

\section{Goals}

Overall the research will aim to investigate the strength of pEp's Trustword fingerprint mappings, and the ease in which partial collisions can be obtained for keys and how this will ultimately affect the end user(s). This will be accompanied by recommendations into how the TrustWord system can be altered to provide maximum security alongside research into what makes an effective wordlist.

\newpage
\section{Possible research questions}
\begin{itemize}
    \item Is the recommended minimum number of Trustwords enough to provide a basic level of security?

    \item What attributes make a strong general wordlist for fingerprint mapping and does the Trustword implementation exhibit these features?

    \item What are some of the most effective ways of measuring linguistic distance or similarity?

    \item How easy is it to generate similar keys that attack a targeted key pair?

    \item How can the search for similar keys be assisted? Could weighting them like ``\textit{Fuzzy Fingerprints Attacking Vulnerabilities in the Human Brain}'' help to find partial matches?

    \item How can similarity be quantified in terms of words? Does this include pronunciation or visual aspects?

    \item As usability is the main justification for the use of Trustwords are there alternatives that provide the same usability but with more security?
\end{itemize}

% \section{RFC drafts}
% \subsection{draft-marques-pep-handshake-02}
% ``Short Trustword Mapping (S-TWM) requires a number of Trustwords that MUST retain \textbf{at least 64 bits} of entropy.  Thus, S-TWM results into at least \textbf{four Trustwords} to be compared by the user."

% Showing that 4 words is too low in certain cases could be very useful?

% \subsection{draft-birk-pep-trustwords-00}
% In another draft document it also states:

% ``It is for further study, what minimal number of words (or entropy) should be required."

% This shows there is some sort of research gap.

\newpage
\section{High Level View}

\subsection*{\hyperref[ref:wordlist]{Wordlist characteristic analysis}}
This area will look into characteristics that are attractive when designing a wordlist. These will be used later to possibility improve the trustword implementation.

\subsection*{Analysis into effective ``similarity'' metrics}
\textit{TODO}

\subsection*{Development of a tool used to find partial collisions for wordlist mappings}
This tool would be fed two keys, one static and one the ``target''. The tool would then generate keys for the ``target'' that create a similar overall wordlist mapping. Here metrics for linguistic distance will be used to define ``similarity''.
The similarity metric will generate a list of keys that provide similar matches, the tool will then hash large number of PGP keys to generate partial matches.

\subsection*{\hyperref[ref:trustwords]{Security of Trustwords}}
This section will evaluate Trustwords using the previously defined metrics. Alongside this, the feasibility of generating partial collisions will be assessed. The security could be quantified by testing the current implementation out on real users and determining the False acceptance rate of near attacks. This could be used as a baseline.

\subsection*{\hyperref[ref:alternatives]{Security of alternative wordlists:}}
In the same way as Trustwords were assessed, the same will be performed on already available wordlists. Such as the PGP wordlist and the wordlist generated by SafeSlinger.

\subsection*{\hyperref[ref:rec]{Security of implemented recommendations}}
This section will then amalgamate all the research performed prior and use it to improve and update the implementation of Trustwords. This would then be assessed by experimentation and the improvements could be quantified with the same experimentation.

\section{In-depth breakdown}

\subsection{Wordlist characteristic analysis}
\label{ref:wordlist}
\begin{itemize}
    \item Investigation into characteristics of a strong wordlist
    \begin{itemize}
        \item Distinctiveness
        \item Homonyms (Visual)
        \item Homophones (Pronunciation)
        \item Length
        \item Current ways to define linguistic distance:
        \begin{itemize}
            \item \textbf{Visual:}
            \begin{itemize}
                \item Levenshtein (Edit distance)
            \end{itemize}

            \item \textbf{Auditory}:
            \begin{itemize}
                \item Soundex
                \item Metaphone
            \end{itemize}
        \end{itemize}

    \end{itemize}

    \item Analysis into the strength of the TrustWords using previously obtained metrics.

    \item Investigation into the strength of other wordlists using defined metrics.
    \begin{itemize}
        \item PGP word list
        \item SafeSlinger
    \end{itemize}

\end{itemize}

\subsection{Security of Trustwords}
\label{ref:trustwords}
Here we'd look at the words used in the dictionary and attempt to generate lists of keys that would generate partial collisions these would then be fed into the created tool

\subsection{Security of alternative wordlists}
\label{ref:alternatives}

\subsection{Security of implemented recommendations}
\label{ref:rec}

### 2019-05-29 Documents/paper_notes/pages/pgpfone.tex
Changes; - Added multi metric mode to Similar_words.cpp - Added some more detail to the plan

\section{Whole-Word Phonetic Distances and the PGPfone Alphabet}

PGPfones designed solution was the development of a wordless based of military NATO codes.

Key terms: ``Phonetic confusability''

The authors used Moby Pronunciator database of nearly 200,000 word/pronunciation pairs.

Use-case for these findings are when verification needs to occur over a auditory line.

Words are created from ``phonemes'' (Unit of sound in a word). They state the the distance between two words can be approximated by between the phonemes that make up the word.

\textit{``It should be noted that this is only one of many possible approaches.''}

Mentions on potential further work in the emprical evaluation of these points

``A larger list (two
bytes per word) would require nearly 650 kilobytes of mem-
ory, as well as a word vocabulary larger than most speakers'
vocabulary.''

Big assumption that the two word PGP word list will be memorised by people ``This assumes, of course, that the (listening) human can tell from which list a word has been drawn.''. However, I think this was rectified with the 2-syllable then 3-syllable trick for even odd words.

Many questions proposed by the author:
\begin{itemize}
    \item Do the pronunciation assumptions fail when the reader is not a native English speaker?
    \item How confusable are the words?
\end{itemize}

### 2019-05-29 Code/TrustWords/Multiple/multi.py

@@ -1,0 +1,80 @@
+import jellyfish
+import numpy as np
+import timeit
+
+algorithm_and_weights = \
+[
+    [jellyfish.soundex, 1],
+    [jellyfish.match_rating_codex, 1],
+    [jellyfish.metaphone, 1],
+    [jellyfish.nysiis, 1]
+]
+
+similarity_tolerance = 3.0
+
+def levenshtein(seq1, seq2):
+    size_x = len(seq1) + 1
+    size_y = len(seq2) + 1
+    matrix = np.zeros((size_x, size_y))
+    for x in range(size_x):
+        matrix[x, 0] = x
+    for y in range(size_y):
+        matrix[0, y] = y
+
+    for x in range(1, size_x):
+        for y in range(1, size_y):
+            if seq1[x-1] == seq2[y-1]:
+                matrix[x, y] = min(
+                    matrix[x-1, y] + 1,
+                    matrix[x-1, y-1],
+                    matrix[x, y-1] + 1
+                )
+            else:
+                matrix[x, y] = min(
+                    matrix[x-1, y] + 1,
+                    matrix[x-1, y-1] + 1,
+                    matrix[x, y-1] + 1
+                )
+    return (matrix[size_x - 1, size_y - 1])
+
+def similar(word1, word2):
+    total= 0.0
+    for aw in algorithm_and_weights:
+
+        al = aw[0]
+        w  = aw[1]
+
+        code1 = al(word1)
+        code2 = al(word2)
+        lev = levenshtein(code1, code2)
+        subtotal = lev * w
+        total += subtotal
+
+    return total
+
+words = None
+with open("../Wordlists/EN/en_unique.csv") as file:
+    words = file.readlines()
+
+# Cleans the words of their newline characters
+words = list(map(str.strip, words))
+
+# Vars
+number_of_words = len(words)
+words_complete = 0
+
+for word1 in words:
+
+    start = timeit.default_timer()
+    for word2 in words:
+
+        if word1 != word2:
+            s = similar(word1, word2)
+
+            if s <= similarity_tolerance:
+                print(word1, word2, s)
+            
+    stop = timeit.default_timer()
+    # print("[!] Time to complete: ", (stop-start)*number_of_words / 3600)
+
+    words_complete += 1

### 2019-05-29 Code/TrustWords/SimilarWords/modes/double_metaphone.cpp

@@ -101,7 +101,7 @@ int StringAt(std::string &s, unsigned int start, unsigned int length, ...)
   return 0;
 }
 
-std::string DoubleMetaphone(const std::string &str)
+std::string metaphone(const std::string &str)
 {
   int length;
   std::string original;
@@ -1100,6 +1100,6 @@ std::string DoubleMetaphone(const std::string &str)
 
 bool metaphone_similar(std::string word1_code, std::string word2)
 {
-  std::string word2_code = DoubleMetaphone(word2);
+  std::string word2_code = metaphone(word2);
   return word1_code == word2_code;
 }

### 2019-05-29 Code/TrustWords/SimilarWords/modes/double_metaphone.hpp

@@ -11,7 +11,7 @@ char GetAt(std::string &s, unsigned int pos);
 void SetAt(std::string &s, unsigned int pos, char c);
 int StringAt(std::string &s, unsigned int start, unsigned int length, ...);
 
-std::string DoubleMetaphone(const std::string &str);
+std::string metaphone(const std::string &str);
 
 bool metaphone_similar(std::string word1, std::string word2);
 

### 2019-05-29 Code/TrustWords/SimilarWords/modes/nysiis.cpp

@@ -1,0 +1,92 @@
+#include <iostream>
+#include <cstring>
+ 
+// CREDIT: https://rosettacode.org/wiki/NYSIIS#C.2B.2B
+
+std::string nysiis( std::string const& str )
+{
+    std::string s, out;
+    s.reserve( str.length() );
+    for( auto const c : str )
+    {
+        if( c >= 'a' && c <= 'z' )
+            s += c - ('a' - 'A');
+        else if( c >= 'A' && c <= 'Z' )
+            s += c;
+    }
+ 
+    auto replace = []( char const * const from, char const* to, char* const dst ) -> bool
+    {
+        auto const n = strlen( from );
+        if( strncmp( from, dst, n ) == 0 )
+        {
+            strncpy( dst, to, n );
+            return true;
+        }
+        return false;
+    };
+ 
+    auto multiReplace = []( char const* const* from, char const* to, char* const dst ) -> bool
+    {
+        auto const n = std::strlen( *from );
+        for( ; *from; ++from )
+            if( strncmp( *from, dst, n ) == 0 )
+            {
+                memcpy( dst, to, n );
+                return true;
+            }
+        return false;
+    };
+ 
+    auto isVowel = []( char const c ) -> bool
+    {
+        return c == 'A' || c == 'E' || c == 'I' || c == 'O' || c == 'U';
+    };
+ 
+    size_t n = s.length();
+    replace( "MAC", "MCC", &s[0] );
+    replace( "KN", "NN", &s[0] );
+    replace( "K", "C", &s[0] );
+    char const* const prefix[] = { "PH", "PF", 0 };
+    multiReplace( prefix, "FF", &s[0] );
+    replace( "SCH", "SSS", &s[0] );
+ 
+    char const* const suffix1[] = { "EE", "IE", 0 };
+    char const* const suffix2[] = { "DT", "RT", "RD", "NT", "ND", 0 };
+    if( multiReplace( suffix1, "Y", &s[n - 2] ) || multiReplace( suffix2, "D", &s[n - 2] ))
+    {
+        s.pop_back();
+        --n;
+    }
+ 
+    out += s[0];
+ 
+    char* vowels[] = { "A", "E", "I", "O", "U", 0 };
+    for( unsigned i = 1; i < n; ++i )
+    {
+        char* const c = &s[i];
+        if( !replace( "EV", "AV", c ) )
+            multiReplace( vowels, "A", c );
[…]

### 2019-05-29 Code/TrustWords/SimilarWords/similar_words.cpp

@@ -8,6 +8,7 @@
 #include "./modes/soundex.hpp"
 #include "./modes/levenshtien.hpp"
 #include "./modes/double_metaphone.hpp"
+#include "./modes/nysiis.hpp"
 
 std::string inputFileName = "";
 std::string outputFileName = "";
@@ -15,10 +16,14 @@ std::string outputFileName = "";
 static bool LEV_DISTANCE = false;
 static bool SOUNDEX = false;
 static bool METAPHONE = false;
+static bool COMBINED_MODE = false;
+
+static float COMBINED_TOLERANCE = 1;
 
 std::string SOUNDEX_CLI_TAG = "-s";
 std::string LEV_CLI_TAG = "-l";
 std::string METAPHONE_CLI_TAG = "-m";
+std::string COMBINED_MODE_TAG = "-c";
 
 /*
     Saves the similar words to a specified file
@@ -53,9 +58,33 @@ std::vector<std::string> load_CSV(std::string filePath)
 }
 
 /*
+    TODO
+*/
+function<std::string(std::string)> algorithms[] = {soundex, metaphone, nysiis}; 
+bool combined_mode(std::string word1, std::string word2)
+{
+    float total = 0.0;
+    for(auto al : algorithms)
+    {
+        auto code1 = al(word1);
+        auto code2 = al(word2);
+        auto lev = lev_distance(code1, code2);
+        
+        //TODO: add weights
+        auto subtotal = lev;
+        total += subtotal;
+    }
+
+    //DEBUG
+    // if (total <= COMBINED_TOLERANCE) std::cout << "[D] " << word1 << " -- " << word2 << std::endl;
+
+    return total <= COMBINED_TOLERANCE;
+}
+
+/*
     Compares each word using it's levistien distance
 */
-void find_similar_words(std::vector<std::string> words)
+void find_similar_words(std::vector<std::string> words, bool combined=false)
 {
     // ## Note ##
     // The format of saving to file after every word alongside a refresh of the vector is 
@@ -76,10 +105,10 @@ void find_similar_words(std::vector<std::string> words)
 
         // ########## PRE-COMP ########## //
         std::string pre_word_y;
-        if      (METAPHONE)  pre_word_y = DoubleMetaphone(word_y);
+        if      (METAPHONE)  pre_word_y = metaphone(word_y);
         else if (SOUNDEX)    pre_word_y = soundex(word_y);
-
         // ############################## //
+
         for (std::string word_x : words)
         {
[…]

### 2019-05-29 Code/TrustWords/create_perms.py

@@ -393,8 +393,6 @@ def args():
     if args.num_words:
         number_of_words = args.num_words[0]
 
-    
-
     # Loads the file paths
     if args.similar:
         similar_mappings_file_name = args.similar[0]

### 2019-05-30 Documents/literature_review/pages/review_content.tex
Changes; - Started formalising the plan for the project - Added elements to the archive - Re-ordered LaTeX documents in the directory
Changes; - Working alterations to literature review - Created first draft of my plan sent off to Sia

--- 2019-05-28 Literature_Review/pages/review_content.tex
@@
-% \section{Possible research questions}
-
-% Overall the research will aim to investigate the strength of pEp's Trustword fingerprint mappings, and the ease in which partial collisions can be obtained for keys and how this will ultimately affect the end user(s).
-
-% Key areas that will be looked into:
-% \begin{itemize}
-%     \item Is the recommended minimum number of Trustwords enough to provide a basic level of security.
-%     \item What attributes make a strong general wordlist for fingerprint mapping and does the Trustword implementation exhibit these features.
-%     \item How easy is it to generate similar keys that attack a targeted key pair?
-%     \item How can similarity be quantified in terms of words? Does this include pronunciation or visual aspects?
-%     \item As usability is the main justification for the use of Trustwords are there alternatives that provide the same usability but with more security?
-% \end{itemize}
-
 \section{Review - Fingerprint representations}
@@
 \subsection{Fingerprint representation comparison}
+
+\textbf{TODO: } - Create written introduction setting the scene.
 
@@
 The aim of the study was to provide the first insight into the best encoding scheme used to represent a hash fingerprint.
-The schemes used were Base32, English words, Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Flag Ext\footnote{The author's own improvement on Flag} and finally Chinese, Korean and Japanese symbol encoding.
+The schemes used were Base32, English words, Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Flag Ext\footnote{The authors' own improvement on Flag} and finally Chinese, Korean and Japanese symbol encodings.
 A total of 436 participants were assessed in the study.
@@
 \\
-The authors' decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes) was due to their similarity to Base32 and their well-known deficiencies.
+The authors' decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes) was based on their own claims with the schemes similarities to Base32 and their well-known deficiencies.
 This is not consistent with available research.
@@
 In terms of encoding schemes, the paper ranked Numerical, Alphanumerical and Words as the top three encoding schemes (These were all with Compare-and-Confirm).
-This took into consideration the usability and security of the scheme.
-This is relatively consistent with other literature where numerical and written encoding schemes seem to be the most effective overall.
+This recommendation took into consideration the usability and security of the scheme and is relatively consistent with other research where numerical and written encoding schemes seem to be the most effective overall.
 
@@
 
-The relevant comparison methods tested were,Compare-and-Confirm, Compare-and-Select and Compare-and-Enter.
+The relevant comparison methods tested were, 
+``Compare-and-Confirm'', ``Compare-and-Select'' and ``Compare-and-Enter''.
 These are almost exactly the same encoding schemes assessed in the relevant research literature.
@@
 paper only reviewed encodings of 4 digit long strings.
-This, therefore,limits the applicability of the results in comparison to other fingerprint encoding literature.
-Between the two rounds, the authors dropped ``Confirm-and-Enter'' due to its low usability and over similarity to a similar scheme called ``Copy'' (used for passphrase verification).
-The low rating for Confirm-and-Enter is in contrast with research performed by Kainda \textit{et al.}\cite{kainda2009usability} They ranked Confirm-and-Enter as the 2nd most usable system.
-With changes to the UX of Confirm-and-Confirm backed up by external research \cite{palmer1990attentional}\cite{hammer2009category} the second round of research was performed with a new set of participants.
+This, therefore, limits the applicability of the results in comparison to other fingerprint encoding literature.
+Between the two rounds, the authors dropped Confirm-and-Enter due to its low usability and over similarity to a similar scheme called ``Copy'' (used for passphrase verification).
+The low rating for Confirm-and-Enter is in contrast with research performed by Kainda \textit{et al.}\cite{kainda2009usability} where they ranked Confirm-and-Enter as best method overall.
+With changes to the UX of Compare-and-Confirm backed up by external research \cite{palmer1990attentional}\cite{hammer2009category} the second round of research was performed with a new set of participants.
 The alterations took Compare-and-Confirm from 20\% to 0\% fatal error rate (FER).
@@
 The authors, therefore, recommended ``Compare-and-Confirm'' as the overall best choice for comparison methods.
-Again, comparing this word to the most similar work done by Kainda \textit{et al.}\cite{kainda2009usability} this is consistent with their findings where they ranked ``Compare-and-Confirm'' as the most secure comparison method.
+Comparing this research to the work done by Kainda \textit{et al.}\cite{kainda2009usability}; this is consistent with their findings where they ranked ``Compare-and-Confirm'' as superior to that of ``Compare-and-Select'' in all regards.
 
 Overall, the paper provides a sizeable insight into suitable methods of comparison, this is due to the cross over between fingerprint comparison and secure device pairing.
-This paper is limited in terms of the short strings compared, the different overall research aim and the size of the number of participants used in the studies.
-In terms of security of the schemes, the results were consistent with that of alternative research but clashed when usability was considered.
-This, however, may be due to the differing use-cases of the comparison methods.
+This paper is limited in terms of the very short strings compared, the different overall research aim and the size of the number of participants used in the studies.
+In terms of overall recommendations, the results were consistent with that of alternative research with the exception of recommendations regarding ``Compare-and-Enter''.
+This, however, may be due to the differing use-cases of the comparison methods in the two respective studies.
 
@@
 Another limitation is the scant amount of research solely investigating modes of comparison, where the literature only contains two papers with this aim.
-Even these limitations, as a whole the literature on this topic has provided a relatively comprehensive and coherent view on the usability of textual and visual hash encoding schemes.
+This is, therefore, an area that requires further research.
+A potential research avenue could be the analysis of comparison methods in unique scenarios, one example of this could be the idea of ``remote-vs-proximity'' proposed by M.
+Shirvanian \textit{et al.}\cite{shirvanian2017pitfalls}.
+Even with these limitations, as a whole the literature on this topic has provided a relatively comprehensive and coherent view on the usability of textual and visual hash encoding schemes with relatively clear recommendations on methods of comparison and suitable encoding schemes.
 
@@
 As mentioned in previous sections visual encoding schemes have been shown to have mixed success, with low security being one of their most alarming flaws.
-This research laid the foundation for further work in analysing the security of visual encoding schemes (as discussed in the previous section).
+This research laid the foundation for further work in analysing the security of visual encoding schemes.
 
@@
 Since the paper's publication in 2009, there seems to have been no research building on the work of the authors.
-This highlights the current gap in the available literature.
+This highlights a current gap in the available literature.
 
@@
 Saxena}\cite{karole2009improving} looked into ways to improve the security of a textual representation.
-This research aim is to improve the secure device pairing process of comparing two numerical values.
-The devices used (Nokia 6030b; Mid-range devices at the time of publication) and short SAS compared results in findings that are not directly applicable in a fingerprint comparison context.
+This research aim was to improve the secure device pairing process of comparing two numerical values.
+The devices used (Nokia 6030b; Mid-range devices at the time of publication) and the SAS compared results in findings that are not directly applicable in a fingerprint comparison context.
 
@@
 \cite{juola1996whole} and their work in generating a word list where phonetic distinctiveness was prioritised.
-Each word is mapped to one byte where the unique aspect of the word list is the separation of ``even'' and ``odd'' words where ``even'' byte positions are sample from the even-list and ``odd'' from the odd-list.
+Each word is mapped to a single byte.
+The unique aspect of the word list is the separation of ``even'' and ``odd'' words where ``even'' byte positions are sample from the even-list and ``odd'' from the odd-list.
 This effectively creates two sub-word lists.
-The pairing of these word lists were determined through the use of a Genetic algorithm with phonetic distance as the metric.
+The maximisation of linguistic distinctiveness of these word lists were maximised through the use of a Genetic algorithm.
 The paper also includes a study on effective measures of ``linguistic distances'' of words and provided an in-depth discussion into these areas.
@@
 This implementation was again, empirically evaluated by Dechand \textit{et al.}\cite{dechand2016empirical}.
-Older work by N.
-Haller with the S/KEY\cite{haller1995s} shows the implementation of a system designed to represent a hash as a series of six short words.
+Older work by \textbf{N.
+Haller} with the S/KEY\cite{haller1995s} shows the implementation of a system designed to represent a hash as a series of six short words.
 However, this system is designed for a one-time-password purpose and only provides word mappings for basic human usability of the password and not within a fingerprint verification context.
@@
 Full mappings (no duplication of words) would, therefore, require $2^{16}$ words in the dictionary and arguably is higher than most users vocabulary.
-This deviation from the norm has not been currently backed up by research.
-Therefore, highlighting on a gap in the current literature.
+this deviation from the norm has not been currently backed up by research.
+Moreover the main RFC documentation still remains in a draft stage and states \textit{``It is for further study, what minimal number of words (or entropy) should be required.''}.
+These aspects clearly highlight on a gap in the current literature.
 
@@
 The fragmentation of this research leaves room for further work into this topic area.
-Alongside this, findings from the previous sections research shows that human language based encodings provided the best usability and, therefore, should be a target for further research looking to improve upon security and usability.
+Alongside this, findings from the previous sections research shows that human language based encodings provided the best usability and, therefore, should be a target for further research looking to improve upon their security and usability.
 
@@
 This differs from previously examined work due to papers discussing the performance and fallibility of encoding schemes simulated the attack without consideration for how the attack would be performed.
-
 Research in this area is scant, with lots of research attention being directed towards the security of Man-in-the-Middle (MITM) attacks and not the encoding schemes themselves.
@@
 The paper contains an implementation with a ``1.2GHz CPU'' being able to obtain 130,000 H/s (With MD5).
-In comparison to this, a mid-range Intel i5-3320M CPU can today obtain 111,700,000 MD5 H/s shows that the results obtained from the paper are outdated.
+In comparison to this, a mid-range Intel i5-3320M CPU can today obtain 111,700,000 MD5 H/s.
+This shows that the results obtained from the paper are significantly outdated.
 However, even with the low hash rate, the author was able to obtain some promising results.
@@
 Overall the paper shows an interesting way to create partial fingerprint matches but is not quantified by any empirical evidence gathered on real world users.
-This, therefore, leaves gaps in the coverage of this literature.
+This, therefore, highlights on gaps in the coverage of this literature.
 

### 2019-05-30 Documents/project_plan/pages/work_plan.tex
Changes; - Added multi metric mode to Similar_words.cpp - Added some more detail to the plan
Changes; - Working alterations to literature review - Created first draft of my plan sent off to Sia

@@
 
-    \item However, the mapping of words to 16-bits is yet to be proved as secure as this is the highest number of bits per word seen in the literature.
+    \item However, the mapping of words to 16-bits is yet to be proved as secure as this is the \textbf{highest number of bits per word}s seen in the literature.
+This results in the number of words required being higher than that of the users' vocabulary and even the number of total words in the respective language.
 
@@
 Overall the research will aim to investigate the strength of pEp's Trustword fingerprint mappings, and the ease in which partial collisions can be obtained for keys and how this will ultimately affect the end user(s).
-This will be accompanied by recommendations into how the TrustWord system can be altered to provide maximum security alongside research into what makes an effective wordlist.
+This will be accompanied by recommendations into how the TrustWord system can be altered to provide increased security alongside research into what makes an effective wordlist.
 
@@
 
-    \item As usability is the main justification for the use of Trustwords are there alternatives that provide the same usability but with more security?
+    \item As usability is the main justification for the use of Trustwords does the increase in usability justify the hypothesised reduction in security?
 \end{itemize}
-
-% \section{RFC drafts}
-% \subsection{draft-marques-pep-handshake-02}
-% ``Short Trustword Mapping (S-TWM) requires a number of Trustwords that MUST retain \textbf{at least 64 bits} of entropy.
-Thus, S-TWM results into at least \textbf{four Trustwords} to be compared by the user."
-
-% Showing that 4 words is too low in certain cases could be very useful?
-
-% \subsection{draft-birk-pep-trustwords-00}
-% In another draft document it also states:
-
-% ``It is for further study, what minimal number of words (or entropy) should be required."
-
-% This shows there is some sort of research gap.
 
@@
 \subsection*{\hyperref[ref:wordlist]{Wordlist characteristic analysis}}
-This area will look into characteristics that are attractive when designing a wordlist. These will be used later to possibility improve the trustword implementation.
+This area will look into characteristics that are attractive when designing a wordlist.
+These will be used later to possibility improve the trustword implementation.
+Past research could provide guidance on this aspect.
 
 \subsection*{Analysis into effective ``similarity'' metrics}
-\textit{TODO}
+This section will involve research into how similarities in words can be quantified. Which options provide us the best balance of number of matches and accuracy of matches?
 
 \subsection*{Development of a tool used to find partial collisions for wordlist mappings}
-This tool would be fed two keys, one static and one the ``target''.
+This tool would be fed two keys, one ``static'' and one the ``target''.
 The tool would then generate keys for the ``target'' that create a similar overall wordlist mapping.
@@
 The similarity metric will generate a list of keys that provide similar matches, the tool will then hash large number of PGP keys to generate partial matches.
+This is useful to define an actual measure of the real-world feasibility.
+This is one aspect missing from the literature as other papers have simulated attacks on encoding schemes.
 
@@
 Alongside this, the feasibility of generating partial collisions will be assessed.
-The security could be quantified by testing the current implementation out on real users and determining the False acceptance rate of near attacks.
-This could be used as a baseline.
+The security could be quantified by testing the current implementation out on real users and determining the False Acceptance Rate of near attacks.
+This could be used as a baseline for improvements to be compared later.
 
@@
 
-\section{In-depth breakdown}
+% \section{In-depth breakdown}
 
-\subsection{Wordlist characteristic analysis}
-\label{ref:wordlist}
-\begin{itemize}
-    \item Investigation into characteristics of a strong wordlist
-    \begin{itemize}
-        \item Distinctiveness
-        \item Homonyms (Visual)
-        \item Homophones (Pronunciation)
-        \item Length
-        \item Current ways to define linguistic distance:
-        \begin{itemize}
-            \item \textbf{Visual:}
-            \begin{itemize}
-                \item Levenshtein (Edit distance)
-            \end{itemize}
+% \subsection{Wordlist characteristic analysis}
+% \label{ref:wordlist}
+% \begin{itemize}
+%     \item Investigation into characteristics of a strong wordlist
+%     \begin{itemize}
+%         \item Distinctiveness
+%         \item Homonyms (Visual)
+%         \item Homophones (Pronunciation)
+%         \item Length
+%         \item Current ways to define linguistic distance:
+%         \begin{itemize}
+%             \item \textbf{Visual:}
+%             \begin{itemize}
+%                 \item Levenshtein (Edit distance)
+%             \end{itemize}
 
-            \item \textbf{Auditory}:
-            \begin{itemize}
-                \item Soundex
-                \item Metaphone
-            \end{itemize}
-        \end{itemize}
+%             \item \textbf{Auditory}:
+%             \begin{itemize}
+%                 \item Soundex
+%                 \item Metaphone
+%                 \item NYSIIS
+%                 \item Match Rating
+%             \end{itemize}
+%         \end{itemize}
 
-    \end{itemize}
+%     \end{itemize}
 
-    \item Analysis into the strength of the TrustWords using previously obtained metrics.
+%     \item Analysis into the strength of the TrustWords using previously obtained metrics.
 
-    \item Investigation into the strength of other wordlists using defined metrics.
-    \begin{itemize}
-        \item PGP word list
-        \item SafeSlinger
-    \end{itemize}
+%     \item Investigation into the strength of other wordlists using defined metrics.
+%     \begin{itemize}
+%         \item PGP word list
+%         \item SafeSlinger
+%     \end{itemize}
 
-\end{itemize}
+% \end{itemize}
 
-\subsection{Security of Trustwords}
-\label{ref:trustwords}
-Here we'd look at the words used in the dictionary and attempt to generate lists of keys that would generate partial collisions these would then be fed into the created tool
+% \subsection{Security of Trustwords}
+% \label{ref:trustwords}
+% Here we'd look at the words used in the dictionary and attempt to generate lists of keys that would generate partial collisions these would then be fed into the created tool
 
-\subsection{Security of alternative wordlists}
-\label{ref:alternatives}
+% \subsection{Security of alternative wordlists}
+% \label{ref:alternatives}
 
-\subsection{Security of implemented recommendations}
-\label{ref:rec}
+% \subsection{Security of implemented recommendations}
+% \label{ref:rec}

### 2019-05-30 Documents/literature_review/pages/review_content.tex
Changes; - Added more content to the literatuer view. I'm attempting to get a good structure for comparing the papers - Added a new combined wordlist generated using Soundex, Metaphone NYSIIS and all distinquished using Levenshtien

@@
 \textbf{TODO: } - Create written introduction setting the scene.
+% \textbf{TODO: } - Check evaluation with each paper in regards to:
+% \begin{itemize}
+%     \item Participant size [P]
+%     \item Social aspects, where have they come from? Age? Gender? Occupation?  [S]
+%     \item Target entropy [E]
+%     \item Attacker strength [A]
+% \end{itemize}
+% [P, S, E, A]
 
-Current research in ways to represent and validate fingerprints has almost exclusively focused on the usability of such schemes.
+Current research into human-based validation of fingerprints has almost exclusively focused on the usability of such schemes.
 The following section will individually discuss available research findings alongside an overall comparison of the research recommendations.
 
+% [A]
 \textbf{Hsu-Chun Hsiao, \textit{et.
-al.}} produced the first work in this area in their paper: \textit{A Study of User-Friendly Hash Comparison Schemes}\cite{hsiao2009study} in around 2009.
-The aim of the study was to provide the first insight into the best encoding scheme used to represent a hash fingerprint.
-The schemes used were Base32, English words, Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Flag Ext\footnote{The authors' own improvement on Flag} and finally Chinese, Korean and Japanese symbol encodings.
+al.}} produced the first work in this area in their paper: \textit{A Study of User-Friendly Hash Comparison Schemes}\cite{hsiao2009study}.
+The main aim of the study was to provide the first insight into the best encoding schemes used to represent a hash fingerprint.
+The schemes used were Base32, English words, Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Flag Ext\footnote{The authors' own improvement on Flag} and finally Chinese, Korean and Japanese symbolic encodings.
 A total of 436 participants were assessed in the study.
 
-Alongside the main aim of the paper, the authors wanted to provide empirical links between participant attributes (such as age or gender) and performance with the encoding scheme.
+In addition to the central aims of the paper, the authors intended to provide empirical links between participant attributes (such as age or gender) and performance with the encoding scheme.
 This is something rarely seen in the related research.
 Hsu-Chun Hsiao \textit{et al.} also provided two categories of similarities; ``hard'' and ``easy''.
+``Hard'' pair only have a very small difference, therefore, difficult to distinguish.
 These were designed to be the worst and best case respectively.
-As a final aim and the reason for the inclusion of Chinese, Korean and Japanese characters was to research if being a native speaker assists the user in distinguishing subtle differences between encodings in the respective language.
+The reasoning behind inclusion of Chinese, Korean and Japanese characters was to investigate the links between language ability and distinguishing subtle differences between encodings in the respective language.
 The entropy of encodings ranged from 22-bits to 28-bits.
-This is extremely low in comparison to similar research.
-However, this can be attributed to the age of the paper.
-\\
-The authors' decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes) was based on their own claims with the schemes similarities to Base32 and their well-known deficiencies.
-This is not consistent with available research.
-For example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}\cite{dechand2016empirical} it was shown numerical representations performed significantly better than that of Base32.
+This is the lowest level of entropy used in the assessed literature.
+To quantify this a hash rate of 10 MH/s SHA-1 compressions would be able to find a match for 28-bits in 26.8 seconds.
+This is addressed by the author at a stage in the paper where they state \textit{``However, increasing entropy is not a solution because it sacrifices usability and accuracy.
+With more entropy, representations will contain longer sequences of characters or more minute details which will lead to increased time and errors during comparisons.''}.
+This claim is entirely unsubstantiated with any empirical evidence alongside no discussion into why the level of entropy was chosen.
+This, however, was followed by in interesting recommendation into the use of commitments\cite{blum1982coin}.
+This provides an attacker with a single chance to find a collision, thus, providing a valid use case for low levels of entropy.\\
+Another limitation is the authors' decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes).
+This was based on their own claims on similarities to Base32 and ``well-known deficiencies" in the excluded schemes.
+This point was provided with no further justification or quantified in any way.
+It is also not consistent with available research, for example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}\cite{dechand2016empirical} it was shown numerical representations performed significantly better than that of Base32.
 
@@
 
-In conclusion, the paper provided a very strong foundation for further research due to the wide variety of topics touched upon.
-However, its age means that results cannot be applicable to modern day scenarios, and oversights in the development of the study such as the exclusion of hexadecimal encoding and the lack of information gained on the perceived usability of the scheme from users results in an ultimately incomplete study.
+In conclusion, the paper touched upon a wide variety of topics.
+Moreover, the consideration into the attributes of participants and consideration into how this would affect their performance with the scheme was a substantial addition.
+This provides a higher level of validity to the results and is something severely lacking from the literature assessed.
+However, the age of the study limits the applicability to modern day scenarios, and oversights in the development of the study such as the exclusion of hexadecimal encoding and the lack of information gained on the perceived usability of the scheme from users results in an incomplete study.
+In addition, the paper failed to consider the quantification of attacker strength and, therefore, failed to discuss the feasibility of these attacks.
 
+% [A]
 \textbf{Kainda \textit{et al.}}\cite{kainda2009usability} in 2009 investigated fingerprint representations and comparison methods in the context of using humans as the Out-Of-Band (OOB) channel for secure device pairing.
@@
 The overall schemes were then quantified using a metric known as the Single Usability Metric (SUM)\cite{sauro2005method}.
-This provides an elementary way to rank and compare the schemes, thus improving the usability of the results.
-However, the one apparent downside to the experimental side of the study is the 40 participants enrolled.
-This is one of the smallest sizes of enrolment in the literature and thus, puts a possible limit on the accuracy and applicability of the obtained results.
+This provides an elementary way to rank and compare the schemes, thus improving the potential validity of the results.
+However, the one apparent downside to the experimental side of the study is the 30 participants enrolled.
+This is one of the smallest sizes of enrolment in the literature and thus, puts a possible limit on the reliability and applicability of the obtained results.
+This limitation was, however,  supplemented by a consideration into the demographics of the participants enrolled.
+The participants were evenly split between male and female alongside an age range of 18 to 75.
 
@@
 In terms of encoding schemes, the paper ranked Numerical, Alphanumerical and Words as the top three encoding schemes (These were all with Compare-and-Confirm).
-This recommendation took into consideration the usability and security of the scheme and is relatively consistent with other research where numerical and written encoding schemes seem to be the most effective overall.
+This recommendation took into consideration the usability and security of the scheme and is relatively consistent with other research where numerical and English language based encoding schemes seem to be the most effective overall.
 
 In conclusion, this paper provided a highly comprehensive review of all the aspects of human fingerprint verification, where it reviewed all the elements involved in the process.
-The only limitation of the paper is the size of the participants enrolled for the study.
+Limitations of the paper involved the inconsistent and low range of entropy (20-bits to 40-bits)alongside the size of the participants enrolled for the study.
 
+% TODO: Implement checks below:
 \textbf{Ersin Uzun \textit{et al.}}\cite{uzun2007usability} exclusively reviewed comparison methods.

### 2019-05-31 Documents/literature_review/pages/review_content.tex
Changes; - Quantified results for all the fingerprint encdoing papers - Reordered papers - Small changes to lit review wording

@@
 \textbf{TODO: } - Create written introduction setting the scene.
+\textbf{TODO: } - Summarise research questions after lit' review. Back them up using my discussion.
 % \textbf{TODO: } - Check evaluation with each paper in regards to:
@@
 % [A]
-\textbf{Hsu-Chun Hsiao, \textit{et.
-al.}} produced the first work in this area in their paper: \textit{A Study of User-Friendly Hash Comparison Schemes}\cite{hsiao2009study}.
+Some of the first work in this area was performed by \textbf{Hsu-Chun Hsiao, \textit{et al.}}\cite{hsiao2009study}.
 The main aim of the study was to provide the first insight into the best encoding schemes used to represent a hash fingerprint.
@@
 replacing the victim where this performed with a 
-\textasciitilde18\% success rate. Morphing gained an 
+$\sim$18\% success rate. Morphing gained an 
 overall success rate of 50.58\% and Reordering a very 

### 2019-05-31 Documents/literature_review/pages/review_content.tex
Changes; - Added TODOs
Changes; - Quantified accuracy with a table - Added results for speed of comparison - Small wording changes

@@
 
-\textbf{TODO: } - Create written introduction setting the scene.
-\textbf{TODO: } - Summarise research questions after lit' review. Back them up using my discussion.
+\textbf{TODO: } - Create written introduction setting the scene. \\
+\textbf{TODO: } - Add participant size to M. Shirvanian (25) \\
+\textbf{TODO: } - Create a background section for Compare-and-X
+
 % \textbf{TODO: } - Check evaluation with each paper in regards to:
@@
 This is a common theme that appears in the majority of the reviewed papers.
-Other references made within the paper touch upon the vulnerabilities and usability issues present with the way humans interact with the security systems.
-Examples of these are studies showing humans find it difficult to comprehend long and ``meaningless" strings and the lack of actual comparison performed by users in live scenarios.
-These are, however, acknowledged as limitations in the later stages of the paper.
 The paper has defined the upper and lower bound costs of the attacker's resources and strength as \$610K to \$16B, with an ability to control 80-bits of the fingerprint.
 This in comparison to other papers is high and is almost encroaching into the realm of a highly sophisticated attacker.
-Therefore, the lack of consideration for the lower-end of the attack resource spectrum can be considered another limitation.
+Therefore, the lack of consideration for the lower-end of the attack resource spectrum can be considered a limitation.
 
@@
 \subsubsection{Topic conclusion}
+
+To provide a visual comparison the accuracy results of the papers have been provided in Table~\ref{tab:results}.
+Each paper used a unique, and, therefore, have been translated into overall accuracy.
+Due to some of the differing characteristics of the papers ultimatly affecting results, Table \ref{tab:attacker} has also be provided.
+This table is useful to compare the health of the study and chosen sizes that may affect the accuracy and reliability of the results.
+
+\textbf{TODO:} Usability table
+
+\begin{table}
+    \makebox[\textwidth][c]{
+        \input{tables/fingerprint_comparison.tex}
+    }%
+    \caption{Accuracy comparison of textual and graphical encoding schemes}
+    \label{tab:results}
+\end{table}
+
+\begin{table}
+    \makebox[\textwidth][c]{
+        \input{tables/fingerprint_attacker_stren.tex}
+    }%
+    \caption{Paper attribute comparison}
+    \label{tab:attacker}
+\end{table}
 
@@
 \textbf{TODO: } Create an overall summary of all the gaps identified
+
+\section{Research Questions}
+\textbf{TODO: } - Backup choice of questions up using my previous discussion.

### 2019-05-31 Documents/literature_review/tables/fingerprint_attacker_stren.tex
Changes; - Quantified accuracy with a table - Added results for speed of comparison - Small wording changes

\begin{tabular}{c|ccccc}
    \toprule
                        & Hsu-Chun\cite{hsiao2009study}      
                        & Kainda\cite{kainda2009usability}      
                        & Dechand\cite{dechand2016empirical}
                        & Tan\cite{tan2017can}      
                        & M. Shirvanian\cite{shirvanian2017pitfalls}
                        \\\hline
    Attacker Strength\footnote{Some attacker strengths are estimations due to the lack of quantification in some papers.}   
    & $\sim2^{28}$  & $\sim2^{40}$ & $2^{80}$ & $2^{60}$ & $\sim2^{242}$ \\
    Entropy Range       & 22-28 bits    & 20-40 bits   & 122 bits & 128 bits & 160-256 bits  \\
    No\degree  ~Participants     & 436           & 30           & 1047     & 661      & 25            \\
    \bottomrule
\end{tabular}

### 2019-06-03 Documents/literature_review/pages/review_content.tex
Changes; - Stated the re-write of the first section.  The previous state has been backed up for reference and persistance

--- 2019-05-31 Documents/literature_review/pages/review_content.tex
@@
-\section{Review - Fingerprint representations}
+\section{Introduction}
+The increasing use of public key cryptography by instant messaging and secure email means key fingerprint 
+verification is an ever more important task.
+One of the biggest risks to the security of the communication channel is a Man-in-the-middle (MiTM) attack .
+A successful MiTH attack can circumvent the encryption as it allows an attacker to read all the encrypted data.
+A countermeasure for this is the verification of each parties' fingerprint.
+\textbf{[...]}
 
+% \textbf{TODO: } Finish introduction
+
+% \textbf{TODO: } - Improve the flow of the first section, need to phrase it like I'm telling a story
+% \textbf{TODO: } - Create written introduction setting the scene. \\
+% \textbf{TODO: } - Add participant size to M. Shirvanian (25) \\
+% \textbf{TODO: } - Create a background section for Compare-and-X
+% \\
+% \textbf{TODO: } - Create comparison area where inconsistencies are compared
+
+\section{Literature Review}
 \subsection{Fingerprint representation comparison}
 
-\textbf{TODO: } - Create written introduction setting the scene.
-\textbf{TODO: } - Summarise research questions after lit' review. Back them up using my discussion.
-% \textbf{TODO: } - Check evaluation with each paper in regards to:
-% \begin{itemize}
-%     \item Participant size [P]
-%     \item Social aspects, where have they come from? Age? Gender? Occupation?  [S]
-%     \item Target entropy [E]
-%     \item Attacker strength [A]
-% \end{itemize}
-% [P, S, E, A]
+Fingerprints are used to quickly compare the similarity of two keys.
+The comparison occurs between the digest of a strong one-way hash function.
+Historically these have been represented as a hexadecimal string and users were tasked with manually comparing fingerprints between two substrates, for example, a monitor screen and a business card.
+We will refer to this process throughout the paper as the \textit{``authentication ceremony''}.
+\\
+It has been shown that the average human can only hold 7-digits worth of data in our working memory\cite{miller1956magical}.
+This rules out the possibility of comparing full digests.
+For examples SHA-1 is 40 hex digits (160-bit) and, therefore, will make it difficult for effective comparison.
+Therefore , if the  process is to involve humans interaction, there is a need for schemes that work effectively with our abilities and senses.
 
-Current research into human-based validation of fingerprints has almost exclusively focused on the usability of such schemes.
-The following section will individually discuss available research findings alongside an overall comparison of the research recommendations.
+Research in this area has taken various encoding schemes and compared their fallibility to impersonated attacks.
+Impersonation of a key would involve brute force of the encoding schemes through the mass creation of keys.
+The main elements of comparison have been accuracy of attack detection and time to complete the comparison.
+In this context we will consider the metrics a measure of security and usability respectively.
 
-% [A]
-Some of the first work in this area was performed by \textbf{Hsu-Chun Hsiao, \textit{et al.}}\cite{hsiao2009study}.
-The main aim of the study was to provide the first insight into the best encoding schemes used to represent a hash fingerprint.
-The schemes used were Base32, English words, Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Flag Ext\footnote{The authors' own improvement on Flag} and finally Chinese, Korean and Japanese symbolic encodings.
-A total of 436 participants were assessed in the study.
+\subsection*{Effective schemes}
+Results 
+from the literature consistently show the effectiveness of language based encodings (Words or Sentences).
+This was shown in \cite{dechand2016empirical}, \cite{tan2017can} and \cite{kainda2009usability} with the accuracy of these schemes all being above 94.00\%.
+In all cases these were the best scemes in terms of accuracy.
+The exception to this is the work performed by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63.00\% (Comparisons of methodology will be discussed in later sections).
+\\\\
+Aside from textual representations were graphical schemes.
+Examples of schemes assessed were: Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Vash\footnote{https://github.com/thevash/vash}, OpenSSH visual host key and Unicorns\footnote{https://unicornify.pictures/} to name a few.
+Accuracy from these schemes were mixed with positive results obtained by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} where their best accuracy was achived by Random Art (94.00\%) and Flag Ext.\footnote{The authors' own improvement on Flag}(88.00\%).
+On the other hand, the worst accuracy was obtained by Flag(50\%).
+The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can} where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
+\\
+In terms of usability of graphical schemes the literature concurred on their ease-of-use.
+In terms of speed of comparison all schemes consistently obtained some of the quickest comparisons times.
+This is also supported indirectly from the the comparison results of alternative literature \cite{kainda2009usability}\cite{dechand2016empirical} where with these in consideration graphical schemes still remain the quickest overall.
+In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with only two papers including graphical schemes in their comparison.
+This is, therefore, a candidate for further research.
 
-In addition to the central aims of the paper, the authors intended to provide empirical links between participant attributes (such as age or gender) and performance with the encoding scheme.
-This is something rarely seen in the related research.
-Hsu-Chun Hsiao \textit{et al.} also provided two categories of similarities; ``hard'' and ``easy''.
-``Hard'' pair only have a very small difference, therefore, difficult to distinguish.
-These were designed to be the worst and best case respectively.
-The reasoning behind inclusion of Chinese, Korean and Japanese characters was to investigate the links between language ability and distinguishing subtle differences between encodings in the respective language.
-The entropy of encodings ranged from 22-bits to 28-bits.
-This is the lowest level of entropy used in the assessed literature.
-To quantify this a hash rate of 10 MH/s SHA-1 compressions would be able to find a match for 28-bits in 26.8 seconds.
-This is addressed by the author at a stage in the paper where they state \textit{``However, increasing entropy is not a solution because it sacrifices usability and accuracy.
-With more entropy, representations will contain longer sequences of characters or more minute details which will lead to increased time and errors during comparisons.''}.
-This claim is entirely unsubstantiated with any empirical evidence alongside no discussion into why the level of entropy was chosen.
-This, however, was followed by in interesting recommendation into the use of commitments\cite{blum1982coin}.
-This provides an attacker with a single chance to find a collision, thus, providing a valid use case for low levels of entropy.\\
-Another limitation is the authors' decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes).
-This was based on their own claims on similarities to Base32 and ``well-known deficiencies" in the excluded schemes.
-This point was provided with no further justification or quantified in any way.
-It is also not consistent with available research, for example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}\cite{dechand2016empirical} it was shown numerical representations performed significantly better than that of Base32.
-
-Findings from the paper showed that age and gender do not affect the accuracy of the scheme, however, younger participants were significantly faster. \\
-The paper recommends Base32, Random Art, T-Flag or their own improvement; Flag Ext.
-These encoding recommendations were also supplemented with a review of the requirements required by these schemes.
-The recommendation of graphical encoding schemes is inconsistent with alternative literature, where most other papers have found graphical encodings easy to use but insecure.
-In terms of language comprehension; being able to speak the language assists in the ability to discern the differences between hard pairs.
-Subsequently, knowledge of the language did not assist in differentiating easy pairs as these had high accuracy regardless of the spoken language.
-
-In conclusion, the paper touched upon a wide variety of topics.
-Moreover, the consideration into the attributes of participants and consideration into how this would affect their performance with the scheme was a substantial addition.
-This provides a higher level of validity to the results and is something severely lacking from the literature assessed.
-However, the age of the study limits the applicability to modern day scenarios, and oversights in the development of the study such as the exclusion of hexadecimal encoding and the lack of information gained on the perceived usability of the scheme from users results in an incomplete study.
-In addition, the paper failed to consider the quantification of attacker strength and, therefore, failed to discuss the feasibility of these attacks.
-
-% [A]
-\textbf{Kainda \textit{et al.}}\cite{kainda2009usability} in 2009 investigated fingerprint representations and comparison methods in the context of using humans as the Out-Of-Band (OOB) channel for secure device pairing.
-This study was comprehensive and assessed a wide variety of concepts.
-This is one of the few papers in the literature that assessed the way to compare encodings alongside the representations themselves.
-For comparison methods the paper looked into ``Compare-and-Confirm'', ``Compare-and-Select'', ``Compare-and-Enter'' and ``Barcode'' scanning.
-This set includes the most common ways of comparison according to available research.
-Alongside this, the paper reviews Numerical, Alphanumerical, Words, Sentences, Images, Melodies and Sound (Numerical/Alphanumerical).
-Again, this in comparison to similar literature is highly comprehensive.
-
-In terms of empirical data gathered by the paper, they reviewed the time completed to asses the representation and the number of security and non-security related errors.
-Furthermore, the authors also collected user opinion on ease-of-use, satisfaction and confidence of the reviewed schemes.
-The overall schemes were then quantified using a metric known as the Single Usability Metric (SUM)\cite{sauro2005method}.
-This provides an elementary way to rank and compare the schemes, thus improving the potential validity of the results.
-However, the one apparent downside to the experimental side of the study is the 30 participants enrolled.
-This is one of the smallest sizes of enrolment in the literature and thus, puts a possible limit on the reliability and applicability of the obtained results.
-This limitation was, however,  supplemented by a consideration into the demographics of the participants enrolled.
-The participants were evenly split between male and female alongside an age range of 18 to 75.
-
-Overall, if usability is the only consideration the paper ranked the comparison methods: Compare-and-Confirm, Compare-and-Enter, Compare-and-Select and Barcode.
-If, however, the consideration of security alongside usability is required the best is: Compare-and-Enter, Barcode, Compare-and-Confirm and Compare-and-Select.
-Research has been limited in this area of modes of comparison, however, the results from this paper are consistent with the limited alternative literature.
-In terms of encoding schemes, the paper ranked Numerical, Alphanumerical and Words as the top three encoding schemes (These were all with Compare-and-Confirm).
-This recommendation took into consideration the usability and security of the scheme and is relatively consistent with other research where numerical and English language based encoding schemes seem to be the most effective overall.
-
-In conclusion, this paper provided a highly comprehensive review of all the aspects of human fingerprint verification, where it reviewed all the elements involved in the process.
-Limitations of the paper involved the inconsistent and low range of entropy (20-bits to 40-bits)alongside the size of the participants enrolled for the study.
-
-% TODO: Implement checks below:
-\textbf{Ersin Uzun \textit{et al.}}\cite{uzun2007usability} exclusively reviewed comparison methods.
-This is performed in the context of ``Secure device pairing'' and thus some comparison schemes are tested that are not relevant in a fingerprint comparison context, for example  ``Choose-and-Enter'' (A participant chooses a passphrase from an available list and enters it into the other device).
-Thus, only relevant comparison scheme and their results have been extracted and compared.
-
-The relevant comparison methods tested were, 
-``Compare-and-Confirm'', ``Compare-and-Select'' and ``Compare-and-Enter''.
-These are almost exactly the same encoding schemes assessed in the relevant research literature.
-The paper also had two rounds of experiments including 40 participants each where changes were made to UX and format between these studies.
-Due to the ``Secure device pairing'' context, consideration needs to be made into the actual strings being encoded.
-Due to secure device pairing commonly utilising Short Authentication Strings (SAS) the
-paper only reviewed encodings of 4 digit long strings.
-This, therefore, limits the applicability of the results in comparison to other fingerprint encoding literature.
-Between the two rounds, the authors dropped Confirm-and-Enter due to its low usability and over similarity to a similar scheme called ``Copy'' (used for passphrase verification).
-The low rating for Confirm-and-Enter is in contrast with research performed by Kainda \textit{et al.}\cite{kainda2009usability} where they ranked Confirm-and-Enter as best method overall.
-With changes to the UX of Compare-and-Confirm backed up by external research \cite{palmer1990attentional}\cite{hammer2009category} the second round of research was performed with a new set of participants.
-The alterations took Compare-and-Confirm from 20\% to 0\% fatal error rate (FER).
-The same trend for Confirm-and-Select with it reducing its FER from 12.5\% to 5\%.
-The authors, therefore, recommended ``Compare-and-Confirm'' as the overall best choice for comparison methods.
-Comparing this research to the work done by Kainda \textit{et al.}\cite{kainda2009usability}; this is consistent with their findings where they ranked ``Compare-and-Confirm'' as superior to that of ``Compare-and-Select'' in all regards.
-
-Overall, the paper provides a sizeable insight into suitable methods of comparison, this is due to the cross over between fingerprint comparison and secure device pairing.
-This paper is limited in terms of the very short strings compared, the different overall research aim and the size of the number of participants used in the studies.
-In terms of overall recommendations, the results were consistent with that of alternative research with the exception of recommendations regarding ``Compare-and-Enter''.
-This, however, may be due to the differing use-cases of the comparison methods in the two respective studies.
-
-\textbf{Dechand \textit{et al.}}\cite{dechand2016empirical} empirically investigated the usability of 4 distinct textual representations evaluated with an experiment involving a total of 1047 participants.
-The textual representations were: Alphanumeric, Numeric, Words and Sentences.
-They assessed the number of attacks missed with each scheme alongside results from a questionnaire on the participants preferred scheme and perceived usability.
-
-The paper touches upon issues with decentralised methods of identification such a PGP's Web of Trust and the problems these solutions have with user adoption.
-These points are made in an attempt to validate the requirement for manual comparison of key based fingerprints.
-This is a common theme that appears in the majority of the reviewed papers.
-Other references made within the paper touch upon the vulnerabilities and usability issues present with the way humans interact with the security systems.
-Examples of these are studies showing humans find it difficult to comprehend long and ``meaningless" strings and the lack of actual comparison performed by users in live scenarios.
-These are, however, acknowledged as limitations in the later stages of the paper.
-The paper has defined the upper and lower bound costs of the attacker's resources and strength as \$610K to \$16B, with an ability to control 80-bits of the fingerprint.
-This in comparison to other papers is high and is almost encroaching into the realm of a highly sophisticated attacker.
-Therefore, the lack of consideration for the lower-end of the attack resource spectrum can be considered another limitation.
-
-Summarised findings from the paper state that conventional encodings such as Hexadecimal and Base32 perform worse than all other alternatives in a realistic threat model with over 10\% of users failing to detect an attack on these encoding schemes.
-The recommendations of the authors are to replace these encoding schemes with Words or Sentences due to their very high success rate and high usability scores.
-The performance of the Alphanumerical encoding schemes is relatively consistent with the literature, however, it is hard to say conclusively due to the small number of total schemes assessed making it hard to place alphanumerical encodings in an overall rating.
-
-\textbf{J Tan \textit{et al.}}\cite{tan2017can} work is very similar to that of the research already discussed.
-Eight distinct fingerprint representations were tested with over 661 participants.
-Each representation was tested using ``Compare-and-Confirm'' and ``Compare-and-Select''.
-The small difference with this paper is the inclusion of two novel graphical encodings Vash\footnote{https://github.com/thevash/vash} and Unicorns\footnote{https://unicornify.pictures/}.
-The compared schemes were: Hexadecimal, Alternating vowel/consonants, Words, Numbers, Sentences, OpenSSH visual host key, Vash and Unicorns.
-
-The target security level chosen was an entropy of 160-bits.
-This is a very high level of security in comparison to alternative literature.
-Alongside this, the paper defined attack strengths of an average $2^{60}$ with other specific use-cases for lower and higher attacker strength.
-Users were recruited via MTurk and assigned an experiment attempting to emulate a real-life condition (Comparison of a fingerprint on a business card).
-The real-world accuracy was one unique element that this paper concentrated on, this was portrayed through the authors' attention to detail when designing the experiment.
-
-Overall, results from the experiments emulated previously discussed literature.
-Textual representations faired effectively well with Words and Sentences again being some of the best options overall.
-Performance of graphical representation was mixed with OpenSSH having performance matching that of a strong textual mapping while Unicorns having the worst performance overall.
-This performance with graphical representations is consistent with the available literature apart from the positive performance of OpenSSH.
-The results of different modes of comparison were highly consistent with other studies where again the recommendation was to not use ``Compare-and-Select'' as its performance across the board was below even basic levels of security.
-
-\textbf{M.
-Shirvanian \textit{et al.}}\cite{shirvanian2017pitfalls} produced further work in the context of secure messaging pairing.
-This paper was unique for a number of reasons.
-First was to consideration for ``remote-vs-proximity'' pairing where, this is the first consideration of this aspect found in the literature.
-Second, was their studies aim into investigating fingerprint security and usability in a end-to-end encryption context.
-The study compared Numerical, Visual and Auditory representations.
-This is a standard setup for similar studies in the literature.
-QR code verification was also added to the proximity tests.
-They split the variance of attack severity into three levels; one character change, one block change and changes to the entire fingerprint.
-
-The findings from the paper showed a high false negative rate for all the schemes, this is an aspect also missing from the literature.
-Alongside this, results for usability were lower in a remote setting for all the schemes where the author comments on the expected nature of this result.\\
-The paper measured the number of successful attacks in the False Accept Rate (FAR).
-With this in mind images were the most secure method of authentication in the remote setting, but voted as the method with the worst usability.
-This is highly inconsistent with previous work in this area.
-However, this could be due to the unique setting of remote verification resulting in distinct results from user studies.
-Without further work in this area it is difficult to conclusively validate these results.
-In the proximity setting the results were negligible where at most 2.67\% of attacks were successful.
-In summary, this paper provides a unique look into the real-world aspects of fingerprint verification in a end-to-end context providing a unique viewpoint on the usability and possible security of the main fingerprint encoding schemes.
-
-\subsubsection{Topic conclusion}
-
-In conclusion for this section, there has been extensive work in the investigation of the usability of textual and visual encoding schemes alongside methods of comparison.
-There are mixed opinions about visual representations, however, the majority defines them as easy to use but severely lacking in security.
-Research on textual representations, however, is in agreement; natural language based encodings such as words or sentences provide some of the highest usability and security over the baseline performance of alphanumerical encodings.
-The literature also concurs on the use of Compare-and-Confirm as the best method of comparing fingerprints overall, with Compare-and-Select being highlighted for its poor security and usability.\\
-The starkest limitations of the literature are the range of participant and encoding entropy, where at its worst only 22-bits of entropy were tested.
-Another limitation is the scant amount of research solely investigating modes of comparison, where the literature only contains two papers with this aim.
-This is, therefore, an area that requires further research.
-A potential research avenue could be the analysis of comparison methods in unique scenarios, one example of this could be the idea of ``remote-vs-proximity'' proposed by M.
-Shirvanian \textit{et al.}\cite{shirvanian2017pitfalls}.
-Even with these limitations, as a whole the literature on this topic has provided a relatively comprehensive and coherent view on the usability of textual and visual hash encoding schemes with relatively clear recommendations on methods of comparison and suitable encoding schemes.
+\subsection*{Experimentation comparison}
 

### 2019-06-03 Documents/literature_review/appendix.tex
Changes; - Added more content to the new lit' review structure

\begin{appendices}
    \section{Encoding Scheme Results}
    \begin{table}[h!]
        \makebox[\textwidth][c]{
            \input{tables/fingerprint_comparison.tex}
        }%
        \caption{Accuracy of correct comparison for the encoding schemes assessed}
        \label{tab:results}
    \end{table}

    \begin{table}[h!]
        \makebox[\textwidth][c]{
            \input{tables/fingerprint_times.tex}
        }%
        \caption{Timing results in seconds for the related schemes}
        \label{tab:times}
    \end{table}
\end{appendices}

### 2019-06-03 Documents/literature_review/pages/review_content.tex
Changes; - Added more content to the new lit' review structure

@@
 \section{Literature Review}
-\subsection{Fingerprint representation comparison}
 
@@
 
-\subsection*{Effective schemes}
+\subsection*{Definition of terms}
+Throughout the paper various terms will be used to define elements of the authentication ceremony relevant to fingerprints verification.
+In this section well defined definitions will me made.
+This is to remove ambiguity and underlying associations readers may have for the words chosen.
+
+\textbf{\textit{Encoding scheme}} - This is the physical method of encoding used to represent the fingerprint.
+For example ``Hexadecimal'' or ``Words'' are a unique way to represent a fingerprint and thus, are encoding schemes.
+
+\textbf{\textit{Method of comparison}} - This is the way in which the encoding scheme is assessed by the user.
+The most common example and the one used as default is ``Compare-and-Confirm''.
+This as the name suggests is the \textit{comparison} of two fingerprints on different devices or mediums that are then \textit{compared}.
+Further examples of these method of comparisons will be explained in later sections.
+
+\subsection{Fingerprint representation comparison}
+
+\subsection*{Encoding scheme performance}
 Results 
@@
 
-\subsection*{Experimentation comparison}
+One unique paper in this research area was the work by \textbf{M.
+Shirvanian \textit{et al.}}\cite{shirvanian2017pitfalls} produced in the context of secure messaging pairing.
+This paper was unique for a number of reasons.
+First was to consideration for ``remote-vs-proximity'' pairing where, this is the first consideration of this aspect found in the literature.
+Second, was their studies aim into investigating fingerprint security and usability in a end-to-end encryption context.
+The study compared Numerical, Visual and Auditory representations.
+This is a standard setup for similar studies in the literature.
+QR code verification was also added to the proximity tests.
+
+The findings from the paper showed a high false negative rate for all the schemes, this is a consideration also missing from the literature.
+Alongside this, results for usability were lower in a remote setting for all the schemes where the author comments on the expected nature of this result.\\
+Images were assessed as being the most secure method of authentication in the remote setting, but voted as the method with the worst usability.
+This is highly inconsistent with all other work in this area.
+However, this could be due to the unique setting of remote verification resulting in distinct results from user studies.
+Without further work in this area it is difficult to conclusively validate these results.
+
+To provide a visual comparison the accuracy results of the papers have been provided in Table~\ref{tab:results} \& \ref{tab:times}.
+Each paper used a unique metric for measuring effectiveness, and, therefore, have been translated into ``overall accuracy''.
+
+\subsection*{Methods of comparison performance}
+As explained in the definition section ``methods of comparison'' are the ways used to compare fingerprints.
+Aside from ``Compare-and-Confirm'' (CaC) there is: ``Compare-and-Select'' (CaS) and ``Compare-and-Enter'' (CaE).
+CaS is the method where one device displays the fingerprint and the other user is provided with a number of options, the user then has to choose the correct value from the list of candidates.
+If there is no match the user must deny the connection attempt.
+This was due to concerns that CaC would be ``too easy'' for users leading to complacency and errors\cite{uzun2007usability}.
+CaE is designed for scenarios where both devices might not have a display, i.e.
+pairing between a phone and a keyboard.
+One device displays the checksum and the other device enters the string.
+The second device then compares the entered string and checks for a match.
+
+Research has been performed assessing the performance of these schemes and how they affect the ultimate security of the authentication ceremony.
+The literature agrees on CaC being the best overall scheme to compare fingerprints \cite{tan2017can}\cite{uzun2007usability} with CaS being highlighted for its poor security and usability.
+CaE has  had contrasting results.
+\cite{uzun2007usability} discarded it after one round due to ``poor usability'', however, \cite{tan2017can} considered it the as the best method overall if usability and security is considered.
+This, therefore, shows how polarised the results are regarding CaE.
+This, however, could be due to the different overall use-cases of the studies.
+Validation of results from either study would, therefore, be an area of extra study.
+
+One aspect of note from the work by \textbf{Ersin Uzun \textit{et al.}}\cite{uzun2007usability} is their studies context  of  “Secure  device  pairing”  and  thus  some comparison schemes are tested that are not relevant in a fingerprint comparison context, for example “Choose-and-Enter” (A participant chooses a passphrase from an available list and enters it into the other device).
+Thus, only relevant comparison schemes and their results have been extracted and compared.
+\\
+
+\subsection*{Experimentation methodology comparison}
+To further look into the validity of previously discussed results it is necessary to asses how the respective studies reached these conclusions.
+Areas for consideration are scheme entropy, attacker strength and participant factors among others.\\
+The starkest limitations of the literature are the range of participant and encoding entropy, where at its worst only 22-bits of entropy were tested.
+This makes it difficult to directly compare results and needs to be taken into consideration when comparing.
+One of the papers this most affects is the early work by \textbf{Hsu-Chun Hsiao, \textit{et al.}} where their highest entropy is 28-bits.
+This was small even at the time of publication.
+There is an attempt by the authors' to address this issue in the later stages of the paper where they write \textit{``[...] increasing entropy is not a solution because it sacrifices usability and accuracy.
+With more entropy, representations will contain longer sequences of characters or more minute details which will lead to increased time and errors during comparisons.''}.
+Although the assumptions in this statement could be seen as following common sense they fail to consider the implications of of a small entropy on the security of the system.
+\\
+This leads into the assessment of attacker strength considerations made by each paper.
+Some papers failed to directly address their attacker strength consideration, but the overall strength has been infered from the changes made to their schemes.
+For example, if they decided to change a single character in a 40-digit (160-bit) SHA-1 hex digest they are indirectly stating that the attacker can control 39-digits (156-bit).
+To achieve this the attacker would have to compute $2^{156}$ SHA-1 compressions to find a key match.
+In the literature this element ranged from $2^{28}$ to around $2^{242}$, however, this has some relation to the size of the encoding schemes used.
+\\
+In terms of the studies performed they all considered demographical data when presenting their results.
+Their average ages were all around $\sim35$ years old with the majority of participants being educated with at least a bachelor degree.
+This was alongside the equal split between male and female.
+
+One consideration of note is that made by Dechand \textit{et al.} \cite{dechand2016empirical} where they briefly consider medical conditions such as ADHD and reading or visual disorders and they way they affect the comparison's effectiveness.
+They highlight on a slight reduction in accuracy but due to their small sample size they cannot conclusively validate these results.
+This is an aspect unique to all other literature, further work would be required to produce conclusive results, thus showing a gap in the literature.
+
+One glaring issue with the demographical health of \textbf{Ersin Uzun \textit{et al.}}\cite{uzun2007usability} study is the use of two entirely different groups of participants.
+Not only were their demographics different but they were from different countries (America and Finland).
+This issue is of a concern due to the dual study design of this paper.
+Changes were made pragmatically regarding the results from the first round of 40 participants.
+These were then re-assessed and the results were directly compared.
+This puts huge doubts on the validity of the results with no consideration made by the authors to control external factors that may effect the methods performance.
+
+\textbf{TODO: } Do an overall comparison of the sizes of the studies and link to the table produced
+
+\begin{table}[h!]
+    \makebox[\textwidth][c]{
+        \input{tables/fingerprint_attacker_stren.tex}
+    }%
+    \caption{Paper attribute comparison}
+    \label{tab:attacker}
+\end{table}
 

### 2019-06-04 Documents/literature_review/pages/review_content.tex
Changes; - Added more content and worked on the wording of the paper

@@
 Examples of schemes assessed were: Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Vash\footnote{https://github.com/thevash/vash}, OpenSSH visual host key and Unicorns\footnote{https://unicornify.pictures/} to name a few.
-Accuracy from these schemes were mixed with positive results obtained by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} where their best accuracy was achived by Random Art (94.00\%) and Flag Ext.\footnote{The authors' own improvement on Flag}(88.00\%).
-On the other hand, the worst accuracy was obtained by Flag(50\%).
+Accuracy from these schemes were mixed with ranges as large as 50\% - 94\% in the work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study}.
 The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can} where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
+With both papers assessing unique schemes, further work is required to validate results.
 \\
-In terms of usability of graphical schemes the literature concurred on their ease-of-use.
-In terms of speed of comparison all schemes consistently obtained some of the quickest comparisons times.
-This is also supported indirectly from the the comparison results of alternative literature \cite{kainda2009usability}\cite{dechand2016empirical} where with these in consideration graphical schemes still remain the quickest overall.
+In terms of usability of graphical schemes, the literature concurred on their high usability.
+The comparison speed of these schemes were all among the quickest.
+This is also supported indirectly when comparing to alternative literature that did not consider graphical schemes.\cite{dechand2016empirical}\cite{kainda2009usability}
 In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with only two papers including graphical schemes in their comparison.
-This is, therefore, a candidate for further research.
+There is also no overlap in the schemes assessed with each paper reviewing a unique set.
+This is, therefore, a promising candidate for further research.
 
@@
 First was to consideration for ``remote-vs-proximity'' pairing where, this is the first consideration of this aspect found in the literature.
-Second, was their studies aim into investigating fingerprint security and usability in a end-to-end encryption context.
-The study compared Numerical, Visual and Auditory representations.
-This is a standard setup for similar studies in the literature.
-QR code verification was also added to the proximity tests.
+There is room for further research with the aim to compare encoding schemes in the context of ``remote-vs-proximity''.
+Another unique aspect was the end-to-end encryption context the study was performed under.
 
@@
 Without further work in this area it is difficult to conclusively validate these results.
+
+Alongside this, it was shown in work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} that age and gender do not affect the accuracy of the scheme.
+However, younger participants were considerably faster.
+Further more, findings also showed that language comprehension helped in discerning small differences between schemes encoded in Chinese, Japanese, Korean or English.
+Subsequently, knowledge of the language did not assist in differentiating larger changes in the schemes as these had high accuracy regardless.
+These were interesting and unique considerations.
+Further work with these considerations in mind could be tasked with corroborating these findings.
 
@@
 If there is no match the user must deny the connection attempt.
-This was due to concerns that CaC would be ``too easy'' for users leading to complacency and errors\cite{uzun2007usability}.
+CaS was devised due to concerns that CaC would be ``too easy'' for users leading to complacency and errors\cite{uzun2007usability}.
 CaE is designed for scenarios where both devices might not have a display, i.e.
@@
 One aspect of note from the work by \textbf{Ersin Uzun \textit{et al.}}\cite{uzun2007usability} is their studies context  of  “Secure  device  pairing”  and  thus  some comparison schemes are tested that are not relevant in a fingerprint comparison context, for example “Choose-and-Enter” (A participant chooses a passphrase from an available list and enters it into the other device).
-Thus, only relevant comparison schemes and their results have been extracted and compared.
+Thus, only relevant comparison schemes and their results were extracted and compared.
 \\
@@
 To further look into the validity of previously discussed results it is necessary to asses how the respective studies reached these conclusions.
-Areas for consideration are scheme entropy, attacker strength and participant factors among others.\\
+Areas for consideration are scheme entropy, attacker strength and participant attributes.
+
 The starkest limitations of the literature are the range of participant and encoding entropy, where at its worst only 22-bits of entropy were tested.
 This makes it difficult to directly compare results and needs to be taken into consideration when comparing.
-One of the papers this most affects is the early work by \textbf{Hsu-Chun Hsiao, \textit{et al.}} where their highest entropy is 28-bits.
+One of the papers this most affects is the early work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study}  where their highest entropy is 28-bits.
 This was small even at the time of publication.
@@
 With more entropy, representations will contain longer sequences of characters or more minute details which will lead to increased time and errors during comparisons.''}.
-Although the assumptions in this statement could be seen as following common sense they fail to consider the implications of of a small entropy on the security of the system.
-\\
+This statement is backed up with no empirical evidence and the authors' fail to consider how the small entropy would affect the overall security of the schemes.
+
 This leads into the assessment of attacker strength considerations made by each paper.
@@
 In the literature this element ranged from $2^{28}$ to around $2^{242}$, however, this has some relation to the size of the encoding schemes used.
-\\
-In terms of the studies performed they all considered demographical data when presenting their results.
+This is a substantial range that makes it ultimately difficult to confidently compare and confer results.
+Further work could exclusively look into the affect attacker strength has on the success of attacks.
+
+All of the studies considered demographical data when presenting their results.
 Their average ages were all around $\sim35$ years old with the majority of participants being educated with at least a bachelor degree.
@@
 They highlight on a slight reduction in accuracy but due to their small sample size they cannot conclusively validate these results.
-This is an aspect unique to all other literature, further work would be required to produce conclusive results, thus showing a gap in the literature.
+This is an aspect unique to all literature.
+Further work would be required to produce conclusive results.
+Therfore, highlighting on a gap in the literature.
 
@@
 
-\textbf{TODO: } Do an overall comparison of the sizes of the studies and link to the table produced
+Hexadecimal and numerical schemes were not included as encoding schemes in the work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} (some of the most widespread encoding schemes).
+This was based on their own claims on similarities to Base32 and ``well-known deficiencies" in the excluded schemes.
+This point was provided with no further justification or quantified in any way.
+It is also not consistent with available research, for example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}\cite{dechand2016empirical} it was shown numerical representations performed significantly better than that of Base32.
 
@@
 \end{table}
+
+Table \ref{tab:attacker} has been provided to visually compare the differing aspects of the papers' parameters.
+Clearly it can be seen from the table the large ranges in participant size, entropy and attacker strength.
 

### 2019-06-04 Documents/literature_review/pages/review_content.tex
Changes; - Final draft has been made for the re-write of the first lit review section

--- 2019-06-03 Documents/literature_review/pages/review_content.tex
@@
-\section{Introduction}
-The increasing use of public key cryptography by instant messaging and secure email means key fingerprint 
-verification is an ever more important task.
-One of the biggest risks to the security of the communication channel is a Man-in-the-middle (MiTM) attack .
-A successful MiTH attack can circumvent the encryption as it allows an attacker to read all the encrypted data.
+% \section{Introduction}
+% The increasing use of public key cryptography by instant messaging and secure email means key fingerprint 
+% verification is an ever more important task.
+One of the most significant risks to the security of the communication channel is a Man-in-the-middle (MiTM) attack.
+A successful MiTM attack can circumvent the encryption as it allows an attacker to read all the encrypted data.
 A countermeasure for this is the verification of each parties' fingerprint.
@@
 
-% \textbf{TODO: } - Improve the flow of the first section, need to phrase it like I'm telling a story
-% \textbf{TODO: } - Create written introduction setting the scene. \\
-% \textbf{TODO: } - Add participant size to M. Shirvanian (25) \\
-% \textbf{TODO: } - Create a background section for Compare-and-X
-% \\
-% \textbf{TODO: } - Create comparison area where inconsistencies are compared
+\section{Literature Review}
 
-\section{Literature Review}
-\subsection{Fingerprint representation comparison}
-
-Fingerprints are used to quickly compare the similarity of two keys.
-The comparison occurs between the digest of a strong one-way hash function.
-Historically these have been represented as a hexadecimal string and users were tasked with manually comparing fingerprints between two substrates, for example, a monitor screen and a business card.
-We will refer to this process throughout the paper as the \textit{``authentication ceremony''}.
-\\
-It has been shown that the average human can only hold 7-digits worth of data in our working memory\cite{miller1956magical}.
-This rules out the possibility of comparing full digests.
-For examples SHA-1 is 40 hex digits (160-bit) and, therefore, will make it difficult for effective comparison.
-Therefore , if the  process is to involve humans interaction, there is a need for schemes that work effectively with our abilities and senses.
+Fingerprints are used to compare the similarity of two keys quickly.
+The comparison occurs between two digests of a secure one-way hash function.
+Historically these have been represented as a hexadecimal string whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card.
+This process is known as the \textit{``authentication ceremony.''} \\
+Prior research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}.
+This rules out the possibility of comparing complete digests.
+For example, SHA-1 is 40 hex digits (160-bit) and, therefore, difficult to effectively compare.
+Therefore, if human interaction is required; there is a need for schemes that work effectively with consideration to individual limitations.
 
 Research in this area has taken various encoding schemes and compared their fallibility to impersonated attacks.
-Impersonation of a key would involve brute force of the encoding schemes through the mass creation of keys.
-The main elements of comparison have been accuracy of attack detection and time to complete the comparison.
-In this context we will consider the metrics a measure of security and usability respectively.
+The main elements of comparison have been the ``accuracy of attack detection" and ``time to compare".
+In this paper, these are considered the metrics of ``security'' and ``usability'', respectively.
 
-\subsection*{Effective schemes}
+\subsection*{Definition of terms}
+Throughout the paper, various terms are used to define elements of the authentication ceremony relevant to fingerprints verification.
+Explicit descriptions are, therefore, stated in this section.
+These are used to remove ambiguity and underlying associations readers may have for the words chosen.
+
+\textbf{\textit{Encoding schemes}} - This is the physical method of encoding used to represent the fingerprint.
+For example, ``Hexadecimal'' or ``Words'' are a unique way to represent a fingerprint and thus, are encoding schemes.
+
+\textbf{\textit{Method of comparison}} - This is how the user assesses the encoding scheme.
+The most common example and the one used as default is ``Compare-and-Confirm'' (CaC).
+CaC, as the name suggests, is the \textit{comparison} of two fingerprints on different devices or mediums that are then \textit{confirmed}.
+The following sections explain alternative methods of comparisons.
+
+\subsection{Authentication ceremony performance}
+
+\subsection*{Encoding scheme performance}
 Results 
-from the literature consistently show the effectiveness of language based encodings (Words or Sentences).
-This was shown in \cite{dechand2016empirical}, \cite{tan2017can} and \cite{kainda2009usability} with the accuracy of these schemes all being above 94.00\%.
-In all cases these were the best scemes in terms of accuracy.
-The exception to this is the work performed by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63.00\% (Comparisons of methodology will be discussed in later sections).
+from the literature consistently show the effectiveness of language-based encodings such as Words or Sentences with accuracies ranging from 94\% \cite{dechand2016empirical}\cite{tan2017can}\cite{kainda2009usability}.
+In all cases, these were the best schemes from the sets assessed.
+The exception to this is the work performed by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63.00\%.
 \\\\
 Aside from textual representations were graphical schemes.
-Examples of schemes assessed were: Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Vash\footnote{https://github.com/thevash/vash}, OpenSSH visual host key and Unicorns\footnote{https://unicornify.pictures/} to name a few.
-Accuracy from these schemes were mixed with positive results obtained by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} where their best accuracy was achived by Random Art (94.00\%) and Flag Ext.\footnote{The authors' own improvement on Flag}(88.00\%).
-On the other hand, the worst accuracy was obtained by Flag(50\%).
+Examples of schemes assessed were: Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Vash\footnote{https://github.com/thevash/vash}, OpenSSH visual host key and Unicorns\footnote{https://unicornify.pictures/}, among others.
+These schemes had mixed accuracy with ranges as large as 50\% - 94\% in work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study}.
 The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can} where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
 \\
-In terms of usability of graphical schemes the literature concurred on their ease-of-use.
-In terms of speed of comparison all schemes consistently obtained some of the quickest comparisons times.
-This is also supported indirectly from the the comparison results of alternative literature \cite{kainda2009usability}\cite{dechand2016empirical} where with these in consideration graphical schemes still remain the quickest overall.
-In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with only two papers including graphical schemes in their comparison.
-This is, therefore, a candidate for further research.
+In terms of usability of graphical schemes, the literature concurred on their high usability.
+The comparison speed of these schemes were all among the quickest (See Table \ref{tab:times} for an overview of timings).
+Other work also indirectly concurred with graphical encodings having significantly quicker comparison times compared to non-graphical schemes \cite{dechand2016empirical}\cite{kainda2009usability}.
+In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with literature only containing two papers.
+There is also no overlap in the schemes assessed with each paper reviewing a unique set.
+This is, therefore, a promising candidate for further research.
 
-\subsection*{Experimentation comparison}
+One unique paper in this research area was the work by \textbf{M.
+Shirvanian \textit{et al.}}\cite{shirvanian2017pitfalls} produced in the context of secure messaging pairing.
+This paper was unique for several reasons.
+First was to consideration for ``remote-vs-proximity'' pairing where this is the first consideration of this aspect found in the literature.
+There is room for further research to compare encoding schemes in the context of ``remote-vs-proximity.'' Another unique aspect was the end-to-end encryption context of the study.
 
-\subsection{Fingerprint representation schemes}
+The findings from the paper showed a high false negative rate for all the schemes; this is a consideration also missing from the literature.
+Alongside this, results for usability were lower in a remote setting for all the schemes.
+The author, however, comments on the expected nature of this result.\\
+Images were assessed as being the most secure method of authentication in the remote setting but voted as the method with the worst usability.
+This conclusion is highly inconsistent with all other work in this area.
+However, this could be due to the unique setting of remote verification, resulting in distinct results from user studies.
+Without further work in this area, it is difficult to validate these results conclusively.
+
+Alongside this, it was shown in work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} that age and gender do not affect the accuracy of the scheme.
+However, younger participants were considerably faster.
+Furthermore, findings also showed that language comprehension helped in discerning small differences between schemes encoded in Chinese, Japanese, Korean or English.
+Subsequently, knowledge of the language did not assist in differentiating more significant changes in the schemes as these had high accuracy regardless.
+These were interesting and unique considerations.
+Further work could aim to corroborate these conclusions.
+
+Tables~\ref{tab:results} \& \ref{tab:times} contain the accuracy results of all papers assessed; this is to aid in visual comparison.
+Each paper used a different metric for measuring accuracy.
+Therefore, all results have been translated into ``overall accuracy.''
+
+\subsection*{Methods of comparison performance}
+Aside 
+from ``Compare-and-Confirm'' (CaC), there is ``Compare-and-Select'' (CaS) and ``Compare-and-Enter'' (CaE).
+CaS is the method where one device displays the fingerprint, and the other user is provided with several options.
+The user then has to choose the correct value from the list of candidates.
+If there is no match, the user must deny the connection attempt.
+The creation of CaS was due to concerns that CaC would be ``too easy'' for users leading to complacency and errors\cite{uzun2007usability}.
+CaE is designed for scenarios where both devices might not have a display, i.e.
+pairing between a phone and a keyboard.
+One device displays the checksum.
+This checksum is entered into the other device.
+The first device then compares the entered string and checks for a match.
+
+Research has been performed assessing the performance of these schemes and how they affect the ultimate security of the authentication ceremony.
+The literature agrees on CaC being the best overall scheme to compare fingerprints \cite{tan2017can}\cite{uzun2007usability} with CaS being highlighted for its poor security and usability.
+CaE has  had contrasting results.
+\cite{uzun2007usability} discarded it after one round due to ``poor usability.'' However, \cite{tan2017can} considered it the best method overall for usability and security.
+These conflicting results, therefore, show polarisation in the results of CaE.
+However, this could be due to the different overall use-cases of the studies.
+Validation of results from either study would, therefore, be an area of additional study.
+
+% One aspect of note from the work by \textbf{Ersin Uzun \textit{et al.}}\cite{uzun2007usability} is their studies context  of  “Secure  device  pairing”  and  thus  some comparison schemes are tested that are not relevant in a fingerprint comparison context, for example “Choose-and-Enter” (A participant chooses a passphrase from an available list and enters it into the other device).
+Thus, only relevant comparison schemes and their results were extracted and compared.
+\\
+
+\subsection*{Experimentation methodology comparison}
+To further look into the validity of previously discussed results, it is necessary to asses how the respective studies reached these conclusions.
+Areas for consideration are scheme entropy, attacker strength and participant attributes.
+
+The starkest limitations of the literature are the range of participants and encoding entropy.
+The worst studies tested only 22-bits of entropy.
+This makes it difficult to compare results directly.
+One of the papers this most effects is the early work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study}  where their highest entropy is 28-bits.
+This level of entropy was inadequate even at the time of publication.
+There is an attempt by the authors' to address this issue in the later stages of the paper where they write \textit{``[...] increasing entropy is not a solution because it sacrifices usability and accuracy.
+With more entropy, representations will contain longer sequences of characters or more minute details which will lead to increased time and errors during comparisons.''}.
+This statement is backed up with no empirical evidence, and the authors' fail to consider how the low entropy would affect the overall security of the schemes.
+
+Attacker strength is also another metric used to compare results concluded by each paper.
+Some papers failed to address their attacker strength consideration directly, but the overall strength has been inferred from the changes made to their schemes.
+For example, if they decided to change a single character in a 40-digit (160-bit) SHA-1 hex digest, they are indirectly stating that the attacker can control 39-digits (156-bit).
+To achieve this, the attacker would have to compute $2^{156}$ SHA-1 compressions to find a key match.
+In the literature, this element ranged from $2^{28}$ to around $2^{242}$; however, this has some relation to the size of the encoding schemes used.
+This is a substantial range that makes it ultimately challenging to compare and confer results confidently.
+Further work could exclusively look into the affects attacker strength has on the success of attacks.
+Moreover, all the papers assessed failed to fully consider the feasibility of attacks in terms of computer and storage requirements.
+This again, shows gaps in the literature.
+
+All of the studies considered demographical data when presenting their results.
+Their average ages were all around $\sim35$ years old with the majority of participants educated with at least a bachelor degree.
+This was alongside the equal split between male and female participants.
+
+One consideration of note is that made by Dechand \textit{et al.} \cite{dechand2016empirical} where they briefly consider medical conditions such as ADHD and reading or visual disorders and the way they affect the comparison's effectiveness.
+They highlight a slight reduction in overall accuracy, although due to their small sample size, they cannot conclusively validate these results.
+This is an aspect unique to all literature.
+Further work would be required to produce conclusive results.
+Therefore, highlighting a gap in the literature.
+
+One glaring issue with the demographical health of \textbf{Ersin Uzun \textit{et al.}}\cite{uzun2007usability} study is the use of two entirely different groups of participants.
+Not only were their demographics different, but they were from different countries (America and Finland).
+Different cultures contain inherent biases and assumptions.
+Moreover, more concerns are raised around the dual study design of this paper with two completely different set of participants.
+Changes were made pragmatically regarding the results from the first round of 40 participants.
+These were then re-assessed and the results were directly compared.
+This puts huge doubts on the validity of the results with no consideration made by the authors to control external factors that may affect the performance of the method of comparison.
+
+Hexadecimal and numerical schemes were not included as encoding schemes in work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} (some of the most widespread encoding schemes).
+This decision was based on their claims on similarities to Base32 and ``well-known deficiencies" in the excluded schemes.
+This point was provided with no further justification or quantified in any way.
+It is also not consistent with available research, for example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}\cite{dechand2016empirical} it was shown numerical representations performed significantly better than that of Base32.
+
+\begin{table}[h!]
+    \makebox[\textwidth][c]{
+        \input{tables/fingerprint_attacker_stren.tex}
+    }%
+    \caption{Paper attribute comparison}
+    \label{tab:attacker}
+\end{table}
+
+Table \ref{tab:attacker} has been provided to visually compare the differing aspects of the papers' parameters.
+Clearly it can be seen from the table the large ranges in participant size, entropy and attacker strength.
+
+%TODO: Maybe talk about the effect of visual or mental impairments 
+\subsubsection{Topic conclusion}
+Overall, this review has identified several key areas suitable for further work.
+The first is the performance assessment of graphical encoding schemes.
+Recreation of pre-existing results from \cite{hsiao2009study}\cite{tan2017can} is required to corroborate current conclusions and validate results.
+Another gap in the research is the consideration into the utilization of encoding schemes in realistic conditions, i.e.
+``remove vs.
+proximity." This topic was initially covered by \cite{shirvanian2017pitfalls} but their scope was limited.
+Further work, therefore, could increased the scope and touch upon a large number of schemes in these settings.
+The final aspect for further work is the limited consideration into the feasibility of attacks on encoding schemes.
+All of the papers assessed simulated attacks and had minimal consideration for the execution of these attacks.
+Therefore, further work could delve into the implementation of such attacks and their feasibility in terms of compute and storage complexity.
+
+\subsection{Encoding schemes}
 Another area of research is investigations into the actual physical encodings of the hash digest.
@@
 
-\subsection{Fingerprint representation attacks}
+\subsection{Attacks on encoding schemes}
 This area of research studies ways to physically execute attacks on fingerprint encoding schemes.

### 2019-06-14 Documents/project_plan/pages/work_plan.tex
Changes; - Updated the plan for the project - Started thinking about an inital pre-pilot question. Added a script to obtain random matches for question material

@@
 
-\subsection*{\hyperref[ref:wordlist]{Wordlist characteristic analysis}}
-This area will look into characteristics that are attractive when designing a wordlist.
-These will be used later to possibility improve the trustword implementation.
-Past research could provide guidance on this aspect.
+\subsection{Trustword attacks}
 
-\subsection*{Analysis into effective ``similarity'' metrics}
-This section will involve research into how similarities in words can be quantified. Which options provide us the best balance of number of matches and accuracy of matches?
+\subsubsection{Similarity metrics}
+This section will discuss the feasibility of attacking 4 Trustwords. This will require "similar" words to be detected in the dictionary. Therefore, "similarity metrics" will be required.
 
-\subsection*{Development of a tool used to find partial collisions for wordlist mappings}
-This tool would be fed two keys, one ``static'' and one the ``target''.
-The tool would then generate keys for the ``target'' that create a similar overall wordlist mapping.
-Here metrics for linguistic distance will be used to define ``similarity''.
-The similarity metric will generate a list of keys that provide similar matches, the tool will then hash large number of PGP keys to generate partial matches.
-This is useful to define an actual measure of the real-world feasibility.
-This is one aspect missing from the literature as other papers have simulated attacks on encoding schemes.
+Due to the defined use-case of Trustwords to be authenticated over a audio based channel, metrics that measure the pronoucability of a word will be used.
 
-\subsection*{\hyperref[ref:trustwords]{Security of Trustwords}}
-This section will evaluate Trustwords using the previously defined metrics.
-Alongside this, the feasibility of generating partial collisions will be assessed.
-The security could be quantified by testing the current implementation out on real users and determining the False Acceptance Rate of near attacks.
-This could be used as a baseline for improvements to be compared later.
+\textbf{[FURTHER WORK: Using metrics that consider the visual aspect of a word - this could be useful due to in-person authentication]}
 
-\subsection*{\hyperref[ref:alternatives]{Security of alternative wordlists:}}
-In the same way as Trustwords were assessed, the same will be performed on already available wordlists. Such as the PGP wordlist and the wordlist generated by SafeSlinger.
+\begin{itemize}
+    \item Soundex
+    \item NYSIIS
+    \item Match Rating Approach
+    \item Word Vectors
+    \item Combined (With Levenshtein distance)
+\end{itemize}
 
-\subsection*{\hyperref[ref:rec]{Security of implemented recommendations}}
-This section will then amalgamate all the research performed prior and use it to improve and update the implementation of Trustwords.
-This would then be assessed by experimentation and the improvements could be quantified with the same experimentation.
+\textbf{[TODO] Experimentation: } Trimming down these metrics might be required with a quick pilot where I attempt to measure the user-perceived similarity accuracy of the schemes.
+What could be considered is the number of permutations and the "perceived" similarity.
 
-% \section{In-depth breakdown}
+\subsubsection{Similar list creation}
+These metrics then can be used to substitute in place of other words to create a list of near-collision matches/permutations. These will help well generating near-collision keys.
 
-% \subsection{Wordlist characteristic analysis}
-% \label{ref:wordlist}
-% \begin{itemize}
-%     \item Investigation into characteristics of a strong wordlist
-%     \begin{itemize}
-%         \item Distinctiveness
-%         \item Homonyms (Visual)
-%         \item Homophones (Pronunciation)
-%         \item Length
-%         \item Current ways to define linguistic distance:
-%         \begin{itemize}
-%             \item \textbf{Visual:}
-%             \begin{itemize}
-%                 \item Levenshtein (Edit distance)
-%             \end{itemize}
+\textbf{CONSIDERATION: } The method works by incrementing the exponent? How does this affect the structure of the key
 
-%             \item \textbf{Auditory}:
-%             \begin{itemize}
-%                 \item Soundex
-%                 \item Metaphone
-%                 \item NYSIIS
-%                 \item Match Rating
-%             \end{itemize}
-%         \end{itemize}
+\subsubsection{Tool design and creation}
+Discussion will occur here around the creation of the tool. Will need to talk about the inspiration of the tool (Scallion) and the improvements made over it:
+\begin{itemize}
+    \item Benchmark of comparison of large number of keys.
+    \item Why C++ was used?
+\end{itemize}
 
-%     \end{itemize}
+\subsubsection{Study into the effectiveness of the matches}
+The could be with the pilot where the results are extrapolated. There are two ways to run this study:
 
-%     \item Analysis into the strength of the TrustWords using previously obtained metrics.
+\begin{itemize}
+    \item[1] Actual matches are computed and compared
+    \item[2] Evaluation of complexity is computed prior, and for the experiment is simulated.
+\end{itemize}
 
-%     \item Investigation into the strength of other wordlists using defined metrics.
-%     \begin{itemize}
-%         \item PGP word list
-%         \item SafeSlinger
-%     \end{itemize}
+I think actually showing the matches can be actually computed and simulating them in the study gives the best balance. [Option 2]
 
-% \end{itemize}
+Would I also want to do this with a random single target key?
+Or the worst case scenario.
+There are keys that have a higher number of potential matches, this is due to the words the key's fingerprint is mapped to.
 
-% \subsection{Security of Trustwords}
-% \label{ref:trustwords}
-% Here we'd look at the words used in the dictionary and attempt to generate lists of keys that would generate partial collisions these would then be fed into the created tool
+\subsubsection{Conclusion of Trustword security}
+This will have a conclusion stating the security of the minimum recommendation of 4 Trustwords.
 
-% \subsection{Security of alternative wordlists}
-% \label{ref:alternatives}
+\textbf{[FURTHER WORK: Evaluation with a higher number of words]}
 
-% \subsection{Security of implemented recommendations}
-% \label{ref:rec}
+\subsection{Improvement study}
+
+This 
+is recommendations into improvements with Trustwords. This will pretty much revolve around the word vectors and their ability to allow wordlist "strength" to be quantified.
+
+\subsection*{Word vectors}
+The strength of the metric was shown in it's own paper with comparison with another famous study into an empirical way to vectorize words. This could even be linked back to the initial pilot study.
+
+\textbf{[FURTHER WORK: More evaluation into the effectiveness of the word vector method]}
+
+\subsection*{Choice of Trustwords}
+
+\begin{itemize}
+    \item Homographs (Spelt the same by pronounced differently)
+    \item Homonyms   (Different spelling same pronunciation)
+\end{itemize}
+
+% https://en.wikipedia.org/wiki/Homograph#/media/File:Homograph_homophone_venn_diagram.png
+
+Here I could make recommendations through improvements on the word lists:
+
+\begin{itemize}
+    \item Reduce the size of the wordlist (8bit (256 words)/10bits (1024 words))
+    \item Different choice of words
+    \item ?
+\end{itemize}
+
+These could then be evaluated in a similar way to show possible improvements over the base wordlist used by Trustwords
+
+\textbf{[FURTHER WORK: Other languages found within Trustwords require this evaluation]}

### 2019-06-14 Code/SimilarWords/modes/word_vectors.cpp

@@ -35,7 +35,7 @@ std::vector<std::string> split(std::string strToSplit, char delimeter)
 std::map<std::string, std::vector<float>> WordVectors::load_word_vectors()
 {
     //TODO: Sort out file path
-    auto path = "/home/main_user/GitHub/Cyber-Security-Individual-Project/Code/SimilarWords/data/word_vectors.dat";
+    auto path = "data/word_vectors.dat";
 
     std::string line;
     std::ifstream myfile(path);
@@ -59,6 +59,12 @@ std::map<std::string, std::vector<float>> WordVectors::load_word_vectors()
 
     }
     myfile.close();
+
+    if(wordVectors.size() == 0)
+    {
+        std::cout << "[!] No wordvectors loaded!" << std::endl;
+        exit(0);
+    }
 }
 
 /*

### 2019-06-14 Code/SimilarWords/similar_words.cpp

@@ -14,22 +14,25 @@
 std::string inputFileName = "";
 std::string outputFileName = "";
 
-static bool LEV_DISTANCE = false;
-static bool SOUNDEX = false;
-static bool METAPHONE = false;
-static bool NYSIIS = false;
-static bool WORD_VEC = false;
-static bool COMBINED_MODE = false;
-
+// Values for quantifying tolerance or the measurement of "difference"
 static float COMBINED_TOLERANCE = 1;
-static float WORDVEC_TOLERANCE = 3;
+static float WORDVEC_TOLERANCE = 3.0;
 
+// Command line tags
 std::string SOUNDEX_CLI_TAG     = "-s";
 std::string LEV_CLI_TAG         = "-l";
 std::string METAPHONE_CLI_TAG   = "-m";
 std::string NYSIIS_CLI_TAG      = "-n";
 std::string COMBINED_MODE_TAG   = "-c";
 std::string WORD_VEC_CLI_TAG    = "-v";
+
+// Mode booleans
+static bool LEV_DISTANCE    = false;
+static bool SOUNDEX         = false;
+static bool METAPHONE       = false;
+static bool NYSIIS          = false;
+static bool WORD_VEC        = false;
+static bool COMBINED_MODE   = false;
 
 /*
     Saves the similar words to a specified file
@@ -184,20 +187,20 @@ void parse_program_mode(std::string commandInput)
 
 int main(int argc, char *argv[])
 {
-    // if ( argc != 4)
-    // {
-    //     usage();
-    // }
+    if ( argc != 4)
+    {
+        usage();
+    }
 
-    // // Sets the args
-    // inputFileName = argv[1];
-    // outputFileName = argv[2];
-    // std::string mode = argv[3];
+    // Sets the args
+    inputFileName = argv[1];
+    outputFileName = argv[2];
+    std::string mode = argv[3];
 
-    //##### DEBUG #####
-    inputFileName = "/home/main_user/GitHub/Cyber-Security-Individual-Project/Wordlists/Dictionary/words_popular.txt";
-    outputFileName = "./test.txt";
-    std::string mode = "-v";
+    // //##### DEBUG #####
+    // inputFileName = "/home/main_user/GitHub/Cyber-Security-Individual-Project/Wordlists/Dictionary/words_popular.txt";
+    // outputFileName = "./test.txt";
+    // std::string mode = "-v";
 
     parse_program_mode(mode);
 

### 2019-06-14 Experiments/Pre-pilot/gen_questions.py

@@ -1,0 +1,60 @@
+import sys
+import random
+
+"""
+Script that is used to generate a number of random pairs from
+a "similar word" list
+"""
+
+
+def usage():
+    print(f"[!] Usage: ./{__file__} <SIMILAR_LIST> <NUM_OF_PAIRS>")
+    exit()
+
+def remove_matchless_words(similar_list):
+    """
+    Removes any words without any matches
+    """
+
+    new_list = []
+    for sword in similar_list:
+
+        parts = sword.split(",")
+
+        if len(parts) > 2:
+            new_list.append(sword)
+
+    return new_list
+
+def spread_out_matches(similar_list):
+
+    new_list = []
+    for sword in similar_list:
+
+        sword = sword.strip()
+        parts = sword[:-1].split(",")
+
+        for p in parts[1:]:
+            new_list.append(f"{parts[0]},{p}")
+
+    return new_list
+
+if __name__ == "__main__":
+    
+    if len(sys.argv) != 3:
+        usage()
+
+    similar_list_path = sys.argv[1]
+    num_of_pairs = int(sys.argv[2])
+
+    similar_list = []
+    with open(similar_list_path) as f:
+        similar_list = f.readlines()
+
+    similar_list = remove_matchless_words(similar_list)
+    similar_list = spread_out_matches(similar_list)
+
+    # Prints out the random pairs
+    for n in range(num_of_pairs):
+        index = random.randint(0, len(similar_list))
+        print(similar_list[index])

### 2019-07-22 Code/TrustwordUtil/calculate_perms.sh
Changes; - Computed values for different target times (2 days/3 days/7 days)

@@ -2,11 +2,13 @@
 
 set -e
 
-# declare -a metricArr=("soundex" "leven" "metaphone" "nysiis" "wordvec")
-# declare -a permsArr=("1000" "10000" "100000")
+declare -a metricArr=("soundex" "leven" "metaphone" "nysiis" "wordvec_4_5")
 
-declare -a metricArr=("wordvec_3" "wordvec_4" "wordvec_5")
-declare -a permsArr=("50000")
+# declare -a permsArr=("1000" "10000" "100000") # 1 day
+# declare -a permsArr=("500" "5000" "50000") # 2 days
+declare -a permsArr=("250" "2500" "25000") # 3 days
+# declare -a permsArr=("152" "1525" "15250") # 1 week
+
 declare -a staticArr=("0" "1" "2")
 
 for perm in "${permsArr[@]}"

### 2019-07-22 .archive/Documents/literature_review/backup/review_content.backup.tex
Changes; - Added inital files for Thesis write up - Ordered and restructured various documents - Moved old lit' review into the .archive

--- 2019-05-28 Literature_Review/pages/review_content.tex
@@
-% \section{Possible research questions}
+\section{Introduction}
+The increasing use of public key cryptography by instant messaging and secure email means key fingerprint 
+verification is an ever more important task.
+One of the biggest risks to the security of the communication channel is a Man-in-the-middle (MiTM) attack .
+A successful MiTH attack can circumvent the encryption as it allows an attacker to read all the encrypted data.
+A countermeasure for this is the verification of each parties' fingerprint.
+\textbf{[...]}
 
-% Overall the research will aim to investigate the strength of pEp's Trustword fingerprint mappings, and the ease in which partial collisions can be obtained for keys and how this will ultimately affect the end user(s).
+\textbf{TODO: } Finish introduction
 
-% Key areas that will be looked into:
-% \begin{itemize}
-%     \item Is the recommended minimum number of Trustwords enough to provide a basic level of security.
-%     \item What attributes make a strong general wordlist for fingerprint mapping and does the Trustword implementation exhibit these features.
-%     \item How easy is it to generate similar keys that attack a targeted key pair?
-%     \item How can similarity be quantified in terms of words? Does this include pronunciation or visual aspects?
-%     \item As usability is the main justification for the use of Trustwords are there alternatives that provide the same usability but with more security?
-% \end{itemize}
-
-\section{Review - Fingerprint representations}
+\section{Literature Review}
 
@@
 
-Current research in ways to represent and validate fingerprints has almost exclusively focused on the usability of such schemes.
+\textbf{TODO: } - Improve the flow of the first section, need to phrase it like I'm telling a story
+\textbf{TODO: } - Create written introduction setting the scene. \\
+\textbf{TODO: } - Add participant size to M. Shirvanian (25) \\
+\textbf{TODO: } - Create a background section for Compare-and-X
+\\
+\textbf{TODO: } - Create comparison area where inconsistencies are compared
+
+% \textbf{TODO: } - Check evaluation with each paper in regards to:
+% \begin{itemize}
+%     \item Participant size [P]
+%     \item Social aspects, where have they come from? Age? Gender? Occupation?  [S]
+%     \item Target entropy [E]
+%     \item Attacker strength [A]
+% \end{itemize}
+% [P, S, E, A]
+
+Current research into human-based validation of fingerprints has almost exclusively focused on the usability of such schemes.
 The following section will individually discuss available research findings alongside an overall comparison of the research recommendations.
 
-\textbf{Hsu-Chun Hsiao, \textit{et.
-al.}} produced the first work in this area in their paper: \textit{A Study of User-Friendly Hash Comparison Schemes}\cite{hsiao2009study} in around 2009.
-The aim of the study was to provide the first insight into the best encoding scheme used to represent a hash fingerprint.
-The schemes used were Base32, English words, Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Flag Ext\footnote{The author's own improvement on Flag} and finally Chinese, Korean and Japanese symbol encoding.
+% [A]
+Some of the first work in this area was performed by \textbf{Hsu-Chun Hsiao, \textit{et al.}}\cite{hsiao2009study}.
+The main aim of the study was to provide the first insight into the best encoding schemes used to represent a hash fingerprint.
+The schemes used were Base32, English words, Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Flag Ext\footnote{The authors' own improvement on Flag} and finally Chinese, Korean and Japanese symbolic encodings.
 A total of 436 participants were assessed in the study.
 
-Alongside the main aim of the paper, the authors wanted to provide empirical links between participant attributes (such as age or gender) and performance with the encoding scheme.
+In addition to the central aims of the paper, the authors intended to provide empirical links between participant attributes (such as age or gender) and performance with the encoding scheme.
 This is something rarely seen in the related research.
 Hsu-Chun Hsiao \textit{et al.} also provided two categories of similarities; ``hard'' and ``easy''.
+``Hard'' pair only have a very small difference, therefore, difficult to distinguish.
 These were designed to be the worst and best case respectively.
-As a final aim and the reason for the inclusion of Chinese, Korean and Japanese characters was to research if being a native speaker assists the user in distinguishing subtle differences between encodings in the respective language.
+The reasoning behind inclusion of Chinese, Korean and Japanese characters was to investigate the links between language ability and distinguishing subtle differences between encodings in the respective language.
 The entropy of encodings ranged from 22-bits to 28-bits.
-This is extremely low in comparison to similar research.
-However, this can be attributed to the age of the paper.
-\\
-The authors' decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes) was due to their similarity to Base32 and their well-known deficiencies.
-This is not consistent with available research.
-For example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}\cite{dechand2016empirical} it was shown numerical representations performed significantly better than that of Base32.
+This is the lowest level of entropy used in the assessed literature.
+To quantify this a hash rate of 10 MH/s SHA-1 compressions would be able to find a match for 28-bits in 26.8 seconds.
+This is addressed by the author at a stage in the paper where they state \textit{``However, increasing entropy is not a solution because it sacrifices usability and accuracy.
+With more entropy, representations will contain longer sequences of characters or more minute details which will lead to increased time and errors during comparisons.''}.
+This claim is entirely unsubstantiated with any empirical evidence alongside no discussion into why the level of entropy was chosen.
+This, however, was followed by in interesting recommendation into the use of commitments\cite{blum1982coin}.
+This provides an attacker with a single chance to find a collision, thus, providing a valid use case for low levels of entropy.\\
+Another limitation is the authors' decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes).
+This was based on their own claims on similarities to Base32 and ``well-known deficiencies" in the excluded schemes.
+This point was provided with no further justification or quantified in any way.
+It is also not consistent with available research, for example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}\cite{dechand2016empirical} it was shown numerical representations performed significantly better than that of Base32.
 
@@
 In terms of encoding schemes, the paper ranked Numerical, Alphanumerical and Words as the top three encoding schemes (These were all with Compare-and-Confirm).
-This took into consideration the usability and security of the scheme.
-This is relatively consistent with other literature where numerical and written encoding schemes seem to be the most effective overall.
+This recommendation took into consideration the usability and security of the scheme and is relatively consistent with other research where numerical and English language based encoding schemes seem to be the most effective overall.
 
 In conclusion, this paper provided a highly comprehensive review of all the aspects of human fingerprint verification, where it reviewed all the elements involved in the process.
-The only limitation of the paper is the size of the participants enrolled for the study.
+Limitations of the paper involved the inconsistent and low range of entropy (20-bits to 40-bits)alongside the size of the participants enrolled for the study.
 
+% TODO: Implement checks below:
 \textbf{Ersin Uzun \textit{et al.}}\cite{uzun2007usability} exclusively reviewed comparison methods.
@@
 
+To provide a visual comparison the accuracy results of the papers have been provided in Table~\ref{tab:results} \& \ref{tab:times}.
+Each paper used a unique accuracy representation, and, therefore, have been translated into overall accuracy.
+Due to some of the differing characteristics of the papers ultimately affecting results, Table \ref{tab:attacker} has also be provided.
+This table is useful to compare the health of the studies and chosen sizes that may affect the accuracy and reliability of the results.
+
+\begin{table}
+    \makebox[\textwidth][c]{
+        \input{tables/fingerprint_comparison.tex}
+    }%
+    \caption{Accuracy of correct comparison for the encoding schemes assessed}
+    \label{tab:results}
+\end{table}
+
+\begin{table}
+    \makebox[\textwidth][c]{
+        \input{tables/fingerprint_times.tex}
+    }%
+    \caption{Timing results in seconds for the related schemes}
+    \label{tab:times}
+\end{table}
+
+\begin{table}
+    \makebox[\textwidth][c]{
+        \input{tables/fingerprint_attacker_stren.tex}
+    }%
+    \caption{Paper attribute comparison}
+    \label{tab:attacker}
+\end{table}
+
 In conclusion for this section, there has been extensive work in the investigation of the usability of textual and visual encoding schemes alongside methods of comparison.
 There are mixed opinions about visual representations, however, the majority defines them as easy to use but severely lacking in security.
-Research on textual representations, however, is in agreement; natural language based encodings such as words or sentences provide some of the highest usability and security over the baseline performance of alphanumerical encodings.
+This can be seen in Table~\ref{tab:times} with graphical schemes having significantly lower comparison times in comparison to all alternatives.
+\\
+Research on textual representations, however, is in agreement; natural language based encodings such as Words or Sentences provide some of the highest usability and security over the baseline performance of alphanumerical encodings.
+This again, can be seen from Table~\ref{tab:results} \& \ref{tab:times}, where consistently Word and Sentences has some of the highest accuracy and lowest comparisons across the various studies.\\
 The literature also concurs on the use of Compare-and-Confirm as the best method of comparing fingerprints overall, with Compare-and-Select being highlighted for its poor security and usability.\\
-The starkest limitations of the literature are the range of participant and encoding entropy, where at its worst only 22-bits of entropy were tested.
-Another limitation is the scant amount of research solely investigating modes of comparison, where the literature only contains two papers with this aim.
-Even these limitations, as a whole the literature on this topic has provided a relatively comprehensive and coherent view on the usability of textual and visual hash encoding schemes.
+The starkest limitations of the literature are the range of participant and encoding entropy, where at its worst only 22-bits of entropy were tested (See Table \ref{tab:attacker}) Another limitation is the scant amount of research solely investigating modes of comparison, where the literature only contains two papers with this aim.
+This is, therefore, an area that requires further research.
+A potential research avenue could be the analysis of comparison methods in unique scenarios, one example of this could be the idea of ``remote-vs-proximity'' proposed by M.
+Shirvanian \textit{et al.}\cite{shirvanian2017pitfalls}.
+\\
+Even with these limitations, as a whole the literature on this topic has provided a relatively comprehensive and coherent view on the usability of textual and visual hash encoding schemes with relatively clear recommendations on methods of comparison and suitable encoding schemes.
 

### 2019-07-22 Thesis/pages/background.tex
Changes; - Added inital files for Thesis write up - Ordered and restructured various documents - Moved old lit' review into the .archive

\chapter{Background}
\label{cha:Background}

\section{PGP}

\section{OpenCL}

\section{Pretty Easy Privacy/Trustwords}

### 2019-07-22 Thesis/pages/experiments.tex
Changes; - Added inital files for Thesis write up - Ordered and restructured various documents - Moved old lit' review into the .archive

\chapter{Experiments}
\label{cha:Experiments}

\section{Scallion vs GreenOnion}
% Show that the bloom filter blows Scallion out of the water

\section{Experiment 1}
% Methodology
% Demographic
% Results

\section{Experiment 2}
% Methodology
% Demographic
% Results

### 2019-07-22 Thesis/pages/introduction.tex
Changes; - Added inital files for Thesis write up - Ordered and restructured various documents - Moved old lit' review into the .archive

\chapter{Introduction}
\label{cha:Introduction}

The increasing use of public key cryptography by instant messaging and secure email means key fingerprint 
verification is an ever more important task. One of the most significant risks to the security of the communication channel is a Man-in-the-middle (MiTM) attack. A successful MiTM attack can circumvent the encryption as it allows an attacker to read all the encrypted data. A countermeasure for this is the verification of each parties' fingerprint. \textbf{[...]}

### 2019-07-22 Thesis/pages/lit_review.tex
Changes; - Added inital files for Thesis write up - Ordered and restructured various documents - Moved old lit' review into the .archive

--- 2019-06-04 Documents/literature_review/pages/review_content.tex
@@
-% \section{Introduction}
-% The increasing use of public key cryptography by instant messaging and secure email means key fingerprint 
-% verification is an ever more important task.
-One of the most significant risks to the security of the communication channel is a Man-in-the-middle (MiTM) attack.
-A successful MiTM attack can circumvent the encryption as it allows an attacker to read all the encrypted data.
-A countermeasure for this is the verification of each parties' fingerprint.
-\textbf{[...]}
-
-% \textbf{TODO: } Finish introduction
-
-\section{Literature Review}
+\chapter{Literature Review}
+\label{cha:LiteratureReview}
 
@@
 Historically these have been represented as a hexadecimal string whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card.
-This process is known as the \textit{``authentication ceremony.''} \\
+This process is known as the \textit{``authentication ceremony.''}
+
 Prior research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}.
@@
 These are used to remove ambiguity and underlying associations readers may have for the words chosen.
-
+\\\\
 \textbf{\textit{Encoding schemes}} - This is the physical method of encoding used to represent the fingerprint.
 For example, ``Hexadecimal'' or ``Words'' are a unique way to represent a fingerprint and thus, are encoding schemes.
-
+\\\\
 \textbf{\textit{Method of comparison}} - This is how the user assesses the encoding scheme.
@@
 The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can} where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
+\\
+\begin{table}[h!]
+    \makebox[\textwidth][c]{
+        \input{tables/fingerprint_times.tex}
+    }%
+    \caption{Timing results in seconds for the related schemes}
+    \label{tab:times}
+\end{table}
 \\
@@
 
-Tables~\ref{tab:results} \& \ref{tab:times} contain the accuracy results of all papers assessed; this is to aid in visual comparison.
+\begin{table}[h!]
+    \makebox[\textwidth][c]{
+        \input{tables/fingerprint_comparison.tex}
+    }%
+    \caption{Accuracy of correct comparison for the encoding schemes assessed}
+    \label{tab:results}
+\end{table}
+
+Tables \ref{tab:times} \& \ref{tab:results} contain the accuracy results of all papers assessed; this is to aid in visual comparison.
 Each paper used a different metric for measuring accuracy.

### 2019-07-22 Thesis/tables/fingerprint_attacker_stren.tex
Changes; - Added inital files for Thesis write up - Ordered and restructured various documents - Moved old lit' review into the .archive

--- 2019-05-31 Documents/literature_review/tables/fingerprint_attacker_stren.tex
@@
     Entropy Range       & 22-28 bits    & 20-40 bits   & 122 bits & 128 bits & 160-256 bits  \\
-    No\degree  ~Participants     & 436           & 30           & 1047     & 661      & 25            \\
+    No\degree  ~Participants     & 436           & 30           & 1001     & 661      & 25            \\
     \bottomrule

### 2019-07-22 Thesis/pages/background.tex
Changes; - Added more content to Thesis background

@@
 
+\section{Problem Context}
+% Goal of the project? Why am I concentrating on PEP's Trustwords?
+The project aims to asses the security of \pep's fingerprint representation "Trustwords".
+Trustwords aim to sacrifice security for increased usability.
+The encoding scheme has been designed to assist this by having  the user compare a reduced set of words by about half in comparison to other schemes.
+To achieve this a larger number of bits are required per word.
+In this case Trustwords maps 16bits per word providing 65537 different combinations.
+This is, however, the largest number of bits per words (As show in the Literature Review in Chapter \ref{cha:LiteratureReview}) and pushes the boundaries of a language's usable vocabulary.
+
+This abnormal design choice has not received a security assessment alongside no research backing up claims. This paper, therefore, aims to rectify this research gap.
+
+However, in order to fully understand the project goal it is important to understand public-key cryptography, the role and functioning of \pep and the role fingerprint comparison has in preventing Man-in-the-middle attacks.
+
+\textbf{TODO:} Maybe research questions here instead of in the literature review
+
+\section{Public-key Cryptography Key Exchange}
+Asymmetric cryptography facilitates the secure encryption of messages in end-to-end encryption (E2EE), verification of digital signatures and sharing of pre-communication secrets, among others.
+The use-case of E2EE messages will be the primary focus of this paper.
+
+The asymmetry stems from the use of "Public" and "Private" keys.
+The Public key is used to encrypt data that only the respective Private key can decrypt.
+This means the keys required to communicate can be easily shared across insecure channels.
+
+To construct an E2EE connection the initial stage will be a key exchange using the key types discussed previously.
+This is the sharing of a pre-shared secret between two verified parties, this will then be used to encrypt subsequent messages with symmetric encryption\footnote{This is due to the speed increase of symmetrical over asymmetrical encryption}.
+This, however, hinges on the verification of the initial parties, if one party impersonates another and gets to view the pre-shared secret all communication becomes decryptable.
+Therefore, the correct identification of parties is crucial to maintaining secure communication channels.
+The exploitation of this is known as a Man-in-the-middle (MiTM) attack.
+This can be bidirectional where the attacker can sit in the middle of a communication channel and decrypt all correspondence.
+Figure \ref{fig:mitm} contains a visual representation of this attack.
+
+\begin{center}
+    \input{diagrams/MITM/basic}
+    \begin{figure}[h]
+        \caption{Photo depicting a MITM attack}
+        \label{fig:mitm}
+    \end{figure}
+\end{center}
+
+Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob) the fingerprint of the public key can be used for identification.
+There are, however, in linking of key fingerprint to real world entity.
+This paper will, however, assume that users know the respective parties' correct fingerprint, as the protocols behind this are outside the project's scope.
+
+The fingerprint of the key is generated by running important sections of the key through a secure one way hash function.
+This process produces a digest of fixed length that can be used to compare keys.
+Therefore, the comparison of expected and actual fingerprints is used to detect MiTM attacks and prevent impersonation.
+
 \section{PGP}
-
-\section{OpenCL}
+Pretty Good Privacy (PGP) is a specific implementation of public key cryptography discussed in the previous section.
+Its main use-case is for securing message based communications but can also be used for file or hard drive encryption.
+\textbf{[...]}
 
 \section{Pretty Easy Privacy/Trustwords}
+
+% Does this need explaining?
+\section{OpenCL}

### 2019-07-22 Thesis/pages/design.tex
Changes; - Added more content to Thesis background

\chapter{Design}
\label{cha:Design}

\section{Design of GreenOnion}
And the way it works. Need to explain it is based on Scallion but improved with the use of C++ alongside a bloom filter.

### 2019-07-23 Thesis/pages/background.tex
Changes; - Added more content to thesis write-up

@@
 
-This abnormal design choice has not received a security assessment alongside no research backing up claims. This paper, therefore, aims to rectify this research gap.
+This abnormal design choice has not received a security assessment to back up claims. This paper, therefore, aims to rectify this research gap.
 
@@
 Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob) the fingerprint of the public key can be used for identification.
-There are, however, in linking of key fingerprint to real world entity.
-This paper will, however, assume that users know the respective parties' correct fingerprint, as the protocols behind this are outside the project's scope.
+There are, however, issues in how a user should link a key's fingerprint to real world entity.
+This paper will, however, assume that users know the respective parties' correct fingerprint, as the protocols used to achieve this are outside the project's scope.
 
-The fingerprint of the key is generated by running important sections of the key through a secure one way hash function.
+The fingerprint of the key is generated by running the main components of the key through a secure one way hash function\footnote{Explain this?}.
 This process produces a digest of fixed length that can be used to compare keys.
@@
 Its main use-case is for securing message based communications but can also be used for file or hard drive encryption.
-\textbf{[...]}
 
-\section{Pretty Easy Privacy/Trustwords}
+Each element of a PGP key is split into what is know as a 'packet'.
+The 'fingerprint' packet v4 contains a version number, timestamp and the main elements of the keys algorithm (i.e.
+RSA exponent and modulus) formatted as MPIs\footnote{Multiprecision integers are unsigned integers used to hold large integers such as the ones used in cryptographic calculations.}.
+This data is then preceded with PGP packet header (used to specify length and version numbers).
+This is all then utilized as input into the one-way hash function SHA-1 to produce a 160-bit digest.
+
+\textbf{TODO: } Generate an image of PGP v4 fingerprint packet
+
+\section{Pretty Easy Privacy}
+Pretty Easy Privacy (\pep) is a data encryption system that utilises PGP encryption to provide E2EE on all common channels of communication such as email of SMS.
+\pep's design principles state that above all the systems should be easy to install, use and understand.
+
+\pep deals with the threat of MiTM attacks by having users compare the respective key fingerprints encoded as a set of words.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[scale=0.15]{trustwords/trustword_handshake.jpg}
+    \caption{Trustword fingerprint verification}
+\end{figure}
 
@@
 \section{OpenCL}
+
+\section{Similarity metrics (Soundex etc)}

### 2019-07-27 Thesis/pages/background.tex
Changes; - Add a small amount of content to the background

@@
 
+\newpage
+
 \section{Pretty Easy Privacy}
+\begin{wrapfigure}{r}{5cm}
+    \centering
+    \includegraphics[scale=0.15]{trustwords/trustword_handshake.jpg}
+    \caption{Trustword fingerprint verification}
+    \label{fig:trustwords}
+\end{wrapfigure}
+
 Pretty Easy Privacy (\pep) is a data encryption system that utilises PGP encryption to provide E2EE on all common channels of communication such as email of SMS.
@@
 \pep deals with the threat of MiTM attacks by having users compare the respective key fingerprints encoded as a set of words.
+Figure \ref{fig:trustwords} shows the \pep Android implementation of trustwords.
+The user pair of users then authenticate the words on an OOB (Out of Band) channel such as a phone call or in-person communication.
+If both users decide the words match they will accept or decline respectively.
+
+The trustwords are unique for each pair of keys, this is the alternative of having a static key for each user.
+The justification behind the unique set for each user pair is in an attempt to motivate users to perform the authentication ceremony.
+The unique combined fingerprint is believed to reduced complacency due to inherent change \textbf{[CITE ME]}.
+
+Each key pair is the exclusive-or of each key's fingerprint, this combined values is then broken down into 16-bit chunks and mapped to words via a pre-defined dictionary.
 
@@
     \centering
-    \includegraphics[scale=0.15]{trustwords/trustword_handshake.jpg}
-    \caption{Trustword fingerprint verification}
+    $KeyFingerprint_{1} \oplus KeyFingerprint_{2} = TrustwordsFingerprint$
+    \caption{Creation of the combined Trustword fingerprint}
 \end{figure}
+
+\begin{wrapfigure}{r}{5cm}
+    \centering
+    \begin{BVerbatim}
+    [...]
+52127 ZYGOTE
+52128 ZYGOTIC
+52129 ZYMURGY
+52130 AACHEN
+52131 AARDVARK
+52132 AAREN
+    [...]
+    \end{BVerbatim}
+    \caption{Re-mapping position in Trustword dictionary}
+    \label{fig:remap}
+\end{wrapfigure}
+
+Due to the number of words required ($2^{16}$) alongside the design choice to exclude slang and profanities the english Trustword dictionary requires dual-mapping of a section of words.
+Approximately 13633/65536 (20.8\%) of words are re-mapped in the dictionary leaving 51903 unique words.
+The re-mapping is also done on a loop with it remaining alphabetical.
+Figure \ref{fig:remap} shows the position in the dictionary where this occurs.
+This predictability within the dictionary will be explored later in the paper.
 

### 2019-07-29 Thesis/pages/background.tex
Changes; - Added more content to the background - Merged background and literature review

@@
 
-\section{Public-key Cryptography Key Exchange}
-Asymmetric cryptography facilitates the secure encryption of messages in end-to-end encryption (E2EE), verification of digital signatures and sharing of pre-communication secrets, among others.
-The use-case of E2EE messages will be the primary focus of this paper.
-
-The asymmetry stems from the use of "Public" and "Private" keys.
-The Public key is used to encrypt data that only the respective Private key can decrypt.
-This means the keys required to communicate can be easily shared across insecure channels.
-
-To construct an E2EE connection the initial stage will be a key exchange using the key types discussed previously.
-This is the sharing of a pre-shared secret between two verified parties, this will then be used to encrypt subsequent messages with symmetric encryption\footnote{This is due to the speed increase of symmetrical over asymmetrical encryption}.
-This, however, hinges on the verification of the initial parties, if one party impersonates another and gets to view the pre-shared secret all communication becomes decryptable.
-Therefore, the correct identification of parties is crucial to maintaining secure communication channels.
-The exploitation of this is known as a Man-in-the-middle (MiTM) attack.
-This can be bidirectional where the attacker can sit in the middle of a communication channel and decrypt all correspondence.
-Figure \ref{fig:mitm} contains a visual representation of this attack.
-
-\begin{center}
-    \input{diagrams/MITM/basic}
-    \begin{figure}[h]
-        \caption{Photo depicting a MITM attack}
-        \label{fig:mitm}
-    \end{figure}
-\end{center}
-
-Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob) the fingerprint of the public key can be used for identification.
-There are, however, issues in how a user should link a key's fingerprint to real world entity.
-This paper will, however, assume that users know the respective parties' correct fingerprint, as the protocols used to achieve this are outside the project's scope.
-
-The fingerprint of the key is generated by running the main components of the key through a secure one way hash function\footnote{Explain this?}.
-This process produces a digest of fixed length that can be used to compare keys.
-Therefore, the comparison of expected and actual fingerprints is used to detect MiTM attacks and prevent impersonation.
-
 \section{PGP}
@@
 \textbf{TODO: } Generate an image of PGP v4 fingerprint packet
-
-\newpage
-
-\section{Pretty Easy Privacy}
-\begin{wrapfigure}{r}{5cm}
-    \centering
-    \includegraphics[scale=0.15]{trustwords/trustword_handshake.jpg}
-    \caption{Trustword fingerprint verification}
-    \label{fig:trustwords}
-\end{wrapfigure}
-
-Pretty Easy Privacy (\pep) is a data encryption system that utilises PGP encryption to provide E2EE on all common channels of communication such as email of SMS.
-\pep's design principles state that above all the systems should be easy to install, use and understand.
-
-\pep deals with the threat of MiTM attacks by having users compare the respective key fingerprints encoded as a set of words.
-Figure \ref{fig:trustwords} shows the \pep Android implementation of trustwords.
-The user pair of users then authenticate the words on an OOB (Out of Band) channel such as a phone call or in-person communication.
-If both users decide the words match they will accept or decline respectively.
-
-The trustwords are unique for each pair of keys, this is the alternative of having a static key for each user.
-The justification behind the unique set for each user pair is in an attempt to motivate users to perform the authentication ceremony.
-The unique combined fingerprint is believed to reduced complacency due to inherent change \textbf{[CITE ME]}.
 

### 2019-07-29 Thesis/pages/lit_review.tex
Changes; - Added more content to the background - Merged background and literature review

@@
 
-Fingerprints are used to compare the similarity of two keys quickly.
-The comparison occurs between two digests of a secure one-way hash function.
+The chapter explains aspects required to fully comprehend the project's achievements alongside an evaluation of current literature and the respective gaps.
+
+\section{Public-key Cryptography and Key Exchange}
+Asymmetric cryptography facilitates the secure encryption of messages in end-to-end encryption (E2EE), verification of digital signatures and sharing of pre-communication secrets, among others.
+The use-case of E2EE messages will be the primary focus of this paper.
+
+The asymmetry stems from the use of "Public" and "Private" keys.
+The Public key is used to encrypt data that only the respective Private key can decrypt.
+This means the keys required to communicate can be easily shared across insecure channels.
+
+To construct an E2EE connection the initial stage will be a key exchange using the key types discussed previously.
+This is the sharing of a pre-shared secret between two verified parties, this will then be used to encrypt subsequent messages with symmetric encryption\footnote{This is due to the speed increase of symmetrical over asymmetrical encryption}.
+This, however, hinges on the verification of the initial parties, if one party impersonates another and gets to view the pre-shared secret all communication becomes decryptable.
+Therefore, the correct identification of parties is crucial to maintaining secure communication channels.
+The exploitation of this is known as a Man-in-the-middle (MiTM) attack.
+This can be bidirectional where the attacker can sit in the middle of a communication channel and decrypt all correspondence.
+Figure \ref{fig:mitm} contains a visual representation of this attack.
+
+\begin{center}
+    \input{diagrams/MITM/basic}
+    \begin{figure}[h]
+        \caption{Photo depicting a MITM attack}
+        \label{fig:mitm}
+    \end{figure}
+\end{center}
+
+Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob) the fingerprint of the public key can be used for identification.
+There are, however, issues in how a user should link a key's fingerprint to real world entity.
+This paper will, however, assume that users know the respective parties' correct fingerprint, as the protocols used to achieve this are outside the project's scope.
+
+The fingerprint of the key is generated by running the main components through a secure one way hash function\footnote{Explain this?}.
+This process produces a digest of fixed length that can be used to compare keys.
+Therefore, the comparison of expected and actual fingerprints is used to detect MiTM attacks and prevent impersonation.
 Historically these have been represented as a hexadecimal string whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card.
-This process is known as the \textit{``authentication ceremony.''}
+This process is known as the \textit{``authentication ceremony.''}.
+However, other systems are moving away from that and creating a single key from each sides' public key.
+In the case of WhatsApp for example, the connection fingerprint of two parties keys is the first 30 bytes of a SHA-512\footnote{5200 iterations} hash of each parties' identity key, these are then both concatenated together to form a single key\cite{whatsapp2017paper}.
+This produces a unique key communication pair.
+\\\\
+\textbf{TODO:} Explain why fingerprints are changing to one-per-pair?
 
+Due to the manual comparison of the fingerprint, length and format is a consideration.
 Prior research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}.
@@
 
-\subsection*{Definition of terms}
+\section*{Definition of terms}
 Throughout the paper, various terms are used to define elements of the authentication ceremony relevant to fingerprints verification.
@@
 
-\subsection{Authentication ceremony performance}
+\section{Authentication ceremony performance}
 
-\subsection*{Encoding scheme performance}
+\section*{Encoding scheme performance}
 Results 
@@
 
-\subsection*{Methods of comparison performance}
+\section*{Methods of comparison performance}
 Aside 
@@
 
-\subsection*{Experimentation methodology comparison}
+\section*{Experimentation methodology comparison}
 To further look into the validity of previously discussed results, it is necessary to asses how the respective studies reached these conclusions.
@@
 %TODO: Maybe talk about the effect of visual or mental impairments 
-\subsubsection{Topic conclusion}
+\subsection{Topic conclusion}
 Overall, this review has identified several key areas suitable for further work.
@@
 
-\subsection{Encoding schemes}
+\section{Encoding schemes}
 Another area of research is investigations into the actual physical encodings of the hash digest.
@@
 Therefore, the wordlist has not been designed with pronounceability in mind.
-\\
-A very recent implementation of a word list can be found in Pretty Easy Privacy (pEp) implementation of TrustWords\footnote{https://tools.ietf.org/html/draft-birk-pep-trustwords-03}.
+\\\\
+A very recent implementation of a word list can be found in Pretty Easy Privacy (\pep) implementation of TrustWords\footnote{https://tools.ietf.org/html/draft-birk-pep-trustwords-03}.
+\pep is a data encryption system that utilises PGP encryption to provide E2EE on all common channels of communication such as email of SMS.
+The imbedded design principles state that above all the systems should be easy to install, use and understand.
+
+\begin{wrapfigure}{r}{6cm}
+    \centering
+    \includegraphics[scale=0.15]{trustwords/trustword_handshake.jpg}
+    \caption{Trustword fingerprint verification}
+    \label{fig:trustwords}
+\end{wrapfigure}
+
+\pep deals with the threat of MiTM attacks by having users compare the respective key fingerprints encoded as a set of words.
+Figure \ref{fig:trustwords} shows the \pep Android implementation of trustwords.
+The user pair of users then authenticate the words on an OOB (Out of Band) channel such as a phone call or in-person communication.
+If both users decide the words match they will accept or decline respectively.
+
 The unique aspect of TrustWords is its mapping of a single word to 16-bits.
@@
 
-\subsubsection{Topic conclusion}
+\textbf{TODO: } Move pep stuff here!
+
+\subsection{Topic conclusion}
 
@@
 
-\subsection{Attacks on encoding schemes}
+\section{Attacks on encoding schemes}
 This area of research studies ways to physically execute attacks on fingerprint encoding schemes.
@@
 
-\subsubsection{Topic Conclusion}
+\subsection{Topic Conclusion}
 Overall the literature for this subtopic remains sparse and incomplete.

### 2019-07-29 Code/GreenOnion/hash.cpp

@@ -45,9 +45,9 @@ static std::mutex kernel_work_lock;
 
 // TODO: Make these script arguments
 bool PRINT_SHA1_TEST = true;
-bool END_ON_KEY_FOUND = true;
+bool END_ON_KEY_FOUND = false;
 bool PRINT_STATS = true;
-bool TEST_KEY_MODE = true;
+bool TEST_KEY_MODE = false;
 
 // RSA key params
 int KEY_LENGTH = 2048;

### 2019-07-30 Thesis/pages/design.tex
Changes; - Added scripts for processing Similar Words results - Added more content to the Thesis

@@
 
+This chapter will discuss and overview of the proposed attack and the elements that are required.
+
+\section{Overall attack design}
+
+The attack on Trustwords involves generating "near-collision" keys.
+These are keys that are deemed a match by the phonetic similar metric (More on this aspect in the following sections).
+A similarity metric is an algorithm designed to determine if two words are phonetically a match.
+For example, the words "THEIR" and "THERE" will be phonetically be a match whereas the words "DARK" and "PRINCIPLE" are not phonetically matching.
+
+As each combined key in Trustwords is an exclusive-or of both sides public key (Figure \ref{fig:xor_trustwords} shows this process) the attack is target to a single pair of users and will require recomputation for every attack instance, this will be considered when discussing the attack feasibility.
+Each pair is also split into a "Uncontrolled" and "Controlled" key.
+Uncontrolled is the reciever of the communication, and, thus, we cannot control their key.
+The Controlled key is the one we are attempting to impersonate, and it is assumed that we have the ability to replace the Controlled key with our malicious option.
+These descriptions will be the terminology used throughout the paper.
+However, it should also be considered that the uncontrolled and controlled can be swapped around with the ability to compute both directions.
+Thus, resulting in the possibility to intercept both directions of communication.
+This, however, will require performing the attack separately for both directions.
+
+\begin{figure}[h!]
+    \centering
+    $KeyFingerprint_{1} \oplus KeyFingerprint_{2} = TrustwordsFingerprint$
+    \caption{Creation of the combined Trustword fingerprint}
+    \label{fig:xor_trustwords}
+\end{figure}
+
+When attacking the respective similarity metric will be used to compute a list of possibilities for each position in the combined fingerprint.
+
+Figure \ref{fig:nearMatch} shows the process of generating a sub section of the combinations.
+A list of each words matches are generated and then the total number of permutations are generated overall.
+
+\begin{figure}[h!]
+    \centering
+    \begin{BVerbatim}[commandchars=\\\{\}]
+        \centering
+\textbf{ CHOKE BLUSHING FRIGHTENING HAND}
+    \end{BVerbatim}
+    \\
+    \verb|COKE                           |
+    \\
+    \verb|SMOKE                          |
+    \\
+    \hspace{1cm}
+
+    \verb|CHOKE                          |
+    \\
+    \begin{BVerbatim}[commandchars=\\\{\}]
+\textbf{COKE BLUSHING FRIGHTENING HAND}
+    \end{BVerbatim}
+    \\
+    \verb|SMOKE                          |
+    \\
+    \hspace{1cm}
+
+    \verb|CHOKE                          |
+    \\
+    \verb|COKE                           |
+    \\
+    \begin{BVerbatim}[commandchars=\\\{\}]
+        \centering
+\textbf{ SMOKE BLUSHING FRIGHTENING HAND}
+    \end{BVerbatim}
+    \caption{Visualization of the generation of near matches}
+    \label{fig:nearMatch}
+\end{figure}
+
+To generate an actual list of fingerprints to search for, the near collision words are converted back into hexadecimal and XORed with the uncontrolled key.
+The provides the impersonated key that will produce the desired combined near-collision.
+Completing this for all of the near-collision permutations will produce a list of fingerprints that can be inserted into a tool designed to hash keys and search for targets.
+This aspect of using a large list to search for keys massively reduces the complexity of the search.
+
+In summary the, attack steps are:
+
+\begin{enumerate}
+    \item Compute all possible matches using a similarity metric on all words in a dictionary (Only needs performing once).
+
+    \item Select a target and allocate "Uncontrolled" and "Controlled" key identification.
+
+    \item Calculate all permutations of near-collisions for the key pair and produce a list of similar key fingerprints.
+
+    \item Use list of similar keys in mass computation of keys to find near-collision keys.
+
+\end{enumerate}
+
+\subsection{Similarity metrics}
+
+\subsubsection{Soundex}
+One of the first requirements for the attack is quantifying "phonetic similarity".
+There are many algorithms currently available to provide this function, is known as Soundex.
+It is one of the most famous example of a phonetic algorithm due to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}.
+Originally designed for indexing names by sound alongside spelling mistakes due to small changes in letters.
+However, due to its design being based on the phonetic features it is highly suitable for this use-case.
+
+Soundex produces a four digit code for each word assessed.
+The first letter of the word is retained alongside the removal of all of a, e, i, o, u, y, h and w. The remaining letters are then mapped to numbers.
+
+\begin{figure}[h!]
+    \centering
+    \begin{BVerbatim}
+b, f, p, v               1
+c, g, j, k, q, s, x, z   2
+d, t                     3
+l                        4
+m, n                     5
+r                        6
+    \end{BVerbatim}
+
+    \caption{Soundex mappings of letters to numbers}
+\end{figure}
+
+Further steps are performed on the code, as the technical details do not add anything to the discussion, the steps of the algorithm can be found in Appendix TODO.
+
+Due to the fixed length and limited digit set the initial concerns from this design is the limited number of combinations.
+There are a total of 5616 codes due to 26 initial letters and three digits of 6 values ($26 * 6^3$).
+The limited combinations will result in matches of a limited quality. This will require consideration later in the project.
+
+\subsubsection{Metaphone}
+\textbf{TODO}
+
+\subsubsection{NYSIIS}
+\textbf{TODO}
+
+\subsubsection{Levenshtien}
+\textbf{TODO}
+
 \section{Design of GreenOnion}

### 2019-07-30 Thesis/pages/lit_review.tex
Changes; - Added scripts for processing Similar Words results - Added more content to the Thesis

@@
 The Public key is used to encrypt data that only the respective Private key can decrypt.
-This means the keys required to communicate can be easily shared across insecure channels.
+This means the keys required to encrypt can be easily shared across insecure channels.
 
@@
 
-The fingerprint of the key is generated by running the main components through a secure one way hash function\footnote{Explain this?}.
+The fingerprint of the key is generated by running the main components through a secure one way hash function such as SHA-1.
 This process produces a digest of fixed length that can be used to compare keys.
-Therefore, the comparison of expected and actual fingerprints is used to detect MiTM attacks and prevent impersonation.
+Therefore, the comparison of expected and actual fingerprints can be used too detect MiTM attacks.
 Historically these have been represented as a hexadecimal string whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card.
-This process is known as the \textit{``authentication ceremony.''}.
-However, other systems are moving away from that and creating a single key from each sides' public key.
+This process is known as the \textit{``authentication ceremony''}.
+However, system designers are moving away from this structure and are now creating a combined key from each sides' public key.
 In the case of WhatsApp for example, the connection fingerprint of two parties keys is the first 30 bytes of a SHA-512\footnote{5200 iterations} hash of each parties' identity key, these are then both concatenated together to form a single key\cite{whatsapp2017paper}.
@@
 \\\\
-\textbf{TODO:} Explain why fingerprints are changing to one-per-pair?
-
 Due to the manual comparison of the fingerprint, length and format is a consideration.
@@
 Therefore, the wordlist has not been designed with pronounceability in mind.
-\\\\
+
+\subsubsection{Pretty Easy Privacy}
 A very recent implementation of a word list can be found in Pretty Easy Privacy (\pep) implementation of TrustWords\footnote{https://tools.ietf.org/html/draft-birk-pep-trustwords-03}.
-\pep is a data encryption system that utilises PGP encryption to provide E2EE on all common channels of communication such as email of SMS.
+\pep is a data encryption system that utilises PGP encryption to provide E2EE on all common channels of communication such as email or SMS.
 The imbedded design principles state that above all the systems should be easy to install, use and understand.
@@
 \pep deals with the threat of MiTM attacks by having users compare the respective key fingerprints encoded as a set of words.
-Figure \ref{fig:trustwords} shows the \pep Android implementation of trustwords.
-The user pair of users then authenticate the words on an OOB (Out of Band) channel such as a phone call or in-person communication.
+Figure \ref{fig:trustwords} shows the \pep Android implementation of Trustwords.
+The users then authenticate the words on an OOB (Out of Band) channel such as a phone call or in-person communication.
 If both users decide the words match they will accept or decline respectively.
@@
 In comparison to other literature, this is the highest number of bits-per-word seen.
-Full mappings (no duplication of words) would, therefore, require $2^{16}$ words in the dictionary and arguably is higher than most users vocabulary.
-this deviation from the norm has not been currently backed up by research.
+Full mappings (no duplication of words) would, therefore, require $2^{16}$ words in the dictionary where arguably the dictionary size is higher than most users' vocabulary.
+This deviation from the norm has not been currently backed up by research.
+
+\begin{wrapfigure}{l}{5cm}
+    \centering
+    \begin{BVerbatim}
+    [...]
+52127 ZYGOTE
+52128 ZYGOTIC
+52129 ZYMURGY
+52130 AACHEN
+52131 AARDVARK
+52132 AAREN
+    [...]
+    \end{BVerbatim}
+    \caption{Re-mapping position in Trustword dictionary}
+    \label{fig:remap}
+\end{wrapfigure}
+
+Alongside the abnormally high number of words the design choice to exclude slang and profanities from the English Trustword dictionary requires dual-mapping of a section of words.
+Approximately 13633/65536 (20.8\%) of words are re-mapped in the dictionary leaving 51903 unique words.
+The re-mapping is also done on a loop with it remaining alphabetical.
+Figure \ref{fig:remap} shows the position in the dictionary where this occurs.
+This predictability within the dictionary will be explored later in the paper.
+
 Moreover the main RFC documentation still remains in a draft stage and states \textit{``It is for further study, what minimal number of words (or entropy) should be required.''}.
 These aspects clearly highlight on a gap in the current literature.
-
-\textbf{TODO: } Move pep stuff here!
 
@@
 \section{Overall Summary}
-\textbf{TODO: } Create an overall summary of all the gaps identified
+In summary of the literature gaps areas discovered; encoding scheme performance requires further work in the performance of all graphical schemes to back up the results made by other work.
+Furthermore, there is a gap with the assessment of encoding schemes in the context of "remote-vs-proximity" first proposed by M.
+Shirvanian et al.
+as it would arguably provide a better simulation of real world scenarios.
 
-\section{Research Questions}
-\textbf{TODO: } - Backup choice of questions up using my previous discussion.
+In the context of human attributes and the way they alter the performance of the schemes; further research is required into how the fluency of languages affects authentication ceremony.
+This is a continuation of the initial work by Hsiao et al and could allow the creation of schemes that are better suited to certain languages.
+Alongside this, there is a research gap in the investigation of how mental impairments affect the performance.
+This is useful due to the number of potential users being affected due to systems not being designed with them in mind.
+For example, 7\% of the population has been identified as having dyslexic tendencies\cite{peterson2012developmental}.
+This means with a UK population of around 63,000,000\footnote{From the 2011 Census collated by the Office for National Statistics}  4,410,000 people could benefit from encoding schemes including dyslexic oriented benefits.
+This is also only one of many visual impairments that could affect a scheme's performance, thus further contributing to the substantial affect further work could have on this area.
+
+Other possible large areas for consideration is the lacks of direct consideration for attack strength when assessing the vulnerability of encoding schemes.
+Issues included the wide range of attack strength ($2^{28}$ - $2^{242}$) and the lack of consideration at all from certain papers.
+This alongside the complete lack of computation and storage complexity considerations means this is a prime area for further research as it would improve the applicability of results.
+
+The final major research gap identified is the lack of justification into the newly created \pep Trustwords.
+Abnormal design choices (16-bit per word) and its recent creation makes it another area for a wide variety of further research.
+This is also combined with the conclusive results from the literature on the effectiveness of language based encodings such as words.
+This would suggest that research into the improvement of Trustword encoding would be highly beneficial.

### 2019-07-30 Thesis/pages/research_question.tex
Changes; - Added scripts for processing Similar Words results - Added more content to the Thesis

\chapter{Research Questions}

Following on from the previous chapter, this chapter will define the selected gaps and the subsequent research questions and aims.

The chosen project aims to asses the security of \pep's minimum recommend number of four Trustwords (As stated in Figure \ref{fig:trustwordsNum}). As discussed in the previous chapter, Trustwords aims to sacrifice security for increased usability. The encoding scheme has been designed to assist this by having  the user compare a reduced set of words. Moreover, issues with the dictionary's design such as the presence of homophones and dual-mapping of words shows the potential for possible vulnerabilities.

As discussed in the previous chapter, the identified research gap regarding the minimal consideration of attack complexity would be a suitable addition for this project. This is due to it providing the ability to asses actual performance and, thus, the actual real-world strength of Trustwords while providing research to a scant area. Therefore, the security assessment will be supplemented with complexity considerations and an actual implementation of the attack proposed.

\begin{figure}[h!]
    \centering
    \begin{verbatim}
"Short Trustword Mapping (S-TWM) requires a number of 
Trustwords that MUST retain at least 64 bits of entropy. 
Thus, S-TWM results into at least four Trustwords to be 
compared by the user."
    \end{verbatim}
    \caption{Most recent RFC security recommendation}
    \label{fig:trustwordsNum}
\end{figure}

By sampling the \pep documentation they have defined the use case of the Trustword handshake: \textit{A handshake is done by comparing the Trustwords between two users through a separate communication channel (e.g. in person or by phone).}\footnote{https://www.pep.security/docs/general\_information.html\#handshake}. It can be assumed due the increased globalization of the planet that the most common handshake occurrence will be over the phone, and, therefore, will not be in person. This is, therefore, the assumed context the handshake will be occurring in. This means the similarity of words will need to be quantified phonetically instead of visually.

\section{Questions}

With the previously discussed points in mind the following research questions have been proposed.

\begin{itemize}
    \item Is the recommended minimum number of four Trustwords enough to provide a basic level of security?

    \item What are the different ways phonetic similarity can be quantified?

    \item What is the time and computation complexity required to generate a 'similar' keys for a targeted key pair?

    \item What kind of hardware is required to compute a matching key?

    \item What percentage of attacks successfully deceive a user?
\end{itemize}

With these research questions defined, the project will now discuss the design of the proposed attack.

### 2019-07-30 Code/TrustwordUtil/calculate_perms.sh

@@ -2,12 +2,14 @@
 
 set -e
 
-declare -a metricArr=("soundex" "leven" "metaphone" "nysiis" "wordvec_4_5")
+# declare -a metricArr=("soundex" "leven" "metaphone" "nysiis" "wordvec_4_5")
+declare -a metricArr=("wordvec_4")
+
 
 # declare -a permsArr=("1000" "10000" "100000") # 1 day
 # declare -a permsArr=("500" "5000" "50000") # 2 days
-declare -a permsArr=("250" "2500" "25000") # 3 days
-# declare -a permsArr=("152" "1525" "15250") # 1 week
+# declare -a permsArr=("250" "2500" "25000") # 3 days
+declare -a permsArr=("152" "1525" "15250") # 1 week
 
 declare -a staticArr=("0" "1" "2")
 

### 2019-07-30 Experiments/MainExperiment/website/backend/CONFIG.py

@@ -1,7 +1,7 @@
 BASE_FILE_LOCATION = "" #B700
 ATTACK_CHANCE = 0.3
-NUMBER_OF_ROUNDS = 10
-GRACE_ROUNDS = 5 # Number of inital rounds that can't contain an attack
+NUMBER_OF_ROUNDS = 15
+GRACE_ROUNDS = 5 # Number of initial rounds that can't contain an attack
 
 ## NOTE:
 #   Naming convension for files is:

### 2019-07-30 Experiments/MainExperiment/website/backend/results/overall_results.py

@@ -1,0 +1,35 @@
+import os
+import sys
+import pickle
+
+sys.path.append("..")
+
+trick_attacks = {}
+all_attacks = {}
+
+for file in os.listdir("."):
+    if file.endswith(".pkl"):
+        
+        exp = pickle.load(open(file, "rb"))
+
+        for i, attack in enumerate(exp.AttackSchema):
+            if attack:
+
+                attack_id = f"{attack[0]}-{attack[1]}"
+
+                if not attack_id in all_attacks:
+                    all_attacks[attack_id] = 1
+                else:
+                    all_attacks[attack_id] += 1
+
+                # Checks if verified
+                if exp.Responses[i] == "True":
+                    
+                    if not attack_id in trick_attacks:
+                        trick_attacks[attack_id] = 1
+                    else:
+                        trick_attacks[attack_id] += 1
+                
+print("[*] Successful attacks (%): ")
+for attackID in trick_attacks:
+    print("\t", attackID, round(trick_attacks[attackID] / all_attacks[attackID], 2))

### 2019-07-30 Experiments/MainExperiment/website/backend/tests/probability_check.py

@@ -1,4 +1,5 @@
 import sys
+sys.path.insert(0, "..")
 sys.path.insert(0, ".")
 import attack
 
@@ -29,7 +30,7 @@ def check_attacks():
         sys.stderr.write(f"{x}/{ROUNDS}\r")
         sys.stderr.flush()
 
-        a = attack.decision(WORDS)
+        a = attack.decision()
         if a != None: 
             METRIC_COUNT[a[0]] += 1
             ATTACK_TYPE_COUNT[a[1]] += 1

### 2019-07-30 Experiments/MainExperiment/website/backend/trustwords_util/util/CONFIG.py

@@ -1,3 +1,3 @@
 # Around 4 x GTX 1080
 HASHSPEED = 2000 * 4
-MAX_PEM_SIZE = 200000
+MAX_PEM_SIZE = 2000000

### 2019-07-30 Experiments/PilotStudy/results/check_for_invalid.py

@@ -1,0 +1,39 @@
+import sys
+
+def usage():
+    print("Usage ./{__file__} <RESULTS_CSV>")
+    exit()
+
+def parse(filepath):
+    responses = []
+    with open(filepath) as file:
+        responses = file.readlines()
+
+    # Removes the headers
+    del responses[0]
+
+    for r in responses:
+
+        parts = r.split(",")
+        
+        sectionsParts = parts[4:len(parts) - 6]
+        testQuestions = parts[len(parts) - 5:len(parts) - 2]
+
+
+        sections = []
+        for i, s in enumerate(sectionsParts[::5]):
+            index = i * 5
+            sections += [sectionsParts[index:index + 5]]
+
+        randomSection = list(map(int, sections[-1]))
+        print(f"[*] Random average: {sum(randomSection) / len(randomSection)}", )
+
+
+
+
+if __name__ == "__main__":
+
+    if len(sys.argv)!= 2:
+        usage()
+
+    parse(sys.argv[1])

### 2019-07-30 Experiments/PilotStudy/results/parse_results.py

@@ -30,6 +30,7 @@ RESULTS = {
 
 def usage():
     print("Usage ./{__file__} <RESULTS_CSV>")
+    exit()
 
 def order_results(filepath):
     responses = []

### 2019-07-30 Thesis/pages/design.tex
Changes; - Added more content to design section

@@
 \end{figure}
+\textbf{TODO: Turn into a table}
 
@@
 
+\subsubsection{NYSIIS}
+The New York State Identification and Intelligence System (NYSIIS) Phonetic Code was created for use matching the phonetics of American names.
+However, due to it having embedded rules to handle word phonetics it would, again be applicable in this application.
+It allows for variable length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex.
+
 \subsubsection{Metaphone}
-\textbf{TODO}
+Metaphone was invented by Lawrence Philips in 1990\cite{philips1990hanging} in response to the deficienies in Soundex.
+It improves on Soundex by including information around inconsistency and variation in English spelling in an attempt to create a more accurate phonetic representation.
+Metaphone is arguably on the same level of ubiquity as that of Soundex with it finding itself implemented in languages such as big examples like PHP\cite{php}.
+Further work would involve the implementation of newer versions of Metaphone.
+Double Metaphone (2000) and Metaphone 3 (2009) claim to improve over the original version due to further research performed by Philips.
+The original version was chosen due to its historical wide spread usage alongside the case of Metaphone 3 being proprietary code and, therefore, under a paid licence.
 
-\subsubsection{NYSIIS}
-\textbf{TODO}
+\textbf{TODO: } Talk about why length of 10 was chosen.
 
@@
 
+\textbf{TODO: } Do a sample conversions table
+
+% List of papers assessing algorithms
+%   - Analysis andComparative Study on Phonetic Matching Techniques
+%   - Performance Evaluation of Phonetic Matching Algorithms on English Words and Street Names
+%   - Study Existing Various Phonetic Algorithms and Designing and Development of a working model for the New Developed Algorithmand Comparison by implementing it with Existing Algorithm(s)
+
+% Other alternatives:
+% - Match Rating Approach
+%   - Couldn't find an algorithm??
+%
+% - Caverphone
+
+\textbf{TODO: } Need to justify why
+
 \section{Design of GreenOnion}

### 2019-07-30 Code/GreenOnion/hash.cpp

@@ -45,7 +45,7 @@ static std::mutex kernel_work_lock;
 
 // TODO: Make these script arguments
 bool PRINT_SHA1_TEST = true;
-bool END_ON_KEY_FOUND = false;
+bool END_ON_KEY_FOUND = true;
 bool PRINT_STATS = true;
 bool TEST_KEY_MODE = false;
 
@@ -58,7 +58,7 @@ int EXPONENT = 0x01000001;
 // TODO: DO NOT CHANGE ME! WITHOUT ALTERING THE VALUE IN THE opencl/SHA1.cl file
 //       passing this value to the script is required
 uint BLOOM_NUMBER_OF_HASHES_STATIC  = 2;          //Set to 0 for dynamic size
-long BLOOM_SIZE_STATIC              = 8000000;    //Set to 0 for dynamic size
+long BLOOM_SIZE_STATIC              = 1000000;    //Set to 0 for dynamic size
 
 // Threading params
 bool running = true;
@@ -67,10 +67,6 @@ std::vector<std::thread> workThreads;
 
 size_t NUM_OF_HASHES = 16777215;            // The amount of hashes per loop
 size_t MAX_WORK_SIZE = 1000;                //Set to 0 for no cap
-
-//DEBUG
-// std::string target_keys_file_path = "/home/main_user/GitHub/Cyber-Security-Individual-Project/Code/GreenOnion/target_keys.txt";
-// std::string kernel_file_path = "/home/main_user/GitHub/Cyber-Security-Individual-Project/Code/GreenOnion/opencl/SHA1.cl";
 
 std::string target_keys_file_path = "";
 std::string kernel_file_path = "./opencl/SHA1.cl";
@@ -269,8 +265,6 @@ void compute()
     cl::Buffer buf_bitVectorSize(context, CL_MEM_READ_ONLY | CL_MEM_COPY_HOST_PTR, sizeof(long), bloom_bit_vector_size, &err);
     if (err != 0) opencl_handle_error(err, "bit_vector_size");
 
-    auto startTime = std::time(nullptr);
-
     while (true)
     {
 
@@ -286,6 +280,8 @@ void compute()
 
         cl::Buffer buf_currentHash(context, CL_MEM_READ_ONLY | CL_MEM_COPY_HOST_PTR, sizeof(uint) * 5, work.CurrentHash, &err);
         if (err != 0) opencl_handle_error(err, "current_hash");
+
+        
         
[…]

### 2019-07-31 Thesis/pages/design.tex
Changes; - Added result from UK MTurk study - More content added to Thesis

@@
 \end{figure}
-\textbf{TODO: Turn into a table}
 
 Further steps are performed on the code, as the technical details do not add anything to the discussion, the steps of the algorithm can be found in Appendix TODO.
+
+\subsubsection{Soundex Issues}
 
@@
 
+Further issues posed in \cite{patman2001soundex} are discussed below and show the further deficiencies of Soundex in a dictionary word matching context.
+
+\begin{enumerate}
+    \item \textbf{Dependency on the first letter:} Soundex cannot match words together if their first letters are different, meaning for example the words "KORBIN" and "CORBIN" will never be matched.
+
+    \item \textbf{Silent consonants.} Soundex does not have logic embedded to deal with silent consonants within words.
+
+    \item \textbf{Poor precision.} Due to the previously discussed point of a small code resulting in lack of precision.
+\cite{patman2001soundex} re-iterates this point but in the context of name matching where Soundex's poor performance was demonstrated.
+Soundex only gained and overall accuracy 36.37\% when matching names within a database.
+\end{enumerate}
+
+However, even with Soundex's fallbacks its algorithmic simplicity and popularity allows it to still remain relevant in this application.
+
 \subsubsection{NYSIIS}
-The New York State Identification and Intelligence System (NYSIIS) Phonetic Code was created for use matching the phonetics of American names.
+The New York State Identification and Intelligence System (NYSIIS) phonetic code was created for use matching the phonetics of American names.
+It was created due to the presence of hispanic names in the American based databases (this was an aspect Soundex was known to have low accuracy with).
 However, due to it having embedded rules to handle word phonetics it would, again be applicable in this application.
-It allows for variable length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex.
+
+It also allows for variable length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex.
+It was in use right up the end of 1998 within various US Government departments.
+Due to this prolific stature and proven track record it was deemed suitable as one of the selected similarity metrics.
 
@@
 
-\textbf{TODO: } Talk about why length of 10 was chosen.
+\subsubsection{Levenshtien Distance}
+Levenshtein distance is a string metric designed to measure the 'distance' between two strings.
+It is simply the number of single-character edits (insertions, deletions or substitutions) required to reach the other string.
+Edit distance is not technically designed as a phonetic algorithm, but due to similar-sounding words often being spelt in similar ways\cite{hettiarachchi2012sparcl} Levenshtien distance was deemed another suitable metric.
 
-\subsubsection{Levenshtien}
-\textbf{TODO}
+An example distance between \verb|trace| and \verb|place| would be the substitutions of the first to letters, from \verb|tr| to \verb|pl| meaning the two strings have a Levenshtein distance of 2.
+
+\subsubsection{Word Vectors}
 
@@
 % List of papers assessing algorithms
-%   - Analysis andComparative Study on Phonetic Matching Techniques
+%   - Analysis and Comparative Study on Phonetic Matching Techniques
 %   - Performance Evaluation of Phonetic Matching Algorithms on English Words and Street Names

### 2019-07-31 Experiments/PilotStudy/MTurk/give_quali.py

@@ -1,0 +1,78 @@
+import sys
+
+"""
+Script that edits MTurk .csv files depending on the result from the study
+"""
+
+
+def load(filePath):
+
+    data = []
+    newData = []
+    with open(filePath) as file:
+        data = file.readlines()
+
+    newData.append(data[0].strip().split(","))
+    headerLength = len(newData[0])
+
+    for d in data[1:]:
+        d = d.replace("\n", "")
+        temp = d.split(",")
+
+        while len(temp) < headerLength:
+            temp.append("")
+
+        newData.append(temp)
+
+    return newData
+
+def save(filePath, data):
+
+    with open(filePath, "w") as file:
+
+        for d in data:
+            file.write(",".join(d) + "\n")
+
+def usage():
+    print(f"Usage: ./{__name__} <MAIN_WORKER_FILE> <HIT_WORKER_FILE>")
+    exit()
+
+
+if __name__ == "__main__":
+    
+    if len(sys.argv) != 3:
+        usage()
+
+    mainWorkerFilePath = sys.argv[1]
+    hitWorkerFilePath = sys.argv[2]
+
+    mainWorkerData = load(mainWorkerFilePath)
+    hitWorkerData = load(hitWorkerFilePath)
+
+    qualiHeaderPosition = mainWorkerData[0].index("\"UPDATE-English Fluency\"")
+
+    answerPosition = hitWorkerData[0].index('\"Answer.howMuch\"') + 1
+    workerIdPosition = hitWorkerData[0].index('\"WorkerId\"') + 1
+    approveHeaderPosition = hitWorkerData[0].index("\"Approve\"") + 1
+
+    for hit in hitWorkerData[1:]:
+        workerID = hit[workerIdPosition]
+
+        mainFileWorkerIDIndex = None
+        for i, m in enumerate(mainWorkerData[1:]):
+            if m[0] == workerID:
+                mainFileWorkerIDIndex = i + 1
+
+                if hit[answerPosition] == '\"5\"':
+                    mainWorkerData[mainFileWorkerIDIndex][qualiHeaderPosition] = '1'
+                    hit[approveHeaderPosition] = "x"
+                break
+
+        else:
+            # raise Exception("Error: Worker ID not found!")
+            print(f"[!] Worker: {workerID} not found!")
+            pass
+
+    save("User.csv", mainWorkerData)
+    save("Batch.csv", hitWorkerData)
+            

### 2019-07-31 Thesis/pages/design.tex
Changes; - Added more content to the design section

@@
 
-\subsubsection{Word Vectors}
+\subsubsection{Phonetic Vectors}
+Phonetic Vectors is the unique addition to the chosen set.
+Created by Allison Parrish in 2017\cite{parrish2017poetic}, Phonetic vectors is as the name suggests the vectorization of a words phonetics.
+This allows a words phonetics to be represented using a continuous number in vector space.
+
+Phonetic features are used in this work as a way to compare the similarity of the phonemes.
+Extensive prior work has gone into producing models of features that map to phonemes.
+\cite{chomsky1968sound}\cite{ladefoged1969measurement}\cite{bradlow2010perceptual}.
+Features, therefore, a newer attempt at mapping the varying and inconsistent rules around pronunciation of the English language.
+The vectors are created using lists phonemes from the CMU Pronouncing Dictionary.
+Phonemes are the phonetic elements that construct a word.
+For example the word "RING" translated into the phonemes \verb|/R IH NG/|.
+Using all words available and mapping all phonemes to phonetic features a list of unique features is created per-word.
+
+\begin{table}[!htb]
+    \tiny
+    \begin{minipage}{.33\linewidth}
+        \centering
+        \begin{tabular}{ll}
+            Phone & Features \\
+            \hline
+            AA & bck, low, unr, vwl \\
+            AE & fnt, low, unr, vwl \\
+            AH & cnt, mid, unr, vwl \\
+            AO & bck, lmd, rnd, vwl \\
+            AW & bck, cnt, low, rnd, smh, unr, vwl \\
+            AY & cnt, fnt, low, smh, unr, vwl \\
+            B & blb, stp, vcd \\
+            CH & alv, frc, stp, vls \\
+            D & alv, stp, vcd \\
+            DH & dnt, frc, vcd \\
+            EH & fnt, lmd, unr, vwl \\
+            ER & cnt, rzd, umd, vwl \\
+            EY & fnt, lmd, smh, unr, vwl
+        \end{tabular}
+    \end{minipage}%
+    \begin{minipage}{.33\linewidth}
+        \centering
+        \begin{tabular}{ll}
+            Phone & Features \\
+            \hline
+            F &  frc, lbd, vls \\
+            G &  stp, vcd, vel \\
+            HH & apr, glt \\
+            IH & fnt, smh, unr, vwl \\
+            IY & fnt, hgh, unr, vwl \\
+            JH & alv, frc, stp, vcd \\
+            K &  stp, vel, vls \\
+            L &  alv, lat \\
+            M &  blb, nas \\
+            N &  alv, nas \\
+            NG & nas, vel \\
+            OW & bck, rnd, smh, umd, vwl \\
+            OY & bck, fnt, lmd, rnd, smh, unr, vwl
+        \end{tabular}
+    \end{minipage} 
+    \begin{minipage}{.33\linewidth}
+        \centering
+        \begin{tabular}{ll}
+            Phone & Features \\
+            \hline
+            P & blb, stp, vls \\
+            R & alv, apr \\
+            S & alv, frc, vls \\
+            SH & frc, pla, vls \\
+            T & alv, stp, vls \\
+            TH & dnt, frc, vls \\
+            UH & bck, rnd, smh, vwl \\
+            UW & bck, hgh, rnd, vwl \\
+            V & frc, lbd, vcd \\
+            W & apr, lbv \\
+            Y & apr, pal \\
+            Z & alv, frc, vcd \\
+            ZH & frc, pla, vcd \\
+        \end{tabular}
+    \end{minipage} 
+    \caption{Phonemes to feature mapping table}
+    \label{tab:features}
+\end{table}
+
+Table \ref{tab:features} contains the mappings used in \cite{parrish2017poetic} to create the phonetic feature lists.
+Using this with all 133,852 entries in version 0.7b of the CMU Pronouncing Dictionary, 949 unique properties were produced overall.
+The author then performed principal components analysis\footnote{Details regarding this process is outside the scope of the project.
+Please, however, if interested please refer to this resource for more information: \url{http://setosa.io/ev/principal-component-analysis/}} on the unique properties to reduce them down to 50.
+
+This metric allows for a unique set of actions to be performed on the phonetic output.
+Not only does this metric allow the user to measure \textit{dissimilarity} (opposed to the similar-or-not method of the alternatives) the continuous nature of the value allows mathematical operations to be performed on the output.
+An example shown in \cite{parrish2017poetic} was the addition of word vectors.
+
+\begin{table}[!htb]
+    \centering
+    \begin{tabular}{cll}
+        No & Operation & Result \\
+        \hline
+        1  & $Vec(\verb|sub|) + Vec(\verb|marine|)$ & \verb|submarine| \\
+        2  & $Vec(\verb|miss|) + Vec(\verb|sieve|)$ & \verb|missive| \\
+        3  & $Vec(\verb|fizz|) + Vec(\verb|theology|)$ & \verb|physiology| \\
+    \end{tabular}
+    \caption{Examples of vector addition}
+    \label{tab:vectorAdd}
+\end{table}
+
+For example, the addition of vectors can be seen in Table \ref{tab:vectorAdd}. This works for any mathematical operation with multiplication allowing the 'tinting' words with a theme.
+
+\textbf{TODO: } Explain why being vectors is useful and its appliactions
 
@@
 
-% List of papers assessing algorithms
-%   - Analysis and Comparative Study on Phonetic Matching Techniques
-%   - Performance Evaluation of Phonetic Matching Algorithms on English Words and Street Names
-%   - Study Existing Various Phonetic Algorithms and Designing and Development of a working model for the New Developed Algorithmand Comparison by implementing it with Existing Algorithm(s)
+\subsection{Alternative Similarity Metrics}
+
+\subsubsection{Match Rating Approach}
+Matching Rating Approach (MRA) is another algorithm designed to match names within a database, therefore, its operation can be grouped with that of NYSIIS and Soundex.
+MRA was discarded as an option.
+This is because of the lack of known utilization in any substantial real world use-cases alongside its similarity to more well established algorithms of Soundex and NYSIIS.
+
+Further work could include the comparison of this algorithm  to similar alternatives in phonetically matching of words to quantify performance.
+This will be discussed further in the evaluative sections of the report.
+
+\subsubsection{Caverphone}
+Another notable alternative solution is that of Caverphone that was designed in New Zealand.
+Caverphone as is the case with the vast majority of phonetic algorithms was designed for use with name matching.
+Caverphone was not chosen to similar reasons to that of MRA alongside its optimization for accents in location of New Zealand it was conceived in.
+Therefore, the low level of utilization alongside the unique design features that suggest it may not be suited for this application.
+This has, however, not be assessed empirically and thus would be a candidate for further work.
 

### 2019-07-31 Experiments/PilotStudy/results/check_for_invalid.py
Changes; - Added results from the complete study

@@ -1,39 +1,0 @@
-import sys
-
-def usage():
-    print("Usage ./{__file__} <RESULTS_CSV>")
-    exit()
-
-def parse(filepath):
-    responses = []
-    with open(filepath) as file:
-        responses = file.readlines()
-
-    # Removes the headers
-    del responses[0]
-
-    for r in responses:
-
-        parts = r.split(",")
-        
-        sectionsParts = parts[4:len(parts) - 6]
-        testQuestions = parts[len(parts) - 5:len(parts) - 2]
-
-
-        sections = []
-        for i, s in enumerate(sectionsParts[::5]):
-            index = i * 5
-            sections += [sectionsParts[index:index + 5]]
-
-        randomSection = list(map(int, sections[-1]))
-        print(f"[*] Random average: {sum(randomSection) / len(randomSection)}", )
-
-
-
-
-if __name__ == "__main__":
-
-    if len(sys.argv)!= 2:
-        usage()
-
-    parse(sys.argv[1])

### 2019-07-31 Results/PiliotStudy/parse_results.py

@@ -4,18 +4,16 @@ import sys
 Parses the results from the Google Forms pilot study
 """
 
-NUM_OF_DEMOGRAPHIC_QUESTIONS = 4
+NUM_OF_DEMOGRAPHIC_QUESTIONS = 7
 
 # This is questions added after the first launch of the survery
 # Google Sheets does not try to maintain the order so new questions
 # are added to the end
 #       
-#   1. English proficiency
-#   2. Attension question "UNIVERSITY-UNIVERSITY"
-#   3. Attension question "DYNAMIC-DYNAMIC"
-#   4. Worder ID
-#   5. Consent
-NEWLY_ADDED_QUESTIONS = 6
+#   1. Attension question "UNIVERSITY-UNIVERSITY"
+#   2. Attension question "DYNAMIC-DYNAMIC"
+#   3. Random Average
+NEWLY_ADDED_QUESTIONS = 3
 
 SECTIONS = ["Soundex", "Metaphone", "Leven", "NYSIIS", "WordVec", "Random"]
 

### 2019-08-01 Thesis/pages/design.tex
Changes; - Added a lot of content to the design stage of the report

@@
 The attack on Trustwords involves generating "near-collision" keys. 
-These are keys that are deemed a match by the phonetic similar metric (More on this aspect in the following sections).
+This will attempt to provide the base to answer Research Questions \ref{goal:numberOfTrustwords}, \ref{goal:complexity} and \ref{goal:hardwareRequired}.
+
+Near-collision keys are keys that are deemed a match by the phonetic similar metric (More on this aspect in the following sections).
 A similarity metric is an algorithm designed to determine if two words are phonetically a match.
@@
 
-\subsection{Similarity metrics}
+\section{Similarity metrics}
+\label{sec:metrics}
+One of the first requirements for the attack is quantifying "phonetic similarity".
+This section is looking to provide an answer for the Research Question \ref{goal:phoneticSimilarity}.
+There are many algorithms currently available to provide this functionality.
+This section will describe algorithms alongside the reasons they were selected for assessment later in the project.
 
-\subsubsection{Soundex}
-One of the first requirements for the attack is quantifying "phonetic similarity".
-There are many algorithms currently available to provide this function, is known as Soundex.
-It is one of the most famous example of a phonetic algorithm due to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}.
-Originally designed for indexing names by sound alongside spelling mistakes due to small changes in letters.
-However, due to its design being based on the phonetic features it is highly suitable for this use-case.
+\subsection{Soundex}
+One of the earliest example of a phonetic algorithm is known as Soundex.
+It is one of the most famous algorithm due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}.
+Originally designed for indexing names by phonetics alongside spelling mistakes due to transpositions in letters.
+Therefore, due to it being based on the phonetic features, it is highly suitable for this project's use-case.
 
 Soundex produces a four digit code for each word assessed.
-The first letter of the word is retained alongside the removal of all of a, e, i, o, u, y, h and w. The remaining letters are then mapped to numbers.
+The first letter of the word is retained alongside the removal of all of a, e, i, o, u, y, h and w.
+The remaining letters are then mapped to numbers\footnote{Further steps are performed on the code, as the technical details do not add anything to the discussion, the steps of the algorithm can be found in Appendix TODO.}.
+These mappings are displayed in Figure \ref{fig:soundexMap}.
 
@@
     \caption{Soundex mappings of letters to numbers}
+    \label{fig:soundexMap}
 \end{figure}
 
-Further steps are performed on the code, as the technical details do not add anything to the discussion, the steps of the algorithm can be found in Appendix TODO.
-
-\subsubsection{Soundex Issues}
+\subsection{Soundex Issues}
+\label{sec:soundexIssues}
 
@@
 
-    \item \textbf{Silent consonants.} Soundex does not have logic embedded to deal with silent consonants within words.
+    \item \textbf{Silent consonants.} Soundex does not have logic embedded to deal with silent consonants.
 
-    \item \textbf{Poor precision.} Due to the previously discussed point of a small code resulting in lack of precision.
+    \item \textbf{Poor precision.} Due to the previously discussed point of a small code space.
 \cite{patman2001soundex} re-iterates this point but in the context of name matching where Soundex's poor performance was demonstrated.
-Soundex only gained and overall accuracy 36.37\% when matching names within a database.
+Soundex only gained and overall accuracy 36.37\% when matching names within a provided database.
 \end{enumerate}
@@
 
-\subsubsection{NYSIIS}
+\subsection{NYSIIS}
 The New York State Identification and Intelligence System (NYSIIS) phonetic code was created for use matching the phonetics of American names.
@@
 
-\subsubsection{Metaphone}
-Metaphone was invented by Lawrence Philips in 1990\cite{philips1990hanging} in response to the deficienies in Soundex.
+\subsection{Metaphone}
+Metaphone was invented by Lawrence Philips in 1990\cite{philips1990hanging} in response to the deficiencies in Soundex.
 It improves on Soundex by including information around inconsistency and variation in English spelling in an attempt to create a more accurate phonetic representation.
-Metaphone is arguably on the same level of ubiquity as that of Soundex with it finding itself implemented in languages such as big examples like PHP\cite{php}.
+Metaphone is arguably on the same level of ubiquity as that of Soundex with it finding itself implemented in languages such as PHP\cite{php}.
+
 Further work would involve the implementation of newer versions of Metaphone.
 Double Metaphone (2000) and Metaphone 3 (2009) claim to improve over the original version due to further research performed by Philips.
-The original version was chosen due to its historical wide spread usage alongside the case of Metaphone 3 being proprietary code and, therefore, under a paid licence.
+The original version was chosen due to its historical widespread usage.
 
-\subsubsection{Levenshtien Distance}
+\subsection{Levenshtien Distance}
 Levenshtein distance is a string metric designed to measure the 'distance' between two strings.
@@
 
-\subsubsection{Phonetic Vectors}
+\subsection{Phonetic Vectors}
 Phonetic Vectors is the unique addition to the chosen set.
 Created by Allison Parrish in 2017\cite{parrish2017poetic}, Phonetic vectors is as the name suggests the vectorization of a words phonetics.
-This allows a words phonetics to be represented using a continuous number in vector space.
+This allows a words phonetics to be represented in vector space.
 
-Phonetic features are used in this work as a way to compare the similarity of the phonemes.
+Phonetic features are used in this work as a way to compare the similarity of a words phonemes.
+Phonemes are the phonetic elements that construct a word.
+For example the word "RING" translated into the phonemes \verb|/R IH NG/|.
 Extensive prior work has gone into producing models of features that map to phonemes.
 \cite{chomsky1968sound}\cite{ladefoged1969measurement}\cite{bradlow2010perceptual}.
-Features, therefore, a newer attempt at mapping the varying and inconsistent rules around pronunciation of the English language.
+Features, therefore, are an attempt at mapping the varying and inconsistent rules around pronunciation of the English language.
 The vectors are created using lists phonemes from the CMU Pronouncing Dictionary.
-Phonemes are the phonetic elements that construct a word.
-For example the word "RING" translated into the phonemes \verb|/R IH NG/|.
-Using all words available and mapping all phonemes to phonetic features a list of unique features is created per-word.
+Using all words available in the CMU Dictionary and mapping all phonemes to phonetic features produces a list of unique features.
 
@@
 
-\textbf{TODO: } Explain why being vectors is useful and its appliactions
+The ability to perform operations and measure dissimilarity allows for a plethora of applications.
+One possible application of note would be the creation of a wordlist where the phonetic difference (vector distance) is maximized.
+This, if the vector mappings are an accurate representation could allow a creation of a phonetically distinctive wordlist.
+This will be discussed further at a later stage of the report.
 
-\textbf{TODO: } Do a sample conversions table
+\section{Alternative Similarity Metrics}
 
-\subsection{Alternative Similarity Metrics}
-
-\subsubsection{Match Rating Approach}
+\subsection{Match Rating Approach}
 Matching Rating Approach (MRA) is another algorithm designed to match names within a database, therefore, its operation can be grouped with that of NYSIIS and Soundex.
@@
 
-\subsubsection{Caverphone}
+\subsection{Caverphone}
 Another notable alternative solution is that of Caverphone that was designed in New Zealand.
@@
 
-% Other alternatives:
-% - Match Rating Approach
-%   - Couldn't find an algorithm??
-%
-% - Caverphone
-
-\textbf{TODO: } Need to justify why
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{ll}
+        Metric & Output \\
+        \hline    
+        Soundex & T614 \\
+        NYSIIS & TRAVAL\\
+        Metaphone & TRFL\\
+        Caverphone & TRF111\\
+        MRA & TRVL
+    \end{tabular}
+    \caption{The various phonetic encodings of the word "Travel"}
+\end{table}
 
 \section{Design of GreenOnion}
-And the way it works. Need to explain it is based on Scallion but improved with the use of C++ alongside a bloom filter.
+To answer Research Questions \ref{goal:complexity} and \ref{goal:hardwareRequired} fully, it is necessary to implement an actual code base that will be used to generate actual keys.
+
+Inspiration of the design of this tool was taken from a tool called Scallion\footnote{\url{https://github.com/lachesis/scallion}}.
+Scallion was designed by Richard Klafter and Eric Swanson and used to demonstrate that 32-bit PGP key ids were insufficient.
+Keeping with the onion-based theme the proposed tool is known as GreenOnion and is a re-write of the tools structure in C++.
+This language was chosen due to the well understood efficiency benefits.
+The proposed tool differs from Scallion most notably in its ability to concurrently search for a large number of keys, GreenOnion improves on this substantially.
+More implementation and experimental details will be discussed in later chapters.
+
+The tool should take two keys as parameters (Uncontrolled/Controlled) and a chosen similarity metric and produce a list of target keys fingerprints.
+This list is then used as a search criteria when hashing a checking a large number of keys.
+In order to utilise the high parallel nature of the GPU to compute the hash of a large number of keys the tool will utilise a GPGPU (General-purpose computing on graphics processing units) framework.
+The chosen framework was OpenCL due to its support for the chosen language (C++) and platform (Linux).
+OpenCL allows the creation of code chunks refereed to as "kernels" to be executed concurrently, this will provide a massive speed increase compare to the sequential nature of the CPU.
+Technical details will be explained further in Chapter \ref{cha:Implementation}.
+
+\section{Experiment Design}
+In order to answer some of the research questions empirical evidence is required and, thus, experiments are required.
+In this section the designs and considerations of the chosen experiments will be discussed.
+
+\subsection{Metric performance}
+In order to answer Research Question \ref{goal:bestMetrics} and reduce the number of metrics to asses in the later rounds, the performance of similarity metrics required comparison.
+The thinning out of metrics is required due to limited resources, further work could involve repeating this work with a much more varied selection of metrics.
+As explained in a previous section (See Section \ref{sec:metrics}) the chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors.
+
+The design for the experiment involves assessing the quality of the metrics matches by matching them to human perception of similarity.
+
+\subsubsection{Matches}
+A match for each code based metric (Soundex, Metaphone and NYSIIS) is when the codes are identical.
+However, for the other cases where the difference is variable other ways of defining a match are required.
+
+In the case of Levenshtein values of similarity are discrete due to it being the number of single character edits.
+Therefore, this requires less deliberation.
+Match size was used as a way to decide on a cut-off point.
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{ll}
+        Metric & Matches \\
+        \hline
+        Soundex     & 1,527,554 \\
+        Metaphone   & 412,916 \\
+        NYSIIS      & 188,474 \\
+        \hline
+        Levenshtein (Distance 1) [L1] & \textbf{97,730} \\
+        Levenshtein (Distance 2) [L2] & 1,070,656
+    \end{tabular}
+    \caption{Levenshtein number of matches comparison}
+    \label{tab:matchSize}
+\end{table}
+
+As it can be seen from Table \ref{tab:matchSize} the number of matches for L2 is massively larger than all but Soundex.
+As the issues with Soundex have been discussed in previous sections (See Section \ref{sec:soundexIssues}) it can be excluded as an abnormally in this context as it is only included due to its historical significance.
+Therefore, due to the excessively high value for a L2, L1 was chosen as the Levenshtein cap for defining a match.
+
+Match size was also used to define the cap for the phonetic vectors.
+This is less distinct that that of Levenshtein due to the continuous nature of the distance between two vectors, however the complexity was reduced by limiting it to increments of 0.5.
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{ll}
+        Metric & Matches \\
+        \hline
+        Soundex     & 1,527,554 \\
+        Metaphone   & 412,916 \\
+        NYSIIS      & 188,474 \\
+        Levenshtein & 97,730 \\
+        \hline
+        Phonetic Vector (Distance 3.0)  & 14,550 \\
+        Phonetic Vector (Distance 4.0)  & 73,962 \\
+        Phonetic Vector (Distance 4.5)  & \textbf{216,156} \\
+        Phonetic Vector (Distance 5.0)  & 685,516 \\
+    \end{tabular}
+    \caption{Phonetic vector number of matches comparison}
+    \label{tab:vectorMatchSize}
+\end{table}
+
+Table \ref{tab:vectorMatchSize} contains the match size comparison for Phonetic vectors distance.
+Distance 4.5 was chosen as the suitable size due to the total matches fitting well within the other metrics.
+Distance 4.0 was the other alternative, this was discarded due to its small size.
+Any metric with a number of matches below 100,000 results in an inadequate number of possible near-collision keys later in the process, a lower number of matches may imply better quality but a balance is required between computational cost and attack quality.
+This will be discussed in more detail in later chapters.

### 2019-08-01 Thesis/pages/implementation.tex
Changes; - Added a lot of content to the design stage of the report

\chapter{Implementation}
\label{cha:Implementation}

### 2019-08-01 Thesis/pages/design.tex
Changes; - Added more content to the Experimental design section

@@
 In order to answer Research Question \ref{goal:bestMetrics} and reduce the number of metrics to asses in the later rounds, the performance of similarity metrics required comparison.
-The thinning out of metrics is required due to limited resources, further work could involve repeating this work with a much more varied selection of metrics.
+The thinning out of metrics is required due to limited resources and, therefore, possible further work could involve repeating this work with a much more varied selection of metrics.
 As explained in a previous section (See Section \ref{sec:metrics}) the chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors.
 
-The design for the experiment involves assessing the quality of the metrics matches by matching them to human perception of similarity.
+The design for the experiment involves assessing the quality of the metrics matches by having participants rate them on a scale of 1 to 5.
 
 \subsubsection{Matches}
-A match for each code based metric (Soundex, Metaphone and NYSIIS) is when the codes are identical.
+A match for each code based metric (Soundex, Metaphone and NYSIIS) occurs when the codes are identical.
 However, for the other cases where the difference is variable other ways of defining a match are required.
@@
 
-As it can be seen from Table \ref{tab:matchSize} the number of matches for L2 is massively larger than all but Soundex.
-As the issues with Soundex have been discussed in previous sections (See Section \ref{sec:soundexIssues}) it can be excluded as an abnormally in this context as it is only included due to its historical significance.
+As it can be seen from Table \ref{tab:matchSize} the number of matches for L2 is massively larger than all metrics excluding Soundex.
+As the issues with Soundex have been discussed in previous sections (See Section \ref{sec:soundexIssues}) it can be excluded as an abnormality in this context.
 Therefore, due to the excessively high value for a L2, L1 was chosen as the Levenshtein cap for defining a match.
@@
 This will be discussed in more detail in later chapters.
+
+\newpage
+
+\subsubsection{Comparisons}
+Each participant is asked to rate the similarity of a match on a scale of 1 to 5.
+Figure \ref{fig:phoneticMatch} shows an example match and the connected scale.
+Users will complete 5 of these comparisons per metric.
+
+\begin{figure}[h!]
+    \centering
+    \fbox{
+        \includegraphics[scale=0.5]{experiment_match.png}
+    }
+    \caption{Example experiment question}
+    \label{fig:phoneticMatch}
+\end{figure}
+
+The experiment randomizes the order of these comparisons per session alongside a complete refreshing of matches once per submission.
+This makes sure selections from the samples are fair and consistent as each user will have a different selection of matches.
+
+\subsubsection{Quality control}
+As the study was being outsourced to Amazon's Mechanical Turk the requirement to check the quality of results is important. Therefore, a couple of additions were provided to check a result's validity.
+
+The first was the addition of 5 "Random matches" questions.
+These were two random words selected from the dictionary.
+Therefore, the overall rating of these words should be close to an average of 1.
+This allows a simple check to see if the user is providing valid results.
+If their average is too high, the results will also be discarded.
+
+\begin{figure}[h!]
+    \centering
+    \fbox{
+        \includegraphics[scale=0.5]{exact_experiment_match.png}
+    }
+    \caption{Exact experiment attention question}
+    \label{fig:exactMatch}
+\end{figure}
+
+Alongside this, was the addition of two questions comparing exactly the same word.
+As both words are the same the result should always be a full 5/5 rating, any results without a full rating will be discarded.
+Figure \ref{fig:exactMatch} contains one example of the attention questions used to filter inaccurate results.
+
+The final check to ensure the validity of results is a check for native 
+English fluency. Having non-native English speakers complete the 
+experiment has the possibility to introduce inconsistencies into the 
+data and, therefore, needs to remain controlled. To achieve this a 
+preliminary MTurk study will be run to ask users for their perceived 
+English fluency on a scale of 1 (Basic Understanding) to 5 (Native). 
+Workers with an answer of 5 will be provided with a 
+Qualification\footnote{\url{https://blog.mturk.com/tutorial-understanding-requirements-and-qualifications-99a26069fba2}} 
+that tags them as defining themselves as native speakers. This is then 
+added as a prerequisite when running the experiment. This will insure 
+only fully native speakers are being assessed. The possibility of the 
+worker falsy stating their level of fluency has also been considered. 
+However, as the worker does not know the purpose for this initial study,
+thereby providing inaccurate results has no real valid motive for the 
+worker.
+
+\subsubsection{Statistical}
+\textbf{TODO}
+
+\newpage
+
+\subsection{Trustword Attacks}
+
+The final experiment required to answer the Research Question \ref{goal:attackPercentage} will simulate attacks on participants.
+The user will be presented with the same design as presented in the \pep Android application (See Section \ref{sec:pep}).
+
+\begin{figure}[h!]
+    \centering
+    \fbox{
+        \includegraphics[width=\textwidth]{experiment/trustword_attack.png}
+    }
+    \caption{Experiment UI}
+    \label{fig:expID}
+\end{figure}
+
+Figure \ref{fig:expID} shows the design of the experiments front end.
+As can be seen by comparing it to Figure \ref{fig:trustwords} it has been designed to be a close as possible to the actual application.
+Users will click the blue button to simulate the authentication ceremony over the phone.
+A text-to-speech system will then read a set of words and the user should accept if they match and decline if they don't.
+
+\subsubsection{Design}
+
+Due to the scarcity of attacks in a real-world setting users will are often complacent about their occurrence.
+Therefore, in this experiment attacks only occur 30\% of the time.
+This is a much higher value than in a real-world setting, but it is a balance between resources and realistic design.
+Alongside, this the first 5 trials of a new experiment will always be benign.
+This is to ensure users are lulled into a level of complacency regarding the possibility for an attack.
+
+Certain keys have higher levels of near-collision possibilities than others due to how certain words are deemed similar by the chosen metric.
+Therefore, this presents the possibility to have keys with a very low number of similar matches.
+The distribution of these keys will be explained further in Chapter \ref{cha:Experiments}.
+Therefore, if random sets of words were chosen with no restraints there are attacks presented to the user that in a real setting would be infeasible in this context as they are close to a $2^{64}$ attack (4 Words * 16-bits).
+Therefore, the experiment will sample from a list of "vulnerable" keys.
+These are keys that have a number of combinations that allow an attack in a certain timeframe.
+Furthermore, certain levels of attacks are also simulated.
+Below are the list of possible attacks:
+
+\begin{itemize}
+    \item \textbf{Zero static words} - All words in the set can vary.
+    \item \textbf{One static word} - All but the first word can vary.
+    \item \textbf{Two static words} - All but the first and last word can vary.
+\end{itemize}
+
+These attacks are ascending in complexity.
+The timeframe for finding a match was decided as 7-days on with attack strengths of 1 GPU/day, 10 GPU/days and 100 GPU/days on a mid range GPU (AMD RX 480 was the example in experiments).
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{lll}
+        GPU/days & No of combinations required & Attack Type \\
+        \hline
+        1       & 15250   & Zero static\\
+        10      & 1525    & One static\\
+        100     & 152     & Two static\\        
+    \end{tabular}
+    \caption{Summary of attack requirements}
+    \label{tab:attackReq}
+\end{table}
+
+Table \ref{tab:attackReq} contains a summary of the different level of attacks and their respective restrictions. More combinations makes the attack search quicker as there are more possibilities.
+
+Any key that exceeds this criteria is deemed as vulnerable is one of the three attack contexts.
+A list of these vulnerable keys are sampled from when an attack is simulated.
+The percentage of vulnerable keys will be explored in Chapter \ref{cha:Experiments}.
+
+\subsubsection{Quality control}
+\textbf{TODO}
+
+\subsubsection{Statistical}
+\textbf{TODO}

### 2019-08-01 Thesis/pages/lit_review.tex
Changes; - Added more content to the Experimental design section

@@
 \subsubsection{Pretty Easy Privacy}
+\label{sec:pep}
 A very recent implementation of a word list can be found in Pretty Easy Privacy (\pep) implementation of TrustWords\footnote{https://tools.ietf.org/html/draft-birk-pep-trustwords-03}.

### 2019-08-01 Thesis/pages/design.tex
Changes; - More progress in the design section

@@
 
+\textbf{TODO: } Explain why the attacks are designed like this. Use heatmap study as justification as why the ends are prioritised.
+
 These attacks are ascending in complexity.
@@
 \subsubsection{Quality control}
-\textbf{TODO}
+As the previous experiment, participants will be sourced from MTurk.
+Therefore, again, quality control is and aspect that requires consideration.
+As with the previous study, initially screened native speakers will be used.
+The same process will be performed to recruit suitable workers.
+Two metrics will be used to detect invalid results.
+Audio button clicks and overall time taken.
+
+Audio buttons clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:expID}.
+If there are rounds without button clicks, this is a sign of non-attentive users.
+The design choice was made to keep this as a result filter, as preventing non-clicks would be a trivial task.
+This provides a way to detect and discard click-throughs\footnote{Workers that aim to complete the task as fast as possible, with no regard for the quality of responses}.
+
+Overall time taken is as the name suggest a recording of the time taken to complete the entire experiment.
+If users complete the experiment in an abnormally small amount of time it can be used as another detection for invalid responses.
+Anything below a certain threshold will be discarded.
 

### 2019-08-02 Thesis/pages/design.tex
Changes; - Small changes made to the main experiment - Updated lists of vuln keys - Added more content to the thesis

@@
 
-Near-collision keys are keys that are deemed a match by the phonetic similar metric (More on this aspect in the following sections).
+Near-collision keys are keys that are deemed a match by the phonetic similarity metric (More on this aspect in the following sections).
 A similarity metric is an algorithm designed to determine if two words are phonetically a match.
-For example, the words "THEIR" and "THERE" will be phonetically be a match whereas the words "DARK" and "PRINCIPLE" are not phonetically matching.
+For example, the words "THEIR" and "THERE" will be a match whereas the words "DARK" and "PRINCIPLE" are not phonetically matching.
 
-As each combined key in Trustwords is an exclusive-or of both sides public key (Figure \ref{fig:xor_trustwords} shows this process) the attack is target to a single pair of users and will require recomputation for every attack instance, this will be considered when discussing the attack feasibility.
+As each combined key in Trustwords is an exclusive-or of both sides public key (Figure \ref{fig:xor_trustwords} shows this process) the attack is target to a single pair of users and will require recomputation for every attack target.
+This will be considered when discussing the attack feasibility.
 Each pair is also split into a "Uncontrolled" and "Controlled" key.
@@
 Further work would involve the implementation of newer versions of Metaphone.
-Double Metaphone (2000) and Metaphone 3 (2009) claim to improve over the original version due to further research performed by Philips.
-The original version was chosen due to its historical widespread usage.
+Double Metaphone (2000) and Metaphone 3 (2009) that claim to improve over the original version due to further research performed by Philips.
+The original version was chosen due to its historical and widespread usage.
 
@@
 For example the word "RING" translated into the phonemes \verb|/R IH NG/|.
+
 Extensive prior work has gone into producing models of features that map to phonemes.
@@
 Features, therefore, are an attempt at mapping the varying and inconsistent rules around pronunciation of the English language.
-The vectors are created using lists phonemes from the CMU Pronouncing Dictionary.
-Using all words available in the CMU Dictionary and mapping all phonemes to phonetic features produces a list of unique features.
+The vectors were created using lists phonemes from the CMU Pronouncing Dictionary and mapping them to possible features.
 
@@
 This allows a simple check to see if the user is providing valid results.
-If their average is too high, the results will also be discarded.
+If their average is too high, the results will be discarded.
 
@@
 
-\textbf{TODO: } Explain why the attacks are designed like this. Use heatmap study as justification as why the ends are prioritised.
+The start and ends were chosen as the highest priority words to keep static.
+This is due to research highlighting on the common habit of users to only check the start and end of a checksum.
+\cite{cherubini2018towards} shows this by measuring user eye movement and displaying it as a heat map.
+
+\begin{figure}[h!]
+    \centering
+    \fbox{
+        \parbox{\textwidth}{
+            \includegraphics[width=\textwidth]{checksum_check.png}
+
+            \includegraphics[width=\textwidth]{checksum_check_2.png}
+        }
+    }
+    \caption{Failed verification of an incorrect checksum\cite{cherubini2018towards}}
+    \label{fig:heatMap}
+\end{figure}
+
+Figure \ref{fig:heatMap} shows the results of a eye tracking experiment where the user failed to detect a mismatching digest.
+As it can be clearly seen the users never compared the center of the digest.
+
+However, this may not be applicable in this context due to the user being linearly fed an audio stream that they cannot skip to the start or end.
+However, we believe that attention will also play a part in defining the most important areas of comparison as the hypothesis is that the users attention will be lower in the middle sections of comparison where it peak at the start and end.
+All these aspects, however, will require empirical evidence to arrive at a conclusion.
+Therefore, this consideration will need to be made when assessing the results of the experiment.
 

### 2019-08-02 Thesis/pages/implementation.tex
Changes; - Small changes made to the main experiment - Updated lists of vuln keys - Added more content to the thesis

@@
 \label{cha:Implementation}
+
+\textbf{TODO: } Talk here about the interesting and challenges that were overcome
+
+\section{GreenOnion}
+Talk about the way a key is expanded and turned into a lot
+of work for the kernel
+
+\section{First Experiment}
+Explain how Google App Script was used?
+
+\section{MainExperiment}
+Design of the application etc

### 2019-08-02 Thesis/pages/lit_review.tex
Changes; - Small changes made to the main experiment - Updated lists of vuln keys - Added more content to the thesis

@@
-\chapter{Literature Review}
+\chapter{Background}
 \label{cha:LiteratureReview}
@@
 
-\section{Public-key Cryptography and Key Exchange}
+The chapter will contain the following sections:
+
+\begin{itemize}
+    \item \textbf{Project context} \\ 
+    Will provide the user with the base knowledge required to understand the context and purpose of the following literature review.
+
+    \item \textbf{Definition of terms}\\
+    Specific definitions relevant to the literature review will initially be defined.
+
+    \item \textbf{Literature Review} \\
+    A review of currently available literature on relevant topics. Recommendations and research gaps will be identified and discussed.
+
+\end{itemize}
+
+\section{Project context}
+
+\subsection*{Public-key Cryptography and Key Exchange}
+
+To fully understand the literature review it is necessary to introduce and explain the base knowledge before continuing.
+
 Asymmetric cryptography facilitates the secure encryption of messages in end-to-end encryption (E2EE), verification of digital signatures and sharing of pre-communication secrets, among others.
@@
 
-\section*{Definition of terms}
+\section{Definition of terms}
 Throughout the paper, various terms are used to define elements of the authentication ceremony relevant to fingerprints verification.
@@
 
-\section{Authentication ceremony performance}
+\section{Literature Review}
+This section will now discuss the current research around the proposed topic.
 
-\section*{Encoding scheme performance}
+The section is organized as follows:
+
+\begin{itemize}
+    \item \textbf{Authentication ceremony performance} \\
+    This section explains the current research on performance of various encoding schemes and methods of comparison.
+This is then complemented with an assessment of the experimentation design for the respective studies.
+
+    \item \textbf{Encoding schemes} \\
+    The following section then discusses research around the design of an encoding scheme.
+Focus in this section will be allocated to the technical details around the creation and design of relevant schemes.
+
+    \item \textbf{Attacks on encoding schemes} \\
+    The final section will then discuss literature that investigates the creation of attacks against encoding schemes in order to deceive the respective users.
+\end{itemize}
+
+\subsection{Authentication ceremony performance}
+
+\subsubsection*{Encoding scheme performance}
 Results 
@@
 
-\section*{Methods of comparison performance}
+\subsubsection*{Methods of comparison performance}
 Aside 
@@
 
-\section*{Experimentation methodology comparison}
+\subsubsection*{Experimentation methodology comparison}
 To further look into the validity of previously discussed results, it is necessary to asses how the respective studies reached these conclusions.
@@
 
-%TODO: Maybe talk about the effect of visual or mental impairments 
-\subsection{Topic conclusion}
+\subsubsection*{Topic conclusion}
 Overall, this review has identified several key areas suitable for further work.
@@
 
-\section{Encoding schemes}
+\subsection{Encoding schemes}
 Another area of research is investigations into the actual physical encodings of the hash digest.
@@
 
-\subsubsection{Pretty Easy Privacy}
+\subsubsection*{Pretty Easy Privacy}
 \label{sec:pep}
@@
 
-\subsection{Topic conclusion}
+\subsubsection*{Topic conclusion}
 
@@
 
-\section{Attacks on encoding schemes}
+\subsection{Attacks on encoding schemes}
 This area of research studies ways to physically execute attacks on fingerprint encoding schemes.
@@
 
-\subsection{Topic Conclusion}
+\subsubsection*{Topic Conclusion}
 Overall the literature for this subtopic remains sparse and incomplete.

### 2019-08-02 Code/TrustwordUtil/calculate_perms.sh

@@ -3,8 +3,7 @@
 set -e
 
 # declare -a metricArr=("soundex" "leven" "metaphone" "nysiis" "wordvec_4_5")
-declare -a metricArr=("wordvec_4")
-
+declare -a metricArr=("leven" "metaphone" "nysiis")
 
 # declare -a permsArr=("1000" "10000" "100000") # 1 day
 # declare -a permsArr=("500" "5000" "50000") # 2 days
@@ -26,8 +25,8 @@ do
         do
             echo $simMetric-$staticWords
     
-            mkdir -p ./vuln_keys/$simMetric
-            mkdir -p ./vuln_keys/$simMetric/$simMetric-$perm
+            mkdir -q ./vuln_keys/$simMetric
+            mkdir -q ./vuln_keys/$simMetric/$simMetric-$perm
 
             python trustwords_util.py --vuln-keys avergae_perms/realWorldAverage/100000_pairs.txt $perm $staticWords -s ../../SimilarLists/$simMetric.csv > ./vuln_keys/$simMetric/$simMetric-$perm/$simMetric-static-$staticWords.txt
 

### 2019-08-02 Experiments/MainExperiment/website/backend/CONFIG.py

@@ -1,11 +1,11 @@
 BASE_FILE_LOCATION = "" #B700
 ATTACK_CHANCE = 0.3
-NUMBER_OF_ROUNDS = 15
-GRACE_ROUNDS = 5 # Number of initial rounds that can't contain an attack
+NUMBER_OF_ROUNDS = 10
+GRACE_ROUNDS = 0 # Number of initial rounds that can't contain an attack
 
 ## NOTE:
 #   Naming convension for files is:
 #
 #       ./data/similar/<lower_case_name>.csv
 #
-ATTACK_METRICS = ['SOUNDEX', "METAPHONE", "NYSIIS"]
+ATTACK_METRICS = ['LEVEN', "METAPHONE", "NYSIIS"]

### 2019-08-02 Experiments/MainExperiment/website/backend/data/vuln_keys/get_files.sh

@@ -1,14 +1,15 @@
 set -e
 
-declare -a metricArr=("metaphone" "soundex" "nysiis")
+declare -a metricArr=("metaphone" "leven" "nysiis")
+declare -a permsArr=("152" "1525" "15250") # 1 week
 
 for i in "${metricArr[@]}"
 do
     rm -fr $i
     mkdir $i
 
-    cp ../../trustwords_util/vuln_keys/$i/$i-1000/$i-static-2.txt  ./$i
-    cp ../../trustwords_util/vuln_keys/$i/$i-10000/$i-static-1.txt  ./$i
-    cp ../../trustwords_util/vuln_keys/$i/$i-100000/$i-static-0.txt  ./$i
+    cp ../../../../../../Code/TrustwordUtil/vuln_keys/$i/$i-152/$i-static-2.txt  ./$i
+    cp ../../../../../../Code/TrustwordUtil/vuln_keys/$i/$i-1525/$i-static-1.txt  ./$i
+    cp ../../../../../../Code/TrustwordUtil/vuln_keys/$i/$i-15250/$i-static-0.txt  ./$i
 
 done

### 2019-08-02 Experiments/MainExperiment/website/backend/experiment.py

@@ -57,6 +57,9 @@ class Experiment:
     def is_attack(self):
         return self.AttackSchema[-1]
 
+    def check_if_round_started(self):
+        return len(self.VisualWords) == len(self.RoundStartTimes)
+
     def num_of_rounds(self):
         return len(self.Responses)
 

### 2019-08-02 Experiments/MainExperiment/website/backend/results/gen_report.py

@@ -1,0 +1,81 @@
+import os
+import pickle
+import sys; sys.path.insert(0, "..")
+import experiment
+
+def usage():
+    print(f"Usage: python {__name__} <OUTPUT_FILE_NAME>")
+    exit()
+
+# Printing out FP
+def red_text(t):
+    return f"\033[1;0;41m{t}\33[0m"
+
+# Printing out FN
+def blue_text(t):
+    return f"\033[1;0;44m{t}\33[0m"
+
+def findSuccessfulAttacks(exp):
+
+
+    attacks = []
+    for i, e in enumerate(exp.Responses):
+
+        # Counts errors in the experiment
+        if exp.AttackSchema[i] != None and e == "True":
+            attacks.append("\t" + str(exp.AttackSchema[i]))
+
+    return attacks
+
+def checkAudioClicks(exp):
+
+    missedCount = 0
+    for i, e in enumerate(exp.AudioButtonClicks):
+        if int(e) == 0:
+            missedCount += 1
+
+    if missedCount > 5:
+        return True
+    else:
+        return False
+
+if __name__ == "__main__":
+
+    if len(sys.argv) != 2:
+        usage()
+
+    outputFileName = sys.argv[1]
+
+    for file in os.listdir("."):
+        if file.endswith(".pkl"):
+
+            exp = pickle.load(open(file, "rb"))
+            print(f"-------------------- {file} --------------------")
+
+            if checkAudioClicks(exp):
+                print("#####################################")
+                print("!! Possible click-through detected !!")
+                print("#####################################")
+                print()
+
+            # User-agent
+            print("## User-agent ##: \n")
+            print("\t", exp.UserAgent)
+            print()
+
+            # Successfull attacks
+            attacks = findSuccessfulAttacks(exp)
+
+            if len(attacks) > 1:
+                print("## Successfull attacks ##:\n")
+                for a in attacks:
+                    print(a)
+            else:
+                print("## No attacks ##\n")
+                
+
+            print("\n\n")
+
+
+            # os.system(f"echo -------------------- {file} -------------------- >> {outputFileName}")
+            # os.system(f"python3 print_data.py {file} 2>&1 | tee -a {outputFileName}")

### 2019-08-02 Experiments/MainExperiment/website/backend/server.py

@@ -93,8 +93,10 @@ def get_words():
                 return "DONE"
 
             exp = Experiment.from_json(session[exp_id])
-            exp.record_round_start_time()
-            session[exp_id] = exp.to_json()
+
+            if not exp.check_if_round_started():
+                exp.record_round_start_time()
+                session[exp_id] = exp.to_json()
 
             return "  ".join(Experiment.from_json(session[exp_id]).get_current_wordlist())
 

### 2019-08-02 Experiments/PilotStudy/MTurk/give_quali.py

@@ -1,78 +1,0 @@
-import sys
-
-"""
-Script that edits MTurk .csv files depending on the result from the study
-"""
-
-
-def load(filePath):
-
-    data = []
-    newData = []
-    with open(filePath) as file:
-        data = file.readlines()
-
-    newData.append(data[0].strip().split(","))
-    headerLength = len(newData[0])
-
-    for d in data[1:]:
-        d = d.replace("\n", "")
-        temp = d.split(",")
-
-        while len(temp) < headerLength:
-            temp.append("")
-
-        newData.append(temp)
-
-    return newData
-
-def save(filePath, data):
-
-    with open(filePath, "w") as file:
-
-        for d in data:
-            file.write(",".join(d) + "\n")
-
-def usage():
-    print(f"Usage: ./{__name__} <MAIN_WORKER_FILE> <HIT_WORKER_FILE>")
-    exit()
-
-
-if __name__ == "__main__":
-    
-    if len(sys.argv) != 3:
-        usage()
-
-    mainWorkerFilePath = sys.argv[1]
-    hitWorkerFilePath = sys.argv[2]
-
-    mainWorkerData = load(mainWorkerFilePath)
-    hitWorkerData = load(hitWorkerFilePath)
-
-    qualiHeaderPosition = mainWorkerData[0].index("\"UPDATE-English Fluency\"")
-
-    answerPosition = hitWorkerData[0].index('\"Answer.howMuch\"') + 1
-    workerIdPosition = hitWorkerData[0].index('\"WorkerId\"') + 1
-    approveHeaderPosition = hitWorkerData[0].index("\"Approve\"") + 1
-
-    for hit in hitWorkerData[1:]:
-        workerID = hit[workerIdPosition]
-
-        mainFileWorkerIDIndex = None
-        for i, m in enumerate(mainWorkerData[1:]):
-            if m[0] == workerID:
-                mainFileWorkerIDIndex = i + 1
-
-                if hit[answerPosition] == '\"5\"':
-                    mainWorkerData[mainFileWorkerIDIndex][qualiHeaderPosition] = '1'
-                    hit[approveHeaderPosition] = "x"
-                break
-
-        else:
-            # raise Exception("Error: Worker ID not found!")
-            print(f"[!] Worker: {workerID} not found!")
-            pass
-
-    save("User.csv", mainWorkerData)
-    save("Batch.csv", hitWorkerData)
-            

### 2019-08-03 Experiments/MTurk/MTurk.py
Changes; - Small changes to utility scripts - Added results from first round the MainExperiment

@@ -1,0 +1,22 @@
+import csv
+
+def load(filePath):
+
+    data = []
+    with open(filePath) as csvDataFile:
+        csvReader = csv.reader(csvDataFile)
+        for row in csvReader:
+            data.append(row)
+
+    return data
+
+def save(filePath, data):
+
+    with open(filePath, "w") as file:
+
+        for d in data:
+            file.write(",".join(d) + "\n")
+
+def usage():
+    print(f"Usage: ./{__name__} <MAIN_WORKER_FILE> <HIT_WORKER_FILE>")
+    exit()

### 2019-08-03 Experiments/MTurk/give_quali.py

@@ -1,42 +1,10 @@
 import sys
 
+from MTurk import *
+
 """
 Script that edits MTurk .csv files depending on the result from the study
 """
-
-
-def load(filePath):
-
-    data = []
-    newData = []
-    with open(filePath) as file:
-        data = file.readlines()
-
-    newData.append(data[0].strip().split(","))
-    headerLength = len(newData[0])
-
-    for d in data[1:]:
-        d = d.replace("\n", "")
-        temp = d.split(",")
-
-        while len(temp) < headerLength:
-            temp.append("")
-
-        newData.append(temp)
-
-    return newData
-
-def save(filePath, data):
-
-    with open(filePath, "w") as file:
-
-        for d in data:
-            file.write(",".join(d) + "\n")
-
-def usage():
-    print(f"Usage: ./{__name__} <MAIN_WORKER_FILE> <HIT_WORKER_FILE>")
-    exit()
-
 
 if __name__ == "__main__":
     

### 2019-08-03 Experiments/MTurk/trustword_quali.py

@@ -1,0 +1,35 @@
+from MTurk import *
+import sys
+
+if __name__ == "__main__":
+    
+    if len(sys.argv) != 3:
+        usage()
+
+    mainWorkerData = load(sys.argv[1])
+    hitWorkerData = load(sys.argv[2])
+    print(len(hitWorkerData))
+
+    qualiHeaderPosition = mainWorkerData[0].index('UPDATE-Trustwords')
+
+    workerIdPosition = hitWorkerData[0].index('WorkerId')
+
+    for hit in hitWorkerData[1:]:
+        workerID = hit[workerIdPosition]
+
+        for i, m in enumerate(mainWorkerData[1:]):
+            if m[0] == workerID:
+
+                mainWorkerData[i + 1][qualiHeaderPosition] = '1'
+                break
+
+        else:
+            # raise Exception("Error: Worker ID not found!")
+            print(f"[!] Worker: {workerID} not found!")
+            pass
+            
+    save("User.csv", mainWorkerData)
+    save("Batch.csv", hitWorkerData)
+
+
+

### 2019-08-03 Experiments/MainExperiment/website/backend/results/check_for_clicks_throughs.py

@@ -1,0 +1,27 @@
+import os
+import sys
+import pickle
+
+sys.path.append("..")
+
+trick_attacks = {}
+all_attacks = {}
+
+def checkAudioClicks(exp):
+
+    missedCount = 0
+    for i, e in enumerate(exp.AudioButtonClicks):
+        if int(e) == 0:
+            missedCount += 1
+
+    return missedCount
+
+for file in os.listdir("."):
+    if file.endswith(".pkl"):
+        
+        exp = pickle.load(open(file, "rb"))
+
+        missedCount = checkAudioClicks(exp)
+
+        if missedCount > 2:
+            print(f"[!] {file} Has rounds with no AudioButtons clicks: {missedCount} ")

### 2019-08-03 Experiments/MainExperiment/website/backend/results/check_for_roundtime_issue.py

@@ -1,0 +1,16 @@
+import os
+import sys
+import pickle
+
+sys.path.append("..")
+
+trick_attacks = {}
+all_attacks = {}
+
+for file in os.listdir("."):
+    if file.endswith(".pkl"):
+        
+        exp = pickle.load(open(file, "rb"))
+
+        if len(exp.RoundStartTimes) != len(exp.RoundEndTimes):
+            print(f"[!] {file} has issues with Round times!")

### 2019-08-03 Experiments/MainExperiment/website/backend/results/overall_results.py

@@ -29,7 +29,7 @@ for file in os.listdir("."):
                         trick_attacks[attack_id] = 1
                     else:
                         trick_attacks[attack_id] += 1
-                
+
 print("[*] Successful attacks (%): ")
 for attackID in trick_attacks:
-    print("\t", attackID, round(trick_attacks[attackID] / all_attacks[attackID], 2))
+    print("\t", attackID, round(trick_attacks[attackID] / all_attacks[attackID] * 100, 2))

### 2019-08-05 Thesis/pages/design.tex
Changes; - Added implementation details - Added some results write ups for the first experiment

@@
 \section{Design of GreenOnion}
+\label{sec:greenDesign}
 To answer Research Questions \ref{goal:complexity} and \ref{goal:hardwareRequired} fully, it is necessary to implement an actual code base that will be used to generate actual keys.
@@
 \subsection{Metric performance}
+\label{exp:metric}
 In order to answer Research Question \ref{goal:bestMetrics} and reduce the number of metrics to asses in the later rounds, the performance of similarity metrics required comparison.
@@
 
+\subsubsection{Considerations}
+This section will discuss the considerations required when interpreting the results of the study.
+
+The first consideration is the way the words are compared.
+Due to the channel of authentication being phone based the comparison of words will be a mixture of auditory and textual.
+This is because a user needs to match a words sound to the one displayed on their device.
+In the case of this experiment the users are asked to compare the sound of two word that are visually displayed to them.
+Therefore, this experiment does not fully capture the targeted scenario.
+This was decided partly to aforementioned lack of resources.
+The main design of the experiment was to provide a simple way to cull the large number of metrics.
+The initial choice of five metrics discussed in Section \ref{sec:metrics} was to be followed by a more empirical decision.
+Further work, therefore, could improve by producing more conclusive results on the performance of the metrics.
+
+Another consideration is the demographics of people accessible on Mechanical Turk.
+A comprehensive and still active survey run by D Difallah \textit{et al.} \cite{difallah2018demographics} shows that MTurk workers are younger and have a larger household income than that of the US population.
+This has to be taken into consideration when interpreting the results because it will inherently introduce a bias.
+This is due to the assumptions that an increase in age provides a better understanding of more obscure words, and, therefore, a better representation of the metrics performance over the entire dictionary.
+
 \newpage
@@
 \textbf{TODO}
+
+\subsubsection{Considerations}
+\textbf{TODO}
+
+Demographics of MTurk workers (Discussed in the previous section)

### 2019-08-05 Thesis/pages/experiments.tex
Changes; - Small changes made to the main experiment - Updated lists of vuln keys - Added more content to the thesis
Changes; - Added implementation details - Added some results write ups for the first experiment

@@
 
-\section{Experiment 1}
-% Methodology
-% Demographic
+\section{Metric Performance - Results}
+As discussed in Section \ref{exp:metric} the goal of the experiment was the cull the number of metrics to be assessed in the following experiment.
+This section will discuss the demographics of participants alongside the subsequent results
+
+\begin{table}[h!]
+    \centering
+    \begin{tabular}{|l|ll|}
+        \hline
+        Gender & Male: & 46.2\% \\
+               & Female: & 53.8\% \\
+        \hline
+        Age:   & 18-24: & 10.6\% \\ 
+               & 25-29: & 20.2\% \\ 
+               & 30-39: & 30.8\% \\ 
+               & 40-49: & 22.1\% \\ 
+               & 50-59: & 11.5\% \\ 
+               & 60-69: & 3.8\% \\ 
+               & 70-79: & 1.0\% \\
+
+        \hline
+        Highest Education:  & Bachelor's degree:    & 51.0\% \\
+                            & A-Level/O-Level:      & 18.3\% \\
+                            & GCSE:                 & 15.4\%  \\
+                            & Master's degree:      & 13.5\% \\ 
+                            & PhD:                  & 1.9\% \\
+        \hline
+
+    \end{tabular}
+    \caption{Participant demographics}
+    \label{tab:exp1_demo}
+\end{table}
+\textbf{TODO: } Create some graphs off this data and put them in the appendix.
+
+\begin{wrapfigure}{l}{6cm}
+    \centering
+    \begin{tabular}{|l|l|}
+        \hline
+        Metric & Average Rating \\
+        \hline
+        Leven     & 3.66 \\
+        NYSIIS    & 2.92 \\
+        Metaphone & 2.56 \\
+        Phonetic Vec & 2.50 \\
+        Soundex & 2.08 \\
+        \hline
+        Random  & 1.16 \\
+        \hline
+    \end{tabular}
+    \caption{Average metric performance}
+    \label{tab:exp1_results}
+\end{wrapfigure}
+
+Table \ref{tab:exp1_demo} contains the geographical breakdown of the participants assessed.
+As it can be seen over 60\% of participants can be considered highly educated (Bachelor’s and up).
+This is not fully reflective of the general population and therefore, has to be considered when interpreting the results.
+All participants were sourced from the US, this again requires consideration due to the large range of dialects present, that may bias the results.
+Further work could investigate the affect of location on these results.
+
+Figure \ref{tab:exp1_results} shows the average results for the metrics
+
+% 22 Missed values
+
 % Results
@@
 % Results
+
+\section{Distribution of keys permutations (Vuln-keys)}

### 2019-08-05 Thesis/pages/implementation.tex
Changes; - Added implementation details - Added some results write ups for the first experiment

@@
 \section{GreenOnion}
-Talk about the way a key is expanded and turned into a lot
-of work for the kernel
+
+\subsubsection{General design}
+This section will discuss the overall technical implementation of GreenOnion alongside a deeper discussion into the unique aspect of the tool.
+
+The tool starts by generating a 2048-bit RSA key through GPG\footnote{GNU Privacy Guard}.
+This key is then used to create a hash of all but the final block of the key.
+The final block of the key is left un-hashed due to the presence of the exponent ($e$).
+This exponent is incremented by one to provide a new key.
+This is the aspect provides rapid generation of unique key as work for the GPU.
+This prevents issues in such as entropy starvation when generating a large number of valid RSA keys.
+This produces valid keys but with abnormally large exponents, this was deemed as suitable due to the short term use-case for these keys.
+3 bytes are used to represent the exponent giving the potential to create $2^{24} - 1$ extra keys for one expensive key generation.
+
+All keys plus the intermediate hash are loaded on the GPU via an OpenCL kernel.
+This kernel is designed with hashing the final block, obtaining the final fingerprint and checking if the fingerprint is present in the provided list.
+
+\subsubsection{Bloom filter}
+
+Mass checking of fingerprints is the tools main functionality as it allows for millions of keys to be checked with a very small amount of overhead.
+This is achieved through the use of a bloom filter.
+A bloom filter is a probabilistic data structure that allows efficient checking for present of an element in a set.
+It is effectively a very large array of booleans that state wether an element is present.
+A position in the array is decided by a hashing algorithm.
+This is repeated a number of times with a number of hashing algorithms ($k$) to populate the array of length ($m$).
+This then means checking the presence of an element in the set will just mean hashing the target and checking the elements returned.
+This data structure therefore has a complexity of $O(k)$ regardless of the number of elements in the set.
+
+However, due to the random distribution of the hashing algorithms commonly there is the possibility for collisions and, thus, the possibility of false-positives.
+The data structure also does not produce any false-negatives.
+This is fully suited to this use-case as any fingerprints tagged as ``possibility'' being present in the bloom filter can be followed up with a more expensive hash-table check to determine the actual presence.
+Therefore, if the levels of false-positives are controlled (by altering $k$ and $m$) the tool can search through huge number of potential keys without any decrease in speed.
+
+\begin{figure}[h!]
+    \centering
+    \input{diagrams/bloom_filter.tex}
+    \caption{Bloom filter example}
+    \label{fig:bloom}
+\end{figure}
+
+Figure \ref{fig:bloom} shows the operation of a simple bloom filter.
+As it can be seen the element $n$ definitely does not exist in the set due to both array indices not being set.
+The performance boost when comparing large numbers of keys is substantial when compared to the similar tool Scallion mentioned in Section \ref{sec:greenDesign}.
+The results from the comparison will be quantified in Chapter \ref{cha:Experiments}.
 

### 2019-08-05 Experiments/MTurk/trustword_quali.py
Changes; - Added results for the 2nd round of experimentation

@@ -8,7 +8,6 @@ if __name__ == "__main__":
 
     mainWorkerData = load(sys.argv[1])
     hitWorkerData = load(sys.argv[2])
-    print(len(hitWorkerData))
 
     qualiHeaderPosition = mainWorkerData[0].index('UPDATE-Trustwords')
 

### 2019-08-05 Experiments/MainExperiment/website/backend/results/overall_results.py

@@ -7,29 +7,43 @@ sys.path.append("..")
 trick_attacks = {}
 all_attacks = {}
 
-for file in os.listdir("."):
-    if file.endswith(".pkl"):
-        
-        exp = pickle.load(open(file, "rb"))
+def usage():
+    print(f"Usage: python {__name__} <TARGET_DIR>")
+    exit()
 
-        for i, attack in enumerate(exp.AttackSchema):
-            if attack:
 
-                attack_id = f"{attack[0]}-{attack[1]}"
+if __name__ == "__main__":
+    
+    if len(sys.argv) != 2:
+        usage()
 
-                if not attack_id in all_attacks:
-                    all_attacks[attack_id] = 1
-                else:
-                    all_attacks[attack_id] += 1
+    target_dir = sys.argv[1]
 
-                # Checks if verified
-                if exp.Responses[i] == "True":
-                    
-                    if not attack_id in trick_attacks:
-                        trick_attacks[attack_id] = 1
+    for file in os.listdir(f"{target_dir}"):
+        if file.endswith(".pkl"):
+            
+            filepath = target_dir + file
+
+            exp = pickle.load(open(filepath, "rb"))
+
+            for i, attack in enumerate(exp.AttackSchema):
+                if attack:
+
+                    attack_id = f"{attack[0]}-{attack[1]}"
+
+                    if not attack_id in all_attacks:
+                        all_attacks[attack_id] = 1
                     else:
-                        trick_attacks[attack_id] += 1
+                        all_attacks[attack_id] += 1
 
-print("[*] Successful attacks (%): ")
-for attackID in trick_attacks:
-    print("\t", attackID, round(trick_attacks[attackID] / all_attacks[attackID] * 100, 2))
+                    # Checks if verified
+                    if exp.Responses[i] == "True":
+                        
+                        if not attack_id in trick_attacks:
+                            trick_attacks[attack_id] = 1
+                        else:
+                            trick_attacks[attack_id] += 1
+
+    print("[*] Successful attacks (%): ")
+    for attackID in trick_attacks:
+        print("\t", attackID, round(trick_attacks[attackID] / all_attacks[attackID] * 100, 2))

### 2019-08-06 Thesis/diagrams/graphs/experiment_one/graph.tex
Changes; - Added graphs for firstexperiment results - More content added to thesis

\begin{figure}[!h]
  \minipage{0.5\textwidth}
    \input{diagrams/graphs/experiment_one/soundex.tex}
    \caption{Soundex}
  \endminipage
  \minipage{0.5\textwidth}
    \input{diagrams/graphs/experiment_one/leven.tex}
    \caption{Levenshtein}
  \endminipage
  \\
  \minipage{0.5\textwidth}
    \input{diagrams/graphs/experiment_one/nysiis.tex}
    \caption{NYSIIS}
  \endminipage
  \minipage{0.5\textwidth}
    \input{diagrams/graphs/experiment_one/metaphone.tex}
    \caption{Metaphone}
  \endminipage
  \\
  \centering
  \minipage{0.5\textwidth}
    \input{diagrams/graphs/experiment_one/wordvec.tex}
    \caption{Phonetic vector}
  \endminipage
  \caption{Individual breakdown of results for each metric}
  \label{fig:exp1_breakdown}
\end{figure}

### 2019-08-06 Thesis/pages/design.tex
Changes; - Added graphs for firstexperiment results - More content added to thesis

@@
 \subsubsection{Quality control}
+\label{sec:exp1_qualitycontrol}
 As the study was being outsourced to Amazon's Mechanical Turk the requirement to check the quality of results is important. Therefore, a couple of additions were provided to check a result's validity.
@@
 \subsubsection{Considerations}
+\label{sec:exp1_considerations}
 This section will discuss the considerations required when interpreting the results of the study.

### 2019-08-06 Thesis/pages/experiments.tex
Changes; - Added graphs for firstexperiment results - More content added to thesis

@@
 As discussed in Section \ref{exp:metric} the goal of the experiment was the cull the number of metrics to be assessed in the following experiment.
-This section will discuss the demographics of participants alongside the subsequent results
+This section will discuss the demographics of participants alongside the subsequent results.
 
@@
 \end{table}
-\textbf{TODO: } Create some graphs off this data and put them in the appendix.
 
-\begin{wrapfigure}{l}{6cm}
+\begin{wrapfigure}[10]{l}{6cm}
     \centering
@@
 
-Table \ref{tab:exp1_demo} contains the geographical breakdown of the participants assessed.
+Table \ref{tab:exp1_demo} contains the demographical breakdown of the participants assessed.
 As it can be seen over 60\% of participants can be considered highly educated (Bachelor’s and up).
 This is not fully reflective of the general population and therefore, has to be considered when interpreting the results.
-All participants were sourced from the US, this again requires consideration due to the large range of dialects present, that may bias the results.
-Further work could investigate the affect of location on these results.
+All participants were sourced from the US, this again requires consideration due to the large range of dialects present that may bias the results.
+Further work could investigate the affect of location and dialect on similar results.
 
-Figure \ref{tab:exp1_results} shows the average results for the metrics
+Overall, 104 participants were assessed in this study.
+Five results were discarded from the set due to either failing the attention questions (See in Section \ref{sec:exp1_qualitycontrol}) or having having too low of a fluency rating.
+This was a necessary process to improve the health of the results.
+
+Figure \ref{tab:exp1_results} shows the average results for the metrics.
+It can be seen that Levenshtein came out substantially above the rest.
+The breakdown of the ratings in Figure \ref{fig:exp1_breakdown} also shows Levenshtein's dominance.
+Levenshtein has a much larger proportion of 4 and 5 ratings than the alternatives alongside a very low level of low ratings.
+This performance may, however, be due to the visual way the comparisons are being performed.
+(Discussed in detail in Section \ref{sec:exp1_considerations}).
+
+The visual comparison will be the first point of contact between the question and the participant, then followed by the mental comparison of the phonetics.
+Therefore, this initial visual contact has the potential to bias the results of the study.
+This would affect Levenshtein due to the matches never being more than one character different, therefore, resulting in very similar looking words.
+The alternative is to run the study with only audio based comparisons between words, this will force the user to compare just the phonetics of the words and not be influenced by the visuals of the pair.
+This, however, adds cost onto the time and execution of the study.
+Therefore, even with the discussed issues, the aim of the experiment was to promptly reduce the number of metrics for use later in the project due to a lack of project resources.
+This experiment, therefore, has achieved that goal of providing three metrics for the subsequent experiment while balancing between accuracy and expenditure.
+Further work could aim to reproduce this study with the proposed audio based design.
+
+\input{diagrams/graphs/experiment_one/graph.tex}
 

### 2019-08-06 Experiments/MTurk/trustword_quali.py

@@ -28,7 +28,3 @@ if __name__ == "__main__":
             pass
             
     save("User.csv", mainWorkerData)
-    save("Batch.csv", hitWorkerData)
-
-
-

### 2019-08-06 Thesis/pages/design.tex
Changes; - Added the third round of results - Small changes applied to the thesis

@@
 Figure \ref{fig:phoneticMatch} shows an example match and the connected scale.
-Users will complete 5 of these comparisons per metric.
+Users will complete five of these comparisons per metric.
 
@@
 
-The first was the addition of 5 "Random matches" questions.
+The first was the addition of five "Random matches" questions.
 These were two random words selected from the dictionary.
@@
 \subsubsection{Considerations}
+
+\textbf{TODO: } Talk more about how the proposed idea of audio-audio would be very expensive etc etc. I need to remove the bit in the Experiment chapter and place it here.
+
 \label{sec:exp1_considerations}

### 2019-08-06 Thesis/pages/implementation.tex
Changes; - Added the third round of results - Small changes applied to the thesis

@@
 \subsubsection{General design}
-This section will discuss the overall technical implementation of GreenOnion alongside a deeper discussion into the unique aspect of the tool.
+This section will briefly discuss the overall technical implementation of GreenOnion alongside a deeper discussion into the unique aspect of the tool.
 
-The tool starts by generating a 2048-bit RSA key through GPG\footnote{GNU Privacy Guard}.
-This key is then used to create a hash of all but the final block of the key.
+GreenOnion is written in C++. This languages was chosen due to its efficiency bonuses over other alternative languages.
+The tool begins by generating a 2048-bit RSA key through GPG\footnote{GNU Privacy Guard}.
+This key is then used to create a hash of all but the final 512-bit block of the key.
 The final block of the key is left un-hashed due to the presence of the exponent ($e$).
-This exponent is incremented by one to provide a new key.
-This is the aspect provides rapid generation of unique key as work for the GPU.
+This exponent is incremented to create a new unique key.
+This is the aspect provides rapid generation of new keys due to the reduction in expensive large prime generation.
 This prevents issues in such as entropy starvation when generating a large number of valid RSA keys.
 This produces valid keys but with abnormally large exponents, this was deemed as suitable due to the short term use-case for these keys.
-3 bytes are used to represent the exponent giving the potential to create $2^{24} - 1$ extra keys for one expensive key generation.
+3 bytes are used to represent the exponent giving the potential to create $2^{24} - 1$ extra keys for a single expensive key generation.
 
 All keys plus the intermediate hash are loaded on the GPU via an OpenCL kernel.
-This kernel is designed with hashing the final block, obtaining the final fingerprint and checking if the fingerprint is present in the provided list.
+This kernel is designed to hash the final block, obtain the final fingerprint and checking if the fingerprint is present in the provided list.
 
@@
 
-Mass checking of fingerprints is the tools main functionality as it allows for millions of keys to be checked with a very small amount of overhead.
+Mass checking of fingerprints is the tools main abilities as it allows for millions of keys to be checked with a very small amount of overhead.
 This is achieved through the use of a bloom filter.
@@
 This data structure therefore has a complexity of $O(k)$ regardless of the number of elements in the set.
+This is the only data structure that provides this characteristic.
 
-However, due to the random distribution of the hashing algorithms commonly there is the possibility for collisions and, thus, the possibility of false-positives.
-The data structure also does not produce any false-negatives.
-This is fully suited to this use-case as any fingerprints tagged as ``possibility'' being present in the bloom filter can be followed up with a more expensive hash-table check to determine the actual presence.
+However, due to the random distribution of the hashing algorithms, there is the possibility for collisions and, thus, the possibility of false-positives.
+The data structure, however, does not produce any false-negatives.
+This, therefore, makes it fully suited to this use-case as any fingerprints tagged as ``possibility'' being present in the bloom filter can be followed up with a more expensive hash-table check to determine their actual presence.
 Therefore, if the levels of false-positives are controlled (by altering $k$ and $m$) the tool can search through huge number of potential keys without any decrease in speed.
@@
 As it can be seen the element $n$ definitely does not exist in the set due to both array indices not being set.
-The performance boost when comparing large numbers of keys is substantial when compared to the similar tool Scallion mentioned in Section \ref{sec:greenDesign}.
-The results from the comparison will be quantified in Chapter \ref{cha:Experiments}.
+The performance boost when comparing large numbers of keys is substantial when compared to the similar tool Scallion (See Section \ref{sec:greenDesign}.) The results from the comparison will be quantified in Chapter \ref{cha:Experiments}.
 

### 2019-08-06 Results/MainExperiment/link_to_questionaire.py

@@ -1,0 +1,75 @@
+import sys
+import csv
+import os
+
+def usage():
+    print(f"Usage: {__name__} <QUESTIONAIRE_PATH> <BATCH_PATH> <DIRECTORY>")
+    exit()
+
+
+def load(filePath):
+
+    data = []
+    with open(filePath) as csvDataFile:
+        csvReader = csv.reader(csvDataFile)
+        for row in csvReader:
+            data.append(row)
+
+    return data
+
+
+workers = {}
+
+if __name__ == "__main__":
+    
+    if len(sys.argv) != 4:
+        usage()
+
+    questionaire_path   = sys.argv[1]
+    batch_path          = sys.argv[2]
+    target_dir          = sys.argv[3]
+
+    # Load batch and link WorkerID to GUID
+    batch_data_raw = load(batch_path)
+
+    workerId_index = batch_data_raw[0].index("WorkerId")
+    guid_index = batch_data_raw[0].index("Answer.surveycode")
+
+    for row in batch_data_raw[1:]:
+        workers.update({row[guid_index]: row[workerId_index]})
+
+    # Uses GUID in directory to get Worker ID that then checks English comprehension
+    
+    guids = []
+    for f in os.listdir(f"{target_dir}"):
+
+        path = target_dir + f
+
+        if f.endswith(".pkl"):
+
+            parts = f.split(".")
+
+            guids.append(parts[0])
+
+    # Loads questionair data
+    questionaire_data_raw = load(questionaire_path)
+
+    quest_workerID_index = questionaire_data_raw[0].index("Worker ID")
+    quest_english_comp = questionaire_data_raw[0].index("English comprehension")
+
+    for g in guids:
+
+        try:
+            wID = workers[g]
+
+            for q in questionaire_data_raw[1:]:
+                
+                if q[quest_workerID_index] == wID:
+                    englishComp = q[quest_english_comp]
+
+                    if int(englishComp) < 5:
+                        print(f"GUID: {g}: WorkerID: {wID} has an English comprehension of: {englishComp}")
+        except:
+            print(f"GUID: {g} does not have a corresponding worker")
+
+

### 2019-08-06 Results/MainExperiment/link_to_questionaire.py
Changes; - Moved files that don't have a worker alongside - Added MTurk csv files - Updated README.md with the overall results - Added text file containing manual alterations to MTurk files

@@ -71,5 +71,6 @@ if __name__ == "__main__":
                         print(f"GUID: {g}: WorkerID: {wID} has an English comprehension of: {englishComp}")
         except:
             print(f"GUID: {g} does not have a corresponding worker")
-
-
+            print("Moving to a separate directory...")
+            #os.system(f"mkdir {target_dir}/NoWorker")
+            os.system(f"mv {target_dir}{g}.pkl {target_dir}/NoWorker")

### 2019-08-08 Thesis/pages/appendix.tex
Changes; - Added data from final round of experiments - Updated all batch files - Added more discussion to the expeirment section of the report

\appendix

\chapter{Randomly generated uncontrolled key}
\label{appendix:uncontrolled_key}
\begin{lstlisting}
-----BEGIN PGP PUBLIC KEY BLOCK-----

mQENBF0vHaYBCACxOy7RacHIprgaUo66vGmIB2VIaSwToliuaEBxOAloD+wTB/T9
TOKgAMLWMgK2z3/tOZj2l5k9ATUr0nZ9iBgew5Ih3ykOp+OkE9dh4NTD3EJz5UWo
M1r6scPhby92zMBqKi0iPFlPcvk+eg+SPusxIp+Vn16ALoB2pwGQvG+qoFEJfdVP
nwSAWJo1mcd+TCxgIMqe11FXDzxpd4BEpMXsHOB8NH/TUiI57sxqT8A2HnnyWo2i
5vs93VAP8rTTIRfGelW2c3oqhV9XhXbvVpJPmvkTxM/SshV1L5HhYr1TUAkAQw6w
RUZqooysgZEDqQw58lFQ7C9plCHOpXIEhbE7ABEBAAG0HEpvaG4gSm9obnNvbiA8
am9obkB3b3JrLmNvbT6JAVQEEwEIAD4WIQRQZ0ukmi5QUEz7KB3FwHKSVKqpwgUC
XS8dpgIbAwUJA8JnAAULCQgHAgYVCgkICwIEFgIDAQIeAQIXgAAKCRDFwHKSVKqp
wg4YB/9knveazSM4yN3EJY7HRZe5PVA5r0GGDlEDMte+surPKLsV/T39SNl8qTH+
DXnOyC4rt1kykTJP+ULcKqGkVRnH2XYZP/W6E9wwBPjoKHaWyn8MP0ix5kgkq6Ld
ZWEQ2pUwCsAhWv8K/ybjQ+Li484JKbrz/GRALp8qU3hZgCo/Fw3sD2KcTPU1v8qU
av9G2N5su10W7G0F1ozszFit+r2iinoZtGSddBPG+pIUEtZoBn4V2FRRSO1UY/TU
jGf2BLsk+ZkNJdx5x6IEU9CQ+ivPuKtupVu9ySKqE2Qfmn5lh9iAjYDN3XxUQfCf
braGoC9JLnL5QmT1JaQXfxkIHilyuQENBF0vHaYBCADDp/u8D/TG5d5HmabmgbBF
3R2d3J00vt7VQQ5sIRMLyP0cx6qy2bTIy9mgfU3/WcrhRp728gBo+NnUfxyiTb5R
u7AbntlkerF3dh0JLm5eIossPW37QXn3Ce4Tv4ixGRLbsGKTu6h0lP41FM5VcqV9
9NE1iml3WyngnsFdKeUYqPW4QY+ydyjpSyblbQTMptIKG2llCmsd9k+hb8nnGx/d
GvyGKaZ270iVGY2im/9VP2VwzqXlFxxx6Dux4egJJMMAy5xkzBKf+Szmm1pMJkt2
4sBrwmLnuUObgsAkq8K+MqEpWeFi6aWsh7RnY8T0SEb/3QUwG12V77ePhrarBwmf
ABEBAAGJATwEGAEIACYWIQRQZ0ukmi5QUEz7KB3FwHKSVKqpwgUCXS8dpgIbDAUJ
A8JnAAAKCRDFwHKSVKqpwoW3CACeKIcQFuVv2vpUHq/4ATH0atPYqR1NbJTegE+v
XZyrNHtmRF4V+kdx/1KX9jsIY2TjyxbhTsrtMFkMZMfAVjXVoS4y8OkwX5IJWgHC
0JQIHQrvaIGfI1yuVrNvWYyPXFxNtbntrgTd8JKYGKYaTqXNZ2r1ozbZElp7fQtR
rWNUGJYYo+aHHLM+Aot5k+Z3YqHifuPSnCEYt/GxnMhYq1IL3LSZ96hsgwqeFoLP
+v4RsvY52Yb5tiOzxZwikALOJdM2aAumxq8R1nYHiswWxotw2WkKFlB7gfLpbMWs
Y+o4J7QKSqpVTrUYBTPF1F4kBWOMY10kpeCDbZ1YwJOZJf8P
=aHBu
-----END PGP PUBLIC KEY BLOCK-----
\end{lstlisting}

\chapter{Computed Attack Keys}

\section{NYSIIS - 0 Static}
\label{appendix:nysiis_0_static}

\subsection{Controlled Key}
\begin{lstlisting}
-----BEGIN PGP PUBLIC KEY BLOCK-----

mI0EXS8lIAEEAMWEJ+NGB/ukiUijzdT+DvzVwouWV/j4Rw78X9YdgJP0ExT4ncHG
TJbOKjEMEI9bb/oYMLF/434ufScYNci+rL/3RVY8CcjEv5l0UGX+udZ78c7Z/vf1
zFr2MQAglr9M8599JwUY25LiNKzDYc87B16hqRV8hRaXHfAFFHBxRsgBABEBAAG0
HUF1dG9nZW5lcmF0ZWQgS2V5IDx1c2VyQENWRUQ+iNQEEwEKAD4WIQSlBU278MbT
iVM5h6GNohojnp5YQgUCXS8lIAIbLwUJAeJfkAULCQgHAgYVCgkICwIEFgIDAQIe
AQIXgAAKCRCNohojnp5YQvxSA/0bjL+4me3hLjrM+8IckKABCRdRYYRG7svbln9q
ULUngsXMpbIMoHFg1ePpT2lniiHtQhDC88ZW1J5yeVZN1cfJhRsByyKlkzG3Dcy7
5wKonbVz1LSYpIDq/DNNP0eINzuVNc1rxqRXPGAh6NHnmZN5MqxLNyu0DSX9oJHm
KbbtLQ==
=FQCu
-----END PGP PUBLIC KEY BLOCK-----
\end{lstlisting}

\subsection{Computed key}
\begin{lstlisting}
-----BEGIN PGP PUBLIC KEY BLOCK-----

mQEOBF0zhx4BCAD0iC55GShgArPzKZdn6we2mrkxS8o8fI7HdWXnLoRAta1Q1j9z
U+mYU9tGYb0yjqIARjjUK2qnq0CsGZJpB65AhbrOsDLv6dmI68tuiT4xjmzcM6+6
6M/EY5E5hYpZeurDJ8rSYrfu/v9P0bV78VnM17uUl4PTyEBmbJsE9kszq4MXd5yz
G+ibBPBvnBWSlRQzyCFMgTL8gQH36XJUj7jgxTKoJWzli/QtNcMOjwSQtEZxFWVK
+qsJjYUClpg9Kkow1LqJmEc1Tj98EipypDtdwNQhn4wHQVgu7SliaNNmrR8MpP9o
gL9hhfafx5FsE7v4zHhzu+ubR+c7KnUlwJyfABkBhI5atQAeSm9obiBEb2UgPGNo
YW5nZV9tZUBlbWFpbC5jb20+
=
-----END PGP PUBLIC KEY BLOCK-----
\end{lstlisting}

\newpage

\section{NYSIIS - 1 Static}
\label{appendix:nysiis_1_static}

\subsection{Controlled Key}
\begin{lstlisting}
-----BEGIN PGP PUBLIC KEY BLOCK-----

mI0EXS8o2AEEAKQmxot2Z5XFrNjg4zXBfvLsTzoO3vZeEI9l8+U2X8aq5KVQJpPU
BRSfqQuMZvA1zh3vH3w4I/vR4nXCNw/hPCi0B/DckUe6IJPZJfMiQfT1Xt16ZEms
W53CBiNqnt5xruo4wKwoKGuHELtPcD4K/iBIFt6n3UTi+R8xU4WMc+PjABEBAAG0
HUF1dG9nZW5lcmF0ZWQgS2V5IDx1c2VyQENWRUQ+iNQEEwEKAD4WIQTFXc8VXOqe
13ib81dcbeH3Z8A13wUCXS8o2AIbLwUJAeJb2AULCQgHAgYVCgkICwIEFgIDAQIe
AQIXgAAKCRBcbeH3Z8A13wItA/kBbfc6kxtLumDQiGpcIzgWmM9UhCn0V8ny9iB2
gt4V8bImpC3qicj6+KywsEsvFIgsJO0UcNeoREKanpXxPf6T7tvBUTLQjPJFedsn
J57996JiZ9COQ4lEg2AvfAKy1alKrMs0Xy4hWrHY9cJWs1a7KpbrsioHd4vDRgMS
2yRn/w==
=krrv
-----END PGP PUBLIC KEY BLOCK-----
\end{lstlisting}

\subsection{Computed key}
\begin{lstlisting}
-----BEGIN PGP PUBLIC KEY BLOCK-----

mQEOBF0yA4QBCAC78Lk2k9BdUEufpqll4D60iAuYVrxVs3lpjwP2hpztBFFw8vY4
26uW1C7MPo9l4Oteks5626hwAAgI1/YHFwWpBDdTWYEnVGrjv5v0Juz5IZc7kiwp
Ui2XWJ7I3VpE5nljFyzaQMGaS5Cvmtco5cjin1Tx486jieGBt0loQQdtiJ3gEAFT
XlUvwIQSdYWY2F8xWKg5aJoDFEZN74KfwQqB7hx/53VHyzOJGygnvvpMcJaX3c8E
V3t7n90WvXJWND7bn6HIJrnFKyRJsKHneL2n0wGd/N0NLCuLTvNK+uQ7sXGNZox1
Qa4a1guiSdaq9NO5mX+tOYox3/onzpshJgVDABkBvckntQAeSm9obiBEb2UgPGNo
YW5nZV9tZUBlbWFpbC5jb20+
=
-----END PGP PUBLIC KEY BLOCK-----
\end{lstlisting}

\newpage

\section{NYSIIS - 2 Static}
\label{appendix:nysiis_2_static}

\subsection{Controlled Key}
\begin{lstlisting}
-----BEGIN PGP PUBLIC KEY BLOCK-----

mI0EXS8s+gEEANkph53UuQkNVFhYimrzH0bXBp/Y3InV9p5MP09TZxtTOf44JBPp
MCFMvgFJpVK3D5PQ2h7fW1lNb41THkiGC7Jk+F7gd+beqH5kaaKmC+RNAF0aZ5av
2al5JvtHT0Z8/1r8bxfp33WLmQXK0/9EwL4HvERRGh7wZ5WemvCrvZPXABEBAAG0
HUF1dG9nZW5lcmF0ZWQgS2V5IDx1c2VyQENWRUQ+iNQEEwEKAD4WIQSjUV9vxlLP
LPE78Z2TulybLqhYHAUCXS8s+gIbLwUJAeJXtgULCQgHAgYVCgkICwIEFgIDAQIe
AQIXgAAKCRCTulybLqhYHONrBAC8uh/K2Adq/o/Qe/EVM5JpT6ETE1WlAj2iUMWB
MAmdjgiQlRyBCTd4Lt9xFsbnvQG9pj4GVHosXjVpuA/1NxyS+DE4EkBDzXA3NuR8
0djhyD27VSsn2q1j8bB1wxO7sLbjo30SIBG2wUaft5DVJiBGG69kh4pt+aKKOcjb
LLPldw==
=dCl/
-----END PGP PUBLIC KEY BLOCK-----
\end{lstlisting}

\subsection{Computed key}
\begin{lstlisting}
-----BEGIN PGP PUBLIC KEY BLOCK-----

mQEOBF0wxGEBCACsqQN92G3IizweQHw42OhUM5ZySKTvzPqVhAeCb2ETSBDZFbGN
lHYPa6dytXwLbU6kdlt8kgxbk75iPJsCSPLAUzKvlVd2rkTu5xtKPFqDTRvbjOjf
Ik8zJimXJGZNYVrMUqkfPR2FtVC4VUJXtML8voj/1lcLxTWRcYjuNQuSRNhJQtUP
ViZMTj97IO894lVg+ciZXEZkzHzlriqeLqwTupQxvzqjmObmeH1NCPSfGcTSNIBu
cNG/DrXTXsVpZPUilIRsXTtc2FM9iY49Zjv01KdzsJlV97JVyghYFFCEe1xq7Twp
U9TOzypXD4NdTKivFZUNT4jdG2HoJE4IcZ3NABkBh0qYtB5Kb2huIERvZSA8Y2hh
bmdlX21lQGVtYWlsLmNvbT4=
=0nU6
-----END PGP PUBLIC KEY BLOCK-----
\end{lstlisting}

### 2019-08-08 Thesis/pages/experiments.tex
Changes; - Added data from final round of experiments - Updated all batch files - Added more discussion to the expeirment section of the report

@@
 % Show that the bloom filter blows Scallion out of the water
+\textbf{TODO}
 
@@
         \hline
-        Highest Education:  & Bachelor's degree:    & 51.0\% \\
+        Highest Education:  
+        & GCSE:                 & 15.4\%  \\
         & A-Level/O-Level:      & 18.3\% \\
-                            & GCSE:                 & 15.4\%  \\
+        & Bachelor's degree:    & 51.0\% \\
         & Master's degree:      & 13.5\% \\ 
@@
 
-\begin{wrapfigure}[10]{l}{6cm}
+\begin{table}[h!]
     \centering
-    \begin{tabular}{|l|l|}
+    \begin{tabular}{|l|l|l|}
         \hline
-        Metric & Average Rating \\
+        Metric & Average Rating  & $\sigma$\\
         \hline
-        Leven     & 3.66 \\
-        NYSIIS    & 2.92 \\
-        Metaphone & 2.56 \\
-        Phonetic Vec & 2.50 \\
-        Soundex & 2.08 \\
+        Leven     & 3.66  & 1.15\\
+        NYSIIS    & 2.92 & 1.31\\
+        Metaphone & 2.56 & 1.32\\
+        Phonetic Vec & 2.50 & 1.35\\
+        Soundex & 2.08 & 1.12 \\
         \hline
-        Random  & 1.16 \\
+        Random  & 1.16 & 0.46\\
         \hline
@@
     \label{tab:exp1_results}
-\end{wrapfigure}
+\end{table}
 
@@
 
+Due to the averages of Metaphone and Phonetic Vectors being so close standard deviation was used as the final decider.
+As it can be seen Megaphone has a slightly lower $\sigma$ value of that of Phonetic vectors, thus, contributing to the decision to select Metaphone to be carried over to the next experiment.
+
+\subsection{Limitations}
+
 The visual comparison will be the first point of contact between the question and the participant, then followed by the mental comparison of the phonetics.
@@
 
-% 22 Missed values
-
-% Results
+\newpage
 
 \section{Experiment 2}
-% Methodology
 % Demographic
@@
 
+\subsection*{Demographics}
+Overall, 435 paid participants recruited via Amazon's MTurk were assessed in this experiment.
+We excluded 66 results; 7 due to being non-native speakers and 59 were discarded for failing the attention metrics (Discussed in Section \ref{sec:exp2_quality}).
+
+\begin{table}[h]
+    \centering
+    \begin{tabular}{|l|ll|}
+        \hline
+        Gender & Male: & 50.41\% \\
+               & Female: & 49.59\% \\
+        \hline
+        Age:   & 18-24: & 12.74\% \\ 
+               & 25-29: & 18.16\% \\ 
+               & 30-39: & 37.4\% \\ 
+               & 40-49: & 17.89\% \\ 
+               & 50-59: & 8.67\% \\ 
+               & 60-69: & 4.34\% \\ 
+               & 70-79: & 0.81\% \\
+
+        \hline
+        Highest Education:  
+        & GCSE:                 & 13.82\%  \\
+        & A-Level/O-Level:      & 24.12\% \\
+        & Bachelor's degree:    & 51.49\% \\
+        & Master's degree:      & 8.4\% \\ 
+        & PhD:                  & 2.17\% \\
+        \hline
+
+    \end{tabular}
+    \caption{Participant demographics}
+    \label{tab:exp2_demo}
+\end{table}
+
+The reduced set of 369 participants had an average age of 36.63 ($\sigma = 11.35$) and consisted of an almost equal split of Male (50.41\%) to Female (49.59\%).
+Around 62\% of participants had completed a single stage of university (Bachelor and up).
+This makes this set of participants more educated that the general population.
+All participants were also sourced from the USA and have rated themselves as fully native English speakers.
+% \begin{table}[!h]
+%     \centering
+%     \begin{tabular}{|l|l|}
+%         \hline
+%         Browser & Percentage \\
+%         \hline
+%         Chrome & 85.09\% \\
+%         Firefox & 12.20\% \\
+%         Safari & 1.90\% \\
+%         Other & 0.81\% \\
+%         \hline
+%     \end{tabular}
+%     \caption{Internet Browser breakdown}
+%     \label{tab:exp2_browser}
+%     \begin{tabular}{|l|l|}
+%         \hline
+%         Operating System & Percentage \\
+%         \hline
+
+%         \hline
+%         Windows (All) & 74.26\% \\
+%         ~~~~\textit{Windows 7} & ~~~12.74\% \\
+%         ~~~~\textit{Windows 8} & ~~~4.07\% \\
+%         ~~~~\textit{Windows 10} & ~~~57.45\% \\
+%         MacOS X	 & 13.82\% \\
+%         ChromeOS & 3.79\% \\
+%         Android	& 4.34\% \\
+%         iPhone	& 1.08\% \\
+%         iPad	& 0.54\% \\
+%         Linux	& 2.17\% \\
+%         \hline
+%     \end{tabular}
+%     \caption{Operating System breakdown}
+%     \label{tab:exp2_os}
+% \end{table}
+
+As user-agent strings were collected for each participant collations of OS and internet browser versions was made possible.
+Tables \ref{tab:exp2_browser} and \ref{tab:exp2_os} contain the browser and OS breakdowns respectively.
+Chrome and Windows 10 seem to dominate the proportion of their respective domains alongside the surprisingly large proportion of workers utilizing older versions of Windows such as 7 or 8 (15.81\%).
+
+\newpage
+
+\subsection*{Results}
+Table \ref{tab:exp2_attacks} contains the break down of results for the experiment.
+It can be seen that the best metric out of the set was Levenshtein with an overall success of 19.80\%.
+The best performer when regarding attack strength, as expected is the 2 static words.
+Levenshtein's 2 static attack performed the best overall with a success rate of 32.05\%.
+The worst performer was Metaphone with an average of 16.88\% over its three levels of attacks.
+When comparing the performance of the metrics to the previous experiment the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in the exactly same order.
+
+\begin{table}
+    \centering
+    \begin{tabular}{|ll|l|l|l|}
+        \hline
+        \textbf{Metric} & & \textbf{Successful Attacks} & \textbf{Total Attacks} & \textbf{Success Rate} \\
+        \hline
+        Levenshtein && 218 & 1101 & 19.80\% \\
+        \hline
+        & 0 static   & 34  & 358  & ~9.50\% \\
+        & 1 static   & 59  & 353  & 16.71\% \\
+        & 2 static   & 125  & 390  & 32.05\% \\
+        \hline\hline
+        Metaphone &&  181 & 1072 & 16.88\% \\
+        \hline
+        & 0 static   & 38 & 345 & 11.01\% \\
+        & 1 static   & 57 & 375 & 15.20\% \\
+        & 2 static   & 86 & 352 & 24.43\% \\
+        \hline\hline
+        NYSIIS &&  209 & 1114 & 18.76\% \\
+        \hline
+        & 0 static   & 36 & 385 & ~9.35\% \\
+        & 1 static   & 72 & 375 & 19.20\% \\
+        & 2 static   & 101 & 354 & 28.53\% \\
+        \hline\hline
+        \textbf{Overall} & & 608 & 3287 & 18.50\% \\
+        \hline\hline
+    \end{tabular}
+    \caption{Success rates for simulated attacks}
+    \label{tab:exp2_attacks}
+\end{table}
+
+As previously mentioned, the set of recruited participants are more highly educated than the general population.
+This combined with the low average age contributes to an inevitable bias being introduced into the data.
+An assumption can be made that higher education leads to more skillful interaction with computer based systems, this, therefore, with the previous assumption in mind results in the results of this experiment being a best case scenario as the attacks would be expected to be more successful with less able users.
+This, however, requires further research and possible empirical data to determine the validity of the assumption.
+
+\subsection*{Limitations}
+Due to multiple attacks occurring for one participant the rate of success cannot be
+
+\subsection{Comparison to alternative literature}
+% # Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols
+
+% Set of 4 words compared from a dictionary of 1024 words (10-bits per word)
+
+% 	- Near matches differ by a single word (No measure of similarity) randomly decided word
+
+% 	- FP (Security faliure)
+% 	- FN (Non-security faliure)
+
+% 	Total: 3.3% (FP) - 16.7% (FN)
+
+% 	Only 30 participants
+
+% # Unicorns
+
+% 	- 16 words long
+
+% 	"Our participants were recruited from MTurk, which is not
+% 	representative of the general U.S. population; MTurk workers
+% 	have been found to be younger and better educated [15]."
+
+% 	14% missed the simulated attacks
+
 \section{Distribution of keys permutations (Vuln-keys)}
+
+\newpage
+
+\section{Generation of keys}
+To demonstrate that the the generation of the near collision keys is not only theoretical actual generation of keys was performed using GreenOnion.
+A random metric was selected from the three carried forward from the first experiment.
+Alongside this a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key).
+Then for each attack level (0 static, 1 static, 2 static) a key was computed.
+NYSIIS was chosen as the selected metric.
+To expedite the process an initial search was performed for controlled keys that had the highest number of permutations, this was due to the demonstration of the actual generation of keys.
+Producing near-matching keys that have a very small number of potential matches, therefore, adds very little to this demonstration with a large computation cost.
+
+\begin{table}[h!]
+    \begin{tabular}{|l|l|}
+        \hline
+        Potential near-collision keys & 142,296 \\
+        Hashing speed & 4000 MH/s \\
+        Estimated computation time & 9 hours \\
+        Actual computation & 6.41 hours \\
+        GPU Days & 0.52 \\
+        \hline
+        Original Trustwords & BELL GRIND ALGERIA ANNULI \\
+        Actual Trustwords   & BOIL GRAND ALGER ANNUL \\
+        \hline
+    \end{tabular}
+    \caption{NYSIIS - 0 static}
+    \label{tab:nysiis0}
+
+    \begin{tabular}{|l|l|}
+        \hline
+        Potential near-collision keys & 133,200 \\
+        Hashing speed & 8000 MH/s \\
+        Estimated computation time & 4.2 hours \\
+        Actual computation & 5.12 hours \\
+        GPU Days & 0.853 \\
+        \hline
+        Original Trustwords & ASSUMING SONOMA DENS KEENER \\
+        Actual Trustwords   & ASSUMING SUMMON DENNI CONNOR \\
+        \hline
+    \end{tabular}
+    \caption{NYSIIS - 1 static}
+    \label{tab:nysiis1}
+
+    \begin{tabular}{|l|l|}
+        \hline
+        Potential near-collision keys & 16,464 \\
+        Hashing speed & 6000 MH/s \\
+        Estimated computation time & 2.16 days \\
+        Actual computation & 23.44 hours \\
+        GPU Days & 2.93 \\
+        \hline
+        Original Trustwords & VOCATION BORE TANN ANTE \\
+        Actual Trustwords   & VOCATION BARE TONE ANTE \\
+        \hline
+    \end{tabular}
+    \caption{NYSIIS - 2 static}
+
+    \label{tab:nysiis2}
+\end{table}
+
+Tables \ref{tab:nysiis0}, \ref{tab:nysiis1} and \ref{tab:nysiis2} contain the parameters and results on the computation.
+Due to varying availability of resources each computation has a varying hashing speed.
+This, however, has been normalized by the introduction of the "GPU Day" metric.
+This is simply the computation time required to reach the same conclusion on a single 2000 MH/s GPU.

### 2019-08-08 Results/MainExperiment/scripts/stats.py

@@ -1,6 +1,7 @@
 import httpagentparser
 import experiment
 import matplotlib.pyplot as plt
+import statistics
 import operator
 import pickle
 import csv
@@ -88,22 +89,49 @@ def user_agent_parsing(experiments):
 
     print("[!] UserAgent Parsing\n")
 
-    operatingSystems = {}
+    # operatingSystems = {}
+    # for e in experiments:
+    #     user_agent = httpagentparser.detect(e.UserAgent)
+
+    #     platformName = user_agent['platform']['name'].strip()
+    #     version = user_agent['platform']['version']
+
+    #     if not platformName in operatingSystems:
+    #         operatingSystems.update({platformName: [version]})
+    #     else:
+    #         operatingSystems[platformName].append(version)
+
+    # for os in operatingSystems:
+    #     print("\t", os, len(operatingSystems[os]))
+    # print("\n\t Total:", len(experiments))
+
+    operating_systems = {}
+    browsers = {}
     for e in experiments:
-        user_agent = httpagentparser.detect(e.UserAgent)
+        user_agent = httpagentparser.simple_detect(e.UserAgent)
 
-        platformName = user_agent['platform']['name'].strip()
-        version = user_agent['platform']['version']
+        platform = user_agent[0]
 
-        if not platformName in operatingSystems:
-            operatingSystems.update({platformName: [version]})
+        browser = user_agent[1].split(" ")[0]
+
+        if not platform in operating_systems:
+            operating_systems.update({platform: 1})
         else:
-            operatingSystems[platformName].append(version)
+            operating_systems[platform] += 1
 
-    for os in operatingSystems:
-        print("\t", os, len(operatingSystems[os]))
+        if not browser in browsers:
+            browsers.update({browser: 1})
+        else:
+            browsers[browser] += 1
 
-    print("\n\t Total:", len(experiments))
+    print("\t [*] Operating systems")
+    for os in operating_systems:
+        print(f"\t   {os}: {operating_systems[os]} -- {round(operating_systems[os] / len(experiments) * 100, 2)}%")
+
+    print()
+    print("\t [*] Browswers: ")
+    for b in browsers:
+        print(f"\t   {b}: {browsers[b]}")
 
 def average_completion_time(experiments):
     
@@ -240,6 +268,8 @@ def demographical_stats(workerData, experiments):
         "PhD": 0
     }
 
+    AGES = []
+
[…]

### 2019-08-08 Results/PiliotStudy/parse_results.py

@@ -1,4 +1,5 @@
 import sys
+import statistics
 
 """
 Parses the results from the Google Forms pilot study
@@ -70,13 +71,18 @@ if __name__ == "__main__":
 
         sect_results = RESULTS[sect]
 
+        all_results = []
+        for s in sect_results:
+            all_results += s
+
+        all_results = list(filter("".__ne__, all_results))
+        all_results = list(map(int, all_results))
+
         total = 0
         num_of_values = 0
         missed = 0
 
-        for response in sect_results:
-
-            for value in response:
+        for value in all_results:
 
                 if value != "":
                     total += int(value)
@@ -85,7 +91,8 @@ if __name__ == "__main__":
                     missed += 1
 
         print(sect)
-        print(f"[!] Average : {round(total/num_of_values, 2)}")
+        print(f"[!] Average : {round(sum(all_results)/len(all_results), 2)}")
+        print(f"[!] Standard Dev: {round(statistics.stdev(all_results), 2)}")
         print(f"[!] Missed  : {missed}")
         print()
 

### 2019-08-09 Thesis/pages/design.tex
Changes; - Added data from final round of experiments - Updated all batch files - Added more discussion to the expeirment section of the report
Changes; - Updated and read through aspects of the report - Continuing with implementation aspects of the project

@@
 
-This chapter will discuss and overview of the proposed attack and the elements that are required.
+This chapter will discuss and overview of the proposed designs for elements required to answer the research questions. Alternative designs are explained when relevant and design choices are justified
 
@@
 There are a total of 5616 codes due to 26 initial letters and three digits of 6 values ($26 * 6^3$).
-The limited combinations will result in matches of a limited quality. This will require consideration later in the project.
+The limited combinations will result in matches of a limited quality.
 
@@
 It was in use right up the end of 1998 within various US Government departments.
-Due to this prolific stature and proven track record it was deemed suitable as one of the selected similarity metrics.
+Due to NYSIIS's aforementioned use in a professional setting alongside its high occurrence in literature, it was deemed suitable as one of the selected similarity metrics.
 
@@
 Metaphone is arguably on the same level of ubiquity as that of Soundex with it finding itself implemented in languages such as PHP\cite{php}.
+Metaphone was chosen due to similar reasons to that of Soundex and NYSIIS.
+
+\textbf{TODO} Better argument needed?
 
@@
 Double Metaphone (2000) and Metaphone 3 (2009) that claim to improve over the original version due to further research performed by Philips.
-The original version was chosen due to its historical and widespread usage.
 
-\subsection{Levenshtien Distance}
+\subsection{Levenshtein Distance}
 Levenshtein distance is a string metric designed to measure the 'distance' between two strings.
@@
 Edit distance is not technically designed as a phonetic algorithm, but due to similar-sounding words often being spelt in similar ways\cite{hettiarachchi2012sparcl} Levenshtien distance was deemed another suitable metric.
+Levenshtein is also the most algorithmically simplistic of all the options, this further contributes to its appeal as a chosen metric.
 
@@
 
-Extensive prior work has gone into producing models of features that map to phonemes.
-\cite{chomsky1968sound}\cite{ladefoged1969measurement}\cite{bradlow2010perceptual}.
+Extensive prior work has gone into producing models of features that map to phonemes \cite{chomsky1968sound}\cite{ladefoged1969measurement}\cite{bradlow2010perceptual}.
 Features, therefore, are an attempt at mapping the varying and inconsistent rules around pronunciation of the English language.
@@
 
-For example, the addition of vectors can be seen in Table \ref{tab:vectorAdd}. This works for any mathematical operation with multiplication allowing the 'tinting' words with a theme.
+For example, the addition of vectors can be seen in Table \ref{tab:vectorAdd}. This works for any mathematical operation with examples like multiplication allowing the `tinting' words with a theme.
 
@@
 This, if the vector mappings are an accurate representation could allow a creation of a phonetically distinctive wordlist.
-This will be discussed further at a later stage of the report.
+These unique aspects contributes to inclusion of this metric in the set.
 
@@
 The first was the addition of five "Random matches" questions.
-These were two random words selected from the dictionary.
-Therefore, the overall rating of these words should be close to an average of 1.
+These are matches consisting of two random words selected from the dictionary.
+Therefore, the expected average rating of these words should be close to 1.
 This allows a simple check to see if the user is providing valid results.
@@
 
-The final check to ensure the validity of results is a check for native 
-English fluency. Having non-native English speakers complete the 
+The final check to ensure the validity of results is a check for native English fluency. Having non-native English speakers complete the 
 experiment has the possibility to introduce inconsistencies into the 
@@
 \subsubsection{Considerations}
-
-\textbf{TODO: } Talk more about how the proposed idea of audio-audio would be very expensive etc etc. I need to remove the bit in the Experiment chapter and place it here.
-
 \label{sec:exp1_considerations}
-This section will discuss the considerations required when interpreting the results of the study.
 
@@
 In the case of this experiment the users are asked to compare the sound of two word that are visually displayed to them.
-Therefore, this experiment does not fully capture the targeted scenario.
-This was decided partly to aforementioned lack of resources.
-The main design of the experiment was to provide a simple way to cull the large number of metrics.
-The initial choice of five metrics discussed in Section \ref{sec:metrics} was to be followed by a more empirical decision.
-Further work, therefore, could improve by producing more conclusive results on the performance of the metrics.
+This visual aspect is the first point of contact between the participant and the question, followed by mental comparison of the phonetics of the word.
+Therefore, this initial visual contact has the potential to bias the results of the study.
+This has the potential to affect Levenshtein due to the matches never being more than one character different, therefore, resulting in very similar looking words.
+The alternative method of running this experiment is to get users to compare audio samples of words, this will force the user to compare just the phonetics of the words and not be influenced by the visual aspects of the pair.
+This, however, adds a substantial cost onto the operation of the study.
+Due to the aforementioned lack of resources the chosen design was decided as most feasible as it is a balance between cost and accuracy.
+Further work, therefore, could improve by producing more conclusive results on the performance of the metrics by implementing the more accurate but costly alternative.
 
@@
 This is due to the assumptions that an increase in age provides a better understanding of more obscure words, and, therefore, a better representation of the metrics performance over the entire dictionary.
-
-\newpage
 
@@
 However, this may not be applicable in this context due to the user being linearly fed an audio stream that they cannot skip to the start or end.
-However, we believe that attention will also play a part in defining the most important areas of comparison as the hypothesis is that the users attention will be lower in the middle sections of comparison where it peak at the start and end.
-All these aspects, however, will require empirical evidence to arrive at a conclusion.
+We believe, however, that attention will also play a part in defining the most important areas of comparison as the hypothesis is that the users attention will be lower in the middle sections of comparison where it peak at the start and end.
+All these aspects will require empirical evidence to arrive at a conclusion.
 Therefore, this consideration will need to be made when assessing the results of the experiment.
@@
 The timeframe for finding a match was decided as 7-days on with attack strengths of 1 GPU/day, 10 GPU/days and 100 GPU/days on a mid range GPU (AMD RX 480 was the example in experiments).
+Due to the long life time of PGP keys, 7 days was chosen as a reasonable length of attack, attackers can just leave the tool and have it compute potential keys for the target without any need for user engagement.
+This is also a maximum time, these attacks also include keys that have a shorter average computation time.
 
@@
 
-Table \ref{tab:attackReq} contains a summary of the different level of attacks and their respective restrictions. More combinations makes the attack search quicker as there are more possibilities.
-
+Table \ref{tab:attackReq} contains a summary of the different level of attacks and their respective restrictions.
+More combinations makes the attack search quicker as there are more possibilities.
 Any key that exceeds this criteria is deemed as vulnerable is one of the three attack contexts.
@@
 
+\todo{Talk here about the sampling of vuln keys from keys harvested from PGP key servers.}
+
 \subsubsection{Quality control}
+\label{sec:exp2_quality}
 As the previous experiment, participants will be sourced from MTurk.
@@
 \subsubsection{Considerations}
-\textbf{TODO}
-
-Demographics of MTurk workers (Discussed in the previous section)
+As with the previous experiment MTurk demographics will result in participants that are not reflective of the general population.
+Due to the attack context of this experiment is can be assumed that the youth of the participants will contribute to less successful attacks.
+Therefore, the results generated by this experiment can be loosely assumed as a best case scenario for the scheme.
+We predict a high attack success rate if assessed over the general population.

### 2019-08-09 Thesis/pages/experiments.tex
Changes; - Updated and read through aspects of the report - Continuing with implementation aspects of the project

@@
 % Show that the bloom filter blows Scallion out of the water
+\textbf{TODO}
+
+\section{Distribution of vulnerable keys}
+\textbf{TODO}
+
+\section{Average number of permutations for each metric}
 \textbf{TODO}
@@
 
-The visual comparison will be the first point of contact between the question and the participant, then followed by the mental comparison of the phonetics.
-Therefore, this initial visual contact has the potential to bias the results of the study.
-This would affect Levenshtein due to the matches never being more than one character different, therefore, resulting in very similar looking words.
-The alternative is to run the study with only audio based comparisons between words, this will force the user to compare just the phonetics of the words and not be influenced by the visuals of the pair.
-This, however, adds cost onto the time and execution of the study.
+\textbf{TODO: } Reference back to the decisions made in the design section.
+
 Therefore, even with the discussed issues, the aim of the experiment was to promptly reduce the number of metrics for use later in the project due to a lack of project resources.
+
 This experiment, therefore, has achieved that goal of providing three metrics for the subsequent experiment while balancing between accuracy and expenditure.
@@
 All participants were also sourced from the USA and have rated themselves as fully native English speakers.
-% \begin{table}[!h]
-%     \centering
-%     \begin{tabular}{|l|l|}
-%         \hline
-%         Browser & Percentage \\
-%         \hline
-%         Chrome & 85.09\% \\
-%         Firefox & 12.20\% \\
-%         Safari & 1.90\% \\
-%         Other & 0.81\% \\
-%         \hline
-%     \end{tabular}
-%     \caption{Internet Browser breakdown}
-%     \label{tab:exp2_browser}
-%     \begin{tabular}{|l|l|}
-%         \hline
-%         Operating System & Percentage \\
-%         \hline
+\begin{table}[!h]
+    \centering
+    \begin{tabular}{|l|l|}
+        \hline
+        Browser & Percentage \\
+        \hline
+        Chrome & 85.09\% \\
+        Firefox & 12.20\% \\
+        Safari & 1.90\% \\
+        Other & 0.81\% \\
+        \hline
+    \end{tabular}
+    \caption{Internet Browser breakdown}
+    \label{tab:exp2_browser}
+    \begin{tabular}{|l|l|}
+        \hline
+        Operating System & Percentage \\
+        \hline
 
-%         \hline
-%         Windows (All) & 74.26\% \\
-%         ~~~~\textit{Windows 7} & ~~~12.74\% \\
-%         ~~~~\textit{Windows 8} & ~~~4.07\% \\
-%         ~~~~\textit{Windows 10} & ~~~57.45\% \\
-%         MacOS X	 & 13.82\% \\
-%         ChromeOS & 3.79\% \\
-%         Android	& 4.34\% \\
-%         iPhone	& 1.08\% \\
-%         iPad	& 0.54\% \\
-%         Linux	& 2.17\% \\
-%         \hline
-%     \end{tabular}
-%     \caption{Operating System breakdown}
-%     \label{tab:exp2_os}
-% \end{table}
+        \hline
+        Windows (All) & 74.26\% \\
+        ~~~~\textit{Windows 7} & ~~~12.74\% \\
+        ~~~~\textit{Windows 8} & ~~~4.07\% \\
+        ~~~~\textit{Windows 10} & ~~~57.45\% \\
+        MacOS X	 & 13.82\% \\
+        ChromeOS & 3.79\% \\
+        Android	& 4.34\% \\
+        iPhone	& 1.08\% \\
+        iPad	& 0.54\% \\
+        Linux	& 2.17\% \\
+        \hline
+    \end{tabular}
+    \caption{Operating System breakdown}
+    \label{tab:exp2_os}
+\end{table}
 
@@
 \subsection{Comparison to alternative literature}
+\todo{Compare to the other similar papers, is this higher or lower than other papers?}
+
 % # Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols
@@
 % 	14% missed the simulated attacks
-
-\section{Distribution of keys permutations (Vuln-keys)}
-
-\newpage
 

### 2019-08-09 Thesis/pages/implementation.tex
Changes; - Updated and read through aspects of the report - Continuing with implementation aspects of the project

@@
 
-\textbf{TODO: } Talk here about the interesting and challenges that were overcome
+\todo{Talk here about the interesting and challenges that were overcome}
 
@@
 \section{First Experiment}
-Explain how Google App Script was used?
+In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}) Google Forms\footnote{\url{https://www.google.com/forms}} was used as the application.
+It provided functionality to easily present questions and record their responses.
+However, as the design requirement of renewing sample from the matches of each metric was not part of the main applications functionality other solution was required.
+This was solved by Google's  App Script\footnote{\url{https://developers.google.com/apps-script/}} service that allows a user to programmatically interact with the Form.
+This allowed the re-sampling of matches each time a user submitted a response.
+
+\begin{figure}[!h]
+\begin{lstlisting}[frame=single, language=Javascript]
+var ALGOS = ["Soundex", "Metaphone", ...];
+var ALGO_SIZES = [763777, 412916, ...];
+
+function updateForm(ss, form) {
+
+  // Obtains a list of the items present on the form
+  formItems = form.getItems();
+
+  // Updates the new values
+  var algo_index = 0;
+  var scale_index = 0;
+  for (var i = 0; i < formItems.length; i++)
+  {
+    if (formItems[i].getType() == "SCALE")
+    {
+      var rnd_index = Math.floor(Math.random() * 
+      ALGO_SIZES[algo_index]) + 1;
+
+      // Obtains the Google Sheets object
+      var sheetname = ALGOS[algo_index];
+      var sheet = ss.getSheetByName(sheetname);
+      var range = sheet.getRange(rnd_index, 1)
+      var values = range.getValues();
+
+      // Re-samples from the connected Google Sheets
+      _updateScaleTitle(formItems[i], values[0]);
+
+      scale_index++;
+
+      // Moves on to the next metric when a group size is
+      // been completed
+      if (scale_index != 0)
+      {
+        if (scale_index % QUESTION_PER_ALGO == 0) {
+            algo_index++;
+        }
+      }
+    }
+  }
+}
+\end{lstlisting}
+\caption{Section of code from the First Experiment's Google App Script}
+\label{fig:GoogleAppScript}
+\end{figure}
+
+Figure \ref{fig:GoogleAppScript} contains an interesting snippet from the script used in the experiment.
+Each time a user submitted their response the \verb|updateForm()| endpoint was called, that subsequently updated the questions for the next user.
+This aimed to keep the samplings fair as they are equality likely to appear when attacking the system alongside an ample exploration of the overall match quality.
 
 \section{MainExperiment}
-Design of the application etc
+In order to asses users in a similar scenario to ones experienced when utilizing \pep in the real-world a custom application was required.
+
+\todo{What interesting aspects do I want to talk about here?}

### 2019-08-09 Thesis/pages/experiments.tex
Changes; - Added further discussion to the report

@@
 \section{Experiment 2}
+\label{sec:exp2}
 % Demographic
@@
 \subsection*{Limitations}
-Due to multiple attacks occurring for one participant the rate of success cannot be
+During this study the main task was to perform the authentication ceremony a large number of times.
+In the real-world the ceremony is a secondary task due to it not strictly being required.
+This alongside the potential for users to downplay the possibility of attack leads to the conclusion that these results have limited applicability in a real-world setting.
+The assumption is that these results display the success rate for extremely attentive user where they will make sure to double check with their participant and not just aim to complete the task as quickly as possible.
+This, therefore, means in a real-world setting the success rates could be even higher.
+
+\todo{Include email example of user assuming error over attack}.
 
 \subsection{Comparison to alternative literature}
-\todo{Compare to the other similar papers, is this higher or lower than other papers?}
+This section will aim to compare the results of the experiment to similar literature.
 
-% # Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols
+Work by Kainda \textit{et al.}\cite{kainda2009usability} (previous discussed in Chapter \ref{cha:LiteratureReview}) is the most comparable to this experiment.
+They were the only study to use exactly 4 words, but differed on the size of dictionary (1024 words) and how a near-match was calculated.
+Near-matches were a difference in a single word, but without the consideration for similarity, this is the unique aspect considered with this experiment.
 
-% Set of 4 words compared from a dictionary of 1024 words (10-bits per word)
+However, with those aspect in mind Words received an overall success rating of 3.3\%, considerably lower than that of this study.
+The results presented in this experiment in the worst case presented almost 3 times as many successful attacks.
 
-% 	- Near matches differ by a single word (No measure of similarity) randomly decided word
+Other relevant work by Dechand \textit{el al.}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words.
+This is less similar to the experiment as 14 words per attack were assessed with each participant, where the comparison was performed visually.
+However, the success for the PGP Word list was 8.78\%.
+As 10/14 words were kept static more comparable to comparable the results to the highest attack strength ``2 static''.
+Therefore, the results presented in this section are substantially higher than this paper, where again the success rate is almost 3 times higher.
 
-% 	- FP (Security faliure)
-% 	- FN (Non-security faliure)
+The final relevant paper to compare is that of Tan \textit{et al.}.
+This paper had the highest number of words assessed with 16 overall.
+With it assessing the same wordlist and attack strength as the work by Dechand \textit{et al.}.
+The attack success was 14\% overall, this again compared to the highest attack assessed in the experiment results in a sizeable difference between the attack successes.
 
-% 	Total: 3.3% (FP) - 16.7% (FN)
-
-% 	Only 30 participants
-
-% # Unicorns
-
-% 	- 16 words long
-
-% 	"Our participants were recruited from MTurk, which is not
-% 	representative of the general U.S. population; MTurk workers
-% 	have been found to be younger and better educated [15]."
-
-% 	14% missed the simulated attacks
+In conclusion, all similar literature had much lower attack success rates that the results presented in this experiment.
+With all papers using similarly designed words lists it highly suggests that the deficiencies in Trustwords are the cause for the substantial increase in attack success.
+Furthermore, the consideration for similarity of words that the other papers have not considered could have also resulted in the higher attack success rates.
 
@@
 This is simply the computation time required to reach the same conclusion on a single 2000 MH/s GPU.
+As it can be seen most notable from Table \ref{tab:nysiis2} the generation of the actual Trustwords differs in only 3 characters making it arguably very similar.
+
+When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU is able to achieve around a 28\% success rate when assessed against actual users.
+Even with the least restricted attack type presented in Table \ref{tab:nysiis0} the computation of half a day can provide almost a 10\% success rate when attacking users.
+This means any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of fooling an actual user assuming the success rate is consistent across all keys.

### 2019-08-09 Thesis/pages/implementation.tex
Changes; - Added further discussion to the report

@@
 
-\todo{Talk here about the interesting and challenges that were overcome}
+This chapter will discuss implementation details of the project.
+Instead of explaining all the technical achievements in detail, the most interesting ones will be discussed alongside the respective challenges encountered.
 
@@
 This is achieved through the use of a bloom filter.
-A bloom filter is a probabilistic data structure that allows efficient checking for present of an element in a set.
-It is effectively a very large array of booleans that state wether an element is present.
-A position in the array is decided by a hashing algorithm.
+A bloom filter is a probabilistic data structure that allows efficient checking for presence of an element in a set.
+It is effectively a very large array of booleans that state wether an element is present where the position in the array is decided by a pre-defined hashing algorithm.
 This is repeated a number of times with a number of hashing algorithms ($k$) to populate the array of length ($m$).
-This then means checking the presence of an element in the set will just mean hashing the target and checking the elements returned.
+This then means checking the presence of an element in the set will just means hashing the target and checking the indices returned.
 This data structure therefore has a complexity of $O(k)$ regardless of the number of elements in the set.
-This is the only data structure that provides this characteristic.
+This is the only data structure that provides this useful characteristic.
 
@@
 \section{First Experiment}
-In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}) Google Forms\footnote{\url{https://www.google.com/forms}} was used as the application.
+In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}) Google Forms\footnote{\url{https://www.google.com/forms}} was used to host and design the questionnaire.
 It provided functionality to easily present questions and record their responses.
-However, as the design requirement of renewing sample from the matches of each metric was not part of the main applications functionality other solution was required.
+However, as the design requirement of renewing sample from the matches of each metric was not part of the main applications functionality a solution was required.
 This was solved by Google's App Script\footnote{\url{https://developers.google.com/apps-script/}} service that allows a user to programmatically interact with the Form.
@@
 In order to asses users in a similar scenario to ones experienced when utilizing \pep in the real-world a custom application was required.
+The front-end is developed in Javascript with a Python-Flask backend that acts as the webpages functionality.
+A number of end points are exposed like \verb|get_audio| or \verb|get_words| that are requested and displayed on the front-end.
 
-\todo{What interesting aspects do I want to talk about here?}
+One of the main problems encountered was the handling of each user's session.
+Initially during testing it was noted that changes in one end-point if timed correctly would overwrite the progress of another, this is commonly know as a ``Lost update''.
+This was due to the user session being stored in the \verb|session| cookie.
+When sending off a request the session cookie is included in the header, the code will then utilise the data within the cookie to make decision and alter state, the updated state is then returned as a cookie in the response.
+If, however, another request is executed before the first has completed, the second request is using the context of the first request and, thus, any alterations made by the first will be completely lost.
+
+\begin{figure}[!h]
+  \centering
+  \begin{sequencediagram}
+    \newthread{A}{Client}{}
+    \newinst[2]{B}{get\_audio()}{}
+    \newinst[2]{C}{get\_words()}{}
+
+    \begin{call}{A}{}{B}{}
+    \begin{call}[1]{A}{}{C}{}
+    \end{call}
+    \end{call}
+
+    \node[anchor=east] (c0) at (0.75, -1.325) {$c$};
+    \node[below of=c0, yshift=.4cm] (c1) {$c$};
+    \node[below of=c1, yshift=.4cm] (c2) {\textbf{\st{$c_{1}$}}};
+    \node[below of=c2, yshift=.4cm] (c3) {$c_2$};
+  \end{sequencediagram}
+  \caption{Sequence diagram for the `Lost Update' problem}
+  \label{fig:cookie}
+\end{figure}
+
+Figure \ref{fig:cookie} shows this problem visually. As it can be seen the response cookie $c_2$ is based of the old data of $c$ and, therefore, when returned will remove the progress of $c_1$.
+
+To keep the complexity of the backend low it was opted to solve this problem by restricting the user via the UI, when a button was clicked all other operations were disabled until a response was received.
+This stopped the possibility of sending off another request while another is still processing.
+
+I order to collate data for results later in the process state had to be saved.
+One potential solution would be to format the data and save it as a .csv file.
+However, this is a static way of data persistence and would require alteration every time the data schema was modified.
+The chosen solution utilized a python object serialization library known as `Pickle'\footnote{\url{https://docs.python.org/2/library/pickle.html}}.
+This library saves the an instance of a class as a file.
+This file then can be used to load the instance of the class back into the program.
+This allows changes to the object to filter down through the program and keeps the design of the application fluid.
+For example, after initial feedback gathered about the application it was decided that a inclusion of `Round times' would be a useful addition.
+Edits were made to the \verb|experiment| class and the changes propagated through the application, no changes were needed on the save functionality.
+To distinguish between old and new save formats a version number was used.

### 2019-08-09 Thesis/pages/introduction.tex
Changes; - Added more content to Thesis background
Changes; - Added scripts for processing Similar Words results - Added more content to the Thesis
Changes; - Added further discussion to the report

@@
 
-The increasing use of public key cryptography by instant messaging and secure email means key fingerprint 
-verification is an ever more important task.
+The increasing use of public key cryptography by instant messaging and secure email means key fingerprint  verification is an ever more important task.
+
 One of the most significant risks to the security of the communication channel is a Man-in-the-middle (MiTM) attack.
-A successful MiTM attack can circumvent the encryption as it allows an attacker to read all the encrypted data.
-A countermeasure for this is the verification of each parties' fingerprint.
-\textbf{[...]}
+A MiTM attack involves an attacker impersonating one or both sides of a connection.
+MiTM attacks can fully circumvent the encryption as it allows an attacker to read all of the encrypted data.
+
+A countermeasure for this is the verification of each parties' key fingerprint.
+A fingerprint is a small string of characters that is unique to each key pair.
+Therefore, it can be used as as a way of identification.
+
+Fingerprints can come in a number of different encodings such as hexadecimal, words and even procedurally generated avatars.
+Previous research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}, alongside this the involvement of human based verification makes the designing the scheme to be user friendly is a task of upmost importance.
+
+Humans have long been known as the most vulnerable part of any system.
+To combat this issue, solutions have been proposed to remove the manual verification with examples such as PGP's web-of-trust\cite{callas1998openpgp} and Namecoin\cite{kalodner2015empirical}.
+However, these suffer from user adoption due to perceived complexity.
+This leaves manual verification in the current position of being a difficult problem, where the proposed solutions need to sacrifice one of usability or security.
+Therefore, research into improving or creating new fingerprint encodings that work well with users remains massively relevant.
+
+The report will asses the security and feasibility of attacking a fingerprint encoding known as ``Trustwords'' as it claims at this point have been unsubstantiated.
+
+The report will be structured as follows:
+
+\textbf{Chapter 2} provides any required background knowledge alongside a review on all relevant literature.
+
+\textbf{Chapter 3} formally defines the aim of this report alongside the research questions the project aims to answer.
+
+\textbf{Chapter 4} documents the prosed designs required to answer the research questions proposed in Chapter 3.
+
+\textbf{Chapter 5} discusses the significant implementation details of the designs formalized in Chapter 4.
+
+\textbf{Chapter 6} presents and analyses all experimentation results of the project.
+
+\textbf{Chapter 7} evaluates the success of the project alongside a discussion into relevant further work. The research aims proposed earlier in Chapter 3 will be used as evaluative metrics.
+
+\textbf{Chapter 8} concludes the project with a culmination of the papers findings alongside the any conclusions that can be drawn from the research.

### 2019-08-12 Thesis/pages/experiments.tex
Changes; - Added more content to the experiment section of the paper - Updated and added new misc scripts

@@
 \section{Scallion vs GreenOnion}
-% Show that the bloom filter blows Scallion out of the water
-\textbf{TODO}
+This section will compare Scallion and the newly designed GreenOnion ability to search for a large number of potential keys.
 
-\section{Distribution of vulnerable keys}
-\textbf{TODO}
+Table \ref{tab:scallion_speed} shows the speed decline as the number of keys increase. Any number of keys over 45 resulted in a crash to the program.
 
-\section{Average number of permutations for each metric}
-\textbf{TODO}
+\todo{Add screenshot of the exception}
 
-\section{Metric Performance - Results}
+\begin{table}[!h]
+    \centering
+    \begin{tabular}{|ll|}
+        \hline
+        \textbf{Scallion} & \\
+        \hline
+        OS & Windows 10 (May 2019) \\
+        Version & Scallion-2.0\footnote{\url{https://github.com/lachesis/scallion/raw/binaries/scallion-v2.0.zip}} \\
+        \hline
+        \textbf{GreenOnion} & \\
+        \hline
+        OS & Linux Mint (Version: TODO) \\ 
+        \hline
+        \textbf{Hardware} & \\
+        \hline
+        GPU & GTX 750 Ti  \\
+        CPU & AMD FX-6300 \\
+        \hline
+    \end{tabular}
+    \caption{Testing environment}
+\end{table}
+
+\begin{table}[!h]
+    \centering
+    \begin{tabular}{|ll|}
+        \hline
+        \textbf{Number of keys} & \textbf{Speed} \\
+        \hline
+        1 & 1001.3 MH/s \\
+        5 & 784.3 MH/s \\
+        10 & 707.9 MH/s \\
+        15 & 628.2 MH/s \\
+        20 & 526.5 MH/s \\
+        25 & 503.8 MH/s \\
+        30 & 473.1 MH/s \\
+        35 & 432.6 MH/s \\
+        40 & 404.9 MH/s \\
+        45+ & \textit{N/A} \\
+        \hline
+    \end{tabular}
+    \caption{Scallion's speed decline}
+    \label{tab:scallion_speed}
+\end{table}
+\todo{Plot scallion speed decline}
+
+\todo{Show the maximum number of keys the tool can achive}
+
+\section{Experiment 1 - Metric performance}
 As discussed in Section \ref{exp:metric} the goal of the experiment was the cull the number of metrics to be assessed in the following experiment.
@@
 
-\section{Experiment 2}
+\section{Experiment 2 - Simulated attacks}
 \label{sec:exp2}
@@
 
-\newpage
-
 \subsection*{Results}
@@
 
+\section{Average number of near-collision keys for each metric}
+In order to predict the effectiveness of the attack over a wide variety of keys the number of average near-matches requires computation.
+Table \ref{tab:average_perm} shows the average keys for each metric.
+The ``Compute Time'' is the computation time required for a single mid range (2000MH/s) GPU.
+
+\begin{table}[!h]
+    \centering
+    \begin{tabular}{|lllll|}
+        \hline
+        \textbf{Metric} & \textbf{Attack Type} & \textbf{Mean permuations} & \textbf{$\sigma$} & \textbf{Compute Time} \\
+        \hline
+        NYSIIS &&&& \\
+        \hline
+        & 0 static & 1963.07 & 24769.48 & ~~27.19 days \\
+        & 1 static & 448.37 & 4316.57 & 119.14 days \\
+        & 2 static & 98.07 & 550.44 & ~~~~1.49 years \\
+        \hline
+
+        Metaphone &&&& \\
+        \hline
+        & 0 static & 27138.78 & 529229.35 & ~~~~1.97 days \\
+        & 1 static & 2822.74 & 23932.39 & ~~18.91 days \\
+        & 2 static & 339.84 & 1730.97 & ~~15.45 days \\
+        \hline
+
+        Levenshtein &&&& \\
+        \hline
+        & 0 static & 293.92 & 2158.24 & 182.17 days \\
+        & 1 static & 102.75 & 719.28 & ~~~~1.43 years \\
+        & 2 static & 35.53 & 120.71 & ~~~~4.18 years \\
+        \hline
+
+    \end{tabular}
+    \caption{Each metric's average near-collision keys}
+    \label{tab:average_perm}
+\end{table}
+
+As it can be seen metrics like Levenshtein have a low overall average and would require much more attacker resources to become feasible.
+However, metaphone has attacks that could be computed on average in under 2 days
+
+\section{Distribution of vulnerable keys}
+As discussed in the design of the second experiment (See Section \ref{sec:exp2}) the attacks sampled from a list of `vulnerable keys'.
+These vulnerable keys were created using real keys extracted from PGP key servers.
+These keys were then randomly sampled and used to create the combined key as discussed in Section \ref{sec:pep}.
+100,000 random key pair were as the total sample, and any vulnerable keys for each attack level were recorded.
+
+\todo{Reference David's work}
+
+\begin{table}[!h]
+    \centering
+    \begin{tabular}{|lll|}
+        \hline
+        \textbf{Attack Type} & \textbf{Metric} & \textbf{Vulnerable \%} \\
+        \hline 
+        2 static (152) && \\ 
+        & Levenshtein & ~~4.295\% \\
+        & Metaphone & 24.095\% \\
+        & NYSIIS & 10.441\% \\
+        \hline
+        1 static (1525) && \\ 
+        & Levenshtein & ~~0.827\% \\
+        & Metaphone & 15.569\% \\
+        & NYSIIS & ~~4.341\% \\
+        \hline
+        0 static (15250) && \\ 
+        & Levenshtein & ~~0.157\% \\
+        & Metaphone & 10.202\% \\
+        & NYSIIS & ~~1.824\% \\
+        \hline
+    \end{tabular}
+    \caption{Number of vulnerable keys per metric}
+\end{table}
+
 \section{Generation of keys}
@@
 NYSIIS was chosen as the selected metric.
-To expedite the process an initial search was performed for controlled keys that had the highest number of permutations, this was due to the demonstration of the actual generation of keys.
+To expedite the process an initial search was performed for controlled keys that had the highest number of near-collision keys, this was due to the demonstration of the actual generation of keys.
 Producing near-matching keys that have a very small number of potential matches, therefore, adds very little to this demonstration with a large computation cost.

### 2019-08-12 Code/Misc/time_calc.py

@@ -15,7 +15,7 @@ length_in_chars = float(sys.argv[1])
 hashspeed = int(sys.argv[2]) * 1000000
 permutations = float(sys.argv[3])
 
-top = (2**(4 * length_in_chars))
+top = (2**(4 * length_in_chars - 1))
 time_seconds = top / hashspeed / permutations
 time_days = time_seconds / 3600 / 24
 

### 2019-08-12 Code/TrustwordUtil/modes/plot_keys_perms.py

@@ -1,0 +1,73 @@
+import sys
+sys.path.append("..")
+sys.path.append("./trustword_util/util")
+
+import matplotlib.pyplot as plt
+import matplotlib.ticker as mticker
+import seaborn as sns
+import statistics
+
+from util.permutations import *
+from util.trustwords import *
+from util.mappings import *
+from util.load import *
+
+NUM_OF_WORDS = 4
+
+def load_keys_and_parse(filePath):
+
+    keys = []
+    with open(filePath) as file:
+
+        for line in file:
+            keys.append(line[:NUM_OF_WORDS * 4])
+
+    return keys
+
+def plot_distribution(data):
+    sns.distplot(data, bins=1000, hist = True, kde = False, kde_kws = \
+        {
+            'linewidth': 1,
+            'linestyle': "--",
+            'shade': True
+        }
+    )
+
+    plt.xlim(left=0)
+    plt.ylim(bottom=0)
+    plt.xlabel("Number of permutations")
+    plt.ylabel("Number of keys")
+
+    f = mticker.ScalarFormatter(useOffset=False, useMathText=True)
+    g = lambda x,pos : "${}$".format(f._formatSciNotation('%1.10e' % x))
+    plt.gca().yaxis.set_major_formatter(mticker.FuncFormatter(g))
+    plt.show()
+
+
+def plot(vulnKeyFilePath, staticWordsVal, mapping):
+    
+    keys = load_keys_and_parse(vulnKeyFilePath)
+
+    static_pos = []
+    if staticWordsVal == 2:
+        static_pos = [0, 3]
+    elif staticWordsVal == 1:
+        static_pos = [0]
+
+    total_loops = len(keys)
+
+    all_permutations = []
+
+    for i, k in enumerate(keys):
+        trustwords = fingerprint_to_words(k, mapping, PRINT=False)
+
+        num_of_perms = similar_perms_size(trustwords, mapping, staticPos=static_pos)
+
+        # num_of_perms == 0 is when RAM protection activates
+        if num_of_perms != 0:
+            all_permutations.append(num_of_perms)
+    
+    # plot_distribution(all_permutations)
+    print("Average: ", sum(all_permutations)/len(all_permutations))
+    print("StDev: ", statistics.stdev(all_permutations))
+

### 2019-08-12 Code/TrustwordUtil/trustwords_util.py

@@ -22,6 +22,7 @@ import modes.average_perms as AP
 import modes.words_from_keys as WK
 import modes.create_actual_key as CK
 import modes.perms_from_words as PW
+import modes.plot_keys_perms as PK
 
 from util.load import load_mappings, load_similar_mappings
 
@@ -116,6 +117,7 @@ def args():
     parser.add_argument("-p", "--perms-for-words", dest="perms", nargs=1, action="store")
     parser.add_argument("--vuln-keys", dest="vuln", nargs=3, action="store")
     parser.add_argument("--static-words", dest="static", nargs=1, action="store")
+    parser.add_argument("--plot", dest="plot", nargs=2, action="store")
     
     arg = parser.parse_args()
 
@@ -193,6 +195,13 @@ def args():
         static_words_val = int(arg.vuln[2])
 
         VK.find_vuln_keys(key_list_path, num_of_perms, static_words_val, mapping)    
+        exit()
+
+    if arg.plot:
+        key_list_path = arg.plot[0]
+        static_words_val = int(arg.plot[1])
+
+        PK.plot(key_list_path, static_words_val, mapping)
         exit()
 
     combined_fingerprint = XOR_fingerprints(CONTROLLABLE_FINGERPRINT, UNCONTROLLED_FINGERPRINT)

### 2019-08-12 Experiments/ScallionVsGreenOnion/CreateTargetKeys.py

@@ -1,0 +1,31 @@
+import os
+import sys
+import hashlib
+
+"""
+    Script that is used to create a list of random keys
+    for a benchmark
+"""
+
+def usage():
+    print(f"Usage {__file__} <NUMBER_OF_KEYS>")
+    exit()
+
+def gen_hash():
+    data = os.urandom(10)
+    h = hashlib.md5(data).hexdigest()
+    return h[:16]
+
+if __name__ == "__main__":
+    
+    if len(sys.argv) != 2:
+        usage()
+
+    num_of_keys = int(sys.argv[1])
+
+    for x in range(num_of_keys):
+        print(gen_hash())
+
+
+    
+

### 2019-08-12 Thesis/pages/design.tex
Changes; - Added further discussion to the report
Changes; - Checked through the writing up until the Implementation section

@@
 
-This chapter will discuss and overview of the proposed designs for elements required to answer the research questions. Alternative designs are explained when relevant and design choices are justified
+This chapter will discuss and overview of the proposed designs for elements required to answer the research questions.
+Alternative solutions are explained when relevant alongside a justification of design choices.
 
@@
 
-As each combined key in Trustwords is an exclusive-or of both sides public key (Figure \ref{fig:xor_trustwords} shows this process) the attack is target to a single pair of users and will require recomputation for every attack target.
+As each combined key in Trustwords is an exclusive-or of both sides' public key (Figure \ref{fig:xor_trustwords} shows this process) the attack is designed to target a single pair of users and will require recomputation for every attack target.
 This will be considered when discussing the attack feasibility.
-Each pair is also split into a "Uncontrolled" and "Controlled" key.
-Uncontrolled is the reciever of the communication, and, thus, we cannot control their key.
+Each pair is also split into an "Uncontrolled" or "Controlled" key.
+Uncontrolled is the receiver of the communication, and, thus, we cannot control their key.
 The Controlled key is the one we are attempting to impersonate, and it is assumed that we have the ability to replace the Controlled key with our malicious option.
@@
 
-Figure \ref{fig:nearMatch} shows the process of generating a sub section of the combinations.
-A list of each words matches are generated and then the total number of permutations are generated overall.
+Figure \ref{fig:nearMatch} shows the process of generating a subsection of the combinations.
+A list of each words' matches is generated, followed by the generation of the total number of near-collision keys.
 
@@
 
-To generate an actual list of fingerprints to search for, the near collision words are converted back into hexadecimal and XORed with the uncontrolled key.
-The provides the impersonated key that will produce the desired combined near-collision.
+In order to generate an actual list of fingerprints to search for, the near-collision words are converted back into hexadecimal and XORed with the uncontrolled key.
+This provides the impersonated key that will produce the desired Trustwords.
 Completing this for all of the near-collision permutations will produce a list of fingerprints that can be inserted into a tool designed to hash keys and search for targets.
@@
 
-In summary the, attack steps are:
+In summary, the attack steps are:
 
@@
 
-    \item Use list of similar keys in mass computation of keys to find near-collision keys.
+    \item Use a list of similar keys in the mass computation of keys to find near-collision keys.
 
@@
 \label{sec:metrics}
-One of the first requirements for the attack is quantifying "phonetic similarity".
-This section is looking to provide an answer for the Research Question \ref{goal:phoneticSimilarity}.
+One of the first requirements for the attack is quantifying "phonetic similarity." This section is looking to provide an answer for Research Question \ref{goal:phoneticSimilarity}.
 There are many algorithms currently available to provide this functionality.
@@
 \subsection{Soundex}
-One of the earliest example of a phonetic algorithm is known as Soundex.
+One of the earliest examples of a phonetic algorithm is known as Soundex.
 It is one of the most famous algorithm due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}.
@@
 \cite{patman2001soundex} re-iterates this point but in the context of name matching where Soundex's poor performance was demonstrated.
-Soundex only gained and overall accuracy 36.37\% when matching names within a provided database.
+Soundex only gained and overall accuracy of 36.37\% when matching names within a provided database.
 \end{enumerate}
@@
 Created by Allison Parrish in 2017\cite{parrish2017poetic}, Phonetic vectors is as the name suggests the vectorization of a words phonetics.
-This allows a words phonetics to be represented in vector space.
+This phonetical representation in vector space.
 
@@
 Caverphone as is the case with the vast majority of phonetic algorithms was designed for use with name matching.
-Caverphone was not chosen to similar reasons to that of MRA alongside its optimization for accents in location of New Zealand it was conceived in.
-Therefore, the low level of utilization alongside the unique design features that suggest it may not be suited for this application.
+Caverphone was not chosen to similar reasons to that of MRA alongside its optimization for the New Zealand accent.
+Therefore, the low level of utilization alongside the unique design features that suggests it may not be suited for this application.
 This has, however, not be assessed empirically and thus would be a candidate for further work.
@@
 The chosen framework was OpenCL due to its support for the chosen language (C++) and platform (Linux).
-OpenCL allows the creation of code chunks refereed to as "kernels" to be executed concurrently, this will provide a massive speed increase compare to the sequential nature of the CPU.
+OpenCL allows the creation of code chunks referred to as "kernels" to be executed concurrently, this will provide a massive speed increase compare to the sequential nature of the CPU.
 Technical details will be explained further in Chapter \ref{cha:Implementation}.
@@
 \label{exp:metric}
-In order to answer Research Question \ref{goal:bestMetrics} and reduce the number of metrics to asses in the later rounds, the performance of similarity metrics required comparison.
+In order to answer Research Question \ref{goal:bestMetrics} and reduce the number of metrics to assess in the later rounds, the performance of similarity metrics required comparison.
 The thinning out of metrics is required due to limited resources and, therefore, possible further work could involve repeating this work with a much more varied selection of metrics.
@@
 
-\newpage
+\todo{Link the less than 100,000 point to experiment data}
 
@@
 only fully native speakers are being assessed. The possibility of the 
-worker falsy stating their level of fluency has also been considered. 
+worker falsely stating their level of fluency has also been considered. 
 However, as the worker does not know the purpose for this initial study,
@@
 worker.
-
-\subsubsection{Statistical}
-\textbf{TODO}
 
@@
 In the case of this experiment the users are asked to compare the sound of two word that are visually displayed to them.
+
 This visual aspect is the first point of contact between the participant and the question, followed by mental comparison of the phonetics of the word.
 Therefore, this initial visual contact has the potential to bias the results of the study.
-This has the potential to affect Levenshtein due to the matches never being more than one character different, therefore, resulting in very similar looking words.
+Levenshtein has the potential to be most affected by this due to the matches never being more than one character different, therefore, resulting in very similar looking words.
 The alternative method of running this experiment is to get users to compare audio samples of words, this will force the user to compare just the phonetics of the words and not be influenced by the visual aspects of the pair.
@@
 \subsection{Trustword Attacks}
+\label{sec:exp2_design}
 
@@
 The distribution of these keys will be explained further in Chapter \ref{cha:Experiments}.
-Therefore, if random sets of words were chosen with no restraints there are attacks presented to the user that in a real setting would be infeasible in this context as they are close to a $2^{64}$ attack (4 Words * 16-bits).
+Therefore, if random sets of words were chosen with no restraints there are attacks presented to the user that in a real setting would be infeasible as they are close to a $2^{64}$ attack (4 Words * 16-bits).
 Therefore, the experiment will sample from a list of "vulnerable" keys.
@@
 However, this may not be applicable in this context due to the user being linearly fed an audio stream that they cannot skip to the start or end.
-We believe, however, that attention will also play a part in defining the most important areas of comparison as the hypothesis is that the users attention will be lower in the middle sections of comparison where it peak at the start and end.
+We believe, however, that attention will also play a part in defining the most important areas of comparison.
+The hypothesis is that the users attention will be lower in the middle sections of comparison where it peak at the start and end.
 All these aspects will require empirical evidence to arrive at a conclusion.
@@
 These attacks are ascending in complexity.
-The timeframe for finding a match was decided as 7-days on with attack strengths of 1 GPU/day, 10 GPU/days and 100 GPU/days on a mid range GPU (AMD RX 480 was the example in experiments).
+The timeframe for finding a match was decided as 7-days with attack strengths of 1 GPU/day, 10 GPU/days and 100 GPU/days on a mid range GPU (AMD RX 480 was the example in experiments).
 Due to the long life time of PGP keys, 7 days was chosen as a reasonable length of attack, attackers can just leave the tool and have it compute potential keys for the target without any need for user engagement.
@@
 
-\todo{Talk here about the sampling of vuln keys from keys harvested from PGP key servers.}
-
 \subsubsection{Quality control}
@@
 
-Audio buttons clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:expID}.
-If there are rounds without button clicks, this is a sign of non-attentive users.
+Audio buttons clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:expID} is clicked.
+If there are rounds without button clicks, this is a sign of non-attentiveness.
 The design choice was made to keep this as a result filter, as preventing non-clicks would be a trivial task.
@@
 
-\subsubsection{Statistical}
-\textbf{TODO}
-
 \subsubsection{Considerations}

### 2019-08-12 Thesis/pages/experiments.tex
Changes; - Checked through the writing up until the Implementation section

@@
         \hline
-        Metric & Average Rating  & $\sigma$\\
+        \textbf{Metric} & \textbf{Average Rating}  & \textbf{$\sigma$}\\
         \hline
@@
 
-\subsection{Limitations}
+\subsection*{Considerations}
+As discussed in Section \ref{sec:exp1_considerations} compromises were made in order to fullfil all requirement with a minimized cost.
+Levenshtein's abnormal performance further backs up concerns around the visual aspect biasing the performance of the metric.
+This will have to be considered when interpreting the results.
 
-\textbf{TODO: } Reference back to the decisions made in the design section.
-
-Therefore, even with the discussed issues, the aim of the experiment was to promptly reduce the number of metrics for use later in the project due to a lack of project resources.
-
+Even with the discussed issues, the aim of the experiment was to promptly reduce the number of metrics for use later in the project.
 This experiment, therefore, has achieved that goal of providing three metrics for the subsequent experiment while balancing between accuracy and expenditure.
+The results are also an improvement over informal ad-hoc methods.
 Further work could aim to reproduce this study with the proposed audio based design.
@@
 
-\section{Experiment 2 - Simulated attacks}
+\section{Experiment 2 - Trustword attacks}
 \label{sec:exp2}
-% Demographic
-% Results
+
+Section \ref{sec:exp2_design} explains the design of the experiment. This section will present and discuss the results of the experiment alongside a comparison to relevant literature.
 
@@
 
+\subsection*{Considerations}
 As previously mentioned, the set of recruited participants are more highly educated than the general population.
 This combined with the low average age contributes to an inevitable bias being introduced into the data.
-An assumption can be made that higher education leads to more skillful interaction with computer based systems, this, therefore, with the previous assumption in mind results in the results of this experiment being a best case scenario as the attacks would be expected to be more successful with less able users.
+An assumption can be made that higher education leads to more skillful interaction with computer based systems, this, therefore, with the previous assumption in mind means the results of this experiment being a `best case' scenario.
+The attacks, therefore, would be expected to be more successful on less technical users.
 This, however, requires further research and possible empirical data to determine the validity of the assumption.
 
-\subsection*{Limitations}
 During this study the main task was to perform the authentication ceremony a large number of times.
 In the real-world the ceremony is a secondary task due to it not strictly being required.
-This alongside the potential for users to downplay the possibility of attack leads to the conclusion that these results have limited applicability in a real-world setting.
-The assumption is that these results display the success rate for extremely attentive user where they will make sure to double check with their participant and not just aim to complete the task as quickly as possible.
-This, therefore, means in a real-world setting the success rates could be even higher.
+This alongside the potential for users to downplay the possibility of attack leads to the conclusion that the success rates could be much higher in a real-world setting.
+The assumption is that these results display the success rate for extremely attentive user where they will make sure to double check with their authentication partner multiple times.
+This is opposed to the assumption that the majority of users will aim to complete the task as quickly as possible.
 
-\todo{Include email example of user assuming error over attack}.
-
-\subsection{Comparison to alternative literature}
+\subsection*{Comparison to alternative literature}
 This section will aim to compare the results of the experiment to similar literature.
@@
 They were the only study to use exactly 4 words, but differed on the size of dictionary (1024 words) and how a near-match was calculated.
-Near-matches were a difference in a single word, but without the consideration for similarity, this is the unique aspect considered with this experiment.
+Near-matches were a difference in a single word but without the consideration for similarity, this is the unique aspect considered with this experiment.
 
-However, with those aspect in mind Words received an overall success rating of 3.3\%, considerably lower than that of this study.
-The results presented in this experiment in the worst case presented almost 3 times as many successful attacks.
+However, with those aspect in mind attacks on words encoding received an overall success rating of 3.3\%, considerably lower than that of this study.
+In the worst case our simulated attacks achieved almost 3 times as many successes compared to this study.
 
@@
 As 10/14 words were kept static more comparable to comparable the results to the highest attack strength ``2 static''.
-Therefore, the results presented in this section are substantially higher than this paper, where again the success rate is almost 3 times higher.
+Therefore, there is another 3 fold improvement in the success rates of our simulated attacks.
 
@@
 With it assessing the same wordlist and attack strength as the work by Dechand \textit{et al.}.
-The attack success was 14\% overall, this again compared to the highest attack assessed in the experiment results in a sizeable difference between the attack successes.
+The attack success was 14\% overall, this again compared to the highest attack assessed in the experiment results in a sizeable difference.
 
@@
 With all papers using similarly designed words lists it highly suggests that the deficiencies in Trustwords are the cause for the substantial increase in attack success.
-Furthermore, the consideration for similarity of words that the other papers have not considered could have also resulted in the higher attack success rates.
+Alongside this, the consideration for similarity when calculating near-collisions could have also resulted in the higher attack success rates.
+This aspect is also a unique consideration compared to available literature.
 
@@
         \hline
-        \textbf{Metric} & \textbf{Attack Type} & \textbf{Mean permuations} & \textbf{$\sigma$} & \textbf{Compute Time} \\
+        \textbf{Metric} & & \textbf{Mean matches} & \textbf{$\sigma$} & \textbf{Compute Time} \\
         \hline
@@
         & 1 static & 2822.74 & 23932.39 & ~~18.91 days \\
-        & 2 static & 339.84 & 1730.97 & ~~15.45 days \\
+        & 2 static & 339.84 & 1730.97 & 157.45 days \\
         \hline
@@
 As it can be seen metrics like Levenshtein have a low overall average and would require much more attacker resources to become feasible.
-However, metaphone has attacks that could be computed on average in under 2 days
+On the other hand, Metaphone has attacks that could be computed on average in under 2 days.
+The success rate for this attack type in the second experiment was 11.01\% on average.
+This means on comity hardware commonly found in the home, an attacker could compute a key in less than two days that could succeed more than 10\% of the time.
+This is substantial and highlights on weaknesses in the Trustword system.
 
@@
 These keys were then randomly sampled and used to create the combined key as discussed in Section \ref{sec:pep}.
-100,000 random key pair were as the total sample, and any vulnerable keys for each attack level were recorded.
+100,000 random key pair were created and used as the sample.
+Any vulnerable keys in this set were recorded and used in the experiment.
 
@@
     \caption{Number of vulnerable keys per metric}
+    \label{tab:vulnkeys}
 \end{table}
+
+Table \ref{tab:vulnkeys} contains the breakdown of the number of vulnerable keys.
+The takeaways from this table is the extremely low values for Levenshtein in the higher attacks.
+This is due to the low number of overall matches produced by Levenshtein.
+This means Levenshtein will not be effective in the vast majority of cases.
+However, the standout metric is Metaphone with a good proportion of vulnerable keys, it was the worst performer when assessed against real users but only by as little as 2\%.
+If you take into consideration the number of vulnerable keys detected in the set alongside the average amount near-collision matches in Table \ref{tab:average_perm} Metaphone appears to be the most usable metric overall.
 
@@
 NYSIIS was chosen as the selected metric.
-To expedite the process an initial search was performed for controlled keys that had the highest number of near-collision keys, this was due to the demonstration of the actual generation of keys.
-Producing near-matching keys that have a very small number of potential matches, therefore, adds very little to this demonstration with a large computation cost.
+To expedite the process an initial search was performed for controlled keys that had the highest number of near-collision keys, this was due to the demonstrative purpose of this experiment.
+Producing near-matching keys from key pairs with a very small number of potential matches, adds very little to this demonstration.
 
@@
 This is simply the computation time required to reach the same conclusion on a single 2000 MH/s GPU.
+
 As it can be seen most notable from Table \ref{tab:nysiis2} the generation of the actual Trustwords differs in only 3 characters making it arguably very similar.
-
 When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU is able to achieve around a 28\% success rate when assessed against actual users.
 Even with the least restricted attack type presented in Table \ref{tab:nysiis0} the computation of half a day can provide almost a 10\% success rate when attacking users.
-This means any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of fooling an actual user assuming the success rate is consistent across all keys.
+This means any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of fooling an actual user.

### 2019-08-13 Thesis/pages/conclusion.tex
Changes; - Content for all sections has been produced. First draft of the draft

\chapter{Conclusion}
\label{cha:conclusion}

Overall, the project has demonstrated a potential attack on \pep's implementation of Trustwords. An attack was proposed that utilized phonetic similarity algorithms to exploit the weaknesses in the Trustword dictionary to generate near-collision keys. To achieve this a tool was created to compute a massive number of keys in a concurrent fashion. It was based of a known tool but improves on its key searching performance substantially. The performance of similarity metrics were compared alongside an experiment assessing participants fallibility to the proposed attack. Results showed as much as a 32.05\% success rate for the best attack. The main project aim was to show that the recommend minimum number of four Trustwords was insufficient to provide a basic level of security. We believe we have demonstrated that four Trustwords is too low to provide enough security for general use-case and the minimum provided words should, therefore, be increased.

### 2019-08-13 Thesis/pages/evaluation.tex
Changes; - Content for all sections has been produced. First draft of the draft

\chapter{Evaluation}
This chapter will collate the findings of the paper, evaluate the paper's success against the research questions and discuss potential further work.

\section{Research Question \ref{goal:numberOfTrustwords}}
Research Question \ref{goal:numberOfTrustwords} states \textit{`` Is the recommended minimum number of four Trustwords enough to provide a basic level of security?''}. The paper has investigated this through the creation of an attack and quantification of its success on actual participants. Findings have shown that an attack computed in half a day can have a success rate of about 9.35\%. A user, therefore, could initiate this attack on-mass with hardware present inside the average gaming computer. On the other hand, the best level of attack success was show to be 32.05\%.

Further more, comparison of these results to similar literature show a huge increase in success rates for the attack present in this paper. All alternative literature used a small dictionary of around 1024 words. This, therefore, is highly suggestive that the issue lies with the design of Trustwords as present in the Trustword dictionary are multiple homophones and obscure and unpronounceable words. Therefore, we believe that 4 Trustwords as a minimum has not provided a basic level of security towards users.

\todo{Make this the last question to answer}

\section{Research Question \ref{goal:phoneticSimilarity}}

Research Question \ref{goal:phoneticSimilarity} asks: \textit{``What are the different ways phonetic similarity can be quantified?''}. This paper has discussed a number of metrics used to quantify phonetic similarly (See Section \ref{sec:metrics}). Most metrics were chosen due to their high utilization and occurrence in literature. The only exception to this is the presence of Phonetic Vectors that were chosen due to their unique qualities. This project has succeeded in presenting a comparison of ways to compare similarity metrics. A more in-depth comparison of all possible metrics is a substantial task and would require a project solely dedicated to this task.

\section{Research Question \ref{goal:bestMetrics}}
Research Question \ref{goal:bestMetrics} asks: \textit{``Out of a chosen set of metrics, which are the most effective?''}. 
The paper has presented the performance of a suite of algorithms that are mostly present in utilization and alternative literature. Performance of these metrics were quantified in a direct study that reduced the number down for 5 to 3. These newly selected metrics were then assessed in an attack context with their performance being indirectly quantified. From the historical set of metrics Levenshtein was the best performer with participants rating its matches as substantial better. Levenshtein was also the best performer in the attack context with it having a better average attack success rate that the alternative metrics. This, therefore, this work seems to corroborate work showing that words that are spelt in similar ways tend to share phonetic similarity \cite{hettiarachchi2012sparcl}. This area, however, will require further work to provide more conclusive results on the most effective ways to quantify phonetic similarity.

\section{Research Question \ref{goal:complexity}}
Research Question \ref{goal:complexity}: \textit{``What is the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys was shown in Section \ref{sec:key_gen} where actual keys were generated. Further more the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}. To achieve this the tool GreenOnion was developed where inspiration was gathered from a currently available tool known as Scallion. Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision key GreenOnion can test for.

\section{Research Question \ref{goal:hardwareRequired}}
Research Question \ref{goal:hardwareRequired} states: \textit{``What kind of hardware is required to compute a matching key?''}. Through the computation of actual keys presented in Section \ref{sec:key_gen} and the theoretical calculation into key computation in some cases it has been shown that a single mid-range GPU\footnote{AMD RX-480} can be used to compute actual keys.

\section{Research Question \ref{goal:attackPercentage}}
Research Question \ref{goal:attackPercentage} \textit{``What percentage of attacks successfully deceive a user?''} was shown by the results presented in Section \ref{sec:exp2}. The weakest attack strength and ones that can be computed by a single mid-range GPU for a single week achieved success rate ranging from 9.35\% - 11.01\%. The middle attack involving the use of 10 mid-range GPUs for a week had success rates of 15.20\% - 19.20\%. Finally, the highest attack strength that theoretically involved the use of 100 mid-range GPUs computing for a week has success rates: 24.43\% - 32.05\%. Therefore, showing the number attacks would deceive a set assessed users.

\section{Further work}

\subsection*{Trustword improvements}
The first area of proposed work could be recommendations into how to improve Trustwords backed by empirical evidence. We feel the most promising avenue would be the utilization of Phonetic Vectors unique qualities to identify words of low quality by measuring very low vector distances. For example, present in the dictionary are the words \verb|THERE| and \verb|THEIR|, these could be massively improved upon and could result in a better quality word list. Moreover, utilizing the quantification of dissimilarity could be used to create a dictionary of maximized phonetic distance that could then be assessed in a similar way to detect the feasibility of the attack with the alterations and its success rate against users.

\subsection*{Similar metrics performance}
Another area of further work is the comprehensive assessment of algorithms used to assess phonetic similarity. The algorithms assessed in this work are a very small proportion of potential options. Thus, further work could assess the performance of metrics against each other to determine the one that works best with human models of phonetics. This could be achieved by repeating the improved experiment discussed in Section \ref{exp:metric}. This could be repeated with a very large number of metrics. Other elements for consideration could be age, location and dialect as variables that affect the metrics performance.

\subsection*{GreenOnion optimizations}
Very little work and time was invested into improving the performance of GreenOnion as low-level optimizations are a very time consuming process. A project, therefore, could aim to improve on the performance already recorded in this paper. This could, therefore, improve on the performance of the attack and allow for more successful attacks to be computed in less time.

### 2019-08-13 Thesis/pages/experiments.tex
Changes; - Content for all sections has been produced. First draft of the draft

@@
 \section{Scallion vs GreenOnion}
+\label{sec:SvG}
 This section will compare Scallion and the newly designed GreenOnion ability to search for a large number of potential keys.
@@
 \section{Average number of near-collision keys for each metric}
+\label{sec:averagePerms}
 In order to predict the effectiveness of the attack over a wide variety of keys the number of average near-matches requires computation.
@@
 \section{Distribution of vulnerable keys}
+\label{sec:vulnKeys}
 As discussed in the design of the second experiment (See Section \ref{sec:exp2}) the attacks sampled from a list of `vulnerable keys'.
@@
 \section{Generation of keys}
+\label{sec:key_gen}
 To demonstrate that the the generation of the near collision keys is not only theoretical actual generation of keys was performed using GreenOnion.

### 2019-08-13 Thesis/pages/implementation.tex
Changes; - Content for all sections has been produced. First draft of the draft

@@
 All keys plus the intermediate hash are loaded on the GPU via an OpenCL kernel.
-This kernel is designed to hash the final block, obtain the final fingerprint and checking if the fingerprint is present in the provided list.
+This kernel is designed to hash the final block, obtain the final fingerprint and check if the fingerprint is present in the provided list.
 
@@
 A bloom filter is a probabilistic data structure that allows efficient checking for presence of an element in a set.
-It is effectively a very large array of booleans that state wether an element is present where the position in the array is decided by a pre-defined hashing algorithm.
+It is effectively a very large array of booleans that state wether an element is present.
+The index in the array is decided by a pre-defined hashing algorithm.
 This is repeated a number of times with a number of hashing algorithms ($k$) to populate the array of length ($m$).
@@
 This data structure therefore has a complexity of $O(k)$ regardless of the number of elements in the set.
-This is the only data structure that provides this useful characteristic.
+This is the only data structure that provides this characteristic.
 
@@
 
+\subsubsection*{OpenCL}
+
+In order to process a substantial number of keys in a concurrent fashion OpenCL was required. Figure \ref{fig:opencl} contains the main sections of the code uploaded to the GPU.
+
+\begin{figure}[!h]
+  \centering
+  \input{diagrams/code/OpenKernel.tex}
+  \caption{OpenCL Kernel}
+  \label{fig:opencl}
+\end{figure}
+
+The \verb|<EXPONENT_INCREMENTING_CODE>| will be explained in the next section.
+After the exponent is increment the code produces the final digest by calling \verb|sha1_block(W, H)|.
+The 32-bit left and right sections of the digest are hashed using the MurmurHash algorithm.
+MurmurHash does not exhibit features suitable for secure hashing as it can be trivially reversed.
+Its use-cases include hash based lookups due to its speed and its distributive properties, making it suitable to work well with a bloom filter.
+The hashed values are then checked against the bloom filter array.
+If there is a possible match, the identification value (\verb|0x12345678|) is placed in the first byte of the \verb|outResult| alongside the exponent used to produce the possibly matching PGP key.
+The minimal amount of data returned to the CPU via the \verb|outResult| variable is due to efficiency reasons.
+Use of this memory is computationally expensive, therefore, at every opportunity writing or reading this memory has been avoided.
+
+\begin{figure}[!h]
+  \centering
+  \input{diagrams/code/ExponentIncrement.tex}
+  \caption{Exponent incrementation code}
+  \label{fig:increment}
+\end{figure}
+
+Figure \ref{fig:increment} contains the code used to increment the exponent.
+Due to the exponent being split across two words alongside the bare bones functionality of OpenCL binary operations were chosen as the solution to the incrementation.
+The code utilise the fact that anything XORed with itself becomes zero alongside the fact that XORing a value $a$ with zero provides the result equal to $a$.
+This will allow us to replace values using binary operations.
+The code manipulates the position of values by multiplication or division  of base-16 values, these shift the hex value either left of right respectively.
+Once it is in position the "Mask" is created by XORing with the original value and the new intended value, this stores the changes required to reach the required values, this then applied to each of the words.
+The \verb|get_global_id| command takes the ID from the currently running thread, this allows a different value to be used for each exponent and allows the code to be run concurrently.
+
 \section{First Experiment}
@@
 \begin{figure}[!h]
-\begin{lstlisting}[frame=single, language=Javascript]
-var ALGOS = ["Soundex", "Metaphone", ...];
-var ALGO_SIZES = [763777, 412916, ...];
-
-function updateForm(ss, form) {
-
-  // Obtains a list of the items present on the form
-  formItems = form.getItems();
-
-  // Updates the new values
-  var algo_index = 0;
-  var scale_index = 0;
-  for (var i = 0; i < formItems.length; i++)
-  {
-    if (formItems[i].getType() == "SCALE")
-    {
-      var rnd_index = Math.floor(Math.random() * 
-      ALGO_SIZES[algo_index]) + 1;
-
-      // Obtains the Google Sheets object
-      var sheetname = ALGOS[algo_index];
-      var sheet = ss.getSheetByName(sheetname);
-      var range = sheet.getRange(rnd_index, 1)
-      var values = range.getValues();
-
-      // Re-samples from the connected Google Sheets
-      _updateScaleTitle(formItems[i], values[0]);
-
-      scale_index++;
-
-      // Moves on to the next metric when a group size is
-      // been completed
-      if (scale_index != 0)
-      {
-        if (scale_index % QUESTION_PER_ALGO == 0) {
-            algo_index++;
-        }
-      }
-    }
-  }
-}
-\end{lstlisting}
+  \centering
+  \input{diagrams/code/GoogleAppScript.tex}
 \caption{Section of code from the First Experiment's Google App Script}
@@
 
-Figure \ref{fig:cookie} shows this problem visually. As it can be seen the response cookie $c_2$ is based of the old data of $c$ and, therefore, when returned will remove the progress of $c_1$.
-
+Figure \ref{fig:cookie} shows this problem visually.
+As it can be seen the response cookie $c_2$ is based of the old data of $c$ and, therefore, when returned will remove the progress of $c_1$.
 To keep the complexity of the backend low it was opted to solve this problem by restricting the user via the UI, when a button was clicked all other operations were disabled until a response was received.
@@
 
-I order to collate data for results later in the process state had to be saved.
+In order to collate data for results later in the process state had to be saved.
 One potential solution would be to format the data and save it as a .csv file.

### 2019-08-13 Code/GreenOnion/hash.cpp

@@ -99,7 +99,6 @@ void sha1_test()
     queue.enqueueTask(kernel);
     queue.enqueueReadBuffer(valueBuf, CL_TRUE, 0, sizeof(openclHash), openclHash);
 
-    // Prints out the hash
     std::cout << "OpenCL: ";
     print_hash(openclHash, 5);
 
@@ -108,7 +107,6 @@ void sha1_test()
 
     SHA1((unsigned char*)ibuf, strlen(ibuf), obuf);
 
-    //Prints the has
     std::cout << "Local:  ";
     for (int i = 0; i < 20; ++i) {
         printf("%02x", obuf[i]);
@@ -259,12 +257,6 @@ void compute()
     auto program = BuildProgram(kernel_file_path, context);
     cl::Kernel kernel(program, "key_hash");
 
-    cl::Buffer buf_bitVector(context, CL_MEM_READ_ONLY | CL_MEM_COPY_HOST_PTR ,(sizeof(bool) * BLOOM_SIZE), bf.m_bits, &err);
-    if (err != 0) opencl_handle_error(err, "bit_vector");
-
-    cl::Buffer buf_bitVectorSize(context, CL_MEM_READ_ONLY | CL_MEM_COPY_HOST_PTR, sizeof(long), bloom_bit_vector_size, &err);
-    if (err != 0) opencl_handle_error(err, "bit_vector_size");
-
     while (true)
     {
 
@@ -281,7 +273,11 @@ void compute()
         cl::Buffer buf_currentHash(context, CL_MEM_READ_ONLY | CL_MEM_COPY_HOST_PTR, sizeof(uint) * 5, work.CurrentHash, &err);
         if (err != 0) opencl_handle_error(err, "current_hash");
 
-        
+        cl::Buffer buf_bitVector(context, CL_MEM_READ_ONLY | CL_MEM_COPY_HOST_PTR ,(sizeof(bool) * BLOOM_SIZE), bf.m_bits, &err);
+        if (err != 0) opencl_handle_error(err, "bit_vector");
+
+        cl::Buffer buf_bitVectorSize(context, CL_MEM_READ_ONLY | CL_MEM_COPY_HOST_PTR, sizeof(long), bloom_bit_vector_size, &err);
+        if (err != 0) opencl_handle_error(err, "bit_vector_size");
         
         cl::Buffer buf_out_result(context, CL_MEM_WRITE_ONLY | CL_MEM_HOST_READ_ONLY, resultSize);
 

### 2019-08-13 Thesis/pages/evaluation.tex
Changes; - Typos - Centered diagrams and papers

@@
 All alternative literature used a small dictionary of around 1024 words.
-This, therefore, is highly suggestive that the issue lies with the design of Trustwords as present in the Trustword dictionary are multiple homophones and obscure and unpronounceable words.
+This, therefore, is highly suggestive that the issue lies with the design of Trustwords.
 Therefore, we believe that 4 Trustwords as a minimum has not provided a basic level of security towards users.
@@
 Research Question \ref{goal:phoneticSimilarity} asks: \textit{``What are the different ways phonetic similarity can be quantified?''}.
-This paper has discussed a number of metrics used to quantify phonetic similarly (See Section \ref{sec:metrics}).
+This paper has discussed a number of metrics used to quantify phonetic similarity (See Section \ref{sec:metrics}).
 Most metrics were chosen due to their high utilization and occurrence in literature.
@@
 This project has succeeded in presenting a comparison of ways to compare similarity metrics.
-A more in-depth comparison of all possible metrics is a substantial task and would require a project solely dedicated to this task.
+A more in-depth comparison of all possible metrics is a substantial task and would require a project with this sole dedication.
 
@@
 Research Question \ref{goal:bestMetrics} asks: \textit{``Out of a chosen set of metrics, which are the most effective?''}. 
-The paper has presented the performance of a suite of algorithms that are mostly present in utilization and alternative literature.
-Performance of these metrics were quantified in a direct study that reduced the number down for 5 to 3.
+The paper has presented the performance of a suite of algorithms that are mostly present in alternative literature.
+Performance of these metrics were quantified in a direct study that selected the top three from a set of five.
 These newly selected metrics were then assessed in an attack context with their performance being indirectly quantified.
-From the historical set of metrics Levenshtein was the best performer with participants rating its matches as substantial better.
-Levenshtein was also the best performer in the attack context with it having a better average attack success rate that the alternative metrics.
-This, therefore, this work seems to corroborate work showing that words that are spelt in similar ways tend to share phonetic similarity \cite{hettiarachchi2012sparcl}.
+From the historical set of metrics Levenshtein was the best performer with participants rating its matches as substantially better.
+Levenshtein was also the best performer in the attack context with it having the best average attack success rate.
+This, therefore, seems to corroborate work showing that words with similar spelling tend to share phonetic similarity \cite{hettiarachchi2012sparcl}.
 This area, however, will require further work to provide more conclusive results on the most effective ways to quantify phonetic similarity.
@@
 To achieve this the tool GreenOnion was developed where inspiration was gathered from a currently available tool known as Scallion.
-Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision key GreenOnion can test for.
+Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for.
+
+\todo{Give some tasty stats}
 

### 2019-08-13 .archive/Documents/paper_notes/pages/action_needed.tex
Changes; - Archived some documents - Deleted unused files

\section{Action Needed! Helping Users Find and Complete the
Authentication Ceremony in Signal}

Papers overall aim is to study and then improve the ease and provide motivation for users to complete the authentication ceremony in Signal IM.
The authors apply what they refer to as ``Opinionated design'' to naturally assist users in completing the authentication ceremony.

\textit{``Two recent papers demonstrated that
with some instruction about the ceremony itself [8] or the
importance of comparing keys [20], users can successfully
find and use the authentication ceremony. However, users
still took an inordinate amount of time—over 11 minutes on
average—to find and complete the ceremony [20].''}

That paper showed increases in the number of users actually completing the ceremony.

Work was inspired by a study by Vazirpour et al \textit{``Is that you, Alice? a usability study of the authentication ceremony of secure messaging''} [COMPARE RESULTS]. They also borrow some methodology from this work.

The paper's actual modification are inspired by work from \textit{``When SIGNAL hits the fan: On the usability and security of state-of-the-art secure mobile messaging''}

### 2019-08-13 .archive/Documents/paper_notes/pages/druken_bishop.tex
Changes; - Archived some documents - Deleted unused files

--- 2019-05-25 Papers/Notes_TeX/pages/paper_notes.tex
@@
-\textbf{TODO:} Need to find papers on study of words are a comparative measure.
-
-Lots of research has been done into the secure pairing of devices with minimal human involvement:
-
-\begin{itemize}
-    \item Using Camera Phones for Human-Verifiable Authentication
-    \item Loud and Clear: Human-Verifiable Authentication Based on Audio
-    \item A human-verifiable authentication protocol using visible laser light
-    \item Secure Device Pairing based on a Visual Channel
-    \item NFC
-    \item Physical contact
-\end{itemize}
-
-\textbf{OVERVIEW} 
-\begin{itemize}
-    \item Lots of research performed on E2E applications (Telegram, WhatsApp etc)
-    \item Lots of study into overall representations of fingerprints
-\end{itemize}
-
-\section{Can Unicorns Help Users Compare Crypto Key Fingerprints}
-
-This paper tested 8 different fingerprint representations with 661 different participants.
-All of these representations are testing using compare-and-confirm (basic comparison process for fingerprints) and compare-and-select (select from a list)
-
-\begin{itemize}
-    \item Hexadecimal
-    \item Alternating vowel/consonant
-    \item Words
-    \item Numbers
-    \item Sentences
-    \item OpenSSH visual host key
-    \item Vash
-    \item Unicorns
-\end{itemize}
-
-The paper also emphasises the attention that has been taken to realism in the experimentation stage.
-
-Talks about long term usability issues with public-key crypto and states fingerprints are a main source of the problem. ([28])
-
-There seems to be mixed findings with compare-and-select and compare-and-confirm ([14, 17])
-
-There has been research into OpenSSH fingerprints and how users interact ([19, 24])
-
-Paper chose to target a security level of 160-bits
-
-Papers attack strengths were $2^{40}$, $2^{60}$ and $2^{80}$
-
-Paper states that MTurk users have been shown to be younger and better educated than the general US population ([15])
-
-\subsection{Findings}
-
-\begin{itemize}
-    \item Graphical representations have mixed success rates (with quick comparison times)
-    \item Recommendations not to use \textbf{compare-and-select}
-    \item \textbf{No method} really provided enough security for high risk situations, they recommend removing users from the loop by using smart phone cameras etc
-\end{itemize}
-
-\newpage
-% \section{An Empirical Study of Textual Key-Fingerprint Representations}
-
-% Study involved 1047 participants evaluating 6 different textual representations on MTurk. The study also includes an evaluation into usability.
-
-% The study has an attacker power of around 80 of 112 bits.
-
-% \begin{itemize}
-%     \item Alphanumerical
-%     \item Numerical
-%     \item Words
-%     \item Sentences
-% \end{itemize}
-
-% More mention to decentralised method finding it hard to find adoption such as Web of Trust and Namecoin ([7, 13, 30])
-
-% References as system called CONIKS and others ([24, 39, 27]) that aim to provided a directory of keys
-
-% States that many systems still rely on fingerprint comparison ([17])
-
-% States that the \textbf{hexadecimal} encoding is used in most systems.
-
-% States again that fingerprint comparison is seldom done in practice ([17, 37])
-
-% Studies have shown that users find it difficult to compare long and "meaningless" strings ([19])
-
-% References to other word lists used. PGP Word list [22] and english word list compiled by K.C. Ogden [31]. The Peerio word list is generated from the most common words in english subtitles.
-
-% Interesting recommendation into the use of \textit{scrypt} [34] and \textit{Argon 2} [3] can be used to shorten the fingerprint length.
-These work slowly and a prevent easy computation of pre-images.
-
-% When generating partial-collision fixing the bits at the start and end has been shown a best practice ([17, 37])
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Overall recommendation is to replace \textbf{hexadecimal} with \textbf{sentence} based encoding
-%     \item Findings show that \textbf{hexadecimal} and \textbf{Base32} perform worse than the other alternatives in realistic threat models.
-With over \textbf{10\%} of users failing to detect attacks with these schemes.
-%     \item According to their study, \textbf{words} and \textbf{sentences} we some of the best methods for avoiding attack
-%     \item Words has the second highest usability ratings second to only sentences
-% \end{itemize}
-
-% \newpage
-% \section{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}
-
-% Paper looks into the positives of secondary channels used to authenticate device pairing.
-Such as device fingerprint comparison.
-It also aims to look into the fact that many studies performed do not take into consideration the aspect of human interaction.
-
-% Total of 30 paid participants were recruited where the experiment simulated a P2P payment system.
-
-% They collected:
-% \begin{itemize}
-%     \item Time to completed the associated process
-%     \item Number of security or non-security related errors
-% \end{itemize}
-
-% And quantified using questionnaires:
-% \begin{itemize}
-%     \item Ease of use with the representation
-%     \item Satisfaction with time spent with a method/representation
-%     \item Participant's confidence with the scheme
-% \end{itemize}
-
-% The paper also tested methods:
-% \begin{itemize}
-%     \item Compare and Confirm
-%     \item Compare and Select
-%     \item Compare and Enter
-%     \item Barcode scanning
-% \end{itemize}
-
-% Representations:
-% \begin{itemize}
-%     \item Numerical
-%     \item Alphanumerical
-%     \item Words
-%     \begin{itemize}
-%         \item Dictionary of 1024 words each mapped to 10-bits
-%     \end{itemize}
-%     \item Sentences
-%     \item Images
-%     \item Melodies
-%     \item Sound (Numerical/Alphanumerical)
-% \end{itemize}
-
-% "People are the weakest link in the security chain" [26]
-
-% Mentions a normal channel as a "Dolev-Yao" channel [5]. This is where an attacker can overhead, delete and modify messages.
-
-% Talks about systems that were secure on paper that ended up in practice being miss-handled to reduce security. One example is with the Russian army in WWI [1]
-
-% Bruce Schneier [27] also argues that systems and involves humans therefore often systems are broken due to improper use.
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Showed for \textbf{usability} methods ranked:
-%     \begin{itemize}
-%         \item Comparing-confirm
-%         \item Typing strings
-%         \item Comparing-select
-%         \item Barcode
-%     \end{itemize}
-
-%     \item Showed for \textbf{combined security} and \textbf{usability} methods ranked:
-%     \begin{itemize}
-%         \item Typing strings
-%         \item Barcodes
-%         \item Comparing-confirm
-%         \item Comparing-select
-%     \end{itemize}
-
-%     Showed that the best methods in terms of the SUM score [24] ranked the top 3 as:
-%     \begin{itemize}
-%         \item Numeric(C\&C)          [73.7]
-%         \item Alphanumerical(C\&C)   [72.5]
-%         \item Words (C\&C)           [70.6]
-%     \end{itemize}
-
-%     Numerical had 0\% security failures, Word 3.3\% and Alphanumerical had a high 13.3\%
-
-%     NOTE: This is a very small sample size.
-% \end{itemize}
-
-% \newpage
-% \section{SafeSlinger: An Easy-to-use and Secure Approach for
-% Human Trust Establishment}
-
-% The aim of SafeSlinger is to solve the issue of key exchange.
-They aim to leverage the initial personal contact of people to facilitate trust.
-To solve the issue of people that would never meet they implement a system of "shared acquaintance"
-
-% Talks about issues with decentralised (PGP [42]) and centralised (SSL CA [27, 34]) key exchange.
-
-% "Tim Berners-Lee has called upon security researchers and professionals to design a public key encryption system for the people [11]"
-
-% Only uses \textbf{24-bits} of a SHA-1 hash of all the exchanged information, \textbf{could this be exploited?}
-
-% \newpage
-% \section{A Study of User-Friendly Hash Comparison Schemes}
-
-% The aim of this study is to provide a study on what hash comparison scheme provides the best accuracy and shortest comparison time.
-
-% The paper also proposes new schemes: An extension to Flag and three asian character representations.
-
-% An interesting aspect is the effort put into the study to link characteristics about the participants, i.e.
-gender or age to how well they perform or rate the usability of the scheme.
-In total they had 436 participants.
-
-% Overall they compare:
-% \begin{itemize}
-%     \item Base32
-%     \item English words
-%     \item Random Art
-%     \item Flag
-%     \item T-Flag
-%     \item Flag ext
-%     \item Chinese, Korean, Japanese characters
-% \end{itemize}
-
-% Key phrase: "We did not use hexadecimal digits because they're similar to Base32 and known to be error prone" [NO REFERENCE].
-This is shown in \textit{``An Empirical Study of Textual Key-Fingerprint Representations''} that this isn't true - ``However, our work shows that numeric representations actually perform significantly better than Base32 and is less error prone.''
-
-% They study also considers the comparison of "easy" and "hard" pairs of hashes.
-Hard is where the hashes are designed to be very similar.
-This is designed to provide a base-line (easy) and a worst-case (hard).
-
-% The paper deals with ranges of entropy of 22-28bits.
-
-% Another system that uses word is the Unmanaged Internet Architecture [4]
-
-% States that users make errors when comparing long strings [11]
-
-% Dicussions are also made into the pre-requirements needed for some of these schemes.
-Random-Art needs a colour display and requires a relativly high computational cost to generate a representation.
-Asian characters require unicode or codec support.
-
-% Paper also touches on ``Additional Benefits'' - the paper talks about the ability to verbally describe the scheme, this is so the encoding scheme can be verified using a channel that does not involve a visual feed such as a telephone conversation
-
-% Overall the paper provides a table of requirements for the schemes with the graphical representations requiring a large number of pre-requirements.
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Source, age and gender have no significant impact on the accuracy across the schemes. But younger participants were significantly faster
-%     \item In general, Base32, Random Art, T-Flag and Flag Ext provide fast and accurate comparisons
-%     \item Comprehension of a language when used as a encoding scheme affects the ability to distinguish hard pairs by a significant amount
-% \end{itemize}
-
-% \newpage
-% \section{Usability Analysis of Secure Pairing Methods}
-
-% Paper is aiming to perform a comparative usability evaluation of \textbf{selection methods} of hash comparisons
-
-% This paper is doing this study in the context of secure device pairing in a diffie-hellman type key exchange.
-However, the results of the study could directly apply to that of hash comparison, however, it must be considered that the comparisons here are for \textbf{very} short strings.
-Around 4-digits
-
-% Comparison methods compared:
-% \begin{itemize}
-%     \item Compare-and-Confirm
-%     \item Select-and-Confirm
-%     \item Copy-and-Confirm
-% \end{itemize}
-
-% The paper also compared to methods of passphrase comparison that weren't relevant.
-
-% Paper also included demographical information in the study, with two round of 40 participants in the usability studies.
-
-% Findings:
-
-% Round 1:
-% \begin{itemize}
-%     \item Copy-and-confirm was percieved as hard to use
-%     \item Copy-and-confirm has the lowest fatal error rate but the longest comparison time and lowest percieved usability
-%     \item The schemes reduced fatal error rate as their comparison times rose
-%     \item Copy-and-confirm had issues with user confusion in terms of use
-% \end{itemize}
-
-% In the second round they only decided to continue with
-
-% \begin{itemize}
-%     \item Compare-and-Confirm
-%     \item Select-and-Confirm
-% \end{itemize}
-
-% They dropped Copy-and-confirm due to its high similarity to the other scheme "Copy" that was being used for passphrase sharing
-
-% The second round included some UI changes that were backed up by external research.
-
-% This round the changes performed on the schemes resulted in much lower fatal error rates.
-However, Select-and-confirm had an unacceptable 5\% error rate.
-Compare-and-confirm had 0\% fatal error rate.
-The was an improvment from 20\% to 0\%.
-
-% Both schemes were again percieved as easy to use
-
-% Overall it was shown that compare-and-confirm was the superior choice.
-
-\newpage
-\section{On the Pitfalls of End-to-End Encrypted Communications: A Study of Remote Key-Fingerprint Verification}
-
-Paper compares the fingerprint verification task in the context of Instant messaging E2E The paper is also choosing to focus on the remote vs proximity ways of comparing fingerprints.
-They aim to study the security and usability of human-centred E2E key verification.
-The study ran with 25 participants.
-
-Seems to be the first study of remote code verification study
-
-Study compares Numerical, Image and verbally spoken codes and QR just for proximity alongside all the other alternatives.
-
-The studies main aim to compare remote to proximity, not compare the various methods
-
-The research is split into two sub-goals: Robustness - looks at the FAR and FRR. User experience and perception - System usability, Comfort, Satisfaction and Adaptability
-
-States that numerical is the one of the most common representations, but out of the chosen methods 50\% use numerical and the rest hexadecimal?
-
-They included 3 level of incorrect codes. One char change, one block and the entire fingerprint
-
-Overall Audio was one of the most secure and easiest to use.
-However results for image based comparisons were not controlled in any way due to the author being unable to access the telegram image generation, this means while the other schemes had controlled restraints the image did not.
-Images was rated the worst.
-
-Findings:
-\begin{itemize}
-    \item High False Acceptance Rate (False Negative) for all code verification methods 
-    \item Results point to low usability in remote code verification settings, aside from audio based verification ever scheme has above 20\% False Rejection Rate (False Positive)
-    \item In proximity settings users were able to detect attacks with minimal error rates
-\end{itemize}
-
-\newpage
-
 \section{The drunken bishop: An analysis of the OpenSSH
@@
 \end{itemize}
-
-\newpage
-
-\section{Improving the Robustness of Wireless Device
-Pairing Using Hyphen-Delimited Numeric
-Comparison}
-
-In the context of secure device pairing the paper aims to improve the human interaction with number pairing.
-
-Lots of research has gone into Short Authentication String (SAS) numbers ([14], [10], [4])
-
-The research was peformed on very old devices. Nokia 6030b, very out of date and not reflective of anything around at this time.
-
-Usability study looked into Efficiency, Robustness, General Usability
-
-Strange format of keeping the numbers exactly the same but just placing hyphens in the middle. The authors attempted to remedy this by spacing the experiments with a days gap
-
-Study was performed with 40 participants
-
-Very small number of values tested only 5 overall???
-
-Initial results show promising results for hypen delimitations etc alongside improved user impressions

### 2019-08-13 .archive/Documents/paper_notes/pages/emprical_study.tex
Changes; - Archived some documents - Deleted unused files

\section{An Empirical Study of Textual Key-Fingerprint Representations}

Study involved 1047 participants evaluating 6 different textual representations on MTurk. The study also includes an evaluation into usability.

The study has an attacker power of around 80 of 112 bits.

\begin{itemize}
    \item Alphanumerical
    \item Numerical
    \item Words
    \item Sentences
\end{itemize}

More mention to decentralised method finding it hard to find adoption such as Web of Trust and Namecoin ([7, 13, 30])

References as system called CONIKS and others ([24, 39, 27]) that aim to provided a directory of keys

States that many systems still rely on fingerprint comparison ([17])

States that the \textbf{hexadecimal} encoding is used in most systems.

States again that fingerprint comparison is seldom done in practice ([17, 37])

Studies have shown that users find it difficult to compare long and "meaningless" strings ([19])

References to other word lists used. PGP Word list [22] and english word list compiled by K.C. Ogden [31]. The Peerio word list is generated from the most common words in english subtitles.

Interesting recommendation into the use of \textit{scrypt} [34] and \textit{Argon 2} [3] can be used to shorten the fingerprint length. These work slowly and a prevent easy computation of pre-images.

When generating partial-collision fixing the bits at the start and end has been shown a best practice ([17, 37])

\subsection{Findings}
\begin{itemize}
    \item Overall recommendation is to replace \textbf{hexadecimal} with \textbf{sentence} based encoding
    \item Findings show that \textbf{hexadecimal} and \textbf{Base32} perform worse than the other alternatives in realistic threat models. With over \textbf{10\%} of users failing to detect attacks with these schemes.
    \item According to their study, \textbf{words} and \textbf{sentences} we some of the best methods for avoiding attack
    \item Words has the second highest usability ratings second to only sentences
\end{itemize}

### 2019-08-13 .archive/Documents/paper_notes/pages/pitfalls_of_e2e.tex
Changes; - Archived some documents - Deleted unused files

--- 2019-05-25 Papers/Notes_TeX/pages/paper_notes.tex
@@
-\textbf{TODO:} Need to find papers on study of words are a comparative measure.
-
-Lots of research has been done into the secure pairing of devices with minimal human involvement:
-
-\begin{itemize}
-    \item Using Camera Phones for Human-Verifiable Authentication
-    \item Loud and Clear: Human-Verifiable Authentication Based on Audio
-    \item A human-verifiable authentication protocol using visible laser light
-    \item Secure Device Pairing based on a Visual Channel
-    \item NFC
-    \item Physical contact
-\end{itemize}
-
-\textbf{OVERVIEW} 
-\begin{itemize}
-    \item Lots of research performed on E2E applications (Telegram, WhatsApp etc)
-    \item Lots of study into overall representations of fingerprints
-\end{itemize}
-
-\section{Can Unicorns Help Users Compare Crypto Key Fingerprints}
-
-This paper tested 8 different fingerprint representations with 661 different participants.
-All of these representations are testing using compare-and-confirm (basic comparison process for fingerprints) and compare-and-select (select from a list)
-
-\begin{itemize}
-    \item Hexadecimal
-    \item Alternating vowel/consonant
-    \item Words
-    \item Numbers
-    \item Sentences
-    \item OpenSSH visual host key
-    \item Vash
-    \item Unicorns
-\end{itemize}
-
-The paper also emphasises the attention that has been taken to realism in the experimentation stage.
-
-Talks about long term usability issues with public-key crypto and states fingerprints are a main source of the problem. ([28])
-
-There seems to be mixed findings with compare-and-select and compare-and-confirm ([14, 17])
-
-There has been research into OpenSSH fingerprints and how users interact ([19, 24])
-
-Paper chose to target a security level of 160-bits
-
-Papers attack strengths were $2^{40}$, $2^{60}$ and $2^{80}$
-
-Paper states that MTurk users have been shown to be younger and better educated than the general US population ([15])
-
-\subsection{Findings}
-
-\begin{itemize}
-    \item Graphical representations have mixed success rates (with quick comparison times)
-    \item Recommendations not to use \textbf{compare-and-select}
-    \item \textbf{No method} really provided enough security for high risk situations, they recommend removing users from the loop by using smart phone cameras etc
-\end{itemize}
-
-\newpage
-% \section{An Empirical Study of Textual Key-Fingerprint Representations}
-
-% Study involved 1047 participants evaluating 6 different textual representations on MTurk. The study also includes an evaluation into usability.
-
-% The study has an attacker power of around 80 of 112 bits.
-
-% \begin{itemize}
-%     \item Alphanumerical
-%     \item Numerical
-%     \item Words
-%     \item Sentences
-% \end{itemize}
-
-% More mention to decentralised method finding it hard to find adoption such as Web of Trust and Namecoin ([7, 13, 30])
-
-% References as system called CONIKS and others ([24, 39, 27]) that aim to provided a directory of keys
-
-% States that many systems still rely on fingerprint comparison ([17])
-
-% States that the \textbf{hexadecimal} encoding is used in most systems.
-
-% States again that fingerprint comparison is seldom done in practice ([17, 37])
-
-% Studies have shown that users find it difficult to compare long and "meaningless" strings ([19])
-
-% References to other word lists used. PGP Word list [22] and english word list compiled by K.C. Ogden [31]. The Peerio word list is generated from the most common words in english subtitles.
-
-% Interesting recommendation into the use of \textit{scrypt} [34] and \textit{Argon 2} [3] can be used to shorten the fingerprint length.
-These work slowly and a prevent easy computation of pre-images.
-
-% When generating partial-collision fixing the bits at the start and end has been shown a best practice ([17, 37])
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Overall recommendation is to replace \textbf{hexadecimal} with \textbf{sentence} based encoding
-%     \item Findings show that \textbf{hexadecimal} and \textbf{Base32} perform worse than the other alternatives in realistic threat models.
-With over \textbf{10\%} of users failing to detect attacks with these schemes.
-%     \item According to their study, \textbf{words} and \textbf{sentences} we some of the best methods for avoiding attack
-%     \item Words has the second highest usability ratings second to only sentences
-% \end{itemize}
-
-% \newpage
-% \section{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}
-
-% Paper looks into the positives of secondary channels used to authenticate device pairing.
-Such as device fingerprint comparison.
-It also aims to look into the fact that many studies performed do not take into consideration the aspect of human interaction.
-
-% Total of 30 paid participants were recruited where the experiment simulated a P2P payment system.
-
-% They collected:
-% \begin{itemize}
-%     \item Time to completed the associated process
-%     \item Number of security or non-security related errors
-% \end{itemize}
-
-% And quantified using questionnaires:
-% \begin{itemize}
-%     \item Ease of use with the representation
-%     \item Satisfaction with time spent with a method/representation
-%     \item Participant's confidence with the scheme
-% \end{itemize}
-
-% The paper also tested methods:
-% \begin{itemize}
-%     \item Compare and Confirm
-%     \item Compare and Select
-%     \item Compare and Enter
-%     \item Barcode scanning
-% \end{itemize}
-
-% Representations:
-% \begin{itemize}
-%     \item Numerical
-%     \item Alphanumerical
-%     \item Words
-%     \begin{itemize}
-%         \item Dictionary of 1024 words each mapped to 10-bits
-%     \end{itemize}
-%     \item Sentences
-%     \item Images
-%     \item Melodies
-%     \item Sound (Numerical/Alphanumerical)
-% \end{itemize}
-
-% "People are the weakest link in the security chain" [26]
-
-% Mentions a normal channel as a "Dolev-Yao" channel [5]. This is where an attacker can overhead, delete and modify messages.
-
-% Talks about systems that were secure on paper that ended up in practice being miss-handled to reduce security. One example is with the Russian army in WWI [1]
-
-% Bruce Schneier [27] also argues that systems and involves humans therefore often systems are broken due to improper use.
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Showed for \textbf{usability} methods ranked:
-%     \begin{itemize}
-%         \item Comparing-confirm
-%         \item Typing strings
-%         \item Comparing-select
-%         \item Barcode
-%     \end{itemize}
-
-%     \item Showed for \textbf{combined security} and \textbf{usability} methods ranked:
-%     \begin{itemize}
-%         \item Typing strings
-%         \item Barcodes
-%         \item Comparing-confirm
-%         \item Comparing-select
-%     \end{itemize}
-
-%     Showed that the best methods in terms of the SUM score [24] ranked the top 3 as:
-%     \begin{itemize}
-%         \item Numeric(C\&C)          [73.7]
-%         \item Alphanumerical(C\&C)   [72.5]
-%         \item Words (C\&C)           [70.6]
-%     \end{itemize}
-
-%     Numerical had 0\% security failures, Word 3.3\% and Alphanumerical had a high 13.3\%
-
-%     NOTE: This is a very small sample size.
-% \end{itemize}
-
-% \newpage
-% \section{SafeSlinger: An Easy-to-use and Secure Approach for
-% Human Trust Establishment}
-
-% The aim of SafeSlinger is to solve the issue of key exchange.
-They aim to leverage the initial personal contact of people to facilitate trust.
-To solve the issue of people that would never meet they implement a system of "shared acquaintance"
-
-% Talks about issues with decentralised (PGP [42]) and centralised (SSL CA [27, 34]) key exchange.
-
-% "Tim Berners-Lee has called upon security researchers and professionals to design a public key encryption system for the people [11]"
-
-% Only uses \textbf{24-bits} of a SHA-1 hash of all the exchanged information, \textbf{could this be exploited?}
-
-% \newpage
-% \section{A Study of User-Friendly Hash Comparison Schemes}
-
-% The aim of this study is to provide a study on what hash comparison scheme provides the best accuracy and shortest comparison time.
-
-% The paper also proposes new schemes: An extension to Flag and three asian character representations.
-
-% An interesting aspect is the effort put into the study to link characteristics about the participants, i.e.
-gender or age to how well they perform or rate the usability of the scheme.
-In total they had 436 participants.
-
-% Overall they compare:
-% \begin{itemize}
-%     \item Base32
-%     \item English words
-%     \item Random Art
-%     \item Flag
-%     \item T-Flag
-%     \item Flag ext
-%     \item Chinese, Korean, Japanese characters
-% \end{itemize}
-
-% Key phrase: "We did not use hexadecimal digits because they're similar to Base32 and known to be error prone" [NO REFERENCE].
-This is shown in \textit{``An Empirical Study of Textual Key-Fingerprint Representations''} that this isn't true - ``However, our work shows that numeric representations actually perform significantly better than Base32 and is less error prone.''
-
-% They study also considers the comparison of "easy" and "hard" pairs of hashes.
-Hard is where the hashes are designed to be very similar.
-This is designed to provide a base-line (easy) and a worst-case (hard).
-
-% The paper deals with ranges of entropy of 22-28bits.
-
-% Another system that uses word is the Unmanaged Internet Architecture [4]
-
-% States that users make errors when comparing long strings [11]
-
-% Dicussions are also made into the pre-requirements needed for some of these schemes.
-Random-Art needs a colour display and requires a relativly high computational cost to generate a representation.
-Asian characters require unicode or codec support.
-
-% Paper also touches on ``Additional Benefits'' - the paper talks about the ability to verbally describe the scheme, this is so the encoding scheme can be verified using a channel that does not involve a visual feed such as a telephone conversation
-
-% Overall the paper provides a table of requirements for the schemes with the graphical representations requiring a large number of pre-requirements.
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Source, age and gender have no significant impact on the accuracy across the schemes. But younger participants were significantly faster
-%     \item In general, Base32, Random Art, T-Flag and Flag Ext provide fast and accurate comparisons
-%     \item Comprehension of a language when used as a encoding scheme affects the ability to distinguish hard pairs by a significant amount
-% \end{itemize}
-
-% \newpage
-% \section{Usability Analysis of Secure Pairing Methods}
-
-% Paper is aiming to perform a comparative usability evaluation of \textbf{selection methods} of hash comparisons
-
-% This paper is doing this study in the context of secure device pairing in a diffie-hellman type key exchange.
-However, the results of the study could directly apply to that of hash comparison, however, it must be considered that the comparisons here are for \textbf{very} short strings.
-Around 4-digits
-
-% Comparison methods compared:
-% \begin{itemize}
-%     \item Compare-and-Confirm
-%     \item Select-and-Confirm
-%     \item Copy-and-Confirm
-% \end{itemize}
-
-% The paper also compared to methods of passphrase comparison that weren't relevant.
-
-% Paper also included demographical information in the study, with two round of 40 participants in the usability studies.
-
-% Findings:
-
-% Round 1:
-% \begin{itemize}
-%     \item Copy-and-confirm was percieved as hard to use
-%     \item Copy-and-confirm has the lowest fatal error rate but the longest comparison time and lowest percieved usability
-%     \item The schemes reduced fatal error rate as their comparison times rose
-%     \item Copy-and-confirm had issues with user confusion in terms of use
-% \end{itemize}
-
-% In the second round they only decided to continue with
-
-% \begin{itemize}
-%     \item Compare-and-Confirm
-%     \item Select-and-Confirm
-% \end{itemize}
-
-% They dropped Copy-and-confirm due to its high similarity to the other scheme "Copy" that was being used for passphrase sharing
-
-% The second round included some UI changes that were backed up by external research.
-
-% This round the changes performed on the schemes resulted in much lower fatal error rates.
-However, Select-and-confirm had an unacceptable 5\% error rate.
-Compare-and-confirm had 0\% fatal error rate.
-The was an improvment from 20\% to 0\%.
-
-% Both schemes were again percieved as easy to use
-
-% Overall it was shown that compare-and-confirm was the superior choice.
-
-\newpage
 \section{On the Pitfalls of End-to-End Encrypted Communications: A Study of Remote Key-Fingerprint Verification}
@@
 \end{itemize}
-
-\newpage
-
-\section{The drunken bishop: An analysis of the OpenSSH
-fingerprint visualization algorithm}
-
-The aim of this research is to study the OpenSSH Visual Host Key.
-The authors claim that the scheme was heuristically designed and has very little backing in terms of formal research, this paper aims to create a foundation for this research.
-
-OpenSSH uses MD5 to generate a 128-bit fingerprint of the Server's key, this is then split into 64 2-bit pairs.
-These are then traversed byte wise in a right to left over the bit pairs.
-Each pair defines the direction of travel.
-If the snake reaches a position multiple times a pre define character is added depending on the number of visits (for example, 6 times == "B")
-
-The paper also discusses ways to create collisions:
-
-In conclusive results and more of an inital PoC
-
-\begin{itemize}
-    \item Brute force
-    \item Graph theory
-    \item Brute forcing a visual set
-\end{itemize}
-
-\newpage
-
-\section{Improving the Robustness of Wireless Device
-Pairing Using Hyphen-Delimited Numeric
-Comparison}
-
-In the context of secure device pairing the paper aims to improve the human interaction with number pairing.
-
-Lots of research has gone into Short Authentication String (SAS) numbers ([14], [10], [4])
-
-The research was peformed on very old devices. Nokia 6030b, very out of date and not reflective of anything around at this time.
-
-Usability study looked into Efficiency, Robustness, General Usability
-
-Strange format of keeping the numbers exactly the same but just placing hyphens in the middle. The authors attempted to remedy this by spacing the experiments with a days gap
-
-Study was performed with 40 participants
-
-Very small number of values tested only 5 overall???
-
-Initial results show promising results for hypen delimitations etc alongside improved user impressions

### 2019-08-13 .archive/Documents/paper_notes/pages/safeslinger.tex
Changes; - Archived some documents - Deleted unused files

\section{SafeSlinger: An Easy-to-use and Secure Approach for
Human Trust Establishment}

The aim of SafeSlinger is to solve the issue of key exchange. They aim to leverage the initial personal contact of people to facilitate trust. To solve the issue of people that would never meet they implement a system of "shared acquaintance"

Talks about issues with decentralised (PGP [42]) and centralised (SSL CA [27, 34]) key exchange.

"Tim Berners-Lee has called upon security researchers and professionals to design a public key encryption system for the people [11]"

Only uses \textbf{24-bits} of a SHA-1 hash of all the exchanged information, \textbf{could this be exploited?}

### 2019-08-13 .archive/Documents/paper_notes/pages/wiretapping.tex
Changes; - Archived some documents - Deleted unused files

--- 2019-05-25 Papers/Notes_TeX/pages/paper_notes.tex
@@
-\textbf{TODO:} Need to find papers on study of words are a comparative measure.
+\section{Wiretapping via Mimicry: Short Voice Imitation
+Man-in-the-Middle Attacks on Crypto Phones}
 
-Lots of research has been done into the secure pairing of devices with minimal human involvement:
+The aim of the paper is to simulate a MITM attack on SAS and the voice channel used to authenticate
 
-\begin{itemize}
-    \item Using Camera Phones for Human-Verifiable Authentication
-    \item Loud and Clear: Human-Verifiable Authentication Based on Audio
-    \item A human-verifiable authentication protocol using visible laser light
-    \item Secure Device Pairing based on a Visual Channel
-    \item NFC
-    \item Physical contact
-\end{itemize}
+``Short voice reordering attack'' builds arbitrary SAS
+strings in a victim’s voice by reordering previously eavesdropped SAS strings spoken by the victim.
 
-\textbf{OVERVIEW} 
-\begin{itemize}
-    \item Lots of research performed on E2E applications (Telegram, WhatsApp etc)
-    \item Lots of study into overall representations of fingerprints
-\end{itemize}
+called the ``short voice morphing attack;;, builds arbitrary SAS strings in a victim’s voice from a few previously eavesdropped sentences (less
+than 3 minutes) spoken by the victim.
 
-\section{Can Unicorns Help Users Compare Crypto Key Fingerprints}
+Is attempting to prove the assumption that "Mallory" being in control of the channel can controls Communications but cannot impersonate alice or bob.
 
-This paper tested 8 different fingerprint representations with 661 different participants.
-All of these representations are testing using compare-and-confirm (basic comparison process for fingerprints) and compare-and-select (select from a list)
-
-\begin{itemize}
-    \item Hexadecimal
-    \item Alternating vowel/consonant
-    \item Words
-    \item Numbers
-    \item Sentences
-    \item OpenSSH visual host key
-    \item Vash
-    \item Unicorns
-\end{itemize}
-
-The paper also emphasises the attention that has been taken to realism in the experimentation stage.
-
-Talks about long term usability issues with public-key crypto and states fingerprints are a main source of the problem. ([28])
-
-There seems to be mixed findings with compare-and-select and compare-and-confirm ([14, 17])
-
-There has been research into OpenSSH fingerprints and how users interact ([19, 24])
-
-Paper chose to target a security level of 160-bits
-
-Papers attack strengths were $2^{40}$, $2^{60}$ and $2^{80}$
-
-Paper states that MTurk users have been shown to be younger and better educated than the general US population ([15])
-
-\subsection{Findings}
-
-\begin{itemize}
-    \item Graphical representations have mixed success rates (with quick comparison times)
-    \item Recommendations not to use \textbf{compare-and-select}
-    \item \textbf{No method} really provided enough security for high risk situations, they recommend removing users from the loop by using smart phone cameras etc
-\end{itemize}
-
-\newpage
-% \section{An Empirical Study of Textual Key-Fingerprint Representations}
-
-% Study involved 1047 participants evaluating 6 different textual representations on MTurk. The study also includes an evaluation into usability.
-
-% The study has an attacker power of around 80 of 112 bits.
-
-% \begin{itemize}
-%     \item Alphanumerical
-%     \item Numerical
-%     \item Words
-%     \item Sentences
-% \end{itemize}
-
-% More mention to decentralised method finding it hard to find adoption such as Web of Trust and Namecoin ([7, 13, 30])
-
-% References as system called CONIKS and others ([24, 39, 27]) that aim to provided a directory of keys
-
-% States that many systems still rely on fingerprint comparison ([17])
-
-% States that the \textbf{hexadecimal} encoding is used in most systems.
-
-% States again that fingerprint comparison is seldom done in practice ([17, 37])
-
-% Studies have shown that users find it difficult to compare long and "meaningless" strings ([19])
-
-% References to other word lists used. PGP Word list [22] and english word list compiled by K.C. Ogden [31]. The Peerio word list is generated from the most common words in english subtitles.
-
-% Interesting recommendation into the use of \textit{scrypt} [34] and \textit{Argon 2} [3] can be used to shorten the fingerprint length.
-These work slowly and a prevent easy computation of pre-images.
-
-% When generating partial-collision fixing the bits at the start and end has been shown a best practice ([17, 37])
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Overall recommendation is to replace \textbf{hexadecimal} with \textbf{sentence} based encoding
-%     \item Findings show that \textbf{hexadecimal} and \textbf{Base32} perform worse than the other alternatives in realistic threat models.
-With over \textbf{10\%} of users failing to detect attacks with these schemes.
-%     \item According to their study, \textbf{words} and \textbf{sentences} we some of the best methods for avoiding attack
-%     \item Words has the second highest usability ratings second to only sentences
-% \end{itemize}
-
-% \newpage
-% \section{Usability and Security of Out-Of-Band Channels in Secure Device Pairing Protocols}
-
-% Paper looks into the positives of secondary channels used to authenticate device pairing.
-Such as device fingerprint comparison.
-It also aims to look into the fact that many studies performed do not take into consideration the aspect of human interaction.
-
-% Total of 30 paid participants were recruited where the experiment simulated a P2P payment system.
-
-% They collected:
-% \begin{itemize}
-%     \item Time to completed the associated process
-%     \item Number of security or non-security related errors
-% \end{itemize}
-
-% And quantified using questionnaires:
-% \begin{itemize}
-%     \item Ease of use with the representation
-%     \item Satisfaction with time spent with a method/representation
-%     \item Participant's confidence with the scheme
-% \end{itemize}
-
-% The paper also tested methods:
-% \begin{itemize}
-%     \item Compare and Confirm
-%     \item Compare and Select
-%     \item Compare and Enter
-%     \item Barcode scanning
-% \end{itemize}
-
-% Representations:
-% \begin{itemize}
-%     \item Numerical
-%     \item Alphanumerical
-%     \item Words
-%     \begin{itemize}
-%         \item Dictionary of 1024 words each mapped to 10-bits
-%     \end{itemize}
-%     \item Sentences
-%     \item Images
-%     \item Melodies
-%     \item Sound (Numerical/Alphanumerical)
-% \end{itemize}
-
-% "People are the weakest link in the security chain" [26]
-
-% Mentions a normal channel as a "Dolev-Yao" channel [5]. This is where an attacker can overhead, delete and modify messages.
-
-% Talks about systems that were secure on paper that ended up in practice being miss-handled to reduce security. One example is with the Russian army in WWI [1]
-
-% Bruce Schneier [27] also argues that systems and involves humans therefore often systems are broken due to improper use.
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Showed for \textbf{usability} methods ranked:
-%     \begin{itemize}
-%         \item Comparing-confirm
-%         \item Typing strings
-%         \item Comparing-select
-%         \item Barcode
-%     \end{itemize}
-
-%     \item Showed for \textbf{combined security} and \textbf{usability} methods ranked:
-%     \begin{itemize}
-%         \item Typing strings
-%         \item Barcodes
-%         \item Comparing-confirm
-%         \item Comparing-select
-%     \end{itemize}
-
-%     Showed that the best methods in terms of the SUM score [24] ranked the top 3 as:
-%     \begin{itemize}
-%         \item Numeric(C\&C)          [73.7]
-%         \item Alphanumerical(C\&C)   [72.5]
-%         \item Words (C\&C)           [70.6]
-%     \end{itemize}
-
-%     Numerical had 0\% security failures, Word 3.3\% and Alphanumerical had a high 13.3\%
-
-%     NOTE: This is a very small sample size.
-% \end{itemize}
-
-% \newpage
-% \section{SafeSlinger: An Easy-to-use and Secure Approach for
-% Human Trust Establishment}
-
-% The aim of SafeSlinger is to solve the issue of key exchange.
-They aim to leverage the initial personal contact of people to facilitate trust.
-To solve the issue of people that would never meet they implement a system of "shared acquaintance"
-
-% Talks about issues with decentralised (PGP [42]) and centralised (SSL CA [27, 34]) key exchange.
-
-% "Tim Berners-Lee has called upon security researchers and professionals to design a public key encryption system for the people [11]"
-
-% Only uses \textbf{24-bits} of a SHA-1 hash of all the exchanged information, \textbf{could this be exploited?}
-
-% \newpage
-% \section{A Study of User-Friendly Hash Comparison Schemes}
-
-% The aim of this study is to provide a study on what hash comparison scheme provides the best accuracy and shortest comparison time.
-
-% The paper also proposes new schemes: An extension to Flag and three asian character representations.
-
-% An interesting aspect is the effort put into the study to link characteristics about the participants, i.e.
-gender or age to how well they perform or rate the usability of the scheme.
-In total they had 436 participants.
-
-% Overall they compare:
-% \begin{itemize}
-%     \item Base32
-%     \item English words
-%     \item Random Art
-%     \item Flag
-%     \item T-Flag
-%     \item Flag ext
-%     \item Chinese, Korean, Japanese characters
-% \end{itemize}
-
-% Key phrase: "We did not use hexadecimal digits because they're similar to Base32 and known to be error prone" [NO REFERENCE].
-This is shown in \textit{``An Empirical Study of Textual Key-Fingerprint Representations''} that this isn't true - ``However, our work shows that numeric representations actually perform significantly better than Base32 and is less error prone.''
-
-% They study also considers the comparison of "easy" and "hard" pairs of hashes.
-Hard is where the hashes are designed to be very similar.
-This is designed to provide a base-line (easy) and a worst-case (hard).
-
-% The paper deals with ranges of entropy of 22-28bits.
-
-% Another system that uses word is the Unmanaged Internet Architecture [4]
-
-% States that users make errors when comparing long strings [11]
-
-% Dicussions are also made into the pre-requirements needed for some of these schemes.
-Random-Art needs a colour display and requires a relativly high computational cost to generate a representation.
-Asian characters require unicode or codec support.
-
-% Paper also touches on ``Additional Benefits'' - the paper talks about the ability to verbally describe the scheme, this is so the encoding scheme can be verified using a channel that does not involve a visual feed such as a telephone conversation
-
-% Overall the paper provides a table of requirements for the schemes with the graphical representations requiring a large number of pre-requirements.
-
-% \subsection{Findings}
-% \begin{itemize}
-%     \item Source, age and gender have no significant impact on the accuracy across the schemes. But younger participants were significantly faster
-%     \item In general, Base32, Random Art, T-Flag and Flag Ext provide fast and accurate comparisons
-%     \item Comprehension of a language when used as a encoding scheme affects the ability to distinguish hard pairs by a significant amount
-% \end{itemize}
-
-% \newpage
-% \section{Usability Analysis of Secure Pairing Methods}
-
-% Paper is aiming to perform a comparative usability evaluation of \textbf{selection methods} of hash comparisons
-
-% This paper is doing this study in the context of secure device pairing in a diffie-hellman type key exchange.
-However, the results of the study could directly apply to that of hash comparison, however, it must be considered that the comparisons here are for \textbf{very} short strings.
-Around 4-digits
-
-% Comparison methods compared:
-% \begin{itemize}
-%     \item Compare-and-Confirm
-%     \item Select-and-Confirm
-%     \item Copy-and-Confirm
-% \end{itemize}
-
-% The paper also compared to methods of passphrase comparison that weren't relevant.
-
-% Paper also included demographical information in the study, with two round of 40 participants in the usability studies.
-
-% Findings:
-
-% Round 1:
-% \begin{itemize}
-%     \item Copy-and-confirm was percieved as hard to use
-%     \item Copy-and-confirm has the lowest fatal error rate but the longest comparison time and lowest percieved usability
-%     \item The schemes reduced fatal error rate as their comparison times rose
-%     \item Copy-and-confirm had issues with user confusion in terms of use
-% \end{itemize}
-
-% In the second round they only decided to continue with
-
-% \begin{itemize}
-%     \item Compare-and-Confirm
-%     \item Select-and-Confirm
-% \end{itemize}
-
-% They dropped Copy-and-confirm due to its high similarity to the other scheme "Copy" that was being used for passphrase sharing
-
-% The second round included some UI changes that were backed up by external research.
-
-% This round the changes performed on the schemes resulted in much lower fatal error rates.
-However, Select-and-confirm had an unacceptable 5\% error rate.
-Compare-and-confirm had 0\% fatal error rate.
-The was an improvment from 20\% to 0\%.
-
-% Both schemes were again percieved as easy to use
-
-% Overall it was shown that compare-and-confirm was the superior choice.
-
-\newpage
-\section{On the Pitfalls of End-to-End Encrypted Communications: A Study of Remote Key-Fingerprint Verification}
-
-Paper compares the fingerprint verification task in the context of Instant messaging E2E The paper is also choosing to focus on the remote vs proximity ways of comparing fingerprints.
-They aim to study the security and usability of human-centred E2E key verification.
-The study ran with 25 participants.
-
-Seems to be the first study of remote code verification study
-
-Study compares Numerical, Image and verbally spoken codes and QR just for proximity alongside all the other alternatives.
-
-The studies main aim to compare remote to proximity, not compare the various methods
-
-The research is split into two sub-goals: Robustness - looks at the FAR and FRR. User experience and perception - System usability, Comfort, Satisfaction and Adaptability
-
-States that numerical is the one of the most common representations, but out of the chosen methods 50\% use numerical and the rest hexadecimal?
-
-They included 3 level of incorrect codes. One char change, one block and the entire fingerprint
-
-Overall Audio was one of the most secure and easiest to use.
-However results for image based comparisons were not controlled in any way due to the author being unable to access the telegram image generation, this means while the other schemes had controlled restraints the image did not.
-Images was rated the worst.
+Paper showed, that it is very possible to successfully attack SAS strings. Authors do comment on their difficulty in generating longer strings i.e. longer hash digests
 
@@
 \begin{itemize}
-    \item High False Acceptance Rate (False Negative) for all code verification methods 
-    \item Results point to low usability in remote code verification settings, aside from audio based verification ever scheme has above 20\% False Rejection Rate (False Positive)
-    \item In proximity settings users were able to detect attacks with minimal error rates
+    \item Success is more likely with shorter strings
+    \item Showed that with 80\% success participants can distinguish a different voice from a familiar voice
+    \item Their morphed attack was overall just above 50\% however, their reordering attack had almost 80\% success rate
+    \item Both attacks were above the baseline of a different voice. I.e. the case of Mallory just replacing the audio with their voice.
 \end{itemize}
-
-\newpage
-
-\section{The drunken bishop: An analysis of the OpenSSH
-fingerprint visualization algorithm}
-
-The aim of this research is to study the OpenSSH Visual Host Key.
-The authors claim that the scheme was heuristically designed and has very little backing in terms of formal research, this paper aims to create a foundation for this research.
-
-OpenSSH uses MD5 to generate a 128-bit fingerprint of the Server's key, this is then split into 64 2-bit pairs.
-These are then traversed byte wise in a right to left over the bit pairs.
-Each pair defines the direction of travel.
-If the snake reaches a position multiple times a pre define character is added depending on the number of visits (for example, 6 times == "B")
-
-The paper also discusses ways to create collisions:
-
-In conclusive results and more of an inital PoC
-
-\begin{itemize}
-    \item Brute force
-    \item Graph theory
-    \item Brute forcing a visual set
-\end{itemize}
-
-\newpage
-
-\section{Improving the Robustness of Wireless Device
-Pairing Using Hyphen-Delimited Numeric
-Comparison}
-
-In the context of secure device pairing the paper aims to improve the human interaction with number pairing.
-
-Lots of research has gone into Short Authentication String (SAS) numbers ([14], [10], [4])
-
-The research was peformed on very old devices. Nokia 6030b, very out of date and not reflective of anything around at this time.
-
-Usability study looked into Efficiency, Robustness, General Usability
-
-Strange format of keeping the numbers exactly the same but just placing hyphens in the middle. The authors attempted to remedy this by spacing the experiments with a days gap
-
-Study was performed with 40 participants
-
-Very small number of values tested only 5 overall???
-
-Initial results show promising results for hypen delimitations etc alongside improved user impressions

### 2019-08-14 Writeup/Thesis/diagrams/bloom_filter.tex
Changes; - Added frame for conference paper - Moved both projects into a shared folder

\begin{tikzpicture}[
    square/.style={regular polygon,regular polygon sides=4, minimum size=1.4cm}
]

    \node at (0,0) [square,draw] (box_0) {$1$};
    \node at (1,0) [square,draw] (box_1) {$1$};
    \node at (2,0) [square,draw] (box_2) {$1$};
    \node at (3,0) [square,draw] (box_3) {$0$};
    \node at (4,0) [square,draw] (box_4) {$0$};
    \node at (5,0) [square,draw] (box_5) {$0$};
    \node at (6,0) [square,draw] (box_6) {$1$};
    \node at (7,0) [square,draw] (box_7) {$0$};
    \node at (8,0) [square,draw] (box_8) {$1$};
    \node at (9,0) [square,draw] (box_9) {$0$};
    \node at (10,0) [square,draw] (box_10) {$1$};
    \node at (11,0) [square,draw] (box_11) {$0$};

    \node[] (set) [above of=box_5, yshift=2cm] {$\{x, y, z\}$};
    \node[] (set_x) [left of=set, xshift=0.65cm, yshift=-0.15cm] {};
    \node[] (set_z) [right of=set, xshift=-0.65cm, yshift=-0.15cm] {};
    \node[] (new_set) [below of=set, yshift=-4.5cm] {$n$};

    % X
    \draw [->, very thick, blue] (set_x) to [out=-90, in=90, xshift=2cm] (box_6);
    \draw [->, very thick, blue] (set_x) to [out=-90, in=90, xshift=2cm] (box_2);

    % Y
    \draw [->, very thick, red] (set) to [out=-90, in=90] (box_0);
    \draw [->, very thick, red] (set) to [out=-90, in=90] (box_8);

    % Z
    \draw [->, very thick, purple] (set_z) to [out=-90, in=90, xshift=2cm] (box_1);
    \draw [->, very thick, purple] (set_z) to [out=-90, in=90, xshift=2cm] (box_10);

    % N
    \draw [->, thick] (new_set) to [out=90, in=-90, xshift=2cm] (box_1);
    \draw [->, thick] (new_set) to [out=90, in=-90, xshift=2cm] (box_7);
\end{tikzpicture}

### 2019-08-14 Writeup/Thesis/pages/design.tex
Changes; - Added frame for conference paper - Moved both projects into a shared folder

--- 2019-08-12 Thesis/pages/design.tex
@@
 The first letter of the word is retained alongside the removal of all of a, e, i, o, u, y, h and w.
-The remaining letters are then mapped to numbers\footnote{Further steps are performed on the code, as the technical details do not add anything to the discussion, the steps of the algorithm can be found in Appendix TODO.}.
+The remaining letters are then mapped to numbers.
 These mappings are displayed in Figure \ref{fig:soundexMap}.
@@
 
-\subsection{Soundex Issues}
+\subsection*{Soundex Issues}
 \label{sec:soundexIssues}
@@
 Metaphone was chosen due to similar reasons to that of Soundex and NYSIIS.
-
-\textbf{TODO} Better argument needed?
 
@@
 
+\todo{Include explination into how audio is generated}
+
 The final experiment required to answer the Research Question \ref{goal:attackPercentage} will simulate attacks on participants.

### 2019-08-14 Writeup/Thesis/pages/experiments.tex
Changes; - Added frame for conference paper - Moved both projects into a shared folder

--- 2019-08-13 Thesis/pages/experiments.tex
@@
 \section{Experiment 1 - Metric performance}
+\todo{talk about participants like the second experiment with Stdev}
+
 As discussed in Section \ref{exp:metric} the goal of the experiment was the cull the number of metrics to be assessed in the following experiment.
@@
 Overall, 104 participants were assessed in this study.
-Five results were discarded from the set due to either failing the attention questions (See in Section \ref{sec:exp1_qualitycontrol}) or having having too low of a fluency rating.
+Five results were discarded from the set due to either failing the attention questions (See in Section \ref{sec:exp1_qualitycontrol}) or having too low of a fluency rating.
 This was a necessary process to improve the health of the results.
@@
 The breakdown of the ratings in Figure \ref{fig:exp1_breakdown} also shows Levenshtein's dominance.
-Levenshtein has a much larger proportion of 4 and 5 ratings than the alternatives alongside a very low level of low ratings.
+Levenshtein has a much larger proportion of 4 and 5 ratings than the alternatives.
 This performance may, however, be due to the visual way the comparisons are being performed.
@@
 The results are also an improvement over informal ad-hoc methods.
-Further work could aim to reproduce this study with the proposed audio based design.
+Further work could aim to reproduce this study with the proposed audio based design (See Section \ref{sec:exp1_considerations}).
 
@@
 \label{sec:exp2}
-
-Section \ref{sec:exp2_design} explains the design of the experiment. This section will present and discuss the results of the experiment alongside a comparison to relevant literature.
+The aim of this experiment is to quantify the success rate of the proposed attack.
+Design details for this experiment can be seen in Section \ref{sec:exp2_design}.
+This section will present and discuss the results of the experiment alongside a comparison to relevant literature.
 
@@
 Around 62\% of participants had completed a single stage of university (Bachelor and up).
-This makes this set of participants more educated that the general population.
+This makes this set of participants more educated than the general population.
 All participants were also sourced from the USA and have rated themselves as fully native English speakers.
@@
 The worst performer was Metaphone with an average of 16.88\% over its three levels of attacks.
-When comparing the performance of the metrics to the previous experiment the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in the exactly same order.
+When comparing the performance of the metrics to the previous experiment the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in exactly the same order.
 
 \begin{table}
+    \makebox[\textwidth][c]{
         \centering
@@
         \end{tabular}
+    }
     \caption{Success rates for simulated attacks}
@@
 This combined with the low average age contributes to an inevitable bias being introduced into the data.
-An assumption can be made that higher education leads to more skillful interaction with computer based systems, this, therefore, with the previous assumption in mind means the results of this experiment being a `best case' scenario.
+An assumption can be made that higher education leads to more skillful interaction with computer based systems, this, therefore, with the previous assumption in mind means the results of this experiment can be considered a `best case' scenario.
 The attacks, therefore, would be expected to be more successful on less technical users.
@@
 This alongside the potential for users to downplay the possibility of attack leads to the conclusion that the success rates could be much higher in a real-world setting.
-The assumption is that these results display the success rate for extremely attentive user where they will make sure to double check with their authentication partner multiple times.
+The assumption is that these results display the success rate for extremely attentive users where they will make sure to double check with their authentication partner multiple times.
 This is opposed to the assumption that the majority of users will aim to complete the task as quickly as possible.
@@
 However, the success for the PGP Word list was 8.78\%.
-As 10/14 words were kept static more comparable to comparable the results to the highest attack strength ``2 static''.
-Therefore, there is another 3 fold improvement in the success rates of our simulated attacks.
+As 10/14 words were kept static more comparable to the results of the highest attack strength ``2 static''.
+This leads to another 3 fold improvement in the success rates of our simulated attacks.
 
-The final relevant paper to compare is that of Tan \textit{et al.}.
+The final relevant paper to compare is that of Tan \textit{et al.}\cite{tan2017can}.
 This paper had the highest number of words assessed with 16 overall.
@@
 \begin{table}[!h]
+    \makebox[\textwidth][c]{
         \centering
@@
         \end{tabular}
+    }
     \caption{Each metric's average near-collision keys}
@@
 The success rate for this attack type in the second experiment was 11.01\% on average.
-This means on comity hardware commonly found in the home, an attacker could compute a key in less than two days that could succeed more than 10\% of the time.
+This means on commodity hardware commonly found in the home, an attacker could compute a key in less than two days that could succeed more than 10\% of the time.
 This is substantial and highlights on weaknesses in the Trustword system.
@@
 These keys were then randomly sampled and used to create the combined key as discussed in Section \ref{sec:pep}.
-100,000 random key pair were created and used as the sample.
+100,000 random key pairs were created and used as the sample.
 Any vulnerable keys in this set were recorded and used in the experiment.
@@
     \centering
+
+    \makebox[\textwidth][c]{
+
         \begin{tabular}{|lll|}
@@
         \end{tabular}
+    }
     \caption{Number of vulnerable keys per metric}
@@
 NYSIIS was chosen as the selected metric.
-To expedite the process an initial search was performed for controlled keys that had the highest number of near-collision keys, this was due to the demonstrative purpose of this experiment.
+To expedite the process an initial search was performed for controlled keys that had the highest number of near-collisions, this was due to the demonstrative purpose of this experiment.
 Producing near-matching keys from key pairs with a very small number of potential matches, adds very little to this demonstration.
@@
 \begin{table}[h!]
+
+    \makebox[\textwidth][c]{
         \begin{tabular}{|l|l|}
@@
         \end{tabular}
+    }
     \caption{NYSIIS - 0 static}
@@
 
+    \makebox[\textwidth][c]{    
         \begin{tabular}{|l|l|}
@@
         \end{tabular}
+    }
     \caption{NYSIIS - 1 static}
@@
 
+    \makebox[\textwidth][c]{
         \begin{tabular}{|l|l|}
@@
         \end{tabular}
+    }
     \caption{NYSIIS - 2 static}
-
     \label{tab:nysiis2}
@@
 
-As it can be seen most notable from Table \ref{tab:nysiis2} the generation of the actual Trustwords differs in only 3 characters making it arguably very similar.
+As it can be seen most notably from Table \ref{tab:nysiis2} the generation of the actual Trustwords differs in only 3 characters making it arguably very similar.
 When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU is able to achieve around a 28\% success rate when assessed against actual users.

### 2019-08-14 Writeup/Thesis/pages/implementation.tex
Changes; - Added frame for conference paper - Moved both projects into a shared folder

--- 2019-08-13 Thesis/pages/implementation.tex
@@
 
-GreenOnion is written in C++. This languages was chosen due to its efficiency bonuses over other alternative languages.
+GreenOnion is written in C++. This language was chosen due to its efficiency bonuses over other alternative languages.
 The tool begins by generating a 2048-bit RSA key through GPG\footnote{GNU Privacy Guard}.
@@
 The final block of the key is left un-hashed due to the presence of the exponent ($e$).
-This exponent is incremented to create a new unique key.
-This is the aspect provides rapid generation of new keys due to the reduction in expensive large prime generation.
-This prevents issues in such as entropy starvation when generating a large number of valid RSA keys.
+This exponent is then incremented to create a new unique key.
+This allows rapid generation of new keys due to the reduction in expensive large prime generation.
+This prevents issues in such as entropy starvation when generating a large number of RSA keys.
 This produces valid keys but with abnormally large exponents, this was deemed as suitable due to the short term use-case for these keys.
@@
 
-Mass checking of fingerprints is the tools main abilities as it allows for millions of keys to be checked with a very small amount of overhead.
+Mass checking of fingerprints is the tools main ability as it allows for millions of keys to be checked with a very small amount of overhead.
 This is achieved through the use of a bloom filter.
@@
 This is repeated a number of times with a number of hashing algorithms ($k$) to populate the array of length ($m$).
-This then means checking the presence of an element in the set will just means hashing the target and checking the indices returned.
+This then means checking the presence of an element in the set just means hashing the target and checking the indices returned.
 This data structure therefore has a complexity of $O(k)$ regardless of the number of elements in the set.
@@
 
-However, due to the random distribution of the hashing algorithms, there is the possibility for collisions and, thus, the possibility of false-positives.
+However, there is the possibility for collisions and, thus, the possibility of false-positives.
 The data structure, however, does not produce any false-negatives.
-This, therefore, makes it fully suited to this use-case as any fingerprints tagged as ``possibility'' being present in the bloom filter can be followed up with a more expensive hash-table check to determine their actual presence.
+This, therefore, makes it fully suited to this use-case as any fingerprints tagged as ``possibly'' being present in the bloom filter can be followed up with a more expensive hash-table check to determine their actual presence.
 Therefore, if the levels of false-positives are controlled (by altering $k$ and $m$) the tool can search through huge number of potential keys without any decrease in speed.
@@
 The \verb|<EXPONENT_INCREMENTING_CODE>| will be explained in the next section.
-After the exponent is increment the code produces the final digest by calling \verb|sha1_block(W, H)|.
+After the exponent is incremented the code produces the final digest by calling \verb|sha1_block(W, H)|.
 The 32-bit left and right sections of the digest are hashed using the MurmurHash algorithm.
@@
 Figure \ref{fig:increment} contains the code used to increment the exponent.
-Due to the exponent being split across two words alongside the bare bones functionality of OpenCL binary operations were chosen as the solution to the incrementation.
+Due to the exponent being split across two words alongside the limited functionality of OpenCL, bitwise operations were chosen as the solution to the incrementation.
 The code utilise the fact that anything XORed with itself becomes zero alongside the fact that XORing a value $a$ with zero provides the result equal to $a$.
@@
 It provided functionality to easily present questions and record their responses.
-However, as the design requirement of renewing sample from the matches of each metric was not part of the main applications functionality a solution was required.
+However, as the design requirement of refreshing questions after each submission was not part of the main applications functionality an extra solution was required.
 This was solved by Google's App Script\footnote{\url{https://developers.google.com/apps-script/}} service that allows a user to programmatically interact with the Form.
@@
 Each time a user submitted their response the \verb|updateForm()| endpoint was called, that subsequently updated the questions for the next user.
-This aimed to keep the samplings fair as they are equality likely to appear when attacking the system alongside an ample exploration of the overall match quality.
+This aimed to keep the samplings fair as they are equally likely to appear when attacking the system.
+
+\newpage
 
 \section{MainExperiment}
-In order to asses users in a similar scenario to ones experienced when utilizing \pep in the real-world a custom application was required.
+In order to assess users in a similar scenario to ones experienced when utilizing \pep in the real-world a custom application was required.
 The front-end is developed in Javascript with a Python-Flask backend that acts as the webpages functionality.
@@
 One of the main problems encountered was the handling of each user's session.
-Initially during testing it was noted that changes in one end-point if timed correctly would overwrite the progress of another, this is commonly know as a ``Lost update''.
+Initially during testing it was noted that changes in one end-point if timed correctly would overwrite the progress of another, this is commonly known as a ``Lost update''.
 This was due to the user session being stored in the \verb|session| cookie.
@@
 Figure \ref{fig:cookie} shows this problem visually.
-As it can be seen the response cookie $c_2$ is based of the old data of $c$ and, therefore, when returned will remove the progress of $c_1$.
-To keep the complexity of the backend low it was opted to solve this problem by restricting the user via the UI, when a button was clicked all other operations were disabled until a response was received.
+As it can be seen the response cookie $c_2$ is based off the old data of $c$.
+When $c_2$ is eventually returned it will remove the progress of $c_1$.
+To keep the complexity of the backend as low as possible it was opted to solve this problem by restricting the user via the UI.
+When a button was clicked all other operations were disabled until a response was received.
 This stopped the possibility of sending off another request while another is still processing.
@@
 The chosen solution utilized a python object serialization library known as `Pickle'\footnote{\url{https://docs.python.org/2/library/pickle.html}}.
-This library saves the an instance of a class as a file.
+This library saves the instance of a class as a file.
 This file then can be used to load the instance of the class back into the program.

### 2019-08-14 Writeup/Thesis/pages/introduction.tex
Changes; - Added frame for conference paper - Moved both projects into a shared folder

--- 2019-08-09 Thesis/pages/introduction.tex
@@
 A fingerprint is a small string of characters that is unique to each key pair.
-Therefore, it can be used as as a way of identification.
+Therefore, it can be used as a way of identification.
 
 Fingerprints can come in a number of different encodings such as hexadecimal, words and even procedurally generated avatars.
-Previous research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}, alongside this the involvement of human based verification makes the designing the scheme to be user friendly is a task of upmost importance.
+Previous research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}, alongside this the involvement of human based verification makes the designing of user friendly schemes a task of upmost importance.
 
@@
 However, these suffer from user adoption due to perceived complexity.
-This leaves manual verification in the current position of being a difficult problem, where the proposed solutions need to sacrifice one of usability or security.
-Therefore, research into improving or creating new fingerprint encodings that work well with users remains massively relevant.
+This leaves manual verification in a difficult position, due the proposed solutions needing to sacrifice either usability or security.
+Therefore, research into improving or creating secure fingerprint encodings that work well with users remains massively relevant.
 
-The report will asses the security and feasibility of attacking a fingerprint encoding known as ``Trustwords'' as it claims at this point have been unsubstantiated.
+The report will asses the security and feasibility of attacking a fingerprint encoding known as ``Trustwords'' as justification for various design choices have been unsubstantiated.
 
@@
 
-\textbf{Chapter 4} documents the prosed designs required to answer the research questions proposed in Chapter 3.
+\textbf{Chapter 4} documents the proposed designs required to answer the research questions proposed in Chapter 3.
 
@@
 
-\textbf{Chapter 8} concludes the project with a culmination of the papers findings alongside the any conclusions that can be drawn from the research.
+\textbf{Chapter 8} concludes the project with a culmination of the papers findings alongside any conclusions that can be drawn from the research.

### 2019-08-14 Writeup/Thesis/pages/lit_review.tex
Changes; - Added frame for conference paper - Moved both projects into a shared folder

--- 2019-08-02 Thesis/pages/lit_review.tex
@@
 
+To fully understand the literature review it is necessary to introduce and explain the base knowledge before continuing.
+
 \subsection*{Public-key Cryptography and Key Exchange}
 
-To fully understand the literature review it is necessary to introduce and explain the base knowledge before continuing.
-
 Asymmetric cryptography facilitates the secure encryption of messages in end-to-end encryption (E2EE), verification of digital signatures and sharing of pre-communication secrets, among others.
-The use-case of E2EE messages will be the primary focus of this paper.
 
@@
 Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob) the fingerprint of the public key can be used for identification.
-There are, however, issues in how a user should link a key's fingerprint to real world entity.
-This paper will, however, assume that users know the respective parties' correct fingerprint, as the protocols used to achieve this are outside the project's scope.
+There are, however, issues in how a user should link a key's fingerprint to a real world entity.
+This paper will, however, assume that users have access to the respective parties' correct fingerprint, as the protocols used to achieve this are outside the project's scope.
 
-The fingerprint of the key is generated by running the main components through a secure one way hash function such as SHA-1.
+The fingerprint of the key is generated by running the main key components through a secure one way hash function such as SHA-1.
 This process produces a digest of fixed length that can be used to compare keys.
-Therefore, the comparison of expected and actual fingerprints can be used too detect MiTM attacks.
+Therefore, the comparison of expected and actual fingerprints can be used to detect MiTM attacks.
 Historically these have been represented as a hexadecimal string whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card.

### 2019-08-14 Writeup/Thesis/pages/research_question.tex
Changes; - Added frame for conference paper - Moved both projects into a shared folder

--- 2019-07-30 Thesis/pages/research_question.tex
@@
-\chapter{Research Questions}
+\chapter{Project Aims}
 
@@
 in person or by phone).}\footnote{https://www.pep.security/docs/general\_information.html\#handshake}.
-It can be assumed due the increased globalization of the planet that the most common handshake occurrence will be over the phone, and, therefore, will not be in person.
+It can be assumed due to the increased globalization of the planet that the most common handshake occurrence will be over the phone, and, therefore, will not be in person.
 This is, therefore, the assumed context the handshake will be occurring in.
@@
 
-\section{Questions}
+\section{Research Questions}
 
@@
 
-\begin{itemize}
-    \item Is the recommended minimum number of four Trustwords enough to provide a basic level of security?
+\begin{enumerate}
 
-    \item What are the different ways phonetic similarity can be quantified?
+    \item Is the recommended minimum number of four Trustwords enough to provide a basic level of security? \label{goal:numberOfTrustwords}
 
-    \item What is the time and computation complexity required to generate a 'similar' keys for a targeted key pair?
+    \item What are the different ways phonetic similarity can be quantified?  \label{goal:phoneticSimilarity}
 
-    \item What kind of hardware is required to compute a matching key?
+    \item Out of a chosen set of metrics, which are the most effective? \label{goal:bestMetrics}
 
-    \item What percentage of attacks successfully deceive a user?
-\end{itemize}
+    \item What is the time and computation complexity required to generate a 'similar' keys for a targeted key pair? \label{goal:complexity}
+
+    \item What kind of hardware is required to compute a matching key? \label{goal:hardwareRequired}
+
+    \item What percentage of attacks successfully deceive a user? \label{goal:attackPercentage}
+\end{enumerate}
 

### 2019-08-14 Writeup/Thesis/pages/introduction.tex
Changes; - Corrections and wording changes

--- 2019-07-22 Thesis/pages/introduction.tex
@@
 
-The increasing use of public key cryptography by instant messaging and secure email means key fingerprint 
-verification is an ever more important task.
+The increasing use of public-key cryptography by instant messaging and secure email means key-fingerprint  verification is an ever more important task.
+
 One of the most significant risks to the security of the communication channel is a Man-in-the-middle (MiTM) attack.
-A successful MiTM attack can circumvent the encryption as it allows an attacker to read all the encrypted data.
-A countermeasure for this is the verification of each parties' fingerprint.
-\textbf{[...]}
+A MiTM attack involves an attacker impersonating one or both sides of a connection.
+MiTM attacks can entirely circumvent the encryption as it allows an attacker to read all of the encrypted data.
+
+A countermeasure for the threat of MiTM attacks is the verification of each parties’ fingerprint.
+A fingerprint is a small string of characters that is unique to each key and, thus, can be used to identify.
+
+Fingerprints can come in several different encodings such as Hexadecimal, words, and even procedurally generated avatars.
+Previous research has shown that the average human can only hold around 7-digits ($\pm 2$) worth of data in their working memory\cite{miller1956magical}.
+Consequently, this makes the designing of user-friendly schemes a task of utmost importance.
+
+Humans are commonly considered the most vulnerable part of any computer system.
+Solutions, therefore, have been proposed to remove this manual verification with examples such as PGP's web-of-trust\cite{callas1998openpgp} and Namecoin\cite{kalodner2015empirical}.
+However, these suffer from user adoption due to perceived complexity.
+Manual verification is, consequently, left in a difficult position, due in part to proposed solutions needing to sacrifice either usability or security.
+Therefore, research into improving or creating a more secure and user-friendly fingerprint encoding remains an important task.
+
+This report evaluates the security and feasibility of attacking a fingerprint encoding known as “Trustwords.” The motivation for this is due in part to the shortage of justification behind some fundamental design choices.
+
+The report is structured as follows:
+
+\textbf{Chapter 2} provides any required background knowledge alongside a review of all relevant literature.
+
+\textbf{Chapter 3} formally defines the aim of this report alongside the research questions the project aims to answer.
+
+\textbf{Chapter 4} documents the proposed designs required to answer the research questions proposed in Chapter 3.
+
+\textbf{Chapter 5} discusses the significant implementation details of the designs formalized in Chapter 4.
+
+\textbf{Chapter 6} presents and analyses all experimentation results of the project.
+
+\textbf{Chapter 7} evaluates the success of the project alongside a discussion into proposed further work. The research aims proposed earlier in Chapter 3 are used as evaluative metrics.
+
+\textbf{Chapter 8} concludes the project with a culmination of the findings of the paper alongside any relevant conclusions.

### 2019-08-14 Writeup/Thesis/pages/lit_review.tex
Changes; - Corrections and wording changes

@@
 
-The chapter will contain the following sections:
+The chapter contains the following sections:
 
@@
     \item \textbf{Project context} \\ 
-    Will provide the user with the base knowledge required to understand the context and purpose of the following literature review.
+    Provides the user with the base knowledge required to understand the context and purpose of the following literature review.
 
     \item \textbf{Definition of terms}\\
-    Specific definitions relevant to the literature review will initially be defined.
+    Specific definitions relevant to the literature review are initially defined.
 
     \item \textbf{Literature Review} \\
-    A review of currently available literature on relevant topics. Recommendations and research gaps will be identified and discussed.
+    A review of currently available literature on relevant topics. Recommendations and research gaps are identified and discussed.
 
@@
 
-To fully understand the literature review it is necessary to introduce and explain the base knowledge before continuing.
+To fully understand the literature review, it is necessary to introduce and explain the base knowledge before continuing.
 
@@
 
-Asymmetric cryptography facilitates the secure encryption of messages in end-to-end encryption (E2EE), verification of digital signatures and sharing of pre-communication secrets, among others.
+Asymmetric cryptography facilitates the secure encryption of messages in end-to-end encryption (E2EE), verification of digital signatures, and sharing of pre-communication secrets, among others.
 
 The asymmetry stems from the use of "Public" and "Private" keys.
-The Public key is used to encrypt data that only the respective Private key can decrypt.
-This means the keys required to encrypt can be easily shared across insecure channels.
+The public-key is used to encrypt data that only the respective private-key can decrypt.
+Hence, this means that sharing the keys required to encrypt can be performed across insecure channels.
 
-To construct an E2EE connection the initial stage will be a key exchange using the key types discussed previously.
-This is the sharing of a pre-shared secret between two verified parties, this will then be used to encrypt subsequent messages with symmetric encryption\footnote{This is due to the speed increase of symmetrical over asymmetrical encryption}.
-This, however, hinges on the verification of the initial parties, if one party impersonates another and gets to view the pre-shared secret all communication becomes decryptable.
-Therefore, the correct identification of parties is crucial to maintaining secure communication channels.
+An E2EE connection uses the key types discussed previously to exchange messages between verified parties securely.
+However, this hinges on the verification of the initial parties, if one party impersonates another and receives sensitive communication, the secure encryption is completely circumvented.
+Therefore, the correct identification of parties is crucial to maintaining security.
 The exploitation of this is known as a Man-in-the-middle (MiTM) attack.
-This can be bidirectional where the attacker can sit in the middle of a communication channel and decrypt all correspondence.
+This attack is commonly bidirectional, and if executed correctly, there is often no discerning change to the user experience.
 Figure \ref{fig:mitm} contains a visual representation of this attack.
@@
 
-Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob) the fingerprint of the public key can be used for identification.
-There are, however, issues in how a user should link a key's fingerprint to a real world entity.
+Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob), the fingerprint of the public keys are, therefore, different, and, thus can be used for identification.
+There are, however, issues in how a user should link a key's fingerprint to a real-world entity.
 This paper will, however, assume that users have access to the respective parties' correct fingerprint, as the protocols used to achieve this are outside the project's scope.
 
-The fingerprint of the key is generated by running the main key components through a secure one way hash function such as SHA-1.
-This process produces a digest of fixed length that can be used to compare keys.
+The fingerprint of the key is generated by running the main key components through a secure one-way hash function such as SHA-1.
+This process produces a digest of a fixed length that can be used to compare keys.
 Therefore, the comparison of expected and actual fingerprints can be used to detect MiTM attacks.
 Historically these have been represented as a hexadecimal string whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card.
-This process is known as the \textit{``authentication ceremony''}.
-However, system designers are moving away from this structure and are now creating a combined key from each sides' public key.
-In the case of WhatsApp for example, the connection fingerprint of two parties keys is the first 30 bytes of a SHA-512\footnote{5200 iterations} hash of each parties' identity key, these are then both concatenated together to form a single key\cite{whatsapp2017paper}.
-This produces a unique key communication pair.
+This process is known as the \textit{``authentication ceremony.''} System designers are, however, moving away from this structure and are now implementing a combined key.
+This change is due to the assumed increase in usability.
+Users now compare a single fingerprint, instead of two sets separately.
+In the case of WhatsApp for example, the connection fingerprint of two parties keys is the first 30 bytes of an SHA-512\footnote{5200 iterations} hash of each parties' identity key, these are then both concatenated together to form a single key\cite{whatsapp2017paper}.
+This process produces a unique-key communication pair.
 \\\\
-Due to the manual comparison of the fingerprint, length and format is a consideration.
+Due to the manual comparison of the fingerprint, length, and format is a core design consideration.
 Prior research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}.
@@
 Research in this area has taken various encoding schemes and compared their fallibility to impersonated attacks.
-The main elements of comparison have been the ``accuracy of attack detection" and ``time to compare".
-In this paper, these are considered the metrics of ``security'' and ``usability'', respectively.
+The main elements of comparison have been the ``accuracy of attack detection" and ``time to compare." In this paper, these are considered the metrics of ``security'' and ``usability,'' respectively.
 
@@
 \\\\
-\textbf{\textit{Encoding schemes}} - This is the physical method of encoding used to represent the fingerprint.
+\textbf{\textit{Encoding schemes}} - are the physical method of encoding used to represent the fingerprint.
 For example, ``Hexadecimal'' or ``Words'' are a unique way to represent a fingerprint and thus, are encoding schemes.
 \\\\
-\textbf{\textit{Method of comparison}} - This is how the user assesses the encoding scheme.
+\textbf{\textit{Method of comparison}} - is the way a user assesses the encoding scheme.
 The most common example and the one used as default is ``Compare-and-Confirm'' (CaC).
@@
 \section{Literature Review}
-This section will now discuss the current research around the proposed topic.
+This section discusses the current research around the proposed topic.
 
-The section is organized as follows:
+The organization of the section is as follows:
 
@@
     \item \textbf{Authentication ceremony performance} \\
-    This section explains the current research on performance of various encoding schemes and methods of comparison.
-This is then complemented with an assessment of the experimentation design for the respective studies.
+    This section explains the current research on the performance of various encoding schemes and methods of comparison, alongside an assessment of the literature's experimental design.
 
     \item \textbf{Encoding schemes} \\
-    The following section then discusses research around the design of an encoding scheme.
-Focus in this section will be allocated to the technical details around the creation and design of relevant schemes.
+    The following section then discusses research around the design of an encoding scheme. The focus of the section is the technical details regarding the creation and design of schemes.
 
     \item \textbf{Attacks on encoding schemes} \\
-    The final section will then discuss literature that investigates the creation of attacks against encoding schemes in order to deceive the respective users.
+    The final section discusses literature that investigates the creation of actual attacks against encoding schemes.
 \end{itemize}
@@
 Results 
-from the literature consistently show the effectiveness of language-based encodings such as Words or Sentences with accuracies ranging from 94\% \cite{dechand2016empirical}\cite{tan2017can}\cite{kainda2009usability}.
+from the literature consistently show the effectiveness of language-based encodings such as Words or Sentences with accuracies ranging up from 94\% \cite{dechand2016empirical}\cite{tan2017can}\cite{kainda2009usability}.
 In all cases, these were the best schemes from the sets assessed.
-The exception to this is the work performed by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63.00\%.
+The exception to this is the work performed by \textbf{Hsiao \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63\%.
 \\\\
@@
 Examples of schemes assessed were: Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Vash\footnote{https://github.com/thevash/vash}, OpenSSH visual host key and Unicorns\footnote{https://unicornify.pictures/}, among others.
-These schemes had mixed accuracy with ranges as large as 50\% - 94\% in work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study}.
+These schemes had mixed accuracy with ranges as large as 50\% - 94\% in work by \textbf{Hsiao \textit{et al.}}\cite{hsiao2009study}.
 The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can} where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
@@
 The comparison speed of these schemes were all among the quickest (See Table \ref{tab:times} for an overview of timings).
-Other work also indirectly concurred with graphical encodings having significantly quicker comparison times compared to non-graphical schemes \cite{dechand2016empirical}\cite{kainda2009usability}.
+Other work also indirectly agreed with graphical encodings having significantly quicker comparison times compared to non-graphical schemes \cite{dechand2016empirical}\cite{kainda2009usability}.
 In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with literature only containing two papers.
 There is also no overlap in the schemes assessed with each paper reviewing a unique set.
-This is, therefore, a promising candidate for further research.
+This area is, therefore, a promising candidate for further research.
 
@@
 
-The findings from the paper showed a high false negative rate for all the schemes; this is a consideration also missing from the literature.
+The findings from the paper showed a high false-negative rate for all the schemes.
+This consideration is also missing from the literature.
 Alongside this, results for usability were lower in a remote setting for all the schemes.
 The author, however, comments on the expected nature of this result.\\
-Images were assessed as being the most secure method of authentication in the remote setting but voted as the method with the worst usability.
+Images were identified as being the most secure method of authentication in the remote setting but voted as the method with the worst usability.
 This conclusion is highly inconsistent with all other work in this area.
@@
 
-Alongside this, it was shown in work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} that age and gender do not affect the accuracy of the scheme.
+Alongside this, it was shown in work by \textbf{Hsiao\textit{et al.}}\cite{hsiao2009study} that age and gender do not affect the accuracy of the scheme.
 However, younger participants were considerably faster.
-Furthermore, findings also showed that language comprehension helped in discerning small differences between schemes encoded in Chinese, Japanese, Korean or English.
+Furthermore, findings also showed that language comprehension helped in discerning small differences between schemes encoded in Chinese, Japanese, Korean, or English.
 Subsequently, knowledge of the language did not assist in differentiating more significant changes in the schemes as these had high accuracy regardless.
-These were interesting and unique considerations.
+These were unique considerations.
 Further work could aim to corroborate these conclusions.
@@
 The creation of CaS was due to concerns that CaC would be ``too easy'' for users leading to complacency and errors\cite{uzun2007usability}.
-CaE is designed for scenarios where both devices might not have a display, i.e.
-pairing between a phone and a keyboard.
+The design of CaE is for scenarios where both devices might not have a display, i.e., pairing between a phone and a keyboard.
 One device displays the checksum.
-This checksum is entered into the other device.
+This checksum is then entered into the other device.
 The first device then compares the entered string and checks for a match.
 
-Research has been performed assessing the performance of these schemes and how they affect the ultimate security of the authentication ceremony.
-The literature agrees on CaC being the best overall scheme to compare fingerprints \cite{tan2017can}\cite{uzun2007usability} with CaS being highlighted for its poor security and usability.
-CaE has  had contrasting results.
+Research has assessed the performance of these schemes and how they affect the security of the authentication ceremony.
+The literature agrees on CaC being the best overall scheme to compare fingerprints \cite{tan2017can}\cite{uzun2007usability} with CaS highlighted for its poor security and usability.
+CaE has had conflicting results.
 \cite{uzun2007usability} discarded it after one round due to ``poor usability.'' However, \cite{tan2017can} considered it the best method overall for usability and security.
@@
 
-% One aspect of note from the work by \textbf{Ersin Uzun \textit{et al.}}\cite{uzun2007usability} is their studies context  of  “Secure  device  pairing”  and  thus  some comparison schemes are tested that are not relevant in a fingerprint comparison context, for example “Choose-and-Enter” (A participant chooses a passphrase from an available list and enters it into the other device).
-Thus, only relevant comparison schemes and their results were extracted and compared.
-\\
-
 \subsubsection*{Experimentation methodology comparison}
-To further look into the validity of previously discussed results, it is necessary to asses how the respective studies reached these conclusions.
-Areas for consideration are scheme entropy, attacker strength and participant attributes.
+To further look into the validity of previously discussed results, it is necessary to asses how the respective studies reached their conclusions.
+Areas for consideration are scheme entropy, attacker strength, and participant demographics.
 
@@
 The worst studies tested only 22-bits of entropy.
-This makes it difficult to compare results directly.
-One of the papers this most effects is the early work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study}  where their highest entropy is 28-bits.
+This lack of entropy makes it challenging to compare results directly.
+One of the papers this most effects is the early work by \textbf{Hsiao \textit{et al.}}\cite{hsiao2009study}  where their highest entropy is 28-bits.
 This level of entropy was inadequate even at the time of publication.
@@
 With more entropy, representations will contain longer sequences of characters or more minute details which will lead to increased time and errors during comparisons.''}.
-This statement is backed up with no empirical evidence, and the authors' fail to consider how the low entropy would affect the overall security of the schemes.
+This statement is backed up with no empirical evidence, and the authors fail to consider how the low entropy would affect the overall security of the schemes.
 
@@
 
-Hexadecimal and numerical schemes were not included as encoding schemes in work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} (some of the most widespread encoding schemes).
+Hexadecimal and numerical schemes were not included as encoding schemes in work by \textbf{Hsiao \textit{et al.}}\cite{hsiao2009study} (some of the most widespread encoding schemes).
 This decision was based on their claims on similarities to Base32 and ``well-known deficiencies" in the excluded schemes.

### 2019-08-14 Writeup/Thesis/pages/design.tex
Changes; - More corrections made

@@
 
-This chapter will discuss and overview of the proposed designs for elements required to answer the research questions.
+This chapter discusses an overview of the proposed designs for elements required to answer the research questions.
 Alternative solutions are explained when relevant alongside a justification of design choices.
@@
 The attack on Trustwords involves generating "near-collision" keys. 
-This will attempt to provide the base to answer Research Questions \ref{goal:numberOfTrustwords}, \ref{goal:complexity} and \ref{goal:hardwareRequired}.
+This attempts to provide the base to answer Research Questions \ref{goal:numberOfTrustwords}, \ref{goal:complexity} and \ref{goal:hardwareRequired}.
 
@@
 A similarity metric is an algorithm designed to determine if two words are phonetically a match.
-For example, the words "THEIR" and "THERE" will be a match whereas the words "DARK" and "PRINCIPLE" are not phonetically matching.
+For example, the words "THEIR" and "THERE" is a match, whereas the words "DARK" and "PRINCIPLE" are not phonetically matching.
 
-As each combined key in Trustwords is an exclusive-or of both sides' public key (Figure \ref{fig:xor_trustwords} shows this process) the attack is designed to target a single pair of users and will require recomputation for every attack target.
-This will be considered when discussing the attack feasibility.
-Each pair is also split into an "Uncontrolled" or "Controlled" key.
-Uncontrolled is the receiver of the communication, and, thus, we cannot control their key.
-The Controlled key is the one we are attempting to impersonate, and it is assumed that we have the ability to replace the Controlled key with our malicious option.
-These descriptions will be the terminology used throughout the paper.
-However, it should also be considered that the uncontrolled and controlled can be swapped around with the ability to compute both directions.
+As each combined key in Trustwords is an exclusive-or of both sides' public-key (Figure \ref{fig:xor_trustwords} shows this process) the attack is designed to target a single pair of users and requires recomputation for every attack target.
+This aspect is considered when discussing the attack feasibility.
+Each pair is split into an "Uncontrolled" or "Controlled" key.
+Uncontrolled is the receiver of the communication, and, thus, the key cannot be altered.
+The Controlled key is the one we are attempting to impersonate.
+It is assumed that there is the ability to replace the Controlled key with the malicious option.
+These descriptions are the terminology used throughout the paper.
+However, the uncontrolled and controlled keys can be swapped around with the ability to compute both directions.
 Thus, resulting in the possibility to intercept both directions of communication.
-This, however, will require performing the attack separately for both directions.
+This, however, requires performing the attack separately for both directions.
 
@@
 
-When attacking the respective similarity metric will be used to compute a list of possibilities for each position in the combined fingerprint.
+When attacking a similarity metric is used to compute a list of possibilities for each position in the target fingerprint.
 
 Figure \ref{fig:nearMatch} shows the process of generating a subsection of the combinations.
-A list of each words' matches is generated, followed by the generation of the total number of near-collision keys.
+A list of each words' matches is generated and combined to create the comprehensive list of near-collision keys.
 
@@
     \end{BVerbatim}
-    \caption{Visualization of the generation of near matches}
+    \caption{Visualisation of the generation of near matches}
     \label{fig:nearMatch}
@@
 
-In order to generate an actual list of fingerprints to search for, the near-collision words are converted back into hexadecimal and XORed with the uncontrolled key.
-This provides the impersonated key that will produce the desired Trustwords.
-Completing this for all of the near-collision permutations will produce a list of fingerprints that can be inserted into a tool designed to hash keys and search for targets.
-This aspect of using a large list to search for keys massively reduces the complexity of the search.
+Completing these steps produces a list of fingerprints that can be inserted into a tool designed to hash a large number of keys and search for matches.
+This aspect of using a extensive list to search for keys massively reduces the complexity of the search.
 
@@
 There are many algorithms currently available to provide this functionality.
-This section will describe algorithms alongside the reasons they were selected for assessment later in the project.
+This section describes the algorithms alongside the reasons they were selected for assessment later in the project.
 
@@
 One of the earliest examples of a phonetic algorithm is known as Soundex.
-It is one of the most famous algorithm due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}.
-Originally designed for indexing names by phonetics alongside spelling mistakes due to transpositions in letters.
+It is one of the most famous algorithms due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}.
+Initially designed for indexing names by phonetics alongside spelling mistakes due to transpositions in letters.
 Therefore, due to it being based on the phonetic features, it is highly suitable for this project's use-case.
 
-Soundex produces a four digit code for each word assessed.
+Soundex produces a four-digit code for each word assessed.
 The first letter of the word is retained alongside the removal of all of a, e, i, o, u, y, h and w.
@@
 There are a total of 5616 codes due to 26 initial letters and three digits of 6 values ($26 * 6^3$).
-The limited combinations will result in matches of a limited quality.
+The limited combinations result in matches of limited quality.
 
@@
 \begin{enumerate}
-    \item \textbf{Dependency on the first letter:} Soundex cannot match words together if their first letters are different, meaning for example the words "KORBIN" and "CORBIN" will never be matched.
+    \item \textbf{Dependency on the first letter:} Soundex cannot match words together if their first letters are different, meaning, for example, the words "KORBIN" and "CORBIN" are considered non-matching.
 
@@
 
-    \item \textbf{Poor precision.} Due to the previously discussed point of a small code space.
-\cite{patman2001soundex} re-iterates this point but in the context of name matching where Soundex's poor performance was demonstrated.
+    \item \textbf{Poor precision.} Due to the previously discussed point of a limited code space.
+\cite{patman2001soundex} re-iterates this point, but in the context of name matching where Soundex's poor performance was demonstrated.
 Soundex only gained and overall accuracy of 36.37\% when matching names within a provided database.
@@
 
-However, even with Soundex's fallbacks its algorithmic simplicity and popularity allows it to still remain relevant in this application.
+However, even with Soundex's issues, it's algorithmic simplicity and popularity allows it to remain relevant in this application.
 
@@
 The New York State Identification and Intelligence System (NYSIIS) phonetic code was created for use matching the phonetics of American names.
-It was created due to the presence of hispanic names in the American based databases (this was an aspect Soundex was known to have low accuracy with).
-However, due to it having embedded rules to handle word phonetics it would, again be applicable in this application.
+The motivation for it's inception was mostly due to the presence of Hispanic names in the American based databases (this was an aspect Soundex was known to have low accuracy with).
+However, due to it having embedded rules to handle word phonetics, it would again be applicable in this application.
 
-It also allows for variable length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex.
-It was in use right up the end of 1998 within various US Government departments.
+It also allows for variable-length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex.
+It was in use right up util the end of 1998 within various US Government departments.
 Due to NYSIIS's aforementioned use in a professional setting alongside its high occurrence in literature, it was deemed suitable as one of the selected similarity metrics.
@@
 Levenshtein distance is a string metric designed to measure the 'distance' between two strings.
-It is simply the number of single-character edits (insertions, deletions or substitutions) required to reach the other string.
-Edit distance is not technically designed as a phonetic algorithm, but due to similar-sounding words often being spelt in similar ways\cite{hettiarachchi2012sparcl} Levenshtien distance was deemed another suitable metric.
-Levenshtein is also the most algorithmically simplistic of all the options, this further contributes to its appeal as a chosen metric.
+It is merely the number of single-character edits (insertions, deletions or substitutions) required to reach the other string.
+Edit distance is not technically designed as a phonetic algorithm, but due to similar-sounding words often being spelt in similar ways\cite{hettiarachchi2012sparcl}.
+Alongside this, Levenshtein is also the most algorithmically simplistic of all the considered options.
+These aspects contributed to Levenshtein's inclusion.
 
-An example distance between \verb|trace| and \verb|place| would be the substitutions of the first to letters, from \verb|tr| to \verb|pl| meaning the two strings have a Levenshtein distance of 2.
+An example distance between \verb|trace| and \verb|place| would be the substitutions of the first to letters, from \verb|tr| to \verb|pl|, meaning the two strings have a Levenshtein distance of 2.
 
 \subsection{Phonetic Vectors}
-Phonetic Vectors is the unique addition to the chosen set.
-Created by Allison Parrish in 2017\cite{parrish2017poetic}, Phonetic vectors is as the name suggests the vectorization of a words phonetics.
-This phonetical representation in vector space.
+Phonetic Vectors is a unique addition to the chosen set.
+Created by Allison Parrish in 2017\cite{parrish2017poetic}, Phonetic vectors is as the name suggests the vectorisation of the phonetics of a word.
 
-Phonetic features are used in this work as a way to compare the similarity of a words phonemes.
+Phonetic features are used in this work as a way to compare the similarity of phonemes.
 Phonemes are the phonetic elements that construct a word.
-For example the word "RING" translated into the phonemes \verb|/R IH NG/|.
+For example, the word "RING" translated into the phonemes \verb|/R IH NG/|.
 
 Extensive prior work has gone into producing models of features that map to phonemes \cite{chomsky1968sound}\cite{ladefoged1969measurement}\cite{bradlow2010perceptual}.
-Features, therefore, are an attempt at mapping the varying and inconsistent rules around pronunciation of the English language.
+Features, therefore, are an attempt at mapping the varying and inconsistent rules around the pronunciation of the English language.
 The vectors were created using lists phonemes from the CMU Pronouncing Dictionary and mapping them to possible features.
@@
 This metric allows for a unique set of actions to be performed on the phonetic output.
-Not only does this metric allow the user to measure \textit{dissimilarity} (opposed to the similar-or-not method of the alternatives) the continuous nature of the value allows mathematical operations to be performed on the output.
+Not only does this metric allow the user to measure \textit{dissimilarity} (as opposed to the similar-or-not method of the alternatives) the continuous nature of the value allows mathematical operations to be performed on the output.
 An example shown in \cite{parrish2017poetic} was the addition of word vectors.
@@
 The ability to perform operations and measure dissimilarity allows for a plethora of applications.
-One possible application of note would be the creation of a wordlist where the phonetic difference (vector distance) is maximized.
-This, if the vector mappings are an accurate representation could allow a creation of a phonetically distinctive wordlist.
-These unique aspects contributes to inclusion of this metric in the set.
+One possible application of note would be the creation of a wordlist where the phonetic difference (vector distance) is maximised.
+This application, if the vector mappings are an accurate representation, could allow the creation of a phonetically distinctive wordlist.
+These unique aspects contribute to the inclusion of this metric in the set.
 
@@
 \subsection{Match Rating Approach}
-Matching Rating Approach (MRA) is another algorithm designed to match names within a database, therefore, its operation can be grouped with that of NYSIIS and Soundex.
+Matching Rating Approach (MRA) is another algorithm designed to match names within a database; therefore, its operation can be grouped with that of NYSIIS and Soundex.
 MRA was discarded as an option.
-This is because of the lack of known utilization in any substantial real world use-cases alongside its similarity to more well established algorithms of Soundex and NYSIIS.
+This removal of this metric is due to the lack of known utilisation in any substantial real-world use-cases alongside its similarity to  more established algorithms like Soundex and NYSIIS.
 
-Further work could include the comparison of this algorithm  to similar alternatives in phonetically matching of words to quantify performance.
-This will be discussed further in the evaluative sections of the report.
+Further work could compare this algorithm to similar alternatives in phonetically matching of words to quantify performance. This further work is discussed in the evaluative sections of the report.
 
@@
 Another notable alternative solution is that of Caverphone that was designed in New Zealand.
-Caverphone as is the case with the vast majority of phonetic algorithms was designed for use with name matching.
-Caverphone was not chosen to similar reasons to that of MRA alongside its optimization for the New Zealand accent.
-Therefore, the low level of utilization alongside the unique design features that suggests it may not be suited for this application.
-This has, however, not be assessed empirically and thus would be a candidate for further work.
+Caverphone, as is the case with the vast majority of phonetic algorithms, was designed for use with name matching.
+Caverphone was not chosen to similar reasons to that of MRA alongside its optimisation for the New Zealand dialect.
+Therefore, the low level of utilisation alongside the unique design features contributed to its exclusion.
+However, this has not been assessed empirically and thus would be a candidate for further work.
 
@@
 \label{sec:greenDesign}
-To answer Research Questions \ref{goal:complexity} and \ref{goal:hardwareRequired} fully, it is necessary to implement an actual code base that will be used to generate actual keys.
+In order to answer Research Questions \ref{goal:complexity} and \ref{goal:hardwareRequired} fully, it is necessary to implement an actual tool to generate actual keys.
 
-Inspiration of the design of this tool was taken from a tool called Scallion\footnote{\url{https://github.com/lachesis/scallion}}.
-Scallion was designed by Richard Klafter and Eric Swanson and used to demonstrate that 32-bit PGP key ids were insufficient.
-Keeping with the onion-based theme the proposed tool is known as GreenOnion and is a re-write of the tools structure in C++.
-This language was chosen due to the well understood efficiency benefits.
-The proposed tool differs from Scallion most notably in its ability to concurrently search for a large number of keys, GreenOnion improves on this substantially.
-More implementation and experimental details will be discussed in later chapters.
+The inspiration for the design of this tool was taken from a tool called Scallion\footnote{\url{https://github.com/lachesis/scallion}}.
+Scallion was designed by Richard Klafter and Eric Swanson and was used to demonstrate that 32-bit PGP key IDs were insufficient.
+To keep with the onion-based theme, the proposed tool is known as GreenOnion and is a re-write of Scallion in C++.
+This language was chosen due to the well-understood efficiency benefits.
+The proposed tool differs from Scallion, most notably in its ability to concurrently search for a large number of keys, GreenOnion improves on this substantially.
+More implementation and experimental details are discussed in later chapters.
 
 The tool should take two keys as parameters (Uncontrolled/Controlled) and a chosen similarity metric and produce a list of target keys fingerprints.
-This list is then used as a search criteria when hashing a checking a large number of keys.
-In order to utilise the high parallel nature of the GPU to compute the hash of a large number of keys the tool will utilise a GPGPU (General-purpose computing on graphics processing units) framework.
+This list is then used as a search criterion when searching for keys.
+To utilise the parallel nature of the GPU to compute the hash of a large number of keys, the tool utilises a GPGPU (General-purpose computing on graphics processing units) framework.
 The chosen framework was OpenCL due to its support for the chosen language (C++) and platform (Linux).
-OpenCL allows the creation of code chunks referred to as "kernels" to be executed concurrently, this will provide a massive speed increase compare to the sequential nature of the CPU.
-Technical details will be explained further in Chapter \ref{cha:Implementation}.
+OpenCL allows the creation of code chunks referred to as "kernels" to be executed concurrently, this provides a massive speed increase compared to the sequential nature of the CPU.
+Technical details are explained further in Chapter \ref{cha:Implementation}.
 
 \section{Experiment Design}
-In order to answer some of the research questions empirical evidence is required and, thus, experiments are required.
-In this section the designs and considerations of the chosen experiments will be discussed.
+To answer some of the research questions, empirical evidence is required and, thus, experiments are required. In this section, the designs and considerations of the chosen experiments are discussed.
 
@@
 \label{exp:metric}
-In order to answer Research Question \ref{goal:bestMetrics} and reduce the number of metrics to assess in the later rounds, the performance of similarity metrics required comparison.
-The thinning out of metrics is required due to limited resources and, therefore, possible further work could involve repeating this work with a much more varied selection of metrics.
+This section answers Research Question \ref{goal:bestMetrics}.
+To reduce the number of metrics to assess in the later rounds, the performance of similarity metrics required comparison.
+The thinning out of metrics is required due to limited resources.
+Therefore, possible further work could involve repeating this work with a much more varied selection of metrics.
 As explained in a previous section (See Section \ref{sec:metrics}) the chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors.
@@
 
-In the case of Levenshtein values of similarity are discrete due to it being the number of single character edits.
+In the case of Levenshtein values of similarity are discrete due to it being the number of single-character edits.
 Therefore, this requires less deliberation.
@@
 
-As it can be seen from Table \ref{tab:matchSize} the number of matches for L2 is massively larger than all metrics excluding Soundex.
+As it can be seen from Table \ref{tab:matchSize}, the number of matches for L2 is more significant than all metrics excluding Soundex.
 As the issues with Soundex have been discussed in previous sections (See Section \ref{sec:soundexIssues}) it can be excluded as an abnormality in this context.
@@
 Match size was also used to define the cap for the phonetic vectors.
-This is less distinct that that of Levenshtein due to the continuous nature of the distance between two vectors, however the complexity was reduced by limiting it to increments of 0.5.
+The decision is less apparent that that of Levenshtein due to the continuous nature of the distance between two vectors.
+However, the complexity was reduced by limiting it to increments of 0.5.
 
@@
 Table \ref{tab:vectorMatchSize} contains the match size comparison for Phonetic vectors distance.
-Distance 4.5 was chosen as the suitable size due to the total matches fitting well within the other metrics.
-Distance 4.0 was the other alternative, this was discarded due to its small size.
-Any metric with a number of matches below 100,000 results in an inadequate number of possible near-collision keys later in the process, a lower number of matches may imply better quality but a balance is required between computational cost and attack quality.
-This will be discussed in more detail in later chapters.
+Distance 4.5 was chosen as a suitable size due to the total matches fitting well within the other metrics.
+Distance 4.0 was the other alternative; this was discarded due to its small size.
+Any metric with a number of matches below 100,000 results in an inadequate number of possible near-collision keys later in the process, a lower number of matches may imply better quality, but a balance is required between computational cost and attack quality.
+This is discussed in more detail in later chapters.
 
@@
 Figure \ref{fig:phoneticMatch} shows an example match and the connected scale.
-Users will complete five of these comparisons per metric.
+Users are provided with five of these comparisons per metric.
 
@@
 
-The experiment randomizes the order of these comparisons per session alongside a complete refreshing of matches once per submission.
-This makes sure selections from the samples are fair and consistent as each user will have a different selection of matches.
+The experiment randomises the order of these comparisons per session alongside a complete refreshing of matches once per submission.
+This design makes sure selections from the samples are fair and consistent as each user has a different selection of matches.
 
@@
 \label{sec:exp1_qualitycontrol}
-As the study was being outsourced to Amazon's Mechanical Turk the requirement to check the quality of results is important. Therefore, a couple of additions were provided to check a result's validity.
+As the study was being outsourced to Amazon's Mechanical Turk, the requirement to check the quality of results is essential.
+Therefore, a couple of additions were provided to check a result's validity.
 
@@
 These are matches consisting of two random words selected from the dictionary.
-Therefore, the expected average rating of these words should be close to 1.
-This allows a simple check to see if the user is providing valid results.
-If their average is too high, the results will be discarded.
+Therefore, the expected average rating of these words should be close to one.
+This design allows for a simple check for valid results.
+If their average is too high, their results are discarded.
 
@@
 
-Alongside this, was the addition of two questions comparing exactly the same word.
-As both words are the same the result should always be a full 5/5 rating, any results without a full rating will be discarded.
+Alongside this, was the addition of two questions comparing precisely the same word.
+As both words are the same, the result should always be a full 5/5 rating, any results without a full rating are discarded.
 Figure \ref{fig:exactMatch} contains one example of the attention questions used to filter inaccurate results.
@@
 The final check to ensure the validity of results is a check for native English fluency. Having non-native English speakers complete the 
-experiment has the possibility to introduce inconsistencies into the 
-data and, therefore, needs to remain controlled. To achieve this a 
-preliminary MTurk study will be run to ask users for their perceived 
+experiment can introduce inconsistencies into the 
+data and, therefore, needs to remain controlled. To achieve this, a preliminary MTurk study has been created to ask users for their perceived 
 English fluency on a scale of 1 (Basic Understanding) to 5 (Native). 
-Workers with an answer of 5 will be provided with a 
+Workers with an answer of 5 are provided with a 
 Qualification\footnote{\url{https://blog.mturk.com/tutorial-understanding-requirements-and-qualifications-99a26069fba2}} 
-that tags them as defining themselves as native speakers. This is then 
-added as a prerequisite when running the experiment. This will insure 
+that tags them as defining themselves as native speakers. This qualification is then 
+added as a prerequisite when running the experiment. This prerequisite ensures 
 only fully native speakers are being assessed. The possibility of the 
 worker falsely stating their level of fluency has also been considered. 
-However, as the worker does not know the purpose for this initial study,
+However, as the worker does not know the purpose of this initial study,
 thereby providing inaccurate results has no real valid motive for the 
@@
 The first consideration is the way the words are compared.
-Due to the channel of authentication being phone based the comparison of words will be a mixture of auditory and textual.
-This is because a user needs to match a words sound to the one displayed on their device.
-In the case of this experiment the users are asked to compare the sound of two word that are visually displayed to them.
-
-This visual aspect is the first point of contact between the participant and the question, followed by mental comparison of the phonetics of the word.
+Due to the channel of authentication being phone-based, the comparison of words is a mixture of auditory and textual.
+This mixture is because a user needs to match a words sound to the one displayed on their device.
+This experiment asks users to compare the sound of two words that are visually displayed to them.
+This visual aspect is the first point of contact between the participant and the question, followed by a mental comparison of the phonetics of the word.
 Therefore, this initial visual contact has the potential to bias the results of the study.
-Levenshtein has the potential to be most affected by this due to the matches never being more than one character different, therefore, resulting in very similar looking words.
-The alternative method of running this experiment is to get users to compare audio samples of words, this will force the user to compare just the phonetics of the words and not be influenced by the visual aspects of the pair.
-This, however, adds a substantial cost onto the operation of the study.
-Due to the aforementioned lack of resources the chosen design was decided as most feasible as it is a balance between cost and accuracy.
+Levenshtein has the potential to be most affected by this due to the matches never being more than one character different, therefore, resulting in very similar-looking words.
+The alternative method of running this experiment is to get users to compare audio samples of words; this forces the user to compare just the phonetics of the words and not be influenced by the visual aspects of the pair.
+However, this adds a substantial cost to the operation of the study.
+Due to the aforementioned lack of resources, the chosen design was decided as most feasible as it is a balance between cost and accuracy.
 Further work, therefore, could improve by producing more conclusive results on the performance of the metrics by implementing the more accurate but costly alternative.
@@
 Another consideration is the demographics of people accessible on Mechanical Turk.
-A comprehensive and still active survey run by D Difallah \textit{et al.} \cite{difallah2018demographics} shows that MTurk workers are younger and have a larger household income than that of the US population.
-This has to be taken into consideration when interpreting the results because it will inherently introduce a bias.
-This is due to the assumptions that an increase in age provides a better understanding of more obscure words, and, therefore, a better representation of the metrics performance over the entire dictionary.
+A comprehensive and still active survey run by D Difallah \textit{et al.} \cite{difallah2018demographics} shows that MTurk workers are younger and have a more substantial household income than that of the US population.
+This deviation has to be taken into consideration when interpreting the results because it has to potential to introduce a bias.
 
@@
 
-The final experiment required to answer the Research Question \ref{goal:attackPercentage} will simulate attacks on participants.
-The user will be presented with the same design as presented in the \pep Android application (See Section \ref{sec:pep}).
+The final experiment required to answer Research Question \ref{goal:attackPercentage} requires the simulation attacks on participants.
+The user is presented with the same design as the \pep Android application (See Section \ref{sec:pep}).
 
@@
 Figure \ref{fig:expID} shows the design of the experiments front end.
-As can be seen by comparing it to Figure \ref{fig:trustwords} it has been designed to be a close as possible to the actual application.
-Users will click the blue button to simulate the authentication ceremony over the phone.
-A text-to-speech system will then read a set of words and the user should accept if they match and decline if they don't.
+As can be seen by comparing it to Figure \ref{fig:trustwords}, it has been designed to be as close as possible to the actual application.
+The blue button is clicked to simulate the authentication ceremony over the phone.
+A text-to-speech system then read a set of words and the user should accept if they match and decline if they don't.
 
@@
 
-Due to the scarcity of attacks in a real-world setting users will are often complacent about their occurrence.
-Therefore, in this experiment attacks only occur 30\% of the time.
-This is a much higher value than in a real-world setting, but it is a balance between resources and realistic design.
-Alongside, this the first 5 trials of a new experiment will always be benign.
-This is to ensure users are lulled into a level of complacency regarding the possibility for an attack.
+Due to the scarcity of attacks in a real-world setting users are often complacent about their occurrence.
+Therefore, in this experiment, attacks only occur 30\% of the time.
+This occurrence is a much higher value than in a real-world setting, but it is a balance between resources and realistic design.
+Alongside, this the first 5 trials of a new experiment is always benign.
+This inclusion is to ensure users are lulled into a level of complacency regarding the possibility of an attack.
 
@@
 Therefore, this presents the possibility to have keys with a very low number of similar matches.
-The distribution of these keys will be explained further in Chapter \ref{cha:Experiments}.
-Therefore, if random sets of words were chosen with no restraints there are attacks presented to the user that in a real setting would be infeasible as they are close to a $2^{64}$ attack (4 Words * 16-bits).
-Therefore, the experiment will sample from a list of "vulnerable" keys.
-These are keys that have a number of combinations that allow an attack in a certain timeframe.
-Furthermore, certain levels of attacks are also simulated.
-Below are the list of possible attacks:
+The distribution of these keys is explained further in Chapter \ref{cha:Experiments}.
+Therefore, if random sets of words are chosen with no restraints, there are attacks presented to the user that in a real setting would be infeasible as they are close to a $2^{64}$ attack (4 Words * 16-bits).
+Therefore, the experiment is designed to sample from a list of "vulnerable" keys.
+These are keys that have a number of combinations that allow an attack in a specified timeframe.
+
+Furthermore, certain levels of attacks are also simulated. Below is the list of possible attacks:
 
@@
 The start and ends were chosen as the highest priority words to keep static.
-This is due to research highlighting on the common habit of users to only check the start and end of a checksum.
+This design choice is due to research highlighting on the common habit of users only to check the start and end of a checksum.
 \cite{cherubini2018towards} shows this by measuring user eye movement and displaying it as a heat map.
@@
 
-Figure \ref{fig:heatMap} shows the results of a eye tracking experiment where the user failed to detect a mismatching digest.
-As it can be clearly seen the users never compared the center of the digest.
+Figure \ref{fig:heatMap} shows the results of an eye-tracking experiment where the user failed to detect a mismatching digest. As it can be seen, the users never compared the centre of the digest.
 

### 2019-08-14 Writeup/Thesis/pages/evaluation.tex
Changes; - More corrections made

--- 2019-08-13 Thesis/pages/evaluation.tex
@@
 \section{Research Question \ref{goal:complexity}}
-Research Question \ref{goal:complexity}: \textit{``What is the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys was shown in Section \ref{sec:key_gen} where actual keys were generated.
+Research Question \ref{goal:complexity}: \textit{``What are the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys was shown in Section \ref{sec:key_gen} where actual keys were generated.
 Further more the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}.

### 2019-08-14 Writeup/Thesis/pages/lit_review.tex
Changes; - More corrections made

@@
 
-The organization of the section is as follows:
+The organisation of the section is as follows:
 
@@
 This level of entropy was inadequate even at the time of publication.
-There is an attempt by the authors' to address this issue in the later stages of the paper where they write \textit{``[...] increasing entropy is not a solution because it sacrifices usability and accuracy.
+There is an attempt by the authors' to address this issue in the later stages of the paper where they write: \textit{``[...] increasing entropy is not a solution because it sacrifices usability and accuracy.
 With more entropy, representations will contain longer sequences of characters or more minute details which will lead to increased time and errors during comparisons.''}.
@@
 To achieve this, the attacker would have to compute $2^{156}$ SHA-1 compressions to find a key match.
-In the literature, this element ranged from $2^{28}$ to around $2^{242}$; however, this has some relation to the size of the encoding schemes used.
-This is a substantial range that makes it ultimately challenging to compare and confer results confidently.
-Further work could exclusively look into the affects attacker strength has on the success of attacks.
+In the literature, this element ranged from $2^{28}$ to around $2^{242}$.
+However, this has some relation to the size of the encoding schemes used.
+This substantial range makes it challenging to compare and confer results confidently.
+Further work could exclusively look into the effects that attacker strength has on the success of attacks.
 Moreover, all the papers assessed failed to fully consider the feasibility of attacks in terms of computer and storage requirements.
-This again, shows gaps in the literature.
 
@@
 Their average ages were all around $\sim35$ years old with the majority of participants educated with at least a bachelor degree.
-This was alongside the equal split between male and female participants.
+Alongside, the equal split between male and female participants.
 
 One consideration of note is that made by Dechand \textit{et al.} \cite{dechand2016empirical} where they briefly consider medical conditions such as ADHD and reading or visual disorders and the way they affect the comparison's effectiveness.
-They highlight a slight reduction in overall accuracy, although due to their small sample size, they cannot conclusively validate these results.
-This is an aspect unique to all literature.
+The results highlight a slight reduction in overall accuracy, however, due to their small sample size, the results cannot be considered conclusive.
+This aspect is unique to all literature assessed.
 Further work would be required to produce conclusive results.
@@
 Different cultures contain inherent biases and assumptions.
-Moreover, more concerns are raised around the dual study design of this paper with two completely different set of participants.
 Changes were made pragmatically regarding the results from the first round of 40 participants.
-These were then re-assessed and the results were directly compared.
-This puts huge doubts on the validity of the results with no consideration made by the authors to control external factors that may affect the performance of the method of comparison.
+These were then re-assessed, alongside the direct comparison of results.
+This aspect casts vast doubts on the validity of the results with no consideration made by the authors to control external factors that may affect the performance of the method of comparison.
 
 Hexadecimal and numerical schemes were not included as encoding schemes in work by \textbf{Hsiao \textit{et al.}}\cite{hsiao2009study} (some of the most widespread encoding schemes).
-This decision was based on their claims on similarities to Base32 and ``well-known deficiencies" in the excluded schemes.
-This point was provided with no further justification or quantified in any way.
-It is also not consistent with available research, for example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}\cite{dechand2016empirical} it was shown numerical representations performed significantly better than that of Base32.
+The justification was the schemes similarities to Base32  alongside "well-known deficiencies".
+This point was provided with no further justification or quantified.
+Moreover, it is also inconsistent with available research, for example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}\cite{dechand2016empirical} it was shown numerical representations performed significantly better than that of Base32.
 
@@
 
-Table \ref{tab:attacker} has been provided to visually compare the differing aspects of the papers' parameters.
-Clearly it can be seen from the table the large ranges in participant size, entropy and attacker strength.
+Table \ref{tab:attacker} has been provided to compare the different aspects of the papers' parameters visually.
+It can be seen from the table the substantial ranges in participant size, entropy and attacker strength.
 
@@
 Recreation of pre-existing results from \cite{hsiao2009study}\cite{tan2017can} is required to corroborate current conclusions and validate results.
-Another gap in the research is the consideration into the utilization of encoding schemes in realistic conditions, i.e.
-``remove vs.
-proximity." This topic was initially covered by \cite{shirvanian2017pitfalls} but their scope was limited.
-Further work, therefore, could increased the scope and touch upon a large number of schemes in these settings.
+Another gap in the research is the consideration into the utilisation of encoding schemes in realistic conditions, i.e.
+``remove vs proximity." This topic was initially covered by \cite{shirvanian2017pitfalls}, but their scope was limited.
+Further work, therefore, could increase the scope and touch upon a large number of schemes in these settings.
 The final aspect for further work is the limited consideration into the feasibility of attacks on encoding schemes.
 All of the papers assessed simulated attacks and had minimal consideration for the execution of these attacks.
-Therefore, further work could delve into the implementation of such attacks and their feasibility in terms of compute and storage complexity.
+Therefore, further work could delve
+into the implementation and feasibility of such attacks.
 
@@
 Another area of research is investigations into the actual physical encodings of the hash digest.
-This section will briefly discuss the current research available on the creation and security of actual encoding schemes.
-The actual details of the operation of the schemes are outside the scope of this literature review, therefore, minimal attention will be allocated to these details.
+This section discusses the current research on the creation and security of actual encoding schemes.
+The technical details of the operation of the schemes are outside the scope of this literature review.
+Therefore, minimal attention is allocated to these details.
 
-Some of the oldest preliminary work into visual encoding schemes was performed by \textbf{Adrian Perrig \textit{et al}}\cite{perrig1999hash}.
-in the creation of their scheme ``Random Art" in 1999.
+Some of the oldest preliminary work into visual encoding schemes is by \textbf{Adrian Perrig \textit{et al.}}\cite{perrig1999hash} in the creation of their scheme ``Random Art" in 1999.
 The motivation for creating such a scheme was the perceived flaws in the ways humans verify and compare written information.
-As mentioned in previous sections visual encoding schemes have been shown to have mixed success, with low security being one of their most alarming flaws.
+As mentioned in previous sections, visual encoding schemes have been shown to have mixed success, with low security being one of their most alarming flaws.
 This research laid the foundation for further work in analysing the security of visual encoding schemes.
 
-Further research into the creation of unique visual hash schemes have been performed by \textbf{C Ellison \textit{et al.}} \cite{ellison2003public} (Flag), \textbf{Yue-Hsun Lin \textit{et al.}}\cite{lin2010spate} (T-Flag) and work by \textbf{M.
+Further research into the creation of unique visual hash schemes has been performed by \textbf{C Ellison \textit{et al.}} \cite{ellison2003public} (Flag), \textbf{Yue-Hsun Lin \textit{et al.}}\cite{lin2010spate} (T-Flag) and work by \textbf{M.
 Olembo \textit{et al.}}\cite{olembo2013developing}.
-Each publication has provided a new way to visually represent a key fingerprint.
-Alongside the academic literature, there are more informally presented methods of visual fingerprints such as Unicorns\footnote{https://unicornify.pictures/} and Robots\footnote{https://github.com/e1ven/Robohash}.
+Each publication has provided a new way  to represent a key fingerprint visually.
+Alongside the academic literature, there are informally presented methods of visual fingerprints such as Unicorns\footnote{https://unicornify.pictures/} and Robots\footnote{https://github.com/e1ven/Robohash}.
 This list is by no means exhaustive but is used to depict the amount of research and work invested into graphical hash representations.
 
-One paper of note is the preliminary work performed by \textbf{D Loss \textit{et al.}}\cite{loss2009drunken} in their \textit{``An analysis of the OpenSSH fingerprint visualization algorithm''} where their aim was to spur on further research with their initial findings into the security of the OpenSSH scheme.
-The authors claim that the use of the algorithm in OpenSSH is only heuristically defined and there is a need for a formal proof of its security.
-\\
-The paper proposed a number of ways to generate similar fingerprints.
+One paper of note is the preliminary work performed by \textbf{D Loss \textit{et al.}}\cite{loss2009drunken} in their \textit{``An analysis of the OpenSSH fingerprint visualisation algorithm''} where  they aimed to spur on further research with their initial findings into the security of the OpenSSH scheme.
+The authors claim that the use of the algorithm in OpenSSH is only heuristically justified, and a more formal proof is required.\\
+The paper proposed several ways to generate similar fingerprints.
 The methods proposed were: Naive brute force, Graph Theory, and brute force of a full visual set.
-They were only able to produce only very basic results and have proposed a large amount of potential further work.
+They were only able to produce only initial results and have proposed a large amount of potential further work.
 Since the paper's publication in 2009, there seems to have been no research building on the work of the authors.
-This highlights a current gap in the available literature.
 
-Minimal research has also focused on basic textual fingerprint representations and their respective security.
+Minimal research has also focused on elemental textual fingerprint representations and their security.
 Work by \textbf{A.
@@
 This research aim was to improve the secure device pairing process of comparing two numerical values.
-The devices used (Nokia 6030b; Mid-range devices at the time of publication) and the SAS compared results in findings that are not directly applicable in a fingerprint comparison context.
+The devices used (Nokia 6030b; Mid-range devices at the time of publication) and the SAS (Short Authentication String) compared results in findings that are not directly applicable in a fingerprint comparison context.
 
-A more specific subsection of textual fingerprints is the use of words and sentences to encode hash digests. Some of the first work in this area was produced by \textbf{Juola} and \textbf{Zimmermann}
-\cite{juola1996whole} and their work in generating a word list where phonetic distinctiveness was prioritised.
+A more specific subsection of textual fingerprints is the use of words and sentences to encode hash digests.
+Some of the first work in this area was by \textbf{Juola} and \textbf{Zimmermann} \cite{juola1996whole}.
+Their work aimed to produce a word list where phonetic distinctiveness was prioritised.
 Each word is mapped to a single byte.
-The unique aspect of the word list is the separation of ``even'' and ``odd'' words where ``even'' byte positions are sample from the even-list and ``odd'' from the odd-list.
-This effectively creates two sub-word lists.
-The maximisation of linguistic distinctiveness of these word lists were maximised through the use of a Genetic algorithm.
+The unique aspect of the word list is the separation of ``even'' and ``odd'' words where ``even'' byte indices are sample from the even-list and ``odd'' from the odd-list.
+This technique effectively creates two sub-word lists.
+A genetic algorithm was used to maximise linguistic distance.
 The paper also includes a study on effective measures of ``linguistic distances'' of words and provided an in-depth discussion into these areas.
@@
 Goodrich \textit{et al.}}\cite{goodrich2006loud} called \textit{Loud and Clear: Human-Verifiable Authentication Based on Audio}.
-As the name suggests the authors were researching ways to improve current methods of secure device pairing.
+As the name suggests, the authors were researching ways to improve current methods of secure device pairing.
 The unique aspect of this work is the use of a Text-to-Speech system reading out syntactically correct English sentences.
-The sentences are based on a MadLibs\footnote{https://en.wikipedia.org/wiki/Mad\_Libs} where static placeholders were replaced with potential words.\\
-The work into a potential wordlist can be seen as an extension to the work performed by Juola and Zimmermann\cite{juola1996whole} as they aimed to emulate the techniques used in PGPfone.
-The paper's finding are limited by the lack of empirical data backing up claims made by the author as the systems performance and security are only theoretically assessed.
+MadLibs\footnote{https://en.wikipedia.org/wiki/Mad\_Libs} was the base for these sentences.
+MadLibs is where static placeholders are replaced with a list potential words.\\
+This work is an extension to work performed by Juola and Zimmermann\cite{juola1996whole} as they aimed to emulate the techniques used in PGPfone.
+The paper's findings are limited by the lack of empirical data backing up claims made by the author the performance of the system, and security is only theoretically assessed.
 
@@
 This implementation was again, empirically evaluated by Dechand \textit{et al.}\cite{dechand2016empirical}.
-Older work by \textbf{N.
+Ealier work by \textbf{N.
 Haller} with the S/KEY\cite{haller1995s} shows the implementation of a system designed to represent a hash as a series of six short words.
@@
 \pep is a data encryption system that utilises PGP encryption to provide E2EE on all common channels of communication such as email or SMS.
-The imbedded design principles state that above all the systems should be easy to install, use and understand.
+The embedded design principles state that above all the systems should be easy to install, use and understand.
 
@@
 The users then authenticate the words on an OOB (Out of Band) channel such as a phone call or in-person communication.
-If both users decide the words match they will accept or decline respectively.
+If both users decide the words match, they accept or decline respectively.
 
 The unique aspect of TrustWords is its mapping of a single word to 16-bits.
-In comparison to other literature, this is the highest number of bits-per-word seen.
-Full mappings (no duplication of words) would, therefore, require $2^{16}$ words in the dictionary where arguably the dictionary size is higher than most users' vocabulary.
+If compared to alternative literature, this is the highest number of bits-per-word seen.
+Full mappings (no duplication of words) would, therefore, require $2^{16}$ words in the dictionary.
+This number of words is arguably higher than most users' vocabulary.
 This deviation from the norm has not been currently backed up by research.
@@
 
-Alongside the abnormally high number of words the design choice to exclude slang and profanities from the English Trustword dictionary requires dual-mapping of a section of words.
-Approximately 13633/65536 (20.8\%) of words are re-mapped in the dictionary leaving 51903 unique words.
-The re-mapping is also done on a loop with it remaining alphabetical.
+Alongside the abnormally high number of words, the design choice to exclude slang and profanities from the English Trustword dictionary requires dual-mapping of a section of words.
+Approximately 13633/65536 (20.8\%) of words are re-mapped in the dictionary, leaving 51903 unique words.
+The re-mapping looped with the dictionary remaining alphabetical.
 Figure \ref{fig:remap} shows the position in the dictionary where this occurs.
-This predictability within the dictionary will be explored later in the paper.
 
-Moreover the main RFC documentation still remains in a draft stage and states \textit{``It is for further study, what minimal number of words (or entropy) should be required.''}.
-These aspects clearly highlight on a gap in the current literature.
+Moreover, the primary RFC documentation remains in a draft stage and states: \textit{``It is for further study, what minimal number of words (or entropy) should be required.''}.
+These aspects highlight a substantial gap in the current literature.
 
@@
 \cite{juola1996whole} and M.
-Goodrich \textit{et al.}\cite{goodrich2006loud} providing meaningful research to build upon in terms of word a sentence based encodings.
+Goodrich \textit{et al.}\cite{goodrich2006loud} providing meaningful research to build upon in terms of word and sentence based encodings.
 The fragmentation of this research leaves room for further work into this topic area.
-Alongside this, findings from the previous sections research shows that human language based encodings provided the best usability and, therefore, should be a target for further research looking to improve upon their security and usability.
+Alongside this, findings from the previous section's research show that human language based encodings provided the best usability and, therefore, should be a target for further research looking to improve upon their security and usability.
 
@@
 This area of research studies ways to physically execute attacks on fingerprint encoding schemes.
-This differs from previously examined work due to papers discussing the performance and fallibility of encoding schemes simulated the attack without consideration for how the attack would be performed.
-Research in this area is scant, with lots of research attention being directed towards the security of Man-in-the-Middle (MITM) attacks and not the encoding schemes themselves.
+This topic differs from previously examined work due to papers discussing the performance and fallibility of encoding schemes simulated the attack without consideration for how the attack execution.
+Research in this area is scant, with lots of research attention on security of Man-in-the-Middle (MITM) attacks and not the encoding schemes themselves.
 
-Research in 2002 by \textbf{Konrad Rieck}\cite{rieck2002fuzzy} is the first formalisation of attacks on fingerprint representations.
-The paper titled \textit{``Fuzzy Fingerprints Attacking Vulnerabilities in the Human Brain''}
-aimed to look into ways users check hexadecimal encoded OpenSSH fingerprint representations.
-The author created an elegant way to `weight' more important chunks of the digest.
+Research in 2002 by \textbf{Konrad Rieck}\cite{rieck2002fuzzy} is one the first formalisation of attacks on fingerprint representations.
+The paper titled \textit{``Fuzzy Fingerprints Attacking Vulnerabilities in the Human Brain''} aimed to look into ways users check hexadecimal encoded OpenSSH fingerprint representations.
+The author created an elegant way to `weight' essential chunks of the digest.
 The bytes furthest to the right and left of the digests provided the highest weight.
-The weight was the smallest in the centre of the digest.
-This provides a way to score digests and determine the best partial collisions found.
-For example with the target fingerprint: \verb|9F23| a partial match \verb|9313| is given a score of 45\% even though only two characters were matching.
-This is due to the weightings.
+This technique provides a way to score digests and determine the best partial collisions found.
+For example, with the target fingerprint: \verb|9F23| and partial match \verb|9313| is given a score of 45\% even though only two characters are matching.
 
@@
 In comparison to this, a mid-range Intel i5-3320M CPU can today obtain 111,700,000 MD5 H/s.
-This shows that the results obtained from the paper are significantly outdated.
+This imbalance shows that the results obtained from the paper are significantly outdated.
 However, even with the low hash rate, the author was able to obtain some promising results.
@@
 
-Overall the paper shows an interesting way to create partial fingerprint matches but is not quantified by any empirical evidence gathered on real world users.
-This, therefore, highlights on gaps in the coverage of this literature.
+Overall the paper shows an interesting way to create partial fingerprint matches but is not quantified by any empirical evidence gathered on real-world users.
 
 The only other relevant research on this topic is the work by \textbf{M Shirvanian \textit{et al.}}\cite{shirvanian2014wiretapping} 
-and their paper \textit{``Wiretapping via Mimicry: Short 
+and their paper: \textit{``Wiretapping via Mimicry: Short 
 Voice Imitation Man-in-the-Middle Attacks on Crypto 
@@
 Further research in the area of ``human voice impersonation'' has received lots of attention \cite{mukhopadhyay2015all}\cite{chen2017you}\cite{wu2015spoofing}.
-This paper was chosen over other alternatives due to is specific use of encoding schemes in its evaluation.
+This paper was chosen over other alternatives due to its specific use of encoding schemes in its evaluation.
 
@@
 impersonate users when authenticating 
-Short-authentication-Strings (SAS) in pairing of 
+Short-authentication-Strings (SAS) in the pairing of 
 Crypto-phones. To achieve this impersonating they propose 
-two methods: ``Short voice reordering attack'' where an 
+two methods: ``Short voice re-ordering attack'' where an 
 arbitrary SAS string is recreated by re-ordering snipped 
@@
 previously eavesdropped audio snippets the attacker can
-morph their own voice to match that of the victim. With 
+morph their voice to match that of the victim. With 
 these methods, they aimed to attack encodings of Numbers, 
@@
 previously discussed). The effectiveness of these attacks 
-were evaluated with a study involving 30 participants.
+was evaluated with a study involving 30 participants.
 
@@
 methods. Compared to the baseline of the attacker's voice 
-replacing the victim where this performed with a 
-$\sim$18\% success rate. Morphing gained an 
-overall success rate of 50.58\% and Reordering a very 
-impressive 78.23\% success rate. Showing that these 
-attacks provide an improvement on top of the naive implementation.
+replacing the victim, performed with an $\sim$18\% success rate.
+Morphing gained an overall success rate of 50.58\% and re-ordering a very impressive 78.23\% success rate and showing that these attacks provide an improvement on top of the naive implementation.
 
-One of the biggest limitations addressed by the authors 
-was the reduction in success rates as the size of the 
-authentication string grew. The morphing and reordering 
-attacks become increasingly ineffective as the user has 
-more time to detect imperfections. This is not quantified by 
-the author and the extent of this degradation is never 
-empirically discussed. Therefore, the results from this 
-study are only effective and applicable in a SAS context.
+One of the most significant limitations addressed by the authors  was the reduction in success rates as the size of the authentication string grew.
+The morphing and re-ordering  attacks become increasingly ineffective as the user had more time to detect imperfections.
+This aspect is not quantified by the author and the extent of this degradation is never empirically discussed.
+Therefore, the results from this study are only effective and applicable in a SAS context.
 
@@
 Shirvanian et al.
-as it would arguably provide a better simulation of real world scenarios.
+as it would arguably provide a better simulation of real-world scenarios.
 
-In the context of human attributes and the way they alter the performance of the schemes; further research is required into how the fluency of languages affects authentication ceremony.
-This is a continuation of the initial work by Hsiao et al and could allow the creation of schemes that are better suited to certain languages.
+In the context of human demographics and the way they alter the performance of the schemes; further research is required into how the fluency of languages affects authentication ceremony.
+This further work would be a continuation of the initial work by Hsiao et al.
+and could allow the creation of schemes that are better suited to specific languages.
 Alongside this, there is a research gap in the investigation of how mental impairments affect the performance.
-This is useful due to the number of potential users being affected due to systems not being designed with them in mind.
-For example, 7\% of the population has been identified as having dyslexic tendencies\cite{peterson2012developmental}.
-This means with a UK population of around 63,000,000\footnote{From the 2011 Census collated by the Office for National Statistics}  4,410,000 people could benefit from encoding schemes including dyslexic oriented benefits.
-This is also only one of many visual impairments that could affect a scheme's performance, thus further contributing to the substantial affect further work could have on this area.
+This aspect is useful due to the number of potential users being affected due to systems not being designed with them in mind.
+For example, 7\% of the population have been identified as having dyslexic tendencies\cite{peterson2012developmental}.
+This fact means that with a UK population of around 63,000,000\footnote{From the 2011 Census collated by the Office for National Statistics}  4,410,000 people could benefit from encoding schemes designed to work well with dyslexia.
+Dyslexia, however, is only one of many impairments that could affect a scheme's performance, thus further contributing to the substantial effect further work could have on this area.
 
 Other possible large areas for consideration is the lacks of direct consideration for attack strength when assessing the vulnerability of encoding schemes.
-Issues included the wide range of attack strength ($2^{28}$ - $2^{242}$) and the lack of consideration at all from certain papers.
-This alongside the complete lack of computation and storage complexity considerations means this is a prime area for further research as it would improve the applicability of results.
+Issues included the previously discussed wide range of attack strength ($2^{28}$ - $2^{242}$) alongside the lack of consideration at all from the majority of papers.
+Moreover, the complete lack of computation and storage complexity considerations means this is a prime area for further research as it would improve the applicability of results.
 
-The final major research gap identified is the lack of justification into the newly created \pep Trustwords.
-Abnormal design choices (16-bit per word) and its recent creation makes it another area for a wide variety of further research.
-This is also combined with the conclusive results from the literature on the effectiveness of language based encodings such as words.
-This would suggest that research into the improvement of Trustword encoding would be highly beneficial.
+The final significant research gap identified is the lack of justification for the newly created Trustwords.
+Abnormal design choices (16-bit per word) and its recent creation alongside the shown effectiveness of language-based encodings, such as words makes this a promising area for further research.

### 2019-08-14 Writeup/Thesis/pages/research_question.tex
Changes; - More corrections made

@@
 
-Following on from the previous chapter, this chapter will define the selected gaps and the subsequent research questions and aims.
+This chapter defines the selected gaps and the subsequent research questions extracted.
 
-The chosen project aims to asses the security of \pep's minimum recommend number of four Trustwords (As stated in Figure \ref{fig:trustwordsNum}).
+The chosen project aims to asses the security of \pep's minimum recommendation of four Trustwords (As stated in Figure \ref{fig:trustwordsNum}).
 As discussed in the previous chapter, Trustwords aims to sacrifice security for increased usability.
 The encoding scheme has been designed to assist this by having  the user compare a reduced set of words.
-Moreover, issues with the dictionary's design such as the presence of homophones and dual-mapping of words shows the potential for possible vulnerabilities.
+Moreover, issues with the dictionary's design, such as the presence of homophones and dual-mapping of words show the potential for possible vulnerabilities.
 
 As discussed in the previous chapter, the identified research gap regarding the minimal consideration of attack complexity would be a suitable addition for this project.
-This is due to it providing the ability to asses actual performance and, thus, the actual real-world strength of Trustwords while providing research to a scant area.
-Therefore, the security assessment will be supplemented with complexity considerations and an actual implementation of the attack proposed.
+This choice is due to it providing the ability to asses actual performance and, thus, the actual real-world strength of Trustwords while providing research to a scant area.
+Therefore, the security assessment is supplemented with complexity considerations alongside an actual implementation of the attack proposed.
 
@@
 
-By sampling the \pep documentation they have defined the use case of the Trustword handshake: \textit{A handshake is done by comparing the Trustwords between two users through a separate communication channel (e.g.
-in person or by phone).}\footnote{https://www.pep.security/docs/general\_information.html\#handshake}.
-It can be assumed due to the increased globalization of the planet that the most common handshake occurrence will be over the phone, and, therefore, will not be in person.
-This is, therefore, the assumed context the handshake will be occurring in.
-This means the similarity of words will need to be quantified phonetically instead of visually.
+By sampling the \pep documentation they have defined the use case of the Trustword handshake: \textit{``A handshake is done by comparing the Trustwords between two users through a separate communication channel (e.g.
+in person or by phone)''.}\footnote{https://www.pep.security/docs/general\_information.html\#handshake}.
+It can be assumed due to the increased globalizatiohat is the time andn of the planet that the most common handshake occurrence is over the phone, and, therefore, not in person.
+This is the assumed context of the handshake.
+This means, to create near-matches, the similarity of words is quantified phonetically instead of visually.
 
@@
 
-With the previously discussed points in mind the following research questions have been proposed.
+With the previously discussed points in mind, the following research questions have been proposed.
 
@@
 
-    \item What is the time and computation complexity required to generate a 'similar' keys for a targeted key pair? \label{goal:complexity}
+    \item What are the time and computation complexity required to generate a 'similar' keys for a targeted key pair? \label{goal:complexity}
 
@@
 \end{enumerate}
-
-With these research questions defined, the project will now discuss the design of the proposed attack.

### 2019-08-15 Writeup/Thesis/diagrams/graphs/speed.tex
Changes; - More corrections made - Added a speed comparison graph

\begin{tikzpicture}[every axis plot/.append style={thick}]
    \begin{axis}[
        width=\linewidth,
        height=10cm,
        grid=major,
        xmin=1, xmax=40,
        % ymin=0, ymax=100,
        xlabel=Number of Keys,
        ylabel=Hashing speed (MH/s)
        ]
        \addplot table [x index=0, y index=1, mark=none, search path=data, col sep=comma]{scallion.csv};
        \addlegendentry{Scallion}

        \addplot table [x index=0, y index=1, mark=none, search path=data, col sep=comma]{green.csv};
        \addlegendentry{GreenOnion}	
     \end{axis}
\end{tikzpicture}

### 2019-08-15 Writeup/Thesis/pages/design.tex
Changes; - More corrections made - Added a speed comparison graph

@@
 
-Due to the scarcity of attacks in a real-world setting users are often complacent about their occurrence.
+Due to the scarcity of attacks in a real-world setting, users are often complacent about their occurrence.
 Therefore, in this experiment, attacks only occur 30\% of the time.
@@
 However, this may not be applicable in this context due to the user being linearly fed an audio stream that they cannot skip to the start or end.
-We believe, however, that attention will also play a part in defining the most important areas of comparison.
-The hypothesis is that the users attention will be lower in the middle sections of comparison where it peak at the start and end.
-All these aspects will require empirical evidence to arrive at a conclusion.
-Therefore, this consideration will need to be made when assessing the results of the experiment.
+We believe, however, that attention also plays a part in defining the most important areas of comparison.
+The hypothesis is that the users' attention is lower in the middle sections of comparison, where it peaks at the start and end.
+All of these aspects require empirical evidence to conclude.
+Therefore, this requires consideration when assessing the results of the experiment.
 
 These attacks are ascending in complexity.
-The timeframe for finding a match was decided as 7-days with attack strengths of 1 GPU/day, 10 GPU/days and 100 GPU/days on a mid range GPU (AMD RX 480 was the example in experiments).
-Due to the long life time of PGP keys, 7 days was chosen as a reasonable length of attack, attackers can just leave the tool and have it compute potential keys for the target without any need for user engagement.
-This is also a maximum time, these attacks also include keys that have a shorter average computation time.
+The timeframe for finding a match was decided as 7-days with attack strengths of 1 GPU/day, 10 GPU/days and 100 GPU/days on a mid-range GPU (AMD RX 480 was the example in experiments).
+Due to the long lifetime of PGP keys, 7 days was chosen as a reasonable length of the attack.
+The tool requires no user interaction once started, therefore, it can be left for an extended period to compute potential keys.
+This timeframe is also a maximum time, these attacks also include keys that have a shorter average computation time.
 
@@
 Table \ref{tab:attackReq} contains a summary of the different level of attacks and their respective restrictions.
-More combinations makes the attack search quicker as there are more possibilities.
-Any key that exceeds this criteria is deemed as vulnerable is one of the three attack contexts.
-A list of these vulnerable keys are sampled from when an attack is simulated.
-The percentage of vulnerable keys will be explored in Chapter \ref{cha:Experiments}.
+More combinations make the attack search quicker.
+Any key that exceeds this criterion is deemed as vulnerable.
+A list of these vulnerable keys is sampled from when an attack is simulated.
+The percentage of vulnerable keys is explored in Chapter \ref{cha:Experiments}.
 
@@
 \label{sec:exp2_quality}
-As the previous experiment, participants will be sourced from MTurk.
-Therefore, again, quality control is and aspect that requires consideration.
-As with the previous study, initially screened native speakers will be used.
-The same process will be performed to recruit suitable workers.
-Two metrics will be used to detect invalid results.
-Audio button clicks and overall time taken.
+Like the previous experiment, participants are sourced from MTurk.
+Therefore, again, quality control is an aspect that requires consideration.
+As with the previous study, initially screened native speakers are used, alongside the utilisation of the same process to recruit suitable workers.
+Two metrics are used to detect invalid results: audio-button-clicks and the overall-time.
 
-Audio buttons clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:expID} is clicked.
+Audio-buttons-clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:expID} is clicked.
 If there are rounds without button clicks, this is a sign of non-attentiveness.
 The design choice was made to keep this as a result filter, as preventing non-clicks would be a trivial task.
-This provides a way to detect and discard click-throughs\footnote{Workers that aim to complete the task as fast as possible, with no regard for the quality of responses}.
+This design provides a way to detect and discard click-throughs\footnote{Workers that aim to complete the task as fast as possible, with no regard for the quality of responses}.
 
-Overall time taken is as the name suggest a recording of the time taken to complete the entire experiment.
-If users complete the experiment in an abnormally small amount of time it can be used as another detection for invalid responses.
-Anything below a certain threshold will be discarded.
+Overall-time is as the name suggest a recording of the time taken to complete the entire experiment.
+If users complete the experiment in an abnormally small amount of time, it can be used as another detection for invalid responses.
+Anything below a certain threshold is discarded.
 
 \subsubsection{Considerations}
-As with the previous experiment MTurk demographics will result in participants that are not reflective of the general population.
-Due to the attack context of this experiment is can be assumed that the youth of the participants will contribute to less successful attacks.
-Therefore, the results generated by this experiment can be loosely assumed as a best case scenario for the scheme.
+As with the previous experiment, sampling from a  MTurk demographics results in a collection of participants that are not reflective of the general population.
+Due to the attack context of this experiment is can be assumed that the youth of the participants contributes to less successful attacks.
+Therefore, the results generated by this experiment can be loosely assumed as a best-case scenario for the scheme.
 We predict a high attack success rate if assessed over the general population.

### 2019-08-15 Writeup/Thesis/pages/evaluation.tex
Changes; - More corrections made - Added a speed comparison graph

@@
 This chapter will collate the findings of the paper, evaluate the paper's success against the research questions and discuss potential further work.
-
-\section{Research Question \ref{goal:numberOfTrustwords}}
-Research Question \ref{goal:numberOfTrustwords} states \textit{`` Is the recommended minimum number of four Trustwords enough to provide a basic level of security?''}.
-The paper has investigated this through the creation of an attack and quantification of its success on actual participants.
-Findings have shown that an attack computed in half a day can have a success rate of about 9.35\%.
-A user, therefore, could initiate this attack on-mass with hardware present inside the average gaming computer.
-On the other hand, the best level of attack success was show to be 32.05\%.
-
-Further more, comparison of these results to similar literature show a huge increase in success rates for the attack present in this paper.
-All alternative literature used a small dictionary of around 1024 words.
-This, therefore, is highly suggestive that the issue lies with the design of Trustwords.
-Therefore, we believe that 4 Trustwords as a minimum has not provided a basic level of security towards users.
-
-\todo{Make this the last question to answer}
 
@@
 To achieve this the tool GreenOnion was developed where inspiration was gathered from a currently available tool known as Scallion.
-Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for.
-
-\todo{Give some tasty stats}
+Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for with GreenOnion being able to handle in excess of 1.5 million keys.
+This is in comparison to maximum of 40 keys Scallion can compare.
 
@@
 Therefore, showing the number attacks would deceive a set assessed users.
+
+\section{Research Question \ref{goal:numberOfTrustwords}}
+Research Question \ref{goal:numberOfTrustwords} states \textit{`` Is the recommended minimum number of four Trustwords enough to provide a basic level of security?''}.
+The paper has investigated this through the creation of an attack and quantification of its success on actual participants.
+Findings have shown that an attack computed in half a day can have a success rate of about 9.35\%.
+A user, therefore, could initiate this attack on-mass with hardware present inside the average gaming computer.
+On the other hand, the best level of attack success was show to be 32.05\%.
+
+Further more, comparison of these results to similar literature show a huge increase in success rates for the attack present in this paper.
+All alternative literature used a small dictionary of around 1024 words.
+This, therefore, is highly suggestive that the issue lies with the design of Trustwords.
+Therefore, we believe that 4 Trustwords as a minimum has not provided a basic level of security towards users.
 

### 2019-08-15 Writeup/Thesis/pages/experiments.tex
Changes; - More corrections made - Added a speed comparison graph

@@
 \label{sec:SvG}
-This section will compare Scallion and the newly designed GreenOnion ability to search for a large number of potential keys.
 
-Table \ref{tab:scallion_speed} shows the speed decline as the number of keys increase. Any number of keys over 45 resulted in a crash to the program.
-
-\todo{Add screenshot of the exception}
-
-\begin{table}[!h]
+\begin{wraptable}[11]{r}{6cm}
     \centering
@@
     \caption{Testing environment}
-\end{table}
+\end{wraptable}
 
-\begin{table}[!h]
+\begin{figure}[h!]
     \centering
-    \begin{tabular}{|ll|}
-        \hline
-        \textbf{Number of keys} & \textbf{Speed} \\
-        \hline
-        1 & 1001.3 MH/s \\
-        5 & 784.3 MH/s \\
-        10 & 707.9 MH/s \\
-        15 & 628.2 MH/s \\
-        20 & 526.5 MH/s \\
-        25 & 503.8 MH/s \\
-        30 & 473.1 MH/s \\
-        35 & 432.6 MH/s \\
-        40 & 404.9 MH/s \\
-        45+ & \textit{N/A} \\
-        \hline
-    \end{tabular}
-    \caption{Scallion's speed decline}
+    \input{diagrams/graphs/speed.tex}
     \label{tab:scallion_speed}
-\end{table}
-\todo{Plot scallion speed decline}
+    \caption{Speed comparison between Scallion and GreenOnion}
+\end{figure}
 
-\todo{Show the maximum number of keys the tool can achive}
+This section compares Scallion and the newly designed GreenOnion ability to search for a large number of potential keys.
+
+Figure \ref{tab:scallion_speed} shows the speed decline as the number of keys increases for Scallion.
+Any number of keys over 40 resulted in a crash for Scallion.
+GreenOnion's speed is almost perfectly consistent.
+It is slower up until  around 5 keys.
+This consistency is due to the overhead of the bloom filter; however, as the number of keys increase, the bloom filter's benefits become apparent.
+In this test, the bloom filter size was kept consistent at exactly 5,000 elements.
+
+GreenOnion has been tested to handle more than 1.5 million keys with a slight reduction in performance. This improvement over Scallion is, therefore, substantial.
 
 \section{Experiment 1 - Metric performance}
-\todo{talk about participants like the second experiment with Stdev}
 
-As discussed in Section \ref{exp:metric} the goal of the experiment was the cull the number of metrics to be assessed in the following experiment.
+As discussed in Section \ref{exp:metric}, the goal of the experiment was the cull the number of metrics to be assessed in the following experiment.
 This section will discuss the demographics of participants alongside the subsequent results.
@@
         \hline
-        Gender & Male: & 46.2\% \\
-               & Female: & 53.8\% \\
+        Gender & Male: & 44.44\% \\
+               & Female: & 55.56\% \\
         \hline
-        Age:   & 18-24: & 10.6\% \\ 
-               & 25-29: & 20.2\% \\ 
-               & 30-39: & 30.8\% \\ 
-               & 40-49: & 22.1\% \\ 
-               & 50-59: & 11.5\% \\ 
-               & 60-69: & 3.8\% \\ 
-               & 70-79: & 1.0\% \\
+        Age:   & 18-24: & 10.10\% \\
+               & 25-29: & 20.20\% \\
+               & 30-39: & 31.31\% \\
+               & 40-49: & 21.21\% \\
+               & 50-59: & 12.12\% \\
+               & 60-69: & ~~4.04\% \\ 
+               & 70-79: & ~~1.01\% \\
 
@@
         Highest Education:  
-        & GCSE:                 & 15.4\%  \\
-        & A-Level/O-Level:      & 18.3\% \\
-        & Bachelor's degree:    & 51.0\% \\
-        & Master's degree:      & 13.5\% \\ 
-        & PhD:                  & 1.9\% \\
+        & GCSE:                 & 13.13\% \\
+        & A-Level/O-Level:      & 19.19\% \\
+        & Bachelor's degree:    & 52.53\% \\
+        & Master's degree:      & 13.13\% \\ 
+        & PhD:                  & ~~2.02\%  \\
         \hline
@@
 
-\begin{table}[h!]
+Overall, 104 participants were assessed in this study.
+Five results were discarded from the set due to either failing the attention questions (See in Section \ref{sec:exp1_qualitycontrol}) or having too low of a fluency rating.
+This dismissal was a necessary process to improve the health of the results.
+
+Table \ref{tab:exp1_demo} contains the demographical breakdown of the reduced set of participants.
+The average ages of the participants were 37.3 years ($\sigma = 11.67$)with a split of 44.44\% of Males to 55.56\% of Females.
+As can be seen, over 60\% of participants can be considered highly educated (Bachelor’s and up).
+This level of education is not sufficiently reflective of the general population and therefore, has to be considered when interpreting the results.
+All participants were sourced from the US; this again requires consideration due to the broad range of dialects present that may bias the results.
+Further work could investigate the effect of location and dialect on similar results.
+
+\begin{wraptable}[11]{r}{8cm}
     \centering
@@
     \label{tab:exp1_results}
-\end{table}
-
-Table \ref{tab:exp1_demo} contains the demographical breakdown of the participants assessed.
-As it can be seen over 60\% of participants can be considered highly educated (Bachelor’s and up).
-This is not fully reflective of the general population and therefore, has to be considered when interpreting the results.
-All participants were sourced from the US, this again requires consideration due to the large range of dialects present that may bias the results.
-Further work could investigate the affect of location and dialect on similar results.
-
-Overall, 104 participants were assessed in this study.
-Five results were discarded from the set due to either failing the attention questions (See in Section \ref{sec:exp1_qualitycontrol}) or having too low of a fluency rating.
-This was a necessary process to improve the health of the results.
+\end{wraptable}
 
@@
 The breakdown of the ratings in Figure \ref{fig:exp1_breakdown} also shows Levenshtein's dominance.
-Levenshtein has a much larger proportion of 4 and 5 ratings than the alternatives.
+Levenshtein has a much more significant proportion of 4 and 5 ratings than the alternatives.
 This performance may, however, be due to the visual way the comparisons are being performed.
@@
 Due to the averages of Metaphone and Phonetic Vectors being so close standard deviation was used as the final decider.
-As it can be seen Megaphone has a slightly lower $\sigma$ value of that of Phonetic vectors, thus, contributing to the decision to select Metaphone to be carried over to the next experiment.
+As can be seen, Megaphone has a slightly lower $\sigma$ value of that of Phonetic vectors, thus, contributing to the decision to select Metaphone.
 
 \subsection*{Considerations}
-As discussed in Section \ref{sec:exp1_considerations} compromises were made in order to fullfil all requirement with a minimized cost.
+As discussed in Section \ref{sec:exp1_considerations}, compromises were made to fulfil all requirement with a minimized cost.
 Levenshtein's abnormal performance further backs up concerns around the visual aspect biasing the performance of the metric.
-This will have to be considered when interpreting the results.
+This aspect requires consideration when interpreting the results.
 
-Even with the discussed issues, the aim of the experiment was to promptly reduce the number of metrics for use later in the project.
+Even with the discussed issues, the experiment was designed to reduce the number of metrics promptly.
 This experiment, therefore, has achieved that goal of providing three metrics for the subsequent experiment while balancing between accuracy and expenditure.
 The results are also an improvement over informal ad-hoc methods.
-Further work could aim to reproduce this study with the proposed audio based design (See Section \ref{sec:exp1_considerations}).
+Further work could aim to reproduce this study with the proposed audio-based design (See Section \ref{sec:exp1_considerations}).
 
@@
 \label{sec:exp2}
-The aim of this experiment is to quantify the success rate of the proposed attack.
+This experiment aims to quantify the success rate of the proposed attack.
 Design details for this experiment can be seen in Section \ref{sec:exp2_design}.
-This section will present and discuss the results of the experiment alongside a comparison to relevant literature.
+This section presents and discusses the results of the experiment alongside a comparison to relevant literature.
 
@@
 Around 62\% of participants had completed a single stage of university (Bachelor and up).
-This makes this set of participants more educated than the general population.
+This aspect makes this set of participants more educated than the general population.
 All participants were also sourced from the USA and have rated themselves as fully native English speakers.
@@
 As user-agent strings were collected for each participant collations of OS and internet browser versions was made possible.
-Tables \ref{tab:exp2_browser} and \ref{tab:exp2_os} contain the browser and OS breakdowns respectively.
+Tables \ref{tab:exp2_browser} and \ref{tab:exp2_os} contain the browser and OS breakdowns,  respectively.
 Chrome and Windows 10 seem to dominate the proportion of their respective domains alongside the surprisingly large proportion of workers utilizing older versions of Windows such as 7 or 8 (15.81\%).
@@
 It can be seen that the best metric out of the set was Levenshtein with an overall success of 19.80\%.
-The best performer when regarding attack strength, as expected is the 2 static words.
+The best performer, when regarding attack strength, as expected, is the 2 static words.
 Levenshtein's 2 static attack performed the best overall with a success rate of 32.05\%.
-The worst performer was Metaphone with an average of 16.88\% over its three levels of attacks.
-When comparing the performance of the metrics to the previous experiment the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in exactly the same order.
+The worst performer was Metaphone, with an average of 16.88\% over its three levels of attacks.
+When comparing the performance of the metrics to the previous experiment the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in the same order.
 
@@
 As previously mentioned, the set of recruited participants are more highly educated than the general population.
-This combined with the low average age contributes to an inevitable bias being introduced into the data.
-An assumption can be made that higher education leads to more skillful interaction with computer based systems, this, therefore, with the previous assumption in mind means the results of this experiment can be considered a `best case' scenario.
+This.
+combined with the lower average age, contributes to an inevitable bias being introduced into the data.
+An assumption can be made that higher education leads to more skilful interaction with computer-based systems, this, therefore, with the previous assumption in mind means the results of this experiment can be considered a `best case' scenario.
 The attacks, therefore, would be expected to be more successful on less technical users.
-This, however, requires further research and possible empirical data to determine the validity of the assumption.
+This consideration, however, requires further research and possible empirical data to determine the validity of the assumption.
 
-During this study the main task was to perform the authentication ceremony a large number of times.
-In the real-world the ceremony is a secondary task due to it not strictly being required.
-This alongside the potential for users to downplay the possibility of attack leads to the conclusion that the success rates could be much higher in a real-world setting.
-The assumption is that these results display the success rate for extremely attentive users where they will make sure to double check with their authentication partner multiple times.
-This is opposed to the assumption that the majority of users will aim to complete the task as quickly as possible.
+During this study, the main task was to perform the authentication ceremony a set number of times.
+In the real-world, the ceremony is a secondary task due to it not strictly being required.
+This aspect, alongside the potential for users to downplay the possibility of attack, leads to the conclusion that the success rates could be much higher in a real-world setting.
+The assumption is that these results display the success rate for extremely attentive users where they make sure to double-check with their authentication partner multiple times.
+It is, therefore, assumed that the majority of users aim to complete the task as quickly as possible, if at all.
 
 \subsection*{Comparison to alternative literature}
-This section will aim to compare the results of the experiment to similar literature.
+This section compares the results of the experiment to similar literature.
 
-Work by Kainda \textit{et al.}\cite{kainda2009usability} (previous discussed in Chapter \ref{cha:LiteratureReview}) is the most comparable to this experiment.
-They were the only study to use exactly 4 words, but differed on the size of dictionary (1024 words) and how a near-match was calculated.
-Near-matches were a difference in a single word but without the consideration for similarity, this is the unique aspect considered with this experiment.
+Work by Kainda \textit{et al.}\cite{kainda2009usability} (previously discussed in Chapter \ref{cha:LiteratureReview}) is the most comparable to this experiment.
+They were the only study to use exactly 4 words but differed on the size of the dictionary (1024 words) and how a near-match were calculated.
+Near-matches were a difference in a single word, but without the consideration for similarity, this is the unique aspect considered with this experiment.
 
-However, with those aspect in mind attacks on words encoding received an overall success rating of 3.3\%, considerably lower than that of this study.
-In the worst case our simulated attacks achieved almost 3 times as many successes compared to this study.
+However, with those aspects in mind attacks on words encoding received an overall success rating of 3.3\%, considerably lower than that of this study.
+In the worst-case, our simulated attacks achieved almost 3 times as many successes compared to this study.
 
 Other relevant work by Dechand \textit{el al.}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words.
-This is less similar to the experiment as 14 words per attack were assessed with each participant, where the comparison was performed visually.
-However, the success for the PGP Word list was 8.78\%.
-As 10/14 words were kept static more comparable to the results of the highest attack strength ``2 static''.
-This leads to another 3 fold improvement in the success rates of our simulated attacks.
+Their experiment is less similar as 14 words per attack were assessed with each participant, where the comparison was performed visually.
+However, the success was 8.78\%.
+As 10/14 words were kept static, this result is more comparable to the highest attack strength ``2 static''.
+This, therefore, leads to another 3 fold improvement in the success rates of our simulated attacks.
 
@@
 This paper had the highest number of words assessed with 16 overall.
-With it assessing the same wordlist and attack strength as the work by Dechand \textit{et al.}.
-The attack success was 14\% overall, this again compared to the highest attack assessed in the experiment results in a sizeable difference.
+With it assessing the same wordlist and attack strength as the work by Dechand \textit{et al.}, the attack success was 14\% overall.
+This success rate compared to the highest attack assessed in the experiment results in another sizeable difference.
 
-In conclusion, all similar literature had much lower attack success rates that the results presented in this experiment.
-With all papers using similarly designed words lists it highly suggests that the deficiencies in Trustwords are the cause for the substantial increase in attack success.
+In conclusion, all related literature had much lower attack success rates that the results presented in this experiment.
+With all papers using similarly designed wordslists, it highly suggests that the deficiencies in Trustwords are the cause for the substantial increase in attack success.
 Alongside this, the consideration for similarity when calculating near-collisions could have also resulted in the higher attack success rates.
-This aspect is also a unique consideration compared to available literature.
+This aspect is also a unique consideration compared to the available literature.
 

### 2019-08-15 Writeup/Thesis/pages/implementation.tex
Changes; - More corrections made - Added a speed comparison graph

@@
 
-This chapter will discuss implementation details of the project.
-Instead of explaining all the technical achievements in detail, the most interesting ones will be discussed alongside the respective challenges encountered.
+This chapter discusses the implementation details of the project.
+Instead of explaining all the technical achievements in detail, the most interesting ones are discussed alongside the respective challenges encountered.
 
@@
 \subsubsection{General design}
-This section will briefly discuss the overall technical implementation of GreenOnion alongside a deeper discussion into the unique aspect of the tool.
+This section briefly discusses the overall technical implementation of GreenOnion alongside a more in-depth discussion into the unique aspect of the tool.
 
@@
 This exponent is then incremented to create a new unique key.
-This allows rapid generation of new keys due to the reduction in expensive large prime generation.
-This prevents issues in such as entropy starvation when generating a large number of RSA keys.
-This produces valid keys but with abnormally large exponents, this was deemed as suitable due to the short term use-case for these keys.
-3 bytes are used to represent the exponent giving the potential to create $2^{24} - 1$ extra keys for a single expensive key generation.
+This technique allows the accelerated generation of new keys due to the reduction in expensive large prime generation.
+Entropy starvation is an example of a common issue encountered when generating a large number of RSA keys.
+This process produces valid keys, but with abnormally large exponents, this was deemed suitable due to the short term use-case for these keys.
+Three bytes are used to represent the exponent giving the potential to create $2^{24} - 1$ extra keys for a single expensive key generation.
 
-All keys plus the intermediate hash are loaded on the GPU via an OpenCL kernel.
+All keys including the intermediate hash are loaded on the GPU via an OpenCL kernel.
 This kernel is designed to hash the final block, obtain the final fingerprint and check if the fingerprint is present in the provided list.
@@
 
-Mass checking of fingerprints is the tools main ability as it allows for millions of keys to be checked with a very small amount of overhead.
-This is achieved through the use of a bloom filter.
-A bloom filter is a probabilistic data structure that allows efficient checking for presence of an element in a set.
-It is effectively a very large array of booleans that state wether an element is present.
-The index in the array is decided by a pre-defined hashing algorithm.
-This is repeated a number of times with a number of hashing algorithms ($k$) to populate the array of length ($m$).
-This then means checking the presence of an element in the set just means hashing the target and checking the indices returned.
-This data structure therefore has a complexity of $O(k)$ regardless of the number of elements in the set.
+Mass checking of fingerprints is the tool's central ability as it allows for millions of keys to be checked with a minimal amount of overhead.
+This functionality is achieved through the use of a bloom filter.
+A bloom filter is a probabilistic data structure that allows efficient checking for the presence of an element in a set.
+It is effectively a vast array of booleans that state whether an element is present.
+A pre-defined hashing algorithm decides the index in the array.
+This process is repeated several times with a set number of hashing algorithms ($k$) to populate the array of length ($m$).
+To check the presence of an element in the set means hashing the target value and checking the indices returned.
+This data structure, therefore, has a complexity of $O(k)$ regardless of the number of elements in the set.
 This is the only data structure that provides this characteristic.
+This benefit comes at a cost.
+Due to the use of hashing algorithms, there is the possibility for collisions and, thus, the possibility of false-positives.
+The data structure, however, does not produce any false-negatives.
 
-However, there is the possibility for collisions and, thus, the possibility of false-positives.
-The data structure, however, does not produce any false-negatives.
-This, therefore, makes it fully suited to this use-case as any fingerprints tagged as ``possibly'' being present in the bloom filter can be followed up with a more expensive hash-table check to determine their actual presence.
-Therefore, if the levels of false-positives are controlled (by altering $k$ and $m$) the tool can search through huge number of potential keys without any decrease in speed.
+These qualities, therefore, makes it fully suited to this use-case as any fingerprints tagged as ``possibly'' being present in the bloom filter can be followed up with a more expensive hash-table check to determine their actual presence.
+Therefore, if the levels of false-positives are controlled (by altering $k$ and $m$), the tool can search through a vast number of potential keys without any decrease in speed.
 
@@
 Figure \ref{fig:bloom} shows the operation of a simple bloom filter.
-As it can be seen the element $n$ definitely does not exist in the set due to both array indices not being set.
-The performance boost when comparing large numbers of keys is substantial when compared to the similar tool Scallion (See Section \ref{sec:greenDesign}.) The results from the comparison will be quantified in Chapter \ref{cha:Experiments}.
+As can be seen, the element $n$ does not exist in the set due to both array indices not being set.
+The performance boost when comparing large numbers of keys is substantial when compared to a similar tool Scallion (See Section \ref{sec:greenDesign}.) The results from the comparison are quantified in Chapter \ref{cha:Experiments}.
 
@@
 
-In order to process a substantial number of keys in a concurrent fashion OpenCL was required. Figure \ref{fig:opencl} contains the main sections of the code uploaded to the GPU.
+In order to process a substantial number of keys in a concurrent fashion, OpenCL was required. Figure \ref{fig:opencl} contains the main sections of the code uploaded to the GPU.
 
@@
 
-The \verb|<EXPONENT_INCREMENTING_CODE>| will be explained in the next section.
-After the exponent is incremented the code produces the final digest by calling \verb|sha1_block(W, H)|.
+The \verb|<EXPONENT_INCREMENTING_CODE>| is explained in the next section.
+After the exponent is incremented, the code produces the final digest by calling \verb|sha1_block(W, H)|.
 The 32-bit left and right sections of the digest are hashed using the MurmurHash algorithm.
 MurmurHash does not exhibit features suitable for secure hashing as it can be trivially reversed.
-Its use-cases include hash based lookups due to its speed and its distributive properties, making it suitable to work well with a bloom filter.
+Its use-cases include hash-based lookups due to its speed and its distributive properties, making it suitable to work well with a bloom filter.
 The hashed values are then checked against the bloom filter array.
@@
 The minimal amount of data returned to the CPU via the \verb|outResult| variable is due to efficiency reasons.
-Use of this memory is computationally expensive, therefore, at every opportunity writing or reading this memory has been avoided.
+Use of this memory is computationally expensive; therefore, at every opportunity, writing or reading this memory has been avoided.
 
@@
 Figure \ref{fig:increment} contains the code used to increment the exponent.
-Due to the exponent being split across two words alongside the limited functionality of OpenCL, bitwise operations were chosen as the solution to the incrementation.
-The code utilise the fact that anything XORed with itself becomes zero alongside the fact that XORing a value $a$ with zero provides the result equal to $a$.
-This will allow us to replace values using binary operations.
-The code manipulates the position of values by multiplication or division  of base-16 values, these shift the hex value either left of right respectively.
+Due to the exponent being split across two words alongside the limited functionality of OpenCL, bitwise operations to increment the exponent.
+The code utilises the fact that anything XORed with itself becomes zero alongside the fact that XORing a value $a$ with zero provides the result equal to $a$.
+The code manipulates the position of values by multiplication or division  of base-16 values; these shift the hex value either left or right, respectively.
 Once it is in position the "Mask" is created by XORing with the original value and the new intended value, this stores the changes required to reach the required values, this then applied to each of the words.
-The \verb|get_global_id| command takes the ID from the currently running thread, this allows a different value to be used for each exponent and allows the code to be run concurrently.
+The \verb|get_global_id| command takes the ID from the currently running thread; this allows a different value to be used for each exponent concurrently
 
 \section{First Experiment}
-In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}) Google Forms\footnote{\url{https://www.google.com/forms}} was used to host and design the questionnaire.
-It provided functionality to easily present questions and record their responses.
-However, as the design requirement of refreshing questions after each submission was not part of the main applications functionality an extra solution was required.
-This was solved by Google's App Script\footnote{\url{https://developers.google.com/apps-script/}} service that allows a user to programmatically interact with the Form.
-This allowed the re-sampling of matches each time a user submitted a response.
+In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}), Google Forms\footnote{\url{https://www.google.com/forms}} was used to host and design the questionnaire.
+It provided the functionality to present questions easily and record responses.
+However, as the design requirement of refreshing questions after each submission was not part of the main applications functionality, an extra solution was required.
+This problem was solved by Google's App Script\footnote{\url{https://developers.google.com/apps-script/}} service that allows a user to interact with the Form programmatically.
+This addition allowed the re-sampling of matches each time a user submitted a response.
 
@@
 Figure \ref{fig:GoogleAppScript} contains an interesting snippet from the script used in the experiment.
-Each time a user submitted their response the \verb|updateForm()| endpoint was called, that subsequently updated the questions for the next user.
-This aimed to keep the samplings fair as they are equally likely to appear when attacking the system.
+Each time a user submitted their response, the \verb|updateForm()| endpoint was called, that subsequently updated the questions for the next user.
+This technique aimed to keep the samplings fair as they are equally likely to appear when attacking the system.
 
@@
 \section{MainExperiment}
-In order to assess users in a similar scenario to ones experienced when utilizing \pep in the real-world a custom application was required.
-The front-end is developed in Javascript with a Python-Flask backend that acts as the webpages functionality.
-A number of end points are exposed like \verb|get_audio| or \verb|get_words| that are requested and displayed on the front-end.
+In order to assess users in a similar scenario to ones experienced when utilizing \pep in the real-world, a custom application was required.
+The front-end is developed in Javascript with a Python-Flask backend that acts as the functionality of the webpage.
+Several endpoints are exposed like \verb|get_audio| or \verb|get_words| that are requested and displayed on the front-end.
 
 One of the main problems encountered was the handling of each user's session.
-Initially during testing it was noted that changes in one end-point if timed correctly would overwrite the progress of another, this is commonly known as a ``Lost update''.
-This was due to the user session being stored in the \verb|session| cookie.
-When sending off a request the session cookie is included in the header, the code will then utilise the data within the cookie to make decision and alter state, the updated state is then returned as a cookie in the response.
-If, however, another request is executed before the first has completed, the second request is using the context of the first request and, thus, any alterations made by the first will be completely lost.
+Initially, during testing, it was noted that changes in one endpoint if timed correctly would overwrite the progress of another, this is commonly known as a ``Lost update''.
+This issue was due to the user session being stored in the \verb|session| cookie.
+When sending off a request the session cookie is included in the header, the code then utilises the data within the cookie to make decisions and alter state, the updated state is then returned as a cookie in the response.
+If, however, another request is executed before the first has completed, the second request is using the context of the first request and, thus, any alterations made by the first is completely lost.
 
@@
 Figure \ref{fig:cookie} shows this problem visually.
-As it can be seen the response cookie $c_2$ is based off the old data of $c$.
-When $c_2$ is eventually returned it will remove the progress of $c_1$.
-To keep the complexity of the backend as low as possible it was opted to solve this problem by restricting the user via the UI.
-When a button was clicked all other operations were disabled until a response was received.
-This stopped the possibility of sending off another request while another is still processing.
+As it can be seen the response cookie $c_2$ is based on the old data of $c$.
+When $c_2$ is eventually returned, it removes the progress of $c_1$.
+The restriction of the UI solved this problem.
+When a button is clicked, all other operations are disabled until a response is received.
+This technique stopped the possibility of sending off another request while another is still processing.
+This solution was chosen to keep the complexity of the backend low.
 
-In order to collate data for results later in the process state had to be saved.
+In order to collate data for results later in the process, the state had to be retained.
 One potential solution would be to format the data and save it as a .csv file.
 However, this is a static way of data persistence and would require alteration every time the data schema was modified.
-The chosen solution utilized a python object serialization library known as `Pickle'\footnote{\url{https://docs.python.org/2/library/pickle.html}}.
+The chosen solution utilised a python object serialisation library known as `Pickle'\footnote{\url{https://docs.python.org/2/library/pickle.html}}.
 This library saves the instance of a class as a file.
 This file then can be used to load the instance of the class back into the program.
-This allows changes to the object to filter down through the program and keeps the design of the application fluid.
-For example, after initial feedback gathered about the application it was decided that a inclusion of `Round times' would be a useful addition.
-Edits were made to the \verb|experiment| class and the changes propagated through the application, no changes were needed on the save functionality.
-To distinguish between old and new save formats a version number was used.
+This inclusion allows changes to the object to filter down through the program and keeps the design of the application fluid.
+For example, after initial feedback gathered about the application, it was decided that the inclusion of `Round times' would be a useful addition.
+Edits were made to the \verb|experiment| class and the changes propagated through the application; no changes were needed on the save functionality.
+To distinguish between old and new save formats, a version number was used.

### 2019-08-15 Writeup/Thesis/pages/conclusion.tex
Changes; - First draft send off to supervisor

--- 2019-08-13 Thesis/pages/conclusion.tex
@@
 Overall, the project has demonstrated a potential attack on \pep's implementation of Trustwords.
-An attack was proposed that utilized phonetic similarity algorithms to exploit the weaknesses in the Trustword dictionary to generate near-collision keys.
-To achieve this a tool was created to compute a massive number of keys in a concurrent fashion.
-It was based of a known tool but improves on its key searching performance substantially.
-The performance of similarity metrics were compared alongside an experiment assessing participants fallibility to the proposed attack.
+An attack was proposed that utilised phonetic similarity algorithms to exploit the weaknesses in the Trustword dictionary to generate near-collision keys.
+To achieve this, a tool was created to compute a massive number of keys concurrently.
+It was based on a known tool but improved substantially on its key searching performance.
+The performance of similarity metrics was compared alongside an experiment assessing participants fallibility to the proposed attack.
 Results showed as much as a 32.05\% success rate for the best attack.
@@
 We believe we have demonstrated that four Trustwords is too low to provide enough security for general use-case and the minimum provided words should, therefore, be increased.
+
+% \todo{Recommendation for metric - Metaphone because best balance of number of possibilities and success rate}

### 2019-08-15 Writeup/Thesis/pages/evaluation.tex
Changes; - First draft send off to supervisor

@@
 \chapter{Evaluation}
-This chapter will collate the findings of the paper, evaluate the paper's success against the research questions and discuss potential further work.
+This chapter collates the findings of the paper, evaluates the paper's success against the research questions and discuss potential further work.
 
@@
 Research Question \ref{goal:phoneticSimilarity} asks: \textit{``What are the different ways phonetic similarity can be quantified?''}.
-This paper has discussed a number of metrics used to quantify phonetic similarity (See Section \ref{sec:metrics}).
+This paper has discussed several metrics used to quantify phonetic similarity (See Section \ref{sec:metrics}).
 Most metrics were chosen due to their high utilization and occurrence in literature.
@@
 The paper has presented the performance of a suite of algorithms that are mostly present in alternative literature.
-Performance of these metrics were quantified in a direct study that selected the top three from a set of five.
+Performance of these metrics was quantified in a direct study that selected the top three from a set of five.
 These newly selected metrics were then assessed in an attack context with their performance being indirectly quantified.
-From the historical set of metrics Levenshtein was the best performer with participants rating its matches as substantially better.
+From the historical set of metrics, Levenshtein was the best performer with participants rating its matches as substantially better.
 Levenshtein was also the best performer in the attack context with it having the best average attack success rate.
-This, therefore, seems to corroborate work showing that words with similar spelling tend to share phonetic similarity \cite{hettiarachchi2012sparcl}.
-This area, however, will require further work to provide more conclusive results on the most effective ways to quantify phonetic similarity.
+This performance, therefore, seems to corroborate work showing that words with similar spelling tend to share phonetic similarity \cite{hettiarachchi2012sparcl}.
+This area, however, requires further work to provide more conclusive results.
 
 \section{Research Question \ref{goal:complexity}}
-Research Question \ref{goal:complexity}: \textit{``What are the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys was shown in Section \ref{sec:key_gen} where actual keys were generated.
-Further more the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}.
-To achieve this the tool GreenOnion was developed where inspiration was gathered from a currently available tool known as Scallion.
+Research Question \ref{goal:complexity}: \textit{``What are the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys as shown in Section \ref{sec:key_gen} where actual keys were generated.
+Furthermore, the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}.
+To achieve this, the tool GreenOnion was developed where inspiration was gathered from a currently available tool known as Scallion.
 Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for with GreenOnion being able to handle in excess of 1.5 million keys.
-This is in comparison to maximum of 40 keys Scallion can compare.
+This capability is in comparison to the maximum of 40 keys Scallion can compare.
 
@@
 Research Question \ref{goal:hardwareRequired} states: \textit{``What kind of hardware is required to compute a matching key?''}.
-Through the computation of actual keys presented in Section \ref{sec:key_gen} and the theoretical calculation into key computation in some cases it has been shown that a single mid-range GPU\footnote{AMD RX-480} can be used to compute actual keys.
+Through the computation of actual keys presented in Section \ref{sec:key_gen} and the theoretical calculation into key computation in some cases, it has been shown that a single mid-range GPU\footnote{AMD RX-480} can be used to compute actual keys.
 
@@
 Finally, the highest attack strength that theoretically involved the use of 100 mid-range GPUs computing for a week has success rates: 24.43\% - 32.05\%.
-Therefore, showing the number attacks would deceive a set assessed users.
+Therefore, showing the number of attacks would deceive a set of users.
 
@@
 A user, therefore, could initiate this attack on-mass with hardware present inside the average gaming computer.
-On the other hand, the best level of attack success was show to be 32.05\%.
+On the other hand, the best level of attack success was shown to be 32.05\%.
 
-Further more, comparison of these results to similar literature show a huge increase in success rates for the attack present in this paper.
+Furthermore, comparison of these results to similar literature shows a considerable increase in success rates for the attack present in this paper.
 All alternative literature used a small dictionary of around 1024 words.
-This, therefore, is highly suggestive that the issue lies with the design of Trustwords.
+Therefore, this is highly suggestive that the issue lies with the design of Trustwords.
 Therefore, we believe that 4 Trustwords as a minimum has not provided a basic level of security towards users.
@@
 Thus, further work could assess the performance of metrics against each other to determine the one that works best with human models of phonetics.
-This could be achieved by repeating the improved experiment discussed in Section \ref{exp:metric}.
-This could be repeated with a very large number of metrics.
+A conclusion could be reached by running the improved experiment discussed in Section \ref{exp:metric}, where it could be repeated with an increased of metrics.
 Other elements for consideration could be age, location and dialect as variables that affect the metrics performance.
@@
 \subsection*{GreenOnion optimizations}
-Very little work and time was invested into improving the performance of GreenOnion as low-level optimizations are a very time consuming process.
+A minimal amount of work and time was allocated to improving the performance of GreenOnion as low-level optimizations are very time-consuming.
 A project, therefore, could aim to improve on the performance already recorded in this paper.
-This could, therefore, improve on the performance of the attack and allow for more successful attacks to be computed in less time.
+This project could, therefore, improve the performance of the attack and allow for more effective keys to be computed in less time.

### 2019-08-15 Writeup/Thesis/pages/experiments.tex
Changes; - First draft send off to supervisor

@@
 \label{sec:averagePerms}
-In order to predict the effectiveness of the attack over a wide variety of keys the number of average near-matches requires computation.
+In order to predict the effectiveness of the attack over a wide variety of keys, the number of average near-matches requires computation.
 Table \ref{tab:average_perm} shows the average keys for each metric.
-The ``Compute Time'' is the computation time required for a single mid range (2000MH/s) GPU.
+The ``Compute Time'' is the computation time required for a single mid-range (2000MH/s) GPU.
 
@@
 
-As it can be seen metrics like Levenshtein have a low overall average and would require much more attacker resources to become feasible.
+As can be seen, metrics like Levenshtein have a low overall average and would require much more attacker resources to become feasible.
 On the other hand, Metaphone has attacks that could be computed on average in under 2 days.
 The success rate for this attack type in the second experiment was 11.01\% on average.
-This means on commodity hardware commonly found in the home, an attacker could compute a key in less than two days that could succeed more than 10\% of the time.
-This is substantial and highlights on weaknesses in the Trustword system.
+This means on commodity hardware commonly found in the home; an attacker could compute a key in less than two days that could succeed more than 10\% of the time.
+This aspect is substantial and highlights weaknesses in the Trustword system.
 
@@
 \label{sec:vulnKeys}
-As discussed in the design of the second experiment (See Section \ref{sec:exp2}) the attacks sampled from a list of `vulnerable keys'.
+As discussed in the design of the second experiment (See Section \ref{sec:exp2}), the attacks sampled from a list of `vulnerable keys'.
 These vulnerable keys were created using real keys extracted from PGP key servers.
-These keys were then randomly sampled and used to create the combined key as discussed in Section \ref{sec:pep}.
+These keys were then randomly sampled and used to create the combined key,as discussed in Section \ref{sec:pep}.
 100,000 random key pairs were created and used as the sample.
@@
 Table \ref{tab:vulnkeys} contains the breakdown of the number of vulnerable keys.
-The takeaways from this table is the extremely low values for Levenshtein in the higher attacks.
-This is due to the low number of overall matches produced by Levenshtein.
-This means Levenshtein will not be effective in the vast majority of cases.
-However, the standout metric is Metaphone with a good proportion of vulnerable keys, it was the worst performer when assessed against real users but only by as little as 2\%.
-If you take into consideration the number of vulnerable keys detected in the set alongside the average amount near-collision matches in Table \ref{tab:average_perm} Metaphone appears to be the most usable metric overall.
+The takeaways from this table are the extremely low values for Levenshtein in the higher attacks.
+This phenomenon is due to the low number of overall matches produced by Levenshtein, meaning Levenshtein is effective in the vast majority of cases.
+However, the standout metric is Metaphone with a sizeable proportion of vulnerable keys; it was the worst performer when assessed against real users but only by as little as 2\%.
+If you take into consideration, the number of vulnerable keys detected in the set alongside the average amount of near-collision matches in Table \ref{tab:average_perm} Metaphone appears to be the most usable metric overall.
 
@@
 \label{sec:key_gen}
-To demonstrate that the the generation of the near collision keys is not only theoretical actual generation of keys was performed using GreenOnion.
+In order to demonstrate that the generation of the near-collision keys is not only theoretical, the actual generation of keys was performed using GreenOnion.
 A random metric was selected from the three carried forward from the first experiment.
-Alongside this a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key).
-Then for each attack level (0 static, 1 static, 2 static) a key was computed.
+Alongside this, a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key).
+Then for each attack level (0 static, 1 static, 2 static), a key was computed.
 NYSIIS was chosen as the selected metric.
-To expedite the process an initial search was performed for controlled keys that had the highest number of near-collisions, this was due to the demonstrative purpose of this experiment.
-Producing near-matching keys from key pairs with a very small number of potential matches, adds very little to this demonstration.
+To expedite the process, an initial search was performed for controlled keys that had the highest number of near-collisions; this was due to the demonstrative purpose of this experiment.
+Producing near-matching keys from key pairs with a very small number of potential matches adds very little to this demonstration.
 
@@
 Tables \ref{tab:nysiis0}, \ref{tab:nysiis1} and \ref{tab:nysiis2} contain the parameters and results on the computation.
-Due to varying availability of resources each computation has a varying hashing speed.
-This, however, has been normalized by the introduction of the "GPU Day" metric.
-This is simply the computation time required to reach the same conclusion on a single 2000 MH/s GPU.
+Due to the varying availability of resources, each computation has a varying hashing speed.
+This variation has been normalized by the introduction of the "GPU Day" metric.
+A GPU day is simply the computation time required to reach the same conclusion on a single 2000 MH/s GPU.
 
-As it can be seen most notably from Table \ref{tab:nysiis2} the generation of the actual Trustwords differs in only 3 characters making it arguably very similar.
-When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU is able to achieve around a 28\% success rate when assessed against actual users.
-Even with the least restricted attack type presented in Table \ref{tab:nysiis0} the computation of half a day can provide almost a 10\% success rate when attacking users.
-This means any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of fooling an actual user.
+As can be seen most notably from Table \ref{tab:nysiis2}, the generation of the actual Trustwords differs in only 3 characters making it arguably very similar.
+When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU can achieve around a 28\% success rate when assessed against actual users.
+Even with the least restricted attack type presented in Table \ref{tab:nysiis0}, the computation of half a day can provide almost a 10\% success rate when attacking users.
+This results in any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of fooling an actual user.

### 2019-08-15 Writeup/Thesis/pages/introduction.tex
Changes; - First draft send off to supervisor

@@
 
+\newpage
 The report is structured as follows:
 
-\textbf{Chapter 2} provides any required background knowledge alongside a review of all relevant literature.
+\begin{itemize}
+    \item \textbf{Chapter 2} provides any required background knowledge alongside a review of all relevant literature.
 
-\textbf{Chapter 3} formally defines the aim of this report alongside the research questions the project aims to answer.
+    \item \textbf{Chapter 3} formally defines the aim of this report alongside the research questions the project aims to answer.
 
-\textbf{Chapter 4} documents the proposed designs required to answer the research questions proposed in Chapter 3.
+    \item \textbf{Chapter 4} documents the proposed designs required to answer the research questions proposed in Chapter 3.
 
-\textbf{Chapter 5} discusses the significant implementation details of the designs formalized in Chapter 4.
+    \item \textbf{Chapter 5} discusses the significant implementation details of the designs formalized in Chapter 4.
 
-\textbf{Chapter 6} presents and analyses all experimentation results of the project.
+    \item \textbf{Chapter 6} presents and analyses all experimentation results of the project.
 
-\textbf{Chapter 7} evaluates the success of the project alongside a discussion into proposed further work. The research aims proposed earlier in Chapter 3 are used as evaluative metrics.
+    \item \textbf{Chapter 7} evaluates the success of the project alongside a discussion into proposed further work. The research aims proposed earlier in Chapter 3 are used as evaluative metrics.
 
-\textbf{Chapter 8} concludes the project with a culmination of the findings of the paper alongside any relevant conclusions.
+    \item \textbf{Chapter 8} concludes the project with a culmination of the findings of the paper alongside any relevant conclusions.
+    \end{itemize}

### 2019-08-15 Writeup/Thesis/pages/research_question.tex
Changes; - More corrections made - Added a speed comparison graph
Changes; - First draft send off to supervisor

@@
 
+\begin{center}
 \begin{figure}[h!]
     \centering
-    \begin{verbatim}
+
+    \begin{lstlisting}[frame=single, numbers=none]
 "Short Trustword Mapping (S-TWM) requires a number of 
@@
 compared by the user."
-    \end{verbatim}
+    \end{lstlisting}
+
     \caption{Most recent RFC security recommendation}
@@
 \end{figure}
-
+\end{center}
 By sampling the \pep documentation they have defined the use case of the Trustword handshake: \textit{``A handshake is done by comparing the Trustwords between two users through a separate communication channel (e.g.
@@
 \begin{enumerate}
-
-    \item Is the recommended minimum number of four Trustwords enough to provide a basic level of security? \label{goal:numberOfTrustwords}
-
     \item What are the different ways phonetic similarity can be quantified?  \label{goal:phoneticSimilarity}
@@
     \item What percentage of attacks successfully deceive a user? \label{goal:attackPercentage}
+
+    \item Is the recommended minimum number of four Trustwords enough to provide a basic level of security? \label{goal:numberOfTrustwords}
 \end{enumerate}

### 2019-08-20 Writeup/Thesis/chapters/background.tex
Changes; - Added some changes from supervisor - Began fixing structure of the document

--- 2019-07-29 Thesis/pages/background.tex
@@
 \label{cha:Background}
-
-\section{Problem Context}
-% Goal of the project? Why am I concentrating on PEP's Trustwords?
-The project aims to asses the security of \pep's fingerprint representation "Trustwords".
-Trustwords aim to sacrifice security for increased usability.
-The encoding scheme has been designed to assist this by having  the user compare a reduced set of words by about half in comparison to other schemes.
-To achieve this a larger number of bits are required per word.
-In this case Trustwords maps 16bits per word providing 65537 different combinations.
-This is, however, the largest number of bits per words (As show in the Literature Review in Chapter \ref{cha:LiteratureReview}) and pushes the boundaries of a language's usable vocabulary.
-
-This abnormal design choice has not received a security assessment to back up claims. This paper, therefore, aims to rectify this research gap.
-
-However, in order to fully understand the project goal it is important to understand public-key cryptography, the role and functioning of \pep and the role fingerprint comparison has in preventing Man-in-the-middle attacks.
 
@@
 Each key pair is the exclusive-or of each key's fingerprint, this combined values is then broken down into 16-bit chunks and mapped to words via a pre-defined dictionary.
-
-\begin{figure}[h!]
-    \centering
-    $KeyFingerprint_{1} \oplus KeyFingerprint_{2} = TrustwordsFingerprint$
-    \caption{Creation of the combined Trustword fingerprint}
-\end{figure}
-
-\begin{wrapfigure}{r}{5cm}
-    \centering
-    \begin{BVerbatim}
-    [...]
-52127 ZYGOTE
-52128 ZYGOTIC
-52129 ZYMURGY
-52130 AACHEN
-52131 AARDVARK
-52132 AAREN
-    [...]
-    \end{BVerbatim}
-    \caption{Re-mapping position in Trustword dictionary}
-    \label{fig:remap}
-\end{wrapfigure}
-
-Due to the number of words required ($2^{16}$) alongside the design choice to exclude slang and profanities the english Trustword dictionary requires dual-mapping of a section of words.
-Approximately 13633/65536 (20.8\%) of words are re-mapped in the dictionary leaving 51903 unique words.
-The re-mapping is also done on a loop with it remaining alphabetical.
-Figure \ref{fig:remap} shows the position in the dictionary where this occurs.
-This predictability within the dictionary will be explored later in the paper.
-
-% Does this need explaining?
-\section{OpenCL}
-
-\section{Similarity metrics (Soundex etc)}

### 2019-08-20 Writeup/Thesis/chapters/design.tex
Changes; - Added some changes from supervisor - Began fixing structure of the document

--- 2019-08-15 Writeup/Thesis/pages/design.tex
@@
 
-As each combined key in Trustwords is an exclusive-or of both sides' public-key (Figure \ref{fig:xor_trustwords} shows this process) the attack is designed to target a single pair of users and requires recomputation for every attack target.
+As each combined key in Trustwords is an exclusive-or of both sides' public-key (Equation \ref{fig:xor_trustwords} shows this process) the attack is designed to target a single pair of users and requires recomputation for every attack target.
 This aspect is considered when discussing the attack feasibility.
@@
 
-\begin{figure}[h!]
-    \centering
-    $KeyFingerprint_{1} \oplus KeyFingerprint_{2} = TrustwordsFingerprint$
-    \caption{Creation of the combined Trustword fingerprint}
+\begin{equation}
+    KeyFingerprint_{1} \oplus KeyFingerprint_{2} = TrustwordsFingerprint
+\end{equation}
 \label{fig:xor_trustwords}
-\end{figure}
 
@@
     \centering
-    \begin{tabular}{ll}
-        Metric & Matches \\
-        \hline
-        Soundex     & 1,527,554 \\
-        Metaphone   & 412,916 \\
-        NYSIIS      & 188,474 \\
-        \hline
-        Levenshtein (Distance 1) [L1] & \textbf{97,730} \\
-        Levenshtein (Distance 2) [L2] & 1,070,656
-    \end{tabular}
+    \input{tables/design/match_size_leven.tex}
     \caption{Levenshtein number of matches comparison}
@@
     \centering
-    \begin{tabular}{ll}
-        Metric & Matches \\
-        \hline
-        Soundex     & 1,527,554 \\
-        Metaphone   & 412,916 \\
-        NYSIIS      & 188,474 \\
-        Levenshtein & 97,730 \\
-        \hline
-        Phonetic Vector (Distance 3.0)  & 14,550 \\
-        Phonetic Vector (Distance 4.0)  & 73,962 \\
-        Phonetic Vector (Distance 4.5)  & \textbf{216,156} \\
-        Phonetic Vector (Distance 5.0)  & 685,516 \\
-    \end{tabular}
+    \input{tables/design/match_size_wordvec.tex}
     \caption{Phonetic vector number of matches comparison}
@@
     \fbox{
-        \includegraphics[scale=0.5]{experiment_match.png}
+        \includegraphics[width=\textwidth]{experiment/experiment_match.png}
     }
@@
     \fbox{
-        \includegraphics[scale=0.5]{exact_experiment_match.png}
+        \includegraphics[width=\textwidth]{experiment/exact_experiment_match.png}
     }
@@
 Another consideration is the demographics of people accessible on Mechanical Turk.
-A comprehensive and still active survey run by D Difallah \textit{et al.} \cite{difallah2018demographics} shows that MTurk workers are younger and have a more substantial household income than that of the US population.
+A comprehensive and still active survey run by \textbf{D.
+Difallah, E.
+Filatova} and \textbf{P.
+Ipeirotis}\cite{difallah2018demographics} shows that MTurk workers are younger and have a more substantial household income than that of the US population.
 This deviation has to be taken into consideration when interpreting the results because it has to potential to introduce a bias.
@@
         \parbox{\textwidth}{
-            \includegraphics[width=\textwidth]{checksum_check.png}
+            \includegraphics[width=\textwidth]{experiment/checksum_check.png}
 
-            \includegraphics[width=\textwidth]{checksum_check_2.png}
+            \includegraphics[width=\textwidth]{experiment/checksum_check_2.png}
         }
@@
     \centering
-    \begin{tabular}{lll}
-        GPU/days & No of combinations required & Attack Type \\
-        \hline
-        1       & 15250   & Zero static\\
-        10      & 1525    & One static\\
-        100     & 152     & Two static\\        
-    \end{tabular}
+    \input{tables/design/attack_types.tex}
     \caption{Summary of attack requirements}

### 2019-08-20 Writeup/Thesis/chapters/evaluation.tex
Changes; - Added some changes from supervisor - Began fixing structure of the document

--- 2019-08-15 Writeup/Thesis/pages/evaluation.tex
@@
-\chapter{Evaluation}
+\chapter{Conclusions}
 This chapter collates the findings of the paper, evaluates the paper's success against the research questions and discuss potential further work.
@@
 This project could, therefore, improve the performance of the attack and allow for more effective keys to be computed in less time.
+
+\section{Final Remarks}
+Overall, the project has demonstrated a potential attack on \pep's implementation of Trustwords.
+An attack was proposed that utilised phonetic similarity algorithms to exploit the weaknesses in the Trustword dictionary to generate near-collision keys.
+To achieve this, a tool was created to compute a massive number of keys concurrently.
+It was based on a known tool but improved substantially on its key searching performance.
+The performance of similarity metrics was compared alongside an experiment assessing participants fallibility to the proposed attack.
+Results showed as much as a 32.05\% success rate for the best attack.
+The main project aim was to show that the recommend minimum number of four Trustwords was insufficient to provide a basic level of security.
+We believe we have demonstrated that four Trustwords is too low to provide enough security for general use-case and the minimum provided words should, therefore, be increased.

### 2019-08-20 Writeup/Thesis/chapters/experiments.tex
Changes; - Added some changes from supervisor - Began fixing structure of the document

--- 2019-08-15 Writeup/Thesis/pages/experiments.tex
@@
     \centering
-    \input{diagrams/graphs/speed.tex}
+    \input{graphs/speed.tex}
     \label{tab:scallion_speed}
@@
 
-\input{diagrams/graphs/experiment_one/graph.tex}
+\input{graphs/experiment_one/graph.tex}
 
@@
         \hline
-        Gender & Male: & 50.41\% \\
-               & Female: & 49.59\% \\
+        Gender & Male: & 50.4\% \\
+               & Female: & 49.6\% \\
         \hline
-        Age:   & 18-24: & 12.74\% \\ 
-               & 25-29: & 18.16\% \\ 
+        Age:   & 18-24: & 12.7\% \\ 
+               & 25-29: & 18.2\% \\ 
                & 30-39: & 37.4\% \\ 
-               & 40-49: & 17.89\% \\ 
-               & 50-59: & 8.67\% \\ 
-               & 60-69: & 4.34\% \\ 
-               & 70-79: & 0.81\% \\
+               & 40-49: & 17.9\% \\ 
+               & 50-59: & ~~8.7\% \\ 
+               & 60-69: & ~~4.3\% \\ 
+               & 70-79: & ~~0.8\% \\
 
@@
         Highest Education:  
-        & GCSE:                 & 13.82\%  \\
-        & A-Level/O-Level:      & 24.12\% \\
-        & Bachelor's degree:    & 51.49\% \\
-        & Master's degree:      & 8.4\% \\ 
-        & PhD:                  & 2.17\% \\
+        & GCSE:                 & 13.8\%  \\
+        & A-Level/O-Level:      & 24.1\% \\
+        & Bachelor's degree:    & 51.5\% \\
+        & Master's degree:      & ~~8.4\% \\ 
+        & PhD:                  & ~~2.2\% \\
         \hline
@@
         \hline
-        Chrome & 85.09\% \\
-        Firefox & 12.20\% \\
-        Safari & 1.90\% \\
-        Other & 0.81\% \\
+        Chrome & 85.1\% \\
+        Firefox & 12.2\% \\
+        Safari & ~~1.9\% \\
+        Other & ~~0.8\% \\
         \hline
@@
         \hline
-        Windows (All) & 74.26\% \\
-        ~~~~\textit{Windows 7} & ~~~12.74\% \\
-        ~~~~\textit{Windows 8} & ~~~4.07\% \\
-        ~~~~\textit{Windows 10} & ~~~57.45\% \\
-        MacOS X	 & 13.82\% \\
-        ChromeOS & 3.79\% \\
-        Android	& 4.34\% \\
-        iPhone	& 1.08\% \\
-        iPad	& 0.54\% \\
-        Linux	& 2.17\% \\
+        Windows (All) & 74.3\% \\
+        ~~~~\textit{Windows 7} & ~~~12.7\% \\
+        ~~~~\textit{Windows 8} & ~~~~~4.1\% \\
+        ~~~~\textit{Windows 10} & ~~~57.5\% \\
+        MacOS X	 & 13.8\% \\
+        ChromeOS & ~~3.8\% \\
+        Android	& ~~4.3\% \\
+        iPhone	& ~~1.1\% \\
+        iPad	& ~~0.5\% \\
+        Linux	& ~~2.2\% \\
         \hline
@@
             \hline
-            Levenshtein && 218 & 1101 & 19.80\% \\
+            Levenshtein && 218 & 1101 & 19.8\% \\
             \hline
-            & 0 static   & 34  & 358  & ~9.50\% \\
-            & 1 static   & 59  & 353  & 16.71\% \\
-            & 2 static   & 125  & 390  & 32.05\% \\
+            & 0 static   & 34  & 358  & ~~9.5\% \\
+            & 1 static   & 59  & 353  & 16.7\% \\
+            & 2 static   & 125  & 390  & 32.1\% \\
             \hline\hline
-            Metaphone &&  181 & 1072 & 16.88\% \\
+            Metaphone &&  181 & 1072 & 16.9\% \\
             \hline
-            & 0 static   & 38 & 345 & 11.01\% \\
-            & 1 static   & 57 & 375 & 15.20\% \\
-            & 2 static   & 86 & 352 & 24.43\% \\
+            & 0 static   & 38 & 345 & 11.0\% \\
+            & 1 static   & 57 & 375 & 15.2\% \\
+            & 2 static   & 86 & 352 & 24.4\% \\
             \hline\hline
-            NYSIIS &&  209 & 1114 & 18.76\% \\
+            NYSIIS &&  209 & 1114 & 18.8\% \\
             \hline
-            & 0 static   & 36 & 385 & ~9.35\% \\
-            & 1 static   & 72 & 375 & 19.20\% \\
-            & 2 static   & 101 & 354 & 28.53\% \\
+            & 0 static   & 36 & 385 & ~~9.3\% \\
+            & 1 static   & 72 & 375 & 19.2\% \\
+            & 2 static   & 101 & 354 & 28.5\% \\
             \hline\hline
-            \textbf{Overall} & & 608 & 3287 & 18.50\% \\
+            \textbf{Overall} & & 608 & 3287 & 18.5\% \\
             \hline\hline
@@
 This aspect, alongside the potential for users to downplay the possibility of attack, leads to the conclusion that the success rates could be much higher in a real-world setting.
-The assumption is that these results display the success rate for extremely attentive users where they make sure to double-check with their authentication partner multiple times.
+The assumption is that these results display the success rate for attentive users where they make sure to double-check with their authentication partner multiple times.
 It is, therefore, assumed that the majority of users aim to complete the task as quickly as possible, if at all.
@@
 
-Work by Kainda \textit{et al.}\cite{kainda2009usability} (previously discussed in Chapter \ref{cha:LiteratureReview}) is the most comparable to this experiment.
+Work by \textbf{R.
+Kainda, I.
+Flechais} and \textbf{A.
+Roscoe, \textit{et al.}}\cite{kainda2009usability} (previously discussed in Chapter \ref{cha:LiteratureReview}) is the most comparable to this experiment.
 They were the only study to use exactly 4 words but differed on the size of the dictionary (1024 words) and how a near-match were calculated.
@@
 
-Other relevant work by Dechand \textit{el al.}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words.
+Other relevant work by \textbf{Dechand \textit{el al.}}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words.
 Their experiment is less similar as 14 words per attack were assessed with each participant, where the comparison was performed visually.
@@
 
-The final relevant paper to compare is that of Tan \textit{et al.}\cite{tan2017can}.
+The final relevant paper to compare is that of \textbf{J.
+Tan \textit{et al.}}\cite{tan2017can}.
 This paper had the highest number of words assessed with 16 overall.
-With it assessing the same wordlist and attack strength as the work by Dechand \textit{et al.}, the attack success was 14\% overall.
+With it assessing the same wordlist and attack strength as the work by \textbf{S.
+Dechand \textit{et al.}}\cite{dechand2016empirical}, the attack success was 14\% overall.
 This success rate compared to the highest attack assessed in the experiment results in another sizeable difference.
@@
 This aspect is also a unique consideration compared to the available literature.
+
+\todo{Include comparison to Hash-Friendly Schemes paper as they used Transposition to create 'Hard Matches' i.e. blub --> bulb}
 

### 2019-08-20 Writeup/Thesis/chapters/introduction.tex
Changes; - Added some changes from supervisor - Began fixing structure of the document

--- 2019-08-15 Writeup/Thesis/pages/introduction.tex
@@
 \chapter{Introduction}
+\pagenumbering{arabic}
 \label{cha:Introduction}
 
-The increasing use of public-key cryptography by instant messaging and secure email means key-fingerprint  verification is an ever more important task.
+The increasing use of public-key cryptography by instant messaging and secure email means ensuring confidentiality is an ever more important task.
 
@@
 
-This report evaluates the security and feasibility of attacking a fingerprint encoding known as “Trustwords.” The motivation for this is due in part to the shortage of justification behind some fundamental design choices.
+One proposed user-friendly scheme is Pretty Easy Privacy's (p$\equiv$p) "Trustwords".
+Trustwords is an implementation of word fingerprint mapping with a emphasis on usability.
+This increase in usability is achieved by the user comparing a reduced number of words.
+This usability boost, however, comes at a cost of a much larger word list.
+
+This report evaluates the security and feasibility of attacking Trustwords. The motivation for this is due in part to the shortage of justification behind the size and features of the chosen wordlist.
 
@@
 
-    \item \textbf{Chapter 7} evaluates the success of the project alongside a discussion into proposed further work. The research aims proposed earlier in Chapter 3 are used as evaluative metrics.
-
-    \item \textbf{Chapter 8} concludes the project with a culmination of the findings of the paper alongside any relevant conclusions.
+    \item \textbf{Chapter 7} evaluates and concludes the success of the project alongside a discussion into proposed further work.
+The research aims proposed earlier in Chapter 3 are used as evaluative metrics.
 \end{itemize}

### 2019-08-20 Writeup/Thesis/chapters/lit_review.tex
Changes; - Added some changes from supervisor - Began fixing structure of the document

--- 2019-08-14 Writeup/Thesis/pages/lit_review.tex
@@
 Figure \ref{fig:mitm} contains a visual representation of this attack.
+In the diagram Eve (attacker) is impersonating Alice to Bob and Bob to Alice.
+Therefore, as both directions of communication are compromised all traffic will route through the attacker Eve.
 
 \begin{center}
-    \input{diagrams/MITM/basic}
+    \input{diagrams/mitm.tex}
     \begin{figure}[h]
@@
 
-Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob), the fingerprint of the public keys are, therefore, different, and, thus can be used for identification.
-There are, however, issues in how a user should link a key's fingerprint to a real-world entity.
-This paper will, however, assume that users have access to the respective parties' correct fingerprint, as the protocols used to achieve this are outside the project's scope.
+Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob), the unique aspects of the keys can be used to identify parties.
+This is achieved succinctly through the use of a fingerprint.
+A fingerprint is a string of alphanumerical characters that are unique to each key.
+Therefore the fingerprint of the two respective public keys are different, and, thus can be used for identification.
+There are, however, issues in how a user should link a key's fingerprint to an identity.
+One example way to achieve this is by meeting in-person to exchange fingerprints.
+This paper will, however, assume that users have been through this process.
 
-The fingerprint of the key is generated by running the main key components through a secure one-way hash function such as SHA-1.
+The fingerprint of the key is generated by running the main key components through a secure one-way hash function such as SHA-256.
 This process produces a digest of a fixed length that can be used to compare keys.
 Therefore, the comparison of expected and actual fingerprints can be used to detect MiTM attacks.
-Historically these have been represented as a hexadecimal string whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card.
-This process is known as the \textit{``authentication ceremony.''} System designers are, however, moving away from this structure and are now implementing a combined key.
+
+Historically fingerprints have been represented as a hexadecimal string, whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card.
+Figure \ref{fig:businessCard} shows an example business card.
+A user will then use the fingerprint present on the card to compare to the one available on a device.
+This will have to be performed by each user.
+This process is known as the \textit{``authentication ceremony.''}
+
+\begin{figure}[h!]
+    \centering
+    \fbox{
+        \input{diagrams/business_card.tex}
+    }
+    \caption{Example business card with fingerprint}
+    \label{fig:businessCard}
+\end{figure}
+
+System designers are, however, moving away from the structure of one fingerprint per identity and are now implementing a combined key.
 This change is due to the assumed increase in usability.
-Users now compare a single fingerprint, instead of two sets separately.
-In the case of WhatsApp for example, the connection fingerprint of two parties keys is the first 30 bytes of an SHA-512\footnote{5200 iterations} hash of each parties' identity key, these are then both concatenated together to form a single key\cite{whatsapp2017paper}.
-This process produces a unique-key communication pair.
-\\\\
+Users now compare a single fingerprint together, instead of two sets separately.
+In the case of WhatsApp for example, the connection fingerprint of two parties keys is the first 30 bytes of an SHA-512\footnote{5200 iterations} hash of each parties' identity key, these are then both concatenated together to form a single fingerprint\cite{whatsapp2017paper}.
+This process produces a unique key per communication pair.
+
 Due to the manual comparison of the fingerprint, length, and format is a core design consideration.
 Prior research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}.
-This rules out the possibility of comparing complete digests.
+This shows that comparing complete digests would be cumbersome and error-prone.
 For example, SHA-1 is 40 hex digits (160-bit) and, therefore, difficult to effectively compare.
-Therefore, if human interaction is required; there is a need for schemes that work effectively with consideration to individual limitations.
+Therefore, if human interaction is required; there is a need for schemes that work effectively with consideration to human limitations.
 
-Research in this area has taken various encoding schemes and compared their fallibility to impersonated attacks.
+\section{Encoding schemes}
+\label{sec:encodingSchemes}
+Encoding schemes are the physical method of encoding used to represent the fingerprint.
+The most common way to represent the fingerprint is alphanumerically with either \textbf{Hexadecimal} (a-f/0-9) or \textbf{Base32} (2-7/A-Z).
+These encoding schemes are the most popular due to their intuitive simplicity and lack of unique hardware requirements such as colour screens.
+
+Fingerprints can also be encoded using natural language.
+The fingerprint can be chunked and mapped to a set or words.
+The same principle can be used to fill placeholders in a pre-defined sentence allowing the simple formation of syntactically accurate English sentences.
+Moreover, other languages can be used such as Chinese, Japanese or Korean to map fingerprint chunks to characters.
+
+\begin{table}[h!]
+    \centering
+    \input{tables/background/encoding_examples.tex}
+    \caption{Examples for text based encodings}
+\end{table}
+
+Graphical schemes can also be used to represent a fingerprint.
+
+\textbf{Random Art}.
+Random Art engine\cite{perrig1999hash} takes any length of input and processes it via SHA-1 to produce a digest that is then converted into an image.
+Figure \ref{fig:randomArt} contains three examples from the Random Art Gallery\footnote{\url{http://www.random-art.org/}}.
+
+\begin{figure}[h!]
+    \centering
+    \minipage{0.32\textwidth}
+        \includegraphics[width=.9\textwidth]{random_art/random_art1.jpg}
+    \endminipage
+    \minipage{0.32\textwidth}
+        \includegraphics[width=.9\textwidth]{random_art/random_art2.jpg}
+    \endminipage
+    \minipage{0.32\textwidth}
+        \includegraphics[width=.9\textwidth]{random_art/random_art3.jpg}
+    \endminipage
+    \caption{Random Art examples}
+    \label{fig:randomArt}
+\end{figure}
+
+\textbf{Flag}.
+Flag is a visual hash scheme proposed by \textbf{C.
+Ellison} and \textbf{S.
+Dohrmann}\cite{ellison2003public}.
+Flag consists of four coloured strips with $2^n$ number of possible colours in each strip.
+
+\textbf{T-Flag}.
+T-Flag is an attempt to improve on the previously mentioned Flag \cite{lin2010spate}.
+Improvements include twice the number of coloured blocks with a choice of eight colourblind-proof colours.
+
+\textbf{Flag-Ext}.
+Flag Extended is the proposed scheme assessed in the paper by \textbf{H.
+Hsiao \textit{et al.}}\cite{hsiao2009study}.
+Flag extended aims again, to improve on flag by reducing the number of blocks while adding 8 possible shapes.
+
+Figure \ref{fig:flag} contains an example of each version of Flag discussed.
+
+\begin{figure}[h!]
+    \centering
+    \minipage{0.32\textwidth}
+        \includegraphics[width=.9\textwidth]{flag/Flag.png}
+        \caption{Flag}
+    \endminipage
+    \minipage{0.32\textwidth}
+        \includegraphics[width=.9\textwidth]{flag/T-Flag.png}
+        \caption{T-Flag}
+    \endminipage
+    \minipage{0.32\textwidth}
+        \includegraphics[width=.9\textwidth]{flag/Flag-ext.png}
+        \caption{Flag Ext}
+    \endminipage
+    \caption{Variations of Flag}
+    \label{fig:flag}
+\end{figure}
+
+\newpage
+
+\textbf{OpenSSH}.
+OpenSSH visual host key is an ASCII based graphical scheme used in MiTM detection when connecting to SSH servers.
+The image is generated by movement of the marker across a grid where every 2-bits of the generated MD5 has defines the diagonal direction of movement.
+For example, if the first 2-bits are \verb|11| the marker will move South East.
+The different characters are determined by the number of times the marker is present in that index, for example, if the maker is present on a square 4 times the character will be an equals sign (\verb|=|).
+
+\textbf{Unicorns}\footnote{https://unicornify.pictures/}.
+Unicorns can be considered an example of an ``Avatar'' graphical scheme.
+The provided hash changes aspects of the image such as background colour, horn length and colour of the Unicorn's mane.
+
+\textbf{Vash}\footnote{https://github.com/thevash/vash}.
+Vash is similar to that of unicorns where the hash determines certain characteristics of the image.
+Vash claims to have $\approx 5,438$ bits of entropy.
+
+\begin{figure}[h!]
+    \centering
+    \minipage{0.32\textwidth}
+        \includegraphics[width=.9\textwidth]{graphical/openssh.png}
+        \caption{OpenSSH Visual Host Key}
+    \endminipage
+    \minipage{0.32\textwidth}
+        \includegraphics[width=.9\textwidth]{graphical/unicorn.png}
+        \caption{Unicorn}
+    \endminipage
+    \minipage{0.32\textwidth}
+        \includegraphics[width=.9\textwidth]{graphical/vash.png}
+        \caption{Vash}
+    \endminipage
+    \caption{Examples of alternative graphical encoding schemes}
+\end{figure}
+
+Research in this area has taken these various encoding schemes and compared their fallibility to impersonated attacks.
 The main elements of comparison have been the ``accuracy of attack detection" and ``time to compare." In this paper, these are considered the metrics of ``security'' and ``usability,'' respectively.
@@
 \\\\
-\textbf{\textit{Encoding schemes}} - are the physical method of encoding used to represent the fingerprint.
-For example, ``Hexadecimal'' or ``Words'' are a unique way to represent a fingerprint and thus, are encoding schemes.
-\\\\
 \textbf{\textit{Method of comparison}} - is the way a user assesses the encoding scheme.
@@
 The following sections explain alternative methods of comparisons.
+
+\todo{Phase this section out - make sure to remove from the introduction layout of the section}
 
@@
 In all cases, these were the best schemes from the sets assessed.
-The exception to this is the work performed by \textbf{Hsiao \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63\%.
+The exception to this is the work performed by \textbf{H.
+Hsiao \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63\%.
 \\\\
 Aside from textual representations were graphical schemes.
-Examples of schemes assessed were: Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Vash\footnote{https://github.com/thevash/vash}, OpenSSH visual host key and Unicorns\footnote{https://unicornify.pictures/}, among others.
+As explained in Section \ref{sec:encodingSchemes} the main graphical schemes assessed by the literature were: Random Art, Flag, T-Flag, Vash, OpenSSH Visual Host Key and Unicorns.
 These schemes had mixed accuracy with ranges as large as 50\% - 94\% in work by \textbf{Hsiao \textit{et al.}}\cite{hsiao2009study}.
@@
     \makebox[\textwidth][c]{
-        \input{tables/fingerprint_times.tex}
+        \input{tables/background/fingerprint_times.tex}
     }%
-    \caption{Timing results in seconds for the related schemes}
+    \caption{Average comparison time (seconds) for the encoding schemes}
     \label{tab:times}
@@
 The comparison speed of these schemes were all among the quickest (See Table \ref{tab:times} for an overview of timings).
-Other work also indirectly agreed with graphical encodings having significantly quicker comparison times compared to non-graphical schemes \cite{dechand2016empirical}\cite{kainda2009usability}.
+Other work also indirectly agreed with graphical encodings having significantly quicker comparison times compared to non-graphical schemes \cite{dechand2016empirical, kainda2009usability}.
 In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with literature only containing two papers.
@@
 One unique paper in this research area was the work by \textbf{M.
-Shirvanian \textit{et al.}}\cite{shirvanian2017pitfalls} produced in the context of secure messaging pairing.
+Shirvanian, N.
+Saxena and J.
+J.
+George}\cite{shirvanian2017pitfalls} produced in the context of secure messaging pairing.
 This paper was unique for several reasons.
@@
 
-Alongside this, it was shown in work by \textbf{Hsiao\textit{et al.}}\cite{hsiao2009study} that age and gender do not affect the accuracy of the scheme.
+Alongside this, it was shown in work by \textbf{H.
+Hsiao \textit{et al.}}\cite{hsiao2009study} that age and gender do not affect the accuracy of the scheme.
 However, younger participants were considerably faster.
@@
     \makebox[\textwidth][c]{
-        \input{tables/fingerprint_comparison.tex}
+        \input{tables/background/fingerprint_comparison.tex}
     }%
-    \caption{Accuracy of correct comparison for the encoding schemes assessed}
+    \caption{Overall accuracy of correct comparison for the encoding schemes assessed}
     \label{tab:results}
@@
 Each paper used a different metric for measuring accuracy.
-Therefore, all results have been translated into ``overall accuracy.''
+Therefore, all results have been translated into ``overall accuracy.''.
+For example, if a paper presented "security failures" or "attack success rate" of 5\% the overall accuracy of the scheme is 95\%.
 
@@
 This lack of entropy makes it challenging to compare results directly.
-One of the papers this most effects is the early work by \textbf{Hsiao \textit{et al.}}\cite{hsiao2009study}  where their highest entropy is 28-bits.
+One of the papers this most effects is the early work by \textbf{H.
+Hsiao \textit{et al.}}\cite{hsiao2009study}  where their highest entropy is 28-bits.
 This level of entropy was inadequate even at the time of publication.
@@
 
-One consideration of note is that made by Dechand \textit{et al.} \cite{dechand2016empirical} where they briefly consider medical conditions such as ADHD and reading or visual disorders and the way they affect the comparison's effectiveness.
+One consideration of note is that made by \textbf{S.
+Dechand \textit{et al.}}\cite{dechand2016empirical} where they briefly consider medical conditions such as ADHD and reading or visual disorders and the way they affect the comparison's effectiveness.
 The results highlight a slight reduction in overall accuracy, however, due to their small sample size, the results cannot be considered conclusive.
@@
 
-One glaring issue with the demographical health of \textbf{Ersin Uzun \textit{et al.}}\cite{uzun2007usability} study is the use of two entirely different groups of participants.
+One glaring issue with the demographical health of the study by \textbf{E.
+Uzun, K.
+Karvonen} and \textbf{N.
+Asokan}\cite{uzun2007usability} is the use of two entirely different groups of participants.
 Not only were their demographics different, but they were from different countries (America and Finland).
@@
 
-Hexadecimal and numerical schemes were not included as encoding schemes in work by \textbf{Hsiao \textit{et al.}}\cite{hsiao2009study} (some of the most widespread encoding schemes).
+Hexadecimal and numerical schemes were not included as encoding schemes in work by \textbf{H.
+Hsiao \textit{et al.}}\cite{hsiao2009study} (some of the most widespread encoding schemes).
 The justification was the schemes similarities to Base32  alongside "well-known deficiencies".
@@
     \makebox[\textwidth][c]{
-        \input{tables/fingerprint_attacker_stren.tex}
+        \input{tables/background/fingerprint_attacker_stren.tex}
     }%
@@
 
-\subsubsection*{Topic conclusion}
+\subsubsection*{Conclusion}
 Overall, this review has identified several key areas suitable for further work.
@@
 
-Some of the oldest preliminary work into visual encoding schemes is by \textbf{Adrian Perrig \textit{et al.}}\cite{perrig1999hash} in the creation of their scheme ``Random Art" in 1999.
+Some of the oldest preliminary work into visual encoding schemes is by \textbf{A.
+Perrig} and \textbf{D.
+Song}\cite{perrig1999hash} in the creation of their scheme ``Random Art" in 1999.
 The motivation for creating such a scheme was the perceived flaws in the ways humans verify and compare written information.
@@
 
-Further research into the creation of unique visual hash schemes has been performed by \textbf{C Ellison \textit{et al.}} \cite{ellison2003public} (Flag), \textbf{Yue-Hsun Lin \textit{et al.}}\cite{lin2010spate} (T-Flag) and work by \textbf{M.
+Further research into the creation of unique visual hash schemes has been performed by \textbf{C.
+Ellison} and \textbf{S.
+Dohrmann}\cite{ellison2003public} (Flag), \textbf{Yue-Hsun Lin \textit{et al.}}\cite{lin2010spate} (T-Flag) and work by \textbf{M.
 Olembo \textit{et al.}}\cite{olembo2013developing}.
@@
 A limitation is the lack of empirical data gathered on the performance.
-However, this was later evaluated in work by Dechand \textit{et al.} \cite{dechand2016empirical} and shown to be an effective encoding scheme.
+However, this was later evaluated in work by \textbf{S.
+Dechand \textit{et al.}}\cite{dechand2016empirical} and shown to be an effective encoding scheme.
 
@@
 MadLibs is where static placeholders are replaced with a list potential words.\\
-This work is an extension to work performed by Juola and Zimmermann\cite{juola1996whole} as they aimed to emulate the techniques used in PGPfone.
+This work is an extension to work performed by \textbf{Juola} and \textbf{Zimmermann}\cite{juola1996whole} as they aimed to emulate the techniques used in PGPfone.
 The paper's findings are limited by the lack of empirical data backing up claims made by the author the performance of the system, and security is only theoretically assessed.
 
-Aside from this research, there have been further informal implementations of fingerprint encodings.
+Tanet alAside from this research, there have been further informal implementations of fingerprint encodings.
 The first being by \textbf{Michael Rogers}\footnote{https://github.com/akwizgran/basic-english}.
 Rogers' implementation is a program designed to map fingerprints to pseudo-random poems.
-This implementation was again, empirically evaluated by Dechand \textit{et al.}\cite{dechand2016empirical}.
+This implementation was again, empirically evaluated by \textbf{S.
+Dechand \textit{et al.}}\cite{dechand2016empirical}.
 Ealier work by \textbf{N.
@@
 
+\newpage
 \subsubsection*{Pretty Easy Privacy}
@@
 
-\subsubsection*{Topic conclusion}
+\subsubsection*{Conclusion}
 
 In conclusion to this topic, the current research has primarily focused on the research and creation of visual representations.
-Research for textual fingerprints is fragmented and incomplete with work Juola and Zimmermann
-\cite{juola1996whole} and M.
-Goodrich \textit{et al.}\cite{goodrich2006loud} providing meaningful research to build upon in terms of word and sentence based encodings.
+Research for textual fingerprints is fragmented and incomplete with work \textbf{Juola} and \textbf{Zimmermann}
+\cite{juola1996whole} and \textbf{M.
+Goodrich \textit{et al.}}\cite{goodrich2006loud} providing meaningful research to build upon in terms of word and sentence based encodings.
 The fragmentation of this research leaves room for further work into this topic area.
@@
 
-The only other relevant research on this topic is the work by \textbf{M Shirvanian \textit{et al.}}\cite{shirvanian2014wiretapping} 
+The only other relevant research on this topic is the work by \textbf{M Shirvanian and N. Saxena}\cite{shirvanian2014wiretapping} 
 and their paper: \textit{``Wiretapping via Mimicry: Short 
@@
 these methods, they aimed to attack encodings of Numbers, 
-PGP word list (previously discussed work by Juola and 
-Zimmermann \cite{juola1996whole}) and MadLib (M. Goodrich 
-\textit{et al.}\cite{goodrich2006loud} work also 
+PGP word list (previously discussed work by \textbf{Juola} and 
+\textbf{Zimmermann} \cite{juola1996whole}) and MadLib (\textbf{M. Goodrich 
+\textit{et al.}}\cite{goodrich2006loud} work also 
 previously discussed). The effectiveness of these attacks 
@@
 In summary of the literature gaps areas discovered; encoding scheme performance requires further work in the performance of all graphical schemes to back up the results made by other work.
-Furthermore, there is a gap with the assessment of encoding schemes in the context of "remote-vs-proximity" first proposed by M.
-Shirvanian et al.
-as it would arguably provide a better simulation of real-world scenarios.
+Furthermore, there is a gap with the assessment of encoding schemes in the context of "remote-vs-proximity" first proposed by \textbf{M.
+Shirvanian, N.
+Saxena} and \textbf{J.
+J.
+George}\cite{shirvanian2017pitfalls} as it would arguably provide a better simulation of real-world scenarios.
 
 In the context of human demographics and the way they alter the performance of the schemes; further research is required into how the fluency of languages affects authentication ceremony.
-This further work would be a continuation of the initial work by Hsiao et al.
-and could allow the creation of schemes that are better suited to specific languages.
+This further work would be a continuation of the initial work by \textbf{H.
+Hsiao \textit{et al.}}\cite{hsiao2009study} and could allow the creation of schemes that are better suited to specific languages.
 Alongside this, there is a research gap in the investigation of how mental impairments affect the performance.

### 2019-08-20 Writeup/Thesis/chapters/research_question.tex
Changes; - Added some changes from supervisor - Began fixing structure of the document

--- 2019-08-15 Writeup/Thesis/pages/research_question.tex
@@
 in person or by phone)''.}\footnote{https://www.pep.security/docs/general\_information.html\#handshake}.
-It can be assumed due to the increased globalizatiohat is the time andn of the planet that the most common handshake occurrence is over the phone, and, therefore, not in person.
+It can be assumed due to the increased globalization of the planet that the most common handshake occurrence is over the phone, and, therefore, not in person.
 This is the assumed context of the handshake.

### 2019-08-20 Writeup/Thesis/code/ExponentIncrement.tex
Changes; - Added some changes from supervisor - Began fixing structure of the document

\begin{adjustbox}{width=\textwidth,height=15cm,keepaspectratio}
\begin{OpenCLCode}
///The exponent is split across two words
// i.e
//
// W[3] = XX EE EE EE
// W[4] = EE XX XX XX
//
int newExponent = get_global_id(0) + \
                    ORIGINAL_EXPONENT_VALUE;

// Moves the value to the right i.e. 0x01ffff -> 0x0001ff
// Diving by "0x100" moves the hex value 3 digits
// to the right
int exponentMaskLeft = ((int)(ORIGINAL_EXPONENT_VALUE / 0x100)) ^ ((int)(newExponent / 0x100));

W[3] = W[3] ^ exponentMaskLeft;

// Grabs the last byte of each exponent to apply to 
// the next word
int lastByte = (int)(ORIGINAL_EXPONENT_VALUE / 0x100) *
    0x100 ^ ORIGINAL_EXPONENT_VALUE;

int lastByteNew = (int)(newExponent / 0x100) * 0x100 ^ newExponent;

// Moves it into position as the MSB of a 32-bit integer 
// i.e 0xff -> 0xff000000
int exponenetMaskRight = (lastByte * 0x1000000) ^ 
    (lastByteNew * 0x1000000);

W[4] = W[4] ^ exponenetMaskRight;
\end{OpenCLCode}
\end{adjustbox}

### 2019-08-20 Writeup/Thesis/code/GoogleAppScript.tex
Changes; - Added some changes from supervisor - Began fixing structure of the document

\begin{adjustbox}{width=\textwidth,keepaspectratio}
  \begin{JavascriptCode}
vvar ALGOS = ["Soundex", "Metaphone", ...];
var ALGO_SIZES = [763777, 412916, ...];

function updateForm(ss, form) {

  // Obtains a list of the items present on the form
  formItems = form.getItems();

  // Updates the new values
  var algo_index = 0;
  var scale_index = 0;
  for (var i = 0; i < formItems.length; i++)
  {
    if (formItems[i].getType() == "SCALE")
    {
      var rnd_index = Math.floor(Math.random() * 
      ALGO_SIZES[algo_index]) + 1;

      // Obtains the Google Sheets object
      var sheetname = ALGOS[algo_index];
      var sheet = ss.getSheetByName(sheetname);
      var range = sheet.getRange(rnd_index, 1)
      var values = range.getValues();

      // Re-samples from the connected Google Sheets
      _updateScaleTitle(formItems[i], values[0]);

      scale_index++;

      // Moves on to the next metric when a group size 
      // has been completed
      if (scale_index != 0)
      {
        if (scale_index % QUESTION_PER_ALGO == 0) {
            algo_index++;
        }
      }
    }
  }
}
  \end{JavascriptCode}
\end{adjustbox}

### 2019-08-20 Writeup/Thesis/code/settings/OpenCL.tex
Changes; - Added some changes from supervisor - Began fixing structure of the document

% ======================================================================== %
% Defines the highlighting, style and environment for the OpenCL language
% ========================================================================%

\lstdefinelanguage{OpenCL}{
  keywords={int, __kernel,kernel,__local,local,__global,global,__constant,constant,__private,private, char2,char3,char4,char8,char16, uchar2,uchar3,uchar4,uchar8,uchar16, short2,short3,short4,short8,short16, ushort2,ushort3,ushort4,ushort8,ushort16, int2,int3,int4,int8,int16, uint2,uint3,uint4,uint8,uint16, long2,long3,long4,long8,long16, ulong2,ulong3,ulong4,ulong8,ulong16, float2,float3,float4,float8,float16, image2d_t,image3d_t,sampler_t,event_t, bool2,bool3,bool4,bool8,bool16, half2,half3,half4,half8,half16, quad,quad2,quad3,quad4,quad8,quad16, complex,imaginary, uint, long, bool, for, if},
  keywordstyle=\color{blue}\bfseries,
  ndkeywords={get_global_id, class, export, boolean, throw, implements, import, this},
  ndkeywordstyle=\color{black}\bfseries,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  commentstyle=\itshape\color{OliveGreen}\ttfamily,
  stringstyle=\color{red}\ttfamily,
  morestring=[b]',
  morestring=[b]"
}

\lstdefinestyle{OpenCLStyle}{
    commentstyle=\color{codegreen},
    keywordstyle={\bf \color{blue}},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\footnotesize\ttfamily,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left, 
    columns=fixed,                                   
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=7,
    numberstyle=\tiny, 
    numbersep=8pt,
    language=OpenCL,
}

\newtcblisting{OpenCLCode}[2][]{
	top=0cm,
	bottom=0cm,
	left=0.5cm,
	right=0cm,
	colback=white,
	colframe=black,
    arc=1pt, outer arc=1pt,
    listing only, 
    listing style=OpenCLStyle,
}

### 2019-08-21 Writeup/Thesis/chapters/design.tex
Changes; - Added some more changes from supervisor feedback

@@
 
-Near-collision keys are keys that are deemed a match by the phonetic similarity metric (More on this aspect in the following sections).
-A similarity metric is an algorithm designed to determine if two words are phonetically a match.
-For example, the words "THEIR" and "THERE" is a match, whereas the words "DARK" and "PRINCIPLE" are not phonetically matching.
+Near-collision keys are keys composed of a set of words that are deemed a match by the phonetic similarity metric (See Section \ref{sec:similarity_metric}).
 
@@
 There are many algorithms currently available to provide this functionality.
-This section describes the algorithms alongside the reasons they were selected for assessment later in the project.
+This section describes and explains the reasons they were selected for assessment later in the project.
 
 \subsection{Soundex}
-One of the earliest examples of a phonetic algorithm is known as Soundex.
-It is one of the most famous algorithms due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}.
-Initially designed for indexing names by phonetics alongside spelling mistakes due to transpositions in letters.
-Therefore, due to it being based on the phonetic features, it is highly suitable for this project's use-case.
+Soundex is one of the most famous example of a phonetic algorithm (See Section \ref{sec:soundex}).
+This is due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}.
 
-Soundex produces a four-digit code for each word assessed.
-The first letter of the word is retained alongside the removal of all of a, e, i, o, u, y, h and w.
-The remaining letters are then mapped to numbers.
-These mappings are displayed in Figure \ref{fig:soundexMap}.
-
-\begin{figure}[h!]
-    \centering
-    \begin{BVerbatim}
-b, f, p, v               1
-c, g, j, k, q, s, x, z   2
-d, t                     3
-l                        4
-m, n                     5
-r                        6
-    \end{BVerbatim}
-
-    \caption{Soundex mappings of letters to numbers}
-    \label{fig:soundexMap}
-\end{figure}
-
-\subsection*{Soundex Issues}
-\label{sec:soundexIssues}
-
-Due to the fixed length and limited digit set the initial concerns from this design is the limited number of combinations.
-There are a total of 5616 codes due to 26 initial letters and three digits of 6 values ($26 * 6^3$).
-The limited combinations result in matches of limited quality.
-
-Further issues posed in \cite{patman2001soundex} are discussed below and show the further deficiencies of Soundex in a dictionary word matching context.
-
-\begin{enumerate}
-    \item \textbf{Dependency on the first letter:} Soundex cannot match words together if their first letters are different, meaning, for example, the words "KORBIN" and "CORBIN" are considered non-matching.
-
-    \item \textbf{Silent consonants.} Soundex does not have logic embedded to deal with silent consonants.
-
-    \item \textbf{Poor precision.} Due to the previously discussed point of a limited code space.
-\cite{patman2001soundex} re-iterates this point, but in the context of name matching where Soundex's poor performance was demonstrated.
-Soundex only gained and overall accuracy of 36.37\% when matching names within a provided database.
-\end{enumerate}
-
-However, even with Soundex's issues, it's algorithmic simplicity and popularity allows it to remain relevant in this application.
+Soundex, however, has had extensive work focused on its own deficiencies alongside quantification of its performance under certain conditions.
+However, even with these previously discussed issues, its algorithmic simplicity and popularity allows it to remain relevant for assessment in this project.
 
 \subsection{NYSIIS}
-The New York State Identification and Intelligence System (NYSIIS) phonetic code was created for use matching the phonetics of American names.
-The motivation for it's inception was mostly due to the presence of Hispanic names in the American based databases (this was an aspect Soundex was known to have low accuracy with).
+NYSIIS main use case was the matching of common names present in a database (See Section \ref{sec:nysiis}).
 However, due to it having embedded rules to handle word phonetics, it would again be applicable in this application.
 
-It also allows for variable-length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex.
-It was in use right up util the end of 1998 within various US Government departments.
 Due to NYSIIS's aforementioned use in a professional setting alongside its high occurrence in literature, it was deemed suitable as one of the selected similarity metrics.
@@
 \subsection{Metaphone}
-Metaphone was invented by Lawrence Philips in 1990\cite{philips1990hanging} in response to the deficiencies in Soundex.
-It improves on Soundex by including information around inconsistency and variation in English spelling in an attempt to create a more accurate phonetic representation.
+Metaphone as discussed in Section \ref{sec:metaphone} is anther famous phonetic algorithm.
 Metaphone is arguably on the same level of ubiquity as that of Soundex with it finding itself implemented in languages such as PHP\cite{php}.
@@
 
-Further work would involve the implementation of newer versions of Metaphone.
-Double Metaphone (2000) and Metaphone 3 (2009) that claim to improve over the original version due to further research performed by Philips.
+Further work would involve the implementation of newer versions of Metaphone. Double Metaphone (2000) and
+Metaphone 3 (2009) that claim to improve over the original version due to further research performed by Philips.
 
 \subsection{Levenshtein Distance}
-Levenshtein distance is a string metric designed to measure the 'distance' between two strings.
-It is merely the number of single-character edits (insertions, deletions or substitutions) required to reach the other string.
-Edit distance is not technically designed as a phonetic algorithm, but due to similar-sounding words often being spelt in similar ways\cite{hettiarachchi2012sparcl}.
+As explained in Section \ref{sec:leven} Levenshtein Distance is the number of whole character edits.
+Levenshtein distance is not technically designed as a phonetic algorithm, but due to similar-sounding words often being spelt in similar ways\cite{hettiarachchi2012sparcl} the use-case of this algorithm remains relevant.
 Alongside this, Levenshtein is also the most algorithmically simplistic of all the considered options.
-These aspects contributed to Levenshtein's inclusion.
-
-An example distance between \verb|trace| and \verb|place| would be the substitutions of the first to letters, from \verb|tr| to \verb|pl|, meaning the two strings have a Levenshtein distance of 2.
+These aspects, therefore, contribute to Levenshtein's inclusion in the chosen set.
 
 \subsection{Phonetic Vectors}
-Phonetic Vectors is a unique addition to the chosen set.
-Created by Allison Parrish in 2017\cite{parrish2017poetic}, Phonetic vectors is as the name suggests the vectorisation of the phonetics of a word.
-
-Phonetic features are used in this work as a way to compare the similarity of phonemes.
-Phonemes are the phonetic elements that construct a word.
-For example, the word "RING" translated into the phonemes \verb|/R IH NG/|.
-
-Extensive prior work has gone into producing models of features that map to phonemes \cite{chomsky1968sound}\cite{ladefoged1969measurement}\cite{bradlow2010perceptual}.
-Features, therefore, are an attempt at mapping the varying and inconsistent rules around the pronunciation of the English language.
-The vectors were created using lists phonemes from the CMU Pronouncing Dictionary and mapping them to possible features.
-
-\begin{table}[!htb]
-    \tiny
-    \begin{minipage}{.33\linewidth}
-        \centering
-        \begin{tabular}{ll}
-            Phone & Features \\
-            \hline
-            AA & bck, low, unr, vwl \\
-            AE & fnt, low, unr, vwl \\
-            AH & cnt, mid, unr, vwl \\
-            AO & bck, lmd, rnd, vwl \\
-            AW & bck, cnt, low, rnd, smh, unr, vwl \\
-            AY & cnt, fnt, low, smh, unr, vwl \\
-            B & blb, stp, vcd \\
-            CH & alv, frc, stp, vls \\
-            D & alv, stp, vcd \\
-            DH & dnt, frc, vcd \\
-            EH & fnt, lmd, unr, vwl \\
-            ER & cnt, rzd, umd, vwl \\
-            EY & fnt, lmd, smh, unr, vwl
-        \end{tabular}
-    \end{minipage}%
-    \begin{minipage}{.33\linewidth}
-        \centering
-        \begin{tabular}{ll}
-            Phone & Features \\
-            \hline
-            F &  frc, lbd, vls \\
-            G &  stp, vcd, vel \\
-            HH & apr, glt \\
-            IH & fnt, smh, unr, vwl \\
-            IY & fnt, hgh, unr, vwl \\
-            JH & alv, frc, stp, vcd \\
-            K &  stp, vel, vls \\
-            L &  alv, lat \\
-            M &  blb, nas \\
-            N &  alv, nas \\
-            NG & nas, vel \\
-            OW & bck, rnd, smh, umd, vwl \\
-            OY & bck, fnt, lmd, rnd, smh, unr, vwl
-        \end{tabular}
-    \end{minipage} 
-    \begin{minipage}{.33\linewidth}
-        \centering
-        \begin{tabular}{ll}
-            Phone & Features \\
-            \hline
-            P & blb, stp, vls \\
-            R & alv, apr \\
-            S & alv, frc, vls \\
-            SH & frc, pla, vls \\
-            T & alv, stp, vls \\
-            TH & dnt, frc, vls \\
-            UH & bck, rnd, smh, vwl \\
-            UW & bck, hgh, rnd, vwl \\
-            V & frc, lbd, vcd \\
-            W & apr, lbv \\
-            Y & apr, pal \\
-            Z & alv, frc, vcd \\
-            ZH & frc, pla, vcd \\
-        \end{tabular}
-    \end{minipage} 
-    \caption{Phonemes to feature mapping table}
-    \label{tab:features}
-\end{table}
-
-Table \ref{tab:features} contains the mappings used in \cite{parrish2017poetic} to create the phonetic feature lists.
-Using this with all 133,852 entries in version 0.7b of the CMU Pronouncing Dictionary, 949 unique properties were produced overall.
-The author then performed principal components analysis\footnote{Details regarding this process is outside the scope of the project.
-Please, however, if interested please refer to this resource for more information: \url{http://setosa.io/ev/principal-component-analysis/}} on the unique properties to reduce them down to 50.
-
-This metric allows for a unique set of actions to be performed on the phonetic output.
-Not only does this metric allow the user to measure \textit{dissimilarity} (as opposed to the similar-or-not method of the alternatives) the continuous nature of the value allows mathematical operations to be performed on the output.
-An example shown in \cite{parrish2017poetic} was the addition of word vectors.
-
-\begin{table}[!htb]
-    \centering
-    \begin{tabular}{cll}
-        No & Operation & Result \\
-        \hline
-        1  & $Vec(\verb|sub|) + Vec(\verb|marine|)$ & \verb|submarine| \\
-        2  & $Vec(\verb|miss|) + Vec(\verb|sieve|)$ & \verb|missive| \\
-        3  & $Vec(\verb|fizz|) + Vec(\verb|theology|)$ & \verb|physiology| \\
-    \end{tabular}
-    \caption{Examples of vector addition}
-    \label{tab:vectorAdd}
-\end{table}
-
-For example, the addition of vectors can be seen in Table \ref{tab:vectorAdd}. This works for any mathematical operation with examples like multiplication allowing the `tinting' words with a theme.
-
-The ability to perform operations and measure dissimilarity allows for a plethora of applications.
+As discussed in Section \ref{sec:phonetic_vectors} the metrics ability to perform operations and measure dissimilarity allows for a plethora of applications.
 One possible application of note would be the creation of a wordlist where the phonetic difference (vector distance) is maximised.
-This application, if the vector mappings are an accurate representation, could allow the creation of a phonetically distinctive wordlist.
-These unique aspects contribute to the inclusion of this metric in the set.
+This application, if the vector mapping is an accurate representation, could allow the creation of a phonetically distinctive wordlist.
+Therefore, these unique aspects contribute to the inclusion of this metric in the set.
 
@@
 Scallion was designed by Richard Klafter and Eric Swanson and was used to demonstrate that 32-bit PGP key IDs were insufficient.
-To keep with the onion-based theme, the proposed tool is known as GreenOnion and is a re-write of Scallion in C++.
+To keep with the onion-based theme, the proposed tool is called `GreenOnion' and is a re-write of Scallion in C++.
 This language was chosen due to the well-understood efficiency benefits.
@@
 Match size was used as a way to decide on a cut-off point.
+Match size is the number of matches determined by the metric on the English version of the Trustword dictionary (51903 unique words).
 
@@
 
-Match size was also used to define the cap for the phonetic vectors.
+Match size was also used to define the threshold for the phonetic vectors.
 The decision is less apparent that that of Levenshtein due to the continuous nature of the distance between two vectors.
@@
 
-\begin{figure}[h!]
-    \centering
-    \fbox{
-        \includegraphics[width=\textwidth]{experiment/trustword_attack.png}
-    }
-    \caption{Experiment UI}
-    \label{fig:expID}
-\end{figure}
-
-Figure \ref{fig:expID} shows the design of the experiments front end.
+Appendix \ref{appendix:trustword_attack} shows the design of the experiments front end\footnote{A live version can also be viewed at the url: \url{https://afray.pythonanywhere.com/}}.
 As can be seen by comparing it to Figure \ref{fig:trustwords}, it has been designed to be as close as possible to the actual application.

### 2019-08-21 Writeup/Thesis/chapters/lit_review.tex
Changes; - Added some more changes from supervisor feedback

@@
 
-\subsection*{Public-key Cryptography and Key Exchange}
+\subsection{Public-key Cryptography and Key Exchange}
 
@@
 
-\section{Encoding schemes}
+\subsection{Encoding schemes}
 \label{sec:encodingSchemes}
@@
 The main elements of comparison have been the ``accuracy of attack detection" and ``time to compare." In this paper, these are considered the metrics of ``security'' and ``usability,'' respectively.
+
+\subsection{Similarity Metrics}
+\label{sec:similarity_metric}
+A similarity metric is an algorithm designed to determine if two words are phonetically a match.
+For example, the words "THEIR" and "THERE" is a match, whereas the words "DARK" and "PRINCIPLE" are not phonetically matching.
+This section provides a base explanation of important phonetic algorithms.
+
+\subsubsection*{Soundex}
+\label{sec:soundex}
+One of the earliest examples of a phonetic algorithm is known as Soundex. It was initially designed for indexing names by phonetics alongside spelling mistakes due to transpositions in letters.
+
+Soundex produces a four-digit code for each word assessed.
+The first letter of the word is retained alongside the removal of all of a, e, i, o, u, y, h and w.
+The remaining letters are then mapped to numbers.
+These mappings are displayed in Figure \ref{fig:soundexMap}.
+
+\begin{figure}[h!]
+    \centering
+    \begin{BVerbatim}
+b, f, p, v               1
+c, g, j, k, q, s, x, z   2
+d, t                     3
+l                        4
+m, n                     5
+r                        6
+    \end{BVerbatim}
+
+    \caption{Soundex mappings of letters to numbers}
+    \label{fig:soundexMap}
+\end{figure}
+
+Due to the fixed length and limited digit set the initial concerns from this design is the limited number of combinations.
+There are a total of 5616 codes due to 26 initial letters and three digits of 6 values ($26 * 6^3$).
+The limited combinations result in matches of limited quality.
+
+Further issues posed in \cite{patman2001soundex} are discussed below and show the further deficiencies of Soundex in a dictionary word matching context.
+
+\begin{enumerate}
+    \item \textbf{Dependency on the first letter:} Soundex cannot match words together if their first letters are different, meaning, for example, the words "KORBIN" and "CORBIN" are considered non-matching.
+
+    \item \textbf{Silent consonants.} Soundex does not have logic embedded to deal with silent consonants.
+
+    \item \textbf{Poor precision.} Due to the previously discussed point of a limited code space.
+\cite{patman2001soundex} re-iterates this point, but in the context of name matching where Soundex's poor performance was demonstrated.
+Soundex only gained and overall accuracy of 36.37\% when matching names within a provided database.
+\end{enumerate}
+
+\subsubsection*{NYSIIS}
+\label{sec:nysiis}
+The New York State Identification and Intelligence System (NYSIIS) phonetic code was created for use matching the phonetics of American names.
+The motivation for it's inception was mostly due to the presence of Hispanic names in the American based databases (this was an aspect Soundex was known to have low accuracy with).
+
+It also allows for variable-length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex.
+It was in use right up util the end of 1998 within various US Government departments.
+
+\subsubsection*{Metaphone}
+\label{sec:metaphone}
+Metaphone was invented by Lawrence Philips in 1990\cite{philips1990hanging} in response to the deficiencies in Soundex.
+It improves on Soundex by including information around inconsistency and variation in English spelling in an attempt to create a more accurate phonetic representation.
+
+\subsubsection{Levenshtein Distance}
+\label{sec:leven}
+Levenshtein distance is a string metric designed to measure the `distance' between two strings.
+It is merely the number of single-character edits (insertions, deletions or substitutions) required to reach the other string.
+
+An example distance between \verb|trace| and \verb|place| would be the substitutions of the first to letters, from \verb|tr| to \verb|pl|, meaning the two strings have a Levenshtein distance of 2.
+
+\subsubsection{Phonetic Vectors}
+\label{sec:phonetic_vectors}
+Phonetic Vectors is a unique addition to the chosen set.
+Created by Allison Parrish in 2017\cite{parrish2017poetic}, Phonetic vectors is as the name suggests the vectorisation of the phonetics of a word.
+
+Phonetic features are used in this work as a way to compare the similarity of phonemes.
+Phonemes are the phonetic elements that construct a word.
+For example, the word "RING" translated into the phonemes \verb|/R IH NG/|.
+
+Extensive prior work has gone into producing models of features that map to phonemes \cite{chomsky1968sound}\cite{ladefoged1969measurement}\cite{bradlow2010perceptual}.
+Features, therefore, are an attempt at mapping the varying and inconsistent rules around the pronunciation of the English language.
+The vectors were created using lists phonemes from the CMU Pronouncing Dictionary and mapping them to possible features.
+
+\begin{table}[!htb]
+    \tiny
+    \begin{minipage}{.33\linewidth}
+        \centering
+        \begin{tabular}{ll}
+            Phone & Features \\
+            \hline
+            AA & bck, low, unr, vwl \\
+            AE & fnt, low, unr, vwl \\
+            AH & cnt, mid, unr, vwl \\
+            AO & bck, lmd, rnd, vwl \\
+            AW & bck, cnt, low, rnd, smh, unr, vwl \\
+            AY & cnt, fnt, low, smh, unr, vwl \\
+            B & blb, stp, vcd \\
+            CH & alv, frc, stp, vls \\
+            D & alv, stp, vcd \\
+            DH & dnt, frc, vcd \\
+            EH & fnt, lmd, unr, vwl \\
+            ER & cnt, rzd, umd, vwl \\
+            EY & fnt, lmd, smh, unr, vwl
+        \end{tabular}
+    \end{minipage}%
+    \begin{minipage}{.33\linewidth}
+        \centering
+        \begin{tabular}{ll}
+            Phone & Features \\
+            \hline
+            F &  frc, lbd, vls \\
+            G &  stp, vcd, vel \\
+            HH & apr, glt \\
+            IH & fnt, smh, unr, vwl \\
+            IY & fnt, hgh, unr, vwl \\
+            JH & alv, frc, stp, vcd \\
+            K &  stp, vel, vls \\
+            L &  alv, lat \\
+            M &  blb, nas \\
+            N &  alv, nas \\
+            NG & nas, vel \\
+            OW & bck, rnd, smh, umd, vwl \\
+            OY & bck, fnt, lmd, rnd, smh, unr, vwl
+        \end{tabular}
+    \end{minipage} 
+    \begin{minipage}{.33\linewidth}
+        \centering
+        \begin{tabular}{ll}
+            Phone & Features \\
+            \hline
+            P & blb, stp, vls \\
+            R & alv, apr \\
+            S & alv, frc, vls \\
+            SH & frc, pla, vls \\
+            T & alv, stp, vls \\
+            TH & dnt, frc, vls \\
+            UH & bck, rnd, smh, vwl \\
+            UW & bck, hgh, rnd, vwl \\
+            V & frc, lbd, vcd \\
+            W & apr, lbv \\
+            Y & apr, pal \\
+            Z & alv, frc, vcd \\
+            ZH & frc, pla, vcd \\
+        \end{tabular}
+    \end{minipage} 
+    \caption{Phonemes to feature mapping table}
+    \label{tab:features}
+\end{table}
+
+Table \ref{tab:features} contains the mappings used in \cite{parrish2017poetic} to create the phonetic feature lists.
+Using this with all 133,852 entries in version 0.7b of the CMU Pronouncing Dictionary, 949 unique properties were produced overall.
+The author then performed principal components analysis\footnote{Details regarding this process is outside the scope of the project.
+Please, however, if interested please refer to this resource for more information: \url{http://setosa.io/ev/principal-component-analysis/}} on the unique properties to reduce them down to 50.
+
+This metric allows for a unique set of actions to be performed on the phonetic output.
+Not only does this metric allow the user to measure \textit{dissimilarity} (as opposed to the similar-or-not method of the alternatives) the continuous nature of the value allows mathematical operations to be performed on the output.
+An example shown in \cite{parrish2017poetic} was the addition of word vectors.
+
+\begin{table}[!htb]
+    \centering
+    \begin{tabular}{cll}
+        No & Operation & Result \\
+        \hline
+        1  & $Vec(\verb|sub|) + Vec(\verb|marine|)$ & \verb|submarine| \\
+        2  & $Vec(\verb|miss|) + Vec(\verb|sieve|)$ & \verb|missive| \\
+        3  & $Vec(\verb|fizz|) + Vec(\verb|theology|)$ & \verb|physiology| \\
+    \end{tabular}
+    \caption{Examples of vector addition}
+    \label{tab:vectorAdd}
+\end{table}
+
+For example, the addition of vectors can be seen in Table \ref{tab:vectorAdd}. This works for any mathematical operation with examples like multiplication allowing the `tinting' words with a theme.
 

### 2019-08-22 Writeup/Thesis/chapters/design.tex
Changes; - More progress added to the thesis

@@
 \section{Overall attack design}
+\label{sec:attackDesign}
 
@@
 
-    \item Calculate all permutations of near-collisions for the key pair and produce a list of similar key fingerprints.
+    \item Calculate all permutations of near-collisions for the key pair and produce a list of near-collision key fingerprints.
 
-    \item Use a list of similar keys in the mass computation of keys to find near-collision keys.
+    \item Use a list of near-collision keys in the mass computation of keys to find near-collision keys.
 
@@
 \subsubsection{Matches}
+\label{sec:matches}
+
 A match for each code based metric (Soundex, Metaphone and NYSIIS) occurs when the codes are identical.
@@
 As it can be seen from Table \ref{tab:matchSize}, the number of matches for L2 is more significant than all metrics excluding Soundex.
-As the issues with Soundex have been discussed in previous sections (See Section \ref{sec:soundexIssues}) it can be excluded as an abnormality in this context.
+As the issues with Soundex have been discussed in previous sections (See Section \ref{sec:soundex}) it can be excluded as an abnormality in this context.
 Therefore, due to the excessively high value for a L2, L1 was chosen as the Levenshtein cap for defining a match.
@@
 \subsubsection{Comparisons}
-Each participant is asked to rate the similarity of a match on a scale of 1 to 5.
+Each comparison contains a match-pair.
+These matches are generated by running the similarity metric over all the pairings in the Trustword dictionary, if the pair meets the criteria discussed in the previous section it is determined a match.
+Potential matches are then sampled from their respective lists.
+
+Each participant is then asked to rate the similarity of a match on a scale of 1 (\textit{`Very different sound'}) and 5 (\textit{`Very similar sound'}).
 Figure \ref{fig:phoneticMatch} shows an example match and the connected scale.
-Users are provided with five of these comparisons per metric.
+Users are provided with five of these comparisons per similarity metric.
 
@@
 
-The final experiment required to answer Research Question \ref{goal:attackPercentage} requires the simulation attacks on participants.
+This experiment is designed to be a simulation of the attack proposed in Section \ref{sec:attackDesign}, in an attempt to answer Research Question \ref{goal:attackPercentage}.
+The experiment will test the simulated matches of three similarity metrics decided by the previous experiment (See Section \ref{sec:metrics}).
+The overall aim of the experiment is to quantify the success rate of the attack on live participants.
 The user is presented with the same design as the \pep Android application (See Section \ref{sec:pep}).
@@
 Therefore, in this experiment, attacks only occur 30\% of the time.
-This occurrence is a much higher value than in a real-world setting, but it is a balance between resources and realistic design.
-Alongside, this the first 5 trials of a new experiment is always benign.
-This inclusion is to ensure users are lulled into a level of complacency regarding the possibility of an attack.
+This occurrence is a much higher value than in a real-world setting, but is a balance between resources and realistic design.
+If the chosen attack rate is too low, many more trials are required to collate a useful number of attack instances, thus, requiring more resources but with a much more realistic design.
+If, however, the attack rate is too high, less total rounds are required to obtain the target number of attack trails, however, the user will lose their complacency as an attack will be expected.
+This loss of complacency is undesirable as it does not realistically reflect real life.
+Furthermore, the first 5 trials of a new experiment is always benign.
+This inclusion is to ensure users are consistently lulled into of complacency.
 
-Certain keys have higher levels of near-collision possibilities than others due to how certain words are deemed similar by the chosen metric.
-Therefore, this presents the possibility to have keys with a very low number of similar matches.
+Certain keys have higher levels of potential near-collision keys than others due to how certain words are deemed similar by the similarity metric.
+Therefore, this presents the possibility to have keys with a very low number of possible near-collision keys.
 The distribution of these keys is explained further in Chapter \ref{cha:Experiments}.
@@
 Therefore, the experiment is designed to sample from a list of "vulnerable" keys.
-These are keys that have a number of combinations that allow an attack in a specified timeframe.
+These are keys that have a number of potential near-collision keys that allow computation in a specified timeframe.
 
-Furthermore, certain levels of attacks are also simulated. Below is the list of possible attacks:
+Furthermore, certain levels of attacks are also simulated. Below is the list of attacks considered in this experiment:
 
 \begin{itemize}
-    \item \textbf{Zero static words} - All words in the set can vary.
-    \item \textbf{One static word} - All but the first word can vary.
-    \item \textbf{Two static words} - All but the first and last word can vary.
+    \item (\OOOO) All words in the set can vary             
+    \item (\XOOO) All but the first word can vary           
+    \item (\XOOX) All but the first and last word can vary  
+\end{itemize}
+
+$Where: $
+\begin{itemize}
+    \item[] \verb|X|: is a static word
+    \item[] \verb|O|: is a changeable word
 \end{itemize}
@@
 These attacks are ascending in complexity.
-The timeframe for finding a match was decided as 7-days with attack strengths of 1 GPU/day, 10 GPU/days and 100 GPU/days on a mid-range GPU (AMD RX 480 was the example in experiments).
+The timeframe for computing a near-collision was decided as 7-days with attack strengths of 1 GPU-day, 10 GPU-days and 100 GPU-days on a mid-range GPU (AMD RX 480).
 Due to the long lifetime of PGP keys, 7 days was chosen as a reasonable length of the attack.
@@
 Table \ref{tab:attackReq} contains a summary of the different level of attacks and their respective restrictions.
-More combinations make the attack search quicker.
-Any key that exceeds this criterion is deemed as vulnerable.
+More potential near-collision keys make the attack search quicker.
+Any key that exceeds the defined numbers of potential near-collision key for attack level are deemed as vulnerable.
+As discussed in Section \ref{sec:attackDesign} the near-collision keys are close keys produced from the similarity-metric's matches.
 A list of these vulnerable keys is sampled from when an attack is simulated.
@@
 If users complete the experiment in an abnormally small amount of time, it can be used as another detection for invalid responses.
-Anything below a certain threshold is discarded.
+A benchmark for the time is set by completing the experiment correctly but as fast as possible.
+Anything below this pace was discarded as anything higher will risk invalid and rushed results.
 

### 2019-08-22 Writeup/Thesis/chapters/implementation.tex
Changes; - Added some changes from supervisor - Began fixing structure of the document
Changes; - More progress added to the thesis

--- 2019-08-15 Writeup/Thesis/pages/implementation.tex
@@
   \centering
-  \input{diagrams/code/OpenKernel.tex}
+  \input{code/OpenKernel.tex}
   \caption{OpenCL Kernel}
@@
   \centering
-  \input{diagrams/code/ExponentIncrement.tex}
+  \input{code/ExponentIncrement.tex}
   \caption{Exponent incrementation code}
@@
 
+\newpage
+
 \section{First Experiment}
+As discussed in Section \ref{sec:matches} as list of matches were generated by each metric.
+Figure REF shows the algorithm designed to compute these match lists.
+It loads the Trustword dictionary and works through all combinations of matches.
+
+\begin{figure}[h!]
+\begin{lstlisting}[language=C++, frame=single]
+  void find_similar_words(std::vector<std::string> words)
+  {
+      std::vector<std::string> sim_words;
+
+      for (std::string word_y : words)
+      {
+          sim_words.push_back(word_y);
+
+          for (std::string word_x : words)
+          {
+                // Makes sure the same words aren't checked
+              if (word_y != word_x)
+              {
+                  bool add_word = false;
+
+                  else
+                  {
+                      if (LEVENSHTEIN) add_word = 
+                            leven_similar(word_y, word_x);
+
+                      else if (METAPHONE) add_word = 
+                            metaphone_similar(word_y, word_x);
+
+                      else if (NYSIIS) add_word = 
+                            nysiis_similar(word_y, word_x);
+                  }
+
+                  if (add_word)
+                  {
+                      sim_words.push_back(word_x);
+                      add_word = false;
+                  }
+              }
+          }
+      }
+  }
+  \end{lstlisting}
+  \caption{}
+\end{figure}
+
+\newpage
+
+Figure REF also shows an example matching algorithm for Levenshtein. The difference is computed and compared to the tolerance discussed in Section \ref{sec:matches}.
+
+\begin{figure}[h!]
+\begin{lstlisting}[language=C++, frame=single]
+bool leven_similar(std::string word1, std::string word2)
+{
+  int diff = lev_distance(word1, word2);
+  return diff <= DIFFERENCE_TOLERANCE;
+}
+\end{lstlisting}
+\caption{}
+\end{figure}
+
 In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}), Google Forms\footnote{\url{https://www.google.com/forms}} was used to host and design the questionnaire.
@@
   \centering
-  \input{diagrams/code/GoogleAppScript.tex}
+  \input{code/GoogleAppScript.tex}
 \caption{Section of code from the First Experiment's Google App Script}

### 2019-08-26 Writeup/Thesis/chapters/experiments.tex
Changes; - Updated a global code style for the paper - Fixed some more supervisor issues - Small changes

@@
-\chapter{Experiments}
+\chapter{Experimentation Results}
 \label{cha:Experiments}
@@
 
-\begin{figure}[h!]
-    \centering
-    \input{graphs/speed.tex}
-    \label{tab:scallion_speed}
-    \caption{Speed comparison between Scallion and GreenOnion}
-\end{figure}
-
 This section compares Scallion and the newly designed GreenOnion ability to search for a large number of potential keys.
 
-Figure \ref{tab:scallion_speed} shows the speed decline as the number of keys increases for Scallion.
+Figure \ref{tab:scallion_speed} shows the speed decline as the number of potential keys checked in one go increases for Scallion.
 Any number of keys over 40 resulted in a crash for Scallion.
@@
 
+GreenOnion's code has been made publicly available on GitHub \footnotemark{TODO}.
+
+\begin{figure}[h!]
+    \centering
+    \input{graphs/speed.tex}
+    \label{tab:scallion_speed}
+    \caption{Speed comparison between Scallion and GreenOnion}
+\end{figure}
+
+\newpage
+
 \section{Experiment 1 - Metric performance}
 
-As discussed in Section \ref{exp:metric}, the goal of the experiment was the cull the number of metrics to be assessed in the following experiment.
+As discussed in Section \ref{exp:metric}, the goal of the experiment was to select a set of metrics to be assessed in the following experiment.
 This section will discuss the demographics of participants alongside the subsequent results.
@@
         \hline
-        Gender & Male: & 44.44\% \\
-               & Female: & 55.56\% \\
+        Gender & Male: & 44.4\% \\
+               & Female: & 55.6\% \\
         \hline
-        Age:   & 18-24: & 10.10\% \\
-               & 25-29: & 20.20\% \\
-               & 30-39: & 31.31\% \\
-               & 40-49: & 21.21\% \\
-               & 50-59: & 12.12\% \\
-               & 60-69: & ~~4.04\% \\ 
-               & 70-79: & ~~1.01\% \\
+        Age:   & 18-24: & 10.1\% \\
+               & 25-29: & 20.2\% \\
+               & 30-39: & 31.3\% \\
+               & 40-49: & 21.2\% \\
+               & 50-59: & 12.1\% \\
+               & 60-69: & ~~4.0\% \\ 
+               & 70-79: & ~~1.0\% \\
 
@@
         Highest Education:  
-        & GCSE:                 & 13.13\% \\
-        & A-Level/O-Level:      & 19.19\% \\
-        & Bachelor's degree:    & 52.53\% \\
-        & Master's degree:      & 13.13\% \\ 
-        & PhD:                  & ~~2.02\%  \\
+        & GCSE:                 & 13.1\% \\
+        & A-Level/O-Level:      & 19.2\% \\
+        & Bachelor's degree:    & 52.5\% \\
+        & Master's degree:      & 13.1\% \\ 
+        & PhD:                  & ~~2.0\%  \\
         \hline
@@
 Table \ref{tab:exp1_demo} contains the demographical breakdown of the reduced set of participants.
-The average ages of the participants were 37.3 years ($\sigma = 11.67$)with a split of 44.44\% of Males to 55.56\% of Females.
+The average ages of the participants were 37.3 years ($\sigma = 11.67$)with a split of 44.4\% of Males to 55.6\% of Females.
 As can be seen, over 60\% of participants can be considered highly educated (Bachelor’s and up).
@@
 
-Figure \ref{tab:exp1_results} shows the average results for the metrics.
+Figure \ref{tab:exp1_results} shows the average results for the selected matches explained in Section \ref{sec:exp1_comparison}.
 It can be seen that Levenshtein came out substantially above the rest.
@@
 \label{sec:averagePerms}
-In order to predict the effectiveness of the attack over a wide variety of keys, the number of average near-matches requires computation.
-Table \ref{tab:average_perm} shows the average keys for each metric.
+In order to predict the effectiveness of the attack over a wide variety of keys, the number of average near-collision keys requires computation.
+Table \ref{tab:average_perm} shows the average number of potential collision keys for each metric.
 The ``Compute Time'' is the computation time required for a single mid-range (2000MH/s) GPU.
@@
     }
-    \caption{Each metric's average near-collision keys}
+    \caption{Each metric's average number of near-collision keys}
     \label{tab:average_perm}

### 2019-08-26 Writeup/Thesis/chapters/implementation.tex
Changes; - Updated a global code style for the paper - Fixed some more supervisor issues - Small changes

--- 2019-08-15 Writeup/Thesis/pages/implementation.tex
@@
 
+\newpage
+
 \section{First Experiment}
+\label{sec:exp1_implemtation}
+As discussed in Section \ref{sec:matches} a list of matches were generated for each metric.
+Figure \ref{fig:trustwordMatch} shows the algorithm designed to compute these lists.
+It loads the entire Trustword dictionary and works through all combinations of words.
+
+\begin{figure}[h!]
+  \centering
+  \input{code/TrustwordPlusPlus.tex}
+  \caption{Main code used to generate match list}
+  \label{fig:trustwordMatch}
+\end{figure}
+
+Figure \ref{fig:matchExample} further shows the code used in the \verb|leven_similar|.
+The levenshtein difference is computed and compared to the tolerance discussed in Section \ref{sec:matches}.
+If this function returns true the match is added to the list of matches.
+
+\begin{figure}[h!]
+\begin{Code}[CppStyle]
+bbool leven_similar(string word1, string word2)
+{
+  int diff = lev_distance(word1, word2);
+  return diff <= DIFFERENCE_TOLERANCE;
+}
+\end{Code}
+\caption{Example similar match function}
+\label{fig:matchExample}
+\end{figure}
+
+\newpage
+
 In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}), Google Forms\footnote{\url{https://www.google.com/forms}} was used to host and design the questionnaire.

### 2019-08-26 Writeup/Thesis/code/ExponentIncrement.tex
Changes; - Updated a global code style for the paper - Fixed some more supervisor issues - Small changes

@@
 \begin{adjustbox}{width=\textwidth,height=15cm,keepaspectratio}
-\begin{OpenCLCode}
+\begin{Code}[OpenCLStyle]
 ///The exponent is split across two words
@@
 W[4] = W[4] ^ exponenetMaskRight;
-\end{OpenCLCode}
+\end{Code}
 \end{adjustbox}

### 2019-08-26 Writeup/Thesis/code/settings/OpenCL.tex
Changes; - Updated a global code style for the paper - Fixed some more supervisor issues - Small changes

@@
 
-\lstdefinestyle{OpenCLStyle}{
-    commentstyle=\color{codegreen},
-    keywordstyle={\bf \color{blue}},
-    numberstyle=\tiny\color{codegray},
-    stringstyle=\color{codepurple},
-    basicstyle=\footnotesize\ttfamily,
-    breakatwhitespace=false,         
-    breaklines=true,                 
-    captionpos=b,                    
-    keepspaces=true,                 
-    numbers=left, 
-    columns=fixed,                                   
-    showspaces=false,                
-    showstringspaces=false,
-    showtabs=false,                  
-    tabsize=7,
-    numberstyle=\tiny, 
-    numbersep=8pt,
-    language=OpenCL,
-}
-
-\newtcblisting{OpenCLCode}[2][]{
-	top=0cm,
-	bottom=0cm,
-	left=0.5cm,
-	right=0cm,
-	colback=white,
-	colframe=black,
-    arc=1pt, outer arc=1pt,
-    listing only, 
-    listing style=OpenCLStyle,
-}
+\defineStyle{OpenCLStyle}{OpenCL}

### 2019-08-28 Writeup/Paper/sections/introduction.tex
Changes; - Implemted changes from Sia - Added abstract and acknowledgements

--- 2019-08-20 Writeup/Thesis/chapters/introduction.tex
@@
-\chapter{Introduction}
-\pagenumbering{arabic}
-\label{cha:Introduction}
+\section{Introduction}
 
 The increasing use of public-key cryptography by instant messaging and secure email means ensuring confidentiality is an ever more important task.
-
 One of the most significant risks to the security of the communication channel is a Man-in-the-middle (MiTM) attack.
@@
 MiTM attacks can entirely circumvent the encryption as it allows an attacker to read all of the encrypted data.
-
 A countermeasure for the threat of MiTM attacks is the verification of each parties’ fingerprint.
 A fingerprint is a small string of characters that is unique to each key and, thus, can be used to identify.
-
 Fingerprints can come in several different encodings such as Hexadecimal, words, and even procedurally generated avatars.
@@
 Consequently, this makes the designing of user-friendly schemes a task of utmost importance.
-
 Humans are commonly considered the most vulnerable part of any computer system.
@@
 Therefore, research into improving or creating a more secure and user-friendly fingerprint encoding remains an important task.
-
 One proposed user-friendly scheme is Pretty Easy Privacy's (p$\equiv$p) "Trustwords".
@@
 This usability boost, however, comes at a cost of a much larger word list.
-
 This report evaluates the security and feasibility of attacking Trustwords. The motivation for this is due in part to the shortage of justification behind the size and features of the chosen wordlist.
-
-\newpage
-The report is structured as follows:
-
-\begin{itemize}
-    \item \textbf{Chapter 2} provides any required background knowledge alongside a review of all relevant literature.
-
-    \item \textbf{Chapter 3} formally defines the aim of this report alongside the research questions the project aims to answer.
-
-    \item \textbf{Chapter 4} documents the proposed designs required to answer the research questions proposed in Chapter 3.
-
-    \item \textbf{Chapter 5} discusses the significant implementation details of the designs formalized in Chapter 4.
-
-    \item \textbf{Chapter 6} presents and analyses all experimentation results of the project.
-
-    \item \textbf{Chapter 7} evaluates and concludes the success of the project alongside a discussion into proposed further work.
-The research aims proposed earlier in Chapter 3 are used as evaluative metrics.
-\end{itemize}

### 2019-08-28 Writeup/Thesis/chapters/abstract.tex
Changes; - Implemted changes from Sia - Added abstract and acknowledgements

Many encrypted connections require the comparison of a fingerprint to protect against eavesdropping. A substantial amount of past work has aimed to propose fingerprint representations that work better with human limitations. "Trustwords" proposed by pEp is an example of such a scheme, where the fingerprint is encoded as words in an attempt to improve usability.

This work implements an attack on Trustwords and quantifies its effectiveness on more than 400 participants.  A tool called GreenOnion was designed to assist in quantifying attack feasibility. GreenOnion improved substantially on a similar tool's ability to search for matches concurrently. Our findings show a substantial increase in attack success compared to related literature. We believe this increase is due to leveraging the design flaws in the Trustword scheme.

### 2019-08-28 Writeup/Thesis/chapters/design.tex
Changes; - Updated a global code style for the paper - Fixed some more supervisor issues - Small changes
Changes; - Implemted changes from Sia - Added abstract and acknowledgements

@@
 The attack on Trustwords involves generating "near-collision" keys. 
-This attempts to provide the base to answer Research Questions \ref{goal:numberOfTrustwords}, \ref{goal:complexity} and \ref{goal:hardwareRequired}.
+This attempts to provide the base to answer Research Questions \ref{goal:numberOfTrustwords} and \ref{goal:complexity}.
 
@@
 \label{sec:greenDesign}
-In order to answer Research Questions \ref{goal:complexity} and \ref{goal:hardwareRequired} fully, it is necessary to implement an actual tool to generate actual keys.
+In order to answer Research Questions \ref{goal:complexity} fully, it is necessary to implement an actual tool to generate actual keys.
 
@@
 \label{exp:metric}
-This section answers Research Question \ref{goal:bestMetrics}.
+This section answers Research Question \ref{goal:phoneticSimilarity}.
 To reduce the number of metrics to assess in the later rounds, the performance of similarity metrics required comparison.
@@
 \subsubsection{Comparisons}
+\label{sec:exp1_comparison}
 Each comparison contains a match-pair.
@@
 
+\newpage
+
 \subsection{Trustword Attacks}
 \label{sec:exp2_design}
-
-\todo{Include explination into how audio is generated}
 

### 2019-08-28 Writeup/Thesis/chapters/evaluation.tex
Changes; - Implemted changes from Sia - Added abstract and acknowledgements

@@
 
-Research Question \ref{goal:phoneticSimilarity} asks: \textit{``What are the different ways phonetic similarity can be quantified?''}.
+Research Question 1 asks: \textit{“What are the best performing schemes to quantify phonetic similarity?”}.
 This paper has discussed several metrics used to quantify phonetic similarity (See Section \ref{sec:metrics}).
@@
 The only exception to this is the presence of Phonetic Vectors that were chosen due to their unique qualities.
-This project has succeeded in presenting a comparison of ways to compare similarity metrics.
-A more in-depth comparison of all possible metrics is a substantial task and would require a project with this sole dedication.
+Performance of these metrics were then quantified in a direct study that selected the top three from a set of five (See Section \ref{exp:metric}).
+These newly selected metrics were then assessed in an attack context with their performance being indirectly quantified (See Section \ref{sec:exp2_design}).
 
-\section{Research Question \ref{goal:bestMetrics}}
-Research Question \ref{goal:bestMetrics} asks: \textit{``Out of a chosen set of metrics, which are the most effective?''}. 
-The paper has presented the performance of a suite of algorithms that are mostly present in alternative literature.
-Performance of these metrics was quantified in a direct study that selected the top three from a set of five.
-These newly selected metrics were then assessed in an attack context with their performance being indirectly quantified.
-From the historical set of metrics, Levenshtein was the best performer with participants rating its matches as substantially better.
-Levenshtein was also the best performer in the attack context with it having the best average attack success rate.
-This performance, therefore, seems to corroborate work showing that words with similar spelling tend to share phonetic similarity \cite{hettiarachchi2012sparcl}.
-This area, however, requires further work to provide more conclusive results.
+The top three metrics (in descending order) were: Levenshtein, NYSIIS and Metaphone.
+We found that Levenshtein was the most aligned with how people rate phonetically similarity.
+Levenshtein had a considerable proportion of 4 and 5 ratings (64\%) compared to the alternatives.
+Levenshtein was also the best performer in the attack context with it having the best attack success rate in all attacks.
+This corroborates work showing that words with similar spelling tend to share phonetic similarity \cite{hettiarachchi2012sparcl}.
+Alongside this, we found Soundex was the least aligned with the human model of similarity with an average rating of just 2 out of 5.
+This corroborates findings that highlighted major issues with the accuracy of Soundex’s phonetic representation (See Section \ref{sec:soundex}).
+
+We believe the outcome of the first experiment were inflated by the way the results were presented (as discussed in Section \ref{sec:exp1_considerations}).
+However, as the performance of the metrics in the second experiment emulated the first with Levenshtein being the best performer alongside Metaphone being the worst, shows that the results of the first study maintains a desirable level of accuracy.
+Improvements can be made with the proposed design discussed in Section \ref{sec:exp1_considerations}, but, we believe the first experiment has achieved its goal of providing a low cost way to reduce the number of selected metrics for the subsequent study.
 
@@
 This capability is in comparison to the maximum of 40 keys Scallion can compare.
-
-\section{Research Question \ref{goal:hardwareRequired}}
-Research Question \ref{goal:hardwareRequired} states: \textit{``What kind of hardware is required to compute a matching key?''}.
-Through the computation of actual keys presented in Section \ref{sec:key_gen} and the theoretical calculation into key computation in some cases, it has been shown that a single mid-range GPU\footnote{AMD RX-480} can be used to compute actual keys.
+We believe this is due to the implementation of the bloom filter.
+Its unique characteristics of $O(k)$ complexity regardless of number of elements in the structure results in a huge number of concurrent checks to occur.
 
@@
 Furthermore, comparison of these results to similar literature shows a considerable increase in success rates for the attack present in this paper.
-All alternative literature used a small dictionary of around 1024 words.
-Therefore, this is highly suggestive that the issue lies with the design of Trustwords.
+We believe this is due to the consideration of `similarity' when forming attacks.
+This was an aspect missing from the literature.
+The effect of `similarity' is further enhanced due to the  weaknesses present in Trustwords such as homophones, dual mappings and the wordlist size.
 Therefore, we believe that 4 Trustwords as a minimum has not provided a basic level of security towards users.

### 2019-08-28 Writeup/Thesis/chapters/experiments.tex
Changes; - Implemted changes from Sia - Added abstract and acknowledgements

@@
 \label{sec:SvG}
+
+\todo{Talk about the exception}
 
@@
 Any number of keys over 40 resulted in a crash for Scallion.
+This crash is solely due to an  implementation issue.
+
+\todo{Fix implementation issue}
+
 GreenOnion's speed is almost perfectly consistent.
@@
 Flechais} and \textbf{A.
-Roscoe, \textit{et al.}}\cite{kainda2009usability} (previously discussed in Chapter \ref{cha:LiteratureReview}) is the most comparable to this experiment.
+Roscoe}\cite{kainda2009usability} (previously discussed in Chapter \ref{cha:LiteratureReview}) is the most comparable to this experiment.
 They were the only study to use exactly 4 words but differed on the size of the dictionary (1024 words) and how a near-match were calculated.

### 2019-08-29 Writeup/Thesis/chapters/evaluation.tex
Changes; - All fixes implemented from supervisor feedback

@@
 Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for with GreenOnion being able to handle in excess of 1.5 million keys.
-This capability is in comparison to the maximum of 40 keys Scallion can compare.
+This capability is in comparison to the maximum of 2513 keys Scallion can compare.
 We believe this is due to the implementation of the bloom filter.
-Its unique characteristics of $O(k)$ complexity regardless of number of elements in the structure results in a huge number of concurrent checks to occur.
+Its unique characteristics of $O(k)$ complexity regardless of number of elements in the structure allows a huge number of concurrent checks to occur.
 

### 2019-08-29 Writeup/Thesis/chapters/experiments.tex
Changes; - All fixes implemented from supervisor feedback

@@
 
-\todo{Talk about the exception}
+This section compares Scallion and the newly designed GreenOnion ability to search for a large number of potential keys.
 
-\begin{wraptable}[11]{r}{6cm}
+Figure \ref{tab:scallion_speed} shows the speed decline as the number of concurrently checked potential keys increases.
+Alongside the results for base version of Scallion is the speed for \textit{Scallion Improved}.
+This is the same Scallion code but with a fix that reduces the severity of the speed decline.
+
+\begin{table}[h!]
     \centering
@@
         OS & Windows 10 (May 2019) \\
-        Version & Scallion-2.0\footnote{\url{https://github.com/lachesis/scallion/raw/binaries/scallion-v2.0.zip}} \\
+        Version & Scallion 2.1 (Commit: \verb|42b4cb5|\footnote{\url{https://github.com/lachesis/scallion/tree/42b4cb555dbf8554b212a2bc3e0ba3d652434ecf}}) \\
         \hline
@@
         \hline
-        OS & Linux Mint (Version: TODO) \\ 
+        OS  & Linux Mint 19.1 \\
+            & Kernel: 4.15.0 \\ 
         \hline
@@
         \hline
-        GPU & GTX 750 Ti  \\
+        GPU & Nvidia GTX 750 Ti  \\
         CPU & AMD FX-6300 \\
@@
     \caption{Testing environment}
-\end{wraptable}
+\end{table}
 
-This section compares Scallion and the newly designed GreenOnion ability to search for a large number of potential keys.
+Figure \ref{fig:scallionCode} contains a snippet of code with the error.
+The calls to \verb|parms.ToolConfig.PredictRuntime()| become increasingly expensive as the number of concurrently checked keys increases.
+Removing this line from the \verb|Console.Write| statement results in a sizeable improvement in speeds as can be seen in Figure \ref{tab:scallion_speed}.
+This was necessary to include as we believe the improved versions show a better comparison between the design of the two tools.
 
-Figure \ref{tab:scallion_speed} shows the speed decline as the number of potential keys checked in one go increases for Scallion.
-Any number of keys over 40 resulted in a crash for Scallion.
-This crash is solely due to an  implementation issue.
-
-\todo{Fix implementation issue}
+\begin{figure}[h!]
+    \input{code/scallion_bug.tex}
+    \caption{Scallion's main print statement}
+    \label{fig:scallionCode}
+\end{figure}
 
 GreenOnion's speed is almost perfectly consistent.
-It is slower up until  around 5 keys.
-This consistency is due to the overhead of the bloom filter; however, as the number of keys increase, the bloom filter's benefits become apparent.
-In this test, the bloom filter size was kept consistent at exactly 5,000 elements.
+It is slower up until  around 800 keys.
+This initial lower speed is due to the overhead of the bloom filter; however, as the number of keys increase, the bloom filter's benefits become apparent.
+In this test, the bloom filter size was kept consistent at exactly 10,000 elements.
 
-GreenOnion has been tested to handle more than 1.5 million keys with a slight reduction in performance. This improvement over Scallion is, therefore, substantial.
+Scallion was unable to handle anything over 2513 concurrent keys.
+This was due to the search strings being passed via a command line argument as a regex string.
+This number of keys hit the character limit of a Powershell command.
+GreenOnion, however, has been tested to handle more than 1.5 million keys with a slight reduction in performance.
+This improvement over Scallion is, therefore, substantial.
 
-GreenOnion's code has been made publicly available on GitHub \footnotemark{TODO}.
+GreenOnion's code has been made publicly available and can be viewed on GitHub\footnote{\url{https://github.com/AidanFray/GreenOnion}}.
 
@@
 
-\todo{Include comparison to Hash-Friendly Schemes paper as they used Transposition to create 'Hard Matches' i.e. blub --> bulb}
-
 \section{Average number of near-collision keys for each metric}
@@
         \centering
-        \begin{tabular}{|lllll|}
+        \begin{tabular}{|llll|}
             \hline
-            \textbf{Metric} & & \textbf{Mean matches} & \textbf{$\sigma$} & \textbf{Compute Time} \\
+            \textbf{Metric} & & \textbf{Mean matches} & \textbf{Compute Time} \\
             \hline
-            NYSIIS &&&& \\
+            NYSIIS &&& \\
             \hline
-            & 0 static & 1963.07 & 24769.48 & ~~27.19 days \\
-            & 1 static & 448.37 & 4316.57 & 119.14 days \\
-            & 2 static & 98.07 & 550.44 & ~~~~1.49 years \\
+            & 0 static & 1963.07 &  ~~27.19 days \\
+            & 1 static & 448.37 &  119.14 days \\
+            & 2 static & 98.07 &  ~~~~1.49 years \\
+            \hline\hline
+
+            Metaphone &&& \\
             \hline
+            & 0 static & 27138.78 &  ~~~~1.97 days \\
+            & 1 static & 2822.74 &  ~~18.91 days \\
+            & 2 static & 339.84 &  157.45 days \\
+            \hline\hline
 
-            Metaphone &&&& \\
+            Levenshtein &&& \\
             \hline
-            & 0 static & 27138.78 & 529229.35 & ~~~~1.97 days \\
-            & 1 static & 2822.74 & 23932.39 & ~~18.91 days \\
-            & 2 static & 339.84 & 1730.97 & 157.45 days \\
-            \hline
-
-            Levenshtein &&&& \\
-            \hline
-            & 0 static & 293.92 & 2158.24 & 182.17 days \\
-            & 1 static & 102.75 & 719.28 & ~~~~1.43 years \\
-            & 2 static & 35.53 & 120.71 & ~~~~4.18 years \\
-            \hline
+            & 0 static & 293.92 &  182.17 days \\
+            & 1 static & 102.75 &  ~~~~1.43 years \\
+            & 2 static & 35.53 &   ~~~~4.18 years \\
+            \hline\hline
 
@@
     }
-    \caption{Each metric's average number of near-collision keys}
+    \caption{Each metric's average number of near-collision keys and average compute times}
     \label{tab:average_perm}
@@
 These keys were then randomly sampled and used to create the combined key,as discussed in Section \ref{sec:pep}.
-100,000 random key pairs were created and used as the sample.
+100,000 random key pairs were created and used as the sample\cite{davidnorman_2019}.
 Any vulnerable keys in this set were recorded and used in the experiment.
-
-\todo{Reference David's work}
 
@@
             & NYSIIS & 10.441\% \\
-            \hline
+            \hline\hline
             1 static (1525) && \\ 
@@
             & NYSIIS & ~~4.341\% \\
-            \hline
+            \hline\hline
             0 static (15250) && \\ 
@@
             & NYSIIS & ~~1.824\% \\
-            \hline
+            \hline\hline
         \end{tabular}
@@
 Producing near-matching keys from key pairs with a very small number of potential matches adds very little to this demonstration.
+This, however, will result in best-case scenario key computation times.
 

### 2019-08-29 Writeup/Thesis/chapters/lit_review.tex
Changes; - Implemted changes from Sia - Added abstract and acknowledgements
Changes; - All fixes implemented from supervisor feedback

@@
     Provides the user with the base knowledge required to understand the context and purpose of the following literature review.
-
-    \item \textbf{Definition of terms}\\
-    Specific definitions relevant to the literature review are initially defined.
 
@@
 
+\newpage
+
 \subsection{Encoding schemes}
@@
 \end{figure}
-
-\newpage
 
@@
 
-\section{Definition of terms}
-Throughout the paper, various terms are used to define elements of the authentication ceremony relevant to fingerprints verification.
-Explicit descriptions are, therefore, stated in this section.
-These are used to remove ambiguity and underlying associations readers may have for the words chosen.
-\\\\
-\textbf{\textit{Method of comparison}} - is the way a user assesses the encoding scheme.
-The most common example and the one used as default is ``Compare-and-Confirm'' (CaC).
-CaC, as the name suggests, is the \textit{comparison} of two fingerprints on different devices or mediums that are then \textit{confirmed}.
-The following sections explain alternative methods of comparisons.
-
-\todo{Phase this section out - make sure to remove from the introduction layout of the section}
-
 \section{Literature Review}
@@
 \subsubsection*{Methods of comparison performance}
-Aside 
-from ``Compare-and-Confirm'' (CaC), there is ``Compare-and-Select'' (CaS) and ``Compare-and-Enter'' (CaE).
+
+Method of comparison is the way a user assesses the encoding scheme.
+The most common example and the one used as default is ``Compare-and-Confirm'' (CaC).
+CaC, as the name suggests, is the \textit{comparison} of two fingerprints on different devices or mediums that are then \textit{confirmed}.
+
+Aside from ``Compare-and-Confirm'' (CaC), there is ``Compare-and-Select'' (CaS) and ``Compare-and-Enter'' (CaE).
 CaS is the method where one device displays the fingerprint, and the other user is provided with several options.

### 2019-08-29 Writeup/Thesis/graphs/speed.tex
Changes; - All fixes implemented from supervisor feedback

\begin{tikzpicture}[every axis plot/.append style={thick}]
    \begin{axis}[
        width=\linewidth,
        height=10cm,
        grid=major,
        xmin=1, xmax=2513,
        % ymin=0, ymax=100,
        x tick label style={rotate=45},
        x label style={at={(axis description cs:0.5,-0.1)},anchor=north},
        xlabel=Number of Keys,
        ylabel=Hashing speed (MH/s)
        ]
        \addplot[color=blue] table [x index=0, y index=1, mark=none, search path=data, col sep=comma]{scallion.csv};
        \addlegendentry{Scallion}

        \addplot[color=red] table [x index=0, y index=1, mark=none, search path=data, col sep=comma]{fscallion.csv};
        \addlegendentry{Scallion (Improved)}

        \addplot[color=green] table [x index=0, y index=1, mark=none, search path=data, col sep=comma]{green.csv};
        \addlegendentry{GreenOnion}	
     \end{axis}
\end{tikzpicture}

### 2019-08-29 Writeup/Thesis/chapters/lit_review.tex
Changes; - Fixed formatting issues

@@
 \label{sec:pep}
-A very recent implementation of a word list can be found in Pretty Easy Privacy (\pep) implementation of TrustWords\footnote{https://tools.ietf.org/html/draft-birk-pep-trustwords-03}.
+A very recent implementation of a word list can be found in Pretty Easy Privacy (\pep) implementation of TrustWords\footnote{\url{https://tools.ietf.org/html/draft-birk-pep-trustwords-03}}.
 \pep is a data encryption system that utilises PGP encryption to provide E2EE on all common channels of communication such as email or SMS.
@@
 
-\begin{wrapfigure}{l}{5cm}
+\begin{wrapfigure}[11]{l}{5cm}
     \centering
@@
     \end{BVerbatim}
-    \caption{Re-mapping position in Trustword dictionary}
+    \caption{Re-mapping position}
     \label{fig:remap}
@@
 Figure \ref{fig:remap} shows the position in the dictionary where this occurs.
+
+\newpage
 
@@
 \begin{figure}[!h]
-    \begin{center}
+    \centering
     \verb|TARGET: d6:b7:df:31:aa:55:d2:56:9b:32:71:61:24:08:44:87|
     \verb|MATCH:  d6:b7:8f:a6:fa:21:0c:0d:7d:0a:fb:9d:30:90:4a:87|
-    \end{center}
     \caption{Best match obtained after a few minutes of hashing}

### 2019-08-30 Writeup/Thesis/chapters/design.tex
Changes; - All fixes implemented from supervisor feedback
Changes; - Re-drafted after reading over a printed version

@@
 The attack on Trustwords involves generating "near-collision" keys. 
-This attempts to provide the base to answer Research Questions \ref{goal:numberOfTrustwords} and \ref{goal:complexity}.
+This attempts to provide the base to answer Research Questions \ref{goal:complexity} and \ref{goal:numberOfTrustwords}.
 
@@
 
-When attacking a similarity metric is used to compute a list of possibilities for each position in the target fingerprint.
+When attacking, a similarity metric is used to compute a list of possibilities for each position in the target fingerprint.
 
@@
 \subsection{Metaphone}
-Metaphone as discussed in Section \ref{sec:metaphone} is anther famous phonetic algorithm.
+Metaphone as discussed in Section \ref{sec:metaphone} is another famous phonetic algorithm.
 Metaphone is arguably on the same level of ubiquity as that of Soundex with it finding itself implemented in languages such as PHP\cite{php}.
@@
 Further work would involve the implementation of newer versions of Metaphone. Double Metaphone (2000) and
-Metaphone 3 (2009) that claim to improve over the original version due to further research performed by Philips.
+Metaphone 3 (2009) that claim to improve over the original version.
 
@@
 
-The design for the experiment involves assessing the quality of the metrics matches by having participants rate them on a scale of 1 to 5.
+The design for the experiment involves assessing the quality of the metrics matches by having participants rate them on a scale of 1 (Very different sound) to 5 (Very similar sound).
 
@@
 This is discussed in more detail in later chapters.
-
-\todo{Link the less than 100,000 point to experiment data}
 
@@
 The first consideration is the way the words are compared.
-Due to the channel of authentication being phone-based, the comparison of words is a mixture of auditory and textual.
+Due to the assumed context of authentication being phone-based, the comparison of words is a mixture of auditory and visual.
+The user will hear their authentication partner read their set of words (Auditory) and compare to their set of words (Visual).
 This mixture is because a user needs to match a words sound to the one displayed on their device.
@@
 The blue button is clicked to simulate the authentication ceremony over the phone.
-A text-to-speech system then read a set of words and the user should accept if they match and decline if they don't.
+A text-to-speech system then reads a set of words and the user should accept if they match and decline if they don't.
 
@@
 This occurrence is a much higher value than in a real-world setting, but is a balance between resources and realistic design.
-If the chosen attack rate is too low, many more trials are required to collate a useful number of attack instances, thus, requiring more resources but with a much more realistic design.
+If the chosen attack rate is too low, many more trials are required to collate a useful number of attack instances, thus, requiring more resources, but with more realism.
 If, however, the attack rate is too high, less total rounds are required to obtain the target number of attack trails, however, the user will lose their complacency as an attack will be expected.
@@
 If there are rounds without button clicks, this is a sign of non-attentiveness.
-The design choice was made to keep this as a result filter, as preventing non-clicks would be a trivial task.
+The design choice was made to allow non-clicks as an attention check.
 This design provides a way to detect and discard click-throughs\footnote{Workers that aim to complete the task as fast as possible, with no regard for the quality of responses}.

### 2019-08-30 Writeup/Thesis/chapters/evaluation.tex
Changes; - Re-drafted after reading over a printed version

@@
 Most metrics were chosen due to their high utilization and occurrence in literature.
-The only exception to this is the presence of Phonetic Vectors that were chosen due to their unique qualities.
+The only exception to this is the presence of Phonetic Vectors.
 Performance of these metrics were then quantified in a direct study that selected the top three from a set of five (See Section \ref{exp:metric}).
@@
 \section{Research Question \ref{goal:complexity}}
-Research Question \ref{goal:complexity}: \textit{``What are the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys as shown in Section \ref{sec:key_gen} where actual keys were generated.
+Research Question \ref{goal:complexity}: \textit{``What are the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys as shown in Section \ref{sec:key_gen}.
 Furthermore, the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}.
-To achieve this, the tool GreenOnion was developed where inspiration was gathered from a currently available tool known as Scallion.
+To achieve this, the tool GreenOnion was developed.
+Inspiration for GreenOnion was gathered from a currently available tool known as Scallion.
 Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for with GreenOnion being able to handle in excess of 1.5 million keys.
@@
 This was an aspect missing from the literature.
-The effect of `similarity' is further enhanced due to the  weaknesses present in Trustwords such as homophones, dual mappings and the wordlist size.
-Therefore, we believe that 4 Trustwords as a minimum has not provided a basic level of security towards users.
+We also believe the effect of considering similarity is further enhanced due to the  weaknesses present in Trustwords such as homophones, dual mappings and the wordlist size.
+Therefore, we believe that four Trustwords as a minimum has not provided a basic level of security towards users.
 
@@
 For example, present in the dictionary are the words \verb|THERE| and \verb|THEIR|, these could be massively improved upon and could result in a better quality word list.
-Moreover, utilizing the quantification of dissimilarity could be used to create a dictionary of maximized phonetic distance that could then be assessed in a similar way to detect the feasibility of the attack with the alterations and its success rate against users.
+Moreover, utilizing the quantification of dissimilarity could be used to create a dictionary of maximized phonetic distance.
+This phonetically distinct wordlist could then be assessed in a similar with its success rate quantified against users.
 

### 2019-08-30 Writeup/Thesis/chapters/experiments.tex
Changes; - Re-drafted after reading over a printed version

@@
 Table \ref{tab:exp1_demo} contains the demographical breakdown of the reduced set of participants.
-The average ages of the participants were 37.3 years ($\sigma = 11.67$)with a split of 44.4\% of Males to 55.6\% of Females.
+The average ages of the participants were 37.3 years ($\sigma = 11.67$) with a split of 44.4\% of Males to 55.6\% of Females.
 As can be seen, over 60\% of participants can be considered highly educated (Bachelor’s and up).
@@
 Levenshtein has a much more significant proportion of 4 and 5 ratings than the alternatives.
-This performance may, however, be due to the visual way the comparisons are being performed.
+This performance may, however, be due to the visual way the comparisons are performed.
 (Discussed in detail in Section \ref{sec:exp1_considerations}).
@@
 
-The reduced set of 369 participants had an average age of 36.63 ($\sigma = 11.35$) and consisted of an almost equal split of Male (50.41\%) to Female (49.59\%).
+The reduced set of 369 participants had an average age of 36.63 ($\sigma = 11.35$) and consisted of an almost equal split of Male (50.4\%) to Female (49.6\%).
 Around 62\% of participants had completed a single stage of university (Bachelor and up).
@@
 It can be seen that the best metric out of the set was Levenshtein with an overall success of 19.80\%.
-The best performer, when regarding attack strength, as expected, is the 2 static words.
-Levenshtein's 2 static attack performed the best overall with a success rate of 32.05\%.
+The best performer, when regarding attack strength, as expected, is the \XOOX~attack.
+Levenshtein's \XOOX~attack performed the best overall with a success rate of 32.05\%.
 The worst performer was Metaphone, with an average of 16.88\% over its three levels of attacks.
@@
             \hline
-            & 0 static   & 34  & 358  & ~~9.5\% \\
-            & 1 static   & 59  & 353  & 16.7\% \\
-            & 2 static   & 125  & 390  & 32.1\% \\
+            & \OOOO   & 34  & 358  & ~~9.5\% \\
+            & \XOOO   & 59  & 353  & 16.7\% \\
+            & \XOOX   & 125  & 390  & 32.1\% \\
             \hline\hline
@@
             \hline
-            & 0 static   & 38 & 345 & 11.0\% \\
-            & 1 static   & 57 & 375 & 15.2\% \\
-            & 2 static   & 86 & 352 & 24.4\% \\
+            & \OOOO   & 38 & 345 & 11.0\% \\
+            & \XOOO   & 57 & 375 & 15.2\% \\
+            & \XOOX   & 86 & 352 & 24.4\% \\
             \hline\hline
@@
             \hline
-            & 0 static   & 36 & 385 & ~~9.3\% \\
-            & 1 static   & 72 & 375 & 19.2\% \\
-            & 2 static   & 101 & 354 & 28.5\% \\
+            & \OOOO   & 36 & 385 & ~~9.3\% \\
+            & \XOOO   & 72 & 375 & 19.2\% \\
+            & \XOOX   & 101 & 354 & 28.5\% \\
             \hline\hline
@@
 As previously mentioned, the set of recruited participants are more highly educated than the general population.
-This.
-combined with the lower average age, contributes to an inevitable bias being introduced into the data.
+This combined with the lower average age, contributes to an inevitable bias being introduced into the data.
 An assumption can be made that higher education leads to more skilful interaction with computer-based systems, this, therefore, with the previous assumption in mind means the results of this experiment can be considered a `best case' scenario.
@@
 
-Other relevant work by \textbf{Dechand \textit{el al.}}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words.
+Other relevant work by \textbf{S.
+Dechand \textit{el al.}}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words.
 Their experiment is less similar as 14 words per attack were assessed with each participant, where the comparison was performed visually.
@@
             \hline
-            & 0 static & 1963.07 &  ~~27.19 days \\
-            & 1 static & 448.37 &  119.14 days \\
-            & 2 static & 98.07 &  ~~~~1.49 years \\
+            & \OOOO & 1963.07 &  ~~27.19 days \\
+            & \XOOO & 448.37 &  119.14 days \\
+            & \XOOX & 98.07 &  ~~~~1.49 years \\
             \hline\hline
@@
             \hline
-            & 0 static & 27138.78 &  ~~~~1.97 days \\
-            & 1 static & 2822.74 &  ~~18.91 days \\
-            & 2 static & 339.84 &  157.45 days \\
+            & \OOOO & 27138.78 &  ~~~~1.97 days \\
+            & \XOOO & 2822.74 &  ~~18.91 days \\
+            & \XOOX & 339.84 &  157.45 days \\
             \hline\hline
@@
             \hline
-            & 0 static & 293.92 &  182.17 days \\
-            & 1 static & 102.75 &  ~~~~1.43 years \\
-            & 2 static & 35.53 &   ~~~~4.18 years \\
+            & \OOOO & 293.92 &  182.17 days \\
+            & \XOOO & 102.75 &  ~~~~1.43 years \\
+            & \XOOX & 35.53 &   ~~~~4.18 years \\
             \hline\hline
@@
             \hline 
-            2 static (152) && \\ 
+            \XOOX~(152) && \\ 
             & Levenshtein & ~~4.295\% \\
@@
             \hline\hline
-            1 static (1525) && \\ 
+            \XOOO~(1525) && \\ 
             & Levenshtein & ~~0.827\% \\
@@
             \hline\hline
-            0 static (15250) && \\ 
+            \OOOO~(15250) && \\ 
             & Levenshtein & ~~0.157\% \\
@@
 The takeaways from this table are the extremely low values for Levenshtein in the higher attacks.
-This phenomenon is due to the low number of overall matches produced by Levenshtein, meaning Levenshtein is effective in the vast majority of cases.
+This phenomenon is due to the low number of overall matches produced by Levenshtein, meaning the metric is not effective in the vast majority of cases.
 However, the standout metric is Metaphone with a sizeable proportion of vulnerable keys; it was the worst performer when assessed against real users but only by as little as 2\%.
@@
 \label{sec:key_gen}
-In order to demonstrate that the generation of the near-collision keys is not only theoretical, the actual generation of keys was performed using GreenOnion.
+In order to demonstrate that the generation of the near-collision keys is not only theoretical, the actual generation was performed using GreenOnion.
 A random metric was selected from the three carried forward from the first experiment.
 Alongside this, a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key).
-Then for each attack level (0 static, 1 static, 2 static), a key was computed.
+Then for each attack level (\OOOO, \XOOO, \XOOX), a key was computed.
 NYSIIS was chosen as the selected metric.
@@
     }
-    \caption{NYSIIS - 0 static}
+    \caption{NYSIIS - OOOO}
     \label{tab:nysiis0}
@@
     }
-    \caption{NYSIIS - 1 static}
+    \caption{NYSIIS - XOOO}
     \label{tab:nysiis1}
@@
     }
-    \caption{NYSIIS - 2 static}
+    \caption{NYSIIS - XOOX}
     \label{tab:nysiis2}
@@
 Even with the least restricted attack type presented in Table \ref{tab:nysiis0}, the computation of half a day can provide almost a 10\% success rate when attacking users.
-This results in any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of fooling an actual user.
+This results in any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of deceiving an actual user.

### 2019-08-30 Writeup/Thesis/chapters/implementation.tex
Changes; - Re-drafted after reading over a printed version

@@
 Figure \ref{fig:increment} contains the code used to increment the exponent.
-Due to the exponent being split across two words alongside the limited functionality of OpenCL, bitwise operations to increment the exponent.
+Due to the exponent being split across two words alongside the limited functionality of OpenCL, bitwise operations are used to increment the exponent.
 The code utilises the fact that anything XORed with itself becomes zero alongside the fact that XORing a value $a$ with zero provides the result equal to $a$.
@@
 The levenshtein difference is computed and compared to the tolerance discussed in Section \ref{sec:matches}.
-If this function returns true the match is added to the list of matches.
+If this function returns true the match is added to the list.
 
@@
 In order to collate data for results later in the process, the state had to be retained.
-One potential solution would be to format the data and save it as a .csv file.
+One potential solution would be to format the data and save it as a \verb|.csv| file.
 However, this is a static way of data persistence and would require alteration every time the data schema was modified.

### 2019-08-30 Writeup/Thesis/chapters/introduction.tex
Changes; - Re-drafted after reading over a printed version

@@
 
-One proposed user-friendly scheme is Pretty Easy Privacy's (p$\equiv$p) "Trustwords".
-Trustwords is an implementation of word fingerprint mapping with a emphasis on usability.
-This increase in usability is achieved by the user comparing a reduced number of words.
-This usability boost, however, comes at a cost of a much larger word list.
+One proposed scheme claiming increased usability is Pretty Easy Privacy's (p$\equiv$p) "Trustwords".
+Trustwords is an implementation of word fingerprint mapping.
+This claimed increase in usability is achieved by the user comparing a reduced number of words compared to alternatives.
+This potential usability boost, however, comes at a cost of a much larger word list.
 

### 2019-08-30 Writeup/Thesis/chapters/lit_review.tex
Changes; - Re-drafted after reading over a printed version

@@
 Therefore the fingerprint of the two respective public keys are different, and, thus can be used for identification.
-There are, however, issues in how a user should link a key's fingerprint to an identity.
-One example way to achieve this is by meeting in-person to exchange fingerprints.
-This paper will, however, assume that users have been through this process.
 
@@
 \label{sec:encodingSchemes}
+
+\subsubsection*{Text-based schemes}
 Encoding schemes are the physical method of encoding used to represent the fingerprint.
 The most common way to represent the fingerprint is alphanumerically with either \textbf{Hexadecimal} (a-f/0-9) or \textbf{Base32} (2-7/A-Z).
-These encoding schemes are the most popular due to their intuitive simplicity and lack of unique hardware requirements such as colour screens.
+These encoding schemes are the most popular due to their intuitive simplicity and lack of hardware requirements.
 
@@
 
-Graphical schemes can also be used to represent a fingerprint.
+\subsubsection*{Graphical Schemes}
+Graphical schemes are a potential alternative to text based schemes.
+They often attempt to visualise small changes in the fingerprint to assist in altering the user to minute changes.
+This should, therefore, be able to provide increased usability and security.
+This section will explain the schemes relevant in this paper.
 
@@
 OpenSSH visual host key is an ASCII based graphical scheme used in MiTM detection when connecting to SSH servers.
-The image is generated by movement of the marker across a grid where every 2-bits of the generated MD5 has defines the diagonal direction of movement.
+The image is generated by movement of the marker across a grid.
+Every 2-bits of the generated MD5 hash defines the diagonal direction of movement.
 For example, if the first 2-bits are \verb|11| the marker will move South East.
@@
 \label{sec:soundex}
-One of the earliest examples of a phonetic algorithm is known as Soundex. It was initially designed for indexing names by phonetics alongside spelling mistakes due to transpositions in letters.
+One of the earliest examples of a phonetic algorithm is known as Soundex. It was initially designed for phonetically indexing names alongside detection of transposed letters in spelling mistakes.
 
 Soundex produces a four-digit code for each word assessed.
-The first letter of the word is retained alongside the removal of all of a, e, i, o, u, y, h and w.
+The first letter of the word is retained alongside the removal of all of \verb|a|, \verb|e|, \verb|i|, \verb|o|, \verb|u|, \verb|y|, \verb|h| and \verb|w|.
 The remaining letters are then mapped to numbers.
@@
 \begin{table}[h!]
+    \centering
+    \resizebox{.8\textwidth}{!}{%
+
         \makebox[\textwidth][c]{
@@
         }%
+    }
     \caption{Overall accuracy of correct comparison for the encoding schemes assessed}
@@
 \begin{table}[h!]
+    \centering
+    \resizebox{.8\textwidth}{!}{%
         \makebox[\textwidth][c]{
@@
         }%
+    }
     \caption{Paper attribute comparison}

### 2019-08-30 Writeup/Thesis/code/GoogleAppScript.tex
Changes; - Updated a global code style for the paper - Fixed some more supervisor issues - Small changes
Changes; - Re-drafted after reading over a printed version

@@
 \begin{adjustbox}{width=\textwidth,keepaspectratio}
-  \begin{JavascriptCode}
+  \begin{Code}[JavascriptStyle]
 vvar ALGOS = ["Soundex", "Metaphone", ...];
 var ALGO_SIZES = [763777, 412916, ...];
+
+var QUESTION_PER_ALGO = 5;
 
@@
 
-  // Updates the new values
   var algo_index = 0;
@@
 }
-  \end{JavascriptCode}
+  \end{Code}
 \end{adjustbox}

### 2019-08-30 Writeup/Thesis/chapters/design.tex
Changes; - More wording fixes

@@
 \label{sec:greenDesign}
-In order to answer Research Questions \ref{goal:complexity} fully, it is necessary to implement an actual tool to generate actual keys.
+In order to answer Research Questions \ref{goal:complexity} fully, it is necessary to implement a tool to generate working keys.
 
@@
 
-The tool should take two keys as parameters (Uncontrolled/Controlled) and a chosen similarity metric and produce a list of target keys fingerprints.
+The tool should take two keys as parameters (Uncontrolled/Controlled) and a chosen similarity metric and produce a list of target key fingerprints.
 This list is then used as a search criterion when searching for keys.
@@
 \section{Experiment Design}
-To answer some of the research questions, empirical evidence is required and, thus, experiments are required. In this section, the designs and considerations of the chosen experiments are discussed.
+To answer some of the research questions, empirical evidence is required. In this section, the designs and considerations of the chosen experiments are discussed.
 
@@
 \label{exp:metric}
-This section answers Research Question \ref{goal:phoneticSimilarity}.
+This section aims to assist answering Research Question \ref{goal:phoneticSimilarity}.
 To reduce the number of metrics to assess in the later rounds, the performance of similarity metrics required comparison.
@@
     \input{tables/design/match_size_leven.tex}
-    \caption{Levenshtein number of matches comparison}
+    \caption{Levenshtein's number of matches comparison}
     \label{tab:matchSize}
@@
 This design allows for a simple check for valid results.
-If their average is too high, their results are discarded.
+If their average rating for Random matches is too high, their results are discarded.
 
@@
 As both words are the same, the result should always be a full 5/5 rating, any results without a full rating are discarded.
-Figure \ref{fig:exactMatch} contains one example of the attention questions used to filter inaccurate results.
+Figure \ref{fig:exactMatch} contains one example of the attention question used to filter inaccurate results.
 
@@
 The user will hear their authentication partner read their set of words (Auditory) and compare to their set of words (Visual).
-This mixture is because a user needs to match a words sound to the one displayed on their device.
 This experiment asks users to compare the sound of two words that are visually displayed to them.
@@
 Furthermore, the first 5 trials of a new experiment is always benign.
-This inclusion is to ensure users are consistently lulled into of complacency.
+This inclusion is to ensure users are consistently lulled into complacency.
 
@@
 Therefore, again, quality control is an aspect that requires consideration.
-As with the previous study, initially screened native speakers are used, alongside the utilisation of the same process to recruit suitable workers.
-Two metrics are used to detect invalid results: audio-button-clicks and the overall-time.
+As with the previous study, initially screened native speakers are used.
+Alongside this, two metrics are used to detect invalid results: audio-button-clicks and the overall-time.
 
@@
 If users complete the experiment in an abnormally small amount of time, it can be used as another detection for invalid responses.
-A benchmark for the time is set by completing the experiment correctly but as fast as possible.
-Anything below this pace was discarded as anything higher will risk invalid and rushed results.
+A benchmark for the time is set by completing the experiment as fast as possible.
+Anything quicker was discarded as anything faster will risk invalid and rushed results.
 
@@
 As with the previous experiment, sampling from a  MTurk demographics results in a collection of participants that are not reflective of the general population.
-Due to the attack context of this experiment is can be assumed that the youth of the participants contributes to less successful attacks.
+Due to the attack context of this experiment it can be assumed that the youth of the participants contributes to less successful attacks.
 Therefore, the results generated by this experiment can be loosely assumed as a best-case scenario for the scheme.

### 2019-08-30 Writeup/Thesis/chapters/lit_review.tex
Changes; - More wording fixes

@@
 
-Due to the manual comparison of the fingerprint, length, and format is a core design consideration.
+Due to the manual comparison of the fingerprint, length and format are core design considerations.
 Prior research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}.
@@
 Encoding schemes are the physical method of encoding used to represent the fingerprint.
-The most common way to represent the fingerprint is alphanumerically with either \textbf{Hexadecimal} (a-f/0-9) or \textbf{Base32} (2-7/A-Z).
+The most common representation is alphanumerically with either \textbf{Hexadecimal} (0-9/A-F) or \textbf{Base32} (2-7/A-Z).
 These encoding schemes are the most popular due to their intuitive simplicity and lack of hardware requirements.
@@
 \subsubsection*{Graphical Schemes}
-Graphical schemes are a potential alternative to text based schemes.
-They often attempt to visualise small changes in the fingerprint to assist in altering the user to minute changes.
-This should, therefore, be able to provide increased usability and security.
-This section will explain the schemes relevant in this paper.
+Graphical schemes are a potential alternative to text-based schemes.
+They often attempt to visualise small changes in the fingerprint to assist in alerting the user to small changes.
+This schemes should, therefore, be able to provide increased usability and security.
+This section will explain the relevant schemes in this paper.
 
@@
 T-Flag is an attempt to improve on the previously mentioned Flag \cite{lin2010spate}.
-Improvements include twice the number of coloured blocks with a choice of eight colourblind-proof colours.
+Improvements include twice the number of coloured blocks with a choice of eight colours.
+The authors claim the choice of colours are ``colourblind proof''.
 
@@
 Hsiao \textit{et al.}}\cite{hsiao2009study}.
-Flag extended aims again, to improve on flag by reducing the number of blocks while adding 8 possible shapes.
+Flag-Ext aims, again, to improve on flag by reducing the number of blocks while adding 8 possible shapes.
 
@@
 \textbf{OpenSSH}.
-OpenSSH visual host key is an ASCII based graphical scheme used in MiTM detection when connecting to SSH servers.
-The image is generated by movement of the marker across a grid.
+OpenSSH Visual Host Key is an ASCII based graphical scheme used in MiTM detection when connecting to SSH servers.
+The image is generated by movement of the central marker across a grid.
 Every 2-bits of the generated MD5 hash defines the diagonal direction of movement.
@@
 
-\textbf{Unicorns}\footnote{https://unicornify.pictures/}.
+\textbf{Unicorns}\footnote{\url{https://unicornify.pictures/}}.
 Unicorns can be considered an example of an ``Avatar'' graphical scheme.
@@
 
-\textbf{Vash}\footnote{https://github.com/thevash/vash}.
+\textbf{Vash}\footnote{\url{https://github.com/thevash/vash}}.
 Vash is similar to that of unicorns where the hash determines certain characteristics of the image.
@@
 
-Research in this area has taken these various encoding schemes and compared their fallibility to impersonated attacks.
+Research in this area has taken these various encoding schemes and compared their falibility to impersonated attacks.
 The main elements of comparison have been the ``accuracy of attack detection" and ``time to compare." In this paper, these are considered the metrics of ``security'' and ``usability,'' respectively.
@@
 For example, the words "THEIR" and "THERE" is a match, whereas the words "DARK" and "PRINCIPLE" are not phonetically matching.
-This section provides a base explanation of important phonetic algorithms.
+This section provides a base explanation of important phonetic algorithms relevant in this project.
 
@@
 \label{sec:nysiis}
-The New York State Identification and Intelligence System (NYSIIS) phonetic code was created for use matching the phonetics of American names.
-The motivation for it's inception was mostly due to the presence of Hispanic names in the American based databases (this was an aspect Soundex was known to have low accuracy with).
+The New York State Identification and Intelligence System (NYSIIS) phonetic code was created for the phonetic matching of American names.
+The motivation for its inception was mostly due to the presence of Hispanic names in the American based databases (this was an aspect Soundex was known to have low accuracy with).
 
@@
 
-For example, the addition of vectors can be seen in Table \ref{tab:vectorAdd}. This works for any mathematical operation with examples like multiplication allowing the `tinting' words with a theme.
+For example, the addition of vectors can be seen in Table \ref{tab:vectorAdd}.
+This works for any mathematical operation with examples like multiplication allowing the `tinting' of words with a phonetical theme.
 
@@
 Other work also indirectly agreed with graphical encodings having significantly quicker comparison times compared to non-graphical schemes \cite{dechand2016empirical, kainda2009usability}.
-In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with literature only containing two papers.
+In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with only two papers available.
 There is also no overlap in the schemes assessed with each paper reviewing a unique set.
@@
 This paper was unique for several reasons.
-First was to consideration for ``remote-vs-proximity'' pairing where this is the first consideration of this aspect found in the literature.
+First was the consideration for ``remote-vs-proximity'' pairing where this is the first consideration of this aspect found in the literature.
 There is room for further research to compare encoding schemes in the context of ``remote-vs-proximity.'' Another unique aspect was the end-to-end encryption context of the study.
 
-The findings from the paper showed a high false-negative rate for all the schemes.
+The findings from the paper showed a high false-negative rate for all the schemes in a remote setting.
 This consideration is also missing from the literature.
@@
 
-Method of comparison is the way a user assesses the encoding scheme.
+Method of comparison is the way a user compares the encoding schemes output.
 The most common example and the one used as default is ``Compare-and-Confirm'' (CaC).
@@
 The justification was the schemes similarities to Base32  alongside "well-known deficiencies".
-This point was provided with no further justification or quantified.
+This point was provided with no further justification.
 Moreover, it is also inconsistent with available research, for example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}\cite{dechand2016empirical} it was shown numerical representations performed significantly better than that of Base32.
@@
 The final aspect for further work is the limited consideration into the feasibility of attacks on encoding schemes.
-All of the papers assessed simulated attacks and had minimal consideration for the execution of these attacks.
+All of the papers assessed simulated attacks and had minimal consideration for their execution.
 Therefore, further work could delve
@@
 This section discusses the current research on the creation and security of actual encoding schemes.
-The technical details of the operation of the schemes are outside the scope of this literature review.
-Therefore, minimal attention is allocated to these details.
+The technical and operation details are outside the scope of this literature review.
+Therefore, minimal attention is allocated to these areas.
 
@@
 Each publication has provided a new way  to represent a key fingerprint visually.
-Alongside the academic literature, there are informally presented methods of visual fingerprints such as Unicorns\footnote{https://unicornify.pictures/} and Robots\footnote{https://github.com/e1ven/Robohash}.
+Alongside the academic literature, there are informally presented methods of visual fingerprints such as Unicorns\footnote{\url{https://unicornify.pictures/}} and Robots\footnote{\url{https://github.com/e1ven/Robohash}}.
 This list is by no means exhaustive but is used to depict the amount of research and work invested into graphical hash representations.
@@
 The unique aspect of this work is the use of a Text-to-Speech system reading out syntactically correct English sentences.
-MadLibs\footnote{https://en.wikipedia.org/wiki/Mad\_Libs} was the base for these sentences.
-MadLibs is where static placeholders are replaced with a list potential words.\\
+MadLibs\footnote{\url{https://en.wikipedia.org/wiki/Mad\_Libs}} was the base for these sentences.
+MadLibs is where static placeholders are replaced with a member from a list of potential words.\\
 This work is an extension to work performed by \textbf{Juola} and \textbf{Zimmermann}\cite{juola1996whole} as they aimed to emulate the techniques used in PGPfone.
@@
 
-Tanet alAside from this research, there have been further informal implementations of fingerprint encodings.
-The first being by \textbf{Michael Rogers}\footnote{https://github.com/akwizgran/basic-english}.
+Aside from this research, there have been further informal implementations of fingerprint encodings.
+The first being by \textbf{Michael Rogers}\footnote{\url{https://github.com/akwizgran/basic-english}}.
 Rogers' implementation is a program designed to map fingerprints to pseudo-random poems.
@@
 Dechand \textit{et al.}}\cite{dechand2016empirical}.
-Ealier work by \textbf{N.
+Earlier work by \textbf{N.
 Haller} with the S/KEY\cite{haller1995s} shows the implementation of a system designed to represent a hash as a series of six short words.
@@
 Approximately 13633/65536 (20.8\%) of words are re-mapped in the dictionary, leaving 51903 unique words.
-The re-mapping looped with the dictionary remaining alphabetical.
+The re-mapping is performed on a alphabetical loop.
 Figure \ref{fig:remap} shows the position in the dictionary where this occurs.
@@
 This area of research studies ways to physically execute attacks on fingerprint encoding schemes.
-This topic differs from previously examined work due to papers discussing the performance and fallibility of encoding schemes simulated the attack without consideration for how the attack execution.
-Research in this area is scant, with lots of research attention on security of Man-in-the-Middle (MITM) attacks and not the encoding schemes themselves.
+This topic differs from previously examined work due to a central focus on the implementation details of an attack.
+Previous work discussed has only simulated the result of respective attacks.
+Research in this area is scant, with lots of research focusing on the security and prevention of Man-in-the-Middle (MITM) attacks.
 
@@
 Short-authentication-Strings (SAS) in the pairing of 
-Crypto-phones. To achieve this impersonating they propose 
+Crypto-phones. To achieve this impersonation they propose 
 two methods: ``Short voice re-ordering attack'' where an 
-arbitrary SAS string is recreated by re-ordering snipped 
+arbitrary SAS string is recreated by re-ordering voice snippets 
 obtained from eavesdropping a previous connection
@@
 The work would aim to focus on the various physical methods used and their feasibility.
-This is one area the previous literature has failed to cover and has only theoretically quantified attacker strength without consideration for the actual real-world cost of these attacks.
+This is one area the previous literature has failed to cover and has only theoretically quantified attacker strength without consideration for the actual real-world cost.
 
 \section{Overall Summary}
-In summary of the literature gaps areas discovered; encoding scheme performance requires further work in the performance of all graphical schemes to back up the results made by other work.
+In summary of the literature gaps discovered; encoding scheme performance requires further work focusing on all graphical schemes to corroborate results made by other work.
 Furthermore, there is a gap with the assessment of encoding schemes in the context of "remote-vs-proximity" first proposed by \textbf{M.
@@
 Hsiao \textit{et al.}}\cite{hsiao2009study} and could allow the creation of schemes that are better suited to specific languages.
-Alongside this, there is a research gap in the investigation of how mental impairments affect the performance.
-This aspect is useful due to the number of potential users being affected due to systems not being designed with them in mind.
+Alongside this, there is a research gap in the investigation of how mental impairments affect a schemes performance.
+This aspect is useful due to the number of potential users being affected.
 For example, 7\% of the population have been identified as having dyslexic tendencies\cite{peterson2012developmental}.
 This fact means that with a UK population of around 63,000,000\footnote{From the 2011 Census collated by the Office for National Statistics}  4,410,000 people could benefit from encoding schemes designed to work well with dyslexia.
-Dyslexia, however, is only one of many impairments that could affect a scheme's performance, thus further contributing to the substantial effect further work could have on this area.
+Dyslexia, however, is only one of many impairments that could affect a scheme's performance, thus, contributing to the substantial effect further work could have on this area.
 
-Other possible large areas for consideration is the lacks of direct consideration for attack strength when assessing the vulnerability of encoding schemes.
+Other possible large areas for consideration is the lack of direct consideration for attack strength when assessing the vulnerability of encoding schemes.
 Issues included the previously discussed wide range of attack strength ($2^{28}$ - $2^{242}$) alongside the lack of consideration at all from the majority of papers.

### 2019-08-30 Writeup/Thesis/chapters/research_question.tex
Changes; - Implemted changes from Sia - Added abstract and acknowledgements
Changes; - More wording fixes

@@
 By sampling the \pep documentation they have defined the use case of the Trustword handshake: \textit{``A handshake is done by comparing the Trustwords between two users through a separate communication channel (e.g.
-in person or by phone)''.}\footnote{https://www.pep.security/docs/general\_information.html\#handshake}.
-It can be assumed due to the increased globalization of the planet that the most common handshake occurrence is over the phone, and, therefore, not in person.
+in person or by phone)''.}\footnote{\url{https://www.pep.security/docs/general\_information.html\#handshake}}.
+It can be assumed due to the increased globalisation of the planet that the most common handshake occurrence is over the phone, and, therefore, not in person.
 This is the assumed context of the handshake.
@@
 \begin{enumerate}
-    \item What are the different ways phonetic similarity can be quantified?  \label{goal:phoneticSimilarity}
-
-    \item Out of a chosen set of metrics, which are the most effective? \label{goal:bestMetrics}
+    \item  What are the best performing schemes to quantify phonetic similarity?  \label{goal:phoneticSimilarity}
 
     \item What are the time and computation complexity required to generate a 'similar' keys for a targeted key pair? \label{goal:complexity}
-
-    \item What kind of hardware is required to compute a matching key? \label{goal:hardwareRequired}
 

### 2019-08-30 Writeup/Thesis/chapters/abstract.tex
Changes; - TTS run over the entire paper and corrections added

@@
 
-This work implements an attack on Trustwords and quantifies its effectiveness on more than 400 participants.
+This works main aim is to asses if Trustword's recommend minimum number of four words is sufficient.
+In order to achieve this goal, this work implements an attack on Trustwords and quantifies its effectiveness on more than 400 participants.
 A tool called GreenOnion was designed to assist in quantifying attack feasibility.
-GreenOnion improved substantially on a similar tool's ability to search for matches concurrently.
+GreenOnion improved substantially on a similar tool's ability to search for matches concurrently where it was able to search for over 1.5 million concurrent keys.
 Our findings show a substantial increase in attack success compared to related literature.
-We believe this increase is due to leveraging the design flaws in the Trustword scheme.
+We believe this increase is due to levering the design flaws in the Trustword scheme.
+Therefore, we believe a minimum of four Trustwords is insufficient to provide even a basic level of security.

### 2019-08-30 Writeup/Thesis/chapters/design.tex
Changes; - TTS run over the entire paper and corrections added

@@
 These attacks are ascending in complexity.
-The timeframe for computing a near-collision was decided as 7-days with attack strengths of 1 GPU-day, 10 GPU-days and 100 GPU-days on a mid-range GPU (AMD RX 480).
+The timeframe for computing a near-collision was decided as one week with attack strengths of 7 GPU-days \textit{(1 x GPU)}, 70 GPU-days \textit{(10 x GPUs)} and 700 GPU-days \textit{(100 x GPUs)} on a mid-range GPU (AMD RX 480).
 Due to the long lifetime of PGP keys, 7 days was chosen as a reasonable length of the attack.

### 2019-08-30 Writeup/Thesis/chapters/evaluation.tex
Changes; - TTS run over the entire paper and corrections added

@@
 \chapter{Conclusions}
-This chapter collates the findings of the paper, evaluates the paper's success against the research questions and discuss potential further work.
+This chapter collates the findings of the paper, evaluates the paper's success against the research questions and discusses potential further work.
 
@@
 The top three metrics (in descending order) were: Levenshtein, NYSIIS and Metaphone.
-We found that Levenshtein was the most aligned with how people rate phonetically similarity.
+We found that Levenshtein was the most aligned with how people rate phonetical similarity.
 Levenshtein had a considerable proportion of 4 and 5 ratings (64\%) compared to the alternatives.
-Levenshtein was also the best performer in the attack context with it having the best attack success rate in all attacks.
+Levenshtein was also the best performer in the attack context with it having the highest success rate.
 This corroborates work showing that words with similar spelling tend to share phonetic similarity \cite{hettiarachchi2012sparcl}.
 Alongside this, we found Soundex was the least aligned with the human model of similarity with an average rating of just 2 out of 5.
-This corroborates findings that highlighted major issues with the accuracy of Soundex’s phonetic representation (See Section \ref{sec:soundex}).
+This also corroborates findings that highlighted major issues with the accuracy of Soundex’s phonetic representation (See Section \ref{sec:soundex}).
 
@@
 \section{Research Question \ref{goal:complexity}}
-Research Question \ref{goal:complexity}: \textit{``What are the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys as shown in Section \ref{sec:key_gen}.
+Research Question \ref{goal:complexity}: \textit{``What is the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project alongside the actual generation of keys as shown in Section \ref{sec:key_gen}.
 Furthermore, the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}.
@@
 Inspiration for GreenOnion was gathered from a currently available tool known as Scallion.
-Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for with GreenOnion being able to handle in excess of 1.5 million keys.
-This capability is in comparison to the maximum of 2513 keys Scallion can compare.
+Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can concurrently search for.
+GreenOnion is able to handle in excess of 1.5 million keys.
+This capability is in comparison to the maximum of 2513 keys the alternative, Scallion can compare.
 We believe this is due to the implementation of the bloom filter.
@@
 Finally, the highest attack strength that theoretically involved the use of 100 mid-range GPUs computing for a week has success rates: 24.43\% - 32.05\%.
-Therefore, showing the number of attacks would deceive a set of users.
+Therefore, showing the number of attacks required to deceive a set of users.
 
@@
 The first area of proposed work could be recommendations into how to improve Trustwords backed by empirical evidence.
-We feel the most promising avenue would be the utilization of Phonetic Vectors unique qualities to identify words of low quality by measuring very low vector distances.
+We feel the most promising avenue would be the utilisation of Phonetic Vectors unique qualities to identify words of low quality by measuring very low vector distances.
 For example, present in the dictionary are the words \verb|THERE| and \verb|THEIR|, these could be massively improved upon and could result in a better quality word list.
 Moreover, utilizing the quantification of dissimilarity could be used to create a dictionary of maximized phonetic distance.
-This phonetically distinct wordlist could then be assessed in a similar with its success rate quantified against users.
+This phonetically distinct wordlist could then be assessed in a similar way with its success rate quantified against users.
 
@@
 The algorithms assessed in this work are a very small proportion of potential options.
-Thus, further work could assess the performance of metrics against each other to determine the one that works best with human models of phonetics.
-A conclusion could be reached by running the improved experiment discussed in Section \ref{exp:metric}, where it could be repeated with an increased of metrics.
-Other elements for consideration could be age, location and dialect as variables that affect the metrics performance.
+Thus, further work could assess the performance of metrics against each other to determine the one that works best with human models.
+A conclusion could be reached by running the improved experiment discussed in Section \ref{exp:metric}, where it could be repeated with an increased number of metrics.
+Other elements for consideration could be age, location and dialect as variables that affect a metrics performance.
 
 \subsection*{GreenOnion optimizations}
-A minimal amount of work and time was allocated to improving the performance of GreenOnion as low-level optimizations are very time-consuming.
+A minimal amount of work was allocated to improving the performance of GreenOnion as low-level optimizations are very time-consuming.
 A project, therefore, could aim to improve on the performance already recorded in this paper.
-This project could, therefore, improve the performance of the attack and allow for more effective keys to be computed in less time.
+This project could improve the performance of the attack and allow for more effective keys to be computed in less time.
 

### 2019-08-30 Writeup/Thesis/chapters/experiments.tex
Changes; - TTS run over the entire paper and corrections added

@@
 The results are also an improvement over informal ad-hoc methods.
-Further work could aim to reproduce this study with the proposed audio-based design (See Section \ref{sec:exp1_considerations}).
+Further work could aim to reproduce this study with the proposed audio-based design.
 
@@
 
-The reduced set of 369 participants had an average age of 36.63 ($\sigma = 11.35$) and consisted of an almost equal split of Male (50.4\%) to Female (49.6\%).
+The reduced set of 369 participants had an average age of 36.6 ($\sigma = 11.35$) and consisted of an almost equal split of Male (50.4\%) to Female (49.6\%).
 Around 62\% of participants had completed a single stage of university (Bachelor and up).
@@
 Table \ref{tab:exp2_attacks} contains the break down of results for the experiment.
-It can be seen that the best metric out of the set was Levenshtein with an overall success of 19.80\%.
+It can be seen that the best metric out of the set was Levenshtein with an overall success of 19.8\%.
 The best performer, when regarding attack strength, as expected, is the \XOOX~attack.
-Levenshtein's \XOOX~attack performed the best overall with a success rate of 32.05\%.
-The worst performer was Metaphone, with an average of 16.88\% over its three levels of attacks.
+Levenshtein's \XOOX~attack performed the best overall with a success rate of 32.1\%.
+The worst performer was Metaphone, with an average of 16.9\% over its three levels of attacks.
 When comparing the performance of the metrics to the previous experiment the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in the same order.
@@
 However, the success was 8.78\%.
-As 10/14 words were kept static, this result is more comparable to the highest attack strength ``2 static''.
+As 10/14 words were kept static, this result is more comparable to the highest attack strength (\XOOX).
 This, therefore, leads to another 3 fold improvement in the success rates of our simulated attacks.
@@
             \hline
-            \textbf{Metric} & & \textbf{Mean matches} & \textbf{Compute Time} \\
+            \textbf{Metric} & & \textbf{Near-collision keys} & \textbf{Compute Time} \\
             \hline
@@
 These vulnerable keys were created using real keys extracted from PGP key servers.
-These keys were then randomly sampled and used to create the combined key,as discussed in Section \ref{sec:pep}.
+These keys were then randomly sampled and used to create the combined key, as discussed in Section \ref{sec:pep}.
 100,000 random key pairs were created and used as the sample\cite{davidnorman_2019}.
@@
 Producing near-matching keys from key pairs with a very small number of potential matches adds very little to this demonstration.
-This, however, will result in best-case scenario key computation times.
+This, however, will result in a best-case scenario for key computation times.
 
@@
 When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU can achieve around a 28\% success rate when assessed against actual users.
+This time, however, has been improved due to the random search for a controlled key with a more favourable number of near-collision keys.
 Even with the least restricted attack type presented in Table \ref{tab:nysiis0}, the computation of half a day can provide almost a 10\% success rate when attacking users.

### 2019-08-31 Writeup/Thesis/chapters/design.tex
Changes; - Final check for gramatical errors

@@
 Completing these steps produces a list of fingerprints that can be inserted into a tool designed to hash a large number of keys and search for matches.
-This aspect of using a extensive list to search for keys massively reduces the complexity of the search.
+This aspect of using an extensive list to search for keys massively reduces the complexity of the search.
 
@@
 \subsection{NYSIIS}
-NYSIIS main use case was the matching of common names present in a database (See Section \ref{sec:nysiis}).
+NYSIIS primary use case was the matching of common names present in a database (See Section \ref{sec:nysiis}).
 However, due to it having embedded rules to handle word phonetics, it would again be applicable in this application.
@@
 \subsection{Metaphone}
-Metaphone as discussed in Section \ref{sec:metaphone} is another famous phonetic algorithm.
+Metaphone, as discussed in Section \ref{sec:metaphone} is another famous phonetic algorithm.
 Metaphone is arguably on the same level of ubiquity as that of Soundex with it finding itself implemented in languages such as PHP\cite{php}.
@@
 \subsection{Levenshtein Distance}
-As explained in Section \ref{sec:leven} Levenshtein Distance is the number of whole character edits.
-Levenshtein distance is not technically designed as a phonetic algorithm, but due to similar-sounding words often being spelt in similar ways\cite{hettiarachchi2012sparcl} the use-case of this algorithm remains relevant.
+As explained in Section \ref{sec:leven}, Levenshtein Distance is the number of whole character edits.
+Levenshtein distance is not technically designed as a phonetic algorithm, but due to similar-sounding words often being spelt in similar ways\cite{hettiarachchi2012sparcl}, the use-case of this algorithm remains relevant.
 Alongside this, Levenshtein is also the most algorithmically simplistic of all the considered options.
@@
 \subsection{Phonetic Vectors}
-As discussed in Section \ref{sec:phonetic_vectors} the metrics ability to perform operations and measure dissimilarity allows for a plethora of applications.
+As discussed in Section \ref{sec:phonetic_vectors}, the metrics ability to perform operations and measure dissimilarity allows for a plethora of applications.
 One possible application of note would be the creation of a wordlist where the phonetic difference (vector distance) is maximised.
@@
 \label{exp:metric}
-This section aims to assist answering Research Question \ref{goal:phoneticSimilarity}.
+This section aims to assist in answering Research Question \ref{goal:phoneticSimilarity}.
 To reduce the number of metrics to assess in the later rounds, the performance of similarity metrics required comparison.
@@
 
-As it can be seen from Table \ref{tab:matchSize}, the number of matches for L2 is more significant than all metrics excluding Soundex.
-As the issues with Soundex have been discussed in previous sections (See Section \ref{sec:soundex}) it can be excluded as an abnormality in this context.
+As can be seen from Table \ref{tab:matchSize}, the number of matches for L2 is more significant than all metrics excluding Soundex.
+As the issues with Soundex have been discussed in previous sections (See Section \ref{sec:soundex}), it can be excluded as an abnormality in this context.
 Therefore, due to the excessively high value for a L2, L1 was chosen as the Levenshtein cap for defining a match.
@@
 Match size was also used to define the threshold for the phonetic vectors.
-The decision is less apparent that that of Levenshtein due to the continuous nature of the distance between two vectors.
+The decision is less apparent than that of Levenshtein due to the continuous nature of the distance between two vectors.
 However, the complexity was reduced by limiting it to increments of 0.5.
@@
 Each comparison contains a match-pair.
-These matches are generated by running the similarity metric over all the pairings in the Trustword dictionary, if the pair meets the criteria discussed in the previous section it is determined a match.
+These matches are generated by running the similarity metric over all the pairings in the Trustword dictionary; if the pair meets the criteria discussed in the previous section, it is determined a match.
 Potential matches are then sampled from their respective lists.
@@
 Due to the assumed context of authentication being phone-based, the comparison of words is a mixture of auditory and visual.
-The user will hear their authentication partner read their set of words (Auditory) and compare to their set of words (Visual).
+The user hears their authentication partner read their set of words (Auditory) and compare to their set of words (Visual).
 This experiment asks users to compare the sound of two words that are visually displayed to them.
@@
 
-This experiment is designed to be a simulation of the attack proposed in Section \ref{sec:attackDesign}, in an attempt to answer Research Question \ref{goal:attackPercentage}.
-The experiment will test the simulated matches of three similarity metrics decided by the previous experiment (See Section \ref{sec:metrics}).
+This experiment is designed to be a simulation of the attack proposed in Section \ref{sec:attackDesign} in an attempt to answer Research Question \ref{goal:attackPercentage}.
+The experiment tests the simulated matches of three similarity metrics decided by the previous experiment (See Section \ref{sec:metrics}).
 The overall aim of the experiment is to quantify the success rate of the attack on live participants.
@@
 Therefore, in this experiment, attacks only occur 30\% of the time.
-This occurrence is a much higher value than in a real-world setting, but is a balance between resources and realistic design.
+This occurrence is a much higher value than in a real-world setting but is a balance between resources and realistic design.
 If the chosen attack rate is too low, many more trials are required to collate a useful number of attack instances, thus, requiring more resources, but with more realism.
-If, however, the attack rate is too high, less total rounds are required to obtain the target number of attack trails, however, the user will lose their complacency as an attack will be expected.
+If, however, the attack rate is too high, less total rounds are required to obtain the target number of attack trails.
+However, the user's complacency is lost as an attack is expected.
 This loss of complacency is undesirable as it does not realistically reflect real life.
-Furthermore, the first 5 trials of a new experiment is always benign.
+Furthermore, the first 5 trials of a new experiment are always benign.
 This inclusion is to ensure users are consistently lulled into complacency.
@@
 Certain keys have higher levels of potential near-collision keys than others due to how certain words are deemed similar by the similarity metric.
-Therefore, this presents the possibility to have keys with a very low number of possible near-collision keys.
+Therefore, this presents the possibility to have keys with a deficient number of possible near-collision keys.
 The distribution of these keys is explained further in Chapter \ref{cha:Experiments}.
@@
 The start and ends were chosen as the highest priority words to keep static.
-This design choice is due to research highlighting on the common habit of users only to check the start and end of a checksum.
+This design choice is due to research highlighting the common habit of users only to check the start and end of a checksum.
 \cite{cherubini2018towards} shows this by measuring user eye movement and displaying it as a heat map.
@@
 
-Figure \ref{fig:heatMap} shows the results of an eye-tracking experiment where the user failed to detect a mismatching digest. As it can be seen, the users never compared the centre of the digest.
+Figure \ref{fig:heatMap} shows the results of an eye-tracking experiment where the user failed to detect a mismatching digest. As can be seen, the users never compared the centre of the digest.
 
@@
 The tool requires no user interaction once started, therefore, it can be left for an extended period to compute potential keys.
-This timeframe is also a maximum time, these attacks also include keys that have a shorter average computation time.
+This timeframe is also a maximum time, as these attacks also include keys that have a shorter average computation time.
 
@@
 More potential near-collision keys make the attack search quicker.
-Any key that exceeds the defined numbers of potential near-collision key for attack level are deemed as vulnerable.
-As discussed in Section \ref{sec:attackDesign} the near-collision keys are close keys produced from the similarity-metric's matches.
+Any key that exceeds the defined numbers of potential near-collision key for attack level is deemed as vulnerable.
+As discussed in Section \ref{sec:attackDesign}, the near-collision keys are close keys produced from the similarity-metric's matches.
 A list of these vulnerable keys is sampled from when an attack is simulated.
@@
 A benchmark for the time is set by completing the experiment as fast as possible.
-Anything quicker was discarded as anything faster will risk invalid and rushed results.
+Anything quicker was discarded as anything faster risks invalid and rushed results.
 
 \subsubsection{Considerations}
-As with the previous experiment, sampling from a  MTurk demographics results in a collection of participants that are not reflective of the general population.
-Due to the attack context of this experiment it can be assumed that the youth of the participants contributes to less successful attacks.
+As with the previous experiment, sampling from MTurk's demographic results in a collection of participants that are not reflective of the general population.
+Due to the attack context of this experiment, it can be assumed that the youth of the participants contributes to less successful attacks.
 Therefore, the results generated by this experiment can be loosely assumed as a best-case scenario for the scheme.

### 2019-08-31 Writeup/Thesis/chapters/evaluation.tex
Changes; - Final check for gramatical errors

@@
 Performance of these metrics were then quantified in a direct study that selected the top three from a set of five (See Section \ref{exp:metric}).
-These newly selected metrics were then assessed in an attack context with their performance being indirectly quantified (See Section \ref{sec:exp2_design}).
+These newly selected metrics was then assessed in an attack context with their performance being indirectly quantified (See Section \ref{sec:exp2_design}).
 
@@
 Alongside this, we found Soundex was the least aligned with the human model of similarity with an average rating of just 2 out of 5.
-This also corroborates findings that highlighted major issues with the accuracy of Soundex’s phonetic representation (See Section \ref{sec:soundex}).
+This also corroborates findings that highlighted significant issues with the accuracy of Soundex’s phonetic representation (See Section \ref{sec:soundex}).
 
 We believe the outcome of the first experiment were inflated by the way the results were presented (as discussed in Section \ref{sec:exp1_considerations}).
-However, as the performance of the metrics in the second experiment emulated the first with Levenshtein being the best performer alongside Metaphone being the worst, shows that the results of the first study maintains a desirable level of accuracy.
-Improvements can be made with the proposed design discussed in Section \ref{sec:exp1_considerations}, but, we believe the first experiment has achieved its goal of providing a low cost way to reduce the number of selected metrics for the subsequent study.
+However, as the performance of the metrics in the second experiment emulated the first with Levenshtein being the best performer alongside Metaphone being the worst, shows that the results of the first study maintain a desirable level of accuracy.
+Improvements can be made with the proposed design discussed in Section \ref{sec:exp1_considerations}, but, we believe the first experiment has achieved its goal of providing a low-cost way to reduce the number of selected metrics for the subsequent study.
 
@@
 GreenOnion is able to handle in excess of 1.5 million keys.
-This capability is in comparison to the maximum of 2513 keys the alternative, Scallion can compare.
+This capability is in comparison to the maximum of 2513 keys the alternative; Scallion can compare.
 We believe this is due to the implementation of the bloom filter.
-Its unique characteristics of $O(k)$ complexity regardless of number of elements in the structure allows a huge number of concurrent checks to occur.
+Its unique characteristics of $O(k)$ complexity regardless of the number of elements in the structure allows a huge number of concurrent checks to occur.
 
@@
 For example, present in the dictionary are the words \verb|THERE| and \verb|THEIR|, these could be massively improved upon and could result in a better quality word list.
-Moreover, utilizing the quantification of dissimilarity could be used to create a dictionary of maximized phonetic distance.
+Moreover, utilising the quantification of dissimilarity could be used to create a dictionary of maximized phonetic distance.
 This phonetically distinct wordlist could then be assessed in a similar way with its success rate quantified against users.

### 2019-08-31 Writeup/Thesis/chapters/experiments.tex
Changes; - Final check for gramatical errors

@@
 Scallion was unable to handle anything over 2513 concurrent keys.
-This was due to the search strings being passed via a command line argument as a regex string.
+This was due to the search strings being passed via a command-line argument as a regex string.
 This number of keys hit the character limit of a Powershell command.
@@
 As discussed in Section \ref{exp:metric}, the goal of the experiment was to select a set of metrics to be assessed in the following experiment.
-This section will discuss the demographics of participants alongside the subsequent results.
+This section discusses the demographics of participants alongside the subsequent results.
 
@@
 \subsection*{Considerations}
-As discussed in Section \ref{sec:exp1_considerations}, compromises were made to fulfil all requirement with a minimized cost.
+As discussed in Section \ref{sec:exp1_considerations}, compromises were made to fulfil all requirement with a minimised cost.
 Levenshtein's abnormal performance further backs up concerns around the visual aspect biasing the performance of the metric.
@@
 Tables \ref{tab:exp2_browser} and \ref{tab:exp2_os} contain the browser and OS breakdowns,  respectively.
-Chrome and Windows 10 seem to dominate the proportion of their respective domains alongside the surprisingly large proportion of workers utilizing older versions of Windows such as 7 or 8 (15.81\%).
+Chrome and Windows 10 seem to dominate the proportion of their respective domains alongside the surprisingly large proportion of workers utilising older versions of Windows such as 7 or 8 (15.81\%).
 
@@
 The worst performer was Metaphone, with an average of 16.9\% over its three levels of attacks.
-When comparing the performance of the metrics to the previous experiment the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in the same order.
+When comparing the performance of the metrics to the previous experiment, the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in the same order.
 
@@
 As previously mentioned, the set of recruited participants are more highly educated than the general population.
-This combined with the lower average age, contributes to an inevitable bias being introduced into the data.
+This combined with the lower average age contributes to an inevitable bias being introduced into the data.
 An assumption can be made that higher education leads to more skilful interaction with computer-based systems, this, therefore, with the previous assumption in mind means the results of this experiment can be considered a `best case' scenario.
@@
 In conclusion, all related literature had much lower attack success rates that the results presented in this experiment.
-With all papers using similarly designed wordslists, it highly suggests that the deficiencies in Trustwords are the cause for the substantial increase in attack success.
+With all papers using similarly designed wordlists, it highly suggests that the deficiencies in Trustwords are the cause for the substantial increase in attack success.
 Alongside this, the consideration for similarity when calculating near-collisions could have also resulted in the higher attack success rates.
@@
 Producing near-matching keys from key pairs with a very small number of potential matches adds very little to this demonstration.
-This, however, will result in a best-case scenario for key computation times.
+This, however, results in a best-case scenario for key computation times.
 
@@
 Due to the varying availability of resources, each computation has a varying hashing speed.
-This variation has been normalized by the introduction of the "GPU Day" metric.
+This variation has been normalised by the introduction of the "GPU Day" metric.
 A GPU day is simply the computation time required to reach the same conclusion on a single 2000 MH/s GPU.

### 2019-08-31 Writeup/Thesis/chapters/implementation.tex
Changes; - Final check for gramatical errors

@@
 
-All keys including the intermediate hash are loaded on the GPU via an OpenCL kernel.
-This kernel is designed to hash the final block, obtain the final fingerprint and check if the fingerprint is present in the provided list.
+The intermediate hash is then loaded on the GPU via an OpenCL kernel.
+This kernel is designed to increment the exponent, hash the final block, obtain the final fingerprint and check if the fingerprint is present in the provided data structure.
 
@@
 Once it is in position the "Mask" is created by XORing with the original value and the new intended value, this stores the changes required to reach the required values, this then applied to each of the words.
-The \verb|get_global_id| command takes the ID from the currently running thread; this allows a different value to be used for each exponent concurrently
+The \verb|get_global_id| command takes the ID from the currently running thread; this allows a different value to be used for each exponent concurrently.
 
@@
 \label{sec:exp1_implemtation}
-As discussed in Section \ref{sec:matches} a list of matches were generated for each metric.
+As discussed in Section \ref{sec:matches}, a list of matches were generated for each metric.
 Figure \ref{fig:trustwordMatch} shows the algorithm designed to compute these lists.
@@
 Figure \ref{fig:matchExample} further shows the code used in the \verb|leven_similar|.
-The levenshtein difference is computed and compared to the tolerance discussed in Section \ref{sec:matches}.
+The Levenshtein difference is computed and compared to the tolerance discussed in Section \ref{sec:matches}.
 If this function returns true the match is added to the list.
@@
 This problem was solved by Google's App Script\footnote{\url{https://developers.google.com/apps-script/}} service that allows a user to interact with the Form programmatically.
-This addition allowed the re-sampling of matches  each time a user submitted a response.
+This addition allowed the re-sampling of matches  each time a response is submitted.
 

### 2019-08-31 Writeup/Thesis/chapters/lit_review.tex
Changes; - Final check for gramatical errors

@@
 In the diagram Eve (attacker) is impersonating Alice to Bob and Bob to Alice.
-Therefore, as both directions of communication are compromised all traffic will route through the attacker Eve.
+Therefore, as both directions of communication are compromised, all traffic routes through the attacker Eve.
 
@@
 A fingerprint is a string of alphanumerical characters that are unique to each key.
-Therefore the fingerprint of the two respective public keys are different, and, thus can be used for identification.
+Therefore the fingerprint of the two respective public keys are different, and, thus, can be used for identification.
 
@@
 
-Historically fingerprints have been represented as a hexadecimal string, whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card.
+Historically fingerprints have been represented as a hexadecimal string; whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card.
 Figure \ref{fig:businessCard} shows an example business card.
-A user will then use the fingerprint present on the card to compare to the one available on a device.
-This will have to be performed by each user.
-This process is known as the \textit{``authentication ceremony.''}
+A user then uses the fingerprint present on the card to compare to the one available on a device.
+This process has to be performed by each user and is known as the \textit{``authentication ceremony.''}
 
@@
 Users now compare a single fingerprint together, instead of two sets separately.
-In the case of WhatsApp for example, the connection fingerprint of two parties keys is the first 30 bytes of an SHA-512\footnote{5200 iterations} hash of each parties' identity key, these are then both concatenated together to form a single fingerprint\cite{whatsapp2017paper}.
+In the case of WhatsApp for example, the connection fingerprint of two parties keys is the first 30 bytes of an SHA-512\footnote{5200 iterations} hash of each parties' identity key; these parts are then concatenated together to form a single fingerprint\cite{whatsapp2017paper}.
 This process produces a unique key per communication pair.
@@
 Prior research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}.
-This shows that comparing complete digests would be cumbersome and error-prone.
+These findings show that comparing complete digests would be cumbersome and error-prone.
 For example, SHA-1 is 40 hex digits (160-bit) and, therefore, difficult to effectively compare.
@@
 Encoding schemes are the physical method of encoding used to represent the fingerprint.
-The most common representation is alphanumerically with either \textbf{Hexadecimal} (0-9/A-F) or \textbf{Base32} (2-7/A-Z).
+The most common representation is alphanumerical with either \textbf{Hexadecimal} (0-9/A-F) or \textbf{Base32} (2-7/A-Z).
 These encoding schemes are the most popular due to their intuitive simplicity and lack of hardware requirements.
@@
 Fingerprints can also be encoded using natural language.
-The fingerprint can be chunked and mapped to a set or words.
-The same principle can be used to fill placeholders in a pre-defined sentence allowing the simple formation of syntactically accurate English sentences.
-Moreover, other languages can be used such as Chinese, Japanese or Korean to map fingerprint chunks to characters.
+The fingerprint can be chunked and mapped to a set of words.
+The same principle can be used to fill placeholders in a pre-defined sentence allowing the simple formation of syntactically correct English sentences.
+Moreover, other languages can be used such as Chinese, Japanese or Korean, to map fingerprint chunks to characters.
 
@@
 This schemes should, therefore, be able to provide increased usability and security.
-This section will explain the relevant schemes in this paper.
+This section explains the relevant schemes discussed later in this paper.
 
@@
 OpenSSH Visual Host Key is an ASCII based graphical scheme used in MiTM detection when connecting to SSH servers.
-The image is generated by movement of the central marker across a grid.
+The image is generated by the movement of the central marker across a grid.
 Every 2-bits of the generated MD5 hash defines the diagonal direction of movement.
-For example, if the first 2-bits are \verb|11| the marker will move South East.
-The different characters are determined by the number of times the marker is present in that index, for example, if the maker is present on a square 4 times the character will be an equals sign (\verb|=|).
+For example, if the first 2-bits are \verb|11|, the marker moves South East.
+The different characters are determined by the number of times the marker is present in that index, for example, if the maker is present on a square 4 times the character is an equals sign (\verb|=|).
 
@@
 Unicorns can be considered an example of an ``Avatar'' graphical scheme.
-The provided hash changes aspects of the image such as background colour, horn length and colour of the Unicorn's mane.
+The provided hash changes aspects of the image, such as background colour, horn length and colour of the Unicorn's mane.
 
 \textbf{Vash}\footnote{\url{https://github.com/thevash/vash}}.
-Vash is similar to that of unicorns where the hash determines certain characteristics of the image.
+Vash is similar to that of unicorns, where the hash determines specific characteristics of the image.
 Vash claims to have $\approx 5,438$ bits of entropy.
@@
 
-Research in this area has taken these various encoding schemes and compared their falibility to impersonated attacks.
+Research in this area has taken these various encoding schemes and compared their fallibility to impersonated attacks.
 The main elements of comparison have been the ``accuracy of attack detection" and ``time to compare." In this paper, these are considered the metrics of ``security'' and ``usability,'' respectively.
@@
     \item \textbf{Poor precision.} Due to the previously discussed point of a limited code space.
-\cite{patman2001soundex} re-iterates this point, but in the context of name matching where Soundex's poor performance was demonstrated.
+\cite{patman2001soundex} re-iterates this point but in the context of name matching where Soundex's poor performance was demonstrated.
 Soundex only gained and overall accuracy of 36.37\% when matching names within a provided database.
@@
 It also allows for variable-length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex.
-It was in use right up util the end of 1998 within various US Government departments.
+It was in use right up until the end of 1998 within various US Government departments.
 
@@
 Using this with all 133,852 entries in version 0.7b of the CMU Pronouncing Dictionary, 949 unique properties were produced overall.
-The author then performed principal components analysis\footnote{Details regarding this process is outside the scope of the project.
-Please, however, if interested please refer to this resource for more information: \url{http://setosa.io/ev/principal-component-analysis/}} on the unique properties to reduce them down to 50.
+
+The author then performed principal components analysis\footnote{Details regarding this process are outside the scope of the project.
+Please, however, if interested please refer to this resource: \url{http://setosa.io/ev/principal-component-analysis/}} on the unique properties to reduce them down to 50.
 
@@
 Aside from textual representations were graphical schemes.
-As explained in Section \ref{sec:encodingSchemes} the main graphical schemes assessed by the literature were: Random Art, Flag, T-Flag, Vash, OpenSSH Visual Host Key and Unicorns.
+As explained in Section \ref{sec:encodingSchemes}, the primary graphical schemes assessed by the literature were: Random Art, Flag, T-Flag, Vash, OpenSSH Visual Host Key and Unicorns.
 These schemes had mixed accuracy with ranges as large as 50\% - 94\% in work by \textbf{Hsiao \textit{et al.}}\cite{hsiao2009study}.
-The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can} where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
+The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can}, where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
 \\
@@
 Therefore, all results have been translated into ``overall accuracy.''.
-For example, if a paper presented "security failures" or "attack success rate" of 5\% the overall accuracy of the scheme is 95\%.
+For example, if a paper presented "security failures" or "attack success rate" of 5\%, the overall accuracy of the scheme is 95\%.
 
@@
 Dechand \textit{et al.}}\cite{dechand2016empirical} where they briefly consider medical conditions such as ADHD and reading or visual disorders and the way they affect the comparison's effectiveness.
-The results highlight a slight reduction in overall accuracy, however, due to their small sample size, the results cannot be considered conclusive.
+The results highlight a slight reduction in overall accuracy; however, due to their small sample size, the results cannot be considered conclusive.
 This aspect is unique to all literature assessed.
@@
 ``remove vs proximity." This topic was initially covered by \cite{shirvanian2017pitfalls}, but their scope was limited.
+
 Further work, therefore, could increase the scope and touch upon a large number of schemes in these settings.
@@
 Each word is mapped to a single byte.
-The unique aspect of the word list is the separation of ``even'' and ``odd'' words where ``even'' byte indices are sample from the even-list and ``odd'' from the odd-list.
+The unique aspect of the word list is the separation of ``even'' and ``odd'' words.
+Even byte indices are sampled from the even-list and odd indices from the odd-list.
 This technique effectively creates two sub-word lists.
@@
 
-Overall the paper provides a foundation for formalising the creation of effective wordlists.
+Overall the paper provides a foundation for formalising the creation of useful wordlists.
 A limitation is the lack of empirical data gathered on the performance.
@@
 
-Aside from this research, there have been further informal implementations of fingerprint encodings.
-The first being by \textbf{Michael Rogers}\footnote{\url{https://github.com/akwizgran/basic-english}}.
+Aside from this research, there have been further informal implementations of fingerprint encodings -- The first being by \textbf{Michael Rogers}\footnote{\url{https://github.com/akwizgran/basic-english}}.
+Rogers' implementation is a program designed to map fingerprints to pseudo-random poems.
+This implementation was again, empirically evaluated by \textbf{S.
+Dechand \textit{et al.}}\cite{dechand2016empirical}.
+Earlier work by \textbf{N.
+Haller} with the S/KEY\cite{haller1995s} shows the implementation of a system designed to represent a hash as a series of six short words.
+However, this system is designed for a one-time-password purpose and only provides word mappings for basic human usability of the password and not within a fingerprint verification context.
+Therefore, the wordlist has not been designed with pronounceability in mind.
+Aside from this research, there have been further informal implementations of fingerprint encodings  The first being by \textbf{Michael Rogers}\footnote{\url{https://github.com/akwizgran/basic-english}}.
 Rogers' implementation is a program designed to map fingerprints to pseudo-random poems.
@@
 Approximately 13633/65536 (20.8\%) of words are re-mapped in the dictionary, leaving 51903 unique words.
-The re-mapping is performed on a alphabetical loop.
+The re-mapping is performed on an alphabetical loop.
 Figure \ref{fig:remap} shows the position in the dictionary where this occurs.
@@
 The morphing and re-ordering  attacks become increasingly ineffective as the user had more time to detect imperfections.
-This aspect is not quantified by the author and the extent of this degradation is never empirically discussed.
-Therefore, the results from this study are only effective and applicable in a SAS context.
+The author does not quantify this aspect, and the extent of this degradation is never empirically discussed.
+Therefore, the results from this study are only practical and applicable in a SAS context.
 
-\subsubsection*{Topic Conclusion}
+\subsubsection*{Conclusion}
 Overall the literature for this subtopic remains sparse and incomplete.
 Further suggested work could look into the feasibility of generating partial collisions for all textual representations alongside quantified effectiveness on users.
-With the possibility to concentrate on a few selected implementations.
 The work would aim to focus on the various physical methods used and their feasibility.
@@
 Hsiao \textit{et al.}}\cite{hsiao2009study} and could allow the creation of schemes that are better suited to specific languages.
-Alongside this, there is a research gap in the investigation of how mental impairments affect a schemes performance.
+Alongside this, there is a research gap in the investigation of how mental impairments affect the performance of a scheme.
 This aspect is useful due to the number of potential users being affected.

### 2019-08-31 Writeup/Thesis/chapters/research_question.tex
Changes; - TTS run over the entire paper and corrections added
Changes; - Final check for gramatical errors

@@
 \end{center}
-By sampling the \pep documentation they have defined the use case of the Trustword handshake: \textit{``A handshake is done by comparing the Trustwords between two users through a separate communication channel (e.g.
+By sampling the \pep documentation, they have defined the use case of the Trustword handshake: \textit{``A handshake is done by comparing the Trustwords between two users through a separate communication channel (e.g.
 in person or by phone)''.}\footnote{\url{https://www.pep.security/docs/general\_information.html\#handshake}}.
@@
 
-    \item What are the time and computation complexity required to generate a 'similar' keys for a targeted key pair? \label{goal:complexity}
+    \item What is the time and computation complexity required to generate a 'similar' keys for a targeted key pair? \label{goal:complexity}
 

### 2019-08-31 Writeup/Paper/sections/abstract.tex
Changes; - Added inital paper content

--- 2019-08-30 Writeup/Thesis/chapters/abstract.tex
@@
-Many encrypted connections require the comparison of a fingerprint to protect against eavesdropping.
-A substantial amount of past work has aimed to propose fingerprint representations that work better with human limitations.
-"Trustwords" proposed by pEp is an example of such a scheme, where the fingerprint is encoded as words in an attempt to improve usability.
-
-This works main aim is to asses if Trustword's recommend minimum number of four words is sufficient.
-In order to achieve this goal, this work implements an attack on Trustwords and quantifies its effectiveness on more than 400 participants.
-A tool called GreenOnion was designed to assist in quantifying attack feasibility.
-GreenOnion improved substantially on a similar tool's ability to search for matches concurrently where it was able to search for over 1.5 million concurrent keys.
-Our findings show a substantial increase in attack success compared to related literature.
-We believe this increase is due to levering the design flaws in the Trustword scheme.
-Therefore, we believe a minimum of four Trustwords is insufficient to provide even a basic level of security.
+\emph{Abstract} -- Many encrypted connections require the comparison of a fingerprint to
+protect against eavesdropping. A substantial amount of past work has
+aimed to propose fingerprint representations that work better with hu-
+man limitations. ``Trustwords'' proposed by pEp is an example of such a
+scheme, where the fingerprint is encoded as words in an attempt to improve
+usability.
+\\\\
+This works main aim is to assess if Trustword’s recommended minimum
+number of four words is sufficient. In order to achieve this goal, this work
+implements an attack on Trustwords and quantifies its effectiveness on
+more than 400 participants. A tool called GreenOnion was designed to
+assist in quantifying attack feasibility. GreenOnion improved substantially
+on a similar tool’s ability to search for matches concurrently where it was
+able to search for over 1.5 million concurrent keys. Our findings show a
+substantial increase in attack success compared to related literature. We
+believe this increase is due to levering the design flaws in the Trustword
+scheme. Therefore, we believe a minimum of four Trustwords is insufficient
+to provide even a basic level of security.

### 2019-08-31 Writeup/Paper/sections/background.tex
Changes; - Added inital paper content

--- 2019-08-30 Writeup/Thesis/chapters/lit_review.tex
@@
-\chapter{Background}
-\label{cha:LiteratureReview}
-
-The chapter explains aspects required to fully comprehend the project's achievements alongside an evaluation of current literature and the respective gaps.
-
-The chapter contains the following sections:
-
-\begin{itemize}
-    \item \textbf{Project context} \\ 
-    Provides the user with the base knowledge required to understand the context and purpose of the following literature review.
-
-    \item \textbf{Literature Review} \\
-    A review of currently available literature on relevant topics. Recommendations and research gaps are identified and discussed.
-
-\end{itemize}
-
-\section{Project context}
-
-To fully understand the literature review, it is necessary to introduce and explain the base knowledge before continuing.
+\section{Background}
+In this section we dicuss
 
 \subsection{Public-key Cryptography and Key Exchange}
+Asymmetric cryptography facilitates the secure encryption of messages
+in end-to-end encryption (E2EE), verification of digital signatures, and
+sharing of pre-communication secrets, among others.
 
-Asymmetric cryptography facilitates the secure encryption of messages in end-to-end encryption (E2EE), verification of digital signatures, and sharing of pre-communication secrets, among others.
+The asymmetry stems from the use of ``Public'' and ``Private'' keys. The
+public-key is used to encrypt data that only the respective private-key
+can decrypt. Hence, this means that sharing the keys required to encrypt
+can be performed across insecure channels.
 
-The asymmetry stems from the use of "Public" and "Private" keys.
-The public-key is used to encrypt data that only the respective private-key can decrypt.
-Hence, this means that sharing the keys required to encrypt can be performed across insecure channels.
-
-An E2EE connection uses the key types discussed previously to exchange messages between verified parties securely.
-However, this hinges on the verification of the initial parties, if one party impersonates another and receives sensitive communication, the secure encryption is completely circumvented.
+An E2EE connection uses the key types discussed previously to ex-
+change messages between verified parties securely. However, this hinges
+on the verification of the initial parties, if one party impersonates another and receives sensitive communication, the secure encryption is
+completely circumvented.
 Therefore, the correct identification of parties is crucial to maintaining security.
@@
 This attack is commonly bidirectional, and if executed correctly, there is often no discerning change to the user experience.
-Figure \ref{fig:mitm} contains a visual representation of this attack.
-In the diagram Eve (attacker) is impersonating Alice to Bob and Bob to Alice.
-Therefore, as both directions of communication are compromised all traffic will route through the attacker Eve.
-
-\begin{center}
-    \input{diagrams/mitm.tex}
-    \begin{figure}[h]
-        \caption{Photo depicting a MITM attack}
-        \label{fig:mitm}
-    \end{figure}
-\end{center}
-
-Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob), the unique aspects of the keys can be used to identify parties.
-This is achieved succinctly through the use of a fingerprint.
-A fingerprint is a string of alphanumerical characters that are unique to each key.
-Therefore the fingerprint of the two respective public keys are different, and, thus can be used for identification.
-
-The fingerprint of the key is generated by running the main key components through a secure one-way hash function such as SHA-256.
-This process produces a digest of a fixed length that can be used to compare keys.
-Therefore, the comparison of expected and actual fingerprints can be used to detect MiTM attacks.
-
-Historically fingerprints have been represented as a hexadecimal string, whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card.
-Figure \ref{fig:businessCard} shows an example business card.
-A user will then use the fingerprint present on the card to compare to the one available on a device.
-This will have to be performed by each user.
-This process is known as the \textit{``authentication ceremony.''}
-
-\begin{figure}[h!]
-    \centering
-    \fbox{
-        \input{diagrams/business_card.tex}
-    }
-    \caption{Example business card with fingerprint}
-    \label{fig:businessCard}
-\end{figure}
-
-System designers are, however, moving away from the structure of one fingerprint per identity and are now implementing a combined key.
-This change is due to the assumed increase in usability.
-Users now compare a single fingerprint together, instead of two sets separately.
-In the case of WhatsApp for example, the connection fingerprint of two parties keys is the first 30 bytes of an SHA-512\footnote{5200 iterations} hash of each parties' identity key, these are then both concatenated together to form a single fingerprint\cite{whatsapp2017paper}.
-This process produces a unique key per communication pair.
-
-Due to the manual comparison of the fingerprint, length and format are core design considerations.
-Prior research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}.
-This shows that comparing complete digests would be cumbersome and error-prone.
-For example, SHA-1 is 40 hex digits (160-bit) and, therefore, difficult to effectively compare.
-Therefore, if human interaction is required; there is a need for schemes that work effectively with consideration to human limitations.
-
-\newpage
-
-\subsection{Encoding schemes}
-\label{sec:encodingSchemes}
-
-\subsubsection*{Text-based schemes}
-Encoding schemes are the physical method of encoding used to represent the fingerprint.
-The most common representation is alphanumerically with either \textbf{Hexadecimal} (0-9/A-F) or \textbf{Base32} (2-7/A-Z).
-These encoding schemes are the most popular due to their intuitive simplicity and lack of hardware requirements.
-
-Fingerprints can also be encoded using natural language.
-The fingerprint can be chunked and mapped to a set or words.
-The same principle can be used to fill placeholders in a pre-defined sentence allowing the simple formation of syntactically accurate English sentences.
-Moreover, other languages can be used such as Chinese, Japanese or Korean to map fingerprint chunks to characters.
-
-\begin{table}[h!]
-    \centering
-    \input{tables/background/encoding_examples.tex}
-    \caption{Examples for text based encodings}
-\end{table}
-
-\subsubsection*{Graphical Schemes}
-Graphical schemes are a potential alternative to text-based schemes.
-They often attempt to visualise small changes in the fingerprint to assist in alerting the user to small changes.
-This schemes should, therefore, be able to provide increased usability and security.
-This section will explain the relevant schemes in this paper.
-
-\textbf{Random Art}.
-Random Art engine\cite{perrig1999hash} takes any length of input and processes it via SHA-1 to produce a digest that is then converted into an image.
-Figure \ref{fig:randomArt} contains three examples from the Random Art Gallery\footnote{\url{http://www.random-art.org/}}.
-
-\begin{figure}[h!]
-    \centering
-    \minipage{0.32\textwidth}
-        \includegraphics[width=.9\textwidth]{random_art/random_art1.jpg}
-    \endminipage
-    \minipage{0.32\textwidth}
-        \includegraphics[width=.9\textwidth]{random_art/random_art2.jpg}
-    \endminipage
-    \minipage{0.32\textwidth}
-        \includegraphics[width=.9\textwidth]{random_art/random_art3.jpg}
-    \endminipage
-    \caption{Random Art examples}
-    \label{fig:randomArt}
-\end{figure}
-
-\textbf{Flag}.
-Flag is a visual hash scheme proposed by \textbf{C.
-Ellison} and \textbf{S.
-Dohrmann}\cite{ellison2003public}.
-Flag consists of four coloured strips with $2^n$ number of possible colours in each strip.
-
-\textbf{T-Flag}.
-T-Flag is an attempt to improve on the previously mentioned Flag \cite{lin2010spate}.
-Improvements include twice the number of coloured blocks with a choice of eight colours.
-The authors claim the choice of colours are ``colourblind proof''.
-
-\textbf{Flag-Ext}.
-Flag Extended is the proposed scheme assessed in the paper by \textbf{H.
-Hsiao \textit{et al.}}\cite{hsiao2009study}.
-Flag-Ext aims, again, to improve on flag by reducing the number of blocks while adding 8 possible shapes.
-
-Figure \ref{fig:flag} contains an example of each version of Flag discussed.
-
-\begin{figure}[h!]
-    \centering
-    \minipage{0.32\textwidth}
-        \includegraphics[width=.9\textwidth]{flag/Flag.png}
-        \caption{Flag}
-    \endminipage
-    \minipage{0.32\textwidth}
-        \includegraphics[width=.9\textwidth]{flag/T-Flag.png}
-        \caption{T-Flag}
-    \endminipage
-    \minipage{0.32\textwidth}
-        \includegraphics[width=.9\textwidth]{flag/Flag-ext.png}
-        \caption{Flag Ext}
-    \endminipage
-    \caption{Variations of Flag}
-    \label{fig:flag}
-\end{figure}
-
-\textbf{OpenSSH}.
-OpenSSH Visual Host Key is an ASCII based graphical scheme used in MiTM detection when connecting to SSH servers.
-The image is generated by movement of the central marker across a grid.
-Every 2-bits of the generated MD5 hash defines the diagonal direction of movement.
-For example, if the first 2-bits are \verb|11| the marker will move South East.
-The different characters are determined by the number of times the marker is present in that index, for example, if the maker is present on a square 4 times the character will be an equals sign (\verb|=|).
-
-\textbf{Unicorns}\footnote{\url{https://unicornify.pictures/}}.
-Unicorns can be considered an example of an ``Avatar'' graphical scheme.
-The provided hash changes aspects of the image such as background colour, horn length and colour of the Unicorn's mane.
-
-\textbf{Vash}\footnote{\url{https://github.com/thevash/vash}}.
-Vash is similar to that of unicorns where the hash determines certain characteristics of the image.
-Vash claims to have $\approx 5,438$ bits of entropy.
-
-\begin{figure}[h!]
-    \centering
-    \minipage{0.32\textwidth}
-        \includegraphics[width=.9\textwidth]{graphical/openssh.png}
-        \caption{OpenSSH Visual Host Key}
-    \endminipage
-    \minipage{0.32\textwidth}
-        \includegraphics[width=.9\textwidth]{graphical/unicorn.png}
-        \caption{Unicorn}
-    \endminipage
-    \minipage{0.32\textwidth}
-        \includegraphics[width=.9\textwidth]{graphical/vash.png}
-        \caption{Vash}
-    \endminipage
-    \caption{Examples of alternative graphical encoding schemes}
-\end{figure}
-
-Research in this area has taken these various encoding schemes and compared their falibility to impersonated attacks.
-The main elements of comparison have been the ``accuracy of attack detection" and ``time to compare." In this paper, these are considered the metrics of ``security'' and ``usability,'' respectively.
 
@@
 \label{sec:soundex}
-One of the earliest examples of a phonetic algorithm is known as Soundex. It was initially designed for phonetically indexing names alongside detection of transposed letters in spelling mistakes.
-
-Soundex produces a four-digit code for each word assessed.
-The first letter of the word is retained alongside the removal of all of \verb|a|, \verb|e|, \verb|i|, \verb|o|, \verb|u|, \verb|y|, \verb|h| and \verb|w|.
-The remaining letters are then mapped to numbers.
-These mappings are displayed in Figure \ref{fig:soundexMap}.
-
-\begin{figure}[h!]
-    \centering
-    \begin{BVerbatim}
-b, f, p, v               1
-c, g, j, k, q, s, x, z   2
-d, t                     3
-l                        4
-m, n                     5
-r                        6
-    \end{BVerbatim}
-
-    \caption{Soundex mappings of letters to numbers}
-    \label{fig:soundexMap}
-\end{figure}
-
-Due to the fixed length and limited digit set the initial concerns from this design is the limited number of combinations.
-There are a total of 5616 codes due to 26 initial letters and three digits of 6 values ($26 * 6^3$).
-The limited combinations result in matches of limited quality.
-
-Further issues posed in \cite{patman2001soundex} are discussed below and show the further deficiencies of Soundex in a dictionary word matching context.
-
-\begin{enumerate}
-    \item \textbf{Dependency on the first letter:} Soundex cannot match words together if their first letters are different, meaning, for example, the words "KORBIN" and "CORBIN" are considered non-matching.
-
-    \item \textbf{Silent consonants.} Soundex does not have logic embedded to deal with silent consonants.
-
-    \item \textbf{Poor precision.} Due to the previously discussed point of a limited code space.
-\cite{patman2001soundex} re-iterates this point, but in the context of name matching where Soundex's poor performance was demonstrated.
-Soundex only gained and overall accuracy of 36.37\% when matching names within a provided database.
-\end{enumerate}
+One of the earliest examples of a phonetic algorithm is known as Soundex.
+It was initially designed for phonetically indexing names alongside detection of transposed letters in spelling mistakes.
+Soundex is one of the most famous example of a phonetic.
+This is due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}.
 
@@
 
-It also allows for variable-length codes and, thus, allows the applicability of the application to increase due to it not confronting the limited code issue of Soundex.
-It was in use right up util the end of 1998 within various US Government departments.
-
 \subsubsection*{Metaphone}
@@
 
-\subsubsection{Levenshtein Distance}
+\subsubsection*{Levenshtein Distance}
 \label{sec:leven}
@@
 
-\subsubsection{Phonetic Vectors}
+\subsubsection*{Phonetic Vectors}
 \label{sec:phonetic_vectors}
@@
 Created by Allison Parrish in 2017\cite{parrish2017poetic}, Phonetic vectors is as the name suggests the vectorisation of the phonetics of a word.
-
 Phonetic features are used in this work as a way to compare the similarity of phonemes.
@@
 
-Extensive prior work has gone into producing models of features that map to phonemes \cite{chomsky1968sound}\cite{ladefoged1969measurement}\cite{bradlow2010perceptual}.
-Features, therefore, are an attempt at mapping the varying and inconsistent rules around the pronunciation of the English language.
-The vectors were created using lists phonemes from the CMU Pronouncing Dictionary and mapping them to possible features.
+\clearpage
 
-\begin{table}[!htb]
-    \tiny
-    \begin{minipage}{.33\linewidth}
-        \centering
-        \begin{tabular}{ll}
-            Phone & Features \\
-            \hline
-            AA & bck, low, unr, vwl \\
-            AE & fnt, low, unr, vwl \\
-            AH & cnt, mid, unr, vwl \\
-            AO & bck, lmd, rnd, vwl \\
-            AW & bck, cnt, low, rnd, smh, unr, vwl \\
-            AY & cnt, fnt, low, smh, unr, vwl \\
-            B & blb, stp, vcd \\
-            CH & alv, frc, stp, vls \\
-            D & alv, stp, vcd \\
-            DH & dnt, frc, vcd \\
-            EH & fnt, lmd, unr, vwl \\
-            ER & cnt, rzd, umd, vwl \\
-            EY & fnt, lmd, smh, unr, vwl
-        \end{tabular}
-    \end{minipage}%
-    \begin{minipage}{.33\linewidth}
-        \centering
-        \begin{tabular}{ll}
-            Phone & Features \\
-            \hline
-            F &  frc, lbd, vls \\
-            G &  stp, vcd, vel \\
-            HH & apr, glt \\
-            IH & fnt, smh, unr, vwl \\
-            IY & fnt, hgh, unr, vwl \\
-            JH & alv, frc, stp, vcd \\
-            K &  stp, vel, vls \\
-            L &  alv, lat \\
-            M &  blb, nas \\
-            N &  alv, nas \\
-            NG & nas, vel \\
-            OW & bck, rnd, smh, umd, vwl \\
-            OY & bck, fnt, lmd, rnd, smh, unr, vwl
-        \end{tabular}
-    \end{minipage} 
-    \begin{minipage}{.33\linewidth}
-        \centering
-        \begin{tabular}{ll}
-            Phone & Features \\
-            \hline
-            P & blb, stp, vls \\
-            R & alv, apr \\
-            S & alv, frc, vls \\
-            SH & frc, pla, vls \\
-            T & alv, stp, vls \\
-            TH & dnt, frc, vls \\
-            UH & bck, rnd, smh, vwl \\
-            UW & bck, hgh, rnd, vwl \\
-            V & frc, lbd, vcd \\
-            W & apr, lbv \\
-            Y & apr, pal \\
-            Z & alv, frc, vcd \\
-            ZH & frc, pla, vcd \\
-        \end{tabular}
-    \end{minipage} 
-    \caption{Phonemes to feature mapping table}
-    \label{tab:features}
-\end{table}
-
-Table \ref{tab:features} contains the mappings used in \cite{parrish2017poetic} to create the phonetic feature lists.
-Using this with all 133,852 entries in version 0.7b of the CMU Pronouncing Dictionary, 949 unique properties were produced overall.
-The author then performed principal components analysis\footnote{Details regarding this process is outside the scope of the project.
-Please, however, if interested please refer to this resource for more information: \url{http://setosa.io/ev/principal-component-analysis/}} on the unique properties to reduce them down to 50.
-
-This metric allows for a unique set of actions to be performed on the phonetic output.
-Not only does this metric allow the user to measure \textit{dissimilarity} (as opposed to the similar-or-not method of the alternatives) the continuous nature of the value allows mathematical operations to be performed on the output.
-An example shown in \cite{parrish2017poetic} was the addition of word vectors.
-
-\begin{table}[!htb]
-    \centering
-    \begin{tabular}{cll}
-        No & Operation & Result \\
-        \hline
-        1  & $Vec(\verb|sub|) + Vec(\verb|marine|)$ & \verb|submarine| \\
-        2  & $Vec(\verb|miss|) + Vec(\verb|sieve|)$ & \verb|missive| \\
-        3  & $Vec(\verb|fizz|) + Vec(\verb|theology|)$ & \verb|physiology| \\
-    \end{tabular}
-    \caption{Examples of vector addition}
-    \label{tab:vectorAdd}
-\end{table}
-
-For example, the addition of vectors can be seen in Table \ref{tab:vectorAdd}.
-This works for any mathematical operation with examples like multiplication allowing the `tinting' of words with a phonetical theme.
-
-\section{Literature Review}
-This section discusses the current research around the proposed topic.
-
-The organisation of the section is as follows:
-
-\begin{itemize}
-    \item \textbf{Authentication ceremony performance} \\
-    This section explains the current research on the performance of various encoding schemes and methods of comparison, alongside an assessment of the literature's experimental design.
-
-    \item \textbf{Encoding schemes} \\
-    The following section then discusses research around the design of an encoding scheme. The focus of the section is the technical details regarding the creation and design of schemes.
-
-    \item \textbf{Attacks on encoding schemes} \\
-    The final section discusses literature that investigates the creation of actual attacks against encoding schemes.
-\end{itemize}
-
-\subsection{Authentication ceremony performance}
-
-\subsubsection*{Encoding scheme performance}
-Results 
-from the literature consistently show the effectiveness of language-based encodings such as Words or Sentences with accuracies ranging up from 94\% \cite{dechand2016empirical}\cite{tan2017can}\cite{kainda2009usability}.
-In all cases, these were the best schemes from the sets assessed.
-The exception to this is the work performed by \textbf{H.
-Hsiao \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63\%.
-\\\\
-Aside from textual representations were graphical schemes.
-As explained in Section \ref{sec:encodingSchemes} the main graphical schemes assessed by the literature were: Random Art, Flag, T-Flag, Vash, OpenSSH Visual Host Key and Unicorns.
-These schemes had mixed accuracy with ranges as large as 50\% - 94\% in work by \textbf{Hsiao \textit{et al.}}\cite{hsiao2009study}.
-The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can} where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
-\\
-\begin{table}[h!]
-    \makebox[\textwidth][c]{
-        \input{tables/background/fingerprint_times.tex}
-    }%
-    \caption{Average comparison time (seconds) for the encoding schemes}
-    \label{tab:times}
-\end{table}
-\\
-In terms of usability of graphical schemes, the literature concurred on their high usability.
-The comparison speed of these schemes were all among the quickest (See Table \ref{tab:times} for an overview of timings).
-Other work also indirectly agreed with graphical encodings having significantly quicker comparison times compared to non-graphical schemes \cite{dechand2016empirical, kainda2009usability}.
-In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with only two papers available.
-There is also no overlap in the schemes assessed with each paper reviewing a unique set.
-This area is, therefore, a promising candidate for further research.
-
-One unique paper in this research area was the work by \textbf{M.
-Shirvanian, N.
-Saxena and J.
-J.
-George}\cite{shirvanian2017pitfalls} produced in the context of secure messaging pairing.
-This paper was unique for several reasons.
-First was the consideration for ``remote-vs-proximity'' pairing where this is the first consideration of this aspect found in the literature.
-There is room for further research to compare encoding schemes in the context of ``remote-vs-proximity.'' Another unique aspect was the end-to-end encryption context of the study.
-
-The findings from the paper showed a high false-negative rate for all the schemes in a remote setting.
-This consideration is also missing from the literature.
-Alongside this, results for usability were lower in a remote setting for all the schemes.
-The author, however, comments on the expected nature of this result.\\
-Images were identified as being the most secure method of authentication in the remote setting but voted as the method with the worst usability.
-This conclusion is highly inconsistent with all other work in this area.
-However, this could be due to the unique setting of remote verification, resulting in distinct results from user studies.
-Without further work in this area, it is difficult to validate these results conclusively.
-
-Alongside this, it was shown in work by \textbf{H.
-Hsiao \textit{et al.}}\cite{hsiao2009study} that age and gender do not affect the accuracy of the scheme.
-However, younger participants were considerably faster.
-Furthermore, findings also showed that language comprehension helped in discerning small differences between schemes encoded in Chinese, Japanese, Korean, or English.
-Subsequently, knowledge of the language did not assist in differentiating more significant changes in the schemes as these had high accuracy regardless.
-These were unique considerations.
-Further work could aim to corroborate these conclusions.
-
-\begin{table}[h!]
-    \centering
-    \resizebox{.8\textwidth}{!}{%
-
-        \makebox[\textwidth][c]{
-            \input{tables/background/fingerprint_comparison.tex}
-        }%
-    }
-    \caption{Overall accuracy of correct comparison for the encoding schemes assessed}
-    \label{tab:results}
-\end{table}
-
-Tables \ref{tab:times} \& \ref{tab:results} contain the accuracy results of all papers assessed; this is to aid in visual comparison.
-Each paper used a different metric for measuring accuracy.
-Therefore, all results have been translated into ``overall accuracy.''.
-For example, if a paper presented "security failures" or "attack success rate" of 5\% the overall accuracy of the scheme is 95\%.
-
-\subsubsection*{Methods of comparison performance}
-
-Method of comparison is the way a user compares the encoding schemes output.
-The most common example and the one used as default is ``Compare-and-Confirm'' (CaC).
-CaC, as the name suggests, is the \textit{comparison} of two fingerprints on different devices or mediums that are then \textit{confirmed}.
-
-Aside from ``Compare-and-Confirm'' (CaC), there is ``Compare-and-Select'' (CaS) and ``Compare-and-Enter'' (CaE).
-CaS is the method where one device displays the fingerprint, and the other user is provided with several options.
-The user then has to choose the correct value from the list of candidates.
-If there is no match, the user must deny the connection attempt.
-The creation of CaS was due to concerns that CaC would be ``too easy'' for users leading to complacency and errors\cite{uzun2007usability}.
-The design of CaE is for scenarios where both devices might not have a display, i.e., pairing between a phone and a keyboard.
-One device displays the checksum.
-This checksum is then entered into the other device.
-The first device then compares the entered string and checks for a match.
-
-Research has assessed the performance of these schemes and how they affect the security of the authentication ceremony.
-The literature agrees on CaC being the best overall scheme to compare fingerprints \cite{tan2017can}\cite{uzun2007usability} with CaS highlighted for its poor security and usability.
-CaE has had conflicting results.
-\cite{uzun2007usability} discarded it after one round due to ``poor usability.'' However, \cite{tan2017can} considered it the best method overall for usability and security.
-These conflicting results, therefore, show polarisation in the results of CaE.
-However, this could be due to the different overall use-cases of the studies.
-Validation of results from either study would, therefore, be an area of additional study.
-
-\subsubsection*{Experimentation methodology comparison}
-To further look into the validity of previously discussed results, it is necessary to asses how the respective studies reached their conclusions.
-Areas for consideration are scheme entropy, attacker strength, and participant demographics.
-
-The starkest limitations of the literature are the range of participants and encoding entropy.
-The worst studies tested only 22-bits of entropy.
-This lack of entropy makes it challenging to compare results directly.
-One of the papers this most effects is the early work by \textbf{H.
-Hsiao \textit{et al.}}\cite{hsiao2009study}  where their highest entropy is 28-bits.
-This level of entropy was inadequate even at the time of publication.
-There is an attempt by the authors' to address this issue in the later stages of the paper where they write: \textit{``[...] increasing entropy is not a solution because it sacrifices usability and accuracy.
-With more entropy, representations will contain longer sequences of characters or more minute details which will lead to increased time and errors during comparisons.''}.
-This statement is backed up with no empirical evidence, and the authors fail to consider how the low entropy would affect the overall security of the schemes.
-
-Attacker strength is also another metric used to compare results concluded by each paper.
-Some papers failed to address their attacker strength consideration directly, but the overall strength has been inferred from the changes made to their schemes.
-For example, if they decided to change a single character in a 40-digit (160-bit) SHA-1 hex digest, they are indirectly stating that the attacker can control 39-digits (156-bit).
-To achieve this, the attacker would have to compute $2^{156}$ SHA-1 compressions to find a key match.
-In the literature, this element ranged from $2^{28}$ to around $2^{242}$.
-However, this has some relation to the size of the encoding schemes used.
-This substantial range makes it challenging to compare and confer results confidently.
-Further work could exclusively look into the effects that attacker strength has on the success of attacks.
-Moreover, all the papers assessed failed to fully consider the feasibility of attacks in terms of computer and storage requirements.
-
-All of the studies considered demographical data when presenting their results.
-Their average ages were all around $\sim35$ years old with the majority of participants educated with at least a bachelor degree.
-Alongside, the equal split between male and female participants.
-
-One consideration of note is that made by \textbf{S.
-Dechand \textit{et al.}}\cite{dechand2016empirical} where they briefly consider medical conditions such as ADHD and reading or visual disorders and the way they affect the comparison's effectiveness.
-The results highlight a slight reduction in overall accuracy, however, due to their small sample size, the results cannot be considered conclusive.
-This aspect is unique to all literature assessed.
-Further work would be required to produce conclusive results.
-Therefore, highlighting a gap in the literature.
-
-One glaring issue with the demographical health of the study by \textbf{E.
-Uzun, K.
-Karvonen} and \textbf{N.
-Asokan}\cite{uzun2007usability} is the use of two entirely different groups of participants.
-Not only were their demographics different, but they were from different countries (America and Finland).
-Different cultures contain inherent biases and assumptions.
-Changes were made pragmatically regarding the results from the first round of 40 participants.
-These were then re-assessed, alongside the direct comparison of results.
-This aspect casts vast doubts on the validity of the results with no consideration made by the authors to control external factors that may affect the performance of the method of comparison.
-
-Hexadecimal and numerical schemes were not included as encoding schemes in work by \textbf{H.
-Hsiao \textit{et al.}}\cite{hsiao2009study} (some of the most widespread encoding schemes).
-The justification was the schemes similarities to Base32  alongside "well-known deficiencies".
-This point was provided with no further justification.
-Moreover, it is also inconsistent with available research, for example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}\cite{dechand2016empirical} it was shown numerical representations performed significantly better than that of Base32.
-
-\begin{table}[h!]
-    \centering
-    \resizebox{.8\textwidth}{!}{%
-        \makebox[\textwidth][c]{
-            \input{tables/background/fingerprint_attacker_stren.tex}
-        }%
-    }
-    \caption{Paper attribute comparison}
-    \label{tab:attacker}
-\end{table}
-
-Table \ref{tab:attacker} has been provided to compare the different aspects of the papers' parameters visually.
-It can be seen from the table the substantial ranges in participant size, entropy and attacker strength.
-
-\subsubsection*{Conclusion}
-Overall, this review has identified several key areas suitable for further work.
-The first is the performance assessment of graphical encoding schemes.
-Recreation of pre-existing results from \cite{hsiao2009study}\cite{tan2017can} is required to corroborate current conclusions and validate results.
-Another gap in the research is the consideration into the utilisation of encoding schemes in realistic conditions, i.e.
-``remove vs proximity." This topic was initially covered by \cite{shirvanian2017pitfalls}, but their scope was limited.
-Further work, therefore, could increase the scope and touch upon a large number of schemes in these settings.
-The final aspect for further work is the limited consideration into the feasibility of attacks on encoding schemes.
-All of the papers assessed simulated attacks and had minimal consideration for their execution.
-Therefore, further work could delve
-into the implementation and feasibility of such attacks.
-
-\subsection{Encoding schemes}
-Another area of research is investigations into the actual physical encodings of the hash digest.
-This section discusses the current research on the creation and security of actual encoding schemes.
-The technical and operation details are outside the scope of this literature review.
-Therefore, minimal attention is allocated to these areas.
-
-Some of the oldest preliminary work into visual encoding schemes is by \textbf{A.
-Perrig} and \textbf{D.
-Song}\cite{perrig1999hash} in the creation of their scheme ``Random Art" in 1999.
-The motivation for creating such a scheme was the perceived flaws in the ways humans verify and compare written information.
-As mentioned in previous sections, visual encoding schemes have been shown to have mixed success, with low security being one of their most alarming flaws.
-This research laid the foundation for further work in analysing the security of visual encoding schemes.
-
-Further research into the creation of unique visual hash schemes has been performed by \textbf{C.
-Ellison} and \textbf{S.
-Dohrmann}\cite{ellison2003public} (Flag), \textbf{Yue-Hsun Lin \textit{et al.}}\cite{lin2010spate} (T-Flag) and work by \textbf{M.
-Olembo \textit{et al.}}\cite{olembo2013developing}.
-Each publication has provided a new way  to represent a key fingerprint visually.
-Alongside the academic literature, there are informally presented methods of visual fingerprints such as Unicorns\footnote{\url{https://unicornify.pictures/}} and Robots\footnote{\url{https://github.com/e1ven/Robohash}}.
-This list is by no means exhaustive but is used to depict the amount of research and work invested into graphical hash representations.
-
-One paper of note is the preliminary work performed by \textbf{D Loss \textit{et al.}}\cite{loss2009drunken} in their \textit{``An analysis of the OpenSSH fingerprint visualisation algorithm''} where  they aimed to spur on further research with their initial findings into the security of the OpenSSH scheme.
-The authors claim that the use of the algorithm in OpenSSH is only heuristically justified, and a more formal proof is required.\\
-The paper proposed several ways to generate similar fingerprints.
-The methods proposed were: Naive brute force, Graph Theory, and brute force of a full visual set.
-They were only able to produce only initial results and have proposed a large amount of potential further work.
-Since the paper's publication in 2009, there seems to have been no research building on the work of the authors.
-
-Minimal research has also focused on elemental textual fingerprint representations and their security.
-Work by \textbf{A.
-Karole} and \textbf{N.
-Saxena}\cite{karole2009improving} looked into ways to improve the security of a textual representation.
-This research aim was to improve the secure device pairing process of comparing two numerical values.
-The devices used (Nokia 6030b; Mid-range devices at the time of publication) and the SAS (Short Authentication String) compared results in findings that are not directly applicable in a fingerprint comparison context.
-
-A more specific subsection of textual fingerprints is the use of words and sentences to encode hash digests.
-Some of the first work in this area was by \textbf{Juola} and \textbf{Zimmermann} \cite{juola1996whole}.
-Their work aimed to produce a word list where phonetic distinctiveness was prioritised.
-Each word is mapped to a single byte.
-The unique aspect of the word list is the separation of ``even'' and ``odd'' words where ``even'' byte indices are sample from the even-list and ``odd'' from the odd-list.
-This technique effectively creates two sub-word lists.
-A genetic algorithm was used to maximise linguistic distance.
-The paper also includes a study on effective measures of ``linguistic distances'' of words and provided an in-depth discussion into these areas.
-
-Overall the paper provides a foundation for formalising the creation of effective wordlists.
-A limitation is the lack of empirical data gathered on the performance.
-However, this was later evaluated in work by \textbf{S.
-Dechand \textit{et al.}}\cite{dechand2016empirical} and shown to be an effective encoding scheme.
-
-Other research of note is work by \textbf{M.
-Goodrich \textit{et al.}}\cite{goodrich2006loud} called \textit{Loud and Clear: Human-Verifiable Authentication Based on Audio}.
-As the name suggests, the authors were researching ways to improve current methods of secure device pairing.
-The unique aspect of this work is the use of a Text-to-Speech system reading out syntactically correct English sentences.
-MadLibs\footnote{\url{https://en.wikipedia.org/wiki/Mad\_Libs}} was the base for these sentences.
-MadLibs is where static placeholders are replaced with a member from a list of potential words.\\
-This work is an extension to work performed by \textbf{Juola} and \textbf{Zimmermann}\cite{juola1996whole} as they aimed to emulate the techniques used in PGPfone.
-The paper's findings are limited by the lack of empirical data backing up claims made by the author the performance of the system, and security is only theoretically assessed.
-
-Aside from this research, there have been further informal implementations of fingerprint encodings.
-The first being by \textbf{Michael Rogers}\footnote{\url{https://github.com/akwizgran/basic-english}}.
-Rogers' implementation is a program designed to map fingerprints to pseudo-random poems.
-This implementation was again, empirically evaluated by \textbf{S.
-Dechand \textit{et al.}}\cite{dechand2016empirical}.
-Earlier work by \textbf{N.
-Haller} with the S/KEY\cite{haller1995s} shows the implementation of a system designed to represent a hash as a series of six short words.
-However, this system is designed for a one-time-password purpose and only provides word mappings for basic human usability of the password and not within a fingerprint verification context.
-Therefore, the wordlist has not been designed with pronounceability in mind.
-
-\newpage
-\subsubsection*{Pretty Easy Privacy}
+\subsection{Pretty Easy Privacy}
 \label{sec:pep}
-A very recent implementation of a word list can be found in Pretty Easy Privacy (\pep) implementation of TrustWords\footnote{\url{https://tools.ietf.org/html/draft-birk-pep-trustwords-03}}.
+A very recent implementation of a word list can be found in Pretty Easy Privacy (\pep) implementation of TrustWords\cite{trustwords}.
 \pep is a data encryption system that utilises PGP encryption to provide E2EE on all common channels of communication such as email or SMS.
 The embedded design principles state that above all the systems should be easy to install, use and understand.
-
-\begin{wrapfigure}{r}{6cm}
-    \centering
-    \includegraphics[scale=0.15]{trustwords/trustword_handshake.jpg}
-    \caption{Trustword fingerprint verification}
-    \label{fig:trustwords}
-\end{wrapfigure}
 
@@
 
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.4\textwidth]{trustwords/trustword_handshake.jpg}
+    \caption{Trustword fingerprint verification}
+    \label{fig:trustwords}
+\end{figure}
+
 The unique aspect of TrustWords is its mapping of a single word to 16-bits.
@@
 This deviation from the norm has not been currently backed up by research.
-
-\begin{wrapfigure}[11]{l}{5cm}
-    \centering
-    \begin{BVerbatim}
-    [...]
-52127 ZYGOTE
-52128 ZYGOTIC
-52129 ZYMURGY
-52130 AACHEN
-52131 AARDVARK
-52132 AAREN
-    [...]
-    \end{BVerbatim}
-    \caption{Re-mapping position}
-    \label{fig:remap}
-\end{wrapfigure}
-
-Alongside the abnormally high number of words, the design choice to exclude slang and profanities from the English Trustword dictionary requires dual-mapping of a section of words.
-Approximately 13633/65536 (20.8\%) of words are re-mapped in the dictionary, leaving 51903 unique words.
-The re-mapping is performed on a alphabetical loop.
-Figure \ref{fig:remap} shows the position in the dictionary where this occurs.
-
-\newpage
-
-Moreover, the primary RFC documentation remains in a draft stage and states: \textit{``It is for further study, what minimal number of words (or entropy) should be required.''}.
-These aspects highlight a substantial gap in the current literature.
-
-\subsubsection*{Conclusion}
-
-In conclusion to this topic, the current research has primarily focused on the research and creation of visual representations.
-Research for textual fingerprints is fragmented and incomplete with work \textbf{Juola} and \textbf{Zimmermann}
-\cite{juola1996whole} and \textbf{M.
-Goodrich \textit{et al.}}\cite{goodrich2006loud} providing meaningful research to build upon in terms of word and sentence based encodings.
-The fragmentation of this research leaves room for further work into this topic area.
-Alongside this, findings from the previous section's research show that human language based encodings provided the best usability and, therefore, should be a target for further research looking to improve upon their security and usability.
-
-\subsection{Attacks on encoding schemes}
-This area of research studies ways to physically execute attacks on fingerprint encoding schemes.
-This topic differs from previously examined work due to a central focus on the implementation details of an attack.
-Previous work discussed has only simulated the result of respective attacks.
-Research in this area is scant, with lots of research focusing on the security and prevention of Man-in-the-Middle (MITM) attacks.
-
-Research in 2002 by \textbf{Konrad Rieck}\cite{rieck2002fuzzy} is one the first formalisation of attacks on fingerprint representations.
-The paper titled \textit{``Fuzzy Fingerprints Attacking Vulnerabilities in the Human Brain''} aimed to look into ways users check hexadecimal encoded OpenSSH fingerprint representations.
-The author created an elegant way to `weight' essential chunks of the digest.
-The bytes furthest to the right and left of the digests provided the highest weight.
-This technique provides a way to score digests and determine the best partial collisions found.
-For example, with the target fingerprint: \verb|9F23| and partial match \verb|9313| is given a score of 45\% even though only two characters are matching.
-
-The paper contains an implementation with a ``1.2GHz CPU'' being able to obtain 130,000 H/s (With MD5).
-In comparison to this, a mid-range Intel i5-3320M CPU can today obtain 111,700,000 MD5 H/s.
-This imbalance shows that the results obtained from the paper are significantly outdated.
-However, even with the low hash rate, the author was able to obtain some promising results.
-Figure~\ref{ref:fuzz} contains the best example used.
-
-\begin{figure}[!h]
-    \centering
-    \verb|TARGET: d6:b7:df:31:aa:55:d2:56:9b:32:71:61:24:08:44:87|
-    \verb|MATCH:  d6:b7:8f:a6:fa:21:0c:0d:7d:0a:fb:9d:30:90:4a:87|
-    \caption{Best match obtained after a few minutes of hashing}
-    \label{ref:fuzz}
-\end{figure}
-
-Overall the paper shows an interesting way to create partial fingerprint matches but is not quantified by any empirical evidence gathered on real-world users.
-
-The only other relevant research on this topic is the work by \textbf{M Shirvanian and N. Saxena}\cite{shirvanian2014wiretapping} 
-and their paper: \textit{``Wiretapping via Mimicry: Short 
-Voice Imitation Man-in-the-Middle Attacks on Crypto 
-Phones''}.
-Further research in the area of ``human voice impersonation'' has received lots of attention \cite{mukhopadhyay2015all}\cite{chen2017you}\cite{wu2015spoofing}.
-This paper was chosen over other alternatives due to its specific use of encoding schemes in its evaluation.
-
-In this paper, the authors develop a way to 
-impersonate users when authenticating 
-Short-authentication-Strings (SAS) in the pairing of 
-Crypto-phones. To achieve this impersonation they propose 
-two methods: ``Short voice re-ordering attack'' where an 
-arbitrary SAS string is recreated by re-ordering voice snippets 
-obtained from eavesdropping a previous connection
-and ``Short voice morphing attacks'' whereby the use of 
-previously eavesdropped audio snippets the attacker can
-morph their voice to match that of the victim. With 
-these methods, they aimed to attack encodings of Numbers, 
-PGP word list (previously discussed work by \textbf{Juola} and 
-\textbf{Zimmermann} \cite{juola1996whole}) and MadLib (\textbf{M. Goodrich 
-\textit{et al.}}\cite{goodrich2006loud} work also 
-previously discussed). The effectiveness of these attacks 
-was evaluated with a study involving 30 participants.
-
-Results from the paper show the effectiveness of these 
-methods. Compared to the baseline of the attacker's voice 
-replacing the victim, performed with an $\sim$18\% success rate.
-Morphing gained an overall success rate of 50.58\% and re-ordering a very impressive 78.23\% success rate and showing that these attacks provide an improvement on top of the naive implementation.
-
-One of the most significant limitations addressed by the authors  was the reduction in success rates as the size of the authentication string grew.
-The morphing and re-ordering  attacks become increasingly ineffective as the user had more time to detect imperfections.
-This aspect is not quantified by the author and the extent of this degradation is never empirically discussed.
-Therefore, the results from this study are only effective and applicable in a SAS context.
-
-\subsubsection*{Topic Conclusion}
-Overall the literature for this subtopic remains sparse and incomplete.
-Further suggested work could look into the feasibility of generating partial collisions for all textual representations alongside quantified effectiveness on users.
-With the possibility to concentrate on a few selected implementations.
-The work would aim to focus on the various physical methods used and their feasibility.
-This is one area the previous literature has failed to cover and has only theoretically quantified attacker strength without consideration for the actual real-world cost.
-
-\section{Overall Summary}
-In summary of the literature gaps discovered; encoding scheme performance requires further work focusing on all graphical schemes to corroborate results made by other work.
-Furthermore, there is a gap with the assessment of encoding schemes in the context of "remote-vs-proximity" first proposed by \textbf{M.
-Shirvanian, N.
-Saxena} and \textbf{J.
-J.
-George}\cite{shirvanian2017pitfalls} as it would arguably provide a better simulation of real-world scenarios.
-
-In the context of human demographics and the way they alter the performance of the schemes; further research is required into how the fluency of languages affects authentication ceremony.
-This further work would be a continuation of the initial work by \textbf{H.
-Hsiao \textit{et al.}}\cite{hsiao2009study} and could allow the creation of schemes that are better suited to specific languages.
-Alongside this, there is a research gap in the investigation of how mental impairments affect a schemes performance.
-This aspect is useful due to the number of potential users being affected.
-For example, 7\% of the population have been identified as having dyslexic tendencies\cite{peterson2012developmental}.
-This fact means that with a UK population of around 63,000,000\footnote{From the 2011 Census collated by the Office for National Statistics}  4,410,000 people could benefit from encoding schemes designed to work well with dyslexia.
-Dyslexia, however, is only one of many impairments that could affect a scheme's performance, thus, contributing to the substantial effect further work could have on this area.
-
-Other possible large areas for consideration is the lack of direct consideration for attack strength when assessing the vulnerability of encoding schemes.
-Issues included the previously discussed wide range of attack strength ($2^{28}$ - $2^{242}$) alongside the lack of consideration at all from the majority of papers.
-Moreover, the complete lack of computation and storage complexity considerations means this is a prime area for further research as it would improve the applicability of results.
-
-The final significant research gap identified is the lack of justification for the newly created Trustwords.
-Abnormal design choices (16-bit per word) and its recent creation alongside the shown effectiveness of language-based encodings, such as words makes this a promising area for further research.

### 2019-08-31 Writeup/Paper/sections/design.tex
Changes; - Added inital paper content

--- 2019-08-31 Writeup/Thesis/chapters/design.tex
@@
-\chapter{Design}
-\label{cha:Design}
+\section{Design}
 
-This chapter discusses an overview of the proposed designs for elements required to answer the research questions.
-Alternative solutions are explained when relevant alongside a justification of design choices.
-
-\section{Overall attack design}
+\subsection{Attack Design}
 \label{sec:attackDesign}
-
-The attack on Trustwords involves generating "near-collision" keys. 
-This attempts to provide the base to answer Research Questions \ref{goal:complexity} and \ref{goal:numberOfTrustwords}.
-
-Near-collision keys are keys composed of a set of words that are deemed a match by the phonetic similarity metric (See Section \ref{sec:similarity_metric}).
-
-As each combined key in Trustwords is an exclusive-or of both sides' public-key (Equation \ref{fig:xor_trustwords} shows this process) the attack is designed to target a single pair of users and requires recomputation for every attack target.
-This aspect is considered when discussing the attack feasibility.
+The attack on Trustwords involves generating ``near-collision'' keys. Near-collision keys are keys composed of a set of words that are deemed a match by the similarity metric.
+\\\\
+As each combined key in Trustwords is an exclusive-or of both sides' public-key the attack is designed to target a single pair of users and requires recomputation for each attack target.
 Each pair is split into an "Uncontrolled" or "Controlled" key.
@@
 It is assumed that there is the ability to replace the Controlled key with the malicious option.
-These descriptions are the terminology used throughout the paper.
-However, the uncontrolled and controlled keys can be swapped around with the ability to compute both directions.
-Thus, resulting in the possibility to intercept both directions of communication.
-This, however, requires performing the attack separately for both directions.
-
-\begin{equation}
-    KeyFingerprint_{1} \oplus KeyFingerprint_{2} = TrustwordsFingerprint
-\end{equation}
-\label{fig:xor_trustwords}
-
+The uncontrolled and controlled keys can be swapped around, thus, resulting in the possibility to intercept both directions of communication.
+This, however, requires performing the attack twice.
+\\\\
 When attacking, a similarity metric is used to compute a list of possibilities for each position in the target fingerprint.
-
-Figure \ref{fig:nearMatch} shows the process of generating a subsection of the combinations.
-A list of each words' matches is generated and combined to create the comprehensive list of near-collision keys.
-
-\begin{figure}[h!]
-    \centering
-    \begin{BVerbatim}[commandchars=\\\{\}]
-        \centering
-\textbf{ CHOKE BLUSHING FRIGHTENING HAND}
-    \end{BVerbatim}
-    \\
-    \verb|COKE                           |
-    \\
-    \verb|SMOKE                          |
-    \\
-    \hspace{1cm}
-
-    \verb|CHOKE                          |
-    \\
-    \begin{BVerbatim}[commandchars=\\\{\}]
-\textbf{COKE BLUSHING FRIGHTENING HAND}
-    \end{BVerbatim}
-    \\
-    \verb|SMOKE                          |
-    \\
-    \hspace{1cm}
-
-    \verb|CHOKE                          |
-    \\
-    \verb|COKE                           |
-    \\
-    \begin{BVerbatim}[commandchars=\\\{\}]
-        \centering
-\textbf{ SMOKE BLUSHING FRIGHTENING HAND}
-    \end{BVerbatim}
-    \caption{Visualisation of the generation of near matches}
-    \label{fig:nearMatch}
-\end{figure}
-
 Completing these steps produces a list of fingerprints that can be inserted into a tool designed to hash a large number of keys and search for matches.
@@
 
-\section{Similarity metrics}
-\label{sec:metrics}
-One of the first requirements for the attack is quantifying "phonetic similarity." This section is looking to provide an answer for Research Question \ref{goal:phoneticSimilarity}.
-There are many algorithms currently available to provide this functionality.
-This section describes and explains the reasons they were selected for assessment later in the project.
-
-\subsection{Soundex}
-Soundex is one of the most famous example of a phonetic algorithm (See Section \ref{sec:soundex}).
-This is due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}.
-
-Soundex, however, has had extensive work focused on its own deficiencies alongside quantification of its performance under certain conditions.
-However, even with these previously discussed issues, its algorithmic simplicity and popularity allows it to remain relevant for assessment in this project.
-
-\subsection{NYSIIS}
-NYSIIS primary use case was the matching of common names present in a database (See Section \ref{sec:nysiis}).
-However, due to it having embedded rules to handle word phonetics, it would again be applicable in this application.
-
-Due to NYSIIS's aforementioned use in a professional setting alongside its high occurrence in literature, it was deemed suitable as one of the selected similarity metrics.
-
-\subsection{Metaphone}
-Metaphone, as discussed in Section \ref{sec:metaphone} is another famous phonetic algorithm.
-Metaphone is arguably on the same level of ubiquity as that of Soundex with it finding itself implemented in languages such as PHP\cite{php}.
-Metaphone was chosen due to similar reasons to that of Soundex and NYSIIS.
-
-Further work would involve the implementation of newer versions of Metaphone. Double Metaphone (2000) and
-Metaphone 3 (2009) that claim to improve over the original version.
-
-\subsection{Levenshtein Distance}
-As explained in Section \ref{sec:leven}, Levenshtein Distance is the number of whole character edits.
-Levenshtein distance is not technically designed as a phonetic algorithm, but due to similar-sounding words often being spelt in similar ways\cite{hettiarachchi2012sparcl}, the use-case of this algorithm remains relevant.
-Alongside this, Levenshtein is also the most algorithmically simplistic of all the considered options.
-These aspects, therefore, contribute to Levenshtein's inclusion in the chosen set.
-
-\subsection{Phonetic Vectors}
-As discussed in Section \ref{sec:phonetic_vectors}, the metrics ability to perform operations and measure dissimilarity allows for a plethora of applications.
-One possible application of note would be the creation of a wordlist where the phonetic difference (vector distance) is maximised.
-This application, if the vector mapping is an accurate representation, could allow the creation of a phonetically distinctive wordlist.
-Therefore, these unique aspects contribute to the inclusion of this metric in the set.
-
-\section{Alternative Similarity Metrics}
-
-\subsection{Match Rating Approach}
-Matching Rating Approach (MRA) is another algorithm designed to match names within a database; therefore, its operation can be grouped with that of NYSIIS and Soundex.
-MRA was discarded as an option.
-This removal of this metric is due to the lack of known utilisation in any substantial real-world use-cases alongside its similarity to  more established algorithms like Soundex and NYSIIS.
-
-Further work could compare this algorithm to similar alternatives in phonetically matching of words to quantify performance. This further work is discussed in the evaluative sections of the report.
-
-\subsection{Caverphone}
-Another notable alternative solution is that of Caverphone that was designed in New Zealand.
-Caverphone, as is the case with the vast majority of phonetic algorithms, was designed for use with name matching.
-Caverphone was not chosen to similar reasons to that of MRA alongside its optimisation for the New Zealand dialect.
-Therefore, the low level of utilisation alongside the unique design features contributed to its exclusion.
-However, this has not been assessed empirically and thus would be a candidate for further work.
-
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{ll}
-        Metric & Output \\
-        \hline    
-        Soundex & T614 \\
-        NYSIIS & TRAVAL\\
-        Metaphone & TRFL\\
-        Caverphone & TRF111\\
-        MRA & TRVL
-    \end{tabular}
-    \caption{The various phonetic encodings of the word "Travel"}
-\end{table}
-
-\section{Design of GreenOnion}
-\label{sec:greenDesign}
-In order to answer Research Questions \ref{goal:complexity} fully, it is necessary to implement a tool to generate working keys.
+\subsection{GreenOnion Design}
 
@@
 OpenCL allows the creation of code chunks referred to as "kernels" to be executed concurrently, this provides a massive speed increase compared to the sequential nature of the CPU.
-Technical details are explained further in Chapter \ref{cha:Implementation}.
-
-\section{Experiment Design}
-To answer some of the research questions, empirical evidence is required. In this section, the designs and considerations of the chosen experiments are discussed.
-
-\subsection{Metric performance}
-\label{exp:metric}
-This section aims to assist in answering Research Question \ref{goal:phoneticSimilarity}.
-To reduce the number of metrics to assess in the later rounds, the performance of similarity metrics required comparison.
-The thinning out of metrics is required due to limited resources.
-Therefore, possible further work could involve repeating this work with a much more varied selection of metrics.
-As explained in a previous section (See Section \ref{sec:metrics}) the chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors.
-
-The design for the experiment involves assessing the quality of the metrics matches by having participants rate them on a scale of 1 (Very different sound) to 5 (Very similar sound).
-
-\subsubsection{Matches}
-\label{sec:matches}
-
-A match for each code based metric (Soundex, Metaphone and NYSIIS) occurs when the codes are identical.
-However, for the other cases where the difference is variable other ways of defining a match are required.
-
-In the case of Levenshtein values of similarity are discrete due to it being the number of single-character edits.
-Therefore, this requires less deliberation.
-Match size was used as a way to decide on a cut-off point.
-Match size is the number of matches determined by the metric on the English version of the Trustword dictionary (51903 unique words).
-
-\begin{table}[h!]
-    \centering
-    \input{tables/design/match_size_leven.tex}
-    \caption{Levenshtein's number of matches comparison}
-    \label{tab:matchSize}
-\end{table}
-
-As can be seen from Table \ref{tab:matchSize}, the number of matches for L2 is more significant than all metrics excluding Soundex.
-As the issues with Soundex have been discussed in previous sections (See Section \ref{sec:soundex}), it can be excluded as an abnormality in this context.
-Therefore, due to the excessively high value for a L2, L1 was chosen as the Levenshtein cap for defining a match.
-
-Match size was also used to define the threshold for the phonetic vectors.
-The decision is less apparent than that of Levenshtein due to the continuous nature of the distance between two vectors.
-However, the complexity was reduced by limiting it to increments of 0.5.
-
-\begin{table}[h!]
-    \centering
-    \input{tables/design/match_size_wordvec.tex}
-    \caption{Phonetic vector number of matches comparison}
-    \label{tab:vectorMatchSize}
-\end{table}
-
-Table \ref{tab:vectorMatchSize} contains the match size comparison for Phonetic vectors distance.
-Distance 4.5 was chosen as a suitable size due to the total matches fitting well within the other metrics.
-Distance 4.0 was the other alternative; this was discarded due to its small size.
-Any metric with a number of matches below 100,000 results in an inadequate number of possible near-collision keys later in the process, a lower number of matches may imply better quality, but a balance is required between computational cost and attack quality.
-This is discussed in more detail in later chapters.
-
-\subsubsection{Comparisons}
-\label{sec:exp1_comparison}
-Each comparison contains a match-pair.
-These matches are generated by running the similarity metric over all the pairings in the Trustword dictionary; if the pair meets the criteria discussed in the previous section, it is determined a match.
-Potential matches are then sampled from their respective lists.
-
-Each participant is then asked to rate the similarity of a match on a scale of 1 (\textit{`Very different sound'}) and 5 (\textit{`Very similar sound'}).
-Figure \ref{fig:phoneticMatch} shows an example match and the connected scale.
-Users are provided with five of these comparisons per similarity metric.
-
-\begin{figure}[h!]
-    \centering
-    \fbox{
-        \includegraphics[width=\textwidth]{experiment/experiment_match.png}
-    }
-    \caption{Example experiment question}
-    \label{fig:phoneticMatch}
-\end{figure}
-
-The experiment randomises the order of these comparisons per session alongside a complete refreshing of matches once per submission.
-This design makes sure selections from the samples are fair and consistent as each user has a different selection of matches.
-
-\subsubsection{Quality control}
-\label{sec:exp1_qualitycontrol}
-As the study was being outsourced to Amazon's Mechanical Turk, the requirement to check the quality of results is essential.
-Therefore, a couple of additions were provided to check a result's validity.
-
-The first was the addition of five "Random matches" questions.
-These are matches consisting of two random words selected from the dictionary.
-Therefore, the expected average rating of these words should be close to one.
-This design allows for a simple check for valid results.
-If their average rating for Random matches is too high, their results are discarded.
-
-\begin{figure}[h!]
-    \centering
-    \fbox{
-        \includegraphics[width=\textwidth]{experiment/exact_experiment_match.png}
-    }
-    \caption{Exact experiment attention question}
-    \label{fig:exactMatch}
-\end{figure}
-
-Alongside this, was the addition of two questions comparing precisely the same word.
-As both words are the same, the result should always be a full 5/5 rating, any results without a full rating are discarded.
-Figure \ref{fig:exactMatch} contains one example of the attention question used to filter inaccurate results.
-
-The final check to ensure the validity of results is a check for native English fluency. Having non-native English speakers complete the 
-experiment can introduce inconsistencies into the 
-data and, therefore, needs to remain controlled. To achieve this, a preliminary MTurk study has been created to ask users for their perceived 
-English fluency on a scale of 1 (Basic Understanding) to 5 (Native). 
-Workers with an answer of 5 are provided with a 
-Qualification\footnote{\url{https://blog.mturk.com/tutorial-understanding-requirements-and-qualifications-99a26069fba2}} 
-that tags them as defining themselves as native speakers. This qualification is then 
-added as a prerequisite when running the experiment. This prerequisite ensures 
-only fully native speakers are being assessed. The possibility of the 
-worker falsely stating their level of fluency has also been considered. 
-However, as the worker does not know the purpose of this initial study,
-thereby providing inaccurate results has no real valid motive for the 
-worker.
-
-\subsubsection{Considerations}
-\label{sec:exp1_considerations}
-
-The first consideration is the way the words are compared.
-Due to the assumed context of authentication being phone-based, the comparison of words is a mixture of auditory and visual.
-The user hears their authentication partner read their set of words (Auditory) and compare to their set of words (Visual).
-This experiment asks users to compare the sound of two words that are visually displayed to them.
-This visual aspect is the first point of contact between the participant and the question, followed by a mental comparison of the phonetics of the word.
-Therefore, this initial visual contact has the potential to bias the results of the study.
-Levenshtein has the potential to be most affected by this due to the matches never being more than one character different, therefore, resulting in very similar-looking words.
-The alternative method of running this experiment is to get users to compare audio samples of words; this forces the user to compare just the phonetics of the words and not be influenced by the visual aspects of the pair.
-However, this adds a substantial cost to the operation of the study.
-Due to the aforementioned lack of resources, the chosen design was decided as most feasible as it is a balance between cost and accuracy.
-Further work, therefore, could improve by producing more conclusive results on the performance of the metrics by implementing the more accurate but costly alternative.
-
-Another consideration is the demographics of people accessible on Mechanical Turk.
-A comprehensive and still active survey run by \textbf{D.
-Difallah, E.
-Filatova} and \textbf{P.
-Ipeirotis}\cite{difallah2018demographics} shows that MTurk workers are younger and have a more substantial household income than that of the US population.
-This deviation has to be taken into consideration when interpreting the results because it has to potential to introduce a bias.
-
-\newpage
-
-\subsection{Trustword Attacks}
-\label{sec:exp2_design}
-
-This experiment is designed to be a simulation of the attack proposed in Section \ref{sec:attackDesign} in an attempt to answer Research Question \ref{goal:attackPercentage}.
-The experiment tests the simulated matches of three similarity metrics decided by the previous experiment (See Section \ref{sec:metrics}).
-The overall aim of the experiment is to quantify the success rate of the attack on live participants.
-The user is presented with the same design as the \pep Android application (See Section \ref{sec:pep}).
-
-Appendix \ref{appendix:trustword_attack} shows the design of the experiments front end\footnote{A live version can also be viewed at the url: \url{https://afray.pythonanywhere.com/}}.
-As can be seen by comparing it to Figure \ref{fig:trustwords}, it has been designed to be as close as possible to the actual application.
-The blue button is clicked to simulate the authentication ceremony over the phone.
-A text-to-speech system then reads a set of words and the user should accept if they match and decline if they don't.
-
-\subsubsection{Design}
-
-Due to the scarcity of attacks in a real-world setting, users are often complacent about their occurrence.
-Therefore, in this experiment, attacks only occur 30\% of the time.
-This occurrence is a much higher value than in a real-world setting but is a balance between resources and realistic design.
-If the chosen attack rate is too low, many more trials are required to collate a useful number of attack instances, thus, requiring more resources, but with more realism.
-If, however, the attack rate is too high, less total rounds are required to obtain the target number of attack trails.
-However, the user's complacency is lost as an attack is expected.
-This loss of complacency is undesirable as it does not realistically reflect real life.
-Furthermore, the first 5 trials of a new experiment are always benign.
-This inclusion is to ensure users are consistently lulled into complacency.
-
-Certain keys have higher levels of potential near-collision keys than others due to how certain words are deemed similar by the similarity metric.
-Therefore, this presents the possibility to have keys with a deficient number of possible near-collision keys.
-The distribution of these keys is explained further in Chapter \ref{cha:Experiments}.
-Therefore, if random sets of words are chosen with no restraints, there are attacks presented to the user that in a real setting would be infeasible as they are close to a $2^{64}$ attack (4 Words * 16-bits).
-Therefore, the experiment is designed to sample from a list of "vulnerable" keys.
-These are keys that have a number of potential near-collision keys that allow computation in a specified timeframe.
-
-Furthermore, certain levels of attacks are also simulated. Below is the list of attacks considered in this experiment:
-
-\begin{itemize}
-    \item (\OOOO) All words in the set can vary             
-    \item (\XOOO) All but the first word can vary           
-    \item (\XOOX) All but the first and last word can vary  
-\end{itemize}
-
-$Where: $
-\begin{itemize}
-    \item[] \verb|X|: is a static word
-    \item[] \verb|O|: is a changeable word
-\end{itemize}
-
-The start and ends were chosen as the highest priority words to keep static.
-This design choice is due to research highlighting the common habit of users only to check the start and end of a checksum.
-\cite{cherubini2018towards} shows this by measuring user eye movement and displaying it as a heat map.
-
-\begin{figure}[h!]
-    \centering
-    \fbox{
-        \parbox{\textwidth}{
-            \includegraphics[width=\textwidth]{experiment/checksum_check.png}
-
-            \includegraphics[width=\textwidth]{experiment/checksum_check_2.png}
-        }
-    }
-    \caption{Failed verification of an incorrect checksum\cite{cherubini2018towards}}
-    \label{fig:heatMap}
-\end{figure}
-
-Figure \ref{fig:heatMap} shows the results of an eye-tracking experiment where the user failed to detect a mismatching digest. As can be seen, the users never compared the centre of the digest.
-
-However, this may not be applicable in this context due to the user being linearly fed an audio stream that they cannot skip to the start or end.
-We believe, however, that attention also plays a part in defining the most important areas of comparison.
-The hypothesis is that the users' attention is lower in the middle sections of comparison, where it peaks at the start and end.
-All of these aspects require empirical evidence to conclude.
-Therefore, this requires consideration when assessing the results of the experiment.
-
-These attacks are ascending in complexity.
-The timeframe for computing a near-collision was decided as one week with attack strengths of 7 GPU-days \textit{(1 x GPU)}, 70 GPU-days \textit{(10 x GPUs)} and 700 GPU-days \textit{(100 x GPUs)} on a mid-range GPU (AMD RX 480).
-Due to the long lifetime of PGP keys, 7 days was chosen as a reasonable length of the attack.
-The tool requires no user interaction once started, therefore, it can be left for an extended period to compute potential keys.
-This timeframe is also a maximum time, as these attacks also include keys that have a shorter average computation time.
-
-\begin{table}[h!]
-    \centering
-    \input{tables/design/attack_types.tex}
-    \caption{Summary of attack requirements}
-    \label{tab:attackReq}
-\end{table}
-
-Table \ref{tab:attackReq} contains a summary of the different level of attacks and their respective restrictions.
-More potential near-collision keys make the attack search quicker.
-Any key that exceeds the defined numbers of potential near-collision key for attack level is deemed as vulnerable.
-As discussed in Section \ref{sec:attackDesign}, the near-collision keys are close keys produced from the similarity-metric's matches.
-A list of these vulnerable keys is sampled from when an attack is simulated.
-The percentage of vulnerable keys is explored in Chapter \ref{cha:Experiments}.
-
-\subsubsection{Quality control}
-\label{sec:exp2_quality}
-Like the previous experiment, participants are sourced from MTurk.
-Therefore, again, quality control is an aspect that requires consideration.
-As with the previous study, initially screened native speakers are used.
-Alongside this, two metrics are used to detect invalid results: audio-button-clicks and the overall-time.
-
-Audio-buttons-clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:expID} is clicked.
-If there are rounds without button clicks, this is a sign of non-attentiveness.
-The design choice was made to allow non-clicks as an attention check.
-This design provides a way to detect and discard click-throughs\footnote{Workers that aim to complete the task as fast as possible, with no regard for the quality of responses}.
-
-Overall-time is as the name suggest a recording of the time taken to complete the entire experiment.
-If users complete the experiment in an abnormally small amount of time, it can be used as another detection for invalid responses.
-A benchmark for the time is set by completing the experiment as fast as possible.
-Anything quicker was discarded as anything faster risks invalid and rushed results.
-
-\subsubsection{Considerations}
-As with the previous experiment, sampling from MTurk's demographic results in a collection of participants that are not reflective of the general population.
-Due to the attack context of this experiment, it can be assumed that the youth of the participants contributes to less successful attacks.
-Therefore, the results generated by this experiment can be loosely assumed as a best-case scenario for the scheme.
-We predict a high attack success rate if assessed over the general population.

### 2019-08-31 Writeup/Paper/sections/discussion.tex
Changes; - Added inital paper content

--- 2019-08-31 Writeup/Thesis/chapters/evaluation.tex
@@
-\chapter{Conclusions}
-This chapter collates the findings of the paper, evaluates the paper's success against the research questions and discusses potential further work.
+\section{Discussion and Further Work}
 
-\section{Research Question \ref{goal:phoneticSimilarity}}
-
-Research Question 1 asks: \textit{“What are the best performing schemes to quantify phonetic similarity?”}.
-This paper has discussed several metrics used to quantify phonetic similarity (See Section \ref{sec:metrics}).
-Most metrics were chosen due to their high utilization and occurrence in literature.
-The only exception to this is the presence of Phonetic Vectors.
-Performance of these metrics were then quantified in a direct study that selected the top three from a set of five (See Section \ref{exp:metric}).
-These newly selected metrics was then assessed in an attack context with their performance being indirectly quantified (See Section \ref{sec:exp2_design}).
-
-The top three metrics (in descending order) were: Levenshtein, NYSIIS and Metaphone.
-We found that Levenshtein was the most aligned with how people rate phonetical similarity.
-Levenshtein had a considerable proportion of 4 and 5 ratings (64\%) compared to the alternatives.
-Levenshtein was also the best performer in the attack context with it having the highest success rate.
-This corroborates work showing that words with similar spelling tend to share phonetic similarity \cite{hettiarachchi2012sparcl}.
-Alongside this, we found Soundex was the least aligned with the human model of similarity with an average rating of just 2 out of 5.
-This also corroborates findings that highlighted significant issues with the accuracy of Soundex’s phonetic representation (See Section \ref{sec:soundex}).
-
-We believe the outcome of the first experiment were inflated by the way the results were presented (as discussed in Section \ref{sec:exp1_considerations}).
-However, as the performance of the metrics in the second experiment emulated the first with Levenshtein being the best performer alongside Metaphone being the worst, shows that the results of the first study maintain a desirable level of accuracy.
-Improvements can be made with the proposed design discussed in Section \ref{sec:exp1_considerations}, but, we believe the first experiment has achieved its goal of providing a low-cost way to reduce the number of selected metrics for the subsequent study.
-
-\section{Research Question \ref{goal:complexity}}
-Research Question \ref{goal:complexity}: \textit{``What is the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project alongside the actual generation of keys as shown in Section \ref{sec:key_gen}.
-Furthermore, the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}.
-To achieve this, the tool GreenOnion was developed.
-Inspiration for GreenOnion was gathered from a currently available tool known as Scallion.
-Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can concurrently search for.
-GreenOnion is able to handle in excess of 1.5 million keys.
-This capability is in comparison to the maximum of 2513 keys the alternative; Scallion can compare.
-We believe this is due to the implementation of the bloom filter.
-Its unique characteristics of $O(k)$ complexity regardless of the number of elements in the structure allows a huge number of concurrent checks to occur.
-
-\section{Research Question \ref{goal:attackPercentage}}
-Research Question \ref{goal:attackPercentage} \textit{``What percentage of attacks successfully deceive a user?''} was shown by the results presented in Section \ref{sec:exp2}.
-The weakest attack strength and ones that can be computed by a single mid-range GPU for a single week achieved success rate ranging from 9.35\% - 11.01\%.
-The middle attack involving the use of 10 mid-range GPUs for a week had success rates of 15.20\% - 19.20\%.
-Finally, the highest attack strength that theoretically involved the use of 100 mid-range GPUs computing for a week has success rates: 24.43\% - 32.05\%.
-Therefore, showing the number of attacks required to deceive a set of users.
-
-\section{Research Question \ref{goal:numberOfTrustwords}}
-Research Question \ref{goal:numberOfTrustwords} states \textit{`` Is the recommended minimum number of four Trustwords enough to provide a basic level of security?''}.
-The paper has investigated this through the creation of an attack and quantification of its success on actual participants.
-Findings have shown that an attack computed in half a day can have a success rate of about 9.35\%.
-A user, therefore, could initiate this attack on-mass with hardware present inside the average gaming computer.
-On the other hand, the best level of attack success was shown to be 32.05\%.
-
-Furthermore, comparison of these results to similar literature shows a considerable increase in success rates for the attack present in this paper.
-We believe this is due to the consideration of `similarity' when forming attacks.
-This was an aspect missing from the literature.
-We also believe the effect of considering similarity is further enhanced due to the  weaknesses present in Trustwords such as homophones, dual mappings and the wordlist size.
-Therefore, we believe that four Trustwords as a minimum has not provided a basic level of security towards users.
-
-\section{Further work}
+\subsection{Further work}
 
@@
 
-\section{Final Remarks}
+\subsection{Conclusion}
 Overall, the project has demonstrated a potential attack on \pep's implementation of Trustwords.

### 2019-08-31 Writeup/Paper/sections/experimental_design.tex
Changes; - Added inital paper content

--- 2019-08-31 Writeup/Thesis/chapters/design.tex
@@
-\chapter{Design}
-\label{cha:Design}
-
-This chapter discusses an overview of the proposed designs for elements required to answer the research questions.
-Alternative solutions are explained when relevant alongside a justification of design choices.
-
-\section{Overall attack design}
-\label{sec:attackDesign}
-
-The attack on Trustwords involves generating "near-collision" keys. 
-This attempts to provide the base to answer Research Questions \ref{goal:complexity} and \ref{goal:numberOfTrustwords}.
-
-Near-collision keys are keys composed of a set of words that are deemed a match by the phonetic similarity metric (See Section \ref{sec:similarity_metric}).
-
-As each combined key in Trustwords is an exclusive-or of both sides' public-key (Equation \ref{fig:xor_trustwords} shows this process) the attack is designed to target a single pair of users and requires recomputation for every attack target.
-This aspect is considered when discussing the attack feasibility.
-Each pair is split into an "Uncontrolled" or "Controlled" key.
-Uncontrolled is the receiver of the communication, and, thus, the key cannot be altered.
-The Controlled key is the one we are attempting to impersonate.
-It is assumed that there is the ability to replace the Controlled key with the malicious option.
-These descriptions are the terminology used throughout the paper.
-However, the uncontrolled and controlled keys can be swapped around with the ability to compute both directions.
-Thus, resulting in the possibility to intercept both directions of communication.
-This, however, requires performing the attack separately for both directions.
-
-\begin{equation}
-    KeyFingerprint_{1} \oplus KeyFingerprint_{2} = TrustwordsFingerprint
-\end{equation}
-\label{fig:xor_trustwords}
-
-When attacking, a similarity metric is used to compute a list of possibilities for each position in the target fingerprint.
-
-Figure \ref{fig:nearMatch} shows the process of generating a subsection of the combinations.
-A list of each words' matches is generated and combined to create the comprehensive list of near-collision keys.
-
-\begin{figure}[h!]
-    \centering
-    \begin{BVerbatim}[commandchars=\\\{\}]
-        \centering
-\textbf{ CHOKE BLUSHING FRIGHTENING HAND}
-    \end{BVerbatim}
-    \\
-    \verb|COKE                           |
-    \\
-    \verb|SMOKE                          |
-    \\
-    \hspace{1cm}
-
-    \verb|CHOKE                          |
-    \\
-    \begin{BVerbatim}[commandchars=\\\{\}]
-\textbf{COKE BLUSHING FRIGHTENING HAND}
-    \end{BVerbatim}
-    \\
-    \verb|SMOKE                          |
-    \\
-    \hspace{1cm}
-
-    \verb|CHOKE                          |
-    \\
-    \verb|COKE                           |
-    \\
-    \begin{BVerbatim}[commandchars=\\\{\}]
-        \centering
-\textbf{ SMOKE BLUSHING FRIGHTENING HAND}
-    \end{BVerbatim}
-    \caption{Visualisation of the generation of near matches}
-    \label{fig:nearMatch}
-\end{figure}
-
-Completing these steps produces a list of fingerprints that can be inserted into a tool designed to hash a large number of keys and search for matches.
-This aspect of using an extensive list to search for keys massively reduces the complexity of the search.
-
-In summary, the attack steps are:
-
-\begin{enumerate}
-    \item Compute all possible matches using a similarity metric on all words in a dictionary (Only needs performing once).
-
-    \item Select a target and allocate "Uncontrolled" and "Controlled" key identification.
-
-    \item Calculate all permutations of near-collisions for the key pair and produce a list of near-collision key fingerprints.
-
-    \item Use a list of near-collision keys in the mass computation of keys to find near-collision keys.
-
-\end{enumerate}
-
-\section{Similarity metrics}
-\label{sec:metrics}
-One of the first requirements for the attack is quantifying "phonetic similarity." This section is looking to provide an answer for Research Question \ref{goal:phoneticSimilarity}.
-There are many algorithms currently available to provide this functionality.
-This section describes and explains the reasons they were selected for assessment later in the project.
-
-\subsection{Soundex}
-Soundex is one of the most famous example of a phonetic algorithm (See Section \ref{sec:soundex}).
-This is due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}.
-
-Soundex, however, has had extensive work focused on its own deficiencies alongside quantification of its performance under certain conditions.
-However, even with these previously discussed issues, its algorithmic simplicity and popularity allows it to remain relevant for assessment in this project.
-
-\subsection{NYSIIS}
-NYSIIS primary use case was the matching of common names present in a database (See Section \ref{sec:nysiis}).
-However, due to it having embedded rules to handle word phonetics, it would again be applicable in this application.
-
-Due to NYSIIS's aforementioned use in a professional setting alongside its high occurrence in literature, it was deemed suitable as one of the selected similarity metrics.
-
-\subsection{Metaphone}
-Metaphone, as discussed in Section \ref{sec:metaphone} is another famous phonetic algorithm.
-Metaphone is arguably on the same level of ubiquity as that of Soundex with it finding itself implemented in languages such as PHP\cite{php}.
-Metaphone was chosen due to similar reasons to that of Soundex and NYSIIS.
-
-Further work would involve the implementation of newer versions of Metaphone. Double Metaphone (2000) and
-Metaphone 3 (2009) that claim to improve over the original version.
-
-\subsection{Levenshtein Distance}
-As explained in Section \ref{sec:leven}, Levenshtein Distance is the number of whole character edits.
-Levenshtein distance is not technically designed as a phonetic algorithm, but due to similar-sounding words often being spelt in similar ways\cite{hettiarachchi2012sparcl}, the use-case of this algorithm remains relevant.
-Alongside this, Levenshtein is also the most algorithmically simplistic of all the considered options.
-These aspects, therefore, contribute to Levenshtein's inclusion in the chosen set.
-
-\subsection{Phonetic Vectors}
-As discussed in Section \ref{sec:phonetic_vectors}, the metrics ability to perform operations and measure dissimilarity allows for a plethora of applications.
-One possible application of note would be the creation of a wordlist where the phonetic difference (vector distance) is maximised.
-This application, if the vector mapping is an accurate representation, could allow the creation of a phonetically distinctive wordlist.
-Therefore, these unique aspects contribute to the inclusion of this metric in the set.
-
-\section{Alternative Similarity Metrics}
-
-\subsection{Match Rating Approach}
-Matching Rating Approach (MRA) is another algorithm designed to match names within a database; therefore, its operation can be grouped with that of NYSIIS and Soundex.
-MRA was discarded as an option.
-This removal of this metric is due to the lack of known utilisation in any substantial real-world use-cases alongside its similarity to  more established algorithms like Soundex and NYSIIS.
-
-Further work could compare this algorithm to similar alternatives in phonetically matching of words to quantify performance. This further work is discussed in the evaluative sections of the report.
-
-\subsection{Caverphone}
-Another notable alternative solution is that of Caverphone that was designed in New Zealand.
-Caverphone, as is the case with the vast majority of phonetic algorithms, was designed for use with name matching.
-Caverphone was not chosen to similar reasons to that of MRA alongside its optimisation for the New Zealand dialect.
-Therefore, the low level of utilisation alongside the unique design features contributed to its exclusion.
-However, this has not been assessed empirically and thus would be a candidate for further work.
-
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{ll}
-        Metric & Output \\
-        \hline    
-        Soundex & T614 \\
-        NYSIIS & TRAVAL\\
-        Metaphone & TRFL\\
-        Caverphone & TRF111\\
-        MRA & TRVL
-    \end{tabular}
-    \caption{The various phonetic encodings of the word "Travel"}
-\end{table}
-
-\section{Design of GreenOnion}
-\label{sec:greenDesign}
-In order to answer Research Questions \ref{goal:complexity} fully, it is necessary to implement a tool to generate working keys.
-
-The inspiration for the design of this tool was taken from a tool called Scallion\footnote{\url{https://github.com/lachesis/scallion}}.
-Scallion was designed by Richard Klafter and Eric Swanson and was used to demonstrate that 32-bit PGP key IDs were insufficient.
-To keep with the onion-based theme, the proposed tool is called `GreenOnion' and is a re-write of Scallion in C++.
-This language was chosen due to the well-understood efficiency benefits.
-The proposed tool differs from Scallion, most notably in its ability to concurrently search for a large number of keys, GreenOnion improves on this substantially.
-More implementation and experimental details are discussed in later chapters.
-
-The tool should take two keys as parameters (Uncontrolled/Controlled) and a chosen similarity metric and produce a list of target key fingerprints.
-This list is then used as a search criterion when searching for keys.
-To utilise the parallel nature of the GPU to compute the hash of a large number of keys, the tool utilises a GPGPU (General-purpose computing on graphics processing units) framework.
-The chosen framework was OpenCL due to its support for the chosen language (C++) and platform (Linux).
-OpenCL allows the creation of code chunks referred to as "kernels" to be executed concurrently, this provides a massive speed increase compared to the sequential nature of the CPU.
-Technical details are explained further in Chapter \ref{cha:Implementation}.
-
-\section{Experiment Design}
-To answer some of the research questions, empirical evidence is required. In this section, the designs and considerations of the chosen experiments are discussed.
+\section{Experimental Design}
 
 \subsection{Metric performance}
-\label{exp:metric}
-This section aims to assist in answering Research Question \ref{goal:phoneticSimilarity}.
-To reduce the number of metrics to assess in the later rounds, the performance of similarity metrics required comparison.
+This experiment aims to reduce the number of metrics to assess in the later rounds.
 The thinning out of metrics is required due to limited resources.
 Therefore, possible further work could involve repeating this work with a much more varied selection of metrics.
-As explained in a previous section (See Section \ref{sec:metrics}) the chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors.
-
+The chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors.
+\\\\
 The design for the experiment involves assessing the quality of the metrics matches by having participants rate them on a scale of 1 (Very different sound) to 5 (Very similar sound).
 
-\subsubsection{Matches}
-\label{sec:matches}
-
-A match for each code based metric (Soundex, Metaphone and NYSIIS) occurs when the codes are identical.
-However, for the other cases where the difference is variable other ways of defining a match are required.
-
-In the case of Levenshtein values of similarity are discrete due to it being the number of single-character edits.
-Therefore, this requires less deliberation.
-Match size was used as a way to decide on a cut-off point.
-Match size is the number of matches determined by the metric on the English version of the Trustword dictionary (51903 unique words).
-
-\begin{table}[h!]
-    \centering
-    \input{tables/design/match_size_leven.tex}
-    \caption{Levenshtein's number of matches comparison}
-    \label{tab:matchSize}
-\end{table}
-
-As can be seen from Table \ref{tab:matchSize}, the number of matches for L2 is more significant than all metrics excluding Soundex.
-As the issues with Soundex have been discussed in previous sections (See Section \ref{sec:soundex}), it can be excluded as an abnormality in this context.
-Therefore, due to the excessively high value for a L2, L1 was chosen as the Levenshtein cap for defining a match.
-
-Match size was also used to define the threshold for the phonetic vectors.
-The decision is less apparent than that of Levenshtein due to the continuous nature of the distance between two vectors.
-However, the complexity was reduced by limiting it to increments of 0.5.
-
-\begin{table}[h!]
-    \centering
-    \input{tables/design/match_size_wordvec.tex}
-    \caption{Phonetic vector number of matches comparison}
-    \label{tab:vectorMatchSize}
-\end{table}
-
-Table \ref{tab:vectorMatchSize} contains the match size comparison for Phonetic vectors distance.
-Distance 4.5 was chosen as a suitable size due to the total matches fitting well within the other metrics.
-Distance 4.0 was the other alternative; this was discarded due to its small size.
-Any metric with a number of matches below 100,000 results in an inadequate number of possible near-collision keys later in the process, a lower number of matches may imply better quality, but a balance is required between computational cost and attack quality.
-This is discussed in more detail in later chapters.
-
-\subsubsection{Comparisons}
-\label{sec:exp1_comparison}
+\subsubsection*{Comparisons}
 Each comparison contains a match-pair.
@@
     \centering
+    \begin{adjustbox}{width=0.5\textwidth,center}
         \fbox{
@@
         }
+    \end{adjustbox}
     \caption{Example experiment question}
@@
 
-\subsubsection{Quality control}
+\subsubsection*{Quality control}
 \label{sec:exp1_qualitycontrol}
@@
 
+Alongside this, was the addition of two questions comparing precisely the same word.
+As both words are the same, the result should always be a full 5/5 rating, any results without a full rating are discarded.
+Figure \ref{fig:exactMatch} contains one example of the attention question used to filter inaccurate results.
+
 \begin{figure}[h!]
     \centering
+    \begin{adjustbox}{width=0.5\textwidth,center}
         \fbox{
@@
         }
+    \end{adjustbox}
     \caption{Exact experiment attention question}
@@
 \end{figure}
-
-Alongside this, was the addition of two questions comparing precisely the same word.
-As both words are the same, the result should always be a full 5/5 rating, any results without a full rating are discarded.
-Figure \ref{fig:exactMatch} contains one example of the attention question used to filter inaccurate results.
 
@@
 Workers with an answer of 5 are provided with a 
-Qualification\footnote{\url{https://blog.mturk.com/tutorial-understanding-requirements-and-qualifications-99a26069fba2}} 
+Qualification
 that tags them as defining themselves as native speakers. This qualification is then 
@@
 
-\subsubsection{Considerations}
-\label{sec:exp1_considerations}
-
-The first consideration is the way the words are compared.
-Due to the assumed context of authentication being phone-based, the comparison of words is a mixture of auditory and visual.
-The user hears their authentication partner read their set of words (Auditory) and compare to their set of words (Visual).
-This experiment asks users to compare the sound of two words that are visually displayed to them.
-This visual aspect is the first point of contact between the participant and the question, followed by a mental comparison of the phonetics of the word.
-Therefore, this initial visual contact has the potential to bias the results of the study.
-Levenshtein has the potential to be most affected by this due to the matches never being more than one character different, therefore, resulting in very similar-looking words.
-The alternative method of running this experiment is to get users to compare audio samples of words; this forces the user to compare just the phonetics of the words and not be influenced by the visual aspects of the pair.
-However, this adds a substantial cost to the operation of the study.
-Due to the aforementioned lack of resources, the chosen design was decided as most feasible as it is a balance between cost and accuracy.
-Further work, therefore, could improve by producing more conclusive results on the performance of the metrics by implementing the more accurate but costly alternative.
-
-Another consideration is the demographics of people accessible on Mechanical Turk.
-A comprehensive and still active survey run by \textbf{D.
-Difallah, E.
-Filatova} and \textbf{P.
-Ipeirotis}\cite{difallah2018demographics} shows that MTurk workers are younger and have a more substantial household income than that of the US population.
-This deviation has to be taken into consideration when interpreting the results because it has to potential to introduce a bias.
-
-\newpage
+% TODO: Consideration section?
 
@@
 
-This experiment is designed to be a simulation of the attack proposed in Section \ref{sec:attackDesign} in an attempt to answer Research Question \ref{goal:attackPercentage}.
-The experiment tests the simulated matches of three similarity metrics decided by the previous experiment (See Section \ref{sec:metrics}).
+This experiment is designed to be a simulation of the attack proposed in Section \ref{sec:attackDesign}.
+The experiment tests the simulated matches of three similarity metrics decided by the previous experiment.
 The overall aim of the experiment is to quantify the success rate of the attack on live participants.
-The user is presented with the same design as the \pep Android application (See Section \ref{sec:pep}).
+Figure \ref{fig:trustwordUI} contains a view of the user interface used in the experiment.
+It has been designed to be as similar as the \pep Android application.
 
-Appendix \ref{appendix:trustword_attack} shows the design of the experiments front end\footnote{A live version can also be viewed at the url: \url{https://afray.pythonanywhere.com/}}.
-As can be seen by comparing it to Figure \ref{fig:trustwords}, it has been designed to be as close as possible to the actual application.
+\begin{figure}[h!]
+    \centering
+    \begin{adjustbox}{width=0.4\textwidth,center}
+        \fbox{
+            \includegraphics[width=\textwidth]{experiment/trustword_attack.png}
+        }
+    \end{adjustbox}
+    \caption{Trustword user interface}
+    \label{fig:trustwordUI}
+\end{figure}
+
+A live version of the application is avaliable\footnote{\url{https://afray.pythonanywhere.com/}}.
 The blue button is clicked to simulate the authentication ceremony over the phone.
-A text-to-speech system then reads a set of words and the user should accept if they match and decline if they don't.
+A text-to-speech system then reads a set of words.
+The user should accept if they match and decline if they don't.
 
@@
 Certain keys have higher levels of potential near-collision keys than others due to how certain words are deemed similar by the similarity metric.
-Therefore, this presents the possibility to have keys with a deficient number of possible near-collision keys.
-The distribution of these keys is explained further in Chapter \ref{cha:Experiments}.
 Therefore, if random sets of words are chosen with no restraints, there are attacks presented to the user that in a real setting would be infeasible as they are close to a $2^{64}$ attack (4 Words * 16-bits).
@@
 
-The start and ends were chosen as the highest priority words to keep static.
-This design choice is due to research highlighting the common habit of users only to check the start and end of a checksum.
-\cite{cherubini2018towards} shows this by measuring user eye movement and displaying it as a heat map.
-
-\begin{figure}[h!]
-    \centering
-    \fbox{
-        \parbox{\textwidth}{
-            \includegraphics[width=\textwidth]{experiment/checksum_check.png}
-
-            \includegraphics[width=\textwidth]{experiment/checksum_check_2.png}
-        }
-    }
-    \caption{Failed verification of an incorrect checksum\cite{cherubini2018towards}}
-    \label{fig:heatMap}
-\end{figure}
-
-Figure \ref{fig:heatMap} shows the results of an eye-tracking experiment where the user failed to detect a mismatching digest. As can be seen, the users never compared the centre of the digest.
-
-However, this may not be applicable in this context due to the user being linearly fed an audio stream that they cannot skip to the start or end.
-We believe, however, that attention also plays a part in defining the most important areas of comparison.
-The hypothesis is that the users' attention is lower in the middle sections of comparison, where it peaks at the start and end.
-All of these aspects require empirical evidence to conclude.
-Therefore, this requires consideration when assessing the results of the experiment.
+The start and ends were chosen as the highest priority words to keep static. This design choice is due to research highlighting the common habit of users only to check the start and end of a checksum.
 
@@
 
-\begin{table}[h!]
-    \centering
-    \input{tables/design/attack_types.tex}
-    \caption{Summary of attack requirements}
-    \label{tab:attackReq}
-\end{table}
+% \begin{table}[h!]
+%     \centering
+%     \input{tables/design/attack_types.tex}
+%     \caption{Summary of attack requirements}
+%     \label{tab:attackReq}
+% \end{table}
 
 Table \ref{tab:attackReq} contains a summary of the different level of attacks and their respective restrictions.
-More potential near-collision keys make the attack search quicker.
 Any key that exceeds the defined numbers of potential near-collision key for attack level is deemed as vulnerable.
-As discussed in Section \ref{sec:attackDesign}, the near-collision keys are close keys produced from the similarity-metric's matches.
 A list of these vulnerable keys is sampled from when an attack is simulated.
-The percentage of vulnerable keys is explored in Chapter \ref{cha:Experiments}.
 
@@
 
-Audio-buttons-clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:expID} is clicked.
+Audio-buttons-clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:trustwordUI} is clicked.
 If there are rounds without button clicks, this is a sign of non-attentiveness.
-The design choice was made to allow non-clicks as an attention check.
+The design choice was made to allow non-clicks.
 This design provides a way to detect and discard click-throughs\footnote{Workers that aim to complete the task as fast as possible, with no regard for the quality of responses}.
@@
 Anything quicker was discarded as anything faster risks invalid and rushed results.
-
-\subsubsection{Considerations}
-As with the previous experiment, sampling from MTurk's demographic results in a collection of participants that are not reflective of the general population.
-Due to the attack context of this experiment, it can be assumed that the youth of the participants contributes to less successful attacks.
-Therefore, the results generated by this experiment can be loosely assumed as a best-case scenario for the scheme.
-We predict a high attack success rate if assessed over the general population.

### 2019-08-31 Writeup/Paper/sections/results.tex
Changes; - Added inital paper content

--- 2019-08-31 Writeup/Thesis/chapters/experiments.tex
@@
-\chapter{Experimentation Results}
-\label{cha:Experiments}
+\section{Results}
 
-\section{Scallion vs GreenOnion}
+\subsection{Scallion vs GreenOnion}
 \label{sec:SvG}
@@
 This is the same Scallion code but with a fix that reduces the severity of the speed decline.
-
-\begin{table}[h!]
-    \centering
-    \begin{tabular}{|ll|}
-        \hline
-        \textbf{Scallion} & \\
-        \hline
-        OS & Windows 10 (May 2019) \\
-        Version & Scallion 2.1 (Commit: \verb|42b4cb5|\footnote{\url{https://github.com/lachesis/scallion/tree/42b4cb555dbf8554b212a2bc3e0ba3d652434ecf}}) \\
-        \hline
-        \textbf{GreenOnion} & \\
-        \hline
-        OS  & Linux Mint 19.1 \\
-            & Kernel: 4.15.0 \\ 
-        \hline
-        \textbf{Hardware} & \\
-        \hline
-        GPU & Nvidia GTX 750 Ti  \\
-        CPU & AMD FX-6300 \\
-        \hline
-    \end{tabular}
-    \caption{Testing environment}
-\end{table}
-
-Figure \ref{fig:scallionCode} contains a snippet of code with the error.
-The calls to \verb|parms.ToolConfig.PredictRuntime()| become increasingly expensive as the number of concurrently checked keys increases.
-Removing this line from the \verb|Console.Write| statement results in a sizeable improvement in speeds as can be seen in Figure \ref{tab:scallion_speed}.
+Scallion contained a call in its print statement that became become increasingly expensive as the number of concurrently checked keys increases.
+Removing this line from the print statement results in a sizeable improvement in speeds as can be seen in Figure \ref{tab:scallion_speed}.
 This was necessary to include as we believe the improved versions show a better comparison between the design of the two tools.
@@
 \begin{figure}[h!]
-    \input{code/scallion_bug.tex}
-    \caption{Scallion's main print statement}
-    \label{fig:scallionCode}
+    \centering
+    \input{graphs/speed.tex}
+    \label{tab:scallion_speed}
+    \caption{Speed comparison between Scallion and GreenOnion}
 \end{figure}
@@
 This improvement over Scallion is, therefore, substantial.
-
 GreenOnion's code has been made publicly available and can be viewed on GitHub\footnote{\url{https://github.com/AidanFray/GreenOnion}}.
 
-\begin{figure}[h!]
-    \centering
-    \input{graphs/speed.tex}
-    \label{tab:scallion_speed}
-    \caption{Speed comparison between Scallion and GreenOnion}
-\end{figure}
+\subsection{Experiment 1 - Metric performance}
 
-\newpage
+The goal of this experiment was to select a set of metrics to be assessed in the subsequent experiment. This section discusses the demographics of participants alongside the subsequent results.
 
-\section{Experiment 1 - Metric performance}
+% \subsubsection*{Demographics}
 
-As discussed in Section \ref{exp:metric}, the goal of the experiment was to select a set of metrics to be assessed in the following experiment.
-This section discusses the demographics of participants alongside the subsequent results.
+Overall, 104 participants were assessed in this study.
+Five results were discarded from the set due to either failing the attention questions (See in Section \ref{sec:exp1_qualitycontrol}) or having too low of a fluency rating.
+This dismissal was a necessary process to improve the health of the results.
+
+Table \ref{tab:exp1_demo} contains the demographical breakdown of the reduced set of participants.
+The average ages of the participants were 37.3 years ($\sigma = 11.67$) with a split of 44.4\% of Males to 55.6\% of Females.
+As can be seen, over 60\% of participants can be considered highly educated (Bachelor’s and up).
+This level of education is not sufficiently reflective of the general population and therefore, has to be considered when interpreting the results.
+All participants were sourced from the US; this again requires consideration due to the broad range of dialects present that may bias the results.
+Further work could investigate the effect of location and dialect on similar results.
 
@@
 
-Overall, 104 participants were assessed in this study.
-Five results were discarded from the set due to either failing the attention questions (See in Section \ref{sec:exp1_qualitycontrol}) or having too low of a fluency rating.
-This dismissal was a necessary process to improve the health of the results.
+Figure \ref{tab:exp1_results} shows the average results for the selected matches..
+It can be seen that Levenshtein came out substantially above the rest.
+The breakdown of the ratings in Figure \ref{fig:exp1_breakdown} also shows Levenshtein's dominance.
+Levenshtein has a much more significant proportion of 4 and 5 ratings than the alternatives.
 
-Table \ref{tab:exp1_demo} contains the demographical breakdown of the reduced set of participants.
-The average ages of the participants were 37.3 years ($\sigma = 11.67$) with a split of 44.4\% of Males to 55.6\% of Females.
-As can be seen, over 60\% of participants can be considered highly educated (Bachelor’s and up).
-This level of education is not sufficiently reflective of the general population and therefore, has to be considered when interpreting the results.
-All participants were sourced from the US; this again requires consideration due to the broad range of dialects present that may bias the results.
-Further work could investigate the effect of location and dialect on similar results.
+Due to the averages of Metaphone and Phonetic Vectors being so close standard deviation was used as the final decider.
+As can be seen, Megaphone has a slightly lower $\sigma$ value of that of Phonetic vectors, thus, contributing to the decision to select Metaphone.
 
-\begin{wraptable}[11]{r}{8cm}
+\begin{table}[h!]
     \centering
@@
     \label{tab:exp1_results}
-\end{wraptable}
+\end{table}
 
-Figure \ref{tab:exp1_results} shows the average results for the selected matches explained in Section \ref{sec:exp1_comparison}.
-It can be seen that Levenshtein came out substantially above the rest.
-The breakdown of the ratings in Figure \ref{fig:exp1_breakdown} also shows Levenshtein's dominance.
-Levenshtein has a much more significant proportion of 4 and 5 ratings than the alternatives.
-This performance may, however, be due to the visual way the comparisons are performed.
-(Discussed in detail in Section \ref{sec:exp1_considerations}).
-
-Due to the averages of Metaphone and Phonetic Vectors being so close standard deviation was used as the final decider.
-As can be seen, Megaphone has a slightly lower $\sigma$ value of that of Phonetic vectors, thus, contributing to the decision to select Metaphone.
-
-\subsection*{Considerations}
-As discussed in Section \ref{sec:exp1_considerations}, compromises were made to fulfil all requirement with a minimised cost.
-Levenshtein's abnormal performance further backs up concerns around the visual aspect biasing the performance of the metric.
-This aspect requires consideration when interpreting the results.
-
-Even with the discussed issues, the experiment was designed to reduce the number of metrics promptly.
-This experiment, therefore, has achieved that goal of providing three metrics for the subsequent experiment while balancing between accuracy and expenditure.
-The results are also an improvement over informal ad-hoc methods.
-Further work could aim to reproduce this study with the proposed audio-based design.
-
-\input{graphs/experiment_one/graph.tex}
-
-\newpage
+%TODO: Include graphs?
 
 \section{Experiment 2 - Trustword attacks}
+
+\begin{table*}[t]
+    \makebox[\textwidth][c]{
+        \centering
+        \begin{tabular}{|ll|l|l|l|}
+            \hline
+            \textbf{Metric} & & \textbf{Successful Attacks} & \textbf{Total Attacks} & \textbf{Success Rate} \\
+            \hline
+            Levenshtein && 218 & 1101 & 19.8\% \\
+            \hline
+            & \OOOO   & 34  & 358  & ~~9.5\% \\
+            & \XOOO   & 59  & 353  & 16.7\% \\
+            & \XOOX   & 125  & 390  & 32.1\% \\
+            \hline\hline
+            Metaphone &&  181 & 1072 & 16.9\% \\
+            \hline
+            & \OOOO   & 38 & 345 & 11.0\% \\
+            & \XOOO   & 57 & 375 & 15.2\% \\
+            & \XOOX   & 86 & 352 & 24.4\% \\
+            \hline\hline
+            NYSIIS &&  209 & 1114 & 18.8\% \\
+            \hline
+            & \OOOO   & 36 & 385 & ~~9.3\% \\
+            & \XOOO   & 72 & 375 & 19.2\% \\
+            & \XOOX   & 101 & 354 & 28.5\% \\
+            \hline\hline
+            \textbf{Overall} & & 608 & 3287 & 18.5\% \\
+            \hline\hline
+        \end{tabular}
+    }
+    \caption{Success rates for simulated attacks}
+    \label{tab:exp2_attacks}
+\end{table*}
+
 \label{sec:exp2}
@@
 
-\subsection*{Demographics}
 Overall, 435 paid participants recruited via Amazon's MTurk were assessed in this experiment.
-We excluded 66 results; 7 due to being non-native speakers and 59 were discarded for failing the attention metrics (Discussed in Section \ref{sec:exp2_quality}).
+We excluded 66 results; 7 due to being non-native speakers and 59 were discarded for failing the attention metrics (Discussed in Section \ref{sec:exp2_quality})
 
@@
 All participants were also sourced from the USA and have rated themselves as fully native English speakers.
-\begin{table}[!h]
-    \centering
-    \begin{tabular}{|l|l|}
-        \hline
-        Browser & Percentage \\
-        \hline
-        Chrome & 85.1\% \\
-        Firefox & 12.2\% \\
-        Safari & ~~1.9\% \\
-        Other & ~~0.8\% \\
-        \hline
-    \end{tabular}
-    \caption{Internet Browser breakdown}
-    \label{tab:exp2_browser}
-    \begin{tabular}{|l|l|}
-        \hline
-        Operating System & Percentage \\
-        \hline
 
-        \hline
-        Windows (All) & 74.3\% \\
-        ~~~~\textit{Windows 7} & ~~~12.7\% \\
-        ~~~~\textit{Windows 8} & ~~~~~4.1\% \\
-        ~~~~\textit{Windows 10} & ~~~57.5\% \\
-        MacOS X	 & 13.8\% \\
-        ChromeOS & ~~3.8\% \\
-        Android	& ~~4.3\% \\
-        iPhone	& ~~1.1\% \\
-        iPad	& ~~0.5\% \\
-        Linux	& ~~2.2\% \\
-        \hline
-    \end{tabular}
-    \caption{Operating System breakdown}
-    \label{tab:exp2_os}
-\end{table}
-
-As user-agent strings were collected for each participant collations of OS and internet browser versions was made possible.
-Tables \ref{tab:exp2_browser} and \ref{tab:exp2_os} contain the browser and OS breakdowns,  respectively.
-Chrome and Windows 10 seem to dominate the proportion of their respective domains alongside the surprisingly large proportion of workers utilising older versions of Windows such as 7 or 8 (15.81\%).
-
-\subsection*{Results}
 Table \ref{tab:exp2_attacks} contains the break down of results for the experiment.
@@
 
-\begin{table}
-    \makebox[\textwidth][c]{
-        \centering
-        \begin{tabular}{|ll|l|l|l|}
-            \hline
-            \textbf{Metric} & & \textbf{Successful Attacks} & \textbf{Total Attacks} & \textbf{Success Rate} \\
-            \hline
-            Levenshtein && 218 & 1101 & 19.8\% \\
-            \hline
-            & \OOOO   & 34  & 358  & ~~9.5\% \\
-            & \XOOO   & 59  & 353  & 16.7\% \\
-            & \XOOX   & 125  & 390  & 32.1\% \\
-            \hline\hline
-            Metaphone &&  181 & 1072 & 16.9\% \\
-            \hline
-            & \OOOO   & 38 & 345 & 11.0\% \\
-            & \XOOO   & 57 & 375 & 15.2\% \\
-            & \XOOX   & 86 & 352 & 24.4\% \\
-            \hline\hline
-            NYSIIS &&  209 & 1114 & 18.8\% \\
-            \hline
-            & \OOOO   & 36 & 385 & ~~9.3\% \\
-            & \XOOO   & 72 & 375 & 19.2\% \\
-            & \XOOX   & 101 & 354 & 28.5\% \\
-            \hline\hline
-            \textbf{Overall} & & 608 & 3287 & 18.5\% \\
-            \hline\hline
-        \end{tabular}
-    }
-    \caption{Success rates for simulated attacks}
-    \label{tab:exp2_attacks}
-\end{table}
-
-\subsection*{Considerations}
-As previously mentioned, the set of recruited participants are more highly educated than the general population.
-This combined with the lower average age contributes to an inevitable bias being introduced into the data.
-An assumption can be made that higher education leads to more skilful interaction with computer-based systems, this, therefore, with the previous assumption in mind means the results of this experiment can be considered a `best case' scenario.
-The attacks, therefore, would be expected to be more successful on less technical users.
-This consideration, however, requires further research and possible empirical data to determine the validity of the assumption.
-
-During this study, the main task was to perform the authentication ceremony a set number of times.
-In the real-world, the ceremony is a secondary task due to it not strictly being required.
-This aspect, alongside the potential for users to downplay the possibility of attack, leads to the conclusion that the success rates could be much higher in a real-world setting.
-The assumption is that these results display the success rate for attentive users where they make sure to double-check with their authentication partner multiple times.
-It is, therefore, assumed that the majority of users aim to complete the task as quickly as possible, if at all.
-
 \subsection*{Comparison to alternative literature}
@@
 Flechais} and \textbf{A.
-Roscoe}\cite{kainda2009usability} (previously discussed in Chapter \ref{cha:LiteratureReview}) is the most comparable to this experiment.
+Roscoe}\cite{kainda2009usability}  is the most comparable to this experiment.
 They were the only study to use exactly 4 words but differed on the size of the dictionary (1024 words) and how a near-match were calculated.
 Near-matches were a difference in a single word, but without the consideration for similarity, this is the unique aspect considered with this experiment.
-
 However, with those aspects in mind attacks on words encoding received an overall success rating of 3.3\%, considerably lower than that of this study.
@@
 Other relevant work by \textbf{S.
-Dechand \textit{el al.}}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words.
+Dechand \textit{el al.}}\cite{dechand2016empirical} assess the success rate of attacks on words.
 Their experiment is less similar as 14 words per attack were assessed with each participant, where the comparison was performed visually.
@@
 This aspect is also a unique consideration compared to the available literature.
-
-\section{Average number of near-collision keys for each metric}
-\label{sec:averagePerms}
-In order to predict the effectiveness of the attack over a wide variety of keys, the number of average near-collision keys requires computation.
-Table \ref{tab:average_perm} shows the average number of potential collision keys for each metric.
-The ``Compute Time'' is the computation time required for a single mid-range (2000MH/s) GPU.
-
-\begin{table}[!h]
-    \makebox[\textwidth][c]{
-        \centering
-        \begin{tabular}{|llll|}
-            \hline
-            \textbf{Metric} & & \textbf{Near-collision keys} & \textbf{Compute Time} \\
-            \hline
-            NYSIIS &&& \\
-            \hline
-            & \OOOO & 1963.07 &  ~~27.19 days \\
-            & \XOOO & 448.37 &  119.14 days \\
-            & \XOOX & 98.07 &  ~~~~1.49 years \\
-            \hline\hline
-
-            Metaphone &&& \\
-            \hline
-            & \OOOO & 27138.78 &  ~~~~1.97 days \\
-            & \XOOO & 2822.74 &  ~~18.91 days \\
-            & \XOOX & 339.84 &  157.45 days \\
-            \hline\hline
-
-            Levenshtein &&& \\
-            \hline
-            & \OOOO & 293.92 &  182.17 days \\
-            & \XOOO & 102.75 &  ~~~~1.43 years \\
-            & \XOOX & 35.53 &   ~~~~4.18 years \\
-            \hline\hline
-
-        \end{tabular}
-    }
-    \caption{Each metric's average number of near-collision keys and average compute times}
-    \label{tab:average_perm}
-\end{table}
-
-As can be seen, metrics like Levenshtein have a low overall average and would require much more attacker resources to become feasible.
-On the other hand, Metaphone has attacks that could be computed on average in under 2 days.
-The success rate for this attack type in the second experiment was 11.01\% on average.
-This means on commodity hardware commonly found in the home; an attacker could compute a key in less than two days that could succeed more than 10\% of the time.
-This aspect is substantial and highlights weaknesses in the Trustword system.
-
-\section{Distribution of vulnerable keys}
-\label{sec:vulnKeys}
-As discussed in the design of the second experiment (See Section \ref{sec:exp2}), the attacks sampled from a list of `vulnerable keys'.
-These vulnerable keys were created using real keys extracted from PGP key servers.
-These keys were then randomly sampled and used to create the combined key, as discussed in Section \ref{sec:pep}.
-100,000 random key pairs were created and used as the sample\cite{davidnorman_2019}.
-Any vulnerable keys in this set were recorded and used in the experiment.
-
-\begin{table}[!h]
-    \centering
-
-    \makebox[\textwidth][c]{
-
-        \begin{tabular}{|lll|}
-            \hline
-            \textbf{Attack Type} & \textbf{Metric} & \textbf{Vulnerable \%} \\
-            \hline 
-            \XOOX~(152) && \\ 
-            & Levenshtein & ~~4.295\% \\
-            & Metaphone & 24.095\% \\
-            & NYSIIS & 10.441\% \\
-            \hline\hline
-            \XOOO~(1525) && \\ 
-            & Levenshtein & ~~0.827\% \\
-            & Metaphone & 15.569\% \\
-            & NYSIIS & ~~4.341\% \\
-            \hline\hline
-            \OOOO~(15250) && \\ 
-            & Levenshtein & ~~0.157\% \\
-            & Metaphone & 10.202\% \\
-            & NYSIIS & ~~1.824\% \\
-            \hline\hline
-        \end{tabular}
-    }
-    \caption{Number of vulnerable keys per metric}
-    \label{tab:vulnkeys}
-\end{table}
-
-Table \ref{tab:vulnkeys} contains the breakdown of the number of vulnerable keys.
-The takeaways from this table are the extremely low values for Levenshtein in the higher attacks.
-This phenomenon is due to the low number of overall matches produced by Levenshtein, meaning the metric is not effective in the vast majority of cases.
-However, the standout metric is Metaphone with a sizeable proportion of vulnerable keys; it was the worst performer when assessed against real users but only by as little as 2\%.
-If you take into consideration, the number of vulnerable keys detected in the set alongside the average amount of near-collision matches in Table \ref{tab:average_perm} Metaphone appears to be the most usable metric overall.
-
-\section{Generation of keys}
-\label{sec:key_gen}
-In order to demonstrate that the generation of the near-collision keys is not only theoretical, the actual generation was performed using GreenOnion.
-A random metric was selected from the three carried forward from the first experiment.
-Alongside this, a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key).
-Then for each attack level (\OOOO, \XOOO, \XOOX), a key was computed.
-NYSIIS was chosen as the selected metric.
-To expedite the process, an initial search was performed for controlled keys that had the highest number of near-collisions; this was due to the demonstrative purpose of this experiment.
-Producing near-matching keys from key pairs with a very small number of potential matches adds very little to this demonstration.
-This, however, results in a best-case scenario for key computation times.
-
-\begin{table}[h!]
-
-    \makebox[\textwidth][c]{
-        \begin{tabular}{|l|l|}
-            \hline
-            Potential near-collision keys & 142,296 \\
-            Hashing speed & 4000 MH/s \\
-            Estimated computation time & 9 hours \\
-            Actual computation & 6.41 hours \\
-            GPU Days & 0.52 \\
-            \hline
-            Original Trustwords & BELL GRIND ALGERIA ANNULI \\
-            Actual Trustwords   & BOIL GRAND ALGER ANNUL \\
-            \hline
-        \end{tabular}
-    }
-    \caption{NYSIIS - OOOO}
-    \label{tab:nysiis0}
-
-    \makebox[\textwidth][c]{    
-        \begin{tabular}{|l|l|}
-            \hline
-            Potential near-collision keys & 133,200 \\
-            Hashing speed & 8000 MH/s \\
-            Estimated computation time & 4.2 hours \\
-            Actual computation & 5.12 hours \\
-            GPU Days & 0.853 \\
-            \hline
-            Original Trustwords & ASSUMING SONOMA DENS KEENER \\
-            Actual Trustwords   & ASSUMING SUMMON DENNI CONNOR \\
-            \hline
-        \end{tabular}
-    }
-    \caption{NYSIIS - XOOO}
-    \label{tab:nysiis1}
-
-    \makebox[\textwidth][c]{
-        \begin{tabular}{|l|l|}
-            \hline
-            Potential near-collision keys & 16,464 \\
-            Hashing speed & 6000 MH/s \\
-            Estimated computation time & 2.16 days \\
-            Actual computation & 23.44 hours \\
-            GPU Days & 2.93 \\
-            \hline
-            Original Trustwords & VOCATION BORE TANN ANTE \\
-            Actual Trustwords   & VOCATION BARE TONE ANTE \\
-            \hline
-        \end{tabular}
-    }
-    \caption{NYSIIS - XOOX}
-    \label{tab:nysiis2}
-\end{table}
-
-Tables \ref{tab:nysiis0}, \ref{tab:nysiis1} and \ref{tab:nysiis2} contain the parameters and results on the computation.
-Due to the varying availability of resources, each computation has a varying hashing speed.
-This variation has been normalised by the introduction of the "GPU Day" metric.
-A GPU day is simply the computation time required to reach the same conclusion on a single 2000 MH/s GPU.
-
-As can be seen most notably from Table \ref{tab:nysiis2}, the generation of the actual Trustwords differs in only 3 characters making it arguably very similar.
-When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU can achieve around a 28\% success rate when assessed against actual users.
-This time, however, has been improved due to the random search for a controlled key with a more favourable number of near-collision keys.
-Even with the least restricted attack type presented in Table \ref{tab:nysiis0}, the computation of half a day can provide almost a 10\% success rate when attacking users.
-This results in any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of deceiving an actual user.

### 2019-08-31 Writeup/Paper/sections/background.tex
Changes; - Changes made to the precis paper structure

@@
 \section{Background}
-In this section we dicuss
 
@@
 A similarity metric is an algorithm designed to determine if two words are phonetically a match.
-For example, the words "THEIR" and "THERE" is a match, whereas the words "DARK" and "PRINCIPLE" are not phonetically matching.
+For example, the words ``THEIR" and "THERE" is a match, whereas the words ``DARK" and ``PRINCIPLE" are not phonetically matching.
 This section provides a base explanation of important phonetic algorithms relevant in this project.
 
-\subsubsection*{Soundex}
-\label{sec:soundex}
-One of the earliest examples of a phonetic algorithm is known as Soundex.
+\textbf{Soundex} - One of the earliest examples of a phonetic algorithm is known as Soundex.
 It was initially designed for phonetically indexing names alongside detection of transposed letters in spelling mistakes.
@@
 
-\subsubsection*{NYSIIS}
-\label{sec:nysiis}
-The New York State Identification and Intelligence System (NYSIIS) phonetic code was created for the phonetic matching of American names.
+\textbf{NYSIIS} - The New York State Identification and Intelligence System (NYSIIS) phonetic code was created for the phonetic matching of American names.
 The motivation for its inception was mostly due to the presence of Hispanic names in the American based databases (this was an aspect Soundex was known to have low accuracy with).
 
-\subsubsection*{Metaphone}
-\label{sec:metaphone}
-Metaphone was invented by Lawrence Philips in 1990\cite{philips1990hanging} in response to the deficiencies in Soundex.
+\textbf{Metaphone} - Metaphone was invented by Lawrence Philips in 1990\cite{philips1990hanging} in response to the deficiencies in Soundex.
 It improves on Soundex by including information around inconsistency and variation in English spelling in an attempt to create a more accurate phonetic representation.
 
-\subsubsection*{Levenshtein Distance}
-\label{sec:leven}
-Levenshtein distance is a string metric designed to measure the `distance' between two strings.
+\textbf{Levenshtein Distance} - Levenshtein distance is a string metric designed to measure the `distance' between two strings.
 It is merely the number of single-character edits (insertions, deletions or substitutions) required to reach the other string.
 
-An example distance between \verb|trace| and \verb|place| would be the substitutions of the first to letters, from \verb|tr| to \verb|pl|, meaning the two strings have a Levenshtein distance of 2.
-
-\subsubsection*{Phonetic Vectors}
-\label{sec:phonetic_vectors}
-Phonetic Vectors is a unique addition to the chosen set.
+\textbf{Phonetic Vectors} - Phonetic Vectors is a unique addition to the chosen set.
 Created by Allison Parrish in 2017\cite{parrish2017poetic}, Phonetic vectors is as the name suggests the vectorisation of the phonetics of a word.
@@
 Phonemes are the phonetic elements that construct a word.
-For example, the word "RING" translated into the phonemes \verb|/R IH NG/|.
+For example, the word ``RING" translated into the phonemes \verb|/R IH NG/|.
 
-\clearpage
-
-\subsection{Pretty Easy Privacy}
-\label{sec:pep}
-A very recent implementation of a word list can be found in Pretty Easy Privacy (\pep) implementation of TrustWords\cite{trustwords}.
+% \subsection{Pretty Easy Privacy}
+% \label{sec:pep}
+% A very recent implementation of a word list can be found in Pretty Easy Privacy (\pep) implementation of TrustWords\cite{trustwords}.
 \pep is a data encryption system that utilises PGP encryption to provide E2EE on all common channels of communication such as email or SMS.
@@
 
-\pep deals with the threat of MiTM attacks by having users compare the respective key fingerprints encoded as a set of words.
+% \pep deals with the threat of MiTM attacks by having users compare the respective key fingerprints encoded as a set of words.
 Figure \ref{fig:trustwords} shows the \pep Android implementation of Trustwords.
@@
 
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.4\textwidth]{trustwords/trustword_handshake.jpg}
-    \caption{Trustword fingerprint verification}
-    \label{fig:trustwords}
-\end{figure}
+% \begin{figure}[h!]
+%     \centering
+%     \includegraphics[width=0.4\textwidth]{trustwords/trustword_handshake.jpg}
+%     \caption{Trustword fingerprint verification}
+%     \label{fig:trustwords}
+% \end{figure}
 
-The unique aspect of TrustWords is its mapping of a single word to 16-bits.
+% The unique aspect of TrustWords is its mapping of a single word to 16-bits.
 If compared to alternative literature, this is the highest number of bits-per-word seen.

### 2019-08-31 Writeup/Paper/sections/design.tex
Changes; - Changes made to the precis paper structure

@@
 \label{sec:attackDesign}
-The attack on Trustwords involves generating ``near-collision'' keys. Near-collision keys are keys composed of a set of words that are deemed a match by the similarity metric.
+The propossed attack on Trustwords involves generating ``near-collision'' keys. Near-collision keys are keys composed of a set of words that are deemed a match by the similarity metrics.
 \\\\
-As each combined key in Trustwords is an exclusive-or of both sides' public-key the attack is designed to target a single pair of users and requires recomputation for each attack target.
+As each combined key in Trustwords is an exclusive-or of both sides' public-key, therefore, the attack is designed to target a single pair of users and requires recomputation for each attack target pair.
 Each pair is split into an "Uncontrolled" or "Controlled" key.
@@
 In summary, the attack steps are:
-
 \begin{enumerate}
@@
 
-    \item Select a target and allocate "Uncontrolled" and "Controlled" key identification.
+    \item Select a target and allocate ``Uncontrolled" and ``Controlled" key identification.
 
@@
 The inspiration for the design of this tool was taken from a tool called Scallion\footnote{\url{https://github.com/lachesis/scallion}}.
-Scallion was designed by Richard Klafter and Eric Swanson and was used to demonstrate that 32-bit PGP key IDs were insufficient.
-To keep with the onion-based theme, the proposed tool is called `GreenOnion' and is a re-write of Scallion in C++.
-This language was chosen due to the well-understood efficiency benefits.
-The proposed tool differs from Scallion, most notably in its ability to concurrently search for a large number of keys, GreenOnion improves on this substantially.
-More implementation and experimental details are discussed in later chapters.
+The proposed tool is called `GreenOnion' and is a re-write of Scallion in C++.
+The proposed tool differs from Scallion, most notably in its ability to concurrently search for a large number of keys.
+This is due to the unique addition of a bloom filter.
+A bloom filter is a probabilistic data structure that allows efficient checking for the presence of an element in a set.
+It is effectively a vast array of booleans that state whether an element is present.
+A pre-defined hashing algorithm decides the index in the array.
+This process is repeated several times with a set number of hashing algorithms ($k$) to populate the array of length ($m$).
+To check the presence of an element in the set means hashing the target value and checking the indices returned.
+This data structure, therefore, has a complexity of $O(k)$ regardless of the number of elements in the set.
+Due to the use of hashing algorithms, there is the possibility for collisions and, thus, the possibility of false-positives.
+The data structure, however, does not produce any false-negatives.
+If the levels of false-positives are controlled (by altering $k$ and $m$), the tool can search through a vast number of potential keys with minimal decrease in speed.
 
@@
 To utilise the parallel nature of the GPU to compute the hash of a large number of keys, the tool utilises a GPGPU (General-purpose computing on graphics processing units) framework.
-The chosen framework was OpenCL due to its support for the chosen language (C++) and platform (Linux).
 OpenCL allows the creation of code chunks referred to as "kernels" to be executed concurrently, this provides a massive speed increase compared to the sequential nature of the CPU.

### 2019-08-31 Writeup/Paper/sections/experimental_design.tex
Changes; - Changes made to the precis paper structure

@@
 Each comparison contains a match-pair.
-These matches are generated by running the similarity metric over all the pairings in the Trustword dictionary; if the pair meets the criteria discussed in the previous section, it is determined a match.
+These matches are generated by running the similarity metric over all the pairings in the Trustword dictionary.
+If two words are deemed a match they are added to their own list.
 Potential matches are then sampled from their respective lists.

### 2019-08-31 Writeup/Paper/sections/introduction.tex
Changes; - Added inital paper content
Changes; - Changes made to the precis paper structure

@@
 The increasing use of public-key cryptography by instant messaging and secure email means ensuring confidentiality is an ever more important task.
+
 One of the most significant risks to the security of the communication channel is a Man-in-the-middle (MiTM) attack.
@@
 A fingerprint is a small string of characters that is unique to each key and, thus, can be used to identify.
+
 Fingerprints can come in several different encodings such as Hexadecimal, words, and even procedurally generated avatars.
@@
 Consequently, this makes the designing of user-friendly schemes a task of utmost importance.
+
 Humans are commonly considered the most vulnerable part of any computer system.
@@
 Therefore, research into improving or creating a more secure and user-friendly fingerprint encoding remains an important task.
-One proposed user-friendly scheme is Pretty Easy Privacy's (p$\equiv$p) "Trustwords".
+
+One proposed user-friendly scheme is Pretty Easy Privacy's (p$\equiv$p) ``Trustwords''.
 Trustwords is an implementation of word fingerprint mapping with a emphasis on usability.
 This increase in usability is achieved by the user comparing a reduced number of words.
-This usability boost, however, comes at a cost of a much larger word list.
-This report evaluates the security and feasibility of attacking Trustwords. The motivation for this is due in part to the shortage of justification behind the size and features of the chosen wordlist.
+This usability boost, however, comes at a cost of a much larger word list ($2^{16}$ words).
+
+The project aims to assess the security of p$\equiv$p’s minimum recommendation of four Trustwords\cite{trustwordsHandshake}.
+Moreover, issues with the dictionary's design, such as the presence of homophones and dual-mapping of words show the potential for possible vulnerabilities.

### 2019-08-31 Writeup/Paper/sections/related_work.tex
Changes; - Changes made to the precis paper structure

\section{Related Work}

\subsection{Encoding Schemes}
Encoding schemes are the physical method of encoding used to represent the fingerprint. The most common representation is alphanumerical with either \textbf{Hexadecimal} (0-9/A-F) or \textbf{Base32} (2-7/A-Z). These encoding schemes are the most popular due to their intuitive simplicity and lack of hardware requirements.

Fingerprints can also be encoded using natural language. The fingerprint can be chunked and mapped to a set of words. The same principle can be used to fill placeholders in a pre-defined sentence allowing the simple formation of syntactically correct English sentences. Moreover, other languages can be used such as Chinese, Japanese or Korean, to map fingerprint chunks to characters.

A substantial amount of work has been performed assessing the performance of encoding schemes. Results from this literature consistently show the effectiveness of language-based encodings such as Words or Sentences with accuracies ranging up from 94\% \cite{dechand2016empirical}\cite{tan2017can}\cite{kainda2009usability}. In all cases, these were the best schemes from the sets assessed. The exception to this is the work performed by \textbf{H. Hsiao \textit{et al.}}\cite{hsiao2009study} with Words achieving an abnormal accuracy of 63\%. All of the papers assessed simulated attacks and had minimal consideration for technical details regarding their execution.

Further research has aimed at creating or improving language based encoding schemes. Work by \textbf{Juola} and \textbf{Zimmermann} \cite{juola1996whole} aimed to produce a word list where phonetic distinctiveness was prioritised alongside, \textbf{Michael Rogers'}\footnote{\url{https://github.com/akwizgran/basic-english}} research detailing a process to map fingerprints to pseudo-random poems.

To our knowledge no research has been performed investigating the unique design choices present in Trustwords. This, therefore, is a promising candidate for research.

### 2019-08-31 Writeup/Paper/sections/abstract.tex
Changes; - Implemented corrections for the paper

@@
 protect against eavesdropping. A substantial amount of past work has
-aimed to propose fingerprint representations that work better with hu-
-man limitations. ``Trustwords'' proposed by pEp is an example of such a
+aimed to propose fingerprint representations that work better with human limitations. ``Trustwords'' proposed by pEp is an example of such a
 scheme, where the fingerprint is encoded as words in an attempt to improve
@@
 \\\\
-This works main aim is to assess if Trustword’s recommended minimum
+This work's main aim is to assess if Trustword’s recommended minimum
 number of four words is sufficient. In order to achieve this goal, this work
@@
 assist in quantifying attack feasibility. GreenOnion improved substantially
-on a similar tool’s ability to search for matches concurrently where it was
-able to search for over 1.5 million concurrent keys. Our findings show a
+on a similar tool’s ability to search for matches concurrently. Our findings show a
 substantial increase in attack success compared to related literature. We

### 2019-08-31 Writeup/Paper/sections/background.tex
Changes; - Implemented corrections for the paper

@@
 
-An E2EE connection uses the key types discussed previously to ex-
-change messages between verified parties securely. However, this hinges
+An E2EE connection uses the key types discussed previously to exchange messages between verified parties securely. However, this hinges
 on the verification of the initial parties, if one party impersonates another and receives sensitive communication, the secure encryption is
@@
 It was initially designed for phonetically indexing names alongside detection of transposed letters in spelling mistakes.
-Soundex is one of the most famous example of a phonetic.
+Soundex is one of the most famous example of a phonetic algorithm.
 This is due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}.
@@
 The motivation for its inception was mostly due to the presence of Hispanic names in the American based databases (this was an aspect Soundex was known to have low accuracy with).
+It was in use right up until the end of 1998 within various US Government departments.
 
@@
 
-\textbf{Phonetic Vectors} - Phonetic Vectors is a unique addition to the chosen set.
-Created by Allison Parrish in 2017\cite{parrish2017poetic}, Phonetic vectors is as the name suggests the vectorisation of the phonetics of a word.
+\textbf{Phonetic Vectors} - Phonetic Vectors; created by Allison Parrish in 2017\cite{parrish2017poetic}, is as the name suggests the vectorisation of the phonetics of a word.
 Phonetic features are used in this work as a way to compare the similarity of phonemes.

### 2019-08-31 Writeup/Paper/sections/design.tex
Changes; - Implemented corrections for the paper

@@
 \\\\
-As each combined key in Trustwords is an exclusive-or of both sides' public-key, therefore, the attack is designed to target a single pair of users and requires recomputation for each attack target pair.
+The attack is designed to target a single pair of users and requires recomputation for each attack target pair.
 Each pair is split into an "Uncontrolled" or "Controlled" key.
@@
 The uncontrolled and controlled keys can be swapped around, thus, resulting in the possibility to intercept both directions of communication.
-This, however, requires performing the attack twice.
 \\\\
@@
 
-    \item Calculate all permutations of near-collisions for the key pair and produce a list of near-collision key fingerprints.
+    \item Calculate all permutations of near-collisions for the key pair and produce a list of near-collision fingerprints.
 
-    \item Use a list of near-collision keys in the mass computation of keys to find near-collision keys.
+    \item Use a list of near-collision fingerprints in the mass computation of keys to find near-collision keys.
 
@@
 To utilise the parallel nature of the GPU to compute the hash of a large number of keys, the tool utilises a GPGPU (General-purpose computing on graphics processing units) framework.
-OpenCL allows the creation of code chunks referred to as "kernels" to be executed concurrently, this provides a massive speed increase compared to the sequential nature of the CPU.
+OpenCL allows the creation of code chunks referred to as ``kernels'' to be executed concurrently, this provides a massive speed increase compared to the sequential nature of the CPU.

### 2019-08-31 Writeup/Paper/sections/discussion.tex
Changes; - Implemented corrections for the paper

@@
 Thus, further work could assess the performance of metrics against each other to determine the one that works best with human models.
-A conclusion could be reached by running the improved experiment discussed in Section \ref{exp:metric}, where it could be repeated with an increased number of metrics.
+A conclusion could be reached by re-running the experiment with an increased number of metrics.
 Other elements for consideration could be age, location and dialect as variables that affect a metrics performance.
 
-\subsection*{GreenOnion optimizations}
+\subsection*{GreenOnion optimisations}
 A minimal amount of work was allocated to improving the performance of GreenOnion as low-level optimizations are very time-consuming.

### 2019-08-31 Writeup/Paper/sections/experimental_design.tex
Changes; - Implemented corrections for the paper

@@
 
-\subsection{Metric performance}
+\subsection{Experiment 1 - Metric performance}
 This experiment aims to reduce the number of metrics to assess in the later rounds.
@@
 Therefore, possible further work could involve repeating this work with a much more varied selection of metrics.
-The chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors.
+The chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors (See Section \ref{sec:similarity_metric}).
 \\\\
@@
 
-The first was the addition of five "Random matches" questions.
+The first was the addition of five ``Random matches" questions.
 These are matches consisting of two random words selected from the dictionary.
@@
 As both words are the same, the result should always be a full 5/5 rating, any results without a full rating are discarded.
-Figure \ref{fig:exactMatch} contains one example of the attention question used to filter inaccurate results.
-
-\begin{figure}[h!]
-    \centering
-    \begin{adjustbox}{width=0.5\textwidth,center}
-        \fbox{
-            \includegraphics[width=\textwidth]{experiment/exact_experiment_match.png}
-        }
-    \end{adjustbox}
-    \caption{Exact experiment attention question}
-    \label{fig:exactMatch}
-\end{figure}
 
@@
 
-\subsection{Trustword Attacks}
+\subsection{Experiment 2 - Trustword Attacks}
 \label{sec:exp2_design}
@@
 
-\subsubsection{Design}
+\subsubsection*{Design}
 
@@
 
-The start and ends were chosen as the highest priority words to keep static. This design choice is due to research highlighting the common habit of users only to check the start and end of a checksum.
-
 These attacks are ascending in complexity.
@@
 
-% \begin{table}[h!]
-%     \centering
-%     \input{tables/design/attack_types.tex}
-%     \caption{Summary of attack requirements}
-%     \label{tab:attackReq}
-% \end{table}
+\begin{table}[h!]
+    \centering
+    \begin{adjustbox}{width=0.5\textwidth,center}
+        \input{tables/design/attack_types.tex}
+    \end{adjustbox}
+    \caption{Summary of attack requirements}
+    \label{tab:attackReq}
+\end{table}
 
@@
 
-\subsubsection{Quality control}
+\subsubsection*{Quality control}
 \label{sec:exp2_quality}
@@
 As with the previous study, initially screened native speakers are used.
-Alongside this, two metrics are used to detect invalid results: audio-button-clicks and the overall-time.
+Alongside this, two metrics are used to detect invalid results: \textit{audio-button-clicks} and the \textit{overall-time}.
 
-Audio-buttons-clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:trustwordUI} is clicked.
+\textbf{Audio-buttons-clicks} is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:trustwordUI} is clicked.
 If there are rounds without button clicks, this is a sign of non-attentiveness.
@@
 
-Overall-time is as the name suggest a recording of the time taken to complete the entire experiment.
+\textbf{Overall-time} is as the name suggest a recording of the time taken to complete the entire experiment.
 If users complete the experiment in an abnormally small amount of time, it can be used as another detection for invalid responses.

### 2019-08-31 Writeup/Paper/sections/introduction.tex
Changes; - Implemented corrections for the paper

@@
 Trustwords is an implementation of word fingerprint mapping with a emphasis on usability.
-This increase in usability is achieved by the user comparing a reduced number of words.
-This usability boost, however, comes at a cost of a much larger word list ($2^{16}$ words).
+This claimed increase in usability is achieved by the user comparing a reduced number of words.
+The intended usability boost, however, comes at a cost of a much larger word list ($2^{16}$ words).
 

### 2019-08-31 Writeup/Paper/sections/results.tex
Changes; - Implemented corrections for the paper

@@
 
-Figure \ref{tab:exp1_results} shows the average results for the selected matches..
+Figure \ref{tab:exp1_results} shows the average results for the selected matches.
 It can be seen that Levenshtein came out substantially above the rest.
-The breakdown of the ratings in Figure \ref{fig:exp1_breakdown} also shows Levenshtein's dominance.
-Levenshtein has a much more significant proportion of 4 and 5 ratings than the alternatives.
+Levenshtein also has a much more significant proportion of 4 and 5 ratings than the alternatives.
 
@@
 
-\section{Experiment 2 - Trustword attacks}
+\subsection{Experiment 2 - Trustword attacks}
 
@@
             \hline\hline
+            NYSIIS &&  209 & 1114 & 18.8\% \\
+            \hline
+            & \OOOO   & 36 & 385 & ~~9.3\% \\
+            & \XOOO   & 72 & 375 & 19.2\% \\
+            & \XOOX   & 101 & 354 & 28.5\% \\
+            \hline\hline
             Metaphone &&  181 & 1072 & 16.9\% \\
@@
             & \XOOX   & 86 & 352 & 24.4\% \\
-            \hline\hline
-            NYSIIS &&  209 & 1114 & 18.8\% \\
-            \hline
-            & \OOOO   & 36 & 385 & ~~9.3\% \\
-            & \XOOO   & 72 & 375 & 19.2\% \\
-            & \XOOX   & 101 & 354 & 28.5\% \\
             \hline\hline

### 2019-08-31 Writeup/Thesis/chapters/evaluation.tex
Changes; - Implemented corrections for the paper

@@
 
-\subsection*{GreenOnion optimizations}
+\subsection*{GreenOnion optimisations}
 A minimal amount of work was allocated to improving the performance of GreenOnion as low-level optimizations are very time-consuming.

### 2019-09-08 Writeup/Thesis/chapters/abstract.tex
Changes; - Final check for gramatical errors
Changes; - Small corrections added

@@
 A substantial amount of past work has aimed to propose fingerprint representations that work better with human limitations.
-"Trustwords" proposed by pEp is an example of such a scheme, where the fingerprint is encoded as words in an attempt to improve usability.
+"Trustwords" proposed by p$\equiv$p is an example of such a scheme, where the fingerprint is encoded as words in an attempt to improve usability.
 
-This works main aim is to asses if Trustword's recommend minimum number of four words is sufficient.
+This works main aim is to assess if Trustword's recommended minimum number of four words is sufficient.
 In order to achieve this goal, this work implements an attack on Trustwords and quantifies its effectiveness on more than 400 participants.
 A tool called GreenOnion was designed to assist in quantifying attack feasibility.
-GreenOnion improved substantially on a similar tool's ability to search for matches concurrently where it was able to search for over 1.5 million concurrent keys.
+GreenOnion improved substantially on a similar tool's ability to search for matches concurrently.
 Our findings show a substantial increase in attack success compared to related literature.

### 2019-09-08 Writeup/Thesis/chapters/design.tex
Changes; - Small corrections added

@@
 \subsection{Soundex}
-Soundex is one of the most famous example of a phonetic algorithm (See Section \ref{sec:soundex}).
+Soundex is one of the most famous examples of a phonetic algorithm (See Section \ref{sec:soundex}).
 This is due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}.
 
-Soundex, however, has had extensive work focused on its own deficiencies alongside quantification of its performance under certain conditions.
+Soundex, however, has had extensive work focused on its deficiencies alongside quantification of its performance under certain conditions.
 However, even with these previously discussed issues, its algorithmic simplicity and popularity allows it to remain relevant for assessment in this project.
@@
 \subsection{Metaphone}
-Metaphone, as discussed in Section \ref{sec:metaphone} is another famous phonetic algorithm.
+Metaphone, as discussed in Section \ref{sec:metaphone}, is another famous phonetic algorithm.
 Metaphone is arguably on the same level of ubiquity as that of Soundex with it finding itself implemented in languages such as PHP\cite{php}.
@@
 Due to the long lifetime of PGP keys, 7 days was chosen as a reasonable length of the attack.
-The tool requires no user interaction once started, therefore, it can be left for an extended period to compute potential keys.
+The tool requires no user interaction once started.
+Therefore, the tool can be left for an extended period to compute potential keys.
 This timeframe is also a maximum time, as these attacks also include keys that have a shorter average computation time.

### 2019-09-08 Writeup/Thesis/chapters/evaluation.tex
Changes; - Small corrections added

@@
 This paper has discussed several metrics used to quantify phonetic similarity (See Section \ref{sec:metrics}).
-Most metrics were chosen due to their high utilization and occurrence in literature.
+Most metrics were chosen due to their high utilisation and occurrence in literature.
 The only exception to this is the presence of Phonetic Vectors.
@@
 We believe this is due to the implementation of the bloom filter.
-Its unique characteristics of $O(k)$ complexity regardless of the number of elements in the structure allows a huge number of concurrent checks to occur.
+Its unique characteristics of $O(k)$ complexity, regardless of the number of elements in the structure allows a huge number of concurrent checks to occur.
 
@@
 For example, present in the dictionary are the words \verb|THERE| and \verb|THEIR|, these could be massively improved upon and could result in a better quality word list.
-Moreover, utilising the quantification of dissimilarity could be used to create a dictionary of maximized phonetic distance.
+Moreover, utilising the quantification of dissimilarity could be used to create a dictionary of maximised phonetic distance.
 This phonetically distinct wordlist could then be assessed in a similar way with its success rate quantified against users.
@@
 \subsection*{GreenOnion optimisations}
-A minimal amount of work was allocated to improving the performance of GreenOnion as low-level optimizations are very time-consuming.
+A minimal amount of work was allocated to improving the performance of GreenOnion as low-level optimisations are very time-consuming.
 A project, therefore, could aim to improve on the performance already recorded in this paper.

### 2019-09-08 Writeup/Thesis/chapters/implementation.tex
Changes; - Small corrections added

@@
 \section{MainExperiment}
-In order to assess users in a similar scenario to ones experienced when utilizing \pep in the real-world, a custom application was required.
+In order to assess users in a similar scenario to ones experienced when utilising \pep in the real-world, a custom application was required.
 The front-end is developed in Javascript with a Python-Flask backend that acts as the functionality of the webpage.

### 2019-09-08 Writeup/Thesis/chapters/introduction.tex
Changes; - More wording fixes
Changes; - Final check for gramatical errors
Changes; - Small corrections added

@@
 Manual verification is, consequently, left in a difficult position, due in part to proposed solutions needing to sacrifice either usability or security.
-Therefore, research into improving or creating a more secure and user-friendly fingerprint encoding remains an important task.
+Therefore, research into improving or creating secure and user-friendly fingerprint encodings remains an important task.
 
@@
 This claimed increase in usability is achieved by the user comparing a reduced number of words compared to alternatives.
-This potential usability boost, however, comes at a cost of a much larger word list.
+This potential usability boost, however, comes at the cost of a much larger word list.
 
@@
 
-\newpage
 The report is structured as follows:
@@
 
-    \item \textbf{Chapter 5} discusses the significant implementation details of the designs formalized in Chapter 4.
+    \item \textbf{Chapter 5} discusses the significant implementation details of the designs formalised in Chapter 4.
 

### 2019-09-08 Writeup/Thesis/chapters/lit_review.tex
Changes; - Small corrections added

@@
 For example, if the first 2-bits are \verb|11|, the marker moves South East.
-The different characters are determined by the number of times the marker is present in that index, for example, if the maker is present on a square 4 times the character is an equals sign (\verb|=|).
+The different characters are determined by the number of times the marker is present in that index, for example, if the marker is present on a square 4 times the character is an equals sign (\verb|=|).
 
@@
 Each paper used a different metric for measuring accuracy.
-Therefore, all results have been translated into ``overall accuracy.''.
-For example, if a paper presented "security failures" or "attack success rate" of 5\%, the overall accuracy of the scheme is 95\%.
+Therefore, all results have been translated into ``overall accuracy.'' For example, if a paper presented ``security failures'' or ``attack success rate'' of 5\%, the overall accuracy of the scheme is 95\%.
 
@@
 However, this could be due to the different overall use-cases of the studies.
-Validation of results from either study would, therefore, be an area of additional study.
+Validation of results from either study would, therefore, be an area of additional work.
 
@@
 Another gap in the research is the consideration into the utilisation of encoding schemes in realistic conditions, i.e.
-``remove vs proximity." This topic was initially covered by \cite{shirvanian2017pitfalls}, but their scope was limited.
+``remote vs proximity." This topic was initially covered by \cite{shirvanian2017pitfalls}, but their scope was limited.
 
@@
 This work is an extension to work performed by \textbf{Juola} and \textbf{Zimmermann}\cite{juola1996whole} as they aimed to emulate the techniques used in PGPfone.
-The paper's findings are limited by the lack of empirical data backing up claims made by the author the performance of the system, and security is only theoretically assessed.
+The paper's findings are limited by the lack of empirical data backing up claims made by the author on the performance of the system, and security is only theoretically assessed.
 
@@
 Therefore, the wordlist has not been designed with pronounceability in mind.
-Aside from this research, there have been further informal implementations of fingerprint encodings  The first being by \textbf{Michael Rogers}\footnote{\url{https://github.com/akwizgran/basic-english}}.
-Rogers' implementation is a program designed to map fingerprints to pseudo-random poems.
-This implementation was again, empirically evaluated by \textbf{S.
-Dechand \textit{et al.}}\cite{dechand2016empirical}.
-Earlier work by \textbf{N.
-Haller} with the S/KEY\cite{haller1995s} shows the implementation of a system designed to represent a hash as a series of six short words.
-However, this system is designed for a one-time-password purpose and only provides word mappings for basic human usability of the password and not within a fingerprint verification context.
-Therefore, the wordlist has not been designed with pronounceability in mind.
 
 \newpage
+
 \subsubsection*{Pretty Easy Privacy}

### 2019-09-08 Writeup/Paper/sections/background.tex
State at submission

@@
 A similarity metric is an algorithm designed to determine if two words are phonetically a match.
-For example, the words ``THEIR" and "THERE" is a match, whereas the words ``DARK" and ``PRINCIPLE" are not phonetically matching.
+For example, the words ``THEIR'' and ``THERE'' is a match, whereas the words ``DARK'' and ``PRINCIPLE'' are not phonetically matching.
 This section provides a base explanation of important phonetic algorithms relevant in this project.
@@
 Phonemes are the phonetic elements that construct a word.
-For example, the word ``RING" translated into the phonemes \verb|/R IH NG/|.
+For example, the word ``RING'' translated into the phonemes \verb|/R IH NG/|.
 

### 2019-09-08 Writeup/Paper/sections/design.tex
State at submission

@@
 \label{sec:attackDesign}
-The propossed attack on Trustwords involves generating ``near-collision'' keys. Near-collision keys are keys composed of a set of words that are deemed a match by the similarity metrics.
+The proposed attack on Trustwords involves generating ``near-collision'' keys. Near-collision keys are keys composed of a set of words that are deemed a match by the similarity metrics.
 \\\\
 The attack is designed to target a single pair of users and requires recomputation for each attack target pair.
-Each pair is split into an "Uncontrolled" or "Controlled" key.
+Each pair is split into an ``Uncontrolled'' or ``Controlled'' key.
 Uncontrolled is the receiver of the communication, and, thus, the key cannot be altered.
@@
 
-    \item Select a target and allocate ``Uncontrolled" and ``Controlled" key identification.
+    \item Select a target and allocate ``Uncontrolled'' and ``Controlled'' key identification.
 

### 2019-09-08 Writeup/Thesis/chapters/evaluation.tex
State at submission

@@
 Performance of these metrics were then quantified in a direct study that selected the top three from a set of five (See Section \ref{exp:metric}).
-These newly selected metrics was then assessed in an attack context with their performance being indirectly quantified (See Section \ref{sec:exp2_design}).
+These newly selected metrics were then assessed in an attack context with their performance being indirectly quantified (See Section \ref{sec:exp2_design}).
 
@@
 The weakest attack strength and ones that can be computed by a single mid-range GPU for a single week achieved success rate ranging from 9.35\% - 11.01\%.
-The middle attack involving the use of 10 mid-range GPUs for a week had success rates of 15.20\% - 19.20\%.
-Finally, the highest attack strength that theoretically involved the use of 100 mid-range GPUs computing for a week has success rates: 24.43\% - 32.05\%.
+The middle attack involving the use of 70 mid-range GPUs for a week had success rates of 15.20\% - 19.20\%.
+Finally, the highest attack strength that theoretically involved the use of 700 mid-range GPUs computing for a week has success rates: 24.43\% - 32.05\%.
 Therefore, showing the number of attacks required to deceive a set of users.

### 2019-09-08 Writeup/Thesis/chapters/experiments.tex
Changes; - Small corrections added
State at submission

@@
 Figure \ref{tab:scallion_speed} shows the speed decline as the number of concurrently checked potential keys increases.
-Alongside the results for base version of Scallion is the speed for \textit{Scallion Improved}.
+Alongside the results for the base version of Scallion is the speed for \textit{Scallion Improved}.
 This is the same Scallion code but with a fix that reduces the severity of the speed decline.
@@
 As can be seen most notably from Table \ref{tab:nysiis2}, the generation of the actual Trustwords differs in only 3 characters making it arguably very similar.
-When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU can achieve around a 28\% success rate when assessed against actual users.
+When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.93 days on a single mid-range GPU can achieve around a 28\% success rate when assessed against actual users.
 This time, however, has been improved due to the random search for a controlled key with a more favourable number of near-collision keys.
 Even with the least restricted attack type presented in Table \ref{tab:nysiis0}, the computation of half a day can provide almost a 10\% success rate when attacking users.
-This results in any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of deceiving an actual user.
